### 2021-04-28 edubots_surveys.Rnw
Changes to knitr to include results

%% BioMed_Central_Tex_Template_v1.06
%%                                      %
%  bmc_article.tex            ver: 1.06 %
%                                       %

%%IMPORTANT: do not delete the first line of this template
%%It must be present to enable the BMC Submission system to
%%recognise this template!!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                     %%
%%  LaTeX template for BioMed Central  %%
%%     journal article submissions     %%
%%                                     %%
%%          <8 June 2012>              %%
%%                                     %%
%%                                     %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% For instructions on how to fill out this Tex template           %%
%% document please refer to Readme.html and the instructions for   %%
%% authors page on the biomed central website                      %%
%% https://www.biomedcentral.com/getpublished                      %%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%% BioMed Central currently use the MikTex distribution of         %%
%% TeX for Windows) of TeX and LaTeX.  This is available from      %%
%% https://miktex.org/                                             %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% additional documentclass options:
%  [doublespacing]
%  [linenumbers]   - put the line numbers on margins

%%% loading packages, author definitions

%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
\documentclass{bmcart}

%%% Load packages
\usepackage{amsthm,amsmath}
%\RequirePackage[numbers]{natbib}
%\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
%\RequirePackage{hyperref}
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                             %%
%%  If you wish to display your graphics for   %%
%%  your own use using includegraphic or       %%
%%  includegraphics, then comment out the      %%
%%  following two lines of code.               %%
%%  NB: These line *must* be included when     %%
%%  submitting to BMC.                         %%
%%  All figure files must be submitted as      %%
%%  separate graphics through the BMC          %%
%%  submission process, not included in the    %%
%%  submitted article.                         %%
%%                                             %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\includegraphic{}
\def\includegraphics{}

%%% Put your definitions there:
\startlocaldefs
\endlocaldefs

%%% Begin ...
\begin{document}

%%% Start of article front matter
\begin{frontmatter}

\begin{fmbox}
\dochead{Research}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter the title of your article here     %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter the authors here                   %%
%%                                          %%
%% Specify information, if available,       %%
%% in the form:                             %%
%%   <key>={<id1>,<id2>}                    %%
%%   <key>=                                 %%
%% Comment or delete the keys which are     %%
%% not used. Repeat \author command as much %%
%% as required.                             %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\author[
  addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
  corref={aff1},                       % id of corresponding address, if any
% noteref={n1},                        % id's of article notes, if any
  email={jane.e.doe@cambridge.co.uk}   % email address
]{\inits{J.E.}\fnm{Jane E.} \snm{Doe}}
\author[
  addressref={aff1,aff2},
  email={john.RS.Smith@cambridge.co.uk}
]{\inits{J.R.S.}\fnm{John R.S.} \snm{Smith}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter the authors' addresses here        %%
%%                                          %%
%% Repeat \address commands as much as      %%
%% required.                                %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\address[id=aff1]{%                           % unique id
  \orgdiv{Department of Science},             % department, if any
  \orgname{University of Cambridge},          % university, etc
  \city{London},                              % city
  \cny{UK}                                    % country
}
\address[id=aff2]{%
  \orgdiv{Institute of Biology},
  \orgname{National University of Sciences},
  %\street{},
  %\postcode{}
  \city{Kiel},
  \cny{Germany}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter short notes here                   %%
%%                                          %%
%% Short notes will be after addresses      %%
%% on first page.                           %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{artnotes}
%%\note{Sample of title note}     % note to the article
%\note[id=n1]{Equal contributor} % note, connected to author
%\end{artnotes}

\end{fmbox}% comment this for two column layout

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                           %%
%% The Abstract begins here                  %%
%%                                           %%
%% Please refer to the Instructions for      %%
%% authors on https://www.biomedcentral.com/ %%
%% and include the section headings          %%
%% accordingly for your article type.        %%
%%                                           %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstractbox}

\begin{abstract} % abstract
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% The keywords begin here                  %%
%%                                          %%
%% Put each keyword in separate \kwd{}.     %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{keyword}
\kwd{Chatbots}
\kwd{Messaging platforms}
\kwd{Tutorship}
\end{keyword}

% MSC classifications codes, if any
%\begin{keyword}[class=AMS]
%\kwd[Primary ]{}
%\kwd{}
%\kwd[; secondary ]{}
%\end{keyword}

\end{abstractbox}
%
%\end{fmbox}% uncomment this for two column layout

\end{frontmatter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                            %%
%% The Main Body begins here                  %%
%%                                            %%
%% Please refer to the instructions for       %%
%% authors on:                                %%
%% https://www.biomedcentral.com/getpublished %%
%% and include the section headings           %%
%% accordingly for your article type.         %%
%%                                            %%
%% See the Results and Discussion section     %%
%% for details on how to create sub-sections  %%
%%                                            %%
%% use \cite{...} to cite references          %%
%%  \cite{koon} and                           %%
%%  \cite{oreg,khar,zvai,xjon,schn,pond}      %%
%%                                            %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% start of article main body
% <put your article body there>

\section{Introduction}

\section{State of the art}

It is essential, when implementing a educational chatbot strategy, to
asses the needs of the community prior to implementation \cite{tsivitanidouusers}.

\bibliographystyle{apalike}
\bibliography{edubots}

\begin{backmatter}

\section*{Acknowledgements}%% if any

This paper has been funded by the Edubots project...

\end{backmatter}

\end{document}

### 2021-04-28 scripts/summaries.R
Continuing analyzing percentages, #3

@@ -1,0 +1,13 @@
+library(psych)
+library(dplyr)
+library(tidyr)
+
+data <- read.csv("../data/survey-pilot-3.csv")
+
+data %>% group_by( Gender, WhatsApp ) %>% summarise ( n = n() ) %>% mutate( freqWhatsApp = n/sum(n)) -> freq.Gender.WhatsApp
+data %>% group_by( Experience, WhatsApp ) %>% summarise ( n = n() ) %>% mutate( freqWhatsApp = n/sum(n)) -> freq.Experience.WhatsApp
+data %>% group_by( Sector, WhatsApp ) %>% summarise ( n = n() ) %>% mutate( freqWhatsApp = n/sum(n)) -> freq.Sector.WhatsApp
+
+data %>% group_by( Gender, Provided ) %>% summarise ( n = n() ) %>% mutate( freqWhatsApp = n/sum(n)) -> freq.Gender.Platform
+data %>% group_by( Experience, Provided ) %>% summarise ( n = n() ) %>% mutate( freqWhatsApp = n/sum(n)) -> freq.Experience.Platform
+data %>% group_by( Sector, Provided ) %>% summarise ( n = n() ) %>% mutate( freqWhatsApp = n/sum(n)) -> freq.Sector.Platform

### 2021-04-28 edubots_surveys.Rnw
Decided on title closes #4
Adds /me #8

@@
 
-\title{}
+\title{Chatbots in the classroom: a analysis from the teacher's perspective}
 
@@
   corref={aff1},                       % id of corresponding address, if any
-% noteref={n1},                        % id's of article notes, if any
-  email={jane.e.doe@cambridge.co.uk}   % email address
-]{\inits{J.E.}\fnm{Jane E.} \snm{Doe}}
+  email={jmerelo@ugr.es}   % email address
+]{\inits{J.J.}\fnm{Juan J.} \snm{Merelo}}
 \author[
@@
 \address[id=aff1]{%                           % unique id
-  \orgdiv{Department of Science},             % department, if any
-  \orgname{University of Cambridge},          % university, etc
-  \city{London},                              % city
-  \cny{UK}                                    % country
+  \orgdiv{Department of Computer Architecture and Technology},             % department, if any
+  \orgname{University of Granada},          % university, etc
+  \city{Granada},                              % city
+  \cny{Spain}                                    % country
 }

### 2021-05-02 scripts/process-tutorship.R
Improve processing, refs #9

@@ -1,0 +1,25 @@
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+library(scales)
+library(ggthemes)
+
+data <- read.csv("../data/survey-student-interaction-pilot-3-2021.csv")
+
+ggplot(data, aes(x = Familiarity, group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age)
+ggplot(data, aes(x = Horizontality, group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age)
+ggplot(data, aes(x = Connectivity, group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age)
+
+ggplot(data, aes(x = Familiarity, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)
+ggplot(data, aes(x = Horizontality, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)
+ggplot(data, aes(x = Connectivity, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)
+
+ggplot(data, aes(x = Familiarity, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Discipline)
+ggplot(data, aes(x = Horizontality, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Discipline)
[…]

### 2021-05-02 scripts/process-tutorship.R
Fixes processing

@@ -9,17 +9,25 @@ data <- read.csv("../data/survey-student-interaction-pilot-3-2021.csv")
 ggplot(data, aes(x = Familiarity, group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age)
 ggplot(data, aes(x = Horizontality, group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age)
 ggplot(data, aes(x = Connectivity, group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age)
+ggplot(data, aes(x = Sustainability, group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age)
+ggplot(data, aes(x = OfficialFormation, group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age)
 
 ggplot(data, aes(x = Familiarity, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)
 ggplot(data, aes(x = Horizontality, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)
 ggplot(data, aes(x = Connectivity, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)
[…]

### 2021-05-03 edubots_surveys.Rnw
First draft abstract refs #5

@@
 %\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
-%\RequirePackage{hyperref}
+\RequirePackage{hyperref}
 \usepackage[utf8]{inputenc} %unicode support
-%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
-%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
 
@@
 \begin{abstractbox}
-
+Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but, above all, an examination of the attitudes of the affected community.
+In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think of the introduction of messaging platforms, what are their needs, what kind of use case they see for them, and in what kind of environment they think its use will be useful.
+We will examine how and when these attitudes vary across gender, experience, and other factors, such as the kind of discipline they are teaching.
 \begin{abstract} % abstract

### 2021-05-03 edubots_surveys.Rnw
Deletes hyperref that produced errors

@@
 \usepackage{amsthm,amsmath}
-%\RequirePackage[numbers]{natbib}
-%\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
-\RequirePackage{hyperref}
+
 \usepackage[utf8]{inputenc} %unicode support
@@
 \begin{abstractbox}
+
+\begin{abstract} % abstract
 Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but, above all, an examination of the attitudes of the affected community.
@@
 We will examine how and when these attitudes vary across gender, experience, and other factors, such as the kind of discipline they are teaching.
-\begin{abstract} % abstract
 \end{abstract}

### 2021-05-04 edubots_surveys.Rnw
adding contents to Introduction and SoA sections

@@
 
+% TODO: introduction
+
+The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}.
+These automatic systems ease personalized learning, adapting individuals' pace of learning, who get personalized online tutoring outside the classroom.
+
+A chatbot is a program that allows the machine to communicate in a similar way as a human does \cite{Gong2008}.
+Chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.
+
+In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor.
+In fact, in many cases, students suffer stress when they have to ask a question in front of the entire class.
+This is why many students prefer to remain silent and ask their question later via email.
+However, this means a waste of time and a delay of hours or even days to get the teacher's answer.
+Chatbot technology has a potential to fill the gap between teacher and students, helping them to solve questions and carry out a dynamic and autonomous learning \cite{Griol2014,kim2020}.
+Moreover, using an automated system such as a chatbot allows the teacher to detect those topics that are most in demand, and on which he or she should consequently place more emphasis in class.
+
 \section{State of the art}
@@
 asses the needs of the community prior to implementation \cite{tsivitanidouusers}.
+
+% TODO: state of the art
+
+% student/teacher preferences towards messaging and chatbots (#6)
+
+Conversational programs to facilitate communication between computers and humans using natural language have existed for many years \cite{Thompson2007,SHAH2016}. 
+However, those were very limited systems in terms of the capacity of the models used at the time \cite{Hutchens1996}.
+
+In recent years, several authors have carried out studies on the convenience of integrating chatbots in teaching, evaluating their characteristics. 
+Thus, Coniam \cite{Coniam2014} evaluates several systems, concluding that they are still in an early stage to be used with guarantees.
+Likewise, Tallyn et al. \cite{Tallyn2018} evaluates a system related to a very specific topic that is suitable for answering specific questions using a chat.
+Finally, Smutny et al.
+\cite{Smutny2020} present a review study examining the educational chatbots in Facebook Messenger with focus to identify characteristics such as language, subject matter and platform.
+
+According to \cite{Roblyer2010}, using either tools such as mobile devices or teaching strategies based on gamification \cite{Yildirim2017} can improve student motivation.
+In this sense, Pimmer et al.
+\cite{Pimmer2019} carried out a series of experiments with technological tools whose results showed positive perception and acceptance of the use of technology in teaching and learning, since students are used to using those media with which they can express themselves freely.
 

### 2021-05-07 edubots_surveys.Rnw
fix some references
Working a bit on the introduction

@@
 \author[
-  addressref={aff1,aff2},
-  email={john.RS.Smith@cambridge.co.uk}
-]{\inits{J.R.S.}\fnm{John R.S.} \snm{Smith}}
+  addressref={aff1},
+  email={pacv@ugr.es}   % email address
+]{\inits{P.A.}\fnm{Pedro A.} \snm{Castillo}}
+\author[
+  addressref={aff2},
+  email={amorag@ugr.es}
+]{\inits{A.M.G}\fnm{Antonio M.} \snm{Mora}}
 
@@
 \address[id=aff2]{%
-  \orgdiv{Institute of Biology},
-  \orgname{National University of Sciences},
-  %\street{},
-  %\postcode{}
-  \city{Kiel},
-  \cny{Germany}
+  \orgdiv{Department of Signal Theory, Telematics and Communications},
+  \orgname{University of Granada},          % university, etc
+  \city{Granada},                              % city
+  \cny{Spain}                                    % country
 }
@@
 
+A \textit{chatbot} is a program that allows a computer to communicate in a similar way as a human does \cite{Gong2008}.
+Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker’s question fluently, and even ask other questions to the human.
+
 The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}.
 These automatic systems ease personalized learning, adapting individuals' pace of learning, who get personalized online tutoring outside the classroom.
-
-A chatbot is a program that allows the machine to communicate in a similar way as a human does \cite{Gong2008}.
-Chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.
+Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.
 
 In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor.
-In fact, in many cases, students suffer stress when they have to ask a question in front of the entire class.
+In fact, in many cases, students suffer from stress when they have to ask a question in front of the entire class.
 This is why many students prefer to remain silent and ask their question later via email.
@@
 
-It is essential, when implementing a educational chatbot strategy, to
-asses the needs of the community prior to implementation \cite{tsivitanidouusers}.
+It is essential, when implementing a educational chatbot strategy, to asses the needs of the community prior to implementation \cite{tsivitanidouusers}.
 
@@
 
-This paper has been funded by the Edubots project...
+This work has been supported by EDUBOTS project, funded under the scheme Erasmus + KA2: Cooperation for innovation and the exchange of good practices - Knowledge Alliances (grant agreement no: 612446).
 

### 2021-05-10 edubots_surveys.Rnw
adds author and fixes title refs #8
fixes typos in abstract refs #5

@@
 \begin{document}
+\SweaveOpts{concordance=TRUE}
 
@@
 
-\title{Chatbots in the classroom: a analysis from the teacher's perspective}
+\title{Chatbots in the classroom: an analysis from the teacher's perspective}
 
@@
 ]{\inits{A.M.G}\fnm{Antonio M.} \snm{Mora}}
+\author[
+  addressref={aff1},
+  email={fbarranco@ugr.es}
+]{\inits{F.}\fnm{Francisco} \snm{Barranco}}
 
@@
 \begin{abstract} % abstract
-Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but, above all, an examination of the attitudes of the affected community.
-In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think of the introduction of messaging platforms, what are their needs, what kind of use case they see for them, and in what kind of environment they think its use will be useful.
+Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but above all, an examination of the attitudes of the affected community.
+In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think of the introduction of messaging platforms, what their needs are, what kind of use cases they see for them, and in what kind of environment they think its use will be valuable.
 We will examine how and when these attitudes vary across gender, experience, and other factors, such as the kind of discipline they are teaching.

### 2021-05-14 edubots_surveys.Rnw
Adds small intro

@@
 \begin{document}
-\SweaveOpts{concordance=TRUE}
 
@@
   email={fbarranco@ugr.es}
-]{\inits{F.}\fnm{Francisco} \snm{Barranco}}
+]{\inits{F.}\fnm{Francisco} \snm{Barranco}}<
 
@@
 \kwd{Tutorship}
+\kwd{Educational bots}
+\kwd{Higher education}
 \end{keyword}
@@
 % TODO: introduction
+Introduction of new technologies in the classroom needs a combination of teacher education, as well as student willingness and skills.
+Some technologies are readily adapted, some of them take a long time to be adopted.
+In most cases, success or failure of the introduction of a
 
@@
 
+\section{Conclusions}
+
+\section*{Acknowledgements}
+
 \bibliographystyle{apalike}

### 2021-05-15 edubots_surveys.Rnw
extends introduction with research questions refs #10

@@
   email={fbarranco@ugr.es}
-]{\inits{F.}\fnm{Francisco} \snm{Barranco}}<
+]{\inits{F.}\fnm{Francisco} \snm{Barranco}}
 
@@
 
+% Maybe move it to a different place later
+As a starting point, we have analyzed the responses to a survey from XXX teachers asking about their attitudes towards the use of chatbots in their classes.
+We are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
+\begin{itemize}
+\item{ RQ1 - Are teachers willing to use chatbots in their classes? }
+\item{ RQ2 - Which kind of chatbots are they interested in? }
+\item{ RQ3 - Regarding technology acceptance, are there any differences regarding age, gender,  or years of experience in Education? }
+\item{ RQ4 - } 
+\end{itemize}
+
 \section{State of the art}
@@
 
+Regarding the factors for the adoption of chatbots in Education, many studies have focused on the evaluation of technology acceptance or usability.
+However, Higher Education is a special domain where according to \cite{hobert2019you}, specific pedagogical factors such as learning success or increased motivation are more important.
+
 \section{Conclusions}

### 2021-05-16 edubots_surveys.Rnw
adds new works to state of the art refs #6
adds chatbot categories and adoption factors refs #6

@@
 
-Regarding the factors for the adoption of chatbots in Education, many studies have focused on the evaluation of technology acceptance or usability.
+% Categorization and examples of what they can do, adapted to questions in the survey   
+A possible categorization of chatbots in Education splits them according to their purpose into service- and teaching-oriented \cite{perez2020rediscovering}.
+The first class includes chatbots that provide service support used e.g.
+to solve questions about the enrollment \cite{santoso2018dinus}, registration, or academic requirements for exchange students \cite{ranoliya2017chatbot}.
+Focusing on the use at class, service-oriented chatbots would help to introduce students to each other (as done with LISA \cite{dibitonto2018chatbot}), would provide information about schedules and deadlines, recommend general learning materials for the next classes, or individually inform about grades.
+Teaching-oriented chatbots are more sophisticated chatbots that set goals and monitor learning progress.
+A simple example is described in \cite{coronado2018cognitive} where authors proposed agents that store learning materials to be provided on demand to students.
+Also, more complex tutoring systems \cite{crockett2017predicting} individually analyze the learning state of students to provide the next most suitable material in their learning path.
+
+% Point: chatbots are accepted if they help to achieve learning goals
+Regarding the factors for the adoption of chatbots in Education, many studies have focused on the evaluation of technology acceptance or usability such as \cite{Pimmer2019, Roblyer2010}.
 However, Higher Education is a special domain where according to \cite{hobert2019you}, specific pedagogical factors such as learning success or increased motivation are more important.

### 2021-05-19 scripts/translate.py
add script for translating responses and new csv file refs #12

@@ -1,0 +1,22 @@
+data = ""
+
+with open("../data/survey-pilot-3.csv") as file:
+     data = file.read()
+
+#Age
+data = data.replace("Más de 55", "> 55")
+
+#Experience 
+data = data.replace("0-5 años", "0-5 years")
+data = data.replace("5-15 años", "6-15 years")
+data = data.replace("15-25 años", "16-25 years")
+data = data.replace("más de 25 años", "> 25 years")
+
+#Gender
+data = data.replace("Hombre", "Male")
+data = data.replace("Mujer", "Female")
+data = data.replace("Prefiero no decirlo", "DN/NA/REF")
+
+
+with open("../data/survey-pilot-3-EN.csv","w") as file:
+     file.write(data)

### 2021-05-19 scripts/process.R
Updates data and scripts for chatbots use refs #12

@@ -5,30 +5,51 @@ library(tidyr)
 library(scales)
 library(ggthemes)
 
-data <- read.csv("../data/survey-pilot-3.csv")
+# data <- read.csv("../data/survey-pilot-3.csv")
+data <- read.csv("../data/survey-pilot-3-EN.csv")
 
-ggplot(data, aes(x = WhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)
-ggplot(data, aes(x = Telegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)
-ggplot(data, aes(x = Provided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)
+ggplot(data, aes(x = WhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)
+ggsave('../figures/sector_whatsapp.eps')
+ggplot(data, aes(x = Telegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)
+ggsave('../figures/sector_telegram.eps')
+ggplot(data, aes(x = Provided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)
+ggsave('../figures/sector_provided.eps')
 
-ggplot(data, aes(x = WhatsApp, group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age)
[…]

### 2021-05-19 scripts/translate.py

@@ -7,15 +7,23 @@ with open("../data/survey-pilot-3.csv") as file:
 data = data.replace("Más de 55", "> 55")
 
 #Experience 
-data = data.replace("0-5 años", "0-5 years")
-data = data.replace("5-15 años", "6-15 years")
+data = data.replace("0-5 años", "0-05 years")
+data = data.replace("5-15 años", "06-15 years")
 data = data.replace("15-25 años", "16-25 years")
 data = data.replace("más de 25 años", "> 25 years")
 
 #Gender
 data = data.replace("Hombre", "Male")
 data = data.replace("Mujer", "Female")
-data = data.replace("Prefiero no decirlo", "DN/NA/REF")
+data = data.replace("Prefiero no decirlo", "PNTS")
+
+#Discipline
+data = data.replace("Biosanitaria", "Biomedicine")
+data = data.replace("Ciencias Sociales", "Social Sciences")
+data = data.replace("Ciencias", "Sciences")
+data = data.replace("Humanidades", "Humanities")
+data = data.replace("Ingeniería", "Engineering")
+data = data.replace("Tecnología", "Technology")
 
 
 with open("../data/survey-pilot-3-EN.csv","w") as file:

### 2021-05-19 edubots_surveys.Rnw
minor fixes
Creates figures for RQ1 on chatbots use refs #13

@@
 Thus, Coniam \cite{Coniam2014} evaluates several systems, concluding that they are still in an early stage to be used with guarantees.
-Likewise, Tallyn et al. \cite{Tallyn2018} evaluates a system related to a very specific topic that is suitable for answering specific questions using a chat.
+Likewise, Tallyn et al.
+\cite{Tallyn2018} evaluates a system related to a very specific topic that is suitable for answering specific questions using a chat.
 Finally, Smutny et al.
@@
 
+\section{Results}
+
+% Describe the survey and population
+
+\subsection{RQ1 - Are teachers usings chatbots in their classes?}
+
+\begin{figure}[t]
+\begin{center}
+    \begin{minipage}[t]{0.30\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/gender_provided.eps}
+    \end{minipage}
+    \begin{minipage}[t]{0.30\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/age_provided.eps}
+    \end{minipage}
+    \begin{minipage}[t]{0.30\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/experience_provided.eps}
+    \end{minipage}
+
+    \vspace{2mm}
+    \begin{minipage}[t]{0.30\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/gender_whatsapp.eps}
+    \end{minipage}
+    \begin{minipage}[t]{0.30\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/age_whatsapp.eps}
+    \end{minipage}
+    \begin{minipage}[t]{0.30\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/experience_whatsapp.eps}
+    \end{minipage}
+
+    \vspace{2mm}
+    \begin{minipage}[t]{0.30\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/gender_telegram.eps}
+    \end{minipage}
+    \begin{minipage}[t]{0.30\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/age_telegram.eps}
+    \end{minipage}
+    \begin{minipage}[t]{0.30\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/experience_telegram.eps}
+    \end{minipage}
+\end{center}
+    \caption{Use of chatbots in class: distributions per gender and age.
+Teachers were specifically asked about two popular instant messaging apps (Whatsapp and Telegram), and the use of platforms already provided by their institutions different than these two ones.}
+\label{figure:chatbots_use_gender_age}
+\end{figure}
+
+\begin{figure}[t]
+\begin{center}
+    \begin{minipage}[t]{0.30\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/sector_provided.eps}
+    \end{minipage}
+    \begin{minipage}[t]{0.50\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/discipline_provided.eps}
+    \end{minipage}
+
+    \vspace{2mm}
+    \begin{minipage}[t]{0.30\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/sector_whatsapp.eps}
+    \end{minipage}
+    \begin{minipage}[t]{0.50\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/discipline_whatsapp.eps}
+    \end{minipage}
+
+    \vspace{2mm}
+    \begin{minipage}[t]{0.30\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/sector_telegram.eps}
+    \end{minipage}
+    \begin{minipage}[t]{0.50\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/discipline_telegram.eps}
+    \end{minipage}
+\end{center}
+    \caption{XXXX}
+\label{figure:chatbots_use_sector_discip_exp}
+\end{figure}
+
 \section{Conclusions}

### 2021-05-19 edubots_surveys.Rnw
Adds some text to RQ1 ref #13

@@
 \begin{itemize}
-\item{ RQ1 - Are teachers willing to use chatbots in their classes? }
+\item{ RQ1 - Are teachers already using messaging apps in their classes? }
 \item{ RQ2 - Which kind of chatbots are they interested in? }
@@
 % Describe the survey and population
+We collected responses from a total of XXX teachers from University and Vocational Education from Spain ...
 
-\subsection{RQ1 - Are teachers usings chatbots in their classes?}
+\subsection{RQ1 - Are teachers already using messaging apps in their classes?}
+
+%Why messaging apps are relevant here --> connect to the development of chatbots
+Group messaging apps have become a powerful tool for keeping touch with students. Also, they are the baseline platform for the development of chatbots to help with the learning process.
+
+According to the results summarized in Fig.
+\ref{figure:chatbots_use_gender_age_exp}, there are no significant differences between male and female teachers.
+Regarding the instant messaging apps, teachers mainly use Whatsapp (40\%-50\%), the most popular messaging app in Spain.
+Similar numbers are shown for the use of the app provided by their institutions, Universities or Education System Administration.
+Finally, about 20\% use Telegram.
+The distribution of messaging apps per age are not significant for the Whatsapp and apps provided by their institutions.
+However, younger teachers use also Telegram with more than 25\%, a percentage that falls to about 10\% for teachers that are 55 or older.
+The third column compares the use of these apps considering the number of years of experience.
+One interesting result is that, contrarily to the idea of technology adaptation issues when considering older teachers, about 65\% of teachers with more than 25 years of experience use the platforms provided by their institutions while the percentage goes down to less than 50\% for teachers with 6-15 years of experience.
 
@@
 Teachers were specifically asked about two popular instant messaging apps (Whatsapp and Telegram), and the use of platforms already provided by their institutions different than these two ones.}
-\label{figure:chatbots_use_gender_age}
+\label{figure:chatbots_use_gender_age_exp}
 \end{figure}
+
+Results in Fig.
+\ref{figure:chatbots_use_sector_discip} do not show differences in the use of instant messaging apps between teachers from University and vocational education.
+In general, most teachers prefer messaging apps provided by their own institutions.
+With respect to specific disciplines, Engineering and Technology teachers are more active in their use, although it is also relevant the amount of teachers from Humanities that answered they used these apps in their classes (around 60\% use the apps provided by their institutions).
 
@@
 \end{center}
-    \caption{XXXX}
-\label{figure:chatbots_use_sector_discip_exp}
+    \caption{Differences in the use of chatbots in class between vocational and university teaching and distributions by discipline.}
+\label{figure:chatbots_use_sector_discip}
 \end{figure}

### 2021-05-19 scripts/process.R
Updates data and scripts for covid impact refs #12

@@ -54,6 +54,9 @@ ggplot(data, aes( x = Messaging.Organization, y = ..count.., group=Sector, fill 
 
 data %>% group_by( PostCOVID.changes ) %>% filter( n() > 1 ) -> data.postCOVID
 data.postCOVID <- within(data.postCOVID, PostCOVID.changes <- factor(PostCOVID.changes, levels=names(sort(table(PostCOVID.changes), decreasing=TRUE))))
-ggplot(data.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()
-ggplot(data.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()
-ggplot(data.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()
+ggplot(data.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+ggsave('../figures/sector_covid.pdf')
+ggplot(data.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+ggsave('../figures/gender_covid.pdf')
+ggplot(data.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+ggsave('../figures/experience_covid.pdf')

### 2021-05-19 scripts/translate.py

@@ -25,6 +25,11 @@ data = data.replace("Humanidades", "Humanities")
 data = data.replace("Ingeniería", "Engineering")
 data = data.replace("Tecnología", "Technology")
 
+#PostCOVID Changes
+data = data.replace("No, antes la usaba y ahora la sigo usando.", "No, I did use it before, and use it now")
+data = data.replace("Sí, antes no usaba ningún tipo de plataforma de mensajería y ahora sí la uso.", "Yes, I didn't use any messaging app before, but do use it now")
+data = data.replace("Sí, he cambiado de plataforma de mensajería a otras más seguras.", "Yes, I use a safer messaging app now")
+data = data.replace("No, no la usaba antes ni ahora.", "No, I didn't use it before, and don't use it now")
 
 with open("../data/survey-pilot-3-EN.csv","w") as file:
      file.write(data)

### 2021-05-19 edubots_surveys.Rnw
Extends RQ1 with discussion on covid impact ref #13

@@
 
+Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' attitudes towards the instant messaging apps.
+The 273 answers are summarized in Fig.
+\ref{figure:chatbots_use_postcovid}, showing that about 77\% of teachers already used these tools before the pandemic and kept using them during the pandemic lockdowns that forced students and educators to use remote education schemes.
+Moreover, approximately 15\% of them switched their messaging app for one that offered a safer interaction with their students.
+According to the responses, an additional 16\% started using messaging apps during the pandemic for the first time in their classes.
+Aggregating the answers, currently 91\% of the teachers are using messaging apps as learning tools.
+
+A few relevant facts from the collected data: teachers with 16-25 years of experience seem more worried about the security of messaging apps and teachers with up to 5 years of experience were more open to adopt messaging apps due to the pandemic; female teachers were more willing to adopt new platforms due to the pandemic, and even to start using safer alternatives; finally, university teachers that did not use them were more reluctant to start using them after the pandemic.
+
+\begin{figure}[t]
+\begin{center}
+    \begin{minipage}[t]{0.45\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/gender_covid.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.45\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.45\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/experience_covid.pdf}
+    \end{minipage}
+\end{center}
+    \caption{Impact of COVID in the use of messaging apps in University and vocational education.}
+\label{figure:chatbots_use_postcovid}
+\end{figure}
+
 \section{Conclusions}

### 2021-05-20 scripts/process.R
Does update new ones in pdf for RQ1 refs #13

@@ -9,44 +9,44 @@ library(ggthemes)
 data <- read.csv("../data/survey-pilot-3-EN.csv")
 
 ggplot(data, aes(x = WhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)
-ggsave('../figures/sector_whatsapp.eps')
+ggsave('../figures/sector_whatsapp.pdf')
 ggplot(data, aes(x = Telegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)
-ggsave('../figures/sector_telegram.eps')
+ggsave('../figures/sector_telegram.pdf')
 ggplot(data, aes(x = Provided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)
-ggsave('../figures/sector_provided.eps')
+ggsave('../figures/sector_provided.pdf')
 
 
 ggplot(data, aes(x = WhatsApp, group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age)
-ggsave('../figures/age_whatsapp.eps')
+ggsave('../figures/age_whatsapp.pdf')
 ggplot(data, aes(x = Telegram, group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age)
-ggsave('../figures/age_telegram.eps')
+ggsave('../figures/age_telegram.pdf')
 ggplot(data, aes(x = Provided, group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age)
-ggsave('../figures/age_provided.eps')
+ggsave('../figures/age_provided.pdf')
 
 
[…]

### 2021-05-20 scripts/translate.py
Updates data and scripts for messaging organization refs #13

@@ -40,7 +40,8 @@ data = data.replace("No, no la usaba antes ni ahora.", "No, I didn't use it befo
 data = data.replace("Prefiero que los estudiantes se autoorganicen y no estar en ningún grupo de mensajería", "I'd rather leave students self-organize and not be part of the chat")
 data = data.replace("Un grupo con los estudiantes de mi asignatura", "A chat with my students in the same course")
 data = data.replace("Un grupo para el curso completo (profesores y estudiantes)", "A chat with all students and teachers in the same semester/year")
-data = data.replace("Un grupo para toda la titulación, Facultad o Escuela (profesores y estudiantes)", "A chat with all the students and teachers in my Faculty or School")
+data = data.replace("Un grupo para toda la titulación o instituto (profesores y estudiantes)", "A chat with all the students and teachers in the same studies (all years)")
+data = data.replace("Un grupo para toda la titulación, Facultad o Escuela (profesores y estudiantes)", "A chat with all the students and teachers in my Faculty/School")
 
 with open("../data/survey-pilot-3-EN.csv","w") as file:
      file.write(data)

### 2021-05-20 scripts/process.R
Adds new figure for messaging organization refs #13

@@ -49,9 +49,6 @@ ggplot(data, aes(x = Provided, group = Gender)) + geom_bar(aes(y = ..prop.., fil
 ggsave('../figures/gender_provided.pdf')
 
 
-data <- within(data, Messaging.Organization <- factor(Messaging.Organization, levels=names(sort(table(Messaging.Organization), decreasing=TRUE))))
-ggplot(data, aes( x = Messaging.Organization, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90))+coord_flip()
-
 data %>% group_by( PostCOVID.changes ) %>% filter( n() > 1 ) -> data.postCOVID
 data.postCOVID <- within(data.postCOVID, PostCOVID.changes <- factor(PostCOVID.changes, levels=names(sort(table(PostCOVID.changes), decreasing=TRUE))))
 ggplot(data.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
@@ -60,3 +57,14 @@ ggplot(data.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Gender, 
 ggsave('../figures/gender_covid.pdf')
 ggplot(data.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
 ggsave('../figures/experience_covid.pdf')
+
+
+#Several answers in the same cell: need to split them (use the commas in the original csv in Spanish as separator after translation)
+#data <- within(data, Messaging.Organization <- factor(Messaging.Organization, levels=names(sort(table(Messaging.Organization), decreasing=TRUE))))
+#ggplot(data, aes( x = Messaging.Organization, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90))+coord_flip()
+
+library(tidyverse)
+data %>%  mutate(Messaging.Organization =str_split(Messaging.Organization, ", ")) %>% unnest(cols = c(Messaging.Organization)) -> data.MessagingOrganization
[…]

### 2021-05-20 scripts/process.R
Fixes image sizes, automatically generated now

@@ -9,54 +9,54 @@ library(ggthemes)
 data <- read.csv("../data/survey-pilot-3-EN.csv")
 
 ggplot(data, aes(x = WhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)
-ggsave('../figures/sector_whatsapp.pdf')
+ggsave('../figures/sector_whatsapp.pdf', width = 130, height = 70, units = "mm")
 ggplot(data, aes(x = Telegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)
-ggsave('../figures/sector_telegram.pdf')
+ggsave('../figures/sector_telegram.pdf', width = 130, height = 70, units = "mm")
 ggplot(data, aes(x = Provided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)
-ggsave('../figures/sector_provided.pdf')
+ggsave('../figures/sector_provided.pdf', width = 130, height = 70, units = "mm")
 
 
 ggplot(data, aes(x = WhatsApp, group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age)
-ggsave('../figures/age_whatsapp.pdf')
+ggsave('../figures/age_whatsapp.pdf', width = 130, height = 70, units = "mm")
 ggplot(data, aes(x = Telegram, group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age)
-ggsave('../figures/age_telegram.pdf')
+ggsave('../figures/age_telegram.pdf', width = 130, height = 70, units = "mm")
[…]

### 2021-05-21 edubots_surveys.Rnw
Does update new ones in pdf for RQ1 refs #13
Fixes image sizes, automatically generated now
Extends RQ1 discussion with messaging organization data refs #13

@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/gender_provided.eps}
+ 	    \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/age_provided.eps}
+ 	    \includegraphics[width=\textwidth]{figures/age_provided.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/experience_provided.eps}
+ 	    \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/gender_whatsapp.eps}
+ 	    \includegraphics[width=\textwidth]{figures/gender_whatsapp.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/age_whatsapp.eps}
+ 	    \includegraphics[width=\textwidth]{figures/age_whatsapp.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/experience_whatsapp.eps}
+ 	    \includegraphics[width=\textwidth]{figures/experience_whatsapp.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/gender_telegram.eps}
+ 	    \includegraphics[width=\textwidth]{figures/gender_telegram.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/age_telegram.eps}
+ 	    \includegraphics[width=\textwidth]{figures/age_telegram.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/experience_telegram.eps}
+ 	    \includegraphics[width=\textwidth]{figures/experience_telegram.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/sector_provided.eps}
+ 	    \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/discipline_provided.eps}
+ 	    \includegraphics[width=\textwidth]{figures/discipline_provided.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/sector_whatsapp.eps}
+ 	    \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/discipline_whatsapp.eps}
+ 	    \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/sector_telegram.eps}
+ 	    \includegraphics[width=\textwidth]{figures/sector_telegram.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/discipline_telegram.eps}
+ 	    \includegraphics[width=\textwidth]{figures/discipline_telegram.pdf}
     \end{minipage}
@@
 \label{figure:chatbots_use_sector_discip}
+\end{figure}
+
+Regarding the social factor of chat groups that teachers use in class, according to Fig.
+\ref{figure:chatbots_messagingorganization} the vast majority prefer small groups only with the students from the same course.
+These are more focused groups with specific goals and dedicated to the organization of the course and its tasks, and from the pedagogic point of view seem more appropriate to improve the learning process.
+Interestingly, about 30\% of teachers consider they should not be part of the chat group.
+Also, only university teachers find interesting a group with all the students and teachers in their own Faculty or School.
+The lack of teachers from vocational Education here may be the consequence of using specific language such as "Faculty".
+Moreover, the fact that many universities and schools already use these groups for administrative and social interaction (e.g.
+\cite{dibitonto2018chatbot}) might be the reason for the low percentage of teachers that selected this response.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=\textwidth]{figures/messaging_organization.pdf}
+\caption{XXX}
+\label{figure:chatbots_messagingorganization}
 \end{figure}
@@
 \begin{center}
-    \begin{minipage}[t]{0.45\textwidth}
+    \begin{minipage}[t]{0.47\textwidth}
 	    \centering
@@
     \end{minipage}
-    \begin{minipage}[t]{0.45\textwidth}
+    \begin{minipage}[t]{0.47\textwidth}
 	    \centering

### 2021-05-21 scripts/process.R

@@ -8,45 +8,45 @@ library(ggthemes)
 # data <- read.csv("../data/survey-pilot-3.csv")
 data <- read.csv("../data/survey-pilot-3-EN.csv")
 
-ggplot(data, aes(x = WhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)
-ggsave('../figures/sector_whatsapp.pdf', width = 130, height = 70, units = "mm")
-ggplot(data, aes(x = Telegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)
-ggsave('../figures/sector_telegram.pdf', width = 130, height = 70, units = "mm")
-ggplot(data, aes(x = Provided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)
-ggsave('../figures/sector_provided.pdf', width = 130, height = 70, units = "mm")
+ggplot(data, aes(x = WhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+ggsave('../figures/sector_whatsapp.pdf', width = 100, height = 70, units = "mm")
+ggplot(data, aes(x = Telegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+ggsave('../figures/sector_telegram.pdf', width = 100, height = 70, units = "mm")
[…]

### 2021-05-21 edubots_surveys.Rnw
Adds telegram frequencies and changes perc. in text refs #13

@@
 According to the results summarized in Fig.
-\ref{figure:chatbots_use_gender_age_exp}, there are no significant differences between male and female teachers.
-Regarding the instant messaging apps, teachers mainly use Whatsapp (40\%-50\%), the most popular messaging app in Spain.
-Similar numbers are shown for the use of the app provided by their institutions, Universities or Education System Administration.
-Finally, about 20\% use Telegram.
-The distribution of messaging apps per age are not significant for the Whatsapp and apps provided by their institutions.
+\ref{figure:chatbots_use_gender_age_exp}, teachers mainly use the instant messaging app provided by their institutions (55\%),  and Whatsapp (44\%), the most popular messaging app in Spain.
+Finally, about 20\% also use Telegram.
+Although gender differences are not significant, female teachers answered they use instant messaging apps more than male teachers (about 10\% more).
+Also, teachers in vocational Education also use Whatsapp more than university teachers.
+
+With respect to the distribution of the use of messaging apps per age, there are no significant differences for the Whatsapp and apps provided by their institutions.
 However, younger teachers use also Telegram with more than 25\%, a percentage that falls to about 10\% for teachers that are 55 or older.

### 2021-05-21 scripts/summaries.R

@@ -8,6 +8,10 @@ data %>% group_by( Gender, WhatsApp ) %>% summarise ( n = n() ) %>% mutate( freq
 data %>% group_by( Experience, WhatsApp ) %>% summarise ( n = n() ) %>% mutate( freqWhatsApp = n/sum(n)) -> freq.Experience.WhatsApp
 data %>% group_by( Sector, WhatsApp ) %>% summarise ( n = n() ) %>% mutate( freqWhatsApp = n/sum(n)) -> freq.Sector.WhatsApp
 
+data %>% group_by( Gender, Telegram ) %>% summarise ( n = n() ) %>% mutate( freqTelegram = n/sum(n)) -> freq.Gender.Telegram
+data %>% group_by( Experience, Telegram ) %>% summarise ( n = n() ) %>% mutate( freqTelegram = n/sum(n)) -> freq.Experience.Telegram
+data %>% group_by( Sector, Telegram ) %>% summarise ( n = n() ) %>% mutate( freqTelegram = n/sum(n)) -> freq.Sector.Telegram
+
 data %>% group_by( Gender, Provided ) %>% summarise ( n = n() ) %>% mutate( freqWhatsApp = n/sum(n)) -> freq.Gender.Platform
 data %>% group_by( Experience, Provided ) %>% summarise ( n = n() ) %>% mutate( freqWhatsApp = n/sum(n)) -> freq.Experience.Platform
 data %>% group_by( Sector, Provided ) %>% summarise ( n = n() ) %>% mutate( freqWhatsApp = n/sum(n)) -> freq.Sector.Platform

### 2021-05-21 edubots_surveys.Rnw
Describes the population sample

@@
 % Describe the survey and population
-We collected responses from a total of XXX teachers from University and Vocational Education from Spain ...
+We collected responses from a 282 teachers from Spain and Spanish Speaking countries.
+The sample includes teachers from university (68\%) and vocational Education (32\%).
+Regarding gender, 63\% are male teachers and 35\% female (approximately 2\% chose not to disclose it).
+Finally, the responses are equally distributed attending to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 27\% for 6-15 years of experience, 30\% for 16-25, and 19\% for teachers with more than 25 years of experience.
 

### 2021-05-22 scripts/process.R
Adds chata for chatbot types refs #15

@@ -68,3 +68,22 @@ data %>%  mutate(Messaging.Organization =str_split(Messaging.Organization, ", ")
 data.MessagingOrganization <- within(data.MessagingOrganization, Messaging.Organization <- factor(Messaging.Organization, levels=names(sort(table(Messaging.Organization), decreasing=TRUE))))
 ggplot(data.MessagingOrganization, aes( x = Messaging.Organization, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90))+coord_flip()+ theme(axis.title.y=element_blank())
 ggsave('../figures/messaging_organization.pdf', width = 190, height = 50, units = "mm")
+
+
+data %>%  mutate(ChatbotType = ifelse(Agenda == "No","","Agenda,")) %>%
+  mutate(ChatbotType = ifelse(ClassMaterial == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "ClassMaterial,",sep=""))) %>%
+  mutate(ChatbotType = ifelse(FAQ == "No",paste(ChatbotType, "",sep=""), paste(ChatbotType, "FAQ,",sep=""))) %>%
+  mutate(ChatbotType = ifelse(Grades == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "Grades,",sep=""))) %>%
+  mutate(ChatbotType = ifelse(OtherBot == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "OtherBot,",sep=""))) %>%
+  mutate(ChatbotType = substr(ChatbotType,1,nchar(ChatbotType)-1))-> df1
+
+df1 %>%  mutate(ChatbotType =str_split(ChatbotType, ",")) %>% unnest(cols = c(ChatbotType)) -> data.ChatbotType
+data.ChatbotType <- within(data.ChatbotType, ChatbotType <- factor(ChatbotType, levels=names(sort(table(ChatbotType), decreasing=TRUE))))
+ggplot(data.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+ggsave('../figures/sector_chatbottype.pdf', width = 190, height = 50, units = "mm")
[…]

### 2021-05-22 edubots_surveys.Rnw
Make it compile again
Adds small text and figures for RQ2 refs #15

@@
 
-\def\includegraphic{}
-\def\includegraphics{}
+%\def\includegraphic{}
+%\def\includegraphics{}
 
@@
 ]{\inits{F.}\fnm{Francisco} \snm{Barranco}}
+\author[
+  addressref={aff3},
+  email={n.h.abbas@leeds.ac.uk}
+]{\inits{N.}\fnm{Noorhan} \snm{Abbas}}
 
@@
 
+\address[id=aff3]{%
+  \orgdiv{School of Computing},
+  \orgname{University of Leeds},          % university, etc
+  \city{Leeds},                              % city
+  \cny{UK}                                    % country
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \item{ RQ1 - Are teachers already using messaging apps in their classes? }
-\item{ RQ2 - Which kind of chatbots are they interested in? }
+\item{ RQ2 -  Which kind of chatbots would teachers find useful in their classes?? }
+
 \item{ RQ3 - Regarding technology acceptance, are there any differences regarding age, gender, or years of experience in Education? }
@@
 
+\subsection{RQ2 - Which kind of chatbots would teachers find useful in their classes?}
+
+\begin{figure}[t]
+\begin{center}
+    \begin{minipage}[t]{0.47\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/gender_chatbottype.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.47\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/sector_chatbottype.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.47\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/experience_chatbottype.pdf}
+    \end{minipage}
+\end{center}
+    \caption{Types of chatbots.}
+\label{figure:chatbots_types}
+\end{figure}
+
 \section{Conclusions}

### 2021-05-23 edubots_surveys.Rnw
Incorporates @pacastillo suggestion, refs #4
Next version of abtract, refs #5

@@
 
-\title{Chatbots in the classroom: an analysis from the teacher's perspective}
+\title{Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective}
 
@@
 Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but above all, an examination of the attitudes of the affected community.
-In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think of the introduction of messaging platforms, what their needs are, what kind of use cases they see for them, and in what kind of environment they think its use will be valuable.
+In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think of the introduction of messaging platforms and chatbots, what their needs are, what kind of use cases they see for them, and in what kind of environment they think its use will be valuable.
 We will examine how and when these attitudes vary across gender, experience, and other factors, such as the kind of discipline they are teaching.
+Our conclusions might help with the adoption of messaging platforms, as well as chatbots or other kind of bots, by higher education institution, and how these must be introduced to teachers so that it helps them achieve desired educational outcomes.
 \end{abstract}

### 2021-05-23 edubots_surveys.Rnw
Update SoA and intro

@@
 % TODO: introduction
-Introduction of new technologies in the classroom needs a combination of teacher education, as well as student willingness and skills.
+The introduction of new technologies in the classroom needs a combination of teacher education, student willingness and (possibly new) skills in both.
 Some technologies are readily adapted, some of them take a long time to be adopted.
-In most cases, success or failure of the introduction of a
+In most cases, success or failure of the introduction of a new technology impinges on the colaboration of all the implied parties, which is why evaluating attitudes towards them is an essential first step.
 
-A \textit{chatbot} is a program that allows a computer to communicate in a similar way as a human does \cite{Gong2008}.
+In the framework of the Edubots KA2 European projects, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms.
+A \textit{chatbot} is a program that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language.
 Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker’s question fluently, and even ask other questions to the human.
 
-The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}.
+The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with.
 These automatic systems ease personalized learning, adapting individuals' pace of learning, who get personalized online tutoring outside the classroom.
@@
 
+Chatbots are obviously associated to messaging applications, and in particular, direct messaging applications, since they are the only time of applications that are able to support a synchronous conversation betweeh the two parties.
+This is why in many cases chatbots couple messaging and the chatbot technology itself \cite{differ.chat}, while in others, you can create chatbots in any number of technologies and then attach them to a messaging application using their API.
+
 % Maybe move it to a different place later
-As a starting point, we have analyzed the responses to a survey from XXX teachers asking about their attitudes towards the use of chatbots in their classes.
+As a starting point, we have analyzed the responses to a survey from 300 teachers asking about their attitudes towards the use of chatbots in their classes.
 We are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
 \begin{itemize}
-\item{ RQ1 - Are teachers already using messaging apps in their classes? }
+\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
 \item{ RQ2 -  Which kind of chatbots would teachers find useful in their classes?? }

### 2021-05-23 scripts/process-tutorship.R
Translates interaction survey refs #12

@@ -4,7 +4,19 @@ library(tidyr)
 library(scales)
 library(ggthemes)
 
-data <- read.csv("../data/survey-student-interaction-pilot-3-2021.csv")
+data <- read.csv("../data/survey-student-interaction-pilot-3-2021-EN.csv")
+
+ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + xlab("Type of interaction") + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank())
+ggsave('../figures/gender_interaction.pdf', width = 100, height = 70, units = "mm")
+ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + xlab("Type of interaction") + ylab("relative frequencies") + facet_grid(~Age) + theme(axis.title.y=element_blank())
+ggsave('../figures/age_interaction.pdf', width = 100, height = 70, units = "mm")
+ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + xlab("Type of interaction") + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank())
+ggsave('../figures/experience_interaction.pdf', width = 100, height = 70, units = "mm")
+ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + xlab("Type of interaction") + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering","No"))) + theme(axis.title.y=element_blank())
+ggsave('../figures/discipline_interaction.pdf', width = 186, height = 77, units = "mm")
+
+
+
 
[…]

### 2021-05-23 scripts/translate.py

@@ -33,10 +33,6 @@ data = data.replace("No, no la usaba antes ni ahora.", "No, I didn't use it befo
 
 
 #Messaging.Organization
-#Un grupo con los estudiantes de mi asignatura
-#Prefiero que los estudiantes se autoorganicen y no estar en ningún grupo de mensajería
-#Un grupo para el curso completo (profesores y estudiantes)
-#Un grupo para toda la titulación, Facultad o Escuela (profesores y estudiantes) 
 data = data.replace("Prefiero que los estudiantes se autoorganicen y no estar en ningún grupo de mensajería", "I'd rather leave students self-organize and not be part of the chat")
 data = data.replace("Un grupo con los estudiantes de mi asignatura", "A chat with my students in the same course")
 data = data.replace("Un grupo para el curso completo (profesores y estudiantes)", "A chat with all students and teachers in the same semester/year")
@@ -44,4 +40,40 @@ data = data.replace("Un grupo para toda la titulación o instituto (profesores y
 data = data.replace("Un grupo para toda la titulación, Facultad o Escuela (profesores y estudiantes)", "A chat with all the students and teachers in my Faculty/School")
 
 with open("../data/survey-pilot-3-EN.csv","w") as file:
+     file.write(data)
+
+
+
+
+data = ""
+
+with open("../data/survey-student-interaction-pilot-3-2021.csv") as file:
+     data = file.read()
+
+#Age
+data = data.replace("Más de 55", "> 55")
+
+#Experience 
+data = data.replace("0-5 años", "0-05 years")
+data = data.replace("5-15 años", "06-15 years")
+data = data.replace("15-25 años", "16-25 years")
+data = data.replace("más de 25 años", "> 25 years")
+
+#Gender
+data = data.replace("Hombre", "Male")
+data = data.replace("Mujer", "Female")
+data = data.replace("Prefiero no decirlo", "PNTS")
+
+#Discipline
+data = data.replace("Biosanitaria", "Biomedicine")
+data = data.replace("Ciencias Sociales", "Social Sciences")
+data = data.replace("Ciencias", "Sciences")
+data = data.replace("Humanidades", "Humanities")
+data = data.replace("Tecnología/Ingeniería", "Tech/Engineering")
+
+#Interaction
+data = data.replace("Asíncrona: el estudiante puede preguntar en cualquier momento, el profesorado contesta cuando puede.", "Asynch.")
[…]

### 2021-05-23 edubots_surveys.Rnw
reorganizes text for RQ1 and script for sample population description refs #13

--- 2021-05-22 edubots_surveys.Rnw
@@
 According to the results summarized in Fig.
-\ref{figure:chatbots_use_gender_age_exp}, teachers mainly use the instant messaging app provided by their institutions (55\%),  and Whatsapp (44\%), the most popular messaging app in Spain.
+\ref{figure:chatbots_use}, teachers mainly use the instant messaging app provided by their institutions (55\%),  and Whatsapp (44\%), the most popular messaging app in Spain.
 Finally, about 20\% also use Telegram.
@@
 
-\begin{figure}[t]
+\begin{figure}[!ht]
 \begin{center}
@@
     \end{minipage}
-
-    \vspace{2mm}
+    %----
+    \vspace{0.5mm}
+    \begin{minipage}[t]{0.30\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.50\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/discipline_provided.pdf}
+    \end{minipage}
+    %----
+    %----
+    \vspace{0.5mm}
     \begin{minipage}[t]{0.30\textwidth}
@@
     \end{minipage}
-
-    \vspace{2mm}
+    %----
+    \vspace{0.5mm}
+    \begin{minipage}[t]{0.30\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.50\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
+    \end{minipage}
+    %----
+    %----
+    \vspace{0.5mm}
     \begin{minipage}[t]{0.30\textwidth}
@@
     \end{minipage}
-\end{center}
-    \caption{Use of chatbots in class: distributions per gender and age.
-Teachers were specifically asked about two popular instant messaging apps (Whatsapp and Telegram), and the use of platforms already provided by their institutions different than these two ones.}
-\label{figure:chatbots_use_gender_age_exp}
-\end{figure}
-
-Results in Fig.
-\ref{figure:chatbots_use_sector_discip} do not show differences in the use of instant messaging apps between teachers from University and vocational education.
-In general, most teachers prefer messaging apps provided by their own institutions.
-With respect to specific disciplines, Engineering and Technology teachers are more active in their use, although it is also relevant the amount of teachers from Humanities that answered they used these apps in their classes (around 60\% use the apps provided by their institutions).
-
-\begin{figure}[t]
-\begin{center}
-    \begin{minipage}[t]{0.30\textwidth}
-	    \centering
- 	    \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.50\textwidth}
-	    \centering
- 	    \includegraphics[width=\textwidth]{figures/discipline_provided.pdf}
-    \end{minipage}
-
-    \vspace{2mm}
-    \begin{minipage}[t]{0.30\textwidth}
-	    \centering
- 	    \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.50\textwidth}
-	    \centering
- 	    \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
-    \end{minipage}
-
-    \vspace{2mm}
+    %----
+    \vspace{0.5mm}
     \begin{minipage}[t]{0.30\textwidth}
@@
 \end{center}
-    \caption{Differences in the use of chatbots in class between vocational and university teaching and distributions by discipline.}
-\label{figure:chatbots_use_sector_discip}
+    \caption{Use of chatbots in class: distributions per gender, age, years of experience in education, university or vocational education, and discipline.
+Teachers were specifically asked about two popular instant messaging apps (Whatsapp and Telegram), and the use of platforms already provided by their institutions different than these two ones.}
+\label{figure:chatbots_use}
 \end{figure}
+
+Results in Fig.
+\ref{figure:chatbots_use} do not show differences in the use of instant messaging apps between teachers from University and vocational education.
+In general, most teachers prefer messaging apps provided by their own institutions.
+With respect to specific disciplines, Engineering and Technology teachers are more active in their use, although it is also relevant the amount of teachers from Humanities that answered they used these apps in their classes (around 60\% use the apps provided by their institutions).
+
+%\begin{figure}[t]
+%\begin{center}
+%    \vspace{2mm}
+%    \begin{minipage}[t]{0.30\textwidth}
+%	    \centering
+% 	    \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
+%    \end{minipage}
+%    \begin{minipage}[t]{0.50\textwidth}
+%	    \centering
+% 	    \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
+%    \end{minipage}
+%    
+%    \vspace{2mm}
+%    \begin{minipage}[t]{0.30\textwidth}
+%	    \centering
+% 	    \includegraphics[width=\textwidth]{figures/sector_telegram.pdf}
+%    \end{minipage}
+%    \begin{minipage}[t]{0.50\textwidth}
+%	    \centering
+% 	    \includegraphics[width=\textwidth]{figures/discipline_telegram.pdf}
+%    \end{minipage}
+%\end{center}
+%    \caption{Differences in the use of chatbots in class between vocational and university teaching and distributions by discipline.}
+%\label{figure:chatbots_use_sector_discip}
+%\end{figure}
 
@@
 \includegraphics[width=\textwidth]{figures/messaging_organization.pdf}
-\caption{XXX}
+\caption{Distribution of teachers' preferences for the chat groups with their students: from groups only with their students from a specific course to groups with greater social interaction with all students in their School or Faculty.}
 \label{figure:chatbots_messagingorganization}
@@
 \begin{center}
-    \begin{minipage}[t]{0.47\textwidth}
+    \begin{minipage}[t]{0.75\textwidth}
 	    \centering
@@
     \end{minipage}
-    \begin{minipage}[t]{0.47\textwidth}
+    \begin{minipage}[t]{0.75\textwidth}
 	    \centering

### 2021-05-23 scripts/summaries.R

@@ -2,7 +2,26 @@ library(psych)
 library(dplyr)
 library(tidyr)
 
-data <- read.csv("../data/survey-pilot-3.csv")
+data <- read.csv("../data/survey-pilot-3-EN.csv")
+
+data %>% group_by( Gender ) %>% summarise ( n = n() ) %>% mutate( freqGender = n/sum(n)) -> freq.Gender
+data %>% group_by( Age ) %>% summarise ( n = n() ) %>% mutate( freqAge = n/sum(n)) -> freq.Age
+data %>% group_by( Experience ) %>% summarise ( n = n() ) %>% mutate( freqExperience = n/sum(n)) -> freq.Experience
+data %>% group_by( Sector ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freq.Sector
+data %>% group_by( Discipline ) %>% summarise ( n = n() ) %>% mutate( freqDiscipline = n/sum(n)) -> freq.Discipline
+
+#aes(y = ..prop.., fill = factor(..x..)),
+ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+ggsave('../figures/gender.pdf', width = 80, height = 55, units = "mm")
+ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+ggsave('../figures/Age.pdf', width = 80, height = 55, units = "mm")
+ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+ggsave('../figures/Experience.pdf', width = 80, height = 55, units = "mm")
[…]

### 2021-05-23 scripts/summaries.R
adds script for population description and some text refs #13

@@ -1,6 +1,7 @@
 library(psych)
 library(dplyr)
 library(tidyr)
+library(ggplot2)
 
 data <- read.csv("../data/survey-pilot-3-EN.csv")
 
@@ -14,13 +15,13 @@ data %>% group_by( Discipline ) %>% summarise ( n = n() ) %>% mutate( freqDiscip
 ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
 ggsave('../figures/gender.pdf', width = 80, height = 55, units = "mm")
 ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-ggsave('../figures/Age.pdf', width = 80, height = 55, units = "mm")
+ggsave('../figures/age.pdf', width = 80, height = 55, units = "mm")
 ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-ggsave('../figures/Experience.pdf', width = 80, height = 55, units = "mm")
+ggsave('../figures/experience.pdf', width = 80, height = 55, units = "mm")
 ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-ggsave('../figures/Sector.pdf', width = 80, height = 55, units = "mm")
+ggsave('../figures/sector.pdf', width = 80, height = 55, units = "mm")
[…]

### 2021-05-24 edubots_surveys.Rnw
adds script for population description and some text refs #13
Revising the Introduction

@@
 Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but above all, an examination of the attitudes of the affected community.
-In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think of the introduction of messaging platforms and chatbots, what their needs are, what kind of use cases they see for them, and in what kind of environment they think its use will be valuable.
+% Antonio - En realidad, la comunidad afectada incluiría también a los estudiates, ¿no?
+% Por cierto, quizá también se podrían incluir aqui las encuestas pasadas a los estudiantes. No son las mismas preguntas, pero van en una línea similar. Quizá tuviesen cabida y le darían 
+% más enjundia al estudio. ;)
+In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think about the introduction of messaging platforms and chatbots, what their needs are, what kind of use cases they see for them, and in what kind of environment they think its use will be valuable.
 We will examine how and when these attitudes vary across gender, experience, and other factors, such as the kind of discipline they are teaching.
@@
 The introduction of new technologies in the classroom needs a combination of teacher education, student willingness and (possibly new) skills in both.
-Some technologies are readily adapted, some of them take a long time to be adopted.
-In most cases, success or failure of the introduction of a new technology impinges on the colaboration of all the implied parties, which is why evaluating attitudes towards them is an essential first step.
+Some technologies are readily adapted, but some of them take a long time to be adopted.
+In most cases, the success or failure of the introduction of a new technology impinges on the colaboration of all the implied parties, which is why evaluating attitudes towards them is an essential first step.
 
-In the framework of the Edubots KA2 European projects, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms.
-A \textit{chatbot} is a program that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language.
+In the framework of the Edubots KA2 European project, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms.
+A \textit{chatbot} is a program, based on Artificial Intelligence techniques, that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language.
 Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker’s question fluently, and even ask other questions to the human.
@@
 The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with.
-These automatic systems ease personalized learning, adapting individuals' pace of learning, who get personalized online tutoring outside the classroom.
+These automatic systems ease personalized learning,
+% customized en lugar de personalized? Por no repetir personalized dos veces en la misma frase
+adapting individuals' pace of learning, who get personalized online tutoring outside the classroom.
 Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.
@@
 Chatbot technology has a potential to fill the gap between teacher and students, helping them to solve questions and carry out a dynamic and autonomous learning \cite{Griol2014,kim2020}.
-Moreover, using an automated system such as a chatbot allows the teacher to detect those topics that are most in demand, and on which he or she should consequently place more emphasis in class.
+Moreover, using an automated system such as a chatbot allows the teacher to detect the most demanded topics, and on which he or she should consequently place more emphasis in class.
 
-Chatbots are obviously associated to messaging applications, and in particular, direct messaging applications, since they are the only time of applications that are able to support a synchronous conversation betweeh the two parties.
-This is why in many cases chatbots couple messaging and the chatbot technology itself \cite{differ.chat}, while in others, you can create chatbots in any number of technologies and then attach them to a messaging application using their API.
+Chatbots are obviously associated to messaging applications, and in particular, direct messaging applications, since they are the only type of applications that are able to support a synchronous conversation between the two parties.
+This is why in many cases chatbots couple messaging and the chatbot technology itself \cite{differ.chat}, while in others, you can create chatbots in any number of technologies and then attach them to a messaging application using their API (Application Program Interface).
 
 % Maybe move it to a different place later
-As a starting point, we have analyzed the responses to a survey from 300 teachers asking about their attitudes towards the use of chatbots in their classes.
-We are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
+Given the potential advantages that chatbots could bring to the classroom, as a previous step, we have performed a survey to 300 teachers asking about their attitudes towards the use of chatbots in their classes.
+We analyse in this work their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
 \begin{itemize}
@@
 \end{itemize}
+
+% ********************** STATE OF THE ART ****************************
 
@@
 
+% ********************** RESULTS ****************************
+
 \section{Results}
@@
 Finally, the responses are equally distributed attending to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 27\% for 6-15 years of experience, 30\% for 16-25, and 19\% for teachers with more than 25 years of experience.
+
+\begin{figure}[t]
+\begin{center}
+    \begin{minipage}[t]{0.3\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/gender.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.3\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/age.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.3\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/sector.pdf}
+    \end{minipage}
+
+    \vspace{0.5mm}
+    \begin{minipage}[t]{0.3\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/experience.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.55\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/discipline.pdf}
+    \end{minipage}
+\end{center}
+    \caption{Sample population description. A total 282 teachers shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
+\label{figure:teachers_population}
+\end{figure}
 
@@
 
+% ********************** CONCLUSIONS ****************************
+
 \section{Conclusions}

### 2021-05-24 scripts/process-tutorship.R
adds the question and section/results for RQ3 refs #16

@@ -6,17 +6,20 @@ library(ggthemes)
 
 data <- read.csv("../data/survey-student-interaction-pilot-3-2021-EN.csv")
 
-ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + xlab("Type of interaction") + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank())
-ggsave('../figures/gender_interaction.pdf', width = 100, height = 70, units = "mm")
-ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + xlab("Type of interaction") + ylab("relative frequencies") + facet_grid(~Age) + theme(axis.title.y=element_blank())
-ggsave('../figures/age_interaction.pdf', width = 100, height = 70, units = "mm")
-ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + xlab("Type of interaction") + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank())
-ggsave('../figures/experience_interaction.pdf', width = 100, height = 70, units = "mm")
-ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + xlab("Type of interaction") + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering","No"))) + theme(axis.title.y=element_blank())
-ggsave('../figures/discipline_interaction.pdf', width = 186, height = 77, units = "mm")
[…]

### 2021-05-24 edubots_surveys.Rnw
adds the question and section/results for RQ3 refs #16
Eliminates sweave
Adds as code #16 :zap:
Also corresponding to #3

@@
 % más enjundia al estudio. ;)
+% They are not part of this paper, Antonio. Also: write in English - JJ
 In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think about the introduction of messaging platforms and chatbots, what their needs are, what kind of use cases they see for them, and in what kind of environment they think its use will be valuable.
@@
 
+<<setup, echo=FALSE>>=
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+library(scales)
+library(ggthemes)
+
+data <- read.csv("data/survey-student-interaction-pilot-3-2021-EN.csv")
+@
+
 \section{Introduction}
@@
 \item{ RQ2 - Which kind of chatbots would teachers find useful in their classes?? }
+\item{ RQ3 - Which kind of interaction do teachers prefer with their students? }
 
-\item{ RQ3 - Regarding technology acceptance, are there any differences regarding age, gender, or years of experience in Education? }
-\item{ RQ4 - } 
 \end{itemize}
@@
 
+\subsection{RQ2 - Which kind of interaction do teachers prefer with their students?}
+
+\begin{figure}[t]
+\begin{center}
+    \begin{minipage}[t]{0.33\textwidth}
+	    \centering
+<<gender_synch, echo=FALSE>>=
+ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+@
+
+% 	    \includegraphics[width=\textwidth]{figures/gender_synch.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.33\textwidth}
+	    \centering
+<<age_synch, echo=FALSE>>=
+ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+@
+% 	    \includegraphics[width=\textwidth]{figures/age_synch.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.35\textwidth}
+	    \centering
+<<experience_sync, echo=FALSE>>=
+ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+@
+
+% 	    \includegraphics[width=\textwidth]{figures/experience_synch.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.6\textwidth}
+	    \centering
+<<discipline_synch, echo=FALSE>>=
+ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering","No"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+@
+
+% 	    \includegraphics[width=\textwidth]{figures/discipline_synch.pdf}
+    \end{minipage}
+\end{center}
+    \caption{Synchronous or asynchronous interaction.}
+\label{figure:chatbots_synch}
+\end{figure}
+
 % ********************** CONCLUSIONS ****************************
@@
 
-\section*{Acknowledgements}
+%This section is repeated
+%\section*{Acknowledgements}
 

### 2021-05-24 edubots_surveys.Rnw
Moves to code figure 1

@@
 
+survey.pilot <- read.csv("data/survey-pilot-3-EN.csv")
+survey.pilot %>% group_by( Gender ) %>% summarise ( n = n() ) %>% mutate( freqGender = n/sum(n)) -> freq.Gender
+survey.pilot %>% group_by( Age ) %>% summarise ( n = n() ) %>% mutate( freqAge = n/sum(n)) -> freq.Age
+survey.pilot %>% group_by( Experience ) %>% summarise ( n = n() ) %>% mutate( freqExperience = n/sum(n)) -> freq.Experience
+survey.pilot %>% group_by( Sector ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freq.Sector
+survey.pilot %>% group_by( Discipline ) %>% summarise ( n = n() ) %>% mutate( freqDiscipline = n/sum(n)) -> freq.Discipline
+
 data <- read.csv("data/survey-student-interaction-pilot-3-2021-EN.csv")
@@
 Some technologies are readily adapted, but some of them take a long time to be adopted.
-In most cases, the success or failure of the introduction of a new technology impinges on the colaboration of all the implied parties, which is why evaluating attitudes towards them is an essential first step.
+In most cases, the success or failure of the introduction of a new technology impinges on the collaboration of all the implied parties, which is why evaluating attitudes towards them is an essential first step.
 
-In the framework of the Edubots KA2 European project, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms.
+In the framework of the EduBots KA2 European project, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms.
 A \textit{chatbot} is a program, based on Artificial Intelligence techniques, that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language.
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/gender.pdf}
+<<gender, echo=FALSE>>=
+ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+@
+
+% 	    \includegraphics[width=\textwidth]{figures/gender.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/age.pdf}
+<<age,echo=FALSE>>=
+ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+@
+
+% 	    \includegraphics[width=\textwidth]{figures/age.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/sector.pdf}
+<<sector, echo=FALSE>>=
+ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+@
+
+% 	    \includegraphics[width=\textwidth]{figures/sector.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/experience.pdf}
+<<experience,echo=FALSE>>=
+ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+@
+
+% 	    \includegraphics[width=\textwidth]{figures/experience.pdf}
     \end{minipage}
@@
 	    \centering
- 	    \includegraphics[width=\textwidth]{figures/discipline.pdf}
+<<discipline,echo=FALSE>>=
+ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+@
+
+% 	    \includegraphics[width=\textwidth]{figures/discipline.pdf}
     \end{minipage}

### 2021-05-24 scripts/summaries.R
Process age and experience, #17

@@ -2,14 +2,24 @@ library(psych)
 library(dplyr)
 library(tidyr)
 library(ggplot2)
+library(forcats)
 
 data <- read.csv("../data/survey-pilot-3-EN.csv")
+
+ggplot(data,aes(Age,Experience))+geom_point(aes(size=value),colour="green")
 
 data %>% group_by( Gender ) %>% summarise ( n = n() ) %>% mutate( freqGender = n/sum(n)) -> freq.Gender
 data %>% group_by( Age ) %>% summarise ( n = n() ) %>% mutate( freqAge = n/sum(n)) -> freq.Age
 data %>% group_by( Experience ) %>% summarise ( n = n() ) %>% mutate( freqExperience = n/sum(n)) -> freq.Experience
 data %>% group_by( Sector ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freq.Sector
 data %>% group_by( Discipline ) %>% summarise ( n = n() ) %>% mutate( freqDiscipline = n/sum(n)) -> freq.Discipline
+
+data %>%
+    mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
+    mutate(Experience = fct_relevel(Experience, "0-05 years", "06-15 years", "16-25 years", "> 25 years" )) %>%
+    group_by( Age, Experience ) %>% summarise( n = n() ) %>% mutate( freq = n/sum(n)) -> Age.vs.Experience
+
+ggplot(Age.vs.Experience,aes(Age,Experience))+geom_point(aes(size=freq),colour="green")
 
 #aes(y = ..prop.., fill = factor(..x..)),
 ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())

### 2021-05-24 edubots_surveys.Rnw
Adds interaction figure and rationale refs #17

@@
 
-\begin{figure}[t]
+\begin{figure}[h!tbp]
 \begin{center}
@@
 \end{figure}
+%
+\begin{figure}[h!tbp]
+\begin{center}
+<<interaction,message=FALSE,echo=FALSE>>=
+library(forcats)
+data %>%
+    mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
+    mutate(Experience = fct_relevel(Experience, "0-05 years", "06-15 years", "16-25 years", "> 25 years" )) %>%
+    group_by( Age, Experience ) %>% summarise( n = n() ) %>% mutate( freq = n/sum(n)) -> Age.vs.Experience
+
+ggplot(Age.vs.Experience,aes(Age,Experience))+geom_point(aes(size=freq),colour="green")
+@
+\end{center}
+\caption{Correlation between age and experience.}
+\label{figure:age.vs.exp}
+\end{figure}
+
+Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar, and as a matter of fact, as Figure \ref{figure:age.vs.exp} age and experience are correlated strongly, with experience being roughly 20-30 years less than age.
+This might indicate that a differential analysis for age and experience will not yield significant differences, except maybe in the 6-15 years experience group, which is spread over all ages.
+At any rate, experience seems to be the dominating factor here and we'll use experience only unless we detect some significant difference by age.
 

### 2021-05-24 edubots_surveys.Rnw
Supress messages
Completing Introduction with preliminary work

@@
 \begin{abstract} % abstract
-Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but above all, an examination of the attitudes of the affected community.
-% Antonio - En realidad, la comunidad afectada incluiría también a los estudiates, ¿no?
-% Por cierto, quizá también se podrían incluir aqui las encuestas pasadas a los estudiantes. No son las mismas preguntas, pero van en una línea similar. Quizá tuviesen cabida y le darían 
-% más enjundia al estudio. ;)
-% They are not part of this paper, Antonio. Also: write in English - JJ
+Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but above all, an examination of the attitudes of the affected teaching community.
 In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think about the introduction of messaging platforms and chatbots, what their needs are, what kind of use cases they see for them, and in what kind of environment they think its use will be valuable.
@@
 
-<<setup, echo=FALSE>>=
+<<setup, echo=FALSE,message=FALSE>>=
 library(ggplot2)
@@
 These automatic systems ease personalized learning,
-% customized en lugar de personalized? Por no repetir personalized dos veces en la misma frase
+% Antonio - customized instead personalized? we are repeating 'personalized' twice in a sentence...
 adapting individuals' pace of learning, who get personalized online tutoring outside the classroom.
@@
 
+Given the potential advantages that chatbots could bring to the classroom, as a previous step, we created two surveys for bachelor and master degree students at the University of Granada (Spain), which were answered by more than 250 pupils.
+The obtained results were analysed in \cite{MoraChatbos2021} aiming to identify students' actual needs.
+The survey asked about their preferences on tools/applications for chatting and messaging, how do they use them in the educational context, who do they like to be in the class messaging groups, and what do they expect bots and chatbots to do to aid them for learning.
+The conclusions show that students prefer to use known messaging applications, such as Telegram or WhatsApp, mainly to communicate in groups including both classmates and teachers, and they expect chatbots to ease their subject organisation, such as calendar bots, as well as bots to provide grades and subject material.
+
 % Maybe move it to a different place later
-Given the potential advantages that chatbots could bring to the classroom, as a previous step, we have performed a survey to 300 teachers asking about their attitudes towards the use of chatbots in their classes.
-We analyse in this work their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
+In the present work we aim to complement this study with the other main community of the educational process, i.e.
+teachers.
+Thus, we have performed a survey among 300 teachers asking about their attitudes towards the use of bots or chatbots in their classes.
+We analyse their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
 \begin{itemize}

### 2021-05-25 edubots_surveys.Rnw
Incorporating into the paper the previous one

@@
 In the framework of the EduBots KA2 European project, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms.
-A \textit{chatbot} is a program, based on Artificial Intelligence techniques, that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language.
+A \textit{chatbot} is a program, sometimes based on Artificial Intelligence techniques, that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language.
 Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker’s question fluently, and even ask other questions to the human.
+However, in most cases a simple messaging-application attached bot will help the students (and teachers); neither computational intelligence nor comprehension of natural languages are requisites, the only one being the fact that they can be accessed from a synchronous conversational application such as the common instant messaging applications used nowadays.
 
@@
 % Antonio - customized instead personalized? we are repeating 'personalized' twice in a sentence...
+% Antonio, if you don't like something, and it's as non-controversial as this thing, just change it directly. Reviews are OK, corrections are even more OK. - JJ
 adapting individuals' pace of learning, who get personalized online tutoring outside the classroom.
@@
 
-Given the potential advantages that chatbots could bring to the classroom, as a previous step, we created two surveys for bachelor and master degree students at the University of Granada (Spain), which were answered by more than 250 pupils.
-The obtained results were analysed in \cite{MoraChatbos2021} aiming to identify students' actual needs.
-The survey asked about their preferences on tools/applications for chatting and messaging, how do they use them in the educational context, who do they like to be in the class messaging groups, and what do they expect bots and chatbots to do to aid them for learning.
-The conclusions show that students prefer to use known messaging applications, such as Telegram or WhatsApp, mainly to communicate in groups including both classmates and teachers, and they expect chatbots to ease their subject organisation, such as calendar bots, as well as bots to provide grades and subject material.
+Given the potential advantages that chatbots could bring to the classroom, as a previous step, we created two surveys for bachelor and master degree students at the University of Granada (Spain), which were answered by more than 250 students.
+The obtained results were analysed with the object of identifying students' actual needs, in \cite{MoraChatbos2021}.
+The survey asked about their preferences on tools/applications for chatting and messaging, how do they use them in the educational context, who do they like to be with in the class messaging groups, and what do they expect bots and chatbots to do to aid them during their learning process.
+We concluded that students prefer to use known whatever messaging application, such as Telegram or WhatsApp, they are already using.
+They also they expected chatbots to help them with their scheduling, provide assignment grades and search class material.
+Only one of the applications mentioned, having them work with frequently asked questions, might actually require some understanding of natural language, although it can be formulated in such a way that is not needed.
 
 % Maybe move it to a different place later
-In the present work we aim to complement this study with the other main community of the educational process, i.e.
-teachers.
+In the present work we aim to complement this study with teachers, who are the ones that actually would need to implement, configure and maybe program chatbots.
 Thus, we have performed a survey among 300 teachers asking about their attitudes towards the use of bots or chatbots in their classes.

### 2021-05-25 edubots_surveys.Rnw
Add methodology section explaining how surveys were made refs #20

@@
 % Maybe move it to a different place later
-In the present work we aim to complement this study with teachers, who are the ones that actually would need to implement, configure and maybe program chatbots.
+In the present work we aim to complement the aforementioned study with teacher attitudes; teachers are the ones that actually would need to implement, configure and maybe program chatbots.
 Thus, we have performed a survey among 300 teachers asking about their attitudes towards the use of bots or chatbots in their classes.
@@
 However, Higher Education is a special domain where according to \cite{hobert2019you}, specific pedagogical factors such as learning success or increased motivation are more important.
+
+\section{Methodology}
+
+Our intention from the beginning was to try and gather a sufficient amount of responses in all sectors, as well as cover different sectors of higher education.
+This is why we created a Google Form, in Spanish, which was intended to be answered in a very short amount of time.
+Initially, our intention was to mirror the questions used in \cite{MoraChatbos2021}; however, an initial exploration of results led us to create a second survey.
+% Questions should probably be included here.
+
+The initial survey was done in two different forms, one for university and other for tertiary non-university teachers.
+Questions and responses were the same, except for the type of tertiary degrees that were taught.
+We got around 300 responses to this one, with two thirds of them coming from university teachers, the rest from high school teachers.
+In both cases, we used mainly mailing lists, as well as Telegram groups, to spread the link to the form.
+The university form was spread in Spanish (mainly Andalucía and Galicia) universities, as well as Costa Rica and Mexico.
+The tertiary non-university teachers are mainly in Andalucía.
+Dissemination and answers took place in the first quarter of 2021, post-pandemic and while, at least in Spain, many universities had mandatory virtual teaching.
+
+The second survey followed the same paths, only in this case there was a single questionnaire.
+It was filled by teachers that were also students in a teacher formation course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers to knew about it by emails from the authors, as well as from the vicedeanship for International Relations that included it in its newsletter.
+This means that there might be a higher proportion of 1) teachers with few years of experience 2) teachers from the computer science faculty and 3) teachers from Granada.
+We think, however that there's no explicit bias in this selection, although of course specific percentages will vary.
 

### 2021-05-27 edubots_surveys.Rnw
Hook for folloup
Adds intro

@@
 
+The rest of the paper is organized as follows.
+Next is an overview of what current research has found about the use of messaging applications, including chatbots, in the classroom.
+The methodology used in the survey is presented in Section \ref{sec:meth}, and the results of the survey are presented next in Section \ref{sec:res}.
+Finally, we discuss these results and conclude with a series of recommendations in the section that closes the paper.
+
 % ********************** STATE OF THE ART ****************************
@@
 \section{State of the art}
+\label{sec:soa}
 
@@
 \section{Methodology}
+\label{sec:meth}
 
@@
 \section{Results}
+\label{sec:res}
 

### 2021-05-28 edubots_surveys.Rnw
Update State of the Art #6

@@
 
-It is essential, when implementing a educational chatbot strategy, to asses the needs of the community prior to implementation \cite{tsivitanidouusers}.
+The Use of Mobile Instant Messaging (MIM) Platforms in Higher Education
+The widespread and rapid adoption of free MIM tools/platforms such as WhatsApp, Telegram, WeChat and Facebook Messenger stems from their simplicity, ease of use and multi-modality (i.e.
+video, audio, text) (Tang and Hew, 2017).
+Using these tools in higher education can facilitate the delivery of personalised learning that occurs anytime anywhere, promote collaborative learning experiences and group discussions (Panah and Baber, 2020).
+WhatsApp is the most popular MIM platform used by educators to give assignments’ feedback to students, support course discussions and provide learning resources in informal learning settings (Panah and Baber, 2020).
+The use of WhatsApp in higher education could enhance social presence (Tang and Hew, 2017) and foster trust relationships between educators and students embedded in the social learning process (Gachago, Strydom, Hanekom, Simons and Walters, 2015).
 
-% TODO: state of the art
+Nevertheless, there are challenges when using MIM tools that occur due to the blurring of boundaries between academic and private life.
+This can lead to technostress (Gachago et al., 2015), difficulty in managing responsibilities especially among mature students and lack of privacy (Tang and Hew, 2017).
+Students’ dropout of the MIM groups, as they can leave groups at any time can hinder their learning and undermine educators’ efforts (Mwakapina, Mhandeni, and Nyinondi, 2016).
+In addition, there is a need to set rules and norms for these MIM groups in order to maintain the safety of these online communities for students (Abbas et al., 2021b) without affecting students’ ownership and control that is vital to advance their learning (Gachago et al., 2015).
 
-% student/teacher preferences towards messaging and chatbots (#6)
+The Use of Chatbots in Higher Education
+The use of conversational agents or chatbots in higher education is still at its infancy (Yang and Evans, 2019).
+Nevertheless, recent studies examining their positive impact on students’ academic performance (Pérez, Daradoumis and Puig, 2020) and engagement (Studente, Ellis and Garivaldis, 2020; Abbas et al., 2021b) have led to a growing interest in using this technology in classes.
+Indeed, the use of chatbots in collecting course feedback from students in higher education improved students’ response quality and boosted their enjoyment levels (Abbas, Pickard, Atwell and Walker, 2021a).
+According to Roblyer et al.
+(2010), using either tools such as mobile devices or teaching strategies based on gamification (Yildirim, 2017) can improve student motivation.
+In this sense, Pimmer et al.
+(2019) carried out a series of experiments with technological tools whose results showed positive perception and acceptance of the use of technology in teaching and learning.
 
-Conversational programs to facilitate communication between computers and humans using natural language have existed for many years \cite{Thompson2007,SHAH2016}. 
-However, those were very limited systems in terms of the capacity of the models used at the time \cite{Hutchens1996}.
+Several higher education chatbots’ evaluation studies were undertaken.
+For instance, an evaluation review study presented by Smutny and Schreiberova (2020) examined 47 educational chatbots implemented in Facebook Messenger with the focus to identify characteristics and quality metric such as language, subject matter and platform.
+Another study aimed to categorise educational chatbots according to their purpose into service-oriented and teaching-oriented (Pérez, Daradoumis and Puig, 2020).
+The first category includes those that provide service support such as the chatbot Ask Holly (University of Durham, 2021) and Dina (Santoso et al., 2018), both chatbots respond to students’ questions about enrolment and registration.
+Ask L.U.
+(Lancaster University, 2019) answers students’ frequently asked questions about timetables, grades, tutors and societies.
+LISA (Dibitonto et al., 2018) and Differ (Differ, 2021) facilitate breaking the ice between new students by introducing them to each other.
+Ranoliya et al.
+(2017) proposed a generic chatbot for university students that is able to answer their frequently asked questions.
 
-In recent years, several authors have carried out studies on the convenience of integrating chatbots in teaching, evaluating their characteristics. 
-Thus, Coniam \cite{Coniam2014} evaluates several systems, concluding that they are still in an early stage to be used with guarantees.
-Likewise, Tallyn et al.
-\cite{Tallyn2018} evaluates a system related to a very specific topic that is suitable for answering specific questions using a chat.
-Finally, Smutny et al.
-\cite{Smutny2020} present a review study examining the educational chatbots in Facebook Messenger with focus to identify characteristics such as language, subject matter and platform.
-
-According to \cite{Roblyer2010}, using either tools such as mobile devices or teaching strategies based on gamification \cite{Yildirim2017} can improve student motivation.
-In this sense, Pimmer et al.
-\cite{Pimmer2019} carried out a series of experiments with technological tools whose results showed positive perception and acceptance of the use of technology in teaching and learning, since students are used to using those media with which they can express themselves freely.
-
-% Categorization and examples of what they can do, adapted to questions in the survey   
-A possible categorization of chatbots in Education splits them according to their purpose into service- and teaching-oriented \cite{perez2020rediscovering}.
-The first class includes chatbots that provide service support used e.g.
-to solve questions about the enrollment \cite{santoso2018dinus}, registration, or academic requirements for exchange students \cite{ranoliya2017chatbot}.
-Focusing on the use at class, service-oriented chatbots would help to introduce students to each other (as done with LISA \cite{dibitonto2018chatbot}), would provide information about schedules and deadlines, recommend general learning materials for the next classes, or individually inform about grades.
-Teaching-oriented chatbots are more sophisticated chatbots that set goals and monitor learning progress.
-A simple example is described in \cite{coronado2018cognitive} where authors proposed agents that store learning materials to be provided on demand to students.
-Also, more complex tutoring systems \cite{crockett2017predicting} individually analyze the learning state of students to provide the next most suitable material in their learning path.
-
-% Point: chatbots are accepted if they help to achieve learning goals
-Regarding the factors for the adoption of chatbots in Education, many studies have focused on the evaluation of technology acceptance or usability such as \cite{Pimmer2019, Roblyer2010}.
-However, Higher Education is a special domain where according to \cite{hobert2019you}, specific pedagogical factors such as learning success or increased motivation are more important.
+On the other hand, teaching-oriented chatbots are more sophisticated as they set personalised learning outcomes and monitor learning progress.
+For instance, Fernoagă, Stelea, Gavrilă, and Sandu (2018) reported on ‘eduAssistant’ a virtual teaching assistant chatobt developed on the Telegram messaging platform.
+In this study, the Telegram platform was chosen because it is easy to use, students are familiar with its features and it enables students to exchange messages in different formats (text, audio and video) (Fernoagă et al., 2018).
+In addition, Telegram could operate on all devices and operating systems.
+The ‘eduAssistant’ chatbot acts as an automatic agent between the teacher-content-student, facilitating real-time feedback loops and providing a personalised learning experience relevant to students’ skills and knowledge.
+Using this chatbot, educators can create interactive instances in their lectures where they pose questions to their students and the chatbot assists students who need further help by giving those more hints and reporting to their educator’s dashboard (Fernoagă et al., 2018).
+This can help educators locate those students that need their attention and send them more educational resources relevant to their academic attainment.
+Furthermore, Sjöström et al.
+(2018) proposed a conceptual architecture for teaching-oriented chatbots in higher education.
+This conceptual architecture is based on a systematic literature review of previous studies examining the design of chatbots in higher education and a content analysis of student emails and discussion forum posts of four instances of a Java programming course.
+The study outlined several design considerations, among them, the authors emphasised the importance of developing chatbots in platforms that students and educators are familiar with and can easily access (i.e.
+Facebook Messenger) which confirms with Hobert’s (2019) and Fernoagă, Stelea, Gavrilă, and Sandu’s (2018)  studies.
+In addition, Sjöström et al.
+argued that a conceptualision of learners’ questions could aid designers in integrating the appropriate types of questions that the chatbots should support for different courses.
+Coronado et al.
+(2018) proposed agents that store learning materials to be provided on demand to students.
+Crockett et al.
+(2017) reported on tutoring systems, which can perform initial assessments of students’ understanding and provid learning material that would advance their understanding to the next level.
+Regarding the factors for the adoption of chatbots in higher education, many studies have focused on the evaluation of technology acceptance and usability (Roblyer et al., 2010; Pimmer et al., 2019).
+However, higher education is a special domain where according to Hobert (2019), specific pedagogical factors such as learning success or increased motivation are more important.
+Therefore, to develop efficient chatbots for higher education, all stakeholders’ (i.e.
+educators, students, institutions, etc) expectations needs to be carefully collected and taken into consideration (Sjöström et al., 2018; Tsivitanidou and Ioannou, 2020).
 

### 2021-05-30 edubots_surveys.Rnw
Inserting bibtex references
@noorhanabbas, there are a couple of references missing in the .bib
file, mainly yours; also I have requested some references in some cases, mainly
chatbots that were used by some university or other.

--- 2021-05-27 edubots_surveys.Rnw
@@
 
-It is essential, when implementing a educational chatbot strategy, to asses the needs of the community prior to implementation \cite{tsivitanidouusers}.
+% The Use of Mobile Instant Messaging (MIM) Platforms in Higher Education
+The widespread and rapid adoption of free Mobile Instant messaging (MIM) tools/platforms such as WhatsApp, Telegram, WeChat and Facebook Messenger stems from their simplicity, ease of use and multi-modality (i.e.
+video, audio, text) \cite{tang2017mobile}.
+Using these tools in higher education can facilitate the delivery of personalised learning that occurs anytime anywhere, promote collaborative learning experiences and group discussions \cite{panah2020study}.
+WhatsApp is the most popular MIM platform used by educators to give assignments’ feedback to students, support course discussions and provide learning resources in informal learning settings \cite{panah2020study}.
+The use of WhatsApp in higher education could enhance social presence \cite{tang2017mobile} and foster trust relationships between educators and students embedded in the social learning process \cite{gachago2015crossing}.
 
-% TODO: state of the art
+Nevertheless, there are challenges when using MIM tools that occur due to the blurring of boundaries between academic and private life.
+This can lead to technostress \cite{gachago2015crossing}, difficulty in managing responsibilities especially among mature students and lack of privacy \cite{tang2017mobile}.
+Students’ dropout of the MIM groups, as they can leave groups at any time can hinder their learning and undermine educators’ efforts \cite{mwakapina2016whatsapp}.
+In addition, there is a need to set rules and norms for these MIM groups in order to maintain the safety of these online communities for students (Abbas et al., 2021b) % This one is missing from the biblio
+without affecting students’ ownership and control that is vital to advance their learning \cite{gachago2015crossing}.
 
-% student/teacher preferences towards messaging and chatbots (#6)
+% The Use of Chatbots in Higher Education
+The use of conversational agents or chatbots in higher education is still at its infancy cite{yang2019opportunities}.
+Nevertheless, recent studies examining their positive impact on students’ academic performance \cite{perez2020rediscovering} and engagement \cite{differ.chat}(Abbas et al., 2021b) have led to a growing interest in using this technology in classes.
+Indeed, the use of chatbots in collecting course feedback from students in higher education improved students’ response quality and boosted their enjoyment levels (Abbas, Pickard, Atwell and Walker, 2021a).
+According to \cite{Roblyer2010}, using either tools such as mobile devices or teaching strategies based on gamification \cite{Yildirim2017} can improve student motivation.
+In this sense, \cite{Pimmer2019} carried out a series of experiments with technological tools whose results showed positive perception and acceptance of the use of technology in teaching and learning.
 
-Conversational programs to facilitate communication between computers and humans using natural language have existed for many years \cite{Thompson2007,SHAH2016}. 
-However, those were very limited systems in terms of the capacity of the models used at the time \cite{Hutchens1996}.
+Several higher education chatbots’ evaluation studies were undertaken.
+For instance, an evaluation review study presented by \cite{Smutny2020} examined 47 educational chatbots implemented in Facebook Messenger with the focus to identify characteristics and quality metric such as language, subject matter and platform.
+Another study aimed to categorise educational chatbots according to their purpose into service-oriented and teaching-oriented \cite{perez2020rediscovering}.
+The first category includes those that provide service support such as the chatbot Ask Holly (University of Durham, 2021) % We probably need a reference for this - JJ
+and Dina \cite{santoso2018dinus}, both chatbots respond to students’ questions about enrolment and registration. Ask L.U. (Lancaster University, 2019 % Another reference
+) answers students’ frequently asked questions about timetables, grades, tutors and societies.
+LISA \cite{dibitonto2018chatbot} and Differ (Differ, 2021) facilitate breaking the ice between new students by introducing them to each other.
+\cite{ranoliya2017chatbot} proposed a generic chatbot for university students that is able to answer their frequently asked questions.
 
-In recent years, several authors have carried out studies on the convenience of integrating chatbots in teaching, evaluating their characteristics. 
-Thus, Coniam \cite{Coniam2014} evaluates several systems, concluding that they are still in an early stage to be used with guarantees.
-Likewise, Tallyn et al.
-\cite{Tallyn2018} evaluates a system related to a very specific topic that is suitable for answering specific questions using a chat.
-Finally, Smutny et al.
-\cite{Smutny2020} present a review study examining the educational chatbots in Facebook Messenger with focus to identify characteristics such as language, subject matter and platform.
+On the other hand, teaching-oriented chatbots are more sophisticated as they set personalised learning outcomes and monitor learning progress.
+For instance, \cite{fernoagua2018intelligent} reported on ‘eduAssistant’ a virtual teaching assistant chatobt developed on the Telegram messaging platform.
+In this study, the Telegram platform was chosen because it is easy to use, students are familiar with its features and it enables students to exchange messages in different formats (text, audio and video) \cite{fernoagua2018intelligent}.
+In addition, Telegram could operate on all devices and operating systems.
+The ‘eduAssistant’ chatbot acts as an automatic agent between the teacher-content-student, facilitating real-time feedback loops and providing a personalised learning experience relevant to students’ skills and knowledge.
+Using this chatbot, educators can create interactive instances in their lectures where they pose questions to their students and the chatbot assists students who need further help by giving those more hints and reporting to their educator’s dashboard \cite{fernoagua2018intelligent}.
+This can help educators locate those students that need their attention and send them more educational resources relevant to their academic attainment.
 
-According to \cite{Roblyer2010}, using either tools such as mobile devices or teaching strategies based on gamification \cite{Yildirim2017} can improve student motivation.
-In this sense, Pimmer et al.
-\cite{Pimmer2019} carried out a series of experiments with technological tools whose results showed positive perception and acceptance of the use of technology in teaching and learning, since students are used to using those media with which they can express themselves freely.
+Furthermore, \cite{sjostrom2018designing} proposed a conceptual architecture for teaching-oriented chatbots in higher education.
+This conceptual architecture is based on a systematic literature review of previous studies examining the design of chatbots in higher education and a content analysis of student emails and discussion forum posts of four instances of a Java programming course.
+The study outlined several design considerations, among them, the authors emphasised the importance of developing chatbots in platforms that students and educators are familiar with and can easily access (i.e.
+Facebook Messenger) which confirms with \cite{hobert2019you} and \cite{fernoagua2018intelligent} studies.
+In addition, \cite{sjostrom2018designing} argued that a conceptualision of learners’ questions could aid designers in integrating the appropriate types of questions that the chatbots should support for different courses.
+\cite{coronado2018cognitive} proposed agents that store learning materials to be provided on demand to students.
+\cite{crockett2017predicting} reported on tutoring systems, which can perform initial assessments of students’ understanding and provide learning material that would advance their understanding to the next level.
 
-% Categorization and examples of what they can do, adapted to questions in the survey   
-A possible categorization of chatbots in Education splits them according to their purpose into service- and teaching-oriented \cite{perez2020rediscovering}.
-The first class includes chatbots that provide service support used e.g.
-to solve questions about the enrollment \cite{santoso2018dinus}, registration, or academic requirements for exchange students \cite{ranoliya2017chatbot}.
-Focusing on the use at class, service-oriented chatbots would help to introduce students to each other (as done with LISA \cite{dibitonto2018chatbot}), would provide information about schedules and deadlines, recommend general learning materials for the next classes, or individually inform about grades.
-Teaching-oriented chatbots are more sophisticated chatbots that set goals and monitor learning progress.
-A simple example is described in \cite{coronado2018cognitive} where authors proposed agents that store learning materials to be provided on demand to students.
-Also, more complex tutoring systems \cite{crockett2017predicting} individually analyze the learning state of students to provide the next most suitable material in their learning path.
-
-% Point: chatbots are accepted if they help to achieve learning goals
-Regarding the factors for the adoption of chatbots in Education, many studies have focused on the evaluation of technology acceptance or usability such as \cite{Pimmer2019, Roblyer2010}.
-However, Higher Education is a special domain where according to \cite{hobert2019you}, specific pedagogical factors such as learning success or increased motivation are more important.
+Regarding the factors for the adoption of chatbots in higher education, many studies have focused on the evaluation of technology acceptance and usability \cite{Roblyer2010,Pimmer2019}.
+However, higher education is a special domain where according to \cite{hobert2019you}, specific pedagogical factors such as learning success or increased motivation are more important.
+Therefore, to develop efficient chatbots for higher education, all stakeholders’ (i.e.
+educators, students, institutions, etc) expectations needs to be carefully collected and taken into consideration  \cite{sjostrom2018designing,tsivitanidouusers}.
 

### 2021-05-30 edubots_surveys.Rnw
As long as we're adding FAQ agents
I guess we could as well add the local Elvira #6

@@
 On the other hand, teaching-oriented chatbots are more sophisticated as they set personalised learning outcomes and monitor learning progress.
-For instance, \cite{fernoagua2018intelligent} reported on ‘eduAssistant’ a virtual teaching assistant chatobt developed on the Telegram messaging platform.
+For instance, \cite{fernoagua2018intelligent} reported on ‘eduAssistant’ a virtual teaching assistant chatbot developed on the Telegram messaging platform.
 In this study, the Telegram platform was chosen because it is easy to use, students are familiar with its features and it enables students to exchange messages in different formats (text, audio and video) \cite{fernoagua2018intelligent}.

### 2021-05-31 edubots_surveys.Rnw
add the EduBots URL https://www.edubots.eu

@@
 
-In the framework of the EduBots KA2 European project, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms.
+In the framework of the EduBots KA2 European project\footnote{https://www.edubots.eu}, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms.
 A \textit{chatbot} is a program, sometimes based on Artificial Intelligence techniques, that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language.
-Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker’s question fluently, and even ask other questions to the human.
+Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker's question fluently, and even ask other questions to the human.
 However, in most cases a simple messaging-application attached bot will help the students (and teachers); neither computational intelligence nor comprehension of natural languages are requisites, the only one being the fact that they can be accessed from a synchronous conversational application such as the common instant messaging applications used nowadays.
@@
 Using these tools in higher education can facilitate the delivery of personalised learning that occurs anytime anywhere, promote collaborative learning experiences and group discussions \cite{panah2020study}.
-WhatsApp is the most popular MIM platform used by educators to give assignments’ feedback to students, support course discussions and provide learning resources in informal learning settings \cite{panah2020study}.
+WhatsApp is the most popular MIM platform used by educators to give assignments???
+feedback to students, support course discussions and provide learning resources in informal learning settings \cite{panah2020study}.
 The use of WhatsApp in higher education could enhance social presence \cite{tang2017mobile} and foster trust relationships between educators and students embedded in the social learning process \cite{gachago2015crossing}.
@@
 This can lead to technostress \cite{gachago2015crossing}, difficulty in managing responsibilities especially among mature students and lack of privacy \cite{tang2017mobile}.
-Students’ dropout of the MIM groups, as they can leave groups at any time can hinder their learning and undermine educators’ efforts \cite{mwakapina2016whatsapp}.
+Students???
+dropout of the MIM groups, as they can leave groups at any time can hinder their learning and undermine educators???
+efforts \cite{mwakapina2016whatsapp}.
 In addition, there is a need to set rules and norms for these MIM groups in order to maintain the safety of these online communities for students (Abbas et al., 2021b) % This one is missing from the biblio
-without affecting students’ ownership and control that is vital to advance their learning \cite{gachago2015crossing}.
+without affecting students??? ownership and control that is vital to advance their learning \cite{gachago2015crossing}.
 
@@
 The use of conversational agents or chatbots in higher education is still at its infancy cite{yang2019opportunities}.
-Nevertheless, recent studies examining their positive impact on students’ academic performance \cite{perez2020rediscovering} and engagement \cite{differ.chat}(Abbas et al., 2021b) have led to a growing interest in using this technology in classes.
-Indeed, the use of chatbots in collecting course feedback from students in higher education improved students’ response quality and boosted their enjoyment levels (Abbas, Pickard, Atwell and Walker, 2021a).
+Nevertheless, recent studies examining their positive impact on students???
+academic performance \cite{perez2020rediscovering} and engagement \cite{differ.chat}(Abbas et al., 2021b) have led to a growing interest in using this technology in classes.
+Indeed, the use of chatbots in collecting course feedback from students in higher education improved students???
+response quality and boosted their enjoyment levels (Abbas, Pickard, Atwell and Walker, 2021a).
 According to \cite{Roblyer2010}, using either tools such as mobile devices or teaching strategies based on gamification \cite{Yildirim2017} can improve student motivation.
@@
 
-Several higher education chatbots’ evaluation studies were undertaken.
+Several higher education chatbots???
+evaluation studies were undertaken.
 For instance, an evaluation review study presented by \cite{Smutny2020} examined 47 educational chatbots implemented in Facebook Messenger with the focus to identify characteristics and quality metric such as language, subject matter and platform.
@@
 The first category includes those that provide service support such as the chatbot Ask Holly (University of Durham, 2021) % We probably need a reference for this - JJ
-and Dina \cite{santoso2018dinus}, both chatbots respond to students’ questions about enrolment and registration. Ask L.U. (Lancaster University, 2019 % Another reference
-) answers students’ frequently asked questions about timetables, grades, tutors and societies.
+and Dina \cite{santoso2018dinus}, both chatbots respond to students??? questions about enrolment and registration. Ask L.U. (Lancaster University, 2019 % Another reference
+) answers students???
+frequently asked questions about timetables, grades, tutors and societies.
 LISA \cite{dibitonto2018chatbot} and Differ (Differ, 2021) facilitate breaking the ice between new students by introducing them to each other.
@@
 On the other hand, teaching-oriented chatbots are more sophisticated as they set personalised learning outcomes and monitor learning progress.
-For instance, \cite{fernoagua2018intelligent} reported on ‘eduAssistant’ a virtual teaching assistant chatbot developed on the Telegram messaging platform.
+For instance, \cite{fernoagua2018intelligent} reported on ???eduAssistant???
+a virtual teaching assistant chatbot developed on the Telegram messaging platform.
 In this study, the Telegram platform was chosen because it is easy to use, students are familiar with its features and it enables students to exchange messages in different formats (text, audio and video) \cite{fernoagua2018intelligent}.
 In addition, Telegram could operate on all devices and operating systems.
-The ‘eduAssistant’ chatbot acts as an automatic agent between the teacher-content-student, facilitating real-time feedback loops and providing a personalised learning experience relevant to students’ skills and knowledge.
-Using this chatbot, educators can create interactive instances in their lectures where they pose questions to their students and the chatbot assists students who need further help by giving those more hints and reporting to their educator’s dashboard \cite{fernoagua2018intelligent}.
+The ???eduAssistant???
+chatbot acts as an automatic agent between the teacher-content-student, facilitating real-time feedback loops and providing a personalised learning experience relevant to students???
+skills and knowledge.
+Using this chatbot, educators can create interactive instances in their lectures where they pose questions to their students and the chatbot assists students who need further help by giving those more hints and reporting to their educator???s dashboard \cite{fernoagua2018intelligent}.
 This can help educators locate those students that need their attention and send them more educational resources relevant to their academic attainment.
@@
 Facebook Messenger) which confirms with \cite{hobert2019you} and \cite{fernoagua2018intelligent} studies.
-In addition, \cite{sjostrom2018designing} argued that a conceptualision of learners’ questions could aid designers in integrating the appropriate types of questions that the chatbots should support for different courses.
+In addition, \cite{sjostrom2018designing} argued that a conceptualision of learners???
+questions could aid designers in integrating the appropriate types of questions that the chatbots should support for different courses.
 \cite{coronado2018cognitive} proposed agents that store learning materials to be provided on demand to students.
-\cite{crockett2017predicting} reported on tutoring systems, which can perform initial assessments of students’ understanding and provide learning material that would advance their understanding to the next level.
+\cite{crockett2017predicting} reported on tutoring systems, which can perform initial assessments of students???
+understanding and provide learning material that would advance their understanding to the next level.
 
@@
 However, higher education is a special domain where according to \cite{hobert2019you}, specific pedagogical factors such as learning success or increased motivation are more important.
-Therefore, to develop efficient chatbots for higher education, all stakeholders’ (i.e.
+Therefore, to develop efficient chatbots for higher education, all stakeholders???
+(i.e.
 educators, students, institutions, etc) expectations needs to be carefully collected and taken into consideration  \cite{sjostrom2018designing,tsivitanidouusers}.
@@
 In both cases, we used mainly mailing lists, as well as Telegram groups, to spread the link to the form.
-The university form was spread in Spanish (mainly Andalucía and Galicia) universities, as well as Costa Rica and Mexico.
-The tertiary non-university teachers are mainly in Andalucía.
+The university form was spread in Spanish (mainly Andaluc??a and Galicia) universities, as well as Costa Rica and Mexico.
+The tertiary non-university teachers are mainly in Andaluc??a.
 Dissemination and answers took place in the first quarter of 2021, post-pandemic and while, at least in Spain, many universities had mandatory virtual teaching.

### 2021-05-31 edubots_surveys.Rnw
fix a couple of typos
fix a couple of typos + a comment

@@
 \item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
-\item{ RQ2 - Which kind of chatbots would teachers find useful in their classes?? }
+\item{ RQ2 - Which kind of chatbots would teachers find useful in their classes? }
 \item{ RQ3 - Which kind of interaction do teachers prefer with their students? }
@@
 Using these tools in higher education can facilitate the delivery of personalised learning that occurs anytime anywhere, promote collaborative learning experiences and group discussions \cite{panah2020study}.
-WhatsApp is the most popular MIM platform used by educators to give assignments???
-feedback to students, support course discussions and provide learning resources in informal learning settings \cite{panah2020study}.
+WhatsApp is the most popular MIM platform used by educators to give assignments' feedback to students, support course discussions and provide learning resources in informal learning settings \cite{panah2020study}.
 The use of WhatsApp in higher education could enhance social presence \cite{tang2017mobile} and foster trust relationships between educators and students embedded in the social learning process \cite{gachago2015crossing}.
@@
 This can lead to technostress \cite{gachago2015crossing}, difficulty in managing responsibilities especially among mature students and lack of privacy \cite{tang2017mobile}.
-Students???
-dropout of the MIM groups, as they can leave groups at any time can hinder their learning and undermine educators???
-efforts \cite{mwakapina2016whatsapp}.
+Students' dropout of the MIM groups, as they can leave groups at any time can hinder their learning and undermine educators' efforts \cite{mwakapina2016whatsapp}.
 In addition, there is a need to set rules and norms for these MIM groups in order to maintain the safety of these online communities for students (Abbas et al., 2021b) % This one is missing from the biblio
-without affecting students??? ownership and control that is vital to advance their learning \cite{gachago2015crossing}.
+without affecting students' ownership and control that is vital to advance their learning \cite{gachago2015crossing}.
 
@@
 The use of conversational agents or chatbots in higher education is still at its infancy cite{yang2019opportunities}.
-Nevertheless, recent studies examining their positive impact on students???
-academic performance \cite{perez2020rediscovering} and engagement \cite{differ.chat}(Abbas et al., 2021b) have led to a growing interest in using this technology in classes.
-Indeed, the use of chatbots in collecting course feedback from students in higher education improved students???
-response quality and boosted their enjoyment levels (Abbas, Pickard, Atwell and Walker, 2021a).
+Nevertheless, recent studies examining their positive impact on students' academic performance \cite{perez2020rediscovering} and engagement \cite{differ.chat}(Abbas et al., 2021b) have led to a growing interest in using this technology in classes.
+Indeed, the use of chatbots in collecting course feedback from students in higher education improved students' response quality and boosted their enjoyment levels (Abbas, Pickard, Atwell and Walker, 2021a).
 According to \cite{Roblyer2010}, using either tools such as mobile devices or teaching strategies based on gamification \cite{Yildirim2017} can improve student motivation.
@@
 
-Several higher education chatbots???
-evaluation studies were undertaken.
+Several higher education chatbots' evaluation studies were undertaken.
 For instance, an evaluation review study presented by \cite{Smutny2020} examined 47 educational chatbots implemented in Facebook Messenger with the focus to identify characteristics and quality metric such as language, subject matter and platform.
@@
 The first category includes those that provide service support such as the chatbot Ask Holly (University of Durham, 2021) % We probably need a reference for this - JJ
-and Dina \cite{santoso2018dinus}, both chatbots respond to students??? questions about enrolment and registration. Ask L.U. (Lancaster University, 2019 % Another reference
-) answers students???
-frequently asked questions about timetables, grades, tutors and societies.
+and Dina \cite{santoso2018dinus}, both chatbots respond to students' questions about enrolment and registration. Ask L.U. (Lancaster University, 2019 % Another reference
+) answers students' frequently asked questions about timetables, grades, tutors and societies.
 LISA \cite{dibitonto2018chatbot} and Differ (Differ, 2021) facilitate breaking the ice between new students by introducing them to each other.
@@
 On the other hand, teaching-oriented chatbots are more sophisticated as they set personalised learning outcomes and monitor learning progress.
-For instance, \cite{fernoagua2018intelligent} reported on ???eduAssistant???
-a virtual teaching assistant chatbot developed on the Telegram messaging platform.
+For instance, \cite{fernoagua2018intelligent} reported on ''eduAssistant'' a virtual teaching assistant chatbot developed on the Telegram messaging platform.
 In this study, the Telegram platform was chosen because it is easy to use, students are familiar with its features and it enables students to exchange messages in different formats (text, audio and video) \cite{fernoagua2018intelligent}.
 In addition, Telegram could operate on all devices and operating systems.
-The ???eduAssistant???
-chatbot acts as an automatic agent between the teacher-content-student, facilitating real-time feedback loops and providing a personalised learning experience relevant to students???
-skills and knowledge.
-Using this chatbot, educators can create interactive instances in their lectures where they pose questions to their students and the chatbot assists students who need further help by giving those more hints and reporting to their educator???s dashboard \cite{fernoagua2018intelligent}.
+The ''eduAssistant'' chatbot acts as an automatic agent between the teacher-content-student, facilitating real-time feedback loops and providing a personalised learning experience relevant to students' skills and knowledge.
+Using this chatbot, educators can create interactive instances in their lectures where they pose questions to their students and the chatbot assists students who need further help by giving those more hints and reporting to their educator's dashboard \cite{fernoagua2018intelligent}.
 This can help educators locate those students that need their attention and send them more educational resources relevant to their academic attainment.
@@
 Facebook Messenger) which confirms with \cite{hobert2019you} and \cite{fernoagua2018intelligent} studies.
-In addition, \cite{sjostrom2018designing} argued that a conceptualision of learners???
-questions could aid designers in integrating the appropriate types of questions that the chatbots should support for different courses.
+In addition, \cite{sjostrom2018designing} argued that a conceptualision of learners' questions could aid designers in integrating the appropriate types of questions that the chatbots should support for different courses.
 \cite{coronado2018cognitive} proposed agents that store learning materials to be provided on demand to students.
-\cite{crockett2017predicting} reported on tutoring systems, which can perform initial assessments of students???
-understanding and provide learning material that would advance their understanding to the next level.
+\cite{crockett2017predicting} reported on tutoring systems, which can perform initial assessments of students' understanding and provide learning material that would advance their understanding to the next level.
 
@@
 However, higher education is a special domain where according to \cite{hobert2019you}, specific pedagogical factors such as learning success or increased motivation are more important.
-Therefore, to develop efficient chatbots for higher education, all stakeholders???
-(i.e.
+Therefore, to develop efficient chatbots for higher education, all stakeholders' (i.e.
 educators, students, institutions, etc) expectations needs to be carefully collected and taken into consideration  \cite{sjostrom2018designing,tsivitanidouusers}.
@@
 In both cases, we used mainly mailing lists, as well as Telegram groups, to spread the link to the form.
-The university form was spread in Spanish (mainly Andaluc??a and Galicia) universities, as well as Costa Rica and Mexico.
-The tertiary non-university teachers are mainly in Andaluc??a.
+The university form was spread in Spanish (mainly Andaluc\'{\i}a and Galicia) universities, as well as Costa Rica and Mexico.
+The tertiary non-university teachers are mainly in Andaluc\'{\i}a.
 Dissemination and answers took place in the first quarter of 2021, post-pandemic and while, at least in Spain, many universities had mandatory virtual teaching.
@@
 % Describe the survey and population
-We collected responses from a 282 teachers from Spain and Spanish Speaking countries.
+We collected responses from  282 teachers from Spain and Spanish Speaking countries.
 The sample includes teachers from university (68\%) and vocational Education (32\%).
@@
 Finally, the responses are equally distributed attending to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 27\% for 6-15 years of experience, 30\% for 16-25, and 19\% for teachers with more than 25 years of experience.
+
+% [pedro]  the way these (5) figures are shown is a bit strange: different sizes of plots...
 
@@
 
-Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar, and as a matter of fact, as Figure \ref{figure:age.vs.exp} age and experience are correlated strongly, with experience being roughly 20-30 years less than age.
+Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar. %, and as a matter of fact,
+Additionally, as a matter of fact, as Figure \ref{figure:age.vs.exp} shows, age and experience are correlated strongly, with experience being roughly 20-30 years less than age. 
 This might indicate that a differential analysis for age and experience will not yield significant differences, except maybe in the 6-15 years experience group, which is spread over all ages.

### 2021-05-31 edubots_surveys.Rnw
Refactors with knitr for figures

@@
 library(ggthemes)
+library(tidyverse)
 
@@
 
-data <- read.csv("data/survey-student-interaction-pilot-3-2021-EN.csv")
+survey.pilot %>%  mutate(Messaging.Organization =str_split(Messaging.Organization, ", ")) %>% unnest(cols = c(Messaging.Organization)) -> survey.pilot.MessagingOrganization
+
+survey.pilot %>% group_by( PostCOVID.changes ) %>% filter( n() > 1 ) -> survey.pilot.postCOVID
+
+survey.pilot %>%  mutate(ChatbotType = ifelse(Agenda == "No","","Agenda,")) %>%
+  mutate(ChatbotType = ifelse(ClassMaterial == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "ClassMaterial,",sep=""))) %>%
+  mutate(ChatbotType = ifelse(FAQ == "No",paste(ChatbotType, "",sep=""), paste(ChatbotType, "FAQ,",sep=""))) %>%
+  mutate(ChatbotType = ifelse(Grades == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "Grades,",sep=""))) %>%
+  mutate(ChatbotType = ifelse(OtherBot == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "OtherBot,",sep=""))) %>%
+  mutate(ChatbotType = substr(ChatbotType,1,nchar(ChatbotType)-1))-> survey.pilot.chatbottype
+survey.pilot.chatbottype %>%  mutate(ChatbotType =str_split(ChatbotType, ",")) %>% unnest(cols = c(ChatbotType)) -> survey.pilot.ChatbotType
+
+survey.student.interaction <- read.csv("data/survey-student-interaction-pilot-3-2021-EN.csv")
 @
@@
         \centering
-<<gender, echo=FALSE>>=
+<<gender, echo=FALSE, fig.width=3.2, fig.height=2.2>>=
 ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@@
         \centering
-<<age,echo=FALSE>>=
+<<age,echo=FALSE, fig.width=3.2, fig.height=2.2>>=
 ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@@
         \centering
-<<sector, echo=FALSE>>=
+<<sector, echo=FALSE, fig.width=3.2, fig.height=2.2>>=
 ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@@
         \centering
-<<experience,echo=FALSE>>=
+<<experience,echo=FALSE, fig.width=3.2, fig.height=2.2>>=
 ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@@
     \end{minipage}
-    \begin{minipage}[t]{0.55\textwidth}
+    \begin{minipage}[t]{0.6\textwidth}
         \centering
-<<discipline,echo=FALSE>>=
+<<discipline,echo=FALSE, fig.width=5.75, fig.height=2.2>>=
 ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@@
 \begin{center}
-<<interaction,message=FALSE,echo=FALSE>>=
+<<interaction,message=FALSE,echo=FALSE, fig.height=2.0, fig.width=4.0>>=
 library(forcats)
-data %>%
+survey.student.interaction %>%
     mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
@@
 
-\begin{figure}[!ht]
+\begin{figure}[h!tbp]
 \begin{center}
-    \begin{minipage}[t]{0.30\textwidth}
+    \begin{minipage}[t]{0.31\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
+<<gender_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+ggplot(survey.pilot, aes(x = Provided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.30\textwidth}
+    \begin{minipage}[t]{0.31\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/age_provided.pdf}
+<<experience_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+ggplot(survey.pilot, aes(x = Provided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.30\textwidth}
+    \begin{minipage}[t]{0.31\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
+<<sector_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+ggplot(survey.pilot, aes(x = Provided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
     \end{minipage}
     %----
-    \vspace{0.5mm}
-    \begin{minipage}[t]{0.30\textwidth}
+    \vspace{0.2mm}
+    \hspace{10mm}
+    \begin{minipage}[t]{0.5\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
+<<discipline_provided, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
+ggplot(survey.pilot, aes(x = Provided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences','Sciences','Engineering','Technology','No')))+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/discipline_provided.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.50\textwidth}
-	    \centering
- 	    \includegraphics[width=\textwidth]{figures/discipline_provided.pdf}
-    \end{minipage}
+    \hspace{10mm}
     %----
@@
     \vspace{0.5mm}
-    \begin{minipage}[t]{0.30\textwidth}
+    \begin{minipage}[t]{0.31\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/gender_whatsapp.pdf}
+<<gender_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+ggplot(survey.pilot, aes(x = WhatsApp, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/gender_whatsapp.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.30\textwidth}
+    \begin{minipage}[t]{0.31\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/age_whatsapp.pdf}
+<<experience_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+ggplot(survey.pilot, aes(x = WhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/experience_whatsapp.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.30\textwidth}
+    \begin{minipage}[t]{0.31\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/experience_whatsapp.pdf}
+<<sector_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+ggplot(survey.pilot, aes(x = WhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
     \end{minipage}
-    %----
-    \vspace{0.5mm}
-    \begin{minipage}[t]{0.30\textwidth}
+    \vspace{0.2mm}
+    \hspace{10mm}
+    \begin{minipage}[t]{0.5\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
+<<discipline_whatsapp, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
+ggplot(survey.pilot, aes(x = WhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences','Sciences','Engineering','Technology','No')))+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.50\textwidth}
-	    \centering
- 	    \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
-    \end{minipage}
+    \hspace{10mm}
     %----
@@
     \vspace{0.5mm}
-    \begin{minipage}[t]{0.30\textwidth}
+    \begin{minipage}[t]{0.31\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/gender_telegram.pdf}
+<<gender_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+ggplot(survey.pilot, aes(x = Telegram, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/gender_telegram.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.30\textwidth}
+    \begin{minipage}[t]{0.31\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/age_telegram.pdf}
+<<experience_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+ggplot(survey.pilot, aes(x = Telegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/experience_telegram.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.30\textwidth}
+    \begin{minipage}[t]{0.31\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/experience_telegram.pdf}
+<<sector_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+ggplot(survey.pilot, aes(x = Telegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/sector_telegram.pdf}
     \end{minipage}
-    %----
-    \vspace{0.5mm}
-    \begin{minipage}[t]{0.30\textwidth}
+    \vspace{0.2mm}
+    \hspace{10mm}
+    \begin{minipage}[t]{0.5\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/sector_telegram.pdf}
+<<discipline_telegram, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
+ggplot(survey.pilot, aes(x = Telegram, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences','Sciences','Engineering','Technology','No')))+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/discipline_telegram.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.50\textwidth}
-	    \centering
- 	    \includegraphics[width=\textwidth]{figures/discipline_telegram.pdf}
-    \end{minipage}
+    \hspace{10mm}
 \end{center}
@@
 
-\begin{figure}[t]
+\begin{figure}[h!tbp]
 \centering
-\includegraphics[width=\textwidth]{figures/messaging_organization.pdf}
+<<messaging_organization, echo=FALSE, fig.width=19/2.54, fig.height=5/2.54>>=
+survey.pilot.MessagingOrganization <- within(survey.pilot.MessagingOrganization, Messaging.Organization <- factor(Messaging.Organization, levels=names(sort(table(Messaging.Organization), decreasing=TRUE))))
+ggplot(survey.pilot.MessagingOrganization, aes( x = Messaging.Organization, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90))+coord_flip()+ theme(axis.title.y=element_blank())
+@
+%\includegraphics[width=\textwidth]{figures/messaging_organization.pdf}
 \caption{Distribution of teachers' preferences for the chat groups with their students: from groups only with their students from a specific course to groups with greater social interaction with all students in their School or Faculty.}
@@
 
-\begin{figure}[t]
+\begin{figure}[h!tbp]
 \begin{center}
-    \begin{minipage}[t]{0.75\textwidth}
+    \begin{minipage}[t]{0.85\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/gender_covid.pdf}
+<<gender_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
+survey.pilot.postCOVID <- within(survey.pilot.postCOVID, PostCOVID.changes <- factor(PostCOVID.changes, levels=names(sort(table(PostCOVID.changes), decreasing=TRUE))))
+ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/gender_covid.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.75\textwidth}
+    \begin{minipage}[t]{0.85\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
+<<sector_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
+ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.75\textwidth}
+    \begin{minipage}[t]{0.85\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/experience_covid.pdf}
+<<experience_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
+ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/experience_covid.pdf}
     \end{minipage}
@@
 
-\begin{figure}[t]
+\begin{figure}[h!tbp]
 \begin{center}
-    \begin{minipage}[t]{0.47\textwidth}
+    \begin{minipage}[t]{0.85\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/gender_chatbottype.pdf}
+<<gender_chatbottype, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
+survey.pilot.ChatbotType <- within(survey.pilot.ChatbotType, ChatbotType <- factor(ChatbotType, levels=names(sort(table(ChatbotType), decreasing=TRUE))))
+ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/gender_chatbottype.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.47\textwidth}
+    \begin{minipage}[t]{0.85\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/sector_chatbottype.pdf}
+<<sector_chatbottype, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
+ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/sector_chatbottype.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.47\textwidth}
+    \begin{minipage}[t]{0.85\textwidth}
         \centering
- 	    \includegraphics[width=\textwidth]{figures/experience_chatbottype.pdf}
+<<experience_chatbottype, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
+ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/experience_chatbottype.pdf}
     \end{minipage}
@@
 
-\subsection{RQ2 - Which kind of interaction do teachers prefer with their students?}
+\subsection{RQ3 - Which kind of interaction do teachers prefer with their students?}
 
-\begin{figure}[t]
+\begin{figure}[h!tbp]
 \begin{center}
-    \begin{minipage}[t]{0.33\textwidth}
+    \begin{minipage}[t]{0.3\textwidth}
         \centering
-<<gender_synch, echo=FALSE>>=
-ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+<<gender_synch, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+ggplot(survey.student.interaction, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
 @
-
 %       \includegraphics[width=\textwidth]{figures/gender_synch.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.33\textwidth}
+    \begin{minipage}[t]{0.3\textwidth}
         \centering
-<<age_synch, echo=FALSE>>=
-ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+<<experience_sync, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+ggplot(survey.student.interaction, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
 @
-% 	    \includegraphics[width=\textwidth]{figures/age_synch.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.35\textwidth}
-	    \centering
-<<experience_sync, echo=FALSE>>=
-ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
-@
-
 %       \includegraphics[width=\textwidth]{figures/experience_synch.pdf}
@@
         \centering
-<<discipline_synch, echo=FALSE>>=
-ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering","No"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+<<discipline_synch, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
+ggplot(survey.student.interaction, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering","No"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
 @
-
 %       \includegraphics[width=\textwidth]{figures/discipline_synch.pdf}

### 2021-06-01 edubots_surveys.Rnw
partially fixes population adding both surveys

@@
 
-survey.student.interaction <- read.csv("data/survey-student-interaction-pilot-3-2021-EN.csv")
+survey.interaction <- read.csv("data/survey-student-interaction-pilot-3-2021-EN.csv")
+survey.interaction %>% group_by( Gender ) %>% summarise ( n = n() ) %>% mutate( freqGender = n/sum(n)) -> freqInteraction.Gender
+survey.interaction %>% group_by( Age ) %>% summarise ( n = n() ) %>% mutate( freqAge = n/sum(n)) -> freqInteraction.Age
+survey.interaction %>% group_by( Experience ) %>% summarise ( n = n() ) %>% mutate( freqExperience = n/sum(n)) -> freqInteraction.Experience
+survey.interaction %>% group_by( Sector ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freqInteraction.Sector
+survey.interaction %>% group_by( Discipline ) %>% summarise ( n = n() ) %>% mutate( freqDiscipline = n/sum(n)) -> freqInteraction.Discipline
 @
@@
 \begin{center}
-    \begin{minipage}[t]{0.3\textwidth}
+    \begin{minipage}[t]{0.45\textwidth}
         \centering
-<<gender, echo=FALSE, fig.width=3.2, fig.height=2.2>>=
-ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+<<gender, echo=FALSE, fig.width=3.2, fig.height=2.5>>=
+#ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+freq.Gender$source<-rep("survey1")
+freqInteraction.Gender$source<-rep("survey2")
+freqbinded.Gender <- rbind(freq.Gender, freqInteraction.Gender)
+freqbinded.Gender$source <- factor(freqbinded.Gender$source) 
+ggplot(freqbinded.Gender, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
 @
@@
     \end{minipage}
-    \begin{minipage}[t]{0.3\textwidth}
+    \begin{minipage}[t]{0.45\textwidth}
         \centering
-<<age,echo=FALSE, fig.width=3.2, fig.height=2.2>>=
-ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+<<age,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
+#ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+freq.Age$source<-rep("survey1")
+freqInteraction.Age$source<-rep("survey2")
+freqbinded.Age <- rbind(freq.Age, freqInteraction.Age)
+freqbinded.Age$source <- factor(freqbinded.Age$source) 
+ggplot(freqbinded.Age, aes(x = Age, y=freqAge, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
 @
@@
     \end{minipage}
-    \begin{minipage}[t]{0.3\textwidth}
+    \vspace{0.5mm}
+    \begin{minipage}[t]{0.5\textwidth}
         \centering
-<<sector, echo=FALSE, fig.width=3.2, fig.height=2.2>>=
-ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+<<experience, echo=FALSE, fig.width=4.5, fig.height=2.5>>=
+#ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+freq.Experience$source<-rep("survey1")
+freqInteraction.Experience$source<-rep("survey2")
+freqbinded.Experience <- rbind(freq.Experience, freqInteraction.Experience)
+freqbinded.Experience$source <- factor(freqbinded.Experience$source) 
+ggplot(freqbinded.Experience, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
 @
@@
     \end{minipage}
-
-    \vspace{0.5mm}
-    \begin{minipage}[t]{0.3\textwidth}
+    \begin{minipage}[t]{0.4\textwidth}
         \centering
-<<experience,echo=FALSE, fig.width=3.2, fig.height=2.2>>=
+<<sector,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
 ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+#freq.Sector$source<-rep("survey1")
+#freqInteraction.Sector$source<-rep("survey2")
+#freqbinded.Sector <- rbind(freq.Sector, freqInteraction.Sector)
+#freqbinded.Sector$source <- factor(freqbinded.Sector$source) 
+#ggplot(freqbinded.Sector, aes(x = Sector, y=freqSector, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
 @
@@
     \end{minipage}
-    \begin{minipage}[t]{0.6\textwidth}
+    \begin{minipage}[t]{\textwidth}
         \centering
-<<discipline,echo=FALSE, fig.width=5.75, fig.height=2.2>>=
-ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+<<discipline,echo=FALSE, fig.width=5.75, fig.height=2.5>>=
+#ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+freq.Discipline$source<-rep("survey1")
+freqInteraction.Discipline$source<-rep("survey2")
+freqbinded.Discipline <- rbind(freq.Discipline, freqInteraction.Discipline)
+freqbinded.Discipline$source <- factor(freqbinded.Discipline$source) 
+ggplot(freqbinded.Discipline, aes(x = Discipline, y=freqDiscipline, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
 @
@@
 \end{figure}
-%
+
+Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar. %, and as a matter of fact,
+Additionally, as a matter of fact, as Figure \ref{figure:age.vs.exp} shows, age and experience are correlated strongly, with experience being roughly 20-30 years less than age. 
+This might indicate that a differential analysis for age and experience will not yield significant differences, except maybe in the 6-15 years experience group, which is spread over all ages.
+At any rate, experience seems to be the dominating factor here and we'll use experience only unless we detect some significant difference by age.
+
 \begin{figure}[h!tbp]
@@
 library(forcats)
-survey.student.interaction %>%
+survey.interaction %>%
     mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
@@
 \end{figure}
-
-Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar. %, and as a matter of fact,
-Additionally, as a matter of fact, as Figure \ref{figure:age.vs.exp} shows, age and experience are correlated strongly, with experience being roughly 20-30 years less than age. 
-This might indicate that a differential analysis for age and experience will not yield significant differences, except maybe in the 6-15 years experience group, which is spread over all ages.
-At any rate, experience seems to be the dominating factor here and we'll use experience only unless we detect some significant difference by age.
 
@@
 <<gender_synch, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.student.interaction, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
 @
@@
 <<experience_sync, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.student.interaction, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
 @
@@
 <<discipline_synch, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.student.interaction, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering","No"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering","No"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
 @

### 2021-06-01 scripts/summaries.R

@@ -4,44 +4,83 @@ library(tidyr)
 library(ggplot2)
 library(forcats)
 
-data <- read.csv("../data/survey-pilot-3-EN.csv")
+survey.pilot <- read.csv("../data/survey-pilot-3-EN.csv")
+survey.interaction <- read.csv("../data/survey-student-interaction-pilot-3-2021-EN.csv")
+#ggplot(survey.pilot,aes(Age,Experience))+geom_point(aes(size=value),colour="green")
 
-ggplot(data,aes(Age,Experience))+geom_point(aes(size=value),colour="green")
+survey.pilot %>% group_by( Gender ) %>% summarise ( n = n() ) %>% mutate( freqGender = n/sum(n)) -> freq.Gender
+survey.pilot %>% group_by( Age ) %>% summarise ( n = n() ) %>% mutate( freqAge = n/sum(n)) -> freq.Age
+survey.pilot %>% group_by( Experience ) %>% summarise ( n = n() ) %>% mutate( freqExperience = n/sum(n)) -> freq.Experience
+survey.pilot %>% group_by( Sector ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freq.Sector
+survey.pilot %>% group_by( Discipline ) %>% summarise ( n = n() ) %>% mutate( freqDiscipline = n/sum(n)) -> freq.Discipline
 
-data %>% group_by( Gender ) %>% summarise ( n = n() ) %>% mutate( freqGender = n/sum(n)) -> freq.Gender
-data %>% group_by( Age ) %>% summarise ( n = n() ) %>% mutate( freqAge = n/sum(n)) -> freq.Age
-data %>% group_by( Experience ) %>% summarise ( n = n() ) %>% mutate( freqExperience = n/sum(n)) -> freq.Experience
-data %>% group_by( Sector ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freq.Sector
-data %>% group_by( Discipline ) %>% summarise ( n = n() ) %>% mutate( freqDiscipline = n/sum(n)) -> freq.Discipline
-
-data %>%
+survey.pilot %>%
     mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
     mutate(Experience = fct_relevel(Experience, "0-05 years", "06-15 years", "16-25 years", "> 25 years" )) %>%
[…]

### 2021-06-01 edubots_surveys.Rnw
fixes variables for population and minor text changes refs #17

@@
 survey.interaction %>% group_by( Experience ) %>% summarise ( n = n() ) %>% mutate( freqExperience = n/sum(n)) -> freqInteraction.Experience
-survey.interaction %>% group_by( Sector ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freqInteraction.Sector
+survey.interaction %>% group_by( Vocational ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freqInteraction.Sector
+freqInteraction.Sector$Sector <- freqInteraction.Sector$Vocational
+freqInteraction.Sector %>% mutate(Sector = ifelse(as.character(Vocational) == "Yes", "Vocational", "University")) -> freqInteraction.Sector
+freqInteraction.Sector <- freqInteraction.Sector[-c(1)]
 survey.interaction %>% group_by( Discipline ) %>% summarise ( n = n() ) %>% mutate( freqDiscipline = n/sum(n)) -> freqInteraction.Discipline
+freqInteraction.Discipline %>%mutate(Discipline = ifelse(as.character(Discipline) == "No", "Other", as.character(Discipline))) -> freqInteraction.Discipline
+freq.Discipline %>% mutate(Discipline = ifelse(as.character(Discipline) == "No", "Other", as.character(Discipline))) %>%
+                mutate(n = ifelse(as.character(Discipline) =="Engineering", sum(n[as.character(Discipline)=="Engineering" | as.character(Discipline)=="Technology"]), n)) %>%
+                mutate(Discipline = ifelse(as.character(Discipline) == "Engineering", "Tech/Engineering", as.character(Discipline))) %>%
+                subset(as.character(Discipline) != "Technology")-> freq.Discipline
 @
@@
 % Describe the survey and population
-We collected responses from  282 teachers from Spain and Spanish Speaking countries.
-The sample includes teachers from university (68\%) and vocational Education (32\%).
-Regarding gender, 63\% are male teachers and 35\% female (approximately 2\% chose not to disclose it).
-Finally, the responses are equally distributed attending to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 27\% for 6-15 years of experience, 30\% for 16-25, and 19\% for teachers with more than 25 years of experience.
+We collected responses from 282 teachers from Spain and Spanish Speaking countries for the first survey (\textit{survey1} in Fig.
+\ref{figure:teachers_population}) and 205 for the second one (\textit{survey2}).
+The sample includes mostly teachers from university, although about 32\% and 8\% are from vocational education in the first and second survey respectively.
+Regarding gender, in total 61\% are male teachers and 32\% female (approximately 5\% chose not to disclose it).
+Finally, the responses are equally distributed attending to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 26\% for 6-15 years of experience, 30\% for 16-25, and 20\% for teachers with more than 25 years of experience.
 
@@
 \begin{center}
-    \begin{minipage}[t]{0.45\textwidth}
+    \begin{minipage}[t]{0.3\textwidth}
         \centering
@@
 freqbinded.Gender$source <- factor(freqbinded.Gender$source) 
-ggplot(freqbinded.Gender, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+ggplot(freqbinded.Gender, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
 @
@@
     \end{minipage}
-    \begin{minipage}[t]{0.45\textwidth}
+    \begin{minipage}[t]{0.3\textwidth}
         \centering
@@
 freqbinded.Age$source <- factor(freqbinded.Age$source) 
-ggplot(freqbinded.Age, aes(x = Age, y=freqAge, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+ggplot(freqbinded.Age, aes(x = Age, y=freqAge, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
 @
@@
     \end{minipage}
+    \begin{minipage}[t]{0.3\textwidth}
+        \centering
+<<sector,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
+#ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+freq.Sector$source<-rep("survey1")
+freqInteraction.Sector$source<-rep("survey2")
+freqbinded.Sector <- rbind(freq.Sector, freqInteraction.Sector)
+freqbinded.Sector$source <- factor(freqbinded.Sector$source) 
+ggplot(freqbinded.Sector, aes(x = Sector, y=freqSector, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/sector.pdf}
+    \end{minipage}
     \vspace{0.5mm}
-    \begin{minipage}[t]{0.5\textwidth}
+    \begin{minipage}[t]{0.38\textwidth}
         \centering
-<<experience, echo=FALSE, fig.width=4.5, fig.height=2.5>>=
+<<experience, echo=FALSE, fig.width=4.5, fig.height=3.475>>=
 #ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@@
 freqbinded.Experience$source <- factor(freqbinded.Experience$source) 
-ggplot(freqbinded.Experience, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+ggplot(freqbinded.Experience, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
 @        
-
-%       \includegraphics[width=\textwidth]{figures/sector.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.4\textwidth}
-        \centering
-<<sector,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
-ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-#freq.Sector$source<-rep("survey1")
-#freqInteraction.Sector$source<-rep("survey2")
-#freqbinded.Sector <- rbind(freq.Sector, freqInteraction.Sector)
-#freqbinded.Sector$source <- factor(freqbinded.Sector$source) 
-#ggplot(freqbinded.Sector, aes(x = Sector, y=freqSector, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-@
-
 %       \includegraphics[width=\textwidth]{figures/experience.pdf}
     \end{minipage}
-    \begin{minipage}[t]{\textwidth}
+    \begin{minipage}[t]{0.52\textwidth}
         \centering
-<<discipline,echo=FALSE, fig.width=5.75, fig.height=2.5>>=
+<<discipline,echo=FALSE, fig.width=8.2, fig.height=4.45>>=
 #ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@@
 freqbinded.Discipline$source <- factor(freqbinded.Discipline$source) 
-ggplot(freqbinded.Discipline, aes(x = Discipline, y=freqDiscipline, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+freqbinded.Discipline$Discipline <- factor(freqbinded.Discipline$Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other"))
+ggplot(freqbinded.Discipline, aes(x = Discipline, y=freqDiscipline, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
 @
@@
 \end{center}
-    \caption{Sample population description. A total 282 teachers shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
+    \caption{Sample population description.
+The responses from two surveys were collected amount to 282 for the first survey (\textit{survey1} in red) and 205 for the second (\textit{survey2} in blue).
+Data are shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
 \label{figure:teachers_population}

### 2021-06-01 scripts/summaries.R

@@ -29,7 +29,6 @@ survey.interaction %>% group_by( Experience ) %>% summarise ( n = n() ) %>% muta
 survey.interaction %>% group_by( Sector ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freqInteraction.Sector
 survey.interaction %>% group_by( Discipline ) %>% summarise ( n = n() ) %>% mutate( freqDiscipline = n/sum(n)) -> freqInteraction.Discipline
 
-
 freq.Gender$source<-rep("survey1")
 freqInteraction.Gender$source<-rep("survey2")
 freqbinded.Gender <- rbind(freq.Gender, freqInteraction.Gender)
@@ -48,18 +47,31 @@ freqbinded.Experience <- rbind(freq.Experience, freqInteraction.Experience)
 freqbinded.Experience$source <- factor(freqbinded.Experience$source) 
 ggplot(freqbinded.Experience, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
 
+
+survey.interaction %>% group_by( Vocational ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freqInteraction.Sector
+freqInteraction.Sector$Sector <- freqInteraction.Sector$Vocational
+freqInteraction.Sector %>% mutate(Sector = ifelse(as.character(Vocational) == "Yes", "Vocational", "University")) -> freqInteraction.Sector
+freqInteraction.Sector <- freqInteraction.Sector[-c(1)]
 freq.Sector$source<-rep("survey1")
 freqInteraction.Sector$source<-rep("survey2")
 freqbinded.Sector <- rbind(freq.Sector, freqInteraction.Sector)
 freqbinded.Sector$source <- factor(freqbinded.Sector$source) 
 ggplot(freqbinded.Sector, aes(x = Sector, y=freqSector, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
 
-freq.Discipline$source<-rep("survey1")
-freqInteraction.Discipline$source<-rep("survey2")
-freqbinded.Discipline <- rbind(freq.Discipline, freqInteraction.Discipline)
-freqbinded.Discipline$source <- factor(freqbinded.Discipline$source) 
[…]

### 2021-06-01 edubots_surveys.Rnw
fixes variables to use similar categories for both surveys refs #17

@@
 survey.pilot.chatbottype %>%  mutate(ChatbotType =str_split(ChatbotType, ",")) %>% unnest(cols = c(ChatbotType)) -> survey.pilot.ChatbotType
+
+survey.pilot %>%mutate(Discipline = ifelse(as.character(Discipline) == "No", "Other", as.character(Discipline))) %>%
+  mutate(Discipline = ifelse(as.character(Discipline) == "Engineering", "Tech/Engineering", as.character(Discipline))) %>%
+  mutate(Discipline = ifelse(as.character(Discipline) == "Technology", "Tech/Engineering", as.character(Discipline)))->survey.pilot.Discipline
 
@@
 <<discipline_provided, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot, aes(x = Provided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences','Sciences','Engineering','Technology','No')))+ theme(axis.title.y=element_blank())
+
+ggplot(survey.pilot.Discipline, aes(x = Provided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
 @
@@
 <<discipline_whatsapp, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot, aes(x = WhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences','Sciences','Engineering','Technology','No')))+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot.Discipline, aes(x = WhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
 @
@@
 <<discipline_telegram, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot, aes(x = Telegram, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences','Sciences','Engineering','Technology','No')))+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot.Discipline, aes(x = Telegram, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
 @

### 2021-06-01 scripts/process.R

@@ -32,12 +32,16 @@ ggplot(data, aes(x = Provided, group = Experience)) + geom_bar(aes(y = ..prop..,
 ggsave('../figures/experience_provided.pdf', width = 100, height = 70, units = "mm")
 
 #ggplot(data, aes(x = WhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Discipline)
-ggplot(data, aes(x = WhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences','Sciences','Engineering','Technology','No')))+ theme(axis.title.y=element_blank())
-ggsave('../figures/discipline_whatsapp.pdf', width = 186, height = 77, units = "mm")
-ggplot(data, aes(x = Telegram, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences','Sciences','Engineering','Technology','No')))+ theme(axis.title.y=element_blank())
-ggsave('../figures/discipline_telegram.pdf', width = 186, height = 77, units = "mm")
-ggplot(data, aes(x = Provided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences','Sciences','Engineering','Technology','No')))+ theme(axis.title.y=element_blank())
-ggsave('../figures/discipline_provided.pdf', width = 186, height = 77, units = "mm")
+
+data %>%mutate(Discipline = ifelse(as.character(Discipline) == "No", "Other", as.character(Discipline))) %>%
+  mutate(Discipline = ifelse(as.character(Discipline) == "Engineering", "Tech/Engineering", as.character(Discipline))) %>%
[…]

### 2021-06-01 scripts/summaries.R

@@ -71,7 +71,7 @@ freqbinded.Discipline <- rbind(freq.Discipline2, freqInteraction.Discipline2)
 freqbinded.Discipline$source <- factor(freqbinded.Discipline$source) 
 freqbinded.Discipline$Discipline <- factor(freqbinded.Discipline$Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other"))
 ggplot(freqbinded.Discipline, aes(x = Discipline, y=freqDiscipline, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-ggsave('../figures/cozas.pdf')
+
 
 #ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
 #ggsave('../figures/gender.pdf', width = 80, height = 55, units = "mm")

### 2021-06-02 scripts/process.R
adds code for statistical significance refs #24

@@ -1,4 +1,3 @@
-
 library(ggplot2)
 library(dplyr)
 library(tidyr)
@@ -53,15 +52,98 @@ ggplot(data, aes(x = Provided, group = Gender)) + geom_bar(aes(y = ..prop.., fil
 ggsave('../figures/gender_provided.pdf', width = 100, height = 70, units = "mm")
 
 
+# Statistical significance
+df <-select(data, WhatsApp, Telegram, Provided, Gender, Sector, Age, Experience, Discipline)
+df[as.character(df$Gender)!="PNTS", ] -> df1
+df2<- droplevels(df1)
+
+mytable<-cbind(table(df2$Gender, df2$WhatsApp), table(df2$Gender, df2$Telegram), table(df2$Gender, df2$Provided))
+App.vs.Gender<-mytable[,-c(1,3,5)]
+colnames(App.vs.Gender)<- c("WhatsApp", "Telegram","Provided")
+chisq.test(App.vs.Gender)$p.value
+
+mytable<-cbind(table(df2$Age, df2$WhatsApp), table(df2$Age, df2$Telegram), table(df2$Age, df2$Provided))
+App.vs.Age<-mytable[,-c(1,3,5)]
+colnames(App.vs.Age)<- c("WhatsApp", "Telegram","Provided")
+chisq.test(App.vs.Age)$p.value
+
+mytable<-cbind(table(df2$Sector, df2$WhatsApp), table(df2$Sector, df2$Telegram), table(df2$Sector, df2$Provided))
+App.vs.Sector<-mytable[,-c(1,3,5)]
+colnames(App.vs.Sector)<- c("WhatsApp", "Telegram","Provided")
+chisq.test(App.vs.Sector)$p.value
+
+df2 %>%mutate(Discipline = ifelse(as.character(Discipline) == "No", "Other", as.character(Discipline))) %>%
+  mutate(Discipline = ifelse(as.character(Discipline) == "Engineering", "Tech/Engineering", as.character(Discipline))) %>%
+  mutate(Discipline = ifelse(as.character(Discipline) == "Technology", "Tech/Engineering", as.character(Discipline)))->df2
+mytable<-cbind(table(df2$Discipline, df2$WhatsApp), table(df2$Discipline, df2$Telegram), table(df2$Discipline, df2$Provided))
+App.vs.Discipline<-mytable[,-c(1,3,5)]
[…]

### 2021-06-04 edubots_surveys.Rnw
Incorporate the local "Elvira" experience, refs #6
It's not totally related, but it was a chatbot and there were similar
experiences reflected in the SoA already.

Also, closes #1 since bibliography is probably complete already.

@@
 This is why many students prefer to remain silent and ask their question later via email.
-However, this means a waste of time and a delay of hours or even days to get the teacher's answer.
+However, this means a waste of time and a delay of hours or even days to get the teacher's answer; it does not scale well with the size of the class.
 Chatbot technology has a potential to fill the gap between teacher and students, helping them to solve questions and carry out a dynamic and autonomous learning \cite{Griol2014,kim2020}.
@@
 LISA \cite{dibitonto2018chatbot} and Differ (Differ, 2021) facilitate breaking the ice between new students by introducing them to each other.
-\cite{ranoliya2017chatbot} proposed a generic chatbot for university students that is able to answer their frequently asked questions.
+\cite{ranoliya2017chatbot} proposed a generic chatbot for university students that is able to answer their frequently asked questions; for some time, the University of Granada had ELVIRA as a chatbot in their main page \cite{MOREO20129}.
+Besides being able to answer pre-established (frequent) questions, it did so from the main University of Granada using an inset character, voiced by a real person, who lip-synched the answers.
+The emphasis in this case, however, was on the authenticity of the synchronization more than in making the update of questions and answers simpler, or more interactive, using actual messaging platforms.
+In most cases, using the inset search engine was able to give you more up-to-date and accurate answers.
 

### 2021-06-04 edubots_surveys.Rnw
Abstract has been exhaustively revised. Closes #5

@@
 \begin{abstract} % abstract
-Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but above all, an examination of the attitudes of the affected teaching community.
+Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but above all, an examination of the attitudes of the affected community, especially those that will need to handle them, teachers.
 In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think about the introduction of messaging platforms and chatbots, what their needs are, what kind of use cases they see for them, and in what kind of environment they think its use will be valuable.
 We will examine how and when these attitudes vary across gender, experience, and other factors, such as the kind of discipline they are teaching.
-Our conclusions might help with the adoption of messaging platforms, as well as chatbots or other kind of bots, by higher education institution, and how these must be introduced to teachers so that it helps them achieve desired educational outcomes.
+Our conclusions might help with the adoption of messaging platforms in an educational setting, as well as chatbots or other kind of bots, by higher education institution, and how these must be introduced to teachers so that it helps them achieve desired educational outcomes.
 \end{abstract}

### 2021-06-14 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Updated the cited papers

@@
 Students' dropout of the MIM groups, as they can leave groups at any time can hinder their learning and undermine educators' efforts \cite{mwakapina2016whatsapp}.
-In addition, there is a need to set rules and norms for these MIM groups in order to maintain the safety of these online communities for students (Abbas et al., 2021b) % This one is missing from the biblio
-without affecting students' ownership and control that is vital to advance their learning \cite{gachago2015crossing}.
+In addition, there is a need to set rules and norms for these MIM groups in order to maintain the safety of these online communities for students \cite{abbas2021onlinechat} without affecting students' ownership and control that is vital to advance their learning \cite{gachago2015crossing}.
 
 % The Use of Chatbots in Higher Education
-The use of conversational agents or chatbots in higher education is still at its infancy cite{yang2019opportunities}.
+The use of conversational agents or chatbots in higher education is still at its infancy \cite{yang2019opportunities}.
 Nevertheless, recent studies examining their positive impact on students' academic performance \cite{perez2020rediscovering} and engagement \cite{differ.chat}(Abbas et al., 2021b) have led to a growing interest in using this technology in classes.
-Indeed, the use of chatbots in collecting course feedback from students in higher education improved students' response quality and boosted their enjoyment levels (Abbas, Pickard, Atwell and Walker, 2021a).
+Indeed, the use of chatbots in collecting course feedback from students in higher education improved students' response quality and boosted their enjoyment levels \cite{abbas2021Surveys}.
 According to \cite{Roblyer2010}, using either tools such as mobile devices or teaching strategies based on gamification \cite{Yildirim2017} can improve student motivation.
@@
 Another study aimed to categorise educational chatbots according to their purpose into service-oriented and teaching-oriented \cite{perez2020rediscovering}.
-The first category includes those that provide service support such as the chatbot Ask Holly (University of Durham, 2021) % We probably need a reference for this - JJ
-and Dina \cite{santoso2018dinus}, both chatbots respond to students' questions about enrolment and registration. Ask L.U. (Lancaster University, 2019 % Another reference
-) answers students' frequently asked questions about timetables, grades, tutors and societies.
-LISA \cite{dibitonto2018chatbot} and Differ (Differ, 2021) facilitate breaking the ice between new students by introducing them to each other.
+The first category includes those that provide service support such as the chatbot Ask Holly \cite{meetholly} and Dina \cite{santoso2018dinus}, both chatbots respond to students' questions about enrolment and registration.
+Ask L.U.
+\cite{LancasterUniversity_2019} answers students' frequently asked questions about timetables, grades, tutors and societies.
+LISA \cite{dibitonto2018chatbot} and Differ \cite{differchat} facilitate breaking the ice between new students by introducing them to each other.
 \cite{ranoliya2017chatbot} proposed a generic chatbot for university students that is able to answer their frequently asked questions; for some time, the University of Granada had ELVIRA as a chatbot in their main page \cite{MOREO20129}.

### 2021-06-15 edubots_surveys.Rnw
Updated citations in State of the Art Section
All citations updated ref #6

--- 2021-06-04 edubots_surveys.Rnw
@@
 library(ggthemes)
-library(tidyverse)
 
@@
 
-survey.pilot %>%  mutate(Messaging.Organization =str_split(Messaging.Organization, ", ")) %>% unnest(cols = c(Messaging.Organization)) -> survey.pilot.MessagingOrganization
-
-survey.pilot %>% group_by( PostCOVID.changes ) %>% filter( n() > 1 ) -> survey.pilot.postCOVID
-
-survey.pilot %>%  mutate(ChatbotType = ifelse(Agenda == "No","","Agenda,")) %>%
-  mutate(ChatbotType = ifelse(ClassMaterial == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "ClassMaterial,",sep=""))) %>%
-  mutate(ChatbotType = ifelse(FAQ == "No",paste(ChatbotType, "",sep=""), paste(ChatbotType, "FAQ,",sep=""))) %>%
-  mutate(ChatbotType = ifelse(Grades == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "Grades,",sep=""))) %>%
-  mutate(ChatbotType = ifelse(OtherBot == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "OtherBot,",sep=""))) %>%
-  mutate(ChatbotType = substr(ChatbotType,1,nchar(ChatbotType)-1))-> survey.pilot.chatbottype
-survey.pilot.chatbottype %>%  mutate(ChatbotType =str_split(ChatbotType, ",")) %>% unnest(cols = c(ChatbotType)) -> survey.pilot.ChatbotType
-
-survey.pilot %>%mutate(Discipline = ifelse(as.character(Discipline) == "No", "Other", as.character(Discipline))) %>%
-  mutate(Discipline = ifelse(as.character(Discipline) == "Engineering", "Tech/Engineering", as.character(Discipline))) %>%
-  mutate(Discipline = ifelse(as.character(Discipline) == "Technology", "Tech/Engineering", as.character(Discipline)))->survey.pilot.Discipline
-
-survey.interaction <- read.csv("data/survey-student-interaction-pilot-3-2021-EN.csv")
-survey.interaction %>% group_by( Gender ) %>% summarise ( n = n() ) %>% mutate( freqGender = n/sum(n)) -> freqInteraction.Gender
-survey.interaction %>% group_by( Age ) %>% summarise ( n = n() ) %>% mutate( freqAge = n/sum(n)) -> freqInteraction.Age
-survey.interaction %>% group_by( Experience ) %>% summarise ( n = n() ) %>% mutate( freqExperience = n/sum(n)) -> freqInteraction.Experience
-survey.interaction %>% group_by( Vocational ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freqInteraction.Sector
-freqInteraction.Sector$Sector <- freqInteraction.Sector$Vocational
-freqInteraction.Sector %>% mutate(Sector = ifelse(as.character(Vocational) == "Yes", "Vocational", "University")) -> freqInteraction.Sector
-freqInteraction.Sector <- freqInteraction.Sector[-c(1)]
-survey.interaction %>% group_by( Discipline ) %>% summarise ( n = n() ) %>% mutate( freqDiscipline = n/sum(n)) -> freqInteraction.Discipline
-freqInteraction.Discipline %>%mutate(Discipline = ifelse(as.character(Discipline) == "No", "Other", as.character(Discipline))) -> freqInteraction.Discipline
-freq.Discipline %>% mutate(Discipline = ifelse(as.character(Discipline) == "No", "Other", as.character(Discipline))) %>%
-                mutate(n = ifelse(as.character(Discipline) =="Engineering", sum(n[as.character(Discipline)=="Engineering" | as.character(Discipline)=="Technology"]), n)) %>%
-                mutate(Discipline = ifelse(as.character(Discipline) == "Engineering", "Tech/Engineering", as.character(Discipline))) %>%
-                subset(as.character(Discipline) != "Technology")-> freq.Discipline
+data <- read.csv("data/survey-student-interaction-pilot-3-2021-EN.csv")
 @
@@
 
-In the framework of the EduBots KA2 European project\footnote{https://www.edubots.eu}, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms.
+In the framework of the EduBots KA2 European project, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms.
 A \textit{chatbot} is a program, sometimes based on Artificial Intelligence techniques, that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language.
-Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker's question fluently, and even ask other questions to the human.
+Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker’s question fluently, and even ask other questions to the human.
 However, in most cases a simple messaging-application attached bot will help the students (and teachers); neither computational intelligence nor comprehension of natural languages are requisites, the only one being the fact that they can be accessed from a synchronous conversational application such as the common instant messaging applications used nowadays.
@@
 This is why many students prefer to remain silent and ask their question later via email.
-However, this means a waste of time and a delay of hours or even days to get the teacher's answer; it does not scale well with the size of the class.
+However, this means a waste of time and a delay of hours or even days to get the teacher's answer.
 Chatbot technology has a potential to fill the gap between teacher and students, helping them to solve questions and carry out a dynamic and autonomous learning \cite{Griol2014,kim2020}.
@@
 \item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
-\item{ RQ2 - Which kind of chatbots would teachers find useful in their classes? }
+\item{ RQ2 - Which kind of chatbots would teachers find useful in their classes?? }
 \item{ RQ3 - Which kind of interaction do teachers prefer with their students? }
@@
 
-% The Use of Mobile Instant Messaging (MIM) Platforms in Higher Education
-The widespread and rapid adoption of free Mobile Instant messaging (MIM) tools/platforms such as WhatsApp, Telegram, WeChat and Facebook Messenger stems from their simplicity, ease of use and multi-modality (i.e.
+The Use of Mobile Instant Messaging (MIM) Platforms in Higher Education
+The widespread and rapid adoption of free MIM tools/platforms such as WhatsApp, Telegram, WeChat and Facebook Messenger stems from their simplicity, ease of use and multi-modality (i.e.
 video, audio, text) \cite{tang2017mobile}.
 Using these tools in higher education can facilitate the delivery of personalised learning that occurs anytime anywhere, promote collaborative learning experiences and group discussions \cite{panah2020study}.
-WhatsApp is the most popular MIM platform used by educators to give assignments' feedback to students, support course discussions and provide learning resources in informal learning settings \cite{panah2020study}.
+WhatsApp is the most popular MIM platform used by educators to give assignments’ feedback to students, support course discussions and provide learning resources in informal learning settings \cite{panah2020study}.
 The use of WhatsApp in higher education could enhance social presence \cite{tang2017mobile} and foster trust relationships between educators and students embedded in the social learning process \cite{gachago2015crossing}.
@@
 This can lead to technostress \cite{gachago2015crossing}, difficulty in managing responsibilities especially among mature students and lack of privacy \cite{tang2017mobile}.
-Students' dropout of the MIM groups, as they can leave groups at any time can hinder their learning and undermine educators' efforts \cite{mwakapina2016whatsapp}.
-In addition, there is a need to set rules and norms for these MIM groups in order to maintain the safety of these online communities for students (Abbas et al., 2021b) % This one is missing from the biblio
-without affecting students' ownership and control that is vital to advance their learning \cite{gachago2015crossing}.
+Students’ dropout of the MIM groups, as they can leave groups at any time can hinder their learning and undermine educators’ efforts \cite{mwakapina2016whatsapp}.
+In addition, there is a need to set rules and norms for these MIM groups in order to maintain the safety of these online communities for students \cite{abbas2021onlinechat} without affecting students’ ownership and control that is vital to advance their learning \cite{gachago2015crossing}.
 
-% The Use of Chatbots in Higher Education
-The use of conversational agents or chatbots in higher education is still at its infancy cite{yang2019opportunities}.
-Nevertheless, recent studies examining their positive impact on students' academic performance \cite{perez2020rediscovering} and engagement \cite{differ.chat}(Abbas et al., 2021b) have led to a growing interest in using this technology in classes.
-Indeed, the use of chatbots in collecting course feedback from students in higher education improved students' response quality and boosted their enjoyment levels (Abbas, Pickard, Atwell and Walker, 2021a).
-According to \cite{Roblyer2010}, using either tools such as mobile devices or teaching strategies based on gamification \cite{Yildirim2017} can improve student motivation.
-In this sense, \cite{Pimmer2019} carried out a series of experiments with technological tools whose results showed positive perception and acceptance of the use of technology in teaching and learning.
+The Use of Chatbots in Higher Education
+The use of conversational agents or chatbots in higher education is still at its infancy \cite{yang2019opportunities}.
+Nevertheless, recent studies examining their positive impact on students’ academic performance \cite{perez2020rediscovering} and engagement \cite{differ.chat, abbas2021onlinechat} have led to a growing interest in using this technology in classes.
+Indeed, the use of chatbots in collecting course feedback from students in higher education improved students’ response quality and boosted their enjoyment levels \cite{abbas2021Surveys}.
+According to Roblyer et al.
+\cite{Roblyer2010}(2010), using either tools such as mobile devices or teaching strategies based on gamification \cite{Yildirim2017} can improve student motivation.
+In this sense, Pimmer et al.
+(2019)\cite{Pimmer2019} carried out a series of experiments with technological tools whose results showed positive perception and acceptance of the use of technology in teaching and learning.
 
-Several higher education chatbots' evaluation studies were undertaken.
-For instance, an evaluation review study presented by \cite{Smutny2020} examined 47 educational chatbots implemented in Facebook Messenger with the focus to identify characteristics and quality metric such as language, subject matter and platform.
+Several higher education chatbots’ evaluation studies were undertaken.
+For instance, an evaluation review study presented by Smutny and Schreiberova (2020)\cite{Smutny2020} examined 47 educational chatbots implemented in Facebook Messenger with the focus to identify characteristics and quality metric such as language, subject matter and platform.
 Another study aimed to categorise educational chatbots according to their purpose into service-oriented and teaching-oriented \cite{perez2020rediscovering}.
-The first category includes those that provide service support such as the chatbot Ask Holly (University of Durham, 2021) % We probably need a reference for this - JJ
-and Dina \cite{santoso2018dinus}, both chatbots respond to students' questions about enrolment and registration. Ask L.U. (Lancaster University, 2019 % Another reference
-) answers students' frequently asked questions about timetables, grades, tutors and societies.
-LISA \cite{dibitonto2018chatbot} and Differ (Differ, 2021) facilitate breaking the ice between new students by introducing them to each other.
-\cite{ranoliya2017chatbot} proposed a generic chatbot for university students that is able to answer their frequently asked questions; for some time, the University of Granada had ELVIRA as a chatbot in their main page \cite{MOREO20129}.
-Besides being able to answer pre-established (frequent) questions, it did so from the main University of Granada using an inset character, voiced by a real person, who lip-synched the answers.
-The emphasis in this case, however, was on the authenticity of the synchronization more than in making the update of questions and answers simpler, or more interactive, using actual messaging platforms.
-In most cases, using the inset search engine was able to give you more up-to-date and accurate answers.
+The first category includes those that provide service support such as the chatbot Ask Holly \cite{meetholly} and Dina \cite{santoso2018dinus}, both chatbots respond to students’ questions about enrolment and registration.
+Ask L.U.
+\cite{lancasterU} answers students’ frequently asked questions about timetables, grades, tutors and societies.
+LISA \cite{dibitonto2018chatbot} and Differ \cite{differchat} facilitate breaking the ice between new students by introducing them to each other.
+Ranoliya et al.
+(2017)\cite{ranoliya2017chatbot} proposed a generic chatbot for university students that is able to answer their frequently asked questions.
 
 On the other hand, teaching-oriented chatbots are more sophisticated as they set personalised learning outcomes and monitor learning progress.
-For instance, \cite{fernoagua2018intelligent} reported on ''eduAssistant'' a virtual teaching assistant chatbot developed on the Telegram messaging platform.
-In this study, the Telegram platform was chosen because it is easy to use, students are familiar with its features and it enables students to exchange messages in different formats (text, audio and video) \cite{fernoagua2018intelligent}.
+For instance, Fernoagă, Stelea, Gavrilă, and Sandu (2018) \cite{ernoagua2018intelligent} reported on ‘eduAssistant’ a virtual teaching assistant chatobt developed on the Telegram messaging platform.
+In this study, the Telegram platform was chosen because it is easy to use, students are familiar with its features and it enables students to exchange messages in different formats (text, audio and video) \cite{ernoagua2018intelligent}.
 In addition, Telegram could operate on all devices and operating systems.
-The ''eduAssistant'' chatbot acts as an automatic agent between the teacher-content-student, facilitating real-time feedback loops and providing a personalised learning experience relevant to students' skills and knowledge.
-Using this chatbot, educators can create interactive instances in their lectures where they pose questions to their students and the chatbot assists students who need further help by giving those more hints and reporting to their educator's dashboard \cite{fernoagua2018intelligent}.
+The ‘eduAssistant’ chatbot acts as an automatic agent between the teacher-content-student, facilitating real-time feedback loops and providing a personalised learning experience relevant to students’ skills and knowledge.
+Using this chatbot, educators can create interactive instances in their lectures where they pose questions to their students and the chatbot assists students who need further help by giving those more hints and reporting to their educator’s dashboard \cite{ernoagua2018intelligent}.
 This can help educators locate those students that need their attention and send them more educational resources relevant to their academic attainment.
-
-Furthermore, \cite{sjostrom2018designing} proposed a conceptual architecture for teaching-oriented chatbots in higher education.
+Furthermore, Sjöström et al.
+(2018) \cite{Sjostrom2018} proposed a conceptual architecture for teaching-oriented chatbots in higher education.
 This conceptual architecture is based on a systematic literature review of previous studies examining the design of chatbots in higher education and a content analysis of student emails and discussion forum posts of four instances of a Java programming course.
 The study outlined several design considerations, among them, the authors emphasised the importance of developing chatbots in platforms that students and educators are familiar with and can easily access (i.e.
-Facebook Messenger) which confirms with \cite{hobert2019you} and \cite{fernoagua2018intelligent} studies.
-In addition, \cite{sjostrom2018designing} argued that a conceptualision of learners' questions could aid designers in integrating the appropriate types of questions that the chatbots should support for different courses.
-\cite{coronado2018cognitive} proposed agents that store learning materials to be provided on demand to students.
-\cite{crockett2017predicting} reported on tutoring systems, which can perform initial assessments of students' understanding and provide learning material that would advance their understanding to the next level.
-
-Regarding the factors for the adoption of chatbots in higher education, many studies have focused on the evaluation of technology acceptance and usability \cite{Roblyer2010,Pimmer2019}.
-However, higher education is a special domain where according to \cite{hobert2019you}, specific pedagogical factors such as learning success or increased motivation are more important.
-Therefore, to develop efficient chatbots for higher education, all stakeholders' (i.e.
-educators, students, institutions, etc) expectations needs to be carefully collected and taken into consideration  \cite{sjostrom2018designing,tsivitanidouusers}.
+Facebook Messenger) which confirms with Hobert’s (2019) \cite{hobert2019you} and Fernoagă, Stelea, Gavrilă, and Sandu’s (2018) \cite{fernoagua2018intelligent}  studies.
+In addition, Sjöström et al.
+\cite{Sjostrom2018} argued that a conceptualision of learners’ questions could aid designers in integrating the appropriate types of questions that the chatbots should support for different courses.
+Coronado et al.
+(2018) \cite{coronado2018cognitive} proposed agents that store learning materials to be provided on demand to students.
+Crockett et al.
+(2017) \cite{crockett2017predicting} reported on tutoring systems, which can perform initial assessments of students’ understanding and provid learning material that would advance their understanding to the next level.
+Regarding the factors for the adoption of chatbots in higher education, many studies have focused on the evaluation of technology acceptance and usability \cite {Roblyer2010, Pimmer2019}.
+However, higher education is a special domain where according to Hobert (2019) \cite{hobert2019you}, specific pedagogical factors such as learning success or increased motivation are more important.
+Therefore, to develop efficient chatbots for higher education, all stakeholders’ (i.e.
+educators, students, institutions, etc) expectations needs to be carefully collected and taken into consideration \cite{sjostrom2018designing, tsivitanidouusers}.
 
@@
 In both cases, we used mainly mailing lists, as well as Telegram groups, to spread the link to the form.
-The university form was spread in Spanish (mainly Andaluc\'{\i}a and Galicia) universities, as well as Costa Rica and Mexico.
-The tertiary non-university teachers are mainly in Andaluc\'{\i}a.
+The university form was spread in Spanish (mainly Andalucía and Galicia) universities, as well as Costa Rica and Mexico.
+The tertiary non-university teachers are mainly in Andalucía.
 Dissemination and answers took place in the first quarter of 2021, post-pandemic and while, at least in Spain, many universities had mandatory virtual teaching.
@@
 % Describe the survey and population
-We collected responses from 282 teachers from Spain and Spanish Speaking countries for the first survey (\textit{survey1} in Fig.
-\ref{figure:teachers_population}) and 205 for the second one (\textit{survey2}).
-The sample includes mostly teachers from university, although about 32\% and 8\% are from vocational education in the first and second survey respectively.
-Regarding gender, in total 61\% are male teachers and 32\% female (approximately 5\% chose not to disclose it).
-Finally, the responses are equally distributed attending to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 26\% for 6-15 years of experience, 30\% for 16-25, and 20\% for teachers with more than 25 years of experience.
-
-% [pedro]  the way these (5) figures are shown is a bit strange: different sizes of plots...
+We collected responses from a 282 teachers from Spain and Spanish Speaking countries.
+The sample includes teachers from university (68\%) and vocational Education (32\%).
+Regarding gender, 63\% are male teachers and 35\% female (approximately 2\% chose not to disclose it).
+Finally, the responses are equally distributed attending to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 27\% for 6-15 years of experience, 30\% for 16-25, and 19\% for teachers with more than 25 years of experience.
 
@@
 	    \centering
-<<gender, echo=FALSE, fig.width=3.2, fig.height=2.5>>=
-#ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-freq.Gender$source<-rep("survey1")
-freqInteraction.Gender$source<-rep("survey2")
-freqbinded.Gender <- rbind(freq.Gender, freqInteraction.Gender)
-freqbinded.Gender$source <- factor(freqbinded.Gender$source) 
-ggplot(freqbinded.Gender, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+<<gender, echo=FALSE>>=
+ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
 @
@@
 	    \centering
-<<age,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
-#ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-freq.Age$source<-rep("survey1")
-freqInteraction.Age$source<-rep("survey2")
-freqbinded.Age <- rbind(freq.Age, freqInteraction.Age)
-freqbinded.Age$source <- factor(freqbinded.Age$source) 
-ggplot(freqbinded.Age, aes(x = Age, y=freqAge, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+<<age,echo=FALSE>>=
+ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
 @
@@
 	    \centering
-<<sector,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
-#ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-freq.Sector$source<-rep("survey1")
-freqInteraction.Sector$source<-rep("survey2")
-freqbinded.Sector <- rbind(freq.Sector, freqInteraction.Sector)
-freqbinded.Sector$source <- factor(freqbinded.Sector$source) 
-ggplot(freqbinded.Sector, aes(x = Sector, y=freqSector, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+<<sector, echo=FALSE>>=
+ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
 @
+
 % 	    \includegraphics[width=\textwidth]{figures/sector.pdf}
     \end{minipage}
+
     \vspace{0.5mm}
-    \begin{minipage}[t]{0.38\textwidth}
+    \begin{minipage}[t]{0.3\textwidth}
 	    \centering
-<<experience, echo=FALSE, fig.width=4.5, fig.height=3.475>>=
-#ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-freq.Experience$source<-rep("survey1")
-freqInteraction.Experience$source<-rep("survey2")
-freqbinded.Experience <- rbind(freq.Experience, freqInteraction.Experience)
-freqbinded.Experience$source <- factor(freqbinded.Experience$source) 
-ggplot(freqbinded.Experience, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+<<experience,echo=FALSE>>=
+ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
 @
+
 % 	    \includegraphics[width=\textwidth]{figures/experience.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.52\textwidth}
+    \begin{minipage}[t]{0.55\textwidth}
 	    \centering
-<<discipline,echo=FALSE, fig.width=8.2, fig.height=4.45>>=
-#ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-freq.Discipline$source<-rep("survey1")
-freqInteraction.Discipline$source<-rep("survey2")
-freqbinded.Discipline <- rbind(freq.Discipline, freqInteraction.Discipline)
-freqbinded.Discipline$source <- factor(freqbinded.Discipline$source) 
-freqbinded.Discipline$Discipline <- factor(freqbinded.Discipline$Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other"))
-ggplot(freqbinded.Discipline, aes(x = Discipline, y=freqDiscipline, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+<<discipline,echo=FALSE>>=
+ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
 @
@@
 \end{center}
-    \caption{Sample population description.
-The responses from two surveys were collected amount to 282 for the first survey (\textit{survey1} in red) and 205 for the second (\textit{survey2} in blue).
-Data are shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
+    \caption{Sample population description. A total 282 teachers shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
 \label{figure:teachers_population}
 \end{figure}
-
-Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar. %, and as a matter of fact,
-Additionally, as a matter of fact, as Figure \ref{figure:age.vs.exp} shows, age and experience are correlated strongly, with experience being roughly 20-30 years less than age. 
-This might indicate that a differential analysis for age and experience will not yield significant differences, except maybe in the 6-15 years experience group, which is spread over all ages.
-At any rate, experience seems to be the dominating factor here and we'll use experience only unless we detect some significant difference by age.
-
+%
 \begin{figure}[h!tbp]
 \begin{center}
-<<interaction,message=FALSE,echo=FALSE, fig.height=2.0, fig.width=4.0>>=
+<<interaction,message=FALSE,echo=FALSE>>=
 library(forcats)
-survey.interaction %>%
+data %>%
     mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
@@
 \end{figure}
+
+Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar, and as a matter of fact, as Figure \ref{figure:age.vs.exp} age and experience are correlated strongly, with experience being roughly 20-30 years less than age.
+This might indicate that a differential analysis for age and experience will not yield significant differences, except maybe in the 6-15 years experience group, which is spread over all ages.
+At any rate, experience seems to be the dominating factor here and we'll use experience only unless we detect some significant difference by age.
 
@@
 
-\begin{figure}[h!tbp]
+\begin{figure}[!ht]
 \begin{center}
-    \begin{minipage}[t]{0.31\textwidth}
+    \begin{minipage}[t]{0.30\textwidth}
 	    \centering
-<<gender_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = Provided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
+    \begin{minipage}[t]{0.30\textwidth}
 	    \centering
-<<experience_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = Provided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/age_provided.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
+    \begin{minipage}[t]{0.30\textwidth}
 	    \centering
-<<sector_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = Provided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
     \end{minipage}
     %----
-    \vspace{0.2mm}
-    \hspace{10mm}
-    \begin{minipage}[t]{0.5\textwidth}
+    \vspace{0.5mm}
+    \begin{minipage}[t]{0.30\textwidth}
 	    \centering
-<<discipline_provided, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-
-ggplot(survey.pilot.Discipline, aes(x = Provided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/discipline_provided.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
     \end{minipage}
-    \hspace{10mm}
+    \begin{minipage}[t]{0.50\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/discipline_provided.pdf}
+    \end{minipage}
     %----
@@
     \vspace{0.5mm}
-    \begin{minipage}[t]{0.31\textwidth}
+    \begin{minipage}[t]{0.30\textwidth}
 	    \centering
-<<gender_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = WhatsApp, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/gender_whatsapp.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/gender_whatsapp.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
+    \begin{minipage}[t]{0.30\textwidth}
 	    \centering
-<<experience_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = WhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/experience_whatsapp.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/age_whatsapp.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
+    \begin{minipage}[t]{0.30\textwidth}
 	    \centering
-<<sector_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = WhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/experience_whatsapp.pdf}
     \end{minipage}
-    \vspace{0.2mm}
-    \hspace{10mm}
-    \begin{minipage}[t]{0.5\textwidth}
+    %----
+    \vspace{0.5mm}
+    \begin{minipage}[t]{0.30\textwidth}
 	    \centering
-<<discipline_whatsapp, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot.Discipline, aes(x = WhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
     \end{minipage}
-    \hspace{10mm}
+    \begin{minipage}[t]{0.50\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
+    \end{minipage}
     %----
@@
     \vspace{0.5mm}
-    \begin{minipage}[t]{0.31\textwidth}
+    \begin{minipage}[t]{0.30\textwidth}
 	    \centering
-<<gender_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = Telegram, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/gender_telegram.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/gender_telegram.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
+    \begin{minipage}[t]{0.30\textwidth}
 	    \centering
-<<experience_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = Telegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/experience_telegram.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/age_telegram.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
+    \begin{minipage}[t]{0.30\textwidth}
 	    \centering
-<<sector_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = Telegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/sector_telegram.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/experience_telegram.pdf}
     \end{minipage}
-    \vspace{0.2mm}
-    \hspace{10mm}
-    \begin{minipage}[t]{0.5\textwidth}
+    %----
+    \vspace{0.5mm}
+    \begin{minipage}[t]{0.30\textwidth}
 	    \centering
-<<discipline_telegram, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot.Discipline, aes(x = Telegram, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/discipline_telegram.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/sector_telegram.pdf}
     \end{minipage}
-    \hspace{10mm}
+    \begin{minipage}[t]{0.50\textwidth}
+	    \centering
+ 	    \includegraphics[width=\textwidth]{figures/discipline_telegram.pdf}
+    \end{minipage}
 \end{center}
@@
 
-\begin{figure}[h!tbp]
+\begin{figure}[t]
 \centering
-<<messaging_organization, echo=FALSE, fig.width=19/2.54, fig.height=5/2.54>>=
-survey.pilot.MessagingOrganization <- within(survey.pilot.MessagingOrganization, Messaging.Organization <- factor(Messaging.Organization, levels=names(sort(table(Messaging.Organization), decreasing=TRUE))))
-ggplot(survey.pilot.MessagingOrganization, aes( x = Messaging.Organization, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90))+coord_flip()+ theme(axis.title.y=element_blank())
-@
-%\includegraphics[width=\textwidth]{figures/messaging_organization.pdf}
+\includegraphics[width=\textwidth]{figures/messaging_organization.pdf}
 \caption{Distribution of teachers' preferences for the chat groups with their students: from groups only with their students from a specific course to groups with greater social interaction with all students in their School or Faculty.}
@@
 
-\begin{figure}[h!tbp]
+\begin{figure}[t]
 \begin{center}
-    \begin{minipage}[t]{0.85\textwidth}
+    \begin{minipage}[t]{0.75\textwidth}
 	    \centering
-<<gender_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-survey.pilot.postCOVID <- within(survey.pilot.postCOVID, PostCOVID.changes <- factor(PostCOVID.changes, levels=names(sort(table(PostCOVID.changes), decreasing=TRUE))))
-ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/gender_covid.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/gender_covid.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.85\textwidth}
+    \begin{minipage}[t]{0.75\textwidth}
 	    \centering
-<<sector_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.85\textwidth}
-        \centering
-<<experience_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/experience_covid.pdf}
+    \begin{minipage}[t]{0.75\textwidth}
+	    \centering[
+ 	    \includegraphics[width=\textwidth]{figures/experience_covid.pdf}
     \end{minipage}
@@
 
-\begin{figure}[h!tbp]
+\begin{figure}[t]
 \begin{center}
-    \begin{minipage}[t]{0.85\textwidth}
+    \begin{minipage}[t]{0.47\textwidth}
 	    \centering
-<<gender_chatbottype, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-survey.pilot.ChatbotType <- within(survey.pilot.ChatbotType, ChatbotType <- factor(ChatbotType, levels=names(sort(table(ChatbotType), decreasing=TRUE))))
-ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/gender_chatbottype.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/gender_chatbottype.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.85\textwidth}
+    \begin{minipage}[t]{0.47\textwidth}
 	    \centering
-<<sector_chatbottype, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/sector_chatbottype.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/sector_chatbottype.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.85\textwidth}
+    \begin{minipage}[t]{0.47\textwidth}
 	    \centering
-<<experience_chatbottype, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/experience_chatbottype.pdf}
+ 	    \includegraphics[width=\textwidth]{figures/experience_chatbottype.pdf}
     \end{minipage}
@@
 
-\subsection{RQ3 - Which kind of interaction do teachers prefer with their students?}
+\subsection{RQ2 - Which kind of interaction do teachers prefer with their students?}
 
-\begin{figure}[h!tbp]
+\begin{figure}[t]
 \begin{center}
-    \begin{minipage}[t]{0.3\textwidth}
+    \begin{minipage}[t]{0.33\textwidth}
 	    \centering
-<<gender_synch, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+<<gender_synch, echo=FALSE>>=
+ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
 @
+
 % 	    \includegraphics[width=\textwidth]{figures/gender_synch.pdf}
     \end{minipage}
-    \begin{minipage}[t]{0.3\textwidth}
+    \begin{minipage}[t]{0.33\textwidth}
 	    \centering
-<<experience_sync, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+<<age_synch, echo=FALSE>>=
+ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
 @
+% 	    \includegraphics[width=\textwidth]{figures/age_synch.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.35\textwidth}
+	    \centering
+<<experience_sync, echo=FALSE>>=
+ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+@
+
 % 	    \includegraphics[width=\textwidth]{figures/experience_synch.pdf}
@@
 	    \centering
-<<discipline_synch, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering","No"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+<<discipline_synch, echo=FALSE>>=
+ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering","No"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
 @
+
 % 	    \includegraphics[width=\textwidth]{figures/discipline_synch.pdf}

### 2021-06-19 edubots_surveys.Rnw
Advances the state of the art #6
Also adds a simple script for knitting

--- 2021-06-14 edubots_surveys.Rnw
@@
 \begin{abstract} % abstract
-Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but above all, an examination of the attitudes of the affected community, especially those that will need to handle them, teachers.
-In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think about the introduction of messaging platforms and chatbots, what their needs are, what kind of use cases they see for them, and in what kind of environment they think its use will be valuable.
-We will examine how and when these attitudes vary across gender, experience, and other factors, such as the kind of discipline they are teaching.
-Our conclusions might help with the adoption of messaging platforms in an educational setting, as well as chatbots or other kind of bots, by higher education institution, and how these must be introduced to teachers so that it helps them achieve desired educational outcomes.
+Introducing new technologies such as messaging platforms, and chatbots
+attached to it, in higher education, requires careful consideration of
+all options, but above all, an examination of the attitudes of the
+affected community, especially those that will need to handle them,
+teachers.
+In this paper we have surveyed the opinions of tertiary education
+teachers based mainly in Spain and Spanish speaking countries, looking
+at what they think about the introduction of messaging platforms and
+chatbots, what their needs are, what kind of use cases they see for
+them, and in what kind of environment they think its use will be
+valuable. We will examine how and when these attitudes vary across
+gender, experience, and other factors, such as the kind of discipline
+they are teaching. Our conclusions might help with the adoption of
+messaging platforms in an educational setting, as well as chatbots or
+other kind of bots, by higher education institution, and how these
+must be introduced to teachers so that it helps them achieve desired
+educational outcomes. 
 \end{abstract}
@@
 
-The rest of the paper is organized as follows.
-Next is an overview of what current research has found about the use of messaging applications, including chatbots, in the classroom.
+The rest of the paper is organized as follows: Next is an overview of what current research has found about the use of messaging applications, including chatbots, in the classroom.
 The methodology used in the survey is presented in Section \ref{sec:meth}, and the results of the survey are presented next in Section \ref{sec:res}.
@@
 % The Use of Mobile Instant Messaging (MIM) Platforms in Higher Education
-The widespread and rapid adoption of free Mobile Instant messaging (MIM) tools/platforms such as WhatsApp, Telegram, WeChat and Facebook Messenger stems from their simplicity, ease of use and multi-modality (i.e.
-video, audio, text) \cite{tang2017mobile}.
-Using these tools in higher education can facilitate the delivery of personalised learning that occurs anytime anywhere, promote collaborative learning experiences and group discussions \cite{panah2020study}.
-WhatsApp is the most popular MIM platform used by educators to give assignments' feedback to students, support course discussions and provide learning resources in informal learning settings \cite{panah2020study}.
-The use of WhatsApp in higher education could enhance social presence \cite{tang2017mobile} and foster trust relationships between educators and students embedded in the social learning process \cite{gachago2015crossing}.
+The widespread and rapid adoption of free Mobile Instant messaging
+(MIM) tools/platforms such as WhatsApp, Telegram, WeChat and Facebook
+Messenger stems from their simplicity, ease of use and multi-modality
+(i.e. video, audio, text) \cite{tang2017mobile}. Using these tools in
+higher education can facilitate the delivery of personalised learning
+that occurs anytime anywhere, promote collaborative learning
+experiences and group discussions \cite{panah2020study}.
 
-Nevertheless, there are challenges when using MIM tools that occur due to the blurring of boundaries between academic and private life.
-This can lead to technostress \cite{gachago2015crossing}, difficulty in managing responsibilities especially among mature students and lack of privacy \cite{tang2017mobile}.
-Students' dropout of the MIM groups, as they can leave groups at any time can hinder their learning and undermine educators' efforts \cite{mwakapina2016whatsapp}.
-In addition, there is a need to set rules and norms for these MIM groups in order to maintain the safety of these online communities for students \cite{abbas2021onlinechat} without affecting students' ownership and control that is vital to advance their learning \cite{gachago2015crossing}.
+WhatsApp is, at least in most Western countries,
+the most popular MIM platform used by educators to give assignments'
+feedback to students, support course discussions and provide learning
+resources in informal learning settings \cite{panah2020study}.  The
+use of WhatsApp in higher education could enhance social presence
+\cite{tang2017mobile} and foster trust relationships between educators
+and students embedded in the social learning process
+\cite{gachago2015crossing}.
+
+Nevertheless, there are challenges when using MIM tools that occur due
+to the blurring of boundaries between academic and private life. This
+can lead to technostress \cite{gachago2015crossing}, difficulty in
+managing responsibilities, especially among mature students, and lack of
+privacy \cite{tang2017mobile}.  Students' dropout of the MIM groups,
+as they can leave groups at any time, can hinder their learning and
+undermine educators' efforts \cite{mwakapina2016whatsapp}.  In
+addition, there is a need to set rules and norms for these MIM groups
+in order to maintain the safety of these online communities for
+students \cite{abbas2021onlinechat} without affecting students'
+ownership and control that is vital to advance their learning
+\cite{gachago2015crossing}.
+This is why examining the role of MIM in higher education is still a challenge, and why the attitudes of the teaching community towards them has to be examined, as we do in this paper.
 
 % The Use of Chatbots in Higher Education
-The use of conversational agents or chatbots in higher education is still at its infancy \cite{yang2019opportunities}.
-Nevertheless, recent studies examining their positive impact on students' academic performance \cite{perez2020rediscovering} and engagement \cite{differ.chat}(Abbas et al., 2021b) have led to a growing interest in using this technology in classes.
-Indeed, the use of chatbots in collecting course feedback from students in higher education improved students' response quality and boosted their enjoyment levels \cite{abbas2021Surveys}.
-According to \cite{Roblyer2010}, using either tools such as mobile devices or teaching strategies based on gamification \cite{Yildirim2017} can improve student motivation.
-In this sense, \cite{Pimmer2019} carried out a series of experiments with technological tools whose results showed positive perception and acceptance of the use of technology in teaching and learning.
+The use of MIM, although possibly valuable by itself, can be enhanced via the use of chatbots, which, being conversational agents, usually well where synchronous conversations take place. 
+The use of conversational agents or chatbots in higher education is
+still at its infancy \cite{yang2019opportunities}. Nevertheless,
+recent studies examining their positive impact on students' academic
+performance \cite{perez2020rediscovering} and engagement
+\cite{differ.chat,abbas2021onlinechat} have led to a growing interest
+in using this technology in the (possibly virtual) classroom. Indeed, the use of chatbots in
+collecting course feedback from students in higher education improved
+students' response quality and boosted their enjoyment levels
+\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using
+either tools such as mobile devices or teaching strategies based on
+gamification \cite{Yildirim2017} can improve student motivation. In
+this sense, \cite{Pimmer2019} carried out a series of experiments with
+technological tools whose results showed positive perception and
+acceptance of the use of technology in teaching and learning.
 
-Several higher education chatbots' evaluation studies were undertaken.
-For instance, an evaluation review study presented by \cite{Smutny2020} examined 47 educational chatbots implemented in Facebook Messenger with the focus to identify characteristics and quality metric such as language, subject matter and platform.
-Another study aimed to categorise educational chatbots according to their purpose into service-oriented and teaching-oriented \cite{perez2020rediscovering}.
-The first category includes those that provide service support such as the chatbot Ask Holly \cite{meetholly} and Dina \cite{santoso2018dinus}, both chatbots respond to students' questions about enrolment and registration.
-Ask L.U.
-\cite{LancasterUniversity_2019} answers students' frequently asked questions about timetables, grades, tutors and societies.
-LISA \cite{dibitonto2018chatbot} and Differ \cite{differchat} facilitate breaking the ice between new students by introducing them to each other.
-\cite{ranoliya2017chatbot} proposed a generic chatbot for university students that is able to answer their frequently asked questions; for some time, the University of Granada had ELVIRA as a chatbot in their main page \cite{MOREO20129}.
-Besides being able to answer pre-established (frequent) questions, it did so from the main University of Granada using an inset character, voiced by a real person, who lip-synched the answers.
-The emphasis in this case, however, was on the authenticity of the synchronization more than in making the update of questions and answers simpler, or more interactive, using actual messaging platforms.
-In most cases, using the inset search engine was able to give you more up-to-date and accurate answers.
+Several higher education chatbots' evaluation studies were
+undertaken. For instance, an evaluation review study presented by
+\cite{Smutny2020} examined 47 educational chatbots implemented in
+Facebook Messenger with the focus to identify characteristics and
+quality metric such as language, subject matter and platform. Another
+study aimed to categorise educational chatbots according to their
+purpose into service-oriented and teaching-oriented
+\cite{perez2020rediscovering}. The first category includes those that
+provide service support such as the chatbot Ask Holly \cite{meetholly}
+and Dina \cite{santoso2018dinus}, both chatbots respond to students'
+questions about enrollment and registration. Ask
+L.U. \cite{LancasterUniversity_2019} answers students' frequently
+asked questions about timetables, grades, tutors and societies. LISA
+\cite{dibitonto2018chatbot} and Differ \cite{differchat} facilitate
+breaking the ice between new students by introducing them to each
+other.  \cite{ranoliya2017chatbot} proposed a generic chatbot for
+university students that is able to answer their frequently asked
+questions; for some time, the University of Granada had ELVIRA as a
+chatbot in their main page \cite{MOREO20129}. Besides being able to
+answer pre-established (frequent) questions, it did so from the main
+University of Granada using an inset character, voiced by a real
+person, who lip-synched the answers. The emphasis in this case,
+however, was on the authenticity of the synchronization more than in
+making the update of questions and answers simpler, or more
+interactive, using actual messaging platforms. In most cases, using
+the inset search engine was able to give you more up-to-date and
+accurate answers.
 
-On the other hand, teaching-oriented chatbots are more sophisticated as they set personalised learning outcomes and monitor learning progress.
-For instance, \cite{fernoagua2018intelligent} reported on ''eduAssistant'' a virtual teaching assistant chatbot developed on the Telegram messaging platform.
-In this study, the Telegram platform was chosen because it is easy to use, students are familiar with its features and it enables students to exchange messages in different formats (text, audio and video) \cite{fernoagua2018intelligent}.
-In addition, Telegram could operate on all devices and operating systems.
-The ''eduAssistant'' chatbot acts as an automatic agent between the teacher-content-student, facilitating real-time feedback loops and providing a personalised learning experience relevant to students' skills and knowledge.
-Using this chatbot, educators can create interactive instances in their lectures where they pose questions to their students and the chatbot assists students who need further help by giving those more hints and reporting to their educator's dashboard \cite{fernoagua2018intelligent}.
-This can help educators locate those students that need their attention and send them more educational resources relevant to their academic attainment.
+On the other hand, teaching-oriented chatbots are more sophisticated
+as they set personalised learning outcomes and monitor learning
+progress. For instance, \cite{fernoagua2018intelligent} reported on
+''eduAssistant'' a virtual teaching assistant chatbot developed on the
+Telegram messaging platform. In this study, the Telegram platform was
+chosen because it is easy to use, students are familiar with its
+features and it enables students to exchange messages in different
+formats (text, audio and video) \cite{fernoagua2018intelligent}. In
+addition, Telegram could operate on all devices and operating
+systems. The ''eduAssistant'' chatbot acts as an automatic agent
+between the teacher-content-student, facilitating real-time feedback
+loops and providing a personalised learning experience relevant to
+students' skills and knowledge. Using this chatbot, educators can
+create interactive instances in their lectures where they pose
+questions to their students and the chatbot assists students who need
+further help by giving those more hints and reporting to their
+educator's dashboard \cite{fernoagua2018intelligent}. This can help
+educators locate those students that need their attention and send
+them more educational resources relevant to their academic
+attainment.
 
-Furthermore, \cite{sjostrom2018designing} proposed a conceptual architecture for teaching-oriented chatbots in higher education.
-This conceptual architecture is based on a systematic literature review of previous studies examining the design of chatbots in higher education and a content analysis of student emails and discussion forum posts of four instances of a Java programming course.
-The study outlined several design considerations, among them, the authors emphasised the importance of developing chatbots in platforms that students and educators are familiar with and can easily access (i.e.
-Facebook Messenger) which confirms with \cite{hobert2019you} and \cite{fernoagua2018intelligent} studies.
-In addition, \cite{sjostrom2018designing} argued that a conceptualision of learners' questions could aid designers in integrating the appropriate types of questions that the chatbots should support for different courses.
-\cite{coronado2018cognitive} proposed agents that store learning materials to be provided on demand to students.
-\cite{crockett2017predicting} reported on tutoring systems, which can perform initial assessments of students' understanding and provide learning material that would advance their understanding to the next level.
+Despite its (arguably) successful implementation in different higher education institutions, over all in the fringes of educational activity, its implementation or deployment is not trivial.
+Some authors \cite{sjostrom2018designing} have proposed a conceptual
+architecture for the adoption teaching-oriented chatbots in higher education.  This
+conceptual architecture is based on a systematic literature review of
+previous studies examining the design of chatbots in higher education
+and a content analysis of student emails and discussion forum posts of
+four instances of a Java programming course.  The study outlined
+several design considerations; among them, the authors emphasised the
+importance of developing chatbots in platforms that students and
+educators are familiar with and can easily access (i.e. Facebook
+Messenger) which confirms with \cite{hobert2019you} and
+\cite{fernoagua2018intelligent} studies. In addition,
+\cite{sjostrom2018designing} argued that a conceptualision of
+learners' questions could aid designers in integrating the appropriate
+types of questions that the chatbots should support for different
+courses.  \cite{coronado2018cognitive} proposed agents that store
+learning materials to be provided on demand to
+students. \cite{crockett2017predicting} reported on tutoring systems,
+which can perform initial assessments of students' understanding and
+provide learning material that would advance their understanding to
+the next level.
 
-Regarding the factors for the adoption of chatbots in higher education, many studies have focused on the evaluation of technology acceptance and usability \cite{Roblyer2010,Pimmer2019}.
-However, higher education is a special domain where according to \cite{hobert2019you}, specific pedagogical factors such as learning success or increased motivation are more important.
-Therefore, to develop efficient chatbots for higher education, all stakeholders' (i.e.
-educators, students, institutions, etc) expectations needs to be carefully collected and taken into consideration  \cite{sjostrom2018designing,tsivitanidouusers}.
+Regarding the factors for the adoption of chatbots in higher
+education, many studies have focused on the evaluation of technology
+acceptance and usability \cite{Roblyer2010,Pimmer2019}. However,
+higher education is a special domain where according to
+\cite{hobert2019you}, specific pedagogical factors such as learning
+success or increased motivation are more important.  Therefore, to
+develop efficient chatbots for higher education, all stakeholders'
+(i.e. educators, students, institutions, etc) expectations needs to be
+carefully collected and taken into consideration
+\cite{sjostrom2018designing,tsivitanidouusers}.
 

### 2021-06-19 knit.R

@@ -1,0 +1,4 @@
+#!/usr/bin/env Rscript
+
+library(knitr)
+knit("edubots_surveys.Rnw")

### 2021-06-19 edubots_surveys.Rnw
Fixed bib
Trying to give closure to #6 linking it with the rest of the paper

@@
 asked questions about timetables, grades, tutors and societies. LISA
-\cite{dibitonto2018chatbot} and Differ \cite{differchat} facilitate
+\cite{dibitonto2018chatbot} and Differ \cite{differ.chat} facilitate
 breaking the ice between new students by introducing them to each
@@
 
-Regarding the factors for the adoption of chatbots in higher
-education, many studies have focused on the evaluation of technology
+As in any new technology, it's important to ascertain which factors will help or impede its adoption; this is why many studies have focused on the evaluation of technology
 acceptance and usability \cite{Roblyer2010,Pimmer2019}. However,
@@
 \cite{sjostrom2018designing,tsivitanidouusers}.
+
+This is why this paper is focused on which factors are considered the most important by the people that are going to use them.
+We spread our survey over university as well as other higher education institution, so that we find out if there's any kind of difference between long-cycle, degree oriented institutions (universities) and vocational/professionally oriented institutions (elsewhere known as "polytechnics" or "vocational training" institutions, in Spain known as high schools).
 

### 2021-06-19 edubots_surveys.Rnw
adds descriptive statistical analysis refs #13 refs #24

--- 2021-06-19 edubots_surveys.Rnw
@@
 library(tidyverse)
+library(corrplot)
 
@@
 
-A few relevant facts from the collected data: teachers with 16-25 years of experience seem more worried about the security of messaging apps and teachers with up to 5 years of experience were more open to adopt messaging apps due to the pandemic; female teachers were more willing to adopt new platforms due to the pandemic, and even to start using safer alternatives; finally, university teachers that did not use them were more reluctant to start using them after the pandemic.
+%A few relevant facts from the collected data: teachers with 16-25 years of experience seem more worried about the security of messaging apps and teachers with up to 5 years of experience were more open to adopt messaging apps due to the pandemic; female teachers were more willing to adopt new platforms due to the pandemic, and even to start using safer alternatives; finally, university teachers that did not use them were more reluctant to start using them after the pandemic.
 
@@
 \label{figure:chatbots_use_postcovid}
+\end{figure}
+
+The descriptive analysis in this case is done using a Chi-square test.
+For the different variables considered, some statistical significance was found for Gender, Sector, and academic Discipline.
+The values found with the test are: $p-value=0.0034$ for Gender, $p-value=0.0440$ for Sector, and $p-value=0.0180$ for Discipline.
+The first column in Fig.
+\ref{figure:postcovid_chisq} shows the Pearson's residuals of the test for these three variables.
+Residuals show the difference between the observed and the expected values, with large residuals showing that variables are not truly independent.
+In this case, blue shows positive contribution and red negative contribution to the test, and saturation shows how large is this contribution in contrast to the expected value by chance.
+Tables on the right side show adjusted standardized residuals that according to \cite{agresti2013categorical}, if greater than +/-2 for cases with few cells, indicate lack of fit of $H_0$ (bolded in our table).
+Also, the table shows the percentage of contribution to the test of each cell.
+
+\begin{figure}[h!tbp]
+\begin{center}
+    \begin{minipage}[c]{0.45\textwidth}
+        \centering
+<<gender_postcovid_chisq, echo=FALSE, fig.width=17/2.54, fig.height=10/2.54>>=
+df <-select(survey.pilot.postCOVID, PostCOVID.changes, Gender, Sector, Experience, Discipline)
+df[as.character(df$Gender)!="PNTS", ] -> df1
+survey.pilot.postCovidChisq<- droplevels(df1)
+
+covidChanges.vs.Gender<-table(survey.pilot.postCovidChisq$Gender, survey.pilot.postCovidChisq$PostCOVID.changes)
+colnames(covidChanges.vs.Gender)<- c("Did/do", "Didn't/do","safer", "Didn't/don't")
+chisq<-chisq.test(covidChanges.vs.Gender)
+corrplot(chisq$residuals, is.corr = FALSE)
+@
+    \end{minipage}
+    \begin{minipage}[c]{0.45\textwidth}
+        \centering
+    \resizebox{\textwidth}{!}{%
+    \begin{tabular}{l|r|r|r|r|}
+    \cline{2-5}
+                                 & Did/Do & Didn't/Do & Safer  & Didn' t/Don't \\ \hline
+    \multicolumn{1}{|l|}{Female} & \textbf{-2.776} & \textbf{2.637} & \textbf{2.028}  & -1.159 \\ 
+    \multicolumn{1}{|l|}{} & 14.48\% & \textbf{27.48\%} &  16.46\% & 5.75\% \\ \hline
+    \multicolumn{1}{|l|}{Male}   & \textbf{2.776} & \textbf{-2.637} & \textbf{-2.028} & 1.159 \\ 
+    \multicolumn{1}{|l|}{} &  8.08\% &  \textbf{15.34\%} & 9.19\% &  3.21\% \\ \hline
+    \end{tabular}%
+    }
+    \end{minipage}
+    \begin{minipage}[c]{0.45\textwidth}
+        \centering
+<<sector_postcovid_chisq, echo=FALSE, fig.width=17/2.54, fig.height=10/2.54, warning=FALSE>>=
+covidChanges.vs.Sector<-table(survey.pilot.postCovidChisq$Sector, survey.pilot.postCovidChisq$PostCOVID.changes)
+colnames(covidChanges.vs.Sector)<- c("Did/do", "Didn't/do","safer", "Didn't/don't")
+chisq<-chisq.test(covidChanges.vs.Sector)
+corrplot(chisq$residuals, is.corr = FALSE)
+@
+    \end{minipage}
+    \begin{minipage}[c]{0.45\textwidth}
+        \centering
+    \resizebox{\textwidth}{!}{%
+    \begin{tabular}{l|r|r|r|r|}
+    \cline{2-5}
+                                 & Did/Do & Didn't/Do & Safer  & Didn' t/Don't \\ \hline
+    \multicolumn{1}{|l|}{University} & -1.895 & 0.397 & 0.049  &  \textbf{2.679}\\ 
+    \multicolumn{1}{|l|}{University} & 5.81\% & 0.54\% & 0.01\%  &  \textbf{26.48\%}\\ \hline
+    \multicolumn{1}{|l|}{Vocational} & -1.895 & -0.397 & -0.049 & \textbf{-2.679}\\ 
+    \multicolumn{1}{|l|}{Vocational} & 11.88\% & 1.10\% & 0.02\% & \textbf{54.17\%}\\ \hline
+    \end{tabular}%
+    }
+    \end{minipage}
+    \begin{minipage}[c]{0.45\textwidth}
+        \centering
+<<discipline_postcovid_chisq, echo=FALSE, fig.width=17/2.54, fig.height=10/2.54, warning=FALSE>>=
+survey.pilot.postCovidChisq %>%mutate(Discipline = ifelse(as.character(Discipline) == "No", "Hum/Social Sciences", as.character(Discipline))) %>%
+  mutate(Discipline = ifelse(as.character(Discipline) == "Other", "Hum/Social Sciences", as.character(Discipline))) %>%
+  mutate(Discipline = ifelse(as.character(Discipline) == "Engineering", "Tech/Engineering", as.character(Discipline))) %>%
+  mutate(Discipline = ifelse(as.character(Discipline) == "Technology", "Tech/Engineering", as.character(Discipline))) %>%
+  mutate(Discipline = ifelse(as.character(Discipline) == "Humanities", "Hum/Social Sciences", as.character(Discipline))) %>%
+  mutate(Discipline = ifelse(as.character(Discipline) == "Social Sciences", "Hum/Social Sciences", as.character(Discipline))) %>%
+  mutate(Discipline = ifelse(as.character(Discipline) == "Sciences", "Biomed/Sciences", as.character(Discipline))) %>%
+  mutate(Discipline = ifelse(as.character(Discipline) == "Biomedicine", "Biomed/Sciences", as.character(Discipline)))->survey.pilot.postCovidChisq
+covidChanges.vs.Discipline<-table(survey.pilot.postCovidChisq$Discipline, survey.pilot.postCovidChisq$PostCOVID.changes)
+colnames(covidChanges.vs.Discipline)<- c("Did/do", "Didn't/do","safer", "Didn't/don't")
+chisq<-chisq.test(covidChanges.vs.Discipline)
+corrplot(chisq$residuals, is.corr = FALSE)
+@
+    \end{minipage}
+    \begin{minipage}[c]{0.45\textwidth}
+        \centering
+    \resizebox{\textwidth}{!}{%
+    \begin{tabular}{l|r|r|r|r|}
+    \cline{2-5}
+                                 & Did/Do & Didn't/Do & Safer & Didn' t/Don't \\ \hline
+    \multicolumn{1}{|l|}{Biomed/Sciences} & -1.202 &  0.715 & 1.424 & -0.635 \\ 
+    \multicolumn{1}{|l|}{Biomed/Sciences} & 3.12\% &  2.32\% & 9.34\% & 1.99\% \\ \hline
+    \multicolumn{1}{|l|}{Hum/Social} &  \textbf{-2.869} & \textbf{2.069} &  1.592 & 0.274\\ 
+    \multicolumn{1}{|l|}{Hum/Social} &  16.58\% & \textbf{18.13\%} &  10.88\% & 0.35\%\\ \hline
+    \multicolumn{1}{|l|}{Tech/Engineering} &  \textbf{3.382} &  \textbf{-2.322} &  \textbf{-2.461} & 0.254\\ 
+    \multicolumn{1}{|l|}{Tech/Engineering} &  11.92\% &  11.80\% &  \textbf{13.43\%} & 0.15\%\\ \hline
+    \end{tabular}%
+    }
+    \end{minipage}
+\end{center}
+    \caption{.}
+\label{figure:postcovid_chisq}
 \end{figure}

### 2021-06-19 scripts/process.R

@@ -8,27 +8,27 @@ library(ggthemes)
 data <- read.csv("../data/survey-pilot-3-EN.csv")
 
 ggplot(data, aes(x = WhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
-ggsave('../figures/sector_whatsapp.pdf', width = 100, height = 70, units = "mm")
+#ggsave('../figures/sector_whatsapp.pdf', width = 100, height = 70, units = "mm")
 ggplot(data, aes(x = Telegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
-ggsave('../figures/sector_telegram.pdf', width = 100, height = 70, units = "mm")
+#ggsave('../figures/sector_telegram.pdf', width = 100, height = 70, units = "mm")
 ggplot(data, aes(x = Provided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
-ggsave('../figures/sector_provided.pdf', width = 100, height = 70, units = "mm")
+#ggsave('../figures/sector_provided.pdf', width = 100, height = 70, units = "mm")
 
 
 ggplot(data, aes(x = WhatsApp, group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age)+ theme(axis.title.y=element_blank())
-ggsave('../figures/age_whatsapp.pdf', width = 100, height = 70, units = "mm")
+#ggsave('../figures/age_whatsapp.pdf', width = 100, height = 70, units = "mm")
[…]

### 2021-06-19 edubots_surveys.Rnw
Adding Declarations section

@@
   email={jmerelo@ugr.es}   % email address
-]{\inits{J.J.}\fnm{Juan J.} \snm{Merelo}}
+]{\inits{J.J.M.}\fnm{Juan J.} \snm{Merelo}}
 \author[
@@
   email={pacv@ugr.es}   % email address
-]{\inits{P.A.}\fnm{Pedro A.} \snm{Castillo}}
+]{\inits{P.A.C.}\fnm{Pedro A.} \snm{Castillo}}
 \author[
@@
   email={amorag@ugr.es}
-]{\inits{A.M.G}\fnm{Antonio M.} \snm{Mora}}
+]{\inits{A.M.M}\fnm{Antonio M.} \snm{Mora}}
 \author[
@@
   email={fbarranco@ugr.es}
-]{\inits{F.}\fnm{Francisco} \snm{Barranco}}
+]{\inits{F.B.}\fnm{Francisco} \snm{Barranco}}
 \author[
@@
   email={n.h.abbas@leeds.ac.uk}
-]{\inits{N.}\fnm{Noorhan} \snm{Abbas}}
+]{\inits{N.A.}\fnm{Noorhan} \snm{Abbas}}
+
+% Antonio - Olia and Alberto are missing. ;)
 
@@
 @
+
+% ********************** INTRODUCTION ****************************
 
@@
 
+% ********************** METHODOLOGY ****************************
+
 \section{Methodology}
@@
 \section{Conclusions}
+\label{sec:concl}
 
@@
 
-\section*{Acknowledgements}%% if any
+% ********************** DECLARATIONS ****************************
+
+\section{Declarations}
+\label{sec:decl}
+
+\subsection{Availability of data and materials}
+
+The datasets generated and analysed during the current study are available in the [NAME] repository, accesible from [PERSISTENT WEB LINK TO DATASETS]
+
+\subsection{Competing interests}
+
+The authors declare that they have no competing interests.
+
+% Antonio - If there is any, please indicate.
+
+\subsection{Funding}
 
@@
 
+\subsection{Authors' contributions}
+
+All the authors have contributed to the study presented in this manuscript. 
+JJM has been the leader...
+PAC has...
+AMM has ...
+FB has...
+NA has...
+OT has...
+AG has...
+All authors read and approved the final manuscript.
+
+% Antonio - here we can explain what we have done author briefly.
+
+\subsection{Acknowledgements}
+
+The authors want to thank to the educators who participated in the survey.
+% Antonio - Add other acknowledgements
+
 \end{backmatter}

### 2021-06-19 edubots_surveys.Rnw
Settig initials following journal indications

@@
   email={jmerelo@ugr.es}   % email address
-]{\inits{J.J.M.}\fnm{Juan J.} \snm{Merelo}}
+]{\inits{JJM}\fnm{Juan J.} \snm{Merelo}}
 \author[
@@
   email={pacv@ugr.es}   % email address
-]{\inits{P.A.C.}\fnm{Pedro A.} \snm{Castillo}}
+]{\inits{PAC}\fnm{Pedro A.} \snm{Castillo}}
 \author[
@@
   email={amorag@ugr.es}
-]{\inits{A.M.M}\fnm{Antonio M.} \snm{Mora}}
+]{\inits{AMM}\fnm{Antonio M.} \snm{Mora}}
 \author[
@@
   email={fbarranco@ugr.es}
-]{\inits{F.B.}\fnm{Francisco} \snm{Barranco}}
+]{\inits{FB}\fnm{Francisco} \snm{Barranco}}
 \author[
@@
   email={n.h.abbas@leeds.ac.uk}
-]{\inits{N.A.}\fnm{Noorhan} \snm{Abbas}}
+]{\inits{NA}\fnm{Noorhan} \snm{Abbas}}
 

### 2021-06-19 scripts/translate.py
translates last columns closes #12

@@ -39,11 +39,15 @@ data = data.replace("Un grupo para el curso completo (profesores y estudiantes)"
 data = data.replace("Un grupo para toda la titulación o instituto (profesores y estudiantes)", "A chat with all the students and teachers in the same studies (all years)")
 data = data.replace("Un grupo para toda la titulación, Facultad o Escuela (profesores y estudiantes)", "A chat with all the students and teachers in my Faculty/School")
 
+
+#Degrees
+data = data.replace("Grado", "Undergrad")
+data = data.replace("Máster", "Master")
+data = data.replace("Doctorado", "PhD")
+data = data.replace("Títulos propios", "University expert course")
+
 with open("../data/survey-pilot-3-EN.csv","w") as file:
      file.write(data)
-
-
-
 
 data = ""
 
@@ -74,6 +78,14 @@ data = data.replace("Tecnología/Ingeniería", "Tech/Engineering")
 #Interaction
 data = data.replace("Asíncrona: el estudiante puede preguntar en cualquier momento, el profesorado contesta cuando puede.", "Asynch.")
 data = data.replace("Síncrona: estudiantes(s) y profesor(es) en el mismo espacio, simultáneamente.", "Synch.")
+
+#Interaction Officiality
+data = data.replace('""oficiales""', "oficiales")
+data = data.replace('""corporativo""', "corporativo")
+data = data.replace('""extraoficiales""', "extraoficiales")
+data = data.replace("Por medios oficiales: visitas al despacho, foros/mensajes en el campus virtual, correo electrónico corporativo", "By official means: office hours, messages in the official virtual campus, or email")
+data = data.replace("Admite el uso de medios extraoficiales: blogs, grupos en programas de mensajería, otros medios", "Admits additional means: blogs, messaging apps, others")
+
 
 with open("../data/survey-student-interaction-pilot-3-2021-EN.csv","w") as file:
      file.write(data)

### 2021-06-20 scripts/parse_spss.py
adds script for spss analysis refs #24

@@ -1,0 +1,32 @@
+data = ""
+
+with open("../data/survey-student-interaction-pilot-3-2021.csv") as file:
+     data = file.read()
+
+#Age
+data = data.replace("Más de 55", "> 55")
+
+#Experience 
+data = data.replace("0-5 años", "0-05 years")
+data = data.replace("5-15 años", "06-15 years")
+data = data.replace("15-25 años", "16-25 years")
+data = data.replace("más de 25 años", "> 25 years")
+
+#Gender
+data = data.replace("Hombre", "Male")
+data = data.replace("Mujer", "Female")
+data = data.replace("Prefiero no decirlo", "PNTS")
+
+#Discipline
+data = data.replace("Biosanitaria", "Biomedicine")
+data = data.replace("Ciencias Sociales", "Social Sciences")
+data = data.replace("Ciencias", "Sciences")
+data = data.replace("Humanidades", "Humanities")
+data = data.replace("Tecnología/Ingeniería", "Tech/Engineering")
+
+#Interaction
+data = data.replace("Asíncrona: el estudiante puede preguntar en cualquier momento, el profesorado contesta cuando puede.", "Asynch.")
+data = data.replace("Síncrona: estudiantes(s) y profesor(es) en el mismo espacio, simultáneamente.", "Synch.")
+
+with open("../data/survey-student-interaction-pilot-3-2021-EN.csv","w") as file:
+     file.write(data)

### 2021-06-20 scripts/translate.py
fixes translation

@@ -44,7 +44,7 @@ data = data.replace("Un grupo para toda la titulación, Facultad o Escuela (prof
 data = data.replace("Grado", "Undergrad")
 data = data.replace("Máster", "Master")
 data = data.replace("Doctorado", "PhD")
-data = data.replace("Títulos propios", "University expert course")
+data = data.replace("Títulos propios", "Non-official degree")
 
 with open("../data/survey-pilot-3-EN.csv","w") as file:
      file.write(data)

### 2021-06-20 edubots_surveys.Rnw
adapts to new data format fixing errors in generation closes #29

@@
 
-survey.pilot %>%  mutate(ChatbotType = ifelse(Agenda == "No","","Agenda,")) %>%
-  mutate(ChatbotType = ifelse(ClassMaterial == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "ClassMaterial,",sep=""))) %>%
-  mutate(ChatbotType = ifelse(FAQ == "No",paste(ChatbotType, "",sep=""), paste(ChatbotType, "FAQ,",sep=""))) %>%
-  mutate(ChatbotType = ifelse(Grades == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "Grades,",sep=""))) %>%
+survey.pilot %>%  mutate(ChatbotType = ifelse(AgendaBot == "No","","AgendaBot,")) %>%
+  mutate(ChatbotType = ifelse(ClassMaterialBot == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "ClassMaterialBot,",sep=""))) %>%
+  mutate(ChatbotType = ifelse(FAQBot == "No",paste(ChatbotType, "",sep=""), paste(ChatbotType, "FAQBot,",sep=""))) %>%
+  mutate(ChatbotType = ifelse(GradesBot == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "GradesBot,",sep=""))) %>%
   mutate(ChatbotType = ifelse(OtherBot == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "OtherBot,",sep=""))) %>%
@@
 survey.interaction %>% group_by( Experience ) %>% summarise ( n = n() ) %>% mutate( freqExperience = n/sum(n)) -> freqInteraction.Experience
-survey.interaction %>% group_by( Vocational ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freqInteraction.Sector
-freqInteraction.Sector$Sector <- freqInteraction.Sector$Vocational
-freqInteraction.Sector %>% mutate(Sector = ifelse(as.character(Vocational) == "Yes", "Vocational", "University")) -> freqInteraction.Sector
-freqInteraction.Sector <- freqInteraction.Sector[-c(1)]
+
+#survey.interaction %>% group_by( Vocational ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freqInteraction.Sector
+#freqInteraction.Sector$Sector <- freqInteraction.Sector$Vocational
+#freqInteraction.Sector %>% mutate(Sector = ifelse(as.character(Vocational) == "Yes", "Vocational", "University")) -> freqInteraction.Sector
+#freqInteraction.Sector <- freqInteraction.Sector[-c(1)]
+survey.interaction %>%  mutate(Sector = ifelse(DegreesVocational == "No","","Vocational,")) %>%
+  mutate(Sector = ifelse(Sector == "No", paste(Sector, "",sep=""), paste(Sector, "University,",sep=""))) %>%
+  mutate(Sector = substr(Sector,1,nchar(Sector)-1))-> df1
+df1 %>%  mutate(Sector =str_split(Sector, ",")) %>% unnest(cols = c(Sector)) -> df1.Sector
+df1.Sector %>% group_by( Sector ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freqInteraction.Sector
+
 survey.interaction %>% group_by( Discipline ) %>% summarise ( n = n() ) %>% mutate( freqDiscipline = n/sum(n)) -> freqInteraction.Discipline
@@
 <<gender_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = Provided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
 @
@@
 <<experience_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = Provided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
 @       
@@
 <<sector_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = Provided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
 @       
@@
 
-ggplot(survey.pilot.Discipline, aes(x = Provided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformProvided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
 @
@@
 <<gender_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = WhatsApp, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot, aes(x = MessagingPlatformWhatsApp, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
 @
@@
 <<experience_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = WhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot, aes(x = MessagingPlatformWhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
 @       
@@
 <<sector_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = WhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot, aes(x = MessagingPlatformWhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
 @       
@@
 <<discipline_whatsapp, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot.Discipline, aes(x = WhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformWhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
 @
@@
 <<gender_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = Telegram, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot, aes(x = MessagingPlatformTelegram, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
 @
@@
 <<experience_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = Telegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot, aes(x = MessagingPlatformTelegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
 @       
@@
 <<sector_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = Telegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot, aes(x = MessagingPlatformTelegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
 @       
@@
 <<discipline_telegram, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot.Discipline, aes(x = Telegram, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformTelegram, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
 @
@@
 For the different variables considered, some statistical significance was found for Gender, Sector, and academic Discipline.
-The values found with the test are: $p-value=0.0034$ for Gender, $p-value=0.0440$ for Sector, and $p-value=0.0180$ for Discipline.
+The values found with the test are: $p-value=0.0034$ for Gender, $p-value=0.0199$ for Sector, and $p-value=0.0211$ for Discipline.
 The first column in Fig.
@@
 df[as.character(df$Gender)!="PNTS", ] -> df1
+df1[as.character(df1$Gender)!="No", ] -> df1
+df1[as.character(df1$Discipline)!="No", ] -> df1
+df1[as.character(df1$Experience)!="No", ] -> df1
+df1[as.character(df1$Sector)!="No", ] -> df1
 survey.pilot.postCovidChisq<- droplevels(df1)
@@
     \end{minipage}
+    %This tables comes from (TODO: generate them automatically from the data)
+    %contrib <- 100*chisq$residuals^2/chisq$statistic
+    %round(contrib, 2)
+    %round(chisq$stdres, 3)
     \begin{minipage}[c]{0.45\textwidth}
@@
                                  & Did/Do & Didn't/Do & Safer  & Didn' t/Don't \\ \hline
-    \multicolumn{1}{|l|}{Female} & \textbf{-2.776} & \textbf{2.637} & \textbf{2.028}  & -1.159 \\ 
-    \multicolumn{1}{|l|}{} & 14.48\% & \textbf{27.48\%} &  16.46\% & 5.75\% \\ \hline
-    \multicolumn{1}{|l|}{Male}   & \textbf{2.776} & \textbf{-2.637} & \textbf{-2.028} & 1.159 \\ 
-    \multicolumn{1}{|l|}{} &  8.08\% &  \textbf{15.34\%} & 9.19\% &  3.21\% \\ \hline
+    \multicolumn{1}{|l|}{Female} & \textbf{-2.850} & \textbf{2.806} & 1.832  & -1.011 \\ 
+    \multicolumn{1}{|l|}{} & 15.15\% & \textbf{31.21\%} &  13.49\% & 4.40\% \\ \hline
+    \multicolumn{1}{|l|}{Male}   & \textbf{2.850} & \textbf{-2.806} & -1.832 & 1.011 \\ 
+    \multicolumn{1}{|l|}{} &  8.43\% &  \textbf{17.36\%} & 7.50\% &  2.45\% \\ \hline
     \end{tabular}%
@@
                                  & Did/Do & Didn't/Do & Safer  & Didn' t/Don't \\ \hline
-    \multicolumn{1}{|l|}{University} & -1.895 & 0.397 & 0.049  &  \textbf{2.679}\\ 
-    \multicolumn{1}{|l|}{University} & 5.81\% & 0.54\% & 0.01\%  &  \textbf{26.48\%}\\ \hline
-    \multicolumn{1}{|l|}{Vocational} & -1.895 & -0.397 & -0.049 & \textbf{-2.679}\\ 
-    \multicolumn{1}{|l|}{Vocational} & 11.88\% & 1.10\% & 0.02\% & \textbf{54.17\%}\\ \hline
+    \multicolumn{1}{|l|}{University} & \textbf{-2.122} & 0.454 & 0.115  &  \textbf{2.939}\\ 
+    \multicolumn{1}{|l|}{University} & 5.71\% & 0.56\% & 0.04\%  &  \textbf{25.26\%}\\ \hline
+    \multicolumn{1}{|l|}{Vocational} & \textbf{2.122} & -0.454 & -0.115 & \textbf{-2.939}\\ 
+    \multicolumn{1}{|l|}{Vocational} & 12.38\% & 1.21\% & 0.08\% & \textbf{54.78\%}\\ \hline
     \end{tabular}%
@@
                                  & Did/Do & Didn't/Do & Safer & Didn' t/Don't \\ \hline
-    \multicolumn{1}{|l|}{Biomed/Sciences} & -1.202 &  0.715 & 1.424 & -0.635 \\ 
-    \multicolumn{1}{|l|}{Biomed/Sciences} & 3.12\% &  2.32\% & 9.34\% & 1.99\% \\ \hline
-    \multicolumn{1}{|l|}{Hum/Social} &  \textbf{-2.869} & \textbf{2.069} &  1.592 & 0.274\\ 
-    \multicolumn{1}{|l|}{Hum/Social} &  16.58\% & \textbf{18.13\%} &  10.88\% & 0.35\%\\ \hline
-    \multicolumn{1}{|l|}{Tech/Engineering} &  \textbf{3.382} &  \textbf{-2.322} &  \textbf{-2.461} & 0.254\\ 
-    \multicolumn{1}{|l|}{Tech/Engineering} &  11.92\% &  11.80\% &  \textbf{13.43\%} & 0.15\%\\ \hline
+    \multicolumn{1}{|l|}{Biomed/Sciences} & -1.265 &  0.733 & 1.452 & -0.588 \\ 
+    \multicolumn{1}{|l|}{Biomed/Sciences} & 3.50\% &  2.50\% & 9.94\% & 1.75\% \\ \hline
+    \multicolumn{1}{|l|}{Hum/Social} &  \textbf{-2.729} & \textbf{2.079} &  1.566 & 0.055\\ 
+    \multicolumn{1}{|l|}{Hum/Social} &  15.55\% & \textbf{19.19\%} &  11.04\% & 0.01\%\\ \hline
+    \multicolumn{1}{|l|}{Tech/Engineering} &  \textbf{3.278} &  \textbf{-2.318} &  \textbf{-2.448} & 0.412\\ 
+    \multicolumn{1}{|l|}{Tech/Engineering} &  11.06\% &  11.76\% &  \textbf{13.29\%} & 0.40\%\\ \hline
     \end{tabular}%

### 2021-06-20 scripts/process.R

@@ -7,27 +7,27 @@ library(ggthemes)
 # data <- read.csv("../data/survey-pilot-3.csv")
 data <- read.csv("../data/survey-pilot-3-EN.csv")
 
-ggplot(data, aes(x = WhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+ggplot(data, aes(x = MessagingPlatformWhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
 #ggsave('../figures/sector_whatsapp.pdf', width = 100, height = 70, units = "mm")
-ggplot(data, aes(x = Telegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+ggplot(data, aes(x = MessagingPlatformTelegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
 #ggsave('../figures/sector_telegram.pdf', width = 100, height = 70, units = "mm")
-ggplot(data, aes(x = Provided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+ggplot(data, aes(x = MessagingPlatformProvided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
[…]

### 2021-06-20 scripts/summaries.R

@@ -26,6 +26,14 @@ ggplot(Age.vs.Experience,aes(Age,Experience))+geom_point(aes(size=freq),colour="
 survey.interaction %>% group_by( Gender ) %>% summarise ( n = n() ) %>% mutate( freqGender = n/sum(n)) -> freqInteraction.Gender
 survey.interaction %>% group_by( Age ) %>% summarise ( n = n() ) %>% mutate( freqAge = n/sum(n)) -> freqInteraction.Age
 survey.interaction %>% group_by( Experience ) %>% summarise ( n = n() ) %>% mutate( freqExperience = n/sum(n)) -> freqInteraction.Experience
+
+
+survey.interaction %>%  mutate(Sector = ifelse(DegreesVocational == "No","","Vocational,")) %>%
+  mutate(Sector = ifelse(Sector == "No", paste(Sector, "",sep=""), paste(Sector, "University,",sep=""))) %>%
+  mutate(Sector = substr(Sector,1,nchar(Sector)-1))-> df1
+df1 %>%  mutate(Sector =str_split(Sector, ",")) %>% unnest(cols = c(Sector)) -> df1.Sector
+df1.Sector %>% group_by( Sector ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freqInteraction.Sector
+
 survey.interaction %>% group_by( Sector ) %>% summarise ( n = n() ) %>% mutate( freqSector = n/sum(n)) -> freqInteraction.Sector
 survey.interaction %>% group_by( Discipline ) %>% summarise ( n = n() ) %>% mutate( freqDiscipline = n/sum(n)) -> freqInteraction.Discipline
 

### 2021-06-21 scripts/parse_spss.py
this time does add script for spss analysis refs #24

@@ -1,32 +1,45 @@
 data = ""
 
-with open("../data/survey-student-interaction-pilot-3-2021.csv") as file:
+with open("survey-student-interaction-pilot-3-2021.csv") as file:
      data = file.read()
 
+#Binary (Yes/No)
+data = data.replace("Yes", "1")
+data = data.replace("No", "2")
+
 #Age
-data = data.replace("Más de 55", "> 55")
+data = data.replace("25-35", "1")
+data = data.replace("35-45", "2")
+data = data.replace("45-55", "3")
+data = data.replace("Más de 55", "4")
 
 #Experience 
-data = data.replace("0-5 años", "0-05 years")
-data = data.replace("5-15 años", "06-15 years")
-data = data.replace("15-25 años", "16-25 years")
-data = data.replace("más de 25 años", "> 25 years")
+data = data.replace("0-5 años", "1")
+data = data.replace("5-15 años", "2")
+data = data.replace("15-25 años", "3")
+data = data.replace("más de 25 años", "4")
 
 #Gender
-data = data.replace("Hombre", "Male")
-data = data.replace("Mujer", "Female")
-data = data.replace("Prefiero no decirlo", "PNTS")
+data = data.replace("Hombre", "1") #Male
+data = data.replace("Mujer", "2") #Female
+data = data.replace("Prefiero no decirlo", "3") #Prefer not to say
 
 #Discipline
-data = data.replace("Biosanitaria", "Biomedicine")
-data = data.replace("Ciencias Sociales", "Social Sciences")
-data = data.replace("Ciencias", "Sciences")
-data = data.replace("Humanidades", "Humanities")
-data = data.replace("Tecnología/Ingeniería", "Tech/Engineering")
+data = data.replace("Biosanitaria", "1") #Biomedicine
+data = data.replace("Ciencias Sociales", "2") #Social Sciences
+data = data.replace("Ciencias", "3") #Sciences 
+data = data.replace("Humanidades", "4") #Humanities
+data = data.replace("Tecnología/Ingeniería", "5") #Tech/Engineering
 
 #Interaction
-data = data.replace("Asíncrona: el estudiante puede preguntar en cualquier momento, el profesorado contesta cuando puede.", "Asynch.")
-data = data.replace("Síncrona: estudiantes(s) y profesor(es) en el mismo espacio, simultáneamente.", "Synch.")
[…]

### 2021-06-25 feature_selection/feature_selec.py
code for variable selection using MI

@@ -1,0 +1,229 @@
+'''
+Performs feature selection considering output variable CoVid changes  
+'''
+
+
+
+
+def preprocess_datos(datos):
+
+    '''
+    tWO OUTLIERS REMOVED... (rows 203 y 230)
+    AgendaBot	            : 1-> Yes 0-> No
+    ClassMaterialBot        : 1-> Yes 0-> No
+    Age                         :	1 -> 25-35 2-> 35-45 3->45-55 4-> >55
+    Experience                  : 1-> 0-05 years   2-> 06-15 years   3-> 16-25 years   4-> >25
+    FAQBot                       :	1-> Yes 0-> No
+    GradesBot               	:	1-> Yes 0-> No
+    Gender                  	: 1 Male   2 PNTS  3 Female
+    MessagingPlatformNone		:	1-> Yes 0-> No
+    MessagingPlatformOther		:	1-> Yes 0-> No
+    MessagingPlatformProvided	:	1-> Yes 0-> No	
+    MessagingPlatformSlack	    :	1-> Yes 0-> No	
+    MessagingPlatformTelegram	:	1-> Yes 0-> No	
+    MessagingPlatformWhatsApp	:	1-> Yes 0-> No	
+    OtherBot	            	:	1-> Yes 0-> No
+    Sector	                    :   1-> University 2 -> Vocational
+    Messaging Organization->Number of approaches considered
+                        	    : 0-> I'd rather leave students self-organize and not be part of the chat
+                                : 1-> A chat with my students in the same course / A chat with all students and teachers in the same semester/year
+                                : >1 = sum of answers (considering 1, 0 and others for example 2 for 1,0 or 3 for 1,0,1)
+
+    Degrees -> Number of degrees involved : 	
+    Discipline          : 0-> No  1-> engineering, technology 2-> Science, Biomedicine 3-> Social Science 4-> Humanities
+    PostCOVID changes	        : 1 -> Yes, now they use it or use it more or in a safer/different way 0 -> No change in use -> -1 No change in not using 
+
+'''
+
+import numpy as np
+
+from scipy.special import gamma,psi
+from scipy import ndimage
+from scipy.linalg import det
+from numpy import pi
+
+from sklearn.neighbors import NearestNeighbors
+
+__all__=['entropy', 'mutual_information', 'entropy_gaussian']
+
+EPS = np.finfo(float).eps
+
+
[…]

### 2021-06-25 feature_selection/feature_selec.py
moved code to notebook and added references

@@ -44,7 +44,7 @@ from numpy import pi
 
 from sklearn.neighbors import NearestNeighbors
 
-__all__=['entropy', 'mutual_information', 'entropy_gaussian']
+__all__=['entropy', 'mutual_information', 'entropy_gaussian', 'nearest_distances', 'gen_all_combinations']
 
 EPS = np.finfo(float).eps
 
@@ -55,6 +55,8 @@ def nearest_distances(X, k=1):
     N = number of points
     M = number of dimensions
     returns the distance to the kth nearest neighbor for every point in X
+
+    https://gist.github.com/GaelVaroquaux/ead9898bd3c973c40429
     '''
     knn = NearestNeighbors(n_neighbors=k + 1)
     knn.fit(X)
@@ -65,6 +67,7 @@ def nearest_distances(X, k=1):
 def entropy_gaussian(C):
     '''
     Entropy of a gaussian variable with covariance matrix C
+    https://gist.github.com/GaelVaroquaux/ead9898bd3c973c40429
     '''
     if np.isscalar(C): # C is the variance
         return .5*(1 + np.log(2*pi)) + .5*np.log(C)
@@ -90,6 +93,8 @@ def entropy(X, k=1):
     and:
     Kraskov A, Stogbauer H, Grassberger P. (2004). Estimating mutual
     information. Phys Rev E 69(6 Pt 2):066138.
+
+    https://gist.github.com/GaelVaroquaux/ead9898bd3c973c40429
     '''
 
     # Distance to kth nearest neighbor
@@ -115,6 +120,8 @@ def mutual_information(variables, k=1):
     Optionally, the following keyword argument can be specified:
       k = number of nearest neighbors for density estimation
     Example: mutual_information((X, Y)), mutual_information((X, Y, Z), k=5)
+
+    https://gist.github.com/GaelVaroquaux/ead9898bd3c973c40429
     '''
     if len(variables) < 2:
         raise AttributeError(
@@ -143,87 +150,4 @@ def gen_all_combinations(n_vars):
     allperms = np.unique(allperms, axis=0)
 
     return allperms
-
-
-from sklearn.feature_selection import mutual_info_classif
-from sklearn.metrics import mutual_info_score
-import pandas as pd
-import numpy as np
-from itertools import permutations
-
-
-
-n_vars = 18
-
[…]

### 2021-06-26 edubots_surveys.Rnw
Revising abstract and Introduction

@@
 affected community, especially those that will need to handle them,
+% Antonio - I would say 'to manage them'. Students should also handle new technologies. ;)
 teachers.
 In this paper we have surveyed the opinions of tertiary education
-teachers based mainly in Spain and Spanish speaking countries, looking
-at what they think about the introduction of messaging platforms and
-chatbots, what their needs are, what kind of use cases they see for
+teachers based mainly in Spain and Spanish speaking countries, 
+% Antonio - Spanish-speaking?
+looking at what they think about the introduction 
+% Antonio - inthe classroom
+of messaging platforms and chatbots, what their needs are, what kind of use cases they see for
 them, and in what kind of environment they think its use will be
 valuable. We will examine how and when these attitudes vary across
-gender, experience, and other factors, such as the kind of discipline
+gender, experience, and other factors, such as the type of discipline
 they are teaching. Our conclusions might help with the adoption of
@@
 \kwd{Higher education}
+% Antonio - add something related to "survey", "teachers' opinion" or so?
 \end{keyword}
@@
 % TODO: introduction
-The introduction of new technologies in the classroom needs a combination of teacher education, student willingness and (possibly new) skills in both.
+The introduction of new technologies in the classroom needs a combination of teacher education, 
+% Antonio - education -> knowledge? motivation? training?
+student willingness and (possibly new) skills in both.
 Some technologies are readily adapted, but some of them take a long time to be adopted.
@@
 Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker's question fluently, and even ask other questions to the human.
-However, in most cases a simple messaging-application attached bot will help the students (and teachers); neither computational intelligence nor comprehension of natural languages are requisites, the only one being the fact that they can be accessed from a synchronous conversational application such as the common instant messaging applications used nowadays.
+However, in most cases a simple messaging-application attached bot will help the students (and teachers); so neither computational intelligence nor comprehension of natural languages are requisites, the only one being the fact that they can be accessed from a synchronous conversational application such as the common instant messaging applications (e.g.
+Telegram, WhatsApp) used nowadays.
+% Antonio - This paragraph needs a conclusion. Why do we say (essentially) that chatbots are not needed and just a simple messaging bot is enough?
 
@@
 These automatic systems ease personalized learning,
-% Antonio - customized instead personalized? we are repeating 'personalized' twice in a sentence...
-% Antonio, if you don't like something, and it's as non-controversial as this thing, just change it directly. Reviews are OK, corrections are even more OK. - JJ
-adapting individuals' pace of learning, who get personalized online tutoring outside the classroom.
+adapting individuals' pace of learning, who get customized online tutoring outside the classroom.
 Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.
@@
 This is why many students prefer to remain silent and ask their question later via email.
-However, this means a waste of time and a delay of hours or even days to get the teacher's answer; it does not scale well with the size of the class.
+However, this means a waste of time and a delay of hours or even days to get the teacher's answer; moreover, it does not scale well with the size of the class.
 Chatbot technology has a potential to fill the gap between teacher and students, helping them to solve questions and carry out a dynamic and autonomous learning \cite{Griol2014,kim2020}.
-Moreover, using an automated system such as a chatbot allows the teacher to detect the most demanded topics, and on which he or she should consequently place more emphasis in class.
+In addition, using an automated system such as a chatbot, allows the teacher to detect the most demanded topics, and on which he or she should consequently place more emphasis in class.
 
@@
 We concluded that students prefer to use known whatever messaging application, such as Telegram or WhatsApp, they are already using.
-They also they expected chatbots to help them with their scheduling, provide assignment grades and search class material.
+They also expected chatbots to help them with their scheduling, to provide assignment grades and to search for class material.
 Only one of the applications mentioned, having them work with frequently asked questions, might actually require some understanding of natural language, although it can be formulated in such a way that is not needed.
@@
 % Maybe move it to a different place later
-In the present work we aim to complement the aforementioned study with teacher attitudes; teachers are the ones that actually would need to implement, configure and maybe program chatbots.
+In the present work we aim to complement the aforementioned study with teacher attitudes; teachers are the ones that actually would need to implement, 
+% Antonio - 'deploy' instead implement? Since in Computer Sciences implement and program are synonyms...
+configure and maybe program chatbots.
 Thus, we have performed a survey among 300 teachers asking about their attitudes towards the use of bots or chatbots in their classes.

### 2021-06-26 feature_selection/feature_selec.py
import bugfix

@@ -41,6 +41,7 @@ from scipy.special import gamma,psi
 from scipy import ndimage
 from scipy.linalg import det
 from numpy import pi
+from itertools import permutations
 
 from sklearn.neighbors import NearestNeighbors
 

### 2021-06-26 edubots_surveys.Rnw
added new subsection to experiments

@@
 ]{\inits{NA}\fnm{Noorhan} \snm{Abbas}}
-
-% Antonio - Olia and Alberto are missing. ;)
+\author[
+  addressref={aff1},
+  email={aguillen@ugr.es}
+]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
+
+% Antonio - Olia is missing. ;)
 
@@
 
+% ************************ New alaysis ***********************
+
+\subsection{Data Analysis using Machine Learning}
+
+To provide a different perspective another analysis was carried out using models from the field of machine learning.
+The idea was to be able to identify which features measured in the survey could identify willingness to change.
+As chatbots are an emerging technology, it is quite probable that this new change will come sooner than later considering the improvemente in Virtual and Augmented Reality \cite{}.
+
+The output variable is set as covid-changes, whose values were grouped to three numerical classes:
+
+\begin{itemize}
+ \item 2 = Yes, now they use it or use it more or in a safer/different way 
+ \item 1 = No change in use 
+ \item 0 = No change in not using 
+\end{itemize}
+
+Regarding the rest of features, a similar preprocessing was applied to the original survey:
+
+\begin{itemize}
+\item Binary Yes/No variables like AgendaBot, ClassMaterialBot, FAQBot, GradesBot, MessagingPlatform..., OtherBot were mappped to values $\in {0,1}$ using 1 for Yes and 0 for No.
+
+\item Gender variable was mapped to: 1 for Male, 2 for PNTS and 3 for Female. In this way we keep equidistance from PNTS to the other well identified genders.
+
+\item Age and Experience were assigned valued $\in {1,2,3,4}$ where the higher number represents the older age or more years of experience.
+
+\item Sector was coded as 1 for University and 2 for Vocational.
+
+\item Messaging Organization was reinterpreted as number of approaches considered by the professors with the following values: 0 for answer of type: "I'd rather leave students self-organize and not be part of the chat" ; 1 for answers like: "A chat with my students in the same course" or "A chat with all students and teachers in the same semester/year".
+If the previous two were marked, or even another answer appeared, the sum of approaches was computed.
+By doing this, we consider a passive professor that does not want to get involved in the chat with a 0 and emphasize the active ones that give a thought on how they want to interact with students.
+
+\item Degrees feature was also reinterpreted as number of degrees involved.
+By doing this, it is possible to see with a number the range width of the professor.
+From this point, it could be possible to study if a wider range professor presents or not more intention of using chatbots (independently of the degree level).
+
+\item Finally, Discipline was grouped into the following categories: 0 for No  1 for Engineering and Technology 2 for Science and Biomedicine ; 3 for Social Science and 4 for Humanities.
+By doing this we keep a similarity criterion just by computing the distance between disciplines.
+
+\end{itemize}
+
+The
+
 % ********************** CONCLUSIONS ****************************

### 2021-06-26 edubots_surveys.Rnw
added table for var reference
added two subsections for MI and xgboost

@@
 
-The
+The reference mapping for the feature names in the experiments is in Table \ref{tab:feature_mapping}.
+
+\begin{table}
+
+\begin{tabular}{|c|c|}
+\hline
+\# Variable & Name \\
+\hline
+0 & AgendaBot	\\
+1 & ClassMaterialBot		\\
+2 & Age		\\
+3 & Experience		\\
+4 & FAQBot		\\
+5 & GradesBot		\\
+6 & Gender		\\
+7 & MessagingPlatform0ne		\\
+8 & MessagingPlatformOther		\\
+9 & MessagingPlatformProvided		\\
+10 & MessagingPlatformSlack		\\
+11 & MessagingPlatformTelegram		\\
+12 & MessagingPlatformWhatsApp		\\
+13 & OtherBot		\\
+14 & Sector		\\
+15 & Messaging Organization → Number of approaches considered		\\
+16 & Degrees → Number of degrees involved		\\
+17 & Discipline		\\
+\hline
+Output & PostCOVID changes	\\
+\hline
+\end{tabular} \label{tab:feature_reference} \caption{Mapping of feature numbers to survey questions.}
+\end{table}
+
+\subsubsection{Using Mutual Information and Neural Networks}
+
+The intuitive idea for Mutual Information (MI) is the amount of information about a variable that another variable, or group of variables, has.
+Therefore, setting as goal the capability of predicting the COVID changes, it is possible to detect the most relevant variables.
+Several approaches can be taken to select a subset of variables that contain enough information to reconstruct the output \cite{}.
+For this study, the estimation of the mutual information provided by the SKlearn package \cite{} and the algorithm mMRM \cite{} are considered.
+
+As the evaluation of all possible combinations might be unfeasible from a computational point of view, the following heuristic was applied: rank the variables using the MI of that variable isolatedly, apply a threshold to discard the ones with smaller MI and then, make a exhaustive search for the combination with higher MI.
+
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\# Variable & Name & MI (considering one variable) & Max Relevance & mRMR\\
+\hline
+0 & AgendaBot	&  &  &\\
+1 & ClassMaterialBot &	&  &	\\
+2 & Age	&		&  &  \\
+3 & Experience &			&  &  	\\
+4 & FAQBot &			&  &  	\\
+5 & GradesBot &			&  &  	\\
+6 & Gender &			&  &  	\\
+7 & MessagingPlatform0ne &			&  &  	\\
+8 & MessagingPlatformOther &			&  &  	\\
+9 & MessagingPlatformProvided	&			&  &  \\
+10 & MessagingPlatformSlack	&			&  &  \\
+11 & MessagingPlatformTelegram	&			&  &  \\
+12 & MessagingPlatformWhatsApp	&			&  &  \\
+13 & OtherBot	&			&  &  \\
+14 & Sector	&			&  &  \\
+15 & Messaging Organization → Number of approaches considered	&			&  &  \\
+16 & Degrees → Number of degrees involved	&			&  &  \\
+17 & Discipline	&		&  &  	\\
+\hline
+Output & \multirow{3}{PostCOVID changes} 	\\
+\hline
+\end{tabular} \label{tab:feature_reference} \caption{Mapping of feature numbers to survey questions.}
+\end{table}
+
+\subsubsection{Using XGBoost}
+
+Due to the lack of data, estimators based on $k$-Nearest Neighbours might be unreliable, thus, another approach can be used: decision trees build during their design process a relevance of the variables that, after being used to take the decision, decrease in a significant way the error.
+Therefore, the well known implementation of the XGBoost was used to obtain the accuracy and the feature relevance.
 

### 2021-06-26 edubots_surveys.Rnw
added xgboost results figure

@@
 
-As the evaluation of all possible combinations might be unfeasible from a computational point of view, the following heuristic was applied: rank the variables using the MI of that variable isolatedly, apply a threshold to discard the ones with smaller MI and then, make a exhaustive search for the combination with higher MI.
+As the evaluation of all possible combinations might be unfeasible from a computational point of view, the following heuristic was applied: rank the variables using the MI of that variable isolated, apply a threshold to discard the ones with smaller MI and then, make a exhaustive search for the combination with higher MI.
 
@@
 \hline
-\end{tabular} \label{tab:feature_reference} \caption{Mapping of feature numbers to survey questions.}
+\end{tabular} \label{tab:feature_results} \caption{Mapping of feature numbers to survey questions.}
 \end{table}
@@
 Due to the lack of data, estimators based on $k$-Nearest Neighbours might be unreliable, thus, another approach can be used: decision trees build during their design process a relevance of the variables that, after being used to take the decision, decrease in a significant way the error.
-Therefore, the well known implementation of the XGBoost was used to obtain the accuracy and the feature relevance.
+Therefore, the well known implementation of the XGBoost \cite{} was used to obtain the accuracy and the feature relevance.
+
+The feature ranking results are shown in Figure \ref{fig:feature_xgboost}.
+\begin{figure}
+\includegraphics{figs/feature_xgboost.png}
+\label{fig:feature_xgboost}\caption{Ranking of features obtained after using XGBoost model.}
+\end{figure}
 

### 2021-06-27 edubots_surveys.Rnw
Reviewing State of the Art

@@
 Given the potential advantages that chatbots could bring to the classroom, as a previous step, we created two surveys for bachelor and master degree students at the University of Granada (Spain), which were answered by more than 250 students.
-The obtained results were analysed with the object of identifying students' actual needs, in \cite{MoraChatbos2021}.
+The obtained results were analysed with the object of identifying students' actual needs, in \cite{MoraChatbots2021}.
 The survey asked about their preferences on tools/applications for chatting and messaging, how do they use them in the educational context, who do they like to be with in the class messaging groups, and what do they expect bots and chatbots to do to aid them during their learning process.
@@
 the most popular MIM platform used by educators to give assignments'
-feedback to students, support course discussions and provide learning
-resources in informal learning settings \cite{panah2020study}.  The
+feedback to students, support course discussions, and provide learning
+resources in informal learning settings \cite{panah2020study}.  Moreover, the
 use of WhatsApp in higher education could enhance social presence
@@
 in order to maintain the safety of these online communities for
-students \cite{abbas2021onlinechat} without affecting students'
-ownership and control that is vital to advance their learning
-\cite{gachago2015crossing}.
-This is why examining the role of MIM in higher education is still a challenge, and why the attitudes of the teaching community towards them has to be examined, as we do in this paper.
+students \cite{abbas2021onlinechat}. However, these rules should not affect students'
+ownership and control, since it is vital to advance in their learning
+\cite{gachago2015crossing} precess. 
+This is why examining the role of MIM in higher education is still a challenge, and why the attitudes of the teaching community towards them have to be examined, as we do in this paper.
 
@@
 The use of MIM, although possibly valuable by itself, can be enhanced via the use of chatbots, which, being conversational agents, usually well where synchronous conversations take place. 
-The use of conversational agents or chatbots in higher education is
+% Antonio - I cannot understand this sentence... what's the point of the expression 'usually well'?
+The use of conversational agents (chatbots) in higher education is
 still at its infancy \cite{yang2019opportunities}. Nevertheless,
@@
 gamification \cite{Yildirim2017} can improve student motivation. In
-this sense, \cite{Pimmer2019} carried out a series of experiments with
+this sense, the authors in \cite{Pimmer2019} carried out a series of experiments with
 technological tools whose results showed positive perception and
@@
 
-Several higher education chatbots' evaluation studies were
-undertaken. For instance, an evaluation review study presented by
+Several higher education chatbots' evaluation studies have been 
+undertaken. For instance, a recent evaluation review study presented by Smutny and Schreiberova 
 \cite{Smutny2020} examined 47 educational chatbots implemented in
 Facebook Messenger with the focus to identify characteristics and
-quality metric such as language, subject matter and platform. Another
+quality metrics such as language, subject matter and platform. Another
 study aimed to categorise educational chatbots according to their
@@
 provide service support such as the chatbot Ask Holly \cite{meetholly}
-and Dina \cite{santoso2018dinus}, both chatbots respond to students'
-questions about enrollment and registration. Ask
-L.U. \cite{LancasterUniversity_2019} answers students' frequently
+and Dina \cite{santoso2018dinus}; both chatbots respond to students'
+questions about enrollment and registration. Ask (Lancaster University)
+ \cite{LancasterUniversity_2019} answers students' frequently
 asked questions about timetables, grades, tutors and societies. LISA
@@
 breaking the ice between new students by introducing them to each
-other.  \cite{ranoliya2017chatbot} proposed a generic chatbot for
-university students that is able to answer their frequently asked
-questions; for some time, the University of Granada had ELVIRA as a
-chatbot in their main page \cite{MOREO20129}. Besides being able to
-answer pre-established (frequent) questions, it did so from the main
+other. Ranoliya et al. \cite{ranoliya2017chatbot} proposed a generic chatbot for
+university students that is able to answer to their frequently asked
+questions. 
+For some time, the University of Granada had ELVIRA as a
+chatbot in its main web page \cite{MOREO20129}. Besides being able to
+answer pre-established (frequent) questions, it did so from the website of the
 University of Granada using an inset character, voiced by a real
@@
 making the update of questions and answers simpler, or more
-interactive, using actual messaging platforms. In most cases, using
-the inset search engine was able to give you more up-to-date and
+interactive, using actual messaging platforms. 
+% Antonio - the last part of the sentence is not clear. Do you refer to all the aforementioned chatbots?
+% Just to Elvira? What messaging platforms do you mean?
+In most cases, using the inset search engine was able to give you more up-to-date and
 accurate answers.
-
-On the other hand, teaching-oriented chatbots are more sophisticated
+% Antonio - again, are you speaking about Elvira? 
+% If we say something like the last sentence, we are actually saying that chatbots are not useful... is this what we want to remark?
+
+On the other hand, teaching-oriented chatbots are more sophisticated,
 as they set personalised learning outcomes and monitor learning
-progress. For instance, \cite{fernoagua2018intelligent} reported on
-''eduAssistant'' a virtual teaching assistant chatbot developed on the
-Telegram messaging platform. In this study, the Telegram platform was
+progress. For instance, the work \cite{fernoagua2018intelligent} reported on
+''eduAssistant'', a virtual teaching assistant chatbot developed inside the
+Telegram messaging platform. In this study, Telegram platform was
 chosen because it is easy to use, students are familiar with its
-features and it enables students to exchange messages in different
+features, and it enables users to exchange messages in different
 formats (text, audio and video) \cite{fernoagua2018intelligent}. In
-addition, Telegram could operate on all devices and operating
-systems. The ''eduAssistant'' chatbot acts as an automatic agent
-between the teacher-content-student, facilitating real-time feedback
-loops and providing a personalised learning experience relevant to
-students' skills and knowledge. Using this chatbot, educators can
+addition, Telegram run on all devices and operating
+systems. ''eduAssistant'' chatbot acts as an automatic agent
+in teacher-content-student, facilitating real-time feedback
+loops and providing a personalised learning experience relevant to the
+students' acquired skills and knowledge. Using this chatbot, educators can
 create interactive instances in their lectures where they pose
-questions to their students and the chatbot assists students who need
-further help by giving those more hints and reporting to their
+questions to their students and the chatbot assists those who need
+further help by giving them more hints and reporting it to their
 educator's dashboard \cite{fernoagua2018intelligent}. This can help 
-educators locate those students that need their attention and send
-them more educational resources relevant to their academic
-attainment.
-
-Despite its (arguably) successful implementation in different higher education institutions, over all in the fringes of educational activity, its implementation or deployment is not trivial.
-Some authors \cite{sjostrom2018designing} have proposed a conceptual
-architecture for the adoption teaching-oriented chatbots in higher education.  This
+educators to locate those students that need their attention and send to 
+them more educational resources relevant to their academic attainment.
+
+Despite its (arguably) successful implementation in different higher education institutions, 
+over all in the fringes of educational activity, its implementation or deployment is not trivial.
+Authors in \cite{sjostrom2018designing} have proposed a conceptual
+architecture for the adoption of teaching-oriented chatbots in higher education.  This
 conceptual architecture is based on a systematic literature review of
-previous studies examining the design of chatbots in higher education
-and a content analysis of student emails and discussion forum posts of
+previous studies, examining the design of chatbots in higher education, as well as a content 
+analysis of student emails and discussion forum posts of
 four instances of a Java programming course.  The study outlined
@@
 educators are familiar with and can easily access (i.e. Facebook
-Messenger) which confirms with \cite{hobert2019you} and
-\cite{fernoagua2018intelligent} studies. In addition,
-\cite{sjostrom2018designing} argued that a conceptualision of
-learners' questions could aid designers in integrating the appropriate
+Messenger) which was confirmed with \cite{hobert2019you} and
+\cite{fernoagua2018intelligent} studies. In addition, Sj{\"o}str{\"o}m et al. \cite{sjostrom2018designing} 
+argued that a conceptualision of learners' questions could aid designers in integrating the appropriate
 types of questions that the chatbots should support for different
-courses.  \cite{coronado2018cognitive} proposed agents that store
-learning materials to be provided on demand to
-students. \cite{crockett2017predicting} reported on tutoring systems,
+courses.  Coronado et al. \cite{coronado2018cognitive} proposed agents that store
+learning materials to be provided on demand to students, whereas the authors in
+\cite{crockett2017predicting} reported on tutoring systems,
 which can perform initial assessments of students' understanding and
@@
 acceptance and usability \cite{Roblyer2010,Pimmer2019}. However,
-higher education is a special domain where according to
-\cite{hobert2019you}, specific pedagogical factors such as learning
-success or increased motivation are more important.  Therefore, to
-develop efficient chatbots for higher education, all stakeholders'
+higher education is a special domain where according to Hobert \cite{hobert2019you}, 
+specific pedagogical factors such as learning success or increased motivation are more important.  
+Therefore, to develop efficient chatbots for higher education, all stakeholders'
 (i.e. educators, students, institutions, etc) expectations needs to be
@@
 
+In this line, our previous work \cite{MoraChatbots2021} aimed at analysing the expectations of students on this regard, whereas the present study is focused on the other key actor in this challenge, i.e.
+educators.
+
 % ********************** METHODOLOGY ****************************
@@
 This is why we created a Google Form, in Spanish, which was intended to be answered in a very short amount of time.
-Initially, our intention was to mirror the questions used in \cite{MoraChatbos2021}; however, an initial exploration of results led us to create a second survey.
+Initially, our intention was to mirror the questions used in \cite{MoraChatbots2021}; however, an initial exploration of results led us to create a second survey.
 % Questions should probably be included here.

### 2021-06-27 edubots_surveys.Rnw
Fixing small typo
More meta-reviews

@@
 % Antonio - I would say 'to manage them'. Students should also handle new technologies. ;)
+% We're talking about teachers here, who need to handle the outcomes and introduce them in class - JJ
 teachers.
 In this paper we have surveyed the opinions of tertiary education
-teachers based mainly in Spain and Spanish speaking countries, 
-% Antonio - Spanish-speaking?
+teachers based mainly in Spain and Spanish-speaking countries, 
 looking at what they think about the introduction 
 % Antonio - inthe classroom
+% that's implied - JJ
 of messaging platforms and chatbots, what their needs are, what kind of use cases they see for
@@
 valuable. We will examine how and when these attitudes vary across
-gender, experience, and other factors, such as the type of discipline
+gender, experience, and other factors, such as the broad discipline
 they are teaching. Our conclusions might help with the adoption of
@@
 ownership and control, since it is vital to advance in their learning
-\cite{gachago2015crossing} precess. 
+\cite{gachago2015crossing} process. 
 This is why examining the role of MIM in higher education is still a challenge, and why the attitudes of the teaching community towards them have to be examined, as we do in this paper.
@@
 and Dina \cite{santoso2018dinus}; both chatbots respond to students'
-questions about enrollment and registration. Ask (Lancaster University)
+questions about enrollment and registration. Ask L. U.
  \cite{LancasterUniversity_2019} answers students' frequently
@@
 University of Granada using an inset character, voiced by a real
-person, who lip-synched the answers. The emphasis in this case,
+person, who lip-synched the answers. The emphasis in the case of Elvira,
 however, was on the authenticity of the synchronization more than in
@@
 % Just to Elvira? What messaging platforms do you mean?
+% Only Elvira - JJ
 In most cases, using the inset search engine was able to give you more up-to-date and
-accurate answers.
+accurate answers than the ones provided by ELVIRA, which had to be updated by hand (and not too often).
 % Antonio - again, are you speaking about Elvira? 
 % If we say something like the last sentence, we are actually saying that chatbots are not useful... is this what we want to remark?
+% No, we're saying that chatbots like Elvira have limited usability, unlike chatbots in messaging platforms - JJ
 
@@
 as they set personalised learning outcomes and monitor learning
-progress. For instance, the work \cite{fernoagua2018intelligent} reported on
-''eduAssistant'', a virtual teaching assistant chatbot developed inside the
+progress. For instance, \cite{fernoagua2018intelligent} reported on
+''eduAssistant'', a virtual teaching assistant chatbot developed on the
 Telegram messaging platform. In this study, Telegram platform was
 chosen because it is easy to use, students are familiar with its
-features, and it enables users to exchange messages in different
+features, and it enables them to exchange messages in different
 formats (text, audio and video) \cite{fernoagua2018intelligent}. In
-addition, Telegram run on all devices and operating
-systems. ''eduAssistant'' chatbot acts as an automatic agent
+addition, Telegram could operate on all devices and operating
+systems. The ''eduAssistant'' chatbot acts as an automatic agent
 in teacher-content-student, facilitating real-time feedback
@@
 over all in the fringes of educational activity, its implementation or deployment is not trivial.
-Authors in \cite{sjostrom2018designing} have proposed a conceptual
+Some authors, for instance \cite{sjostrom2018designing} have proposed a conceptual
 architecture for the adoption of teaching-oriented chatbots in higher education.  This
 conceptual architecture is based on a systematic literature review of
-previous studies, examining the design of chatbots in higher education, as well as a content 
+previous studies, examining the design of chatbots in higher education, as well as making a content 
 analysis of student emails and discussion forum posts of
@@
 
-In this line, our previous work \cite{MoraChatbots2021} aimed at analysing the expectations of students on this regard, whereas the present study is focused on the other key actor in this challenge, i.e.
+Along this line of work, our previous work \cite{MoraChatbots2021} aimed at analysing the expectations of students on this regard, whereas the present study is focused on the other key actor in this challenge, i.e.
 educators.

### 2021-06-27 edubots_surveys.Rnw
Add acknowledgements

@@
 \begin{document}
-\SweaveOpts{concordance=TRUE}
+%\SweaveOpts{concordance=TRUE}
 
@@
 All the authors have contributed to the study presented in this manuscript. 
-JJM has been the leader...
+JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
 PAC has...
@@
 
-The authors want to thank to the educators who participated in the survey.
+The authors want to thank to the educators who participated in the survey, and also people who have distributed the survey in their mailing lists, especially Mario García Valdez, Jesús Moreno León and José Raúl Canay.
 % Antonio - Add other acknowledgements

### 2021-06-27 edubots_surveys.Rnw
Fixing table, but now it hangs
Trying to fix the error
Trying to find the error. Delegating to @fbarranco

@@
 ]{\inits{JJM}\fnm{Juan J.} \snm{Merelo}}
-\author[
-  addressref={aff1},
-  email={pacv@ugr.es}   % email address
-]{\inits{PAC}\fnm{Pedro A.} \snm{Castillo}}
-\author[
-  addressref={aff2},
-  email={amorag@ugr.es}
-]{\inits{AMM}\fnm{Antonio M.} \snm{Mora}}
-\author[
-  addressref={aff1},
-  email={fbarranco@ugr.es}
-]{\inits{FB}\fnm{Francisco} \snm{Barranco}}
-\author[
-  addressref={aff3},
-  email={n.h.abbas@leeds.ac.uk}
-]{\inits{NA}\fnm{Noorhan} \snm{Abbas}}
-\author[
-  addressref={aff1},
-  email={aguillen@ugr.es}
-]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
+% \author[
+%   addressref={aff1},
+%   email={pacv@ugr.es}   % email address
+% ]{\inits{PAC}\fnm{Pedro A.} \snm{Castillo}}
+% \author[
+%   addressref={aff2},
+%   email={amorag@ugr.es}
+% ]{\inits{AMM}\fnm{Antonio M.} \snm{Mora}}
+% \author[
+%   addressref={aff1},
+%   email={fbarranco@ugr.es}
+% ]{\inits{FB}\fnm{Francisco} \snm{Barranco}}
+% \author[
+%   addressref={aff3},
+%   email={n.h.abbas@leeds.ac.uk}
+% ]{\inits{NA}\fnm{Noorhan} \snm{Abbas}}
+% \author[
+%   addressref={aff1},
+%   email={aguillen@ugr.es}
+% ]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
 
@@
 
+\begin{table}
 \begin{tabular}{|c|c|c|c|c|}
@@
 \hline
-Output & \multirow{3}{PostCOVID changes} 	\\
+% Output & \multirow{3}{PostCOVID changes} & 	\\
 \hline
-\end{tabular} \label{tab:feature_results} \caption{Mapping of feature numbers to survey questions.}
+\caption{Mapping of feature numbers to survey questions.}
+\label{tab:feature_results}
+\end{tabular}
 \end{table}
@@
 The feature ranking results are shown in Figure \ref{fig:feature_xgboost}.
-\begin{figure}
-\includegraphics{figs/feature_xgboost.png}
-\label{fig:feature_xgboost}\caption{Ranking of features obtained after using XGBoost model.}
-\end{figure}
+% \begin{figure}
+% \includegraphics{figs/feature_xgboost.png}
+% \label{fig:feature_xgboost}\caption{Ranking of features obtained after using XGBoost model.}
+% \end{figure}
 

### 2021-06-27 edubots_surveys.Rnw
OK, I give up
More attempts. It's around here
fixes typo in tables, again stable version

@@
 
-% ************************ New alaysis ***********************
+% ********************** ALBERTO HERE ****************************
+% ************************ New analysis ***********************
 
@@
 The reference mapping for the feature names in the experiments is in Table \ref{tab:feature_mapping}. 
-
 \begin{table}
-
 \begin{tabular}{|c|c|}
@@
 14 & Sector		\\
-15 & Messaging Organization → Number of approaches considered		\\
-16 & Degrees → Number of degrees involved		\\
+15 & Messaging Organization $\rightarrow$ Number of approaches considered		\\
+16 & Degrees $\rightarrow$ Number of degrees involved		\\
 17 & Discipline		\\
@@
 \hline
-\end{tabular} \label{tab:feature_reference} \caption{Mapping of feature numbers to survey questions.}
+\end{tabular}
+\caption{Mapping of feature numbers to survey questions.}
+\label{tab:feature_reference} 
 \end{table}
@@
 14 & Sector	&			&  &  \\
-15 & Messaging Organization → Number of approaches considered	&			&  &  \\
-16 & Degrees → Number of degrees involved	&			&  &  \\
+15 & Messaging Organization $\rightarrow$ Number of approaches considered	&			&  &  \\
+16 & Degrees $\rightarrow$ Number of degrees involved	&			&  &  \\
 17 & Discipline	&		&  &  	\\
@@
 \hline
+\end{tabular}
 \caption{Mapping of feature numbers to survey questions.}
 \label{tab:feature_results}
-\end{tabular}
 \end{table}
@@
 AG has...
-All authors read and approved the final manuscript.
+All authors have read and approved the final manuscript.
 

### 2021-06-27 edubots_surveys.Rnw
Fixing table unsuccessfully
Add latest papers (2021) and include them in SoA :memo: #6

@@
 % The Use of Chatbots in Higher Education
-The use of MIM, although possibly valuable by itself, can be enhanced via the use of chatbots, which, being conversational agents, usually well where synchronous conversations take place. 
+The use of MIM, although possibly valuable by itself, can be enhanced via the use of chatbots, which, being conversational agents, usually dwell in systems where synchronous conversations take place. 
 % Antonio - I cannot understand this sentence... what's the point of the expression 'usually well'?
+% Dwell, not well - JJ
 The use of conversational agents (chatbots) in higher education is
@@
 acceptance and usability \cite{Roblyer2010,Pimmer2019}. However,
-higher education is a special domain where according to Hobert \cite{hobert2019you}, 
+higher education is a special domain where, according to Hobert \cite{hobert2019you}, 
 specific pedagogical factors such as learning success or increased motivation are more important.  
@@
 educators.
+This has been analyzed very recently by Chocarro et al.
+\cite{doi:10.1080/03055698.2020.1850426}, who, by analyzing surveys, created a {\em technology acceptance model} that proposed a series of features that would make chatbots easier to accept; among them, formality of language as well as easiness and usefulness.
+The survey targeted primary and secondary education teachers, and was also more interested in the general use of chatbots in education, not specifically in a classroom setting, seeking educational outcomes.
+However, they establish a series of results that are obviously interesting and relevant for this work.
+
+We will present next the methodology we have followed to find out teachers' attitudes.
 
@@
 The idea was to be able to identify which features measured in the survey could identify willingness to change.
-As chatbots are an emerging technology, it is quite probable that this new change will come sooner than later considering the improvemente in Virtual and Augmented Reality \cite{}.
+As chatbots are an emerging technology, it is quite probable that this new change will come sooner than later considering the improvements in Virtual and Augmented Reality \cite{}.
 
@@
 \hline
-% Output & \multirow{3}{PostCOVID changes} & 	\\
+Output & \multicolumn{3}{c}{PostCOVID changes} & 	\\
 \hline

### 2021-06-27 edubots_surveys.Rnw
Adds another survey to the state of the art

@@
 
-Along this line of work, our previous work \cite{MoraChatbots2021} aimed at analysing the expectations of students on this regard, whereas the present study is focused on the other key actor in this challenge, i.e.
+Along this line of work, our previous work \cite{MoraChatbots2021} aimed at analysing the expectations of students on this regard; recent papers have also analyzed how the use of chatbots affected the learning outcomes of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
+This paper analyzed conversational chatbots in an one-to-one setting, finding that learning really benefited from it.
+This is, once again, a proof of the benefit of chatbots in certain settings; however, there are some attitudes that might prevent the successful acceptance of the technology, and these are what we are trying to find out in this paper, together with what kind of features would make its acceptance better.
+
+Besides, the present study is focused on the other key actor in this challenge, i.e.
 educators.
-This has been analyzed very recently by Chocarro et al.
+Their attitudes have been analyzed very recently by Chocarro et al.
 \cite{doi:10.1080/03055698.2020.1850426}, who, by analyzing surveys, created a {\em technology acceptance model} that proposed a series of features that would make chatbots easier to accept; among them, formality of language as well as easiness and usefulness.

### 2021-06-27 edubots_surveys.Rnw
Add back names eliminated for testing

@@
 ]{\inits{JJM}\fnm{Juan J.} \snm{Merelo}}
-% \author[
-%   addressref={aff1},
-%   email={pacv@ugr.es}   % email address
-% ]{\inits{PAC}\fnm{Pedro A.} \snm{Castillo}}
-% \author[
-%   addressref={aff2},
-%   email={amorag@ugr.es}
-% ]{\inits{AMM}\fnm{Antonio M.} \snm{Mora}}
-% \author[
-%   addressref={aff1},
-%   email={fbarranco@ugr.es}
-% ]{\inits{FB}\fnm{Francisco} \snm{Barranco}}
-% \author[
-%   addressref={aff3},
-%   email={n.h.abbas@leeds.ac.uk}
-% ]{\inits{NA}\fnm{Noorhan} \snm{Abbas}}
-% \author[
-%   addressref={aff1},
-%   email={aguillen@ugr.es}
-% ]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
+\author[
+  addressref={aff1},
+  email={pacv@ugr.es}   % email address
+]{\inits{PAC}\fnm{Pedro A.} \snm{Castillo}}
+\author[
+  addressref={aff2},
+  email={amorag@ugr.es}
+]{\inits{AMM}\fnm{Antonio M.} \snm{Mora}}
+\author[
+  addressref={aff1},
+  email={fbarranco@ugr.es}
+]{\inits{FB}\fnm{Francisco} \snm{Barranco}}
+\author[
+  addressref={aff3},
+  email={n.h.abbas@leeds.ac.uk}
+]{\inits{NA}\fnm{Noorhan} \snm{Abbas}}
+\author[
+  addressref={aff1},
+  email={aguillen@ugr.es}
+]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
 

### 2021-06-27 edubots_surveys.Rnw
removed new analysis from paper

@@
 
-% ********************** ALBERTO HERE ****************************
-% ************************ New analysis ***********************
-
-\subsection{Data Analysis using Machine Learning}
-
-To provide a different perspective another analysis was carried out using models from the field of machine learning.
-The idea was to be able to identify which features measured in the survey could identify willingness to change.
-As chatbots are an emerging technology, it is quite probable that this new change will come sooner than later considering the improvements in Virtual and Augmented Reality \cite{}.
-
-The output variable is set as covid-changes, whose values were grouped to three numerical classes:
-
-\begin{itemize}
- \item 2 = Yes, now they use it or use it more or in a safer/different way 
- \item 1 = No change in use 
- \item 0 = No change in not using 
-\end{itemize}
-
-Regarding the rest of features, a similar preprocessing was applied to the original survey:
-
-\begin{itemize}
-\item Binary Yes/No variables like AgendaBot, ClassMaterialBot, FAQBot, GradesBot, MessagingPlatform..., OtherBot were mappped to values $\in {0,1}$ using 1 for Yes and 0 for No.
-
-\item Gender variable was mapped to: 1 for Male, 2 for PNTS and 3 for Female. In this way we keep equidistance from PNTS to the other well identified genders.
-
-\item Age and Experience were assigned valued $\in {1,2,3,4}$ where the higher number represents the older age or more years of experience.
-
-\item Sector was coded as 1 for University and 2 for Vocational.
-
-\item Messaging Organization was reinterpreted as number of approaches considered by the professors with the following values: 0 for answer of type: "I'd rather leave students self-organize and not be part of the chat" ; 1 for answers like: "A chat with my students in the same course" or "A chat with all students and teachers in the same semester/year".
-If the previous two were marked, or even another answer appeared, the sum of approaches was computed.
-By doing this, we consider a passive professor that does not want to get involved in the chat with a 0 and emphasize the active ones that give a thought on how they want to interact with students.
-
-\item Degrees feature was also reinterpreted as number of degrees involved.
-By doing this, it is possible to see with a number the range width of the professor.
-From this point, it could be possible to study if a wider range professor presents or not more intention of using chatbots (independently of the degree level).
-
-\item Finally, Discipline was grouped into the following categories: 0 for No  1 for Engineering and Technology 2 for Science and Biomedicine ; 3 for Social Science and 4 for Humanities.
-By doing this we keep a similarity criterion just by computing the distance between disciplines.
-
-\end{itemize}
-
-The reference mapping for the feature names in the experiments is in Table \ref{tab:feature_mapping}. 
-\begin{table}
-\begin{tabular}{|c|c|}
-\hline
-\# Variable & Name \\
-\hline
-0 & AgendaBot	\\
-1 & ClassMaterialBot		\\
-2 & Age		\\
-3 & Experience		\\
-4 & FAQBot		\\
-5 & GradesBot		\\
-6 & Gender		\\
-7 & MessagingPlatform0ne		\\
-8 & MessagingPlatformOther		\\
-9 & MessagingPlatformProvided		\\
-10 & MessagingPlatformSlack		\\
-11 & MessagingPlatformTelegram		\\
-12 & MessagingPlatformWhatsApp		\\
-13 & OtherBot		\\
-14 & Sector		\\
-15 & Messaging Organization $\rightarrow$ Number of approaches considered		\\
-16 & Degrees $\rightarrow$ Number of degrees involved		\\
-17 & Discipline		\\
-\hline
-Output & PostCOVID changes	\\
-\hline
-\end{tabular}
-\caption{Mapping of feature numbers to survey questions.}
-\label{tab:feature_reference} 
-\end{table}
-
-\subsubsection{Using Mutual Information and Neural Networks}
-
-The intuitive idea for Mutual Information (MI) is the amount of information about a variable that another variable, or group of variables, has.
-Therefore, setting as goal the capability of predicting the COVID changes, it is possible to detect the most relevant variables.
-Several approaches can be taken to select a subset of variables that contain enough information to reconstruct the output \cite{}.
-For this study, the estimation of the mutual information provided by the SKlearn package \cite{} and the algorithm mMRM \cite{} are considered.
-
-As the evaluation of all possible combinations might be unfeasible from a computational point of view, the following heuristic was applied: rank the variables using the MI of that variable isolated, apply a threshold to discard the ones with smaller MI and then, make a exhaustive search for the combination with higher MI.
-
-\begin{table}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\# Variable & Name & MI (considering one variable) & Max Relevance & mRMR\\
-\hline
-0 & AgendaBot	&  &  &\\
-1 & ClassMaterialBot &	&  &	\\
-2 & Age	&		&  &  \\
-3 & Experience &			&  &  	\\
-4 & FAQBot &			&  &  	\\
-5 & GradesBot &			&  &  	\\
-6 & Gender &			&  &  	\\
-7 & MessagingPlatform0ne &			&  &  	\\
-8 & MessagingPlatformOther &			&  &  	\\
-9 & MessagingPlatformProvided	&			&  &  \\
-10 & MessagingPlatformSlack	&			&  &  \\
-11 & MessagingPlatformTelegram	&			&  &  \\
-12 & MessagingPlatformWhatsApp	&			&  &  \\
-13 & OtherBot	&			&  &  \\
-14 & Sector	&			&  &  \\
-15 & Messaging Organization $\rightarrow$ Number of approaches considered	&			&  &  \\
-16 & Degrees $\rightarrow$ Number of degrees involved	&			&  &  \\
-17 & Discipline	&		&  &  	\\
-\hline
-Output & \multicolumn{3}{c}{PostCOVID changes} & 	\\
-\hline
-\end{tabular}
-\caption{Mapping of feature numbers to survey questions.}
-\label{tab:feature_results}
-\end{table}
-
-\subsubsection{Using XGBoost}
-
-Due to the lack of data, estimators based on $k$-Nearest Neighbours might be unreliable, thus, another approach can be used: decision trees build during their design process a relevance of the variables that, after being used to take the decision, decrease in a significant way the error.
-Therefore, the well known implementation of the XGBoost \cite{} was used to obtain the accuracy and the feature relevance.
-
-The feature ranking results are shown in Figure \ref{fig:feature_xgboost}.
-% \begin{figure}
-% \includegraphics{figs/feature_xgboost.png}
-% \label{fig:feature_xgboost}\caption{Ranking of features obtained after using XGBoost model.}
-% \end{figure}
-
 % ********************** CONCLUSIONS ****************************

### 2021-06-27 edubots_surveys_future_paper.Rnw
created file for future paper

--- 2021-06-27 edubots_surveys.Rnw
@@
 
-\title{Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective}
+\title{Analysing intention of chatbots use after COVID pandemic using Machine Learning}
 
@@
 \begin{abstract} % abstract
-Introducing new technologies such as messaging platforms, and chatbots
-attached to it, in higher education, requires careful consideration of
-all options, but above all, an examination of the attitudes of the
-affected community, especially those that will need to handle them,
-% Antonio - I would say 'to manage them'. Students should also handle new technologies. ;)
-% We're talking about teachers here, who need to handle the outcomes and introduce them in class - JJ
-teachers.
-In this paper we have surveyed the opinions of tertiary education
-teachers based mainly in Spain and Spanish-speaking countries, 
-looking at what they think about the introduction 
-% Antonio - inthe classroom
-% that's implied - JJ
-of messaging platforms and chatbots, what their needs are, what kind of use cases they see for
-them, and in what kind of environment they think its use will be
-valuable. We will examine how and when these attitudes vary across
-gender, experience, and other factors, such as the broad discipline
-they are teaching. Our conclusions might help with the adoption of
-messaging platforms in an educational setting, as well as chatbots or
-other kind of bots, by higher education institution, and how these
-must be introduced to teachers so that it helps them achieve desired
-educational outcomes. 
+
 \end{abstract}
@@
 \kwd{Higher education}
-% Antonio - add something related to "survey", "teachers' opinion" or so?
 \end{keyword}
@@
 
-% ********************** METHODOLOGY ****************************
+% ********************** SURVEY DESCRIPTION ****************************
 
-\section{Methodology}
-\label{sec:meth}
+\sectionData description}
+\label{sec:data}
 
-Our intention from the beginning was to try and gather a sufficient amount of responses in all sectors, as well as cover different sectors of higher education.
-This is why we created a Google Form, in Spanish, which was intended to be answered in a very short amount of time.
-Initially, our intention was to mirror the questions used in \cite{MoraChatbots2021}; however, an initial exploration of results led us to create a second survey.
-% Questions should probably be included here.
+% ************************ DATA ANALYSIS ***********************
 
-The initial survey was done in two different forms, one for university and other for tertiary non-university teachers.
-Questions and responses were the same, except for the type of tertiary degrees that were taught.
-We got around 300 responses to this one, with two thirds of them coming from university teachers, the rest from high school teachers.
-In both cases, we used mainly mailing lists, as well as Telegram groups, to spread the link to the form.
-The university form was spread in Spanish (mainly Andaluc\'{\i}a and Galicia) universities, as well as Costa Rica and Mexico.
-The tertiary non-university teachers are mainly in Andaluc\'{\i}a.
-Dissemination and answers took place in the first quarter of 2021, post-pandemic and while, at least in Spain, many universities had mandatory virtual teaching.
-
-The second survey followed the same paths, only in this case there was a single questionnaire.
-It was filled by teachers that were also students in a teacher formation course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers to knew about it by emails from the authors, as well as from the vicedeanship for International Relations that included it in its newsletter.
-This means that there might be a higher proportion of 1) teachers with few years of experience 2) teachers from the computer science faculty and 3) teachers from Granada.
-We think, however that there's no explicit bias in this selection, although of course specific percentages will vary.
-
-% ********************** RESULTS ****************************
-
-\section{Results}
-\label{sec:res}
-
-% Describe the survey and population
-We collected responses from 282 teachers from Spain and Spanish Speaking countries for the first survey (\textit{survey1} in Fig.
-\ref{figure:teachers_population}) and 205 for the second one (\textit{survey2}).
-The sample includes mostly teachers from university, although about 32\% and 8\% are from vocational education in the first and second survey respectively.
-Regarding gender, in total 61\% are male teachers and 32\% female (approximately 5\% chose not to disclose it).
-Finally, the responses are equally distributed attending to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 26\% for 6-15 years of experience, 30\% for 16-25, and 20\% for teachers with more than 25 years of experience.
-
-% [pedro]  the way these (5) figures are shown is a bit strange: different sizes of plots...
-
-\begin{figure}[h!tbp]
-\begin{center}
-    \begin{minipage}[t]{0.3\textwidth}
-        \centering
-<<gender, echo=FALSE, fig.width=3.2, fig.height=2.5>>=
-#ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-freq.Gender$source<-rep("survey1")
-freqInteraction.Gender$source<-rep("survey2")
-freqbinded.Gender <- rbind(freq.Gender, freqInteraction.Gender)
-freqbinded.Gender$source <- factor(freqbinded.Gender$source) 
-ggplot(freqbinded.Gender, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-@
-
-%       \includegraphics[width=\textwidth]{figures/gender.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.3\textwidth}
-        \centering
-<<age,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
-#ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-freq.Age$source<-rep("survey1")
-freqInteraction.Age$source<-rep("survey2")
-freqbinded.Age <- rbind(freq.Age, freqInteraction.Age)
-freqbinded.Age$source <- factor(freqbinded.Age$source) 
-ggplot(freqbinded.Age, aes(x = Age, y=freqAge, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-@
-
-%       \includegraphics[width=\textwidth]{figures/age.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.3\textwidth}
-        \centering
-<<sector,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
-#ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-freq.Sector$source<-rep("survey1")
-freqInteraction.Sector$source<-rep("survey2")
-freqbinded.Sector <- rbind(freq.Sector, freqInteraction.Sector)
-freqbinded.Sector$source <- factor(freqbinded.Sector$source) 
-ggplot(freqbinded.Sector, aes(x = Sector, y=freqSector, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/sector.pdf}
-    \end{minipage}
-    \vspace{0.5mm}
-    \begin{minipage}[t]{0.38\textwidth}
-        \centering
-<<experience, echo=FALSE, fig.width=4.5, fig.height=3.475>>=
-#ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-freq.Experience$source<-rep("survey1")
-freqInteraction.Experience$source<-rep("survey2")
-freqbinded.Experience <- rbind(freq.Experience, freqInteraction.Experience)
-freqbinded.Experience$source <- factor(freqbinded.Experience$source) 
-ggplot(freqbinded.Experience, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-@        
-%       \includegraphics[width=\textwidth]{figures/experience.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.52\textwidth}
-        \centering
-<<discipline,echo=FALSE, fig.width=8.2, fig.height=4.45>>=
-#ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-freq.Discipline$source<-rep("survey1")
-freqInteraction.Discipline$source<-rep("survey2")
-freqbinded.Discipline <- rbind(freq.Discipline, freqInteraction.Discipline)
-freqbinded.Discipline$source <- factor(freqbinded.Discipline$source) 
-freqbinded.Discipline$Discipline <- factor(freqbinded.Discipline$Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other"))
-ggplot(freqbinded.Discipline, aes(x = Discipline, y=freqDiscipline, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-@
-
-%       \includegraphics[width=\textwidth]{figures/discipline.pdf}
-    \end{minipage}
-\end{center}
-    \caption{Sample population description.
-The responses from two surveys were collected amount to 282 for the first survey (\textit{survey1} in red) and 205 for the second (\textit{survey2} in blue).
-Data are shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
-\label{figure:teachers_population}
-\end{figure}
-
-Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar. %, and as a matter of fact,
-Additionally, as a matter of fact, as Figure \ref{figure:age.vs.exp} shows, age and experience are correlated strongly, with experience being roughly 20-30 years less than age. 
-This might indicate that a differential analysis for age and experience will not yield significant differences, except maybe in the 6-15 years experience group, which is spread over all ages.
-At any rate, experience seems to be the dominating factor here and we'll use experience only unless we detect some significant difference by age.
-
-\begin{figure}[h!tbp]
-\begin{center}
-<<interaction,message=FALSE,echo=FALSE, fig.height=2.0, fig.width=4.0>>=
-library(forcats)
-survey.interaction %>%
-    mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
-    mutate(Experience = fct_relevel(Experience, "0-05 years", "06-15 years", "16-25 years", "> 25 years" )) %>%
-    group_by( Age, Experience ) %>% summarise( n = n() ) %>% mutate( freq = n/sum(n)) -> Age.vs.Experience
-
-ggplot(Age.vs.Experience,aes(Age,Experience))+geom_point(aes(size=freq),colour="green")
-@
-\end{center}
-\caption{Correlation between age and experience.}
-\label{figure:age.vs.exp}
-\end{figure}
-
-\subsection{RQ1 - Are teachers already using messaging apps in their classes?}
-
-%Why messaging apps are relevant here --> connect to the development of chatbots
-Group messaging apps have become a powerful tool for keeping touch with students. Also, they are the baseline platform for the development of chatbots to help with the learning process.
-
-According to the results summarized in Fig.
-\ref{figure:chatbots_use}, teachers mainly use the instant messaging app provided by their institutions (55\%),  and Whatsapp (44\%), the most popular messaging app in Spain.
-Finally, about 20\% also use Telegram.
-Although gender differences are not significant, female teachers answered they use instant messaging apps more than male teachers (about 10\% more).
-Also, teachers in vocational Education also use Whatsapp more than university teachers.
-
-With respect to the distribution of the use of messaging apps per age, there are no significant differences for the Whatsapp and apps provided by their institutions.
-However, younger teachers use also Telegram with more than 25\%, a percentage that falls to about 10\% for teachers that are 55 or older.
-The third column compares the use of these apps considering the number of years of experience.
-One interesting result is that, contrarily to the idea of technology adaptation issues when considering older teachers, about 65\% of teachers with more than 25 years of experience use the platforms provided by their institutions while the percentage goes down to less than 50\% for teachers with 6-15 years of experience.
-
-\begin{figure}[h!tbp]
-\begin{center}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<gender_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<experience_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<sector_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
-    \end{minipage}
-    %----
-    \vspace{0.2mm}
-    \hspace{10mm}
-    \begin{minipage}[t]{0.5\textwidth}
-        \centering
-<<discipline_provided, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-
-ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformProvided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/discipline_provided.pdf}
-    \end{minipage}
-    \hspace{10mm}
-    %----
-    %----
-    \vspace{0.5mm}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<gender_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformWhatsApp, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/gender_whatsapp.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<experience_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformWhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/experience_whatsapp.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<sector_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformWhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
-    \end{minipage}
-    \vspace{0.2mm}
-    \hspace{10mm}
-    \begin{minipage}[t]{0.5\textwidth}
-        \centering
-<<discipline_whatsapp, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformWhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
-    \end{minipage}
-    \hspace{10mm}
-    %----
-    %----
-    \vspace{0.5mm}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<gender_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformTelegram, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/gender_telegram.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<experience_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformTelegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/experience_telegram.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<sector_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformTelegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/sector_telegram.pdf}
-    \end{minipage}
-    \vspace{0.2mm}
-    \hspace{10mm}
-    \begin{minipage}[t]{0.5\textwidth}
-        \centering
-<<discipline_telegram, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformTelegram, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/discipline_telegram.pdf}
-    \end{minipage}
-    \hspace{10mm}
-\end{center}
-    \caption{Use of chatbots in class: distributions per gender, age, years of experience in education, university or vocational education, and discipline.
-Teachers were specifically asked about two popular instant messaging apps (Whatsapp and Telegram), and the use of platforms already provided by their institutions different than these two ones.}
-\label{figure:chatbots_use}
-\end{figure}
-
-Results in Fig.
-\ref{figure:chatbots_use} do not show differences in the use of instant messaging apps between teachers from University and vocational education.
-In general, most teachers prefer messaging apps provided by their own institutions.
-With respect to specific disciplines, Engineering and Technology teachers are more active in their use, although it is also relevant the amount of teachers from Humanities that answered they used these apps in their classes (around 60\% use the apps provided by their institutions).
-
-%\begin{figure}[t]
-%\begin{center}
-%    \vspace{2mm}
-%    \begin{minipage}[t]{0.30\textwidth}
-%	    \centering
-% 	    \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
-%    \end{minipage}
-%    \begin{minipage}[t]{0.50\textwidth}
-%	    \centering
-% 	    \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
-%    \end{minipage}
-%    
-%    \vspace{2mm}
-%    \begin{minipage}[t]{0.30\textwidth}
-%	    \centering
-% 	    \includegraphics[width=\textwidth]{figures/sector_telegram.pdf}
-%    \end{minipage}
-%    \begin{minipage}[t]{0.50\textwidth}
-%	    \centering
-% 	    \includegraphics[width=\textwidth]{figures/discipline_telegram.pdf}
-%    \end{minipage}
-%\end{center}
-%    \caption{Differences in the use of chatbots in class between vocational and university teaching and distributions by discipline.}
-%\label{figure:chatbots_use_sector_discip}
-%\end{figure}
-
-Regarding the social factor of chat groups that teachers use in class, according to Fig.
-\ref{figure:chatbots_messagingorganization} the vast majority prefer small groups only with the students from the same course.
-These are more focused groups with specific goals and dedicated to the organization of the course and its tasks, and from the pedagogic point of view seem more appropriate to improve the learning process.
-Interestingly, about 30\% of teachers consider they should not be part of the chat group.
-Also, only university teachers find interesting a group with all the students and teachers in their own Faculty or School.
-The lack of teachers from vocational Education here may be the consequence of using specific language such as "Faculty".
-Moreover, the fact that many universities and schools already use these groups for administrative and social interaction (e.g.
-\cite{dibitonto2018chatbot}) might be the reason for the low percentage of teachers that selected this response.
-
-\begin{figure}[h!tbp]
-\centering
-<<messaging_organization, echo=FALSE, fig.width=19/2.54, fig.height=5/2.54>>=
-survey.pilot.MessagingOrganization <- within(survey.pilot.MessagingOrganization, Messaging.Organization <- factor(Messaging.Organization, levels=names(sort(table(Messaging.Organization), decreasing=TRUE))))
-ggplot(survey.pilot.MessagingOrganization, aes( x = Messaging.Organization, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90))+coord_flip()+ theme(axis.title.y=element_blank())
-@
-%\includegraphics[width=\textwidth]{figures/messaging_organization.pdf}
-\caption{Distribution of teachers' preferences for the chat groups with their students: from groups only with their students from a specific course to groups with greater social interaction with all students in their School or Faculty.}
-\label{figure:chatbots_messagingorganization}
-\end{figure}
-
-Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' attitudes towards the instant messaging apps.
-The 273 answers are summarized in Fig.
-\ref{figure:chatbots_use_postcovid}, showing that about 77\% of teachers already used these tools before the pandemic and kept using them during the pandemic lockdowns that forced students and educators to use remote education schemes.
-Moreover, approximately 15\% of them switched their messaging app for one that offered a safer interaction with their students.
-According to the responses, an additional 16\% started using messaging apps during the pandemic for the first time in their classes.
-Aggregating the answers, currently 91\% of the teachers are using messaging apps as learning tools.
-
-%A few relevant facts from the collected data: teachers with 16-25 years of experience seem more worried about the security of messaging apps and teachers with up to 5 years of experience were more open to adopt messaging apps due to the pandemic; female teachers were more willing to adopt new platforms due to the pandemic, and even to start using safer alternatives; finally, university teachers that did not use them were more reluctant to start using them after the pandemic.
-
-\begin{figure}[h!tbp]
-\begin{center}
-    \begin{minipage}[t]{0.85\textwidth}
-        \centering
-<<gender_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-survey.pilot.postCOVID <- within(survey.pilot.postCOVID, PostCOVID.changes <- factor(PostCOVID.changes, levels=names(sort(table(PostCOVID.changes), decreasing=TRUE))))
-ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/gender_covid.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.85\textwidth}
-        \centering
-<<sector_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.85\textwidth}
-        \centering
-<<experience_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/experience_covid.pdf}
-    \end{minipage}
-\end{center}
-    \caption{Impact of COVID in the use of messaging apps in University and vocational education.}
-\label{figure:chatbots_use_postcovid}
-\end{figure}
-
-The descriptive analysis in this case is done using a Chi-square test.
-For the different variables considered, some statistical significance was found for Gender, Sector, and academic Discipline.
-The values found with the test are: $p-value=0.0034$ for Gender, $p-value=0.0199$ for Sector, and $p-value=0.0211$ for Discipline.
-The first column in Fig.
-\ref{figure:postcovid_chisq} shows the Pearson's residuals of the test for these three variables.
-Residuals show the difference between the observed and the expected values, with large residuals showing that variables are not truly independent.
-In this case, blue shows positive contribution and red negative contribution to the test, and saturation shows how large is this contribution in contrast to the expected value by chance.
-Tables on the right side show adjusted standardized residuals that according to \cite{agresti2013categorical}, if greater than +/-2 for cases with few cells, indicate lack of fit of $H_0$ (bolded in our table).
-Also, the table shows the percentage of contribution to the test of each cell.
-
-\begin{figure}[h!tbp]
-\begin{center}
-    \begin{minipage}[c]{0.45\textwidth}
-        \centering
-<<gender_postcovid_chisq, echo=FALSE, fig.width=17/2.54, fig.height=10/2.54>>=
-df <-select(survey.pilot.postCOVID, PostCOVID.changes, Gender, Sector, Experience, Discipline)
-df[as.character(df$Gender)!="PNTS", ] -> df1
-df1[as.character(df1$Gender)!="No", ] -> df1
-df1[as.character(df1$Discipline)!="No", ] -> df1
-df1[as.character(df1$Experience)!="No", ] -> df1
-df1[as.character(df1$Sector)!="No", ] -> df1
-survey.pilot.postCovidChisq<- droplevels(df1)
-
-covidChanges.vs.Gender<-table(survey.pilot.postCovidChisq$Gender, survey.pilot.postCovidChisq$PostCOVID.changes)
-colnames(covidChanges.vs.Gender)<- c("Did/do", "Didn't/do","safer", "Didn't/don't")
-chisq<-chisq.test(covidChanges.vs.Gender)
-corrplot(chisq$residuals, is.corr = FALSE)
-@
-    \end{minipage}
-    %This tables comes from (TODO: generate them automatically from the data)
-    %contrib <- 100*chisq$residuals^2/chisq$statistic
-    %round(contrib, 2)
-    %round(chisq$stdres, 3)
-    \begin{minipage}[c]{0.45\textwidth}
-        \centering
-    \resizebox{\textwidth}{!}{%
-    \begin{tabular}{l|r|r|r|r|}
-    \cline{2-5}
-                                 & Did/Do & Didn't/Do & Safer  & Didn' t/Don't \\ \hline
-    \multicolumn{1}{|l|}{Female} & \textbf{-2.850} & \textbf{2.806} & 1.832  & -1.011 \\ 
-    \multicolumn{1}{|l|}{} & 15.15\% & \textbf{31.21\%} &  13.49\% & 4.40\% \\ \hline
-    \multicolumn{1}{|l|}{Male}   & \textbf{2.850} & \textbf{-2.806} & -1.832 & 1.011 \\ 
-    \multicolumn{1}{|l|}{} &  8.43\% &  \textbf{17.36\%} & 7.50\% &  2.45\% \\ \hline
-    \end{tabular}%
-    }
-    \end{minipage}
-    \begin{minipage}[c]{0.45\textwidth}
-        \centering
-<<sector_postcovid_chisq, echo=FALSE, fig.width=17/2.54, fig.height=10/2.54, warning=FALSE>>=
-covidChanges.vs.Sector<-table(survey.pilot.postCovidChisq$Sector, survey.pilot.postCovidChisq$PostCOVID.changes)
-colnames(covidChanges.vs.Sector)<- c("Did/do", "Didn't/do","safer", "Didn't/don't")
-chisq<-chisq.test(covidChanges.vs.Sector)
-corrplot(chisq$residuals, is.corr = FALSE)
-@
-    \end{minipage}
-    \begin{minipage}[c]{0.45\textwidth}
-        \centering
-    \resizebox{\textwidth}{!}{%
-    \begin{tabular}{l|r|r|r|r|}
-    \cline{2-5}
-                                 & Did/Do & Didn't/Do & Safer  & Didn' t/Don't \\ \hline
-    \multicolumn{1}{|l|}{University} & \textbf{-2.122} & 0.454 & 0.115  &  \textbf{2.939}\\ 
-    \multicolumn{1}{|l|}{University} & 5.71\% & 0.56\% & 0.04\%  &  \textbf{25.26\%}\\ \hline
-    \multicolumn{1}{|l|}{Vocational} & \textbf{2.122} & -0.454 & -0.115 & \textbf{-2.939}\\ 
-    \multicolumn{1}{|l|}{Vocational} & 12.38\% & 1.21\% & 0.08\% & \textbf{54.78\%}\\ \hline
-    \end{tabular}%
-    }
-    \end{minipage}
-    \begin{minipage}[c]{0.45\textwidth}
-        \centering
-<<discipline_postcovid_chisq, echo=FALSE, fig.width=17/2.54, fig.height=10/2.54, warning=FALSE>>=
-survey.pilot.postCovidChisq %>%mutate(Discipline = ifelse(as.character(Discipline) == "No", "Hum/Social Sciences", as.character(Discipline))) %>%
-  mutate(Discipline = ifelse(as.character(Discipline) == "Other", "Hum/Social Sciences", as.character(Discipline))) %>%
-  mutate(Discipline = ifelse(as.character(Discipline) == "Engineering", "Tech/Engineering", as.character(Discipline))) %>%
-  mutate(Discipline = ifelse(as.character(Discipline) == "Technology", "Tech/Engineering", as.character(Discipline))) %>%
-  mutate(Discipline = ifelse(as.character(Discipline) == "Humanities", "Hum/Social Sciences", as.character(Discipline))) %>%
-  mutate(Discipline = ifelse(as.character(Discipline) == "Social Sciences", "Hum/Social Sciences", as.character(Discipline))) %>%
-  mutate(Discipline = ifelse(as.character(Discipline) == "Sciences", "Biomed/Sciences", as.character(Discipline))) %>%
-  mutate(Discipline = ifelse(as.character(Discipline) == "Biomedicine", "Biomed/Sciences", as.character(Discipline)))->survey.pilot.postCovidChisq
-covidChanges.vs.Discipline<-table(survey.pilot.postCovidChisq$Discipline, survey.pilot.postCovidChisq$PostCOVID.changes)
-colnames(covidChanges.vs.Discipline)<- c("Did/do", "Didn't/do","safer", "Didn't/don't")
-chisq<-chisq.test(covidChanges.vs.Discipline)
-corrplot(chisq$residuals, is.corr = FALSE)
-@
-    \end{minipage}
-    \begin{minipage}[c]{0.45\textwidth}
-        \centering
-    \resizebox{\textwidth}{!}{%
-    \begin{tabular}{l|r|r|r|r|}
-    \cline{2-5}
-                                 & Did/Do & Didn't/Do & Safer & Didn' t/Don't \\ \hline
-    \multicolumn{1}{|l|}{Biomed/Sciences} & -1.265 &  0.733 & 1.452 & -0.588 \\ 
-    \multicolumn{1}{|l|}{Biomed/Sciences} & 3.50\% &  2.50\% & 9.94\% & 1.75\% \\ \hline
-    \multicolumn{1}{|l|}{Hum/Social} &  \textbf{-2.729} & \textbf{2.079} &  1.566 & 0.055\\ 
-    \multicolumn{1}{|l|}{Hum/Social} &  15.55\% & \textbf{19.19\%} &  11.04\% & 0.01\%\\ \hline
-    \multicolumn{1}{|l|}{Tech/Engineering} &  \textbf{3.278} &  \textbf{-2.318} &  \textbf{-2.448} & 0.412\\ 
-    \multicolumn{1}{|l|}{Tech/Engineering} &  11.06\% &  11.76\% &  \textbf{13.29\%} & 0.40\%\\ \hline
-    \end{tabular}%
-    }
-    \end{minipage}
-\end{center}
-    \caption{.}
-\label{figure:postcovid_chisq}
-\end{figure}
-
-\subsection{RQ2 - Which kind of chatbots would teachers find useful in their classes?}
-
-\begin{figure}[h!tbp]
-\begin{center}
-    \begin{minipage}[t]{0.85\textwidth}
-        \centering
-<<gender_chatbottype, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-survey.pilot.ChatbotType <- within(survey.pilot.ChatbotType, ChatbotType <- factor(ChatbotType, levels=names(sort(table(ChatbotType), decreasing=TRUE))))
-ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/gender_chatbottype.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.85\textwidth}
-        \centering
-<<sector_chatbottype, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/sector_chatbottype.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.85\textwidth}
-        \centering
-<<experience_chatbottype, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/experience_chatbottype.pdf}
-    \end{minipage}
-\end{center}
-    \caption{Types of chatbots.}
-\label{figure:chatbots_types}
-\end{figure}
-
-\subsection{RQ3 - Which kind of interaction do teachers prefer with their students?}
-
-\begin{figure}[h!tbp]
-\begin{center}
-    \begin{minipage}[t]{0.3\textwidth}
-        \centering
-<<gender_synch, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/gender_synch.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.3\textwidth}
-        \centering
-<<experience_sync, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/experience_synch.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.6\textwidth}
-        \centering
-<<discipline_synch, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering","No"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/discipline_synch.pdf}
-    \end{minipage}
-\end{center}
-    \caption{Synchronous or asynchronous interaction.}
-\label{figure:chatbots_synch}
-\end{figure}
-
-% ********************** ALBERTO HERE ****************************
-% ************************ New analysis ***********************
-
-\subsection{Data Analysis using Machine Learning}
+\section{Data Analysis using Machine Learning}
 

### 2021-06-27 edubots_surveys.Rnw
Update edubots_surveys.Rnw

@@
 ]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
+\author[
+  addressref={aff4},
+  email={o.tsivitanidou@cyens.org.cy}
+]{\inits{OT}\fnm{Olia} \snm{Tsivitanidou}}
 
@@
 
+% Olia - I do not think that we should say here that the first survey was done in two different forms.
+Wasn't the same survey for university and vocational teachers?
+It is just that they had to specify in which sector of education they were teaching, right?
+The second survey is another story...
+this is what I understand.
+
 The initial survey was done in two different forms, one for university and other for tertiary non-university teachers.
 Questions and responses were the same, except for the type of tertiary degrees that were taught.
-We got around 300 responses to this one, with two thirds of them coming from university teachers, the rest from high school teachers.
+A total of 282 teachers responded to the survey: 193 teaching at the University (68.4%) and 89 at high school (31.6%).
 In both cases, we used mainly mailing lists, as well as Telegram groups, to spread the link to the form.
@@
 The second survey followed the same paths, only in this case there was a single questionnaire.
+% Olia - see my comment above.
 It was filled by teachers that were also students in a teacher formation course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers to knew about it by emails from the authors, as well as from the vicedeanship for International Relations that included it in its newsletter.
@@
 We think, however that there's no explicit bias in this selection, although of course specific percentages will vary.
+% Olia - we shoudl say here a few words about the two surveys, and their main difference. Also, whch RQs each survey addresses etc.
 
@@
 
+For answering RQ1, teachers were queried about whether they use messaging apps in their classes, specifically, Telegram, WhatsApp, Slack, or any other messaging app, and whether they use messaging apps provided by their Academic Institution.
 According to the results summarized in Fig.
@@
 Finally, about 20\% also use Telegram.
+Only 19 teachers (6.7%) replied that they do not use any messaging app in their class.
 Although gender differences are not significant, female teachers answered they use instant messaging apps more than male teachers (about 10\% more).
@@
 
+%Olia - Isn't the following paragraph better fittng for RQ3? What kind interactions do teachers prefer with their students? 
 Regarding the social factor of chat groups that teachers use in class, according to Fig.
@@
 
+%Olia - A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
+The relation between the latter variable and the instructors’ sector was significant, X2 (4, N = 282) = 9.598, p =0.048.
+The frequencies cross tabulated are given in Table X.
+[we can add a table here with the crosstabulations].
+In effect, this finding indicates that how teachers responded to the use of messaging apps during the pandemic and in particular, whether they changed their habits in the use of apps for teaching purposes, was related to their sector (university vs vocational).
 The descriptive analysis in this case is done using a Chi-square test.

### 2021-06-27 edubots_surveys.Rnw
Update edubots_surveys.Rnw

@@
 \begin{document}
+\SweaveOpts{concordance=TRUE}
 %\SweaveOpts{concordance=TRUE}
@@
 
+Answer to these questions are plotted in Figure \ref{figure:chatbots_types} grouped by gender, sector and experience.
+As it was a multiple choice question, the counts are over the total number of people that answered.
+One of the most interesting questions that can arise from the plots, and the should require further study, is: Are our professors really aware of the possibilities of chatbots in the classroom?
+The reason to ask ourselves this question is due to the fact of the small number of responses for other uses in comparison with the other approaches proposed.
+Another way to loook about it is that, unless you provide the specific instructions on how to use a tool, the teaching staff is already too busy or burn out to think about innovation.
+
+Regarding Gender grouping, both gender agree in their uses, so it seems not relevant at all.
+When looking at the plot containing the sector differentiation it is interesting ot observe how university professors prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational/High School teachers.
+This seems reasonable as the frequency of seeing the students is smaller at the University so, automating the grade notification for continuous evaluation could seem much more comfortable using an automated tool than using the traditional platform.
+Furthermore, the high student/professor ratios that university professors have to deal with could be another reason to have a higher number of them willing to use chatbots for FAQs.
+This could ameliorate the number of misunderstandings and email overload that so many students might generate.
+
+The results, when grouping by experience, confirm the previous observation that experienced professors are not afraid of changes and are willing to accept new technological challenges, at least, in the same way that younger professors are.
+From this concrete plot it is interesting as well the fact that very few young/inexperience professors are willing to use chatbots for other uses.
+This reinforces the hypothesis thrown at the beginning of this section and, as these professors have less experience, they also have less field of view to think about ways of using chatbots.
+
 \begin{figure}[h!tbp]

### 2021-06-27 edubots_surveys.Rnw
added a few paragraphs to RQ2 https://github.com/JJ/edubots-paper/issues/15

@@
 ]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
-\author[
-  addressref={aff4},
-  email={o.tsivitanidou@cyens.org.cy}
-]{\inits{OT}\fnm{Olia} \snm{Tsivitanidou}}
 
@@
 
-% Olia - I do not think that we should say here that the first survey was done in two different forms.
-Wasn't the same survey for university and vocational teachers?
-It is just that they had to specify in which sector of education they were teaching, right?
-The second survey is another story...
-this is what I understand.
-
 The initial survey was done in two different forms, one for university and other for tertiary non-university teachers.
 Questions and responses were the same, except for the type of tertiary degrees that were taught.
-A total of 282 teachers responded to the survey: 193 teaching at the University (68.4%) and 89 at high school (31.6%).
+We got around 300 responses to this one, with two thirds of them coming from university teachers, the rest from high school teachers.
 In both cases, we used mainly mailing lists, as well as Telegram groups, to spread the link to the form.
@@
 The second survey followed the same paths, only in this case there was a single questionnaire.
-% Olia - see my comment above.
 It was filled by teachers that were also students in a teacher formation course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers to knew about it by emails from the authors, as well as from the vicedeanship for International Relations that included it in its newsletter.
@@
 We think, however that there's no explicit bias in this selection, although of course specific percentages will vary.
-% Olia - we shoudl say here a few words about the two surveys, and their main difference. Also, whch RQs each survey addresses etc.
 
@@
 
-For answering RQ1, teachers were queried about whether they use messaging apps in their classes, specifically, Telegram, WhatsApp, Slack, or any other messaging app, and whether they use messaging apps provided by their Academic Institution.
 According to the results summarized in Fig.
@@
 Finally, about 20\% also use Telegram.
-Only 19 teachers (6.7%) replied that they do not use any messaging app in their class.
 Although gender differences are not significant, female teachers answered they use instant messaging apps more than male teachers (about 10\% more).
@@
 
-%Olia - Isn't the following paragraph better fittng for RQ3? What kind interactions do teachers prefer with their students? 
 Regarding the social factor of chat groups that teachers use in class, according to Fig.
@@
 
-%Olia - A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
-The relation between the latter variable and the instructors’ sector was significant, X2 (4, N = 282) = 9.598, p =0.048.
-The frequencies cross tabulated are given in Table X.
-[we can add a table here with the crosstabulations].
-In effect, this finding indicates that how teachers responded to the use of messaging apps during the pandemic and in particular, whether they changed their habits in the use of apps for teaching purposes, was related to their sector (university vs vocational).
 The descriptive analysis in this case is done using a Chi-square test.

### 2021-06-28 edubots_surveys.Rnw
Adds address and compiles to correction
Some answers to @oliatsi and @amoragar

--- 2021-06-27 edubots_surveys.Rnw
@@
 \begin{document}
-\SweaveOpts{concordance=TRUE}
-%\SweaveOpts{concordance=TRUE}
 
@@
 
-% Antonio - Olia is missing. ;)
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \cny{UK}                                    % country
+}
+
+\address[id=aff4]{%
+  \orgname{CYENS},          % university, etc
+  \city{Nicosia},                              % city
+  \cny{Cyprus}                                    % country
 }
@@
 % TODO: introduction
-The introduction of new technologies in the classroom needs a combination of teacher education, 
+The introduction of new technologies in the classroom needs a combination of teacher motivation, 
 % Antonio - education -> knowledge? motivation? training?
+% Changed to motivation just in case we want to relate it to the technology acceptance model - JJ
 student willingness and (possibly new) skills in both.
@@
 % Antonio - This paragraph needs a conclusion. Why do we say (essentially) that chatbots are not needed and just a simple messaging bot is enough?
+% JJ - feel free to add one
 
@@
 % Antonio - 'deploy' instead implement? Since in Computer Sciences implement and program are synonyms...
+% JJ - deployment would be done by the university or whoever publishes the system. Deployment and implementation are two different things, anyway
 configure and maybe program chatbots.
@@
 The use of MIM, although possibly valuable by itself, can be enhanced via the use of chatbots, which, being conversational agents, usually dwell in systems where synchronous conversations take place. 
-% Antonio - I cannot understand this sentence... what's the point of the expression 'usually well'?
-% Dwell, not well - JJ
 The use of conversational agents (chatbots) in higher education is
@@
 interactive, using actual messaging platforms. 
-% Antonio - the last part of the sentence is not clear. Do you refer to all the aforementioned chatbots?
-% Just to Elvira? What messaging platforms do you mean?
-% Only Elvira - JJ
 In most cases, using the inset search engine was able to give you more up-to-date and
@@
 Questions and responses were the same, except for the type of tertiary degrees that were taught.
-A total of 282 teachers responded to the survey: 193 teaching at the University (68.4%) and 89 at high school (31.6%).
+A total of 282 teachers responded to the survey: 193 teaching at the University (68.4\%) and 89 at high school (31.6\%).
 In both cases, we used mainly mailing lists, as well as Telegram groups, to spread the link to the form.
@@
 
-The second survey followed the same paths, only in this case there was a single questionnaire.
-% Olia - see my comment above.
+The second survey followed the same paths, only in this case there was a single questionnaire. % Olia - see my comment above.
 It was filled by teachers that were also students in a teacher formation course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers to knew about it by emails from the authors, as well as from the vicedeanship for International Relations that included it in its newsletter.
@@
 % Olia - we shoudl say here a few words about the two surveys, and their main difference. Also, whch RQs each survey addresses etc. 
+% JJ - Yep...
 

### 2021-06-29 edubots_surveys.Rnw
Removing solved comments and asking a bit more

@@
 teachers.
+% Antonio - Not yet, this is the abstract and not mentioned yet that teachers are the target (just in the title). We speak about the community. But anyway. It is not very relevant.
 In this paper we have surveyed the opinions of tertiary education
@@
 looking at what they think about the introduction 
-% Antonio - inthe classroom
-% that's implied - JJ
 of messaging platforms and chatbots, what their needs are, what kind of use cases they see for
@@
 The introduction of new technologies in the classroom needs a combination of teacher motivation, 
-% Antonio - education -> knowledge? motivation? training?
-% Changed to motivation just in case we want to relate it to the technology acceptance model - JJ
 student willingness and (possibly new) skills in both.
@@
 % JJ - feel free to add one 
+% Antonio - The thing is I don't catch why are we saying that, since it is supossed that we should 'defend' the use of chatbots (from the project perspective, at least).
+Or if we don't want to defend them, at least not saying that they are useless most of times.
+XD
+% Moreover, considering that in the following paragraphs we are trying to 'sell' them.
 
@@
 % JJ - deployment would be done by the university or whoever publishes the system. Deployment and implementation are two different things, anyway
+% Antonio - Ok, but what I said is that 'implement' is a synonym of 'program' in this scope, and we write both in the same sentence as different things.
 configure and maybe program chatbots.
@@
 accurate answers than the ones provided by ELVIRA, which had to be updated by hand (and not too often).
-% Antonio - again, are you speaking about Elvira? 
-% If we say something like the last sentence, we are actually saying that chatbots are not useful... is this what we want to remark?
-% No, we're saying that chatbots like Elvira have limited usability, unlike chatbots in messaging platforms - JJ
 

### 2021-06-29 edubots_surveys.Rnw
A couple of fixings

@@
 In both cases, we used mainly mailing lists, as well as Telegram groups, to spread the link to the form.
-The university form was spread in Spanish (mainly Andaluc\'{\i}a and Galicia) universities, as well as Costa Rica and Mexico.
+The university form was spread in Spanish (mainly Andaluc\'{\i}a and Galicia) universities, and also Costa Rica and Mexico.
 The tertiary non-university teachers are mainly in Andaluc\'{\i}a.
@@
 The second survey followed the same paths, only in this case there was a single questionnaire. % Olia - see my comment above.
-It was filled by teachers that were also students in a teacher formation course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers to knew about it by emails from the authors, as well as from the vicedeanship for International Relations that included it in its newsletter.
+It was filled by teachers that were also students in a teacher formation course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers who knew about it by emails from the authors, or from the vicedeanship for International Relations that included it in its newsletter.
 This means that there might be a higher proportion of 1) teachers with few years of experience 2) teachers from the computer science faculty and 3) teachers from Granada.

### 2021-06-29 edubots_surveys.Rnw
Adding Interaction Media Features description

@@
 
-Along this line of work, our previous work \cite{MoraChatbots2021} aimed at analysing the expectations of students on this regard; recent papers have also analyzed how the use of chatbots affected the learning outcomes of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
+Along this line of research, our previous work \cite{MoraChatbots2021} aimed at analysing the expectations of students on this regard; recent papers have also analyzed how the use of chatbots affected the learning outcomes of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
 This paper analyzed conversational chatbots in an one-to-one setting, finding that learning really benefited from it.
@@
 
-Besides, the present study is focused on the other key actor in this challenge, i.e.
+Besides, the present work is focused on the other key actor in this challenge, i.e.
 educators.
-Their attitudes have been analyzed very recently by Chocarro et al.
+Their attitudes have been studied very recently by Chocarro et al.
 \cite{doi:10.1080/03055698.2020.1850426}, who, by analyzing surveys, created a {\em technology acceptance model} that proposed a series of features that would make chatbots easier to accept; among them, formality of language as well as easiness and usefulness.
@@
 % JJ - Yep...
+
+% Antonio - I include here the description of interaction features. Not sure if it is the best place for it. Move wherever it better fits.
+This survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are their feelings and preferences with regard to the use of communication tools with students, and even using bots or chatbots in the classroom.
+In addition the survey asked about the most relevant \textit{Interaction media features} for the teachers with respect to the potential tool to use in class. These features are:
+\begin{itemize}
+\item \textit{Analytics}: the tool allows to extract data about students performance or development during the academic course on the teacher's subject.
+\item \textit{Connectivity}: it is possible to link or connect the tool with other applications.
+\item \textit{Familiarity}: it is something already known or previously used, so no need to learn something new.
+\item \textit{Hidden Phone}: it is possible to use the tool without showing my phone number, normally using an alias or an own account independent from my physical telephone.
+\item \textit{Horizontally}: all the actors are at the same level (for instance, teacher and students). There is not a hierarchy.
+\item \textit{Official formation}: the university offers some training courses or talks about the tool (mainly for teachers). 
+\item \textit{Pluggability}: the tool offers different pluggins to the teacher, so he/she can deploy his/her own implemented modules.
+\item \textit{Sustainability}: teacher should not be worried about the tool maintenance.
+\item \textit{Unidirectionality}: only the teacher can publish information in the channel, i.e. students are not allowed to ask or answer.
+\item \textit{Officiality}: the tool has been granted by the university where the teacher works. This means normally that there is also technical support by university's staff.
+\item \textit{Synchrony}: it is possible to publish/receive the data or information in several devices and all of them will contain or show the same.
+\end{itemize}
+
+% Antonio - I'm not sure about the last one (Synchrony)
 

### 2021-06-29 edubots_surveys.Rnw
added RQ4 from Olia and added a qualitative interpretation - TODO Chi Table

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RQ1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{RQ1 - Are teachers already using messaging apps in their classes?}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RQ2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{RQ2 - Which kind of chatbots would teachers find useful in their classes?}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RQ3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{RQ3 - Which kind of interaction do teachers prefer with their students?}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RQ4 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{RQ4 - What kind of interaction media features do teachers value the most? }
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
+The majority of the teachers were aged 45-55 years old (70; 34.1\%), followed by individuals aged 35-45 (67, 32.7\%), and 25-35 (42; 20.5\%), while the minority was aged >55 years old (26; 12.7\%).
+In terms of teaching experience, 59 teachers (28.8\%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9\%), 0-5 years (51; 24.9\%) and more than 25 years of experience (44; 21.5\%).
+The teachers were asked about what kind of interaction media features they value the most; the frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
+
+\begin{table}[h!]
+\begin{tabular}{lcccc}
+\hline
+Interaction features & \multicolumn{2}{c}{Yes} & \multicolumn{2}{c}{No} \\
+\hline
+                    &  Freq. & \% &  Freq. & \% \\
+                    \cline{2-5}
+
+Analytics & 108 & 52.7 & 97 & 47.3 \\
+Connectivity & 119 & 58.0 & 86 & 42.0 \\
+Familiarity & 121 & 59.0 & 84 & 41.0 \\
+Hidden Phone & 113 & 55.1 & 92 & 44.9 \\
+Horizontally & 134 & 65.4 & 71 & 34.6 \\
+Official formation & 42 & 20.5 & 163 & 79.5 \\
+Pluggability & 65 & 31.7 & 140 & 68.3 \\
+Sustainability & 157 & 76.6 & 48 & 23.4\\
+Unidirectionality & 27 & 13.2 & 178 & 86.8 \\
+Officiality & 150 & 73.2 & 55 & 26.8 \\
+Synchrony & 45 & 22.0 & 160 & 78.0\\
+Other & 5 & 2.4 & 200 & 97.6 \\
+\hline
+\end{tabular}\caption{Interaction media features valued by teachers}
+\label{tab:interaction}
+\end{table}
+
+As it appears in the responses presented above, teachers’ responses are distributed between positive and negative in relation to the media features: analytics, connectivity, and hidden phone, while for the features: familiarity, horizontally, sustainability and officiality the majority provided a positive response, designating their preference to these features.
+On the other hand, the majority of teachers seems to consider not valuable the presence of official formation, pluggability, unidirectionality and synchrony in the interaction media features of messaging apps.
+
+From a qualitative point of view, these results show comsensus in a few key aspects:
+
+\begin{itemize}
+ \item Professors want to have support from their corresponding institution.
+This is probably due to the strict European data regulations and to avoid the overhead required to sing up and deleting students from year to year.
+
+ \item Professors need sustainability.
+The main reason is that implementing changes is expensive in terms of effort and prone to errors in the first years of implementing new procedures, therefore, it is logical that if chatbots or messaging platforms are to be introduced, they want this change to be as permanent as possible.
+
+ \item Keep it Simple.
+Media interaction requirements are simple and only a 2.4\% is requesting more features.
+This could be a sign of technological burn out produced by the previous and current courses where, due to the pandemic, the use of computer has increased significantly.
+
+\end{itemize}
+% TODO A chi-square test of independence was performed to examine the potential relationship among the various features. The statistically significant correlations are given in the table that follows.
 

### 2021-06-30 edubots_surveys.Rnw
removes No/NA values from data

@@
 }
-
 \address[id=aff3]{%
@@
 }
-
 \address[id=aff4]{%
@@
 survey.pilot %>%  mutate(Messaging.Organization =str_split(Messaging.Organization, ", ")) %>% unnest(cols = c(Messaging.Organization)) -> survey.pilot.MessagingOrganization
+survey.pilot.MessagingOrganization[as.character(survey.pilot.MessagingOrganization$Messaging.Organization)!="No", ] -> survey.pilot.MessagingOrganization
 
 survey.pilot %>% group_by( PostCOVID.changes ) %>% filter( n() > 1 ) -> survey.pilot.postCOVID
+survey.pilot.postCOVID[as.character(survey.pilot.postCOVID$PostCOVID.changes)!="No", ] -> survey.pilot.postCOVID
 
@@
 survey.pilot.chatbottype %>%  mutate(ChatbotType =str_split(ChatbotType, ",")) %>% unnest(cols = c(ChatbotType)) -> survey.pilot.ChatbotType
+survey.pilot.ChatbotType[as.character(survey.pilot.ChatbotType$Gender)!="No", ] -> survey.pilot.ChatbotType
+survey.pilot.ChatbotType[as.character(survey.pilot.ChatbotType$Experience)!="No", ] -> survey.pilot.ChatbotType
 
@@
 survey.interaction <- read.csv("data/survey-student-interaction-pilot-3-2021-EN.csv")
+survey.interaction[as.character(survey.interaction$Discipline)!="No", ] -> survey.interaction
 survey.interaction %>% group_by( Gender ) %>% summarise ( n = n() ) %>% mutate( freqGender = n/sum(n)) -> freqInteraction.Gender
@@
 freqbinded.Gender$source <- factor(freqbinded.Gender$source) 
-ggplot(freqbinded.Gender, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+freqbinded.Gender[as.character(freqbinded.Gender$Gender)!="No", ] -> df1
+ggplot(df1, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
 @
@@
 freqbinded.Age$source <- factor(freqbinded.Age$source) 
-ggplot(freqbinded.Age, aes(x = Age, y=freqAge, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+freqbinded.Age[as.character(freqbinded.Age$Age)!="No", ] -> df1
+ggplot(df1, aes(x = Age, y=freqAge, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
 @
@@
 freqbinded.Experience$source <- factor(freqbinded.Experience$source) 
-ggplot(freqbinded.Experience, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+freqbinded.Experience[as.character(freqbinded.Experience$Experience)!="No", ] -> df1
+ggplot(df1, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
 @        
@@
 <<gender_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
+survey.pilot[as.character(survey.pilot$Gender)!="No", ] -> df1
+ggplot(df1, aes(x = MessagingPlatformProvided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
 @
@@
 <<experience_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
+survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
+ggplot(df1, aes(x = MessagingPlatformProvided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
 @       
@@
 <<discipline_provided, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-
 ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformProvided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
@@
 <<gender_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformWhatsApp, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
+survey.pilot[as.character(survey.pilot$Gender)!="No", ] -> df1
+ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
 @
@@
 <<experience_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformWhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
+survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
+ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
 @       
@@
 <<gender_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformTelegram, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
+survey.pilot[as.character(survey.pilot$Gender)!="No", ] -> df1
+ggplot(df1, aes(x = MessagingPlatformTelegram, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
 @
@@
 <<experience_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformTelegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
+survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
+ggplot(df1, aes(x = MessagingPlatformTelegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
 @       
@@
     \multicolumn{1}{|l|}{University} & \textbf{-2.122} & 0.454 & 0.115  &  \textbf{2.939}\\ 
-    \multicolumn{1}{|l|}{University} & 5.71\% & 0.56\% & 0.04\%  &  \textbf{25.26\%}\\ \hline
+    \multicolumn{1}{|l|}{} & 5.71\% & 0.56\% & 0.04\%  &  \textbf{25.26\%}\\ \hline
     \multicolumn{1}{|l|}{Vocational} & \textbf{2.122} & -0.454 & -0.115 & \textbf{-2.939}\\ 
-    \multicolumn{1}{|l|}{Vocational} & 12.38\% & 1.21\% & 0.08\% & \textbf{54.78\%}\\ \hline
+    \multicolumn{1}{|l|}{} & 12.38\% & 1.21\% & 0.08\% & \textbf{54.78\%}\\ \hline
     \end{tabular}%
@@
     \multicolumn{1}{|l|}{Biomed/Sciences} & -1.265 &  0.733 & 1.452 & -0.588 \\ 
-    \multicolumn{1}{|l|}{Biomed/Sciences} & 3.50\% &  2.50\% & 9.94\% & 1.75\% \\ \hline
+    \multicolumn{1}{|l|}{} & 3.50\% &  2.50\% & 9.94\% & 1.75\% \\ \hline
     \multicolumn{1}{|l|}{Hum/Social} &  \textbf{-2.729} & \textbf{2.079} &  1.566 & 0.055\\ 
-    \multicolumn{1}{|l|}{Hum/Social} &  15.55\% & \textbf{19.19\%} &  11.04\% & 0.01\%\\ \hline
+    \multicolumn{1}{|l|}{} &  15.55\% & \textbf{19.19\%} &  11.04\% & 0.01\%\\ \hline
     \multicolumn{1}{|l|}{Tech/Engineering} &  \textbf{3.278} &  \textbf{-2.318} &  \textbf{-2.448} & 0.412\\ 
-    \multicolumn{1}{|l|}{Tech/Engineering} &  11.06\% &  11.76\% &  \textbf{13.29\%} & 0.40\%\\ \hline
+    \multicolumn{1}{|l|}{} &  11.06\% &  11.76\% &  \textbf{13.29\%} & 0.40\%\\ \hline
     \end{tabular}%

### 2021-06-30 scripts/summaries.R

@@ -41,7 +41,8 @@ freq.Gender$source<-rep("survey1")
 freqInteraction.Gender$source<-rep("survey2")
 freqbinded.Gender <- rbind(freq.Gender, freqInteraction.Gender)
 freqbinded.Gender$source <- factor(freqbinded.Gender$source) 
-ggplot(freqbinded.Gender, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+freqbinded.Gender[as.character(freqbinded.Gender$Gender)!="No", ] -> df1
+ggplot(df1, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
 
 freq.Age$source<-rep("survey1")
 freqInteraction.Age$source<-rep("survey2")

### 2021-06-30 edubots_surveys.Rnw
Updated version of the abstract
I have updated the abstract and pasted it on the top of the older abstract.  The two versions of the abstracts are separated by ***

@@
 \begin{abstract} % abstract
+Introducing new technologies such as messaging platforms, and the chatbots attached to them, in higher education, is rapidly growing.
+This introduction entails a careful consideration of the potential opportunities and/or challenges of adopting these tools.
+Hence, a thorough examination of the teachers’ experiences in this discipline can shed the light on the effective ways of enhancing students’ learning and boosting their progress.
+In this contribution, we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish-speaking countries.
+The focus of these surveys is to collect teachers’ feedback about their opinions of the introduction of the messaging platforms and chatbots in their classes, understand their needs and to gather information about the various educational use cases where these tools are valuable.
+In addition, an analysis of how and when teachers’ attitudes towards the use of these tools can vary across gender, experience, and their discipline of specialisation is presented.
+The key findings of this study highlight the factors that can contribute to the advancement of the adoption of messaging platforms and chatbots in higher education institutions to achieve the desired learning outcomes.
+****
 Introducing new technologies such as messaging platforms, and chatbots

### 2021-06-30 edubots_surveys.Rnw
Updated version of the abstract
I have updated the abstract and pasted it on the top of the older abstract.  The two versions of the abstracts are separated by ***

@@
 
+The key findings of this study shed the light on educators’ preference to use messaging applications that their institutions support.
+Technology adoption literature often focus on users’ perceptions of the technology’s usefulness and ease of use as important prerequisites for successful adoption and utilization.
+Nevertheless, in higher education, institutions’ role in integrating these tools to their educational systems can improve the uptake of these applications and shape the social and educational experiences of their students.
+This integration, to be fruitful, institutions have to ensure that these messaging applications not only are GDPR compliant to keep students’ data secure but also should provide IT support to all stakeholders who use the applications .
+
 %This section is repeated

### 2021-07-01 edubots_surveys.Rnw
Updated the Conclusion section

--- 2021-06-30 edubots_surveys.Rnw
@@
 \section{Conclusions}
+\begin
+The key findings of this study shed the light on educators’ preference to use messaging applications that their institutions support.
+Technology adoption literature often focus on users’ perceptions of the technology’s usefulness and ease of use as important prerequisites for successful adoption and utilization.
+Nevertheless, in higher education, institutions’ role in integrating these tools to their educational systems can improve the uptake of these applications and shape the social and educational experiences of their students.
+This integration, to be fruitful, institutions have to ensure that these messaging applications not only are GDPR compliant to keep students’ data secure but also should provide IT support to all stakeholders who use the applications .
+
+\end {Conclusions}
 \label{sec:concl}

### 2021-07-01 edubots_surveys.Rnw
Adapt to Latex commands.
Eliminates old text so that we can compare.

--- 2021-06-30 edubots_surveys.Rnw
@@
 The key findings of this study highlight the factors that can contribute to the advancement of the adoption of messaging platforms and chatbots in higher education institutions to achieve the desired learning outcomes.
-****
-Introducing new technologies such as messaging platforms, and chatbots
-attached to it, in higher education, requires careful consideration of
-all options, but above all, an examination of the attitudes of the
-affected community, especially those that will need to handle them,
-% Antonio - I would say 'to manage them'. Students should also handle new technologies. ;)
-% We're talking about teachers here, who need to handle the outcomes and introduce them in class - JJ
-teachers.
-% Antonio - Not yet, this is the abstract and not mentioned yet that teachers are the target (just in the title). We speak about the community. But anyway. It is not very relevant.
-In this paper we have surveyed the opinions of tertiary education
-teachers based mainly in Spain and Spanish-speaking countries, 
-looking at what they think about the introduction 
-of messaging platforms and chatbots, what their needs are, what kind of use cases they see for
-them, and in what kind of environment they think its use will be
-valuable. We will examine how and when these attitudes vary across
-gender, experience, and other factors, such as the broad discipline
-they are teaching. Our conclusions might help with the adoption of
-messaging platforms in an educational setting, as well as chatbots or
-other kind of bots, by higher education institution, and how these
-must be introduced to teachers so that it helps them achieve desired
-educational outcomes. 
 \end{abstract}

### 2021-07-02 edubots_surveys.Rnw
Update edubots_surveys.Rnw

@@
 \item{ RQ3 - Which kind of interaction do teachers prefer with their students? }
+\item{ RQ4 - What kind of interaction media features do teachers value the most? }
 
@@
 Our intention from the beginning was to try and gather a sufficient amount of responses in all sectors, as well as cover different sectors of higher education.
-This is why we created a Google Form, in Spanish, which was intended to be answered in a very short amount of time.
+In doing so, an online survey was administered (i.e., Google Form), in Spanish, which was intended to be answered in a very short amount of time.
 Initially, our intention was to mirror the questions used in \cite{MoraChatbots2021}; however, an initial exploration of results led us to create a second survey.
+The survey items focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider useful to be used in their teaching, and the type of interactions that teachers prefer to have with their students while using messaging apps in their teaching.
 % Questions should probably be included here.
@@
 Questions and responses were the same, except for the type of tertiary degrees that were taught.
-A total of 282 teachers responded to the survey: 193 teaching at the University (68.4\%) and 89 at high school (31.6\%).
 In both cases, we used mainly mailing lists, as well as Telegram groups, to spread the link to the form.
@@
 Dissemination and answers took place in the first quarter of 2021, post-pandemic and while, at least in Spain, many universities had mandatory virtual teaching.
-
-The second survey followed the same paths, only in this case there was a single questionnaire. % Olia - see my comment above.
+A total of 282 teachers responded to the survey: 193 teaching at the University (68.4\%) and 89 at high school (31.6\%).
+
+The second survey followed the same paths, only in this case there was a single questionnaire, and with a different scope, focusing on the kind of interaction media features that teachers value the most.
+% Olia - see my comment above.
 It was filled by teachers that were also students in a teacher formation course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers who knew about it by emails from the authors, or from the vicedeanship for International Relations that included it in its newsletter.
@@
 We think, however that there's no explicit bias in this selection, although of course specific percentages will vary.
-% Olia - we shoudl say here a few words about the two surveys, and their main difference. Also, whch RQs each survey addresses etc. 
+% Olia - we shoudl say here a few words about the two surveys, and their main difference. Also, which RQs each survey addresses etc. 
 % JJ - Yep...
@@
 % Antonio - I include here the description of interaction features. Not sure if it is the best place for it. Move wherever it better fits.
-This survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are their feelings and preferences with regard to the use of communication tools with students, and even using bots or chatbots in the classroom.
+Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are their feelings and preferences with regard to the use of communication tools with students, and even using bots or chatbots in the classroom.
 In addition the survey asked about the most relevant \textit{Interaction media features} for the teachers with respect to the potential tool to use in class. These features are:
@@
 
-%Olia - A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
+A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
 The relation between the latter variable and the instructors’ sector was significant, X2 (4, N = 282) = 9.598, p =0.048.
-The frequencies cross tabulated are given in Table X.
-[we can add a table here with the crosstabulations].
+The frequencies cross tabulated are given in Table 2.
 In effect, this finding indicates that how teachers responded to the use of messaging apps during the pandemic and in particular, whether they changed their habits in the use of apps for teaching purposes, was related to their sector (university vs vocational).
+The relationships between changes in the use of messaging apps, due to the covid-19 pandemic, and the instructors’ discipline, X2 (24, N = 282) = 44.856, p =0.006, as well as the gender, X2 (8, N = 282) = 16.249, p= 0.039 were also significant.
+% Olia - Fran, please also add here tables 1 and 2, as in the attachment that I have sent you. And check for repetitions in the following paragraph that you added. thank you.
 The descriptive analysis in this case is done using a Chi-square test.
@@
 
+For answering RQ2, teachers were provided with a list of different potential chatbot functionalities (use cases) and were requested to respond on whether each given use case would be useful in their classes.
+The findings are summarized in the table that follows.
+% Fran pleas add table 3 here, as in the attachment I sent you, along with the given caption. 
+For the findings it occurs that the most favourable use case for chatbots in Higher Education and vocational training is their use for the facilitation of an agenda formation (171 positive response, 60.6%), followed by the FAQs use case (148 positive responses, 52.5%) and the sharing class material use case (136; 48.2%).
+A chi-square test of independence was performed to examine the relation among participants’ preferences for particular chatbot use cases.
+The relation between agenda and the FAQs use case was significant, X2 (1, N = 282) = 10.467, p =0.001.
+The frequencies cross tabulated are given in Table 4.
+Out of the 171 teachers who consider useful the use of chatbots for agenda preparation in the class, 103 also consider useful chatbots’ use for FAQs.
+% Fran pleas add table 4 here, as in the attachment I sent you, along with the given caption. 
 Answer to these questions are plotted in Figure \ref{figure:chatbots_types} grouped by gender, sector and experience.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+For answering RQ3, teachers were provided with a list of different kind of interactions that may take place among students and between students and the teacher, with the use of messaging apps.
+The findings are summarized in the table that follows.
+% Fran please add table 5, as per attachment, along with the given caption.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RQ4 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{RQ4 - What kind of interaction media features do teachers value the most?}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+A total of 205 teachers responded to the second survey, 124 males (60.5%), 65 females (31.7%) and 16 individuals who chose not to identify their gender (7.8%).
+The majority of the teachers were aged 45-55 years old (70; 34.1%), followed by individuals aged 35-45 (67, 32.7%), and 25-35 (42; 20.5%), while the minority was aged >55 years old (26; 12.7%).
+In terms of teaching experience, 59 teachers (28.8%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9%), 0-5 years (51; 24.9%) and more than 25 years of experience (44; 21.5%).
+The teachers were asked about what kind of interaction media features they value the most; the frequencies and percentages of their responses are given in the table that follows.
+% Fran, please add table 6 here, as per attachment, along with the given caption.
+
+As it appears in the responses presented above, teachers’ responses are distributed between positive and negative in relation to the media features: analytics, connectivity, and hidden phone, while for the features: familiarity, horizontally, sustainability and officiality the majority provided a positive response, designating their preference to these features.
+On the other hand, the majority of teachers seems to consider not valuable the presence of official formation, pluggability, unidirectionality and synchrony in the interaction media features of messaging apps.
+
+A chi-square test of independence was performed to examine the potential relationship among the various features. The statistically significant correlations are given in the table that follows.  
+% Fran, please add table 7 here, as per attachment, along with the given caption.
+
+Finally, A two-step cluster analysis was conducted, with a log-likelihood distance measure adopted, to explore how the cases could be grouped based on their preferences of specific interaction media features, and which features have larger predictor importance for the clustering.
+Two clusters occurred from the analysis: cluster 1 (n=78, 60.9%) was comprise of instructors who did not value interaction media pluggability, connectivity, official formation, but valued interaction media analytics, familiarity, officiality, while cluster 2 (n=50, 39.1%) was comprise of instructors from which the majority did not value media analytics, official formation, familiarity, but valued pluggability, connectivity, and officiality.
+Interaction media pluggability appears to have the most important predictor importance in the clustering of cases (predictor importance = 1.0), whilst media unidirectionality was the least important factor (predictor importance = 0.04).
+The cluster quality is fair, but not a good one (silhouette measure of cohesion and separation).
+% Fran, please add figure 1 here as per attachment, along with the given caption.
 

### 2021-07-02 edubots_surveys.Rnw
integrates Olia' s contribution refs #24

@@
 \usepackage{amsthm,amsmath}
+\usepackage{multirow}
 
@@
 A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
-The relation between the latter variable and the instructors’ sector was significant, X2 (4, N = 282) = 9.598, p =0.048.
-The frequencies cross tabulated are given in Table 2.
+The relation between the latter variable and the instructors’ sector was significant, $X^{2}_{(4, N = 282)} = 9.598$, $p =0.048$.
+The frequencies cross tabulated are given in Table \ref{tab:sector*covid}.
 In effect, this finding indicates that how teachers responded to the use of messaging apps during the pandemic and in particular, whether they changed their habits in the use of apps for teaching purposes, was related to their sector (university vs vocational).
-The relationships between changes in the use of messaging apps, due to the covid-19 pandemic, and the instructors’ discipline, X2 (24, N = 282) = 44.856, p =0.006, as well as the gender, X2 (8, N = 282) = 16.249, p= 0.039 were also significant.
-% Olia - Fran, please also add here tables 1 and 2, as in the attachment that I have sent you. And check for repetitions in the following paragraph that you added. thank you.
+The relationships between changes in the use of messaging apps, due to the covid-19 pandemic, and the instructors’ discipline, $X^{2}_{(24, N = 282)} = 44.856$, $p =0.006$, as well as the gender, $X^{2}_{(8, N = 282)} = 16.249$, $p= 0.039$ were also significant.
+
+%TODO: This table is not referenced in the text
+\begin{table}[h!tbp]
+\begin{tabular}{lllll}
+\hline
+\multicolumn{1}{c}{Messaging App} & \multicolumn{2}{c}{Yes} & \multicolumn{2}{l}{No} \\ \cline{2-5} 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{Frequency} & \multicolumn{1}{c}{\%} & Frequency & \multicolumn{1}{c}{\%} \\ \hline
+Telegram & 62 & 22.0 & 220 & 78.0 \\
+WhatsApp & 124 & 44.0 & 158 & 56.0 \\
+Slack & 15 & 5.3 & 267 & 94.7 \\
+Other & 60 & 21.3 & 222 & 78.7 \\
+\begin{tabular}[c]{@{}l@{}}Provided by the Academic\\ Institution\end{tabular} & 159 & 56.4 & 123 & 43.6 \\
+None & 19 & 6.7 & 263 & 93.3 \\ \hline
+\end{tabular}
+\caption{Use of messaging apps in class}
+\label{tab:use_messapps}
+\end{table}
+
+\begin{table}[h!tbp]
+\begin{tabular}{llccc}
+\hline
+ & \multicolumn{1}{c}{} & \multicolumn{2}{c}{Sector} & Total \\ \cline{3-5} 
+ & \multicolumn{1}{c}{} & \begin{tabular}[c]{@{}c@{}}University \\ (f)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Vocational\\ (f)\end{tabular} &  \\ \cline{2-5} 
+\multirow{4}{*}{\begin{tabular}[c]{@{}l@{}}Post-covid\\ changes\end{tabular}} & \begin{tabular}[c]{@{}l@{}}Yes, I use a safer messaging \\ app now\end{tabular} & 27 & 13 & 40 \\
+ & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use any \\ messaging app before, but \\ do use it now\end{tabular} & 31 & 13 & 44 \\
+ & \begin{tabular}[c]{@{}l@{}}No, I did use it before and \\ use it now\end{tabular} & 105 & 60 & 165 \\
+ & \begin{tabular}[c]{@{}l@{}}No, I didn’t use it before and \\ don’t use it now\end{tabular} & 22 & 2 & 24 \\
+Total &  & 193 & 89 & 282 \\ \hline
+\end{tabular}
+\caption{Sector * post-covid changes crosstabulation}
+\label{tab:sector*covid}
+\end{table}
+
+% Olia - TODO: check for repetitions in the following paragraph that you added. thank you.
 The descriptive analysis in this case is done using a Chi-square test.
@@
 For answering RQ2, teachers were provided with a list of different potential chatbot functionalities (use cases) and were requested to respond on whether each given use case would be useful in their classes.
-The findings are summarized in the table that follows.
-% Fran pleas add table 3 here, as in the attachment I sent you, along with the given caption. 
-For the findings it occurs that the most favourable use case for chatbots in Higher Education and vocational training is their use for the facilitation of an agenda formation (171 positive response, 60.6%), followed by the FAQs use case (148 positive responses, 52.5%) and the sharing class material use case (136; 48.2%).
+The findings are summarized in Table \ref{tab:chatbottypes}.
+
+\begin{table}[h!tbp]
+\begin{tabular}{lllll}
+\hline
+\multicolumn{1}{c}{Chatbot use cases} & \multicolumn{2}{c}{Yes} & \multicolumn{2}{l}{No} \\ \cline{2-5} 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{Frequency} & \multicolumn{1}{c}{\%} & Frequency & \multicolumn{1}{c}{\%} \\ \hline
+Answering to students' FAQs & 148 & 52.5 & 134 & 47.5 \\
+Assigning student grades & 113 & 40.1 & 169 & 59.9 \\
+Facilitating agenda information & 171 & 60.6 & 111 & 39.4 \\
+Sharing class materials & 136 & 48.2 & 146 & 51.8 \\
+Others & 25 & 8.9 & 257 & 91.1 \\ \hline
+\end{tabular}
+\caption{Perceived useful chatbot use cases}
+\label{tab:chatbottypes}
+\end{table}
+
+For the findings it occurs that the most favourable use case for chatbots in Higher Education and vocational training is their use for the facilitation of an agenda formation (171 positive response, 60.6\%), followed by the FAQs use case (148 positive responses, 52.5\%) and the sharing class material use case (136; 48.2\%).
 A chi-square test of independence was performed to examine the relation among participants’ preferences for particular chatbot use cases.
-The relation between agenda and the FAQs use case was significant, X2 (1, N = 282) = 10.467, p =0.001.
-The frequencies cross tabulated are given in Table 4.
+The relation between agenda and the FAQs use case was significant, $X^{2}_{(1, N = 282)} = 10.467$, $p =0.001$.
+The frequencies cross tabulated are given in Table \ref{tab:agenda*faq}.
 Out of the 171 teachers who consider useful the use of chatbots for agenda preparation in the class, 103 also consider useful chatbots’ use for FAQs.
-% Fran pleas add table 4 here, as in the attachment I sent you, along with the given caption. 
+
+\begin{table}[h!tbp]
+\begin{tabular}{llccc}
+\hline
+ & \multicolumn{1}{c}{} & \multicolumn{2}{c}{FAQs} & Total \\ \cline{3-5} 
+ & \multicolumn{1}{c}{} & Yes & No &  \\ \cline{2-5} 
+\multirow{2}{*}{Agenda} & Yes & 103 & 68 & 171 \\
+ & No & 45 & 66 & 111 \\
+Total &  & 148 & 134 & 282 \\ \hline
+\end{tabular}
+\caption{Agenda use case * FAQs use case crosstabulation }
+\label{tab:agenda*faq}
+\end{table}
+
 Answer to these questions are plotted in Figure \ref{figure:chatbots_types} grouped by gender, sector and experience.
@@
 For answering RQ3, teachers were provided with a list of different kind of interactions that may take place among students and between students and the teacher, with the use of messaging apps.
-The findings are summarized in the table that follows.
-% Fran please add table 5, as per attachment, along with the given caption.
+The findings are summarized in Table \ref{tab:kindinteractions}.
+
+\begin{table}[h!tbp]
+\begin{tabular}{lllll}
+\hline
+\multicolumn{1}{c}{Kind of interactions} & \multicolumn{2}{c}{Yes} & \multicolumn{2}{l}{No} \\ \cline{2-5} 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{Frequency} & \multicolumn{1}{c}{\%} & Frequency & \multicolumn{1}{c}{\%} \\ \hline
+\begin{tabular}[c]{@{}l@{}}Chat interactions among \\ students in the same course\end{tabular} & 171 & 60.6 & 110 & 39.0 \\
+\begin{tabular}[c]{@{}l@{}}Chat interactions among students, \\ teachers, and the faculty\end{tabular} & 13 & 4.6 & 269 & 95.4 \\
+\begin{tabular}[c]{@{}l@{}}Chat interactions among students \\ of the same study year and teachers\end{tabular} & 51 & 18.1 & 231 & 81.9 \\
+\begin{tabular}[c]{@{}l@{}}Teacher not being part of the \\ interaction\end{tabular} & 113 & 40.1 & 169 & 59.9 \\ \hline
+\end{tabular}
+\caption{Kind of interactions preferred}
+\label{tab:kindinteractions}
+\end{table}
 
@@
 
-\subsection{RQ4 - What kind of interaction media features do teachers value the most?}
+%\subsection{RQ4 - What kind of interaction media features do teachers value the most?}
 
@@
 
-A total of 205 teachers responded to the second survey, 124 males (60.5%), 65 females (31.7%) and 16 individuals who chose not to identify their gender (7.8%).
-The majority of the teachers were aged 45-55 years old (70; 34.1%), followed by individuals aged 35-45 (67, 32.7%), and 25-35 (42; 20.5%), while the minority was aged >55 years old (26; 12.7%).
-In terms of teaching experience, 59 teachers (28.8%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9%), 0-5 years (51; 24.9%) and more than 25 years of experience (44; 21.5%).
+%A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
+The majority of the teachers were aged 45-55 years old (70; 34.1\%), followed by individuals aged 35-45 (67, 32.7\%), and 25-35 (42; 20.5\%), while the minority was aged >55 years old (26; 12.7\%).
+In terms of teaching experience, 59 teachers (28.8\%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9\%), 0-5 years (51; 24.9\%) and more than 25 years of experience (44; 21.5\%).
 The teachers were asked about what kind of interaction media features they value the most; the frequencies and percentages of their responses are given in the table that follows.
-% Fran, please add table 6 here, as per attachment, along with the given caption.
-
-As it appears in the responses presented above, teachers’ responses are distributed between positive and negative in relation to the media features: analytics, connectivity, and hidden phone, while for the features: familiarity, horizontally, sustainability and officiality the majority provided a positive response, designating their preference to these features.
-On the other hand, the majority of teachers seems to consider not valuable the presence of official formation, pluggability, unidirectionality and synchrony in the interaction media features of messaging apps.
-
-A chi-square test of independence was performed to examine the potential relationship among the various features. The statistically significant correlations are given in the table that follows.  
-% Fran, please add table 7 here, as per attachment, along with the given caption.
-
-Finally, A two-step cluster analysis was conducted, with a log-likelihood distance measure adopted, to explore how the cases could be grouped based on their preferences of specific interaction media features, and which features have larger predictor importance for the clustering.
-Two clusters occurred from the analysis: cluster 1 (n=78, 60.9%) was comprise of instructors who did not value interaction media pluggability, connectivity, official formation, but valued interaction media analytics, familiarity, officiality, while cluster 2 (n=50, 39.1%) was comprise of instructors from which the majority did not value media analytics, official formation, familiarity, but valued pluggability, connectivity, and officiality.
-Interaction media pluggability appears to have the most important predictor importance in the clustering of cases (predictor importance = 1.0), whilst media unidirectionality was the least important factor (predictor importance = 0.04).
-The cluster quality is fair, but not a good one (silhouette measure of cohesion and separation).
-% Fran, please add figure 1 here as per attachment, along with the given caption.
 
@@
 This could be a sign of technological burn out produced by the previous and current courses where, due to the pandemic, the use of computer has increased significantly.
-
 \end{itemize}
-% TODO A chi-square test of independence was performed to examine the potential relationship among the various features. The statistically significant correlations are given in the table that follows.
+
+A chi-square test of independence was performed to examine the potential relationship among the various features.
+The statistically significant correlations are given in Table \ref{tab:interactionfeatures}.
+
+\begin{table}[h!tbp]
+\centering
+\resizebox{\textwidth}{!}{\begin{tabular}{llllllllllll}
+\hline
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{Analytics} & Connectivity & Familiarity & Hidden phone & Horizontallity & \begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} & Pluggability & Sustainability & Unidirectionality & Officiality & Synchrony \\ \hline
+Analytics & \multicolumn{1}{c}{-} & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 12.172^{***}$} & $X^{2}_{(1, N = 205)} = 4.855^{*}$ & ns & ns & $X^{2}_{(1, N = 205)} = 4.144^{*}$ & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 12.490^{***}$} & $X^{2}_{(1, N = 205)} = 4.314^{*}$ & ns & ns & ns \\
+Connectivity & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-} & ns & ns & $X^{2}_{(1, N = 205)} = 5.971^{***}$ & ns & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 16.286^{***}$} & ns & ns & ns & ns \\
+Familiarity &  &  & - & ns & ns & ns & ns & ns & ns & ns & ns \\
+Hidden phone &  &  &  & - & ns & $X^{2}_{(1, N = 205)} = 5.678^{*}$ & $X^{2}_{(1, N = 205)} = 4.683^{*}$ & ns & $X^{2}_{(1, N = 205)} = 4.515^{*}$ & ns & ns \\
+Horizontallity &  &  &  &  & - & ns & ns & ns & ns & $X^{2}_{(1, N = 205)} = 5.453^{*}$ & ns \\
+\begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} &  &  &  &  &  & - & $X^{2}_{(1, N = 205)} = 8.163^{**}$ & ns & ns & ns & ns \\
+Pluggability &  &  &  &  &  &  & - & ns & ns & ns & ns \\
+Sustainability &  &  &  &  &  &  &  & - & ns & ns & ns \\
+Unidirectionality &  &  &  &  &  &  &  &  & - & ns & ns \\
+Officiality &  &  &  &  &  &  &  &  &  & - & ns \\
+Synchrony & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  &  &  & \multicolumn{1}{c}{} &  &  &  & - \\ \hline
+\end{tabular}}
+\caption{Interaction media features analysis ($^{***}p<0.001$, $^{**}p<0.01$, $^{*}p<0.05$).}
+\label{tab:interactionfeatures}
+\end{table}
+
+Finally, A two-step cluster analysis was conducted, with a log-likelihood distance measure adopted, to explore how the cases could be grouped based on their preferences of specific interaction media features, and which features have larger predictor importance for the clustering.
+Two clusters occurred from the analysis: cluster 1 (n=78, 60.9\%) was comprise of instructors who did not value interaction media pluggability, connectivity, official formation, but valued interaction media analytics, familiarity, officiality, while cluster 2 (n=50, 39.1\%) was comprise of instructors from which the majority did not value media analytics, official formation, familiarity, but valued pluggability, connectivity, and officiality.
+Interaction media pluggability appears to have the most important predictor importance in the clustering of cases (predictor importance = 1.0), whilst media unidirectionality was the least important factor (predictor importance = 0.04).
+The cluster quality is fair, but not a good one (silhouette measure of cohesion and separation).
+
+% Fran, please add figure 1 here as per attachment, along with the given caption.
 

### 2021-07-02 edubots_surveys.Rnw
integrates Olia two cluster analysis fig refs #24

@@
 
+%TODO - table fits better in landscape? try to fit in page size 
 \begin{table}[h!tbp]
@@
 
-Finally, A two-step cluster analysis was conducted, with a log-likelihood distance measure adopted, to explore how the cases could be grouped based on their preferences of specific interaction media features, and which features have larger predictor importance for the clustering.
+Finally, a two-step cluster analysis was conducted, with a log-likelihood distance measure adopted, to explore how the cases could be grouped based on their preferences of specific interaction media features, and which features have larger predictor importance for the clustering (see Fig.
+\ref{figure:predictor}).
 Two clusters occurred from the analysis: cluster 1 (n=78, 60.9\%) was comprise of instructors who did not value interaction media pluggability, connectivity, official formation, but valued interaction media analytics, familiarity, officiality, while cluster 2 (n=50, 39.1\%) was comprise of instructors from which the majority did not value media analytics, official formation, familiarity, but valued pluggability, connectivity, and officiality.
@@
 
-% Fran, please add figure 1 here as per attachment, along with the given caption.
+\begin{figure}[h!tbp]
+\begin{center}
+\includegraphics[width=\textwidth]{figure/2clusteranalysis.pdf}
+\end{center}
+    \caption{Two-step cluster analysis for interaction media features: predictor importance}
+\label{figure:predictor}
+\end{figure}
 

### 2021-07-02 edubots_surveys.Rnw
Check in

--- 2021-07-02 edubots_surveys.Rnw
@@
 \item{ RQ3 - Which kind of interaction do teachers prefer with their students? }
-\item{ RQ4 - What kind of interaction media features do teachers value the most? }
 
@@
 Our intention from the beginning was to try and gather a sufficient amount of responses in all sectors, as well as cover different sectors of higher education.
-In doing so, an online survey was administered (i.e., Google Form), in Spanish, which was intended to be answered in a very short amount of time.
+This is why we created a Google Form, in Spanish, which was intended to be answered in a very short amount of time.
 Initially, our intention was to mirror the questions used in \cite{MoraChatbots2021}; however, an initial exploration of results led us to create a second survey.
-The survey items focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider useful to be used in their teaching, and the type of interactions that teachers prefer to have with their students while using messaging apps in their teaching.
 % Questions should probably be included here.
@@
 Questions and responses were the same, except for the type of tertiary degrees that were taught.
+A total of 282 teachers responded to the survey: 193 teaching at the University (68.4\%) and 89 at high school (31.6\%).
 In both cases, we used mainly mailing lists, as well as Telegram groups, to spread the link to the form.
@@
 Dissemination and answers took place in the first quarter of 2021, post-pandemic and while, at least in Spain, many universities had mandatory virtual teaching.
-A total of 282 teachers responded to the survey: 193 teaching at the University (68.4\%) and 89 at high school (31.6\%).
-
-The second survey followed the same paths, only in this case there was a single questionnaire, and with a different scope, focusing on the kind of interaction media features that teachers value the most.
-% Olia - see my comment above.
+
+The second survey followed the same paths, only in this case there was a single questionnaire. % Olia - see my comment above.
 It was filled by teachers that were also students in a teacher formation course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers who knew about it by emails from the authors, or from the vicedeanship for International Relations that included it in its newsletter.
@@
 We think, however that there's no explicit bias in this selection, although of course specific percentages will vary.
-% Olia - we shoudl say here a few words about the two surveys, and their main difference. Also, which RQs each survey addresses etc. 
+% Olia - we shoudl say here a few words about the two surveys, and their main difference. Also, whch RQs each survey addresses etc. 
 % JJ - Yep...
@@
 % Antonio - I include here the description of interaction features. Not sure if it is the best place for it. Move wherever it better fits.
-Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are their feelings and preferences with regard to the use of communication tools with students, and even using bots or chatbots in the classroom.
+This survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are their feelings and preferences with regard to the use of communication tools with students, and even using bots or chatbots in the classroom.
 In addition the survey asked about the most relevant \textit{Interaction media features} for the teachers with respect to the potential tool to use in class. These features are:
@@
 
-A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
+%Olia - A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
 The relation between the latter variable and the instructors’ sector was significant, X2 (4, N = 282) = 9.598, p =0.048.
-The frequencies cross tabulated are given in Table 2.
+The frequencies cross tabulated are given in Table X.
+[we can add a table here with the crosstabulations].
 In effect, this finding indicates that how teachers responded to the use of messaging apps during the pandemic and in particular, whether they changed their habits in the use of apps for teaching purposes, was related to their sector (university vs vocational).
-The relationships between changes in the use of messaging apps, due to the covid-19 pandemic, and the instructors’ discipline, X2 (24, N = 282) = 44.856, p =0.006, as well as the gender, X2 (8, N = 282) = 16.249, p= 0.039 were also significant.
-% Olia - Fran, please also add here tables 1 and 2, as in the attachment that I have sent you. And check for repetitions in the following paragraph that you added. thank you.
 The descriptive analysis in this case is done using a Chi-square test.
@@
 
-For answering RQ2, teachers were provided with a list of different potential chatbot functionalities (use cases) and were requested to respond on whether each given use case would be useful in their classes.
-The findings are summarized in the table that follows.
-% Fran pleas add table 3 here, as in the attachment I sent you, along with the given caption. 
-For the findings it occurs that the most favourable use case for chatbots in Higher Education and vocational training is their use for the facilitation of an agenda formation (171 positive response, 60.6%), followed by the FAQs use case (148 positive responses, 52.5%) and the sharing class material use case (136; 48.2%).
-A chi-square test of independence was performed to examine the relation among participants’ preferences for particular chatbot use cases.
-The relation between agenda and the FAQs use case was significant, X2 (1, N = 282) = 10.467, p =0.001.
-The frequencies cross tabulated are given in Table 4.
-Out of the 171 teachers who consider useful the use of chatbots for agenda preparation in the class, 103 also consider useful chatbots’ use for FAQs.
-% Fran pleas add table 4 here, as in the attachment I sent you, along with the given caption. 
 Answer to these questions are plotted in Figure \ref{figure:chatbots_types} grouped by gender, sector and experience.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-For answering RQ3, teachers were provided with a list of different kind of interactions that may take place among students and between students and the teacher, with the use of messaging apps.
-The findings are summarized in the table that follows.
-% Fran please add table 5, as per attachment, along with the given caption.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RQ4 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{RQ4 - What kind of interaction media features do teachers value the most?}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-A total of 205 teachers responded to the second survey, 124 males (60.5%), 65 females (31.7%) and 16 individuals who chose not to identify their gender (7.8%).
-The majority of the teachers were aged 45-55 years old (70; 34.1%), followed by individuals aged 35-45 (67, 32.7%), and 25-35 (42; 20.5%), while the minority was aged >55 years old (26; 12.7%).
-In terms of teaching experience, 59 teachers (28.8%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9%), 0-5 years (51; 24.9%) and more than 25 years of experience (44; 21.5%).
-The teachers were asked about what kind of interaction media features they value the most; the frequencies and percentages of their responses are given in the table that follows.
-% Fran, please add table 6 here, as per attachment, along with the given caption.
-
-As it appears in the responses presented above, teachers’ responses are distributed between positive and negative in relation to the media features: analytics, connectivity, and hidden phone, while for the features: familiarity, horizontally, sustainability and officiality the majority provided a positive response, designating their preference to these features.
-On the other hand, the majority of teachers seems to consider not valuable the presence of official formation, pluggability, unidirectionality and synchrony in the interaction media features of messaging apps.
-
-A chi-square test of independence was performed to examine the potential relationship among the various features. The statistically significant correlations are given in the table that follows.  
-% Fran, please add table 7 here, as per attachment, along with the given caption.
-
-Finally, A two-step cluster analysis was conducted, with a log-likelihood distance measure adopted, to explore how the cases could be grouped based on their preferences of specific interaction media features, and which features have larger predictor importance for the clustering.
-Two clusters occurred from the analysis: cluster 1 (n=78, 60.9%) was comprise of instructors who did not value interaction media pluggability, connectivity, official formation, but valued interaction media analytics, familiarity, officiality, while cluster 2 (n=50, 39.1%) was comprise of instructors from which the majority did not value media analytics, official formation, familiarity, but valued pluggability, connectivity, and officiality.
-Interaction media pluggability appears to have the most important predictor importance in the clustering of cases (predictor importance = 1.0), whilst media unidirectionality was the least important factor (predictor importance = 0.04).
-The cluster quality is fair, but not a good one (silhouette measure of cohesion and separation).
-% Fran, please add figure 1 here as per attachment, along with the given caption.
 

### 2021-07-02 edubots_surveys.Rnw
Turn table sideways

--- 2021-07-02 edubots_surveys.Rnw
@@
 \usepackage{multirow}
+\usepackage{rotating}
 
@@
 \begin{document}
-%\SweaveOpts{concordance=TRUE}
 
@@
 \end{tabular}
+\vspace{0.8em}
 \caption{Use of messaging apps in class}
@@
 \end{tabular}
+\vspace{0.8em}
 \caption{Sector * post-covid changes crosstabulation}
@@
 \end{tabular}
+\vspace{0.8em}
 \caption{Agenda use case * FAQs use case crosstabulation }
@@
 \end{tabular}
+\vspace{0.8em}
 \caption{Kind of interactions preferred}
@@
 Familiarity & 121 & 59.0 & 84 & 41.0 \\
-Hidden Phone & 113 & 55.1 & 92 & 44.9 \\
+Hidden Phone Number & 113 & 55.1 & 92 & 44.9 \\
 Horizontally & 134 & 65.4 & 71 & 34.6 \\
@@
 \hline
-\end{tabular}\caption{Interaction media features valued by teachers}
+\end{tabular}
+\vspace{0.8em}
+\caption{Interaction media features valued by teachers}
 \label{tab:interaction}
@@
 %TODO - table fits better in landscape? try to fit in page size 
-\begin{table}[h!tbp]
+\begin{sidewaystable}[h!tbp]
 \centering
@@
 \label{tab:interactionfeatures}
-\end{table}
+\end{sidewaystable}
 

### 2021-07-04 edubots_surveys.Rnw
Eliminates rows and one column

@@
 \centering
-\resizebox{\textwidth}{!}{\begin{tabular}{llllllllllll}
+\resizebox{\textwidth}{!}{\begin{tabular}{lllllllllll}
 \hline
-\multicolumn{1}{c}{} & \multicolumn{1}{c}{Analytics} & Connectivity & Familiarity & Hidden phone & Horizontallity & \begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} & Pluggability & Sustainability & Unidirectionality & Officiality & Synchrony \\ \hline
-Analytics & \multicolumn{1}{c}{-} & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 12.172^{***}$} & $X^{2}_{(1, N = 205)} = 4.855^{*}$ & ns & ns & $X^{2}_{(1, N = 205)} = 4.144^{*}$ & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 12.490^{***}$} & $X^{2}_{(1, N = 205)} = 4.314^{*}$ & ns & ns & ns \\
-Connectivity & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-} & ns & ns & $X^{2}_{(1, N = 205)} = 5.971^{***}$ & ns & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 16.286^{***}$} & ns & ns & ns & ns \\
-Familiarity &  &  & - & ns & ns & ns & ns & ns & ns & ns & ns \\
-Hidden phone &  &  &  & - & ns & $X^{2}_{(1, N = 205)} = 5.678^{*}$ & $X^{2}_{(1, N = 205)} = 4.683^{*}$ & ns & $X^{2}_{(1, N = 205)} = 4.515^{*}$ & ns & ns \\
-Horizontallity &  &  &  &  & - & ns & ns & ns & ns & $X^{2}_{(1, N = 205)} = 5.453^{*}$ & ns \\
-\begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} &  &  &  &  &  & - & $X^{2}_{(1, N = 205)} = 8.163^{**}$ & ns & ns & ns & ns \\
-Pluggability &  &  &  &  &  &  & - & ns & ns & ns & ns \\
-Sustainability &  &  &  &  &  &  &  & - & ns & ns & ns \\
-Unidirectionality &  &  &  &  &  &  &  &  & - & ns & ns \\
-Officiality &  &  &  &  &  &  &  &  &  & - & ns \\
-Synchrony & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  &  &  & \multicolumn{1}{c}{} &  &  &  & - \\ \hline
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{Analytics} & Connectivity & Familiarity & Hidden phone & Horizontallity & \begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} & Pluggability & Sustainability & Unidirectionality & Officiality \\ \hline
+Analytics & \multicolumn{1}{c}{-} & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 12.172^{***}$} & $X^{2}_{(1, N = 205)} = 4.855^{*}$ & ns & ns & $X^{2}_{(1, N = 205)} = 4.144^{*}$ & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 12.490^{***}$} & $X^{2}_{(1, N = 205)} = 4.314^{*}$ & ns & ns \\
+Connectivity & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-} & ns & ns & $X^{2}_{(1, N = 205)} = 5.971^{***}$ & ns & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 16.286^{***}$} & ns & ns & ns \\
+Familiarity &  &  & - & ns & ns & ns & ns & ns & ns & ns \\
+Hidden phone &  &  &  & - & ns & $X^{2}_{(1, N = 205)} = 5.678^{*}$ & $X^{2}_{(1, N = 205)} = 4.683^{*}$ & ns & $X^{2}_{(1, N = 205)} = 4.515^{*}$ & ns \\
+Horizontallity &  &  &  &  & - & ns & ns & ns & ns & $X^{2}_{(1, N = 205)} = 5.453^{*}$ \\
+\begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} &  &  &  &  &  & - & $X^{2}_{(1, N = 205)} = 8.163^{**}$ & ns & ns & ns  \\
+Synchrony & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  &  &  & \multicolumn{1}{c}{} &  &  & \\ \hline
 \end{tabular}}
-\caption{Interaction media features analysis ($^{***}p<0.001$, $^{**}p<0.01$, $^{*}p<0.05$).}
+\caption{Interaction media features analysis ($^{***}p<0.001$, $^{**}p<0.01$, $^{*}p<0.05$). Columns and rows with no significant interaction have been suppressed for clarity.}
 \label{tab:interactionfeatures}

### 2021-07-04 edubots_surveys.Rnw
One hour to edit the table
Which is why, kids, please use knitr to include data into papers.

@@
 %TODO - table fits better in landscape? try to fit in page size 
-\begin{sidewaystable}[h!tbp]
-\centering
-\resizebox{\textwidth}{!}{\begin{tabular}{lllllllllll}
+\begin{table}[h!tbp]
+\centering
+\resizebox{\textwidth}{!}{\begin{tabular}{lllllllll}
 \hline
-\multicolumn{1}{c}{} & \multicolumn{1}{c}{Analytics} & Connectivity & Familiarity & Hidden phone & Horizontallity & \begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} & Pluggability & Sustainability & Unidirectionality & Officiality \\ \hline
-Analytics & \multicolumn{1}{c}{-} & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 12.172^{***}$} & $X^{2}_{(1, N = 205)} = 4.855^{*}$ & ns & ns & $X^{2}_{(1, N = 205)} = 4.144^{*}$ & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 12.490^{***}$} & $X^{2}_{(1, N = 205)} = 4.314^{*}$ & ns & ns \\
-Connectivity & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-} & ns & ns & $X^{2}_{(1, N = 205)} = 5.971^{***}$ & ns & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 16.286^{***}$} & ns & ns & ns \\
-Familiarity &  &  & - & ns & ns & ns & ns & ns & ns & ns \\
-Hidden phone &  &  &  & - & ns & $X^{2}_{(1, N = 205)} = 5.678^{*}$ & $X^{2}_{(1, N = 205)} = 4.683^{*}$ & ns & $X^{2}_{(1, N = 205)} = 4.515^{*}$ & ns \\
-Horizontallity &  &  &  &  & - & ns & ns & ns & ns & $X^{2}_{(1, N = 205)} = 5.453^{*}$ \\
-\begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} &  &  &  &  &  & - & $X^{2}_{(1, N = 205)} = 8.163^{**}$ & ns & ns & ns  \\
-Synchrony & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  &  &  & \multicolumn{1}{c}{} &  &  & \\ \hline
+ & Connectivity & Familiarity  & Horizontallity & \begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} & Pluggability & Sustainability & Unidirectionality & Officiality \\ \hline
+Analytics &  $12.172^{***}$ & $4.855^{*}$ & ns & $4.144^{*}$ &  $12.490^{***}$ & $4.314^{*}$ & ns & ns \\
+Connectivity & - & ns & $5.971^{***}$ & ns & $16.286^{***}$ & ns & ns & ns \\
+Hidden phone &  &  & ns & $5.678^{*}$ & $4.683^{*}$ & ns & $4.515^{*}$ & ns \\
+Horizontallity &  &  - & ns & ns & ns & ns & ns & $5.453^{*}$ \\
+\begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} &  & &  & - & $8.163^{**}$ & ns & ns & ns  \\
 \end{tabular}}
-\caption{Interaction media features analysis ($^{***}p<0.001$, $^{**}p<0.01$, $^{*}p<0.05$). Columns and rows with no significant interaction have been suppressed for clarity.}
+\vspace{0.8em}
+\caption{Interaction media features analysis ($^{***}p<0.001$, $^{**}p<0.01$, $^{*}p<0.05$).
+Columns and rows with no significant interaction have been suppressed for clarity.
+Every cell value represents $X^{2}_{(1, N = 205)}$.}
 \label{tab:interactionfeatures}
-\end{sidewaystable}
+\end{table}
 

### 2021-07-04 edubots_surveys.Rnw
Table :bug: done
Examining responses to RQ3
I will, with this, close #3, since analysis have been already included everywhere.

@@
 
+We will try to answer these questions through the analysis of questions and answers in the two surveys.
+
 The rest of the paper is organized as follows: Next is an overview of what current research has found about the use of messaging applications, including chatbots, in the classroom.
@@
 
-For answering RQ3, teachers were provided with a list of different kind of interactions that may take place among students and between students and the teacher, with the use of messaging apps.
+Since chatbots are intended to mediate or help in this interaction, it is essential to understand the kind of interaction teachers prefer.
+Chatbots should address those modes, and not others.
+In order to find out these modes, and thus answering RQ3, teachers were provided with a list of different kind of interactions that may take place among students and between students and the teacher, with the use of messaging apps.
 The findings are summarized in Table \ref{tab:kindinteractions}.
@@
 
+As it can be seen by the answer to the first and last question, in general teachers do not want to participate in a chat group with students; either they want to simply leave leave the students alone in their own chat group, or otherwise they prefer not to be part of that interaction.
+In general, that is going to be the case no matter what; it is well known that students organize their own chat groups with many (and not always conveyable) intentions, so teachers do not want to take any part in it.
+Overwhelmingly, they don't want to participate in any chat group with students, but even less so if it includes the rest of the faculty.
+
+The answer, then, to this research question, is that, in general, teachers do {\em not} want to have interaction with students in a chat group.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RQ4 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%TODO - table fits better in landscape? try to fit in page size 
 \begin{table}[h!tbp]

### 2021-07-04 edubots_surveys.Rnw
Clarify the purpose of the paper

@@
 % Maybe move it to a different place later
-In the present work we aim to complement the aforementioned study with teacher attitudes; teachers are the ones that actually would need to implement, 
+In the present work we aim to complement the aforementioned study with an analysis of teacher attitudes; teachers are the ones that actually would need to use, 
 % Antonio - 'deploy' instead implement? Since in Computer Sciences implement and program are synonyms...
@@
 % Antonio - Ok, but what I said is that 'implement' is a synonym of 'program' in this scope, and we write both in the same sentence as different things.
+% And deploy does not make sense in this context. I will simply say use - JJ
 configure and maybe program chatbots.
@@
 We will try to answer these questions through the analysis of questions and answers in the two surveys.
+Eventually, what we want to obtain is a series of recommendations to make a successful deployment of chatbot technologies (and, in some cases, general instant messaging applications) in higher education.
 

### 2021-07-04 edubots_surveys.Rnw
Eliminate comments, closes #8

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Enter the authors here                   %%
-%%                                          %%
-%% Specify information, if available,       %%
-%% in the form:                             %%
-%%   <key>={<id1>,<id2>}                    %%
-%%   <key>=                                 %%
-%% Comment or delete the keys which are     %%
-%% not used. Repeat \author command as much %%
-%% as required.                             %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \author[
-  addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
-  corref={aff1},                       % id of corresponding address, if any
-  email={jmerelo@ugr.es}   % email address
+  addressref={aff1},                  
+  corref={aff1},                      
+  email={jmerelo@ugr.es}  
 ]{\inits{JJM}\fnm{Juan J.} \snm{Merelo}}
@@
   addressref={aff1},
-  email={pacv@ugr.es}   % email address
+  email={pacv@ugr.es}
 ]{\inits{PAC}\fnm{Pedro A.} \snm{Castillo}}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Enter the authors' addresses here        %%
-%%                                          %%
-%% Repeat \address commands as much as      %%
-%% required.                                %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\address[id=aff1]{%                           % unique id
-  \orgdiv{Department of Computer Architecture and Technology},             % department, if any
-  \orgname{University of Granada},          % university, etc
-  \city{Granada},                              % city
-  \cny{Spain}                                    % country
+\address[id=aff1]{%                           
+  \orgdiv{Department of Computer Architecture and Technology},           
+  \orgname{University of Granada},
+  \city{Granada},
+  \cny{Spain}
 }
@@
   \orgdiv{Department of Signal Theory, Telematics and Communications},
-  \orgname{University of Granada},          % university, etc
-  \city{Granada},                              % city
-  \cny{Spain}                                    % country
+  \orgname{University of Granada},
+  \city{Granada},
+  \cny{Spain}
 }
@@
   \orgdiv{School of Computing},
-  \orgname{University of Leeds},          % university, etc
-  \city{Leeds},                              % city
-  \cny{UK}                                    % country
+  \orgname{University of Leeds},
+  \city{Leeds},
+  \cny{UK}
 }
 \address[id=aff4]{%
-  \orgname{CYENS},          % university, etc
-  \city{Nicosia},                              % city
-  \cny{Cyprus}                                    % country
+  \orgname{CYENS},         
+  \city{Nicosia},
+  \cny{Cyprus} 
 }

### 2021-07-04 edubots_surveys.Rnw
Revises RQ3 according to @oliatsi suggestions
Also revises and closes #6, no more work is needed here, after excellent work by @noorhanabbas.

@@
 and students embedded in the social learning process
-\cite{gachago2015crossing}.
+\cite{gachago2015crossing}; however, this last paper also reflects the need for
+learners to "take ownership of the tool" and the advantages of social learning
+in general. At the same time, it also mentions different challenges, among which
+the most important is the blurring of social and academic life. Examining these
+attitudes will be the objective of RQ3 in this paper.
 
@@
 \cite{gachago2015crossing} process. 
-This is why examining the role of MIM in higher education is still a challenge, and why the attitudes of the teaching community towards them have to be examined, as we do in this paper.
+This is why examining the role of MIM in higher education is still a challenge,
+and why the attitudes of the teaching community towards them have to be
+examined, as we do in this paper.
 
@@
 
-%Olia - Isn't the following paragraph better fittng for RQ3? What kind interactions do teachers prefer with their students? 
-Regarding the social factor of chat groups that teachers use in class, according to Fig.
-\ref{figure:chatbots_messagingorganization} the vast majority prefer small groups only with the students from the same course.
-These are more focused groups with specific goals and dedicated to the organization of the course and its tasks, and from the pedagogic point of view seem more appropriate to improve the learning process.
-Interestingly, about 30\% of teachers consider they should not be part of the chat group.
-Also, only university teachers find interesting a group with all the students and teachers in their own Faculty or School.
-The lack of teachers from vocational Education here may be the consequence of using specific language such as "Faculty".
-Moreover, the fact that many universities and schools already use these groups for administrative and social interaction (e.g.
-\cite{dibitonto2018chatbot}) might be the reason for the low percentage of teachers that selected this response.
-
-\begin{figure}[h!tbp]
-\centering
-<<messaging_organization, echo=FALSE, fig.width=19/2.54, fig.height=5/2.54>>=
-survey.pilot.MessagingOrganization <- within(survey.pilot.MessagingOrganization, Messaging.Organization <- factor(Messaging.Organization, levels=names(sort(table(Messaging.Organization), decreasing=TRUE))))
-ggplot(survey.pilot.MessagingOrganization, aes( x = Messaging.Organization, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90))+coord_flip()+ theme(axis.title.y=element_blank())
-@
-%\includegraphics[width=\textwidth]{figures/messaging_organization.pdf}
-\caption{Distribution of teachers' preferences for the chat groups with their students: from groups only with their students from a specific course to groups with greater social interaction with all students in their School or Faculty.}
-\label{figure:chatbots_messagingorganization}
-\end{figure}
-
 Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' attitudes towards the instant messaging apps.
@@
 
+\begin{figure}[h!tbp]
+\centering
+<<messaging_organization, echo=FALSE, fig.width=19/2.54, fig.height=5/2.54>>=
+survey.pilot.MessagingOrganization <- within(survey.pilot.MessagingOrganization, Messaging.Organization <- factor(Messaging.Organization, levels=names(sort(table(Messaging.Organization), decreasing=TRUE))))
+ggplot(survey.pilot.MessagingOrganization, aes( x = Messaging.Organization, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90))+coord_flip()+ theme(axis.title.y=element_blank())
+@
+%\includegraphics[width=\textwidth]{figures/messaging_organization.pdf}
+\caption{Distribution of teachers' preferences for the chat groups with their students: from groups only with their students from a specific course to groups with greater social interaction with all students in their School or Faculty.}
+\label{figure:chatbots_messagingorganization}
+\end{figure}
+
 Since chatbots are intended to mediate or help in this interaction, it is essential to understand the kind of interaction teachers prefer.
@@
 The answer, then, to this research question, is that, in general, teachers do {\em not} want to have interaction with students in a chat group.
+To a certain point, this would seem to contradict results by Gachago et al.
+\cite{gachago2015crossing}, although this might be due to cultural attitudes, or other factors such as the average size of classes.
+It does confirm, however, that the challenges cited in that study, and possibly others, are an obstacle to the adoption of mobile (and other) instant messaging among the community of surveyed teachers.
+
+%Olia - Isn't the following paragraph better fitting for RQ3? What kind interactions do teachers prefer with their students? 
+% Moved here
+Regarding the social factor of chat groups that teachers use in class, according to Fig.
+\ref{figure:chatbots_messagingorganization} the vast majority prefer small groups only with the students from the same course.
+These are more focused groups with specific goals and dedicated to the organization of the course and its tasks, and from the pedagogic point of view seem more appropriate to improve the learning process.
+Interestingly, and as a cross-check of the answers above, about 30\% of teachers consider they should not be part of the chat group.
+This might seem to contradict the results of the other survey, but in fact, being a result of different surveys, to a certain point affirms the same thing: there is a great amount of teachers that would be against being in a chat group with students.
+Whether that's a slim majority or not, that's open to debate (and would probably need a more pointed survey focused on this), but what is clear is that forcing teachers to create chat groups with students and participate in them would create a certain amount of resistance.
+Also, only university teachers find interesting a group with all the students and teachers in their own Faculty or School.
+The lack of teachers from vocational education here may be the consequence of using specific language such as "Faculty".
+Moreover, the fact that many universities and schools already use these groups for administrative and social interaction (e.g.
+\cite{dibitonto2018chatbot}) might be the reason for the low percentage of teachers that selected this response.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RQ4 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-07-05 edubots_surveys.Rnw
Update edubots_surveys.Rnw

@@
 Only one of the applications mentioned, having them work with frequently asked questions, might actually require some understanding of natural language, although it can be formulated in such a way that is not needed.
-
+ In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor.
+In fact, in many cases, some students experience stress because of their need to ask a question in front of the entire class.
+This is why many students refrain to silence in the classroom and tend to contact their teachers later via email.
+Consequently, this can lead to not only a delay in obtaining answers to their questions but also can cause a significant increase in their teachers’ workload, especially when factoring in the disproportion between the class size and the number of teachers.
+Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning experience \cite{Griol2014,kim2020}.
+In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding.
 % Maybe move it to a different place later
 In the present work we aim to complement the aforementioned study with an analysis of teacher attitudes; teachers are the ones that actually would need to use, 
+% Olia-I believe we should avoid refereeing to “attitudes”. Also here, it is not mentioned that we explore their views towards the use of chat tools/ messaging apps. 
 % Antonio - 'deploy' instead implement? Since in Computer Sciences implement and program are synonyms...
@@
 % Antonio - I include here the description of interaction features. Not sure if it is the best place for it. Move wherever it better fits.
+% Olia- in the text below, we refer to "communucation tools", we should be consisten with the terms we use. Should we refere to communication tools? Messaging apps? Chat tools? 
 Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are their feelings and preferences with regard to the use of communication tools with students, and even using bots or chatbots in the classroom.
@@
 \item \textit{Officiality}: the tool has been granted by the university where the teacher works. This means normally that there is also technical support by university's staff.
-\item \textit{Synchrony}: it is possible to publish/receive the data or information in several devices and all of them will contain or show the same.
+\item \textit{Synchronous communication}: the interactions between teacher and students take place in real time, i.e. it is not a delayed communication scheme such as e-mail.
 \end{itemize}
@@
 % Olia - TODO: check for repetitions in the following paragraph that you added. thank you.
-The descriptive analysis in this case is done using a Chi-square test.
-For the different variables considered, some statistical significance was found for Gender, Sector, and academic Discipline.
-The values found with the test are: $p-value=0.0034$ for Gender, $p-value=0.0199$ for Sector, and $p-value=0.0211$ for Discipline.
 The first column in Fig.
@@
 As it was a multiple choice question, the counts are over the total number of people that answered.
-One of the most interesting questions that can arise from the plots, and the should require further study, is: Are our professors really aware of the possibilities of chatbots in the classroom?
+One of the most interesting questions that can arise from the plots, and the should require further study, is: Are teachers really aware of the possibilities of chatbots in the classroom?
 The reason to ask ourselves this question is due to the fact of the small number of responses for other uses in comparison with the other approaches proposed.
-Another way to loook about it is that, unless you provide the specific instructions on how to use a tool, the teaching staff is already too busy or burn out to think about innovation.
+Another way to look about it is that, unless you provide the specific instructions on how to use a tool, the teaching staff is already too busy or burn out to think about innovation.
 
@@
 
+%Olia - move figure 7 elsewhere, not at the beginning of this section (RQ3). 
 Since chatbots are intended to mediate or help in this interaction, it is essential to understand the kind of interaction teachers prefer.
@@
 \end{itemize}
+%Olia: be consistent in the terms being used, we refer to teachers, then to professors. I would replace the word "professors" above with the word "teachers".
 
@@
 This integration, to be fruitful, institutions have to ensure that these messaging applications not only are GDPR compliant to keep students’ data secure but also should provide IT support to all stakeholders who use the applications .
-
+Moreover, this study clarifies the differences between the teachers’ perspectives and/or intentions and that of their students when using the messaging applications in higher education.
+Teachers tend to adopt technologies supported by their institutions.
+This could be to ensure that their universities can oversee their efforts in supporting their students during the learning process.
+Another reason could be their familiarity with the technology provided by their institutions.
+On the other hand, students use the non-institution messaging applications to form informal discussion groups with their peers.
+It is worth noting that peer support and collaboration is inseparable from learning \cite{ timmis2012constant } and correlates positively with higher retention in higher education \cite{ o2014front }.
+Therefore, both perspectives are complementary and play different roles in promoting the learning process.
 %This section is repeated

### 2021-07-05 edubots_surveys.Rnw
Update edubots_surveys.Rnw

--- 2021-07-04 edubots_surveys.Rnw
@@
 In the present work we aim to complement the aforementioned study with an analysis of teacher attitudes; teachers are the ones that actually would need to use, 
+% Olia-I believe we should avoid refereeing to “attitudes”. Also here, it is not mentioned that we explore their views towards the use of chat tools/ messaging apps. 
 % Antonio - 'deploy' instead implement? Since in Computer Sciences implement and program are synonyms...

### 2021-07-05 edubots_surveys.Rnw
Updating the Introduction section
Added the first paragraph in the introduction section

--- 2021-07-04 edubots_surveys.Rnw
@@
 % TODO: introduction
+The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new skills by both.
+Some technologies are readily adapted, but others require longer time for full adoption.
+In most cases, the magnitude of the uptake of the new technology impinges on the collaboration of all the parties using it.
+Hence, examining the users’ attitudes and the opinions is an important first step in boosting this collaboration and reaping the benefits of the technology.
+Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp, Telegram and Facebook Messenger took place.
+Some messaging applications have built in chatbots that are able to support a synchronous conversation between the different parties \cite{differ.chat}, while other chatbots are developed as standalone systems and can possibly be attached to a messaging application using an API (Application Program Interface).
 The introduction of new technologies in the classroom needs a combination of teacher motivation, 

### 2021-07-05 edubots_surveys.Rnw
Updating the Introduction section
Added the first paragraph in the introduction section

--- 2021-07-05 edubots_surveys.Rnw
@@
 On the other hand, students use the non-institution messaging applications to form informal discussion groups with their peers.
-It is worth noting that peer support and collaboration is inseparable from learning \cite{ timmis2012constant } and correlates positively with higher retention in higher education \cite{ o2014front }.
+It is worth noting that peer support and collaboration is inseparable from learning \cite{timmis2012constant} and correlates positively with higher retention in higher education \cite{o2014front}.
 Therefore, both perspectives are complementary and play different roles in promoting the learning process.

### 2021-07-05 edubots_surveys.Rnw
Second Paragraph in Introduction
Updated the second paragraph in the introduction

@@
 Some messaging applications have built in chatbots that are able to support a synchronous conversation between the different parties \cite{differ.chat}, while other chatbots are developed as standalone systems and can possibly be attached to a messaging application using an API (Application Program Interface).
-The introduction of new technologies in the classroom needs a combination of teacher motivation, 
-student willingness and (possibly new) skills in both.
-Some technologies are readily adapted, but some of them take a long time to be adopted.
-In most cases, the success or failure of the introduction of a new technology impinges on the collaboration of all the implied parties, which is why evaluating attitudes towards them is an essential first step.
 
@@
 % Moreover, considering that in the following paragraphs we are trying to 'sell' them.
-
+A chatbot is a program, sometimes developed using Artificial Intelligence techniques, that allows a computer to communicate in a similar way as humans do \cite{Gong2008}, using natural language.
+Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{ moor2003turing }, since they are able to answer almost any question fluently, and even pose questions in their conversations.
+The recent advancement in this discipline has played an important role in many fields especially in education and online tutoring \cite{clarizia2018,Smutny2020}.
+These automatic systems facilitate the delivery of personalized learning by adapting to students’ pace of learning and providing customized online tutoring outside the classroom.
+Thus, chatbots can significantly contribute to providing interactive learning experiences as well as improving individual attention \cite{agarwal2020}.
 The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with.

### 2021-07-05 edubots_surveys.Rnw
Second Paragraph in Introduction
Updated the second paragraph in the introduction

--- 2021-07-05 edubots_surveys.Rnw
@@
 % TODO: introduction
-The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new skills by both.
-Some technologies are readily adapted, but others require longer time for full adoption.
-In most cases, the magnitude of the uptake of the new technology impinges on the collaboration of all the parties using it.
-Hence, examining the users’ attitudes and the opinions is an important first step in boosting this collaboration and reaping the benefits of the technology.
-Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp, Telegram and Facebook Messenger took place.
-Some messaging applications have built in chatbots that are able to support a synchronous conversation between the different parties \cite{differ.chat}, while other chatbots are developed as standalone systems and can possibly be attached to a messaging application using an API (Application Program Interface).
 The introduction of new technologies in the classroom needs a combination of teacher motivation, 

### 2021-07-05 edubots_surveys.Rnw
Third paragraph in the introduction section
Updated the third paragraph in the introduction section

@@
 % Moreover, considering that in the following paragraphs we are trying to 'sell' them.
-A chatbot is a program, sometimes developed using Artificial Intelligence techniques, that allows a computer to communicate in a similar way as humans do \cite{Gong2008}, using natural language.
-Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{ moor2003turing }, since they are able to answer almost any question fluently, and even pose questions in their conversations.
-The recent advancement in this discipline has played an important role in many fields especially in education and online tutoring \cite{clarizia2018,Smutny2020}.
-These automatic systems facilitate the delivery of personalized learning by adapting to students’ pace of learning and providing customized online tutoring outside the classroom.
-Thus, chatbots can significantly contribute to providing interactive learning experiences as well as improving individual attention \cite{agarwal2020}.
+
 The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with.
@@
 Only one of the applications mentioned, having them work with frequently asked questions, might actually require some understanding of natural language, although it can be formulated in such a way that is not needed.
-
+ In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor.
+In fact, in many cases, some students experience stress because of their need to ask a question in front of the entire class.
+This is why many students refrain to silence in the classroom and tend to contact their teachers later via email.
+Consequently, this can lead to not only a delay in obtaining answers to their questions but also can cause a significant increase in their teachers’ workload, especially when factoring in the disproportion between the class size and the number of teachers.
+Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning experience \cite{Griol2014,kim2020}.
+In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding.
 % Maybe move it to a different place later

### 2021-07-05 edubots_surveys.Rnw
Third paragraph in the introduction section
Updated the third paragraph in the introduction section

@@
 This integration, to be fruitful, institutions have to ensure that these messaging applications not only are GDPR compliant to keep students’ data secure but also should provide IT support to all stakeholders who use the applications .
-Moreover, this study clarifies the differences between the teachers’ perspectives and/or intentions and that of their students when using the messaging applications in higher education.
-Teachers tend to adopt technologies supported by their institutions.
-This could be to ensure that their universities can oversee their efforts in supporting their students during the learning process.
-Another reason could be their familiarity with the technology provided by their institutions.
-On the other hand, students use the non-institution messaging applications to form informal discussion groups with their peers.
-It is worth noting that peer support and collaboration is inseparable from learning \cite{ timmis2012constant } and correlates positively with higher retention in higher education \cite{ o2014front }.
-Therefore, both perspectives are complementary and play different roles in promoting the learning process.
+
 %This section is repeated

### 2021-07-05 edubots_surveys.Rnw
Fourth and Fifth Paragraph in Introduction section
Updated the fourth and fifth paragraphs in the introduction section

--- 2021-07-05 edubots_surveys.Rnw
@@
 % TODO: introduction
-The introduction of new technologies in the classroom needs a combination of teacher motivation, 
-student willingness and (possibly new) skills in both.
-Some technologies are readily adapted, but some of them take a long time to be adopted.
-In most cases, the success or failure of the introduction of a new technology impinges on the collaboration of all the implied parties, which is why evaluating attitudes towards them is an essential first step.
+The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new skills by both.
+Some technologies are readily adapted, but others require longer time for full adoption.
+In most cases, the magnitude of the uptake of the new technology impinges on the collaboration of all the parties using it.
+Hence, examining the users’ attitudes and the opinions is an important first step in boosting this collaboration and reaping the benefits of the technology.
+Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp, Telegram and Facebook Messenger took place.
+Some messaging applications have built in chatbots that are able to support a synchronous conversation between the different parties \cite{differ.chat}, while other chatbots are developed as standalone systems and can possibly be attached to a messaging application using an API (Application Program Interface).
 
@@
 Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.
+Given the potential benefits that chatbots could bring to the classroom, the focus of the EDUBOTS KA2 European project [1], the sponsor of this study, is to gather, analyse and disseminate best practice of the use of chatbots in higher education institutions.
+This study involves two phases of data collection.
+The first phase aimed to collect feedback from students about their actual needs \cite{MoraChatbots2021}.
+Hence, the objective was to collect information about students’ preferences of tools/applications for chatting and messaging, how they use them in educational context, who do they like to be with in the class messaging groups, and their expectations of the chatbots in terms of assisting them during their learning process.
+Therefore, two surveys for bachelor and master degree students at the University of Granada (Spain) were developed and answers from more than 250 students were collected.
+The key findings of the students surveys reveal that they prefer to use messaging applications, such as Telegram or WhatsApp as they are familiar to them.
+Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course’s resources.
+The results of the first phase were fed into the second phase of the study, which focussed on teachers’ opinions about using chatbots and messaging applications in classes.
+Another survey was developed for this purpose.
+Responses from 300 teachers were collected and analysed.
+This study focuses on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:
+• RQ1 - Are teachers already using messaging apps in their classes? 
+• RQ2 - Which kind of chatbots would teachers find useful in their classes? 
+• RQ3 - Which kind of interaction do teachers prefer with their students? 
+The remainder of the paper is organized as follows: Next is an overview of what current research has found about the use of messaging applications, including chatbots, in the classroom.
+The methodology used in the survey is presented in Section 3, and the results of the survey are presented next in Section 4.
+Finally, we discuss these results and conclude with a series of recommendations in the section that closes the paper.
 

### 2021-07-05 edubots_surveys.Rnw
Fourth and Fifth Paragraph in Introduction section
Updated the fourth and fifth paragraphs in the introduction section

--- 2021-07-05 edubots_surveys.Rnw
@@
 Only one of the applications mentioned, having them work with frequently asked questions, might actually require some understanding of natural language, although it can be formulated in such a way that is not needed.
- In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor.
-In fact, in many cases, some students experience stress because of their need to ask a question in front of the entire class.
-This is why many students refrain to silence in the classroom and tend to contact their teachers later via email.
-Consequently, this can lead to not only a delay in obtaining answers to their questions but also can cause a significant increase in their teachers’ workload, especially when factoring in the disproportion between the class size and the number of teachers.
-Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning experience \cite{Griol2014,kim2020}.
-In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding.
+
 % Maybe move it to a different place later

### 2021-07-05 edubots_surveys.Rnw
Updated the introduction section
Added the reviewed paragraphs to the introduction section.

--- 2021-07-05 edubots_surveys.Rnw
@@
 % TODO: introduction
+
 The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new skills by both.
@@
 
-In the framework of the EduBots KA2 European project\footnote{https://www.edubots.eu}, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms.
-A \textit{chatbot} is a program, sometimes based on Artificial Intelligence techniques, that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language.
-Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker's question fluently, and even ask other questions to the human.
-However, in most cases a simple messaging-application attached bot will help the students (and teachers); so neither computational intelligence nor comprehension of natural languages are requisites, the only one being the fact that they can be accessed from a synchronous conversational application such as the common instant messaging applications (e.g.
-Telegram, WhatsApp) used nowadays.
-% Antonio - This paragraph needs a conclusion. Why do we say (essentially) that chatbots are not needed and just a simple messaging bot is enough?
-% JJ - feel free to add one 
-% Antonio - The thing is I don't catch why are we saying that, since it is supossed that we should 'defend' the use of chatbots (from the project perspective, at least).
-Or if we don't want to defend them, at least not saying that they are useless most of times.
-XD
-% Moreover, considering that in the following paragraphs we are trying to 'sell' them.
 A chatbot is a program, sometimes developed using Artificial Intelligence techniques, that allows a computer to communicate in a similar way as humans do \cite{Gong2008}, using natural language.
@@
 Thus, chatbots can significantly contribute to providing interactive learning experiences as well as improving individual attention \cite{agarwal2020}.
-The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with.
-These automatic systems ease personalized learning,
-adapting individuals' pace of learning, who get customized online tutoring outside the classroom.
-Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.
-Given the potential benefits that chatbots could bring to the classroom, the focus of the EDUBOTS KA2 European project [1], the sponsor of this study, is to gather, analyse and disseminate best practice of the use of chatbots in higher education institutions.
+ In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor.
+In fact, in many cases, some students experience stress because of their need to ask a question in front of the entire class.
+This is why many students refrain to silence in the classroom and tend to contact their teachers later via email.
+Consequently, this can lead to not only a delay in obtaining answers to their questions but also can cause a significant increase in their teachers’ workload, especially when factoring in the disproportion between the class size and the number of teachers.
+Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning experience \cite{Griol2014,kim2020}.
+In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding.
+Given the potential benefits that chatbots could bring to the classroom, the focus of the EDUBOTS KA2 European project \footnote{https://www.edubots.eu}, the sponsor of this study, is to gather, analyse and disseminate best practice of the use of chatbots in higher education institutions.
 This study involves two phases of data collection.
@@
 This study focuses on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:
-• RQ1 - Are teachers already using messaging apps in their classes? 
-• RQ2 - Which kind of chatbots would teachers find useful in their classes? 
-• RQ3 - Which kind of interaction do teachers prefer with their students? 
-The remainder of the paper is organized as follows: Next is an overview of what current research has found about the use of messaging applications, including chatbots, in the classroom.
-The methodology used in the survey is presented in Section 3, and the results of the survey are presented next in Section 4.
-Finally, we discuss these results and conclude with a series of recommendations in the section that closes the paper.
-
-In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor.
-In fact, in many cases, students suffer from stress when they have to ask a question in front of the entire class.
-This is why many students prefer to remain silent and ask their question later via email.
-However, this means a waste of time and a delay of hours or even days to get the teacher's answer; moreover, it does not scale well with the size of the class.
-Chatbot technology has a potential to fill the gap between teacher and students, helping them to solve questions and carry out a dynamic and autonomous learning \cite{Griol2014,kim2020}.
-In addition, using an automated system such as a chatbot, allows the teacher to detect the most demanded topics, and on which he or she should consequently place more emphasis in class.
-
-Chatbots are obviously associated to messaging applications, and in particular, direct messaging applications, since they are the only type of applications that are able to support a synchronous conversation between the two parties.
-This is why in many cases chatbots couple messaging and the chatbot technology itself \cite{differ.chat}, while in others, you can create chatbots in any number of technologies and then attach them to a messaging application using their API (Application Program Interface).
-
-Given the potential advantages that chatbots could bring to the classroom, as a previous step, we created two surveys for bachelor and master degree students at the University of Granada (Spain), which were answered by more than 250 students.
-The obtained results were analysed with the object of identifying students' actual needs, in \cite{MoraChatbots2021}.
-The survey asked about their preferences on tools/applications for chatting and messaging, how do they use them in the educational context, who do they like to be with in the class messaging groups, and what do they expect bots and chatbots to do to aid them during their learning process.
-We concluded that students prefer to use known whatever messaging application, such as Telegram or WhatsApp, they are already using.
-They also expected chatbots to help them with their scheduling, to provide assignment grades and to search for class material.
-Only one of the applications mentioned, having them work with frequently asked questions, might actually require some understanding of natural language, although it can be formulated in such a way that is not needed.
- In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor.
-In fact, in many cases, some students experience stress because of their need to ask a question in front of the entire class.
-This is why many students refrain to silence in the classroom and tend to contact their teachers later via email.
-Consequently, this can lead to not only a delay in obtaining answers to their questions but also can cause a significant increase in their teachers’ workload, especially when factoring in the disproportion between the class size and the number of teachers.
-Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning experience \cite{Griol2014,kim2020}.
-In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding.
+
+% Antonio - This paragraph needs a conclusion. Why do we say (essentially) that chatbots are not needed and just a simple messaging bot is enough?
+% JJ - feel free to add one 
+% Antonio - The thing is I don't catch why are we saying that, since it is supossed that we should 'defend' the use of chatbots (from the project perspective, at least).
+Or if we don't want to defend them, at least not saying that they are useless most of times.
+XD
+% Moreover, considering that in the following paragraphs we are trying to 'sell' them.
+
 % Maybe move it to a different place later
 In the present work we aim to complement the aforementioned study with an analysis of teacher attitudes; teachers are the ones that actually would need to use, 
-% Olia-I believe we should avoid refereeing to “attitudes”. Also here, it is not mentioned that we explore their views towards the use of chat tools/ messaging apps. 
 % Antonio - 'deploy' instead implement? Since in Computer Sciences implement and program are synonyms...
@@
 % Antonio - I include here the description of interaction features. Not sure if it is the best place for it. Move wherever it better fits.
-% Olia- in the text below, we refer to "communucation tools", we should be consisten with the terms we use. Should we refere to communication tools? Messaging apps? Chat tools? 
 Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are their feelings and preferences with regard to the use of communication tools with students, and even using bots or chatbots in the classroom.
@@
 \item \textit{Officiality}: the tool has been granted by the university where the teacher works. This means normally that there is also technical support by university's staff.
-\item \textit{Synchronous communication}: the interactions between teacher and students take place in real time, i.e. it is not a delayed communication scheme such as e-mail.
+\item \textit{Synchrony}: it is possible to publish/receive the data or information in several devices and all of them will contain or show the same.
 \end{itemize}
@@
 % Olia - TODO: check for repetitions in the following paragraph that you added. thank you.
+The descriptive analysis in this case is done using a Chi-square test.
+For the different variables considered, some statistical significance was found for Gender, Sector, and academic Discipline.
+The values found with the test are: $p-value=0.0034$ for Gender, $p-value=0.0199$ for Sector, and $p-value=0.0211$ for Discipline.
 The first column in Fig.
@@
 As it was a multiple choice question, the counts are over the total number of people that answered.
-One of the most interesting questions that can arise from the plots, and the should require further study, is: Are teachers really aware of the possibilities of chatbots in the classroom?
+One of the most interesting questions that can arise from the plots, and the should require further study, is: Are our professors really aware of the possibilities of chatbots in the classroom?
 The reason to ask ourselves this question is due to the fact of the small number of responses for other uses in comparison with the other approaches proposed.
-Another way to look about it is that, unless you provide the specific instructions on how to use a tool, the teaching staff is already too busy or burn out to think about innovation.
+Another way to loook about it is that, unless you provide the specific instructions on how to use a tool, the teaching staff is already too busy or burn out to think about innovation.
 
@@
 
-%Olia - move figure 7 elsewhere, not at the beginning of this section (RQ3). 
 Since chatbots are intended to mediate or help in this interaction, it is essential to understand the kind of interaction teachers prefer.
@@
 \end{itemize}
-%Olia: be consistent in the terms being used, we refer to teachers, then to professors. I would replace the word "professors" above with the word "teachers".
 
@@
 This integration, to be fruitful, institutions have to ensure that these messaging applications not only are GDPR compliant to keep students’ data secure but also should provide IT support to all stakeholders who use the applications .
-Moreover, this study clarifies the differences between the teachers’ perspectives and/or intentions and that of their students when using the messaging applications in higher education.
-Teachers tend to adopt technologies supported by their institutions.
-This could be to ensure that their universities can oversee their efforts in supporting their students during the learning process.
-Another reason could be their familiarity with the technology provided by their institutions.
-On the other hand, students use the non-institution messaging applications to form informal discussion groups with their peers.
-It is worth noting that peer support and collaboration is inseparable from learning \cite{timmis2012constant} and correlates positively with higher retention in higher education \cite{o2014front}.
-Therefore, both perspectives are complementary and play different roles in promoting the learning process.
+
 %This section is repeated

### 2021-07-05 edubots_surveys.Rnw
Added another paragraph to the conclusion
Added a paragraph to the conclusion section

--- 2021-07-05 edubots_surveys.Rnw
@@
 Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.
-Given the potential benefits that chatbots could bring to the classroom, the focus of the EDUBOTS KA2 European project [1], the sponsor of this study, is to gather, analyse and disseminate best practice of the use of chatbots in higher education institutions.
-This study involves two phases of data collection.
-The first phase aimed to collect feedback from students about their actual needs \cite{MoraChatbots2021}.
-Hence, the objective was to collect information about students’ preferences of tools/applications for chatting and messaging, how they use them in educational context, who do they like to be with in the class messaging groups, and their expectations of the chatbots in terms of assisting them during their learning process.
-Therefore, two surveys for bachelor and master degree students at the University of Granada (Spain) were developed and answers from more than 250 students were collected.
-The key findings of the students surveys reveal that they prefer to use messaging applications, such as Telegram or WhatsApp as they are familiar to them.
-Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course’s resources.
-The results of the first phase were fed into the second phase of the study, which focussed on teachers’ opinions about using chatbots and messaging applications in classes.
-Another survey was developed for this purpose.
-Responses from 300 teachers were collected and analysed.
-This study focuses on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:
-• RQ1 - Are teachers already using messaging apps in their classes? 
-• RQ2 - Which kind of chatbots would teachers find useful in their classes? 
-• RQ3 - Which kind of interaction do teachers prefer with their students? 
-The remainder of the paper is organized as follows: Next is an overview of what current research has found about the use of messaging applications, including chatbots, in the classroom.
-The methodology used in the survey is presented in Section 3, and the results of the survey are presented next in Section 4.
-Finally, we discuss these results and conclude with a series of recommendations in the section that closes the paper.
 

### 2021-07-07 edubots_surveys.Rnw
Fix again citations

--- 2021-07-07 edubots_surveys.Rnw
@@
 % Moreover, considering that in the following paragraphs we are trying to 'sell' them.
-
+A chatbot is a program, sometimes developed using Artificial Intelligence techniques, that allows a computer to communicate in a similar way as humans do \cite{Gong2008}, using natural language.
+Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any question fluently, and even pose questions in their conversations.
+The recent advancement in this discipline has played an important role in many fields especially in education and online tutoring \cite{clarizia2018,Smutny2020}.
+These automatic systems facilitate the delivery of personalized learning by adapting to students’ pace of learning and providing customized online tutoring outside the classroom.
+Thus, chatbots can significantly contribute to providing interactive learning experiences as well as improving individual attention \cite{agarwal2020}.
 The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with.

### 2021-07-07 edubots_surveys.Rnw
Trying to make incorporation

@@
 Telegram, WhatsApp) used nowadays.
-% Antonio - This paragraph needs a conclusion. Why do we say (essentially) that chatbots are not needed and just a simple messaging bot is enough?
-% JJ - feel free to add one 
-% Antonio - The thing is I don't catch why are we saying that, since it is supossed that we should 'defend' the use of chatbots (from the project perspective, at least).
-Or if we don't want to defend them, at least not saying that they are useless most of times.
-XD
-% Moreover, considering that in the following paragraphs we are trying to 'sell' them.
+
 A chatbot is a program, sometimes developed using Artificial Intelligence techniques, that allows a computer to communicate in a similar way as humans do \cite{Gong2008}, using natural language.
@@
 Thus, chatbots can significantly contribute to providing interactive learning experiences as well as improving individual attention \cite{agarwal2020}.
+
 The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with.
@@
 Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.
-Given the potential benefits that chatbots could bring to the classroom, the focus of the EDUBOTS KA2 European project [1], the sponsor of this study, is to gather, analyse and disseminate best practice of the use of chatbots in higher education institutions.
+
+Given the potential benefits that chatbots could bring to the classroom, the focus of the EduBots KA2 European project, the sponsor of this study, is to gather, analyse and disseminate best practice of the use of chatbots in higher education institutions.
 This study involves two phases of data collection.
@@
 Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course’s resources.
+
 The results of the first phase were fed into the second phase of the study, which focussed on teachers’ opinions about using chatbots and messaging applications in classes.
@@
 Responses from 300 teachers were collected and analysed.
-This study focuses on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:
-• RQ1 - Are teachers already using messaging apps in their classes? 
-• RQ2 - Which kind of chatbots would teachers find useful in their classes? 
-• RQ3 - Which kind of interaction do teachers prefer with their students? 
+This study focuses on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:\begin{itemize}
+\item RQ1 - Are teachers already using messaging apps in their classes? 
+\item RQ2 - Which kind of chatbots would teachers find useful in their classes? 
+\item RQ3 - Which kind of interaction do teachers prefer with their students? 
+\end{itemize}
+
 The remainder of the paper is organized as follows: Next is an overview of what current research has found about the use of messaging applications, including chatbots, in the classroom.
-The methodology used in the survey is presented in Section 3, and the results of the survey are presented next in Section 4.
-Finally, we discuss these results and conclude with a series of recommendations in the section that closes the paper.
-
-In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor.
-In fact, in many cases, students suffer from stress when they have to ask a question in front of the entire class.
-This is why many students prefer to remain silent and ask their question later via email.
-However, this means a waste of time and a delay of hours or even days to get the teacher's answer; moreover, it does not scale well with the size of the class.
-Chatbot technology has a potential to fill the gap between teacher and students, helping them to solve questions and carry out a dynamic and autonomous learning \cite{Griol2014,kim2020}.
-In addition, using an automated system such as a chatbot, allows the teacher to detect the most demanded topics, and on which he or she should consequently place more emphasis in class.
-
-Chatbots are obviously associated to messaging applications, and in particular, direct messaging applications, since they are the only type of applications that are able to support a synchronous conversation between the two parties.
-This is why in many cases chatbots couple messaging and the chatbot technology itself \cite{differ.chat}, while in others, you can create chatbots in any number of technologies and then attach them to a messaging application using their API (Application Program Interface).
-
-Given the potential advantages that chatbots could bring to the classroom, as a previous step, we created two surveys for bachelor and master degree students at the University of Granada (Spain), which were answered by more than 250 students.
-The obtained results were analysed with the object of identifying students' actual needs, in \cite{MoraChatbots2021}.
-The survey asked about their preferences on tools/applications for chatting and messaging, how do they use them in the educational context, who do they like to be with in the class messaging groups, and what do they expect bots and chatbots to do to aid them during their learning process.
-We concluded that students prefer to use known whatever messaging application, such as Telegram or WhatsApp, they are already using.
-They also expected chatbots to help them with their scheduling, to provide assignment grades and to search for class material.
-Only one of the applications mentioned, having them work with frequently asked questions, might actually require some understanding of natural language, although it can be formulated in such a way that is not needed.
- In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor.
-In fact, in many cases, some students experience stress because of their need to ask a question in front of the entire class.
-This is why many students refrain to silence in the classroom and tend to contact their teachers later via email.
-Consequently, this can lead to not only a delay in obtaining answers to their questions but also can cause a significant increase in their teachers’ workload, especially when factoring in the disproportion between the class size and the number of teachers.
-Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning experience \cite{Griol2014,kim2020}.
-In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding.
-% Maybe move it to a different place later
-In the present work we aim to complement the aforementioned study with an analysis of teacher attitudes; teachers are the ones that actually would need to use, 
-% Olia-I believe we should avoid refereeing to “attitudes”. Also here, it is not mentioned that we explore their views towards the use of chat tools/ messaging apps. 
-% Antonio - 'deploy' instead implement? Since in Computer Sciences implement and program are synonyms...
-% JJ - deployment would be done by the university or whoever publishes the system. Deployment and implementation are two different things, anyway
-% Antonio - Ok, but what I said is that 'implement' is a synonym of 'program' in this scope, and we write both in the same sentence as different things.
-% And deploy does not make sense in this context. I will simply say use - JJ
-configure and maybe program chatbots.
-Thus, we have performed a survey among 300 teachers asking about their attitudes towards the use of bots or chatbots in their classes.
-We analyse their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
-\begin{itemize}
-\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
-\item{ RQ2 - Which kind of chatbots would teachers find useful in their classes? }
-\item{ RQ3 - Which kind of interaction do teachers prefer with their students? }
-\item{ RQ4 - What kind of interaction media features do teachers value the most? }
-
-\end{itemize}
-
-We will try to answer these questions through the analysis of questions and answers in the two surveys.
-Eventually, what we want to obtain is a series of recommendations to make a successful deployment of chatbot technologies (and, in some cases, general instant messaging applications) in higher education.
-
-The rest of the paper is organized as follows: Next is an overview of what current research has found about the use of messaging applications, including chatbots, in the classroom.
 The methodology used in the survey is presented in Section \ref{sec:meth}, and the results of the survey are presented next in Section \ref{sec:res}.

### 2021-07-07 edubots_surveys_future_paper.Rnw
Updated the introduction section
Deleted the extra information and added the updated introduction

@@
 
-In the framework of the EduBots KA2 European project\footnote{https://www.edubots.eu}, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms.
-A \textit{chatbot} is a program, sometimes based on Artificial Intelligence techniques, that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language.
-Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker's question fluently, and even ask other questions to the human.
-However, in most cases a simple messaging-application attached bot will help the students (and teachers); so neither computational intelligence nor comprehension of natural languages are requisites, the only one being the fact that they can be accessed from a synchronous conversational application such as the common instant messaging applications (e.g.
-Telegram, WhatsApp) used nowadays.
-% Antonio - This paragraph needs a conclusion. Why do we say (essentially) that chatbots are not needed and just a simple messaging bot is enough?
-
-The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with.
-These automatic systems ease personalized learning,
-adapting individuals' pace of learning, who get customized online tutoring outside the classroom.
-Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.
+A chatbot is a program, sometimes developed using Artificial Intelligence techniques, that allows a computer to communicate in a similar way as humans do \cite{Gong2008}, using natural language.
+Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{ moor2003turing }, since they are able to answer almost any question fluently, and even pose questions in their conversations.
+The recent advancement in this discipline has played an important role in many fields especially in education and online tutoring \cite{clarizia2018,Smutny2020}.
+These automatic systems facilitate the delivery of personalized learning by adapting to students’ pace of learning and providing customized online tutoring outside the classroom.
+Thus, chatbots can significantly contribute to providing interactive learning experiences as well as improving individual attention \cite{agarwal2020}.
 
 In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor.
-In fact, in many cases, students suffer from stress when they have to ask a question in front of the entire class.
-This is why many students prefer to remain silent and ask their question later via email.
-However, this means a waste of time and a delay of hours or even days to get the teacher's answer; moreover, it does not scale well with the size of the class.
-Chatbot technology has a potential to fill the gap between teacher and students, helping them to solve questions and carry out a dynamic and autonomous learning \cite{Griol2014,kim2020}.
-In addition, using an automated system such as a chatbot, allows the teacher to detect the most demanded topics, and on which he or she should consequently place more emphasis in class.
-
-Chatbots are obviously associated to messaging applications, and in particular, direct messaging applications, since they are the only type of applications that are able to support a synchronous conversation between the two parties.
-This is why in many cases chatbots couple messaging and the chatbot technology itself \cite{differ.chat}, while in others, you can create chatbots in any number of technologies and then attach them to a messaging application using their API (Application Program Interface).
-
-Given the potential advantages that chatbots could bring to the classroom, as a previous step, we created two surveys for bachelor and master degree students at the University of Granada (Spain), which were answered by more than 250 students.
-The obtained results were analysed with the object of identifying students' actual needs, in \cite{MoraChatbots2021}.
-The survey asked about their preferences on tools/applications for chatting and messaging, how do they use them in the educational context, who do they like to be with in the class messaging groups, and what do they expect bots and chatbots to do to aid them during their learning process.
-We concluded that students prefer to use known whatever messaging application, such as Telegram or WhatsApp, they are already using.
-They also expected chatbots to help them with their scheduling, to provide assignment grades and to search for class material.
-Only one of the applications mentioned, having them work with frequently asked questions, might actually require some understanding of natural language, although it can be formulated in such a way that is not needed.
-
-% Maybe move it to a different place later
-In the present work we aim to complement the aforementioned study with teacher attitudes; teachers are the ones that actually would need to implement, 
-% Antonio - 'deploy' instead implement? Since in Computer Sciences implement and program are synonyms...
-configure and maybe program chatbots.
-Thus, we have performed a survey among 300 teachers asking about their attitudes towards the use of bots or chatbots in their classes.
-We analyse their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
+In fact, in many cases, some students experience stress because of their need to ask a question in front of the entire class.
+This is why many students refrain to silence in the classroom and tend to contact their teachers later via email.
+Consequently, this can lead to not only a delay in obtaining answers to their questions but also can cause a significant increase in their teachers’ workload, especially when factoring in the disproportion between the class size and the number of teachers.
+Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning experience \cite{Griol2014,kim2020}.
+In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding.
+Given the potential benefits that chatbots could bring to the classroom, the focus of the EDUBOTS KA2 European project \footnote{https://www.edubots.eu}, the sponsor of this study, is to gather, analyse and disseminate best practice of the use of chatbots in higher education institutions.
+This study involves two phases of data collection.
+The first phase aimed to collect feedback from students about their actual needs \cite{MoraChatbots2021}.
+Hence, the objective was to collect information about students’ preferences of tools/applications for chatting and messaging, how they use them in educational context, who do they like to be with in the class messaging groups, and their expectations of the chatbots in terms of assisting them during their learning process.
+Therefore, two surveys for bachelor and master degree students at the University of Granada (Spain) were developed and answers from more than 250 students were collected.
+The key findings of the students surveys reveal that they prefer to use messaging applications, such as Telegram or WhatsApp as they are familiar to them.
+Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course’s resources.
+The results of the first phase were fed into the second phase of the study, which focussed on teachers’ opinions about using chatbots and messaging applications in classes.
+Another survey was developed for this purpose.
+Responses from 300 teachers were collected and analysed.
+This study focuses on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:
 \begin{itemize}

### 2021-07-07 edubots_surveys.Rnw
Updated the introduction section
Updated the introduction section

@@
 
-In the framework of the EduBots KA2 European project\footnote{https://www.edubots.eu}, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms.
-A \textit{chatbot} is a program, sometimes based on Artificial Intelligence techniques, that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language.
-Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker's question fluently, and even ask other questions to the human.
-However, in most cases a simple messaging-application attached bot will help the students (and teachers); so neither computational intelligence nor comprehension of natural languages are requisites, the only one being the fact that they can be accessed from a synchronous conversational application such as the common instant messaging applications (e.g.
-Telegram, WhatsApp) used nowadays.
-
 A chatbot is a program, sometimes developed using Artificial Intelligence techniques, that allows a computer to communicate in a similar way as humans do \cite{Gong2008}, using natural language.
-Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any question fluently, and even pose questions in their conversations.
+Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{ moor2003turing }, since they are able to answer almost any question fluently, and even pose questions in their conversations.
 The recent advancement in this discipline has played an important role in many fields especially in education and online tutoring \cite{clarizia2018,Smutny2020}.
@@
 Thus, chatbots can significantly contribute to providing interactive learning experiences as well as improving individual attention \cite{agarwal2020}.
-
-The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with.
-These automatic systems ease personalized learning,
-adapting individuals' pace of learning, who get customized online tutoring outside the classroom.
-Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.
-
-Given the potential benefits that chatbots could bring to the classroom, the focus of the EduBots KA2 European project, the sponsor of this study, is to gather, analyse and disseminate best practice of the use of chatbots in higher education institutions.
+ In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor.
+In fact, in many cases, some students experience stress because of their need to ask a question in front of the entire class.
+This is why many students refrain to silence in the classroom and tend to contact their teachers later via email.
+Consequently, this can lead to not only a delay in obtaining answers to their questions but also can cause a significant increase in their teachers’ workload, especially when factoring in the disproportion between the class size and the number of teachers.
+Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning experience \cite{Griol2014,kim2020}.
+In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding.
+Given the potential benefits that chatbots could bring to the classroom, the focus of the EDUBOTS KA2 European project \footnote{https://www.edubots.eu}, the sponsor of this study, is to gather, analyse and disseminate best practice of the use of chatbots in higher education institutions.
 This study involves two phases of data collection.
@@
 Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course’s resources.
-
 The results of the first phase were fed into the second phase of the study, which focussed on teachers’ opinions about using chatbots and messaging applications in classes.
@@
 Responses from 300 teachers were collected and analysed.
-This study focuses on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:\begin{itemize}
+This study focuses on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:
+\begin{itemize}
 \item RQ1 - Are teachers already using messaging apps in their classes? 

### 2021-07-07 edubots_surveys.Rnw
Checkpoint since I just realized RQ4 has disappeared

@@
 
-A chatbot is a program, sometimes developed using Artificial Intelligence techniques, that allows a computer to communicate in a similar way as humans do \cite{Gong2008}, using natural language.
-Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{ moor2003turing }, since they are able to answer almost any question fluently, and even pose questions in their conversations.
+A chatbot is a program, sometimes developed using Artificial Intelligence, techniques, that allows an application to communicate in a similar way as humans do \cite{Gong2008}, using, in some cases, natural language.
+Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any question fluently, and even pose questions in their conversations.
 The recent advancement in this discipline has played an important role in many fields especially in education and online tutoring \cite{clarizia2018,Smutny2020}.
@@
 In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding.
+
 Given the potential benefits that chatbots could bring to the classroom, the focus of the EDUBOTS KA2 European project \footnote{https://www.edubots.eu}, the sponsor of this study, is to gather, analyse and disseminate best practice of the use of chatbots in higher education institutions.
-This study involves two phases of data collection.
-The first phase aimed to collect feedback from students about their actual needs \cite{MoraChatbots2021}.
+The study presented in this paper involves two phases of data collection.\begin{itemize}
+\item The first phase aimed to collect feedback from students about their actual needs \cite{MoraChatbots2021}.
 Hence, the objective was to collect information about students’ preferences of tools/applications for chatting and messaging, how they use them in educational context, who do they like to be with in the class messaging groups, and their expectations of the chatbots in terms of assisting them during their learning process.
-Therefore, two surveys for bachelor and master degree students at the University of Granada (Spain) were developed and answers from more than 250 students were collected.
+Therefore, two surveys for bachelor and master degree students at the University of Granada (Spain) were designed and answers from more than 250 students were collected.
 The key findings of the students surveys reveal that they prefer to use messaging applications, such as Telegram or WhatsApp as they are familiar to them.
 Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course’s resources.
-The results of the first phase were fed into the second phase of the study, which focussed on teachers’ opinions about using chatbots and messaging applications in classes.
+\item The results of the first phase were fed into the second phase of the study, which focused on teachers’ opinions about using chatbots and messaging applications in classes.
+\end{itemize}
+
 Another survey was developed for this purpose.

### 2021-07-07 edubots_surveys.Rnw
Re-adds RQ4 which has disappeared
Adds common survey questions

@@
 \item RQ3 - Which kind of interaction do teachers prefer with their students?
+\item RQ4 - What kind of interaction media features do teachers value the most?
 \end{itemize}
@@
 
-The initial survey was done in two different forms, one for university and other for tertiary non-university teachers.
+The initial survey was done in two separate Google forms, one for university and other for tertiary non-university teachers.
 Questions and responses were the same, except for the type of tertiary degrees that were taught.
@@
 A total of 282 teachers responded to the survey: 193 teaching at the University (68.4\%) and 89 at high school (31.6\%).
+
+All surveys had the same common, initial questions for segmentation:\begin{itemize}
+\item Degrees or titles where the teacher was working, either university or other tertiary education.
+\item Discipline: Engineering, Social Sciences, Health and Bio, Sciences, Humanities, Other.
+\item Gender: Man, Woman, Rather not say.
+\item Age: 25-35, 35-45, 45-55, more than 55.
+\item Experience on the job: up to 5 years, 5-15 years, 15-25 years, more than 25 years.
+\item Type of degree: university, other tertiary education. This question was implicit in the first survey, since one and the other filled different forms, it was explicit in the second survey.
+\end{itemize}
 

### 2021-07-08 edubots_surveys.Rnw
Revising the new Introduction

@@
 In most cases, the magnitude of the uptake of the new technology impinges on the collaboration of all the parties using it.
-Hence, examining the users’ attitudes and the opinions is an important first step in boosting this collaboration and reaping the benefits of the technology.
+Hence, examining the users’ attitudes and their opinions is an important first step in boosting this collaboration and reaping the benefits of the technology.
 Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp, Telegram and Facebook Messenger took place.
@@
 
-A chatbot is a program, sometimes developed using Artificial Intelligence, techniques, that allows an application to communicate in a similar way as humans do \cite{Gong2008}, using, in some cases, natural language.
-Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any question fluently, and even pose questions in their conversations.
+A \textit{chatbot} is a program, sometimes developed using Artificial Intelligence techniques, able to communicate in a similar way as humans do \cite{Gong2008}, using, in some cases, natural language.
+Indeed, most of these applications would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any question fluently, and even pose own questions in their conversations.
 The recent advancement in this discipline has played an important role in many fields especially in education and online tutoring \cite{clarizia2018,Smutny2020}.
@@
 In fact, in many cases, some students experience stress because of their need to ask a question in front of the entire class.
-This is why many students refrain to silence in the classroom and tend to contact their teachers later via email.
+This is why many students refrain to speak
+ % Antonio - I guess refrain to silence is the opposite of what we wanted to say, isn't it? :D
+ in the classroom and tend to contact their teachers later via email.
  Consequently, this can lead to not only a delay in obtaining answers to their questions but also can cause a significant increase in their teachers’ workload, especially when factoring in the disproportion between the class size and the number of teachers.
@@
 
-Given the potential benefits that chatbots could bring to the classroom, the focus of the EDUBOTS KA2 European project \footnote{https://www.edubots.eu}, the sponsor of this study, is to gather, analyse and disseminate best practice of the use of chatbots in higher education institutions.
-The study presented in this paper involves two phases of data collection.\begin{itemize}
-\item The first phase aimed to collect feedback from students about their actual needs \cite{MoraChatbots2021}.
+Given the potential benefits that chatbots could bring to the classroom, the focus of the EDUBOTS KA2 European project \footnote{https://www.edubots.eu}, the sponsor of this study, is to gather, analyse and disseminate best practices on the use of chatbots in higher education institutions.
+% Antonio - Actually there was a previous study focused on students and the present one, focused on teachers. I'll try to explain this, please revise the text below. ;)
+With this aim, the authors conducted a previous study aimed to collect feedback from students about their actual needs \cite{MoraChatbots2021}.
 Hence, the objective was to collect information about students’ preferences of tools/applications for chatting and messaging, how they use them in educational context, who do they like to be with in the class messaging groups, and their expectations of the chatbots in terms of assisting them during their learning process.
@@
 Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course’s resources.
-\item The results of the first phase were fed into the second phase of the study, which focused on teachers’ opinions about using chatbots and messaging applications in classes.
-\end{itemize}
-
-Another survey was developed for this purpose.
-Responses from 300 teachers were collected and analysed.
+
+The results of this first phase were fed into the second phase of the study, which is addressed in the present work.
+It is focused on the other main actor in education process: the teacher.
+Thus, we have now collected and analised teachers’ opinions about using chatbots and messaging applications in classes.
+To this end two new surveys have been developed, and responses from almost 500 teachers (282 + 205) were collected and analysed.
 This study focuses on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:
@@
 
+We will try to answer these questions through the analysis of questions and answers in the two surveys.
+Eventually, what we want to obtain is a series of recommendations to make a successful deployment of chatbot technologies (and, in some cases, general instant messaging applications) in higher education.
+
 The remainder of the paper is organized as follows: Next is an overview of what current research has found about the use of messaging applications, including chatbots, in the classroom.
-The methodology used in the survey is presented in Section \ref{sec:meth}, and the results of the survey are presented next in Section \ref{sec:res}.
+The methodology used in the surveys is presented in Section \ref{sec:meth}, and the results of the surveys are presented next in Section \ref{sec:res}.
 Finally, we discuss these results and conclude with a series of recommendations in the section that closes the paper.

### 2021-07-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw

@@
 In fact, in many cases, some students experience stress because of their need to ask a question in front of the entire class.
-This is why many students refrain to speak
+This is why many students resort to silence
  % Antonio - I guess refrain to silence is the opposite of what we wanted to say, isn't it? :D
+ % mistaking "resort" for "refrain". You don't say "refrain to", but refrain from.
  in the classroom and tend to contact their teachers later via email.
- Consequently, this can lead to not only a delay in obtaining answers to their questions but also can cause a significant increase in their teachers’ workload, especially when factoring in the disproportion between the class size and the number of teachers.
+ Consequently, this can lead to not only a delay in obtaining answers to their questions butcan also cause a significant increase in their teachers’ workload, especially when factoring in the disproportion between the class size and the number of teachers.
 Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning experience \cite{Griol2014,kim2020}.
@@
 Given the potential benefits that chatbots could bring to the classroom, the focus of the EDUBOTS KA2 European project \footnote{https://www.edubots.eu}, the sponsor of this study, is to gather, analyse and disseminate best practices on the use of chatbots in higher education institutions.
-% Antonio - Actually there was a previous study focused on students and the present one, focused on teachers. I'll try to explain this, please revise the text below. ;)
-With this aim, the authors conducted a previous study aimed to collect feedback from students about their actual needs \cite{MoraChatbots2021}.
+
+ The line of research of which this paper is a part has involved two phases of data collection.
+ \begin{itemize}
+\item The first phase aimed to collect feedback from students about their actual needs \cite{MoraChatbots2021}.
 Hence, the objective was to collect information about students’ preferences of tools/applications for chatting and messaging, how they use them in educational context, who do they like to be with in the class messaging groups, and their expectations of the chatbots in terms of assisting them during their learning process.
@@
 Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course’s resources.
-
-The results of this first phase were fed into the second phase of the study, which is addressed in the present work.
-It is focused on the other main actor in education process: the teacher.
-Thus, we have now collected and analised teachers’ opinions about using chatbots and messaging applications in classes.
-To this end two new surveys have been developed, and responses from almost 500 teachers (282 + 205) were collected and analysed.
-This study focuses on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:
+\item The results of the first phase were fed into the second phase of the study, which focused on teachers’ opinions about using chatbots and messaging applications in classes.
+This is what is going to be presented in this paper.
+\end{itemize}
+
+Initially, a single survey was developed for this purpose.
+Responses from 300 teachers were collected and analysed.
+An initial analysis led to the creation of a second survey, which collected responses from 200 different higher education teachers.
+The questions on this survey focus on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:
+
 \begin{itemize}
@@
 <<messaging_organization, echo=FALSE, fig.width=19/2.54, fig.height=5/2.54>>=
-survey.pilot.MessagingOrganization <- within(survey.pilot.MessagingOrganization, Messaging.Organization <- factor(Messaging.Organization, levels=names(sort(table(Messaging.Organization), decreasing=TRUE))))
-ggplot(survey.pilot.MessagingOrganization, aes( x = Messaging.Organization, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90))+coord_flip()+ theme(axis.title.y=element_blank())
+survey.pilot.MessagingOrganization %>%mutate(Messaging.Organization = ifelse(as.character(Messaging.Organization) == "A chat with all the students and teachers in my Faculty/School", "A chat with all the students and teachers in my Faculty/School/all years", as.character(Messaging.Organization))) %>%
+  mutate(Messaging.Organization = ifelse(as.character(Messaging.Organization) == "A chat with all the students and teachers in the same studies (all years)", "A chat with all the students and teachers in my Faculty/School/all years", as.character(Messaging.Organization)))->df2
+
+df2 %>%mutate(Messaging.Organization = ifelse(as.character(Messaging.Organization) == "A chat with all the students and teachers in my Faculty/School/all years", "Chat interactions among all students, teachers of the School/Faculty", as.character(Messaging.Organization))) %>%
+  mutate(Messaging.Organization = ifelse(as.character(Messaging.Organization) == "I'd rather leave students self-organize and not be part of the chat", "Teacher not being part of the interaction", as.character(Messaging.Organization)))%>%
+  mutate(Messaging.Organization = ifelse(as.character(Messaging.Organization) == "A chat with my students in the same course", "Chat interactions among students in the same course", as.character(Messaging.Organization)))%>%
+  mutate(Messaging.Organization = ifelse(as.character(Messaging.Organization) == "A chat with all students and teachers in the same semester/year", "Chat interactions among students of the same study year and teachers", as.character(Messaging.Organization)))->df2
+
+df2 <- within(df2, Messaging.Organization <- factor(Messaging.Organization, levels=names(sort(table(Messaging.Organization), decreasing=TRUE))))
+ggplot(df2, aes( x = Messaging.Organization, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90))+coord_flip()+ theme(axis.title.y=element_blank())
 @
@@
 \multicolumn{1}{c}{} & \multicolumn{1}{c}{Frequency} & \multicolumn{1}{c}{\%} & Frequency & \multicolumn{1}{c}{\%} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Chat interactions among \\ students in the same course\end{tabular} & 171 & 60.6 & 110 & 39.0 \\
-\begin{tabular}[c]{@{}l@{}}Chat interactions among students, \\ teachers, and the faculty\end{tabular} & 13 & 4.6 & 269 & 95.4 \\
-\begin{tabular}[c]{@{}l@{}}Chat interactions among students \\ of the same study year and teachers\end{tabular} & 51 & 18.1 & 231 & 81.9 \\
-\begin{tabular}[c]{@{}l@{}}Teacher not being part of the \\ interaction\end{tabular} & 113 & 40.1 & 169 & 59.9 \\ \hline
+%\begin{tabular}[c]{@{}l@{}}Chat interactions among \\ students in the same course\end{tabular} & 171 & 60.6 & 110 & 39.0 \\
+%\begin{tabular}[c]{@{}l@{}}Chat interactions among students, \\ teachers of the School/Faculty\end{tabular} & 13 & 4.6 & 269 & 95.4 \\
+%\begin{tabular}[c]{@{}l@{}}Chat interactions among students \\ of the same study year and teachers\end{tabular} & 51 & 18.1 & 231 & 81.9 \\
+%\begin{tabular}[c]{@{}l@{}}Teacher not being part of the \\ interaction\end{tabular} & 113 & 40.1 & 169 & 59.9 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Chat interactions among \\ students in the same course\end{tabular} & 166 & 59.1 & 115& 40.9 \\
+\begin{tabular}[c]{@{}l@{}}Chat interactions among students, \\ teachers of the School/Faculty\end{tabular} & 19 & 6.7 & 266 & 94.3 \\
+\begin{tabular}[c]{@{}l@{}}Chat interactions among students \\ of the same study year and teachers\end{tabular} & 58 & 20.5 & 224 & 79.4 \\
+\begin{tabular}[c]{@{}l@{}}Teacher not being part of the \\ interaction\end{tabular} & 81 & 28.7 & 201 & 71.3 \\ \hline
 \end{tabular}
@@
 
-%Olia - Isn't the following paragraph better fitting for RQ3? What kind interactions do teachers prefer with their students? 
-% Moved here
 Regarding the social factor of chat groups that teachers use in class, according to Fig.
@@
 As it appears in the responses presented above, teachers’ responses are distributed between positive and negative in relation to the media features: analytics, connectivity, and hidden phone, while for the features: familiarity, horizontally, sustainability and officiality the majority provided a positive response, designating their preference to these features.
-On the other hand, the majority of teachers seems to consider not valuable the presence of official formation, pluggability, unidirectionality and synchrony in the interaction media features of messaging apps.
+On the other hand, the majority of teachers seems to consider not valuable the presence of official formation, pluggability, unidirectionality and synchronization in the interaction media features of messaging apps.
+In other words, the majority of the teachers seem to prefer to use messaging apps to which they are already familiar, and which have been granted by their academic institution, normally also accompanied with technical support by the university’s staff and which do not require any actions on the behalf of the teachers for maintenance.
+In addition, the majority of the teachers value more the messaging apps in which there is no hierarchy in the communication level among the different users (i.e., teachers, students), and when the use of the app does not require or reveal their personal phone number.
+Last, the majority of the teachers value the most messaging apps that provide analytics in a form of a dashboard.
 
@@
 The statistically significant correlations are given in Table \ref{tab:interactionfeatures}.
+As indicated from the chi square results, the presence of the analytics feature in messaging apps, has been found to be positively correlated with the presence of features such as, connectivity, familiarity, official formation, pluggability and sustainability.
+This means, that teachers who prefer to use an app (or tool) that provides analytics about students’ actions and/or performance, most probably also prefer this app to be able to be connected to other applications, offer different plugins to the teachers and be an app with which the teachers are already familiar, while receiving some training from the university about its use and do not have to worry about its maintenance.
+In addition, the hidden phone feature was found to be correlated with the features: official formation (i.e., the university offers some training courses or talks about the tool/app) and unidirectionality (i.e., only the teacher can publish information in the channel).
+This can be expected, as teachers might prefer not to reveal personal data, such as their personal phone number, when the tool is being introduced by the university and when the level of communication is one-way (i.e., from the teacher to the students).
+Furthermore, pluggability has been found to be correlated with official formation, implying that teachers who prefer pluggability as a feature in a messaging app/tool, they should also prefer to having this tool/app being properly and officially introduced by the university and offer some training about its usage.
 
@@
 Two clusters occurred from the analysis: cluster 1 (n=78, 60.9\%) was comprise of instructors who did not value interaction media pluggability, connectivity, official formation, but valued interaction media analytics, familiarity, officiality, while cluster 2 (n=50, 39.1\%) was comprise of instructors from which the majority did not value media analytics, official formation, familiarity, but valued pluggability, connectivity, and officiality.
+The formation of the two clusters demonstrates different trends that appear to exist in teachers’ responses, based on their most preferred interaction media features.
+In other words, there is a group of teachers who value the most certain features, such as being familiar with an application, having access to analytics, and having the support from the university when using the application, while a second group of teachers seems to value mostly the features of pluggability, the capability of the app to connect with other apps, and receiving training from the university before/while using the app for teaching purposes.
 Interaction media pluggability appears to have the most important predictor importance in the clustering of cases (predictor importance = 1.0), whilst media unidirectionality was the least important factor (predictor importance = 0.04).

### 2021-07-09 scripts/process.R
fixes table and figure in RQ3 closes #36

@@ -173,11 +173,20 @@ df <-select(data.MessagingOrganization, Messaging.Organization, Gender, Sector, 
 df[as.character(df$Gender)!="PNTS", ] -> df1
 df1[as.character(df1$Gender)!="No", ] -> df1
 df1[as.character(df1$Discipline)!="No", ] -> df1
-df1[as.character(df1$Experience)!="No", ] -> df1
+df1[as.character(df1$Experience)!="No", ] -> df2
 df1[as.character(df1$Sector)!="No", ] %>% droplevels -> df2
+#df2 %>%mutate(Sector = ifelse(as.character(Sector) == "No", "Vocational", as.character(Sector)))->df2
+#df2[as.character(df2$Gender)!="PNTS", ] -> df1
+
 df2 %>%mutate(Messaging.Organization = ifelse(as.character(Messaging.Organization) == "A chat with all the students and teachers in my Faculty/School", "A chat with all the students and teachers in my Faculty/School/all years", as.character(Messaging.Organization))) %>%
   mutate(Messaging.Organization = ifelse(as.character(Messaging.Organization) == "A chat with all the students and teachers in the same studies (all years)", "A chat with all the students and teachers in my Faculty/School/all years", as.character(Messaging.Organization)))->df2
-#df2[as.character(df2$Gender)!="PNTS", ] -> df1
+df2 %>%mutate(Messaging.Organization = ifelse(as.character(Messaging.Organization) == "A chat with all the students and teachers in my Faculty/School/all years", "Chat interactions among all students, teachers of the School/Faculty", as.character(Messaging.Organization))) %>%
+  mutate(Messaging.Organization = ifelse(as.character(Messaging.Organization) == "I'd rather leave students self-organize and not be part of the chat", "Teacher not being part of the interaction", as.character(Messaging.Organization)))%>%
+  mutate(Messaging.Organization = ifelse(as.character(Messaging.Organization) == "A chat with my students in the same course", "Chat interactions among students in the same course", as.character(Messaging.Organization)))%>%
+  mutate(Messaging.Organization = ifelse(as.character(Messaging.Organization) == "A chat with all students and teachers in the same semester/year", "Chat interactions among students of the same study year and teachers", as.character(Messaging.Organization)))->df2
+
+df2 <- within(df2, Messaging.Organization <- factor(Messaging.Organization, levels=names(sort(table(Messaging.Organization), decreasing=TRUE))))
[…]

### 2021-07-10 edubots_surveys.Rnw
fixes minor typos/errors

--- 2021-07-09 edubots_surveys.Rnw
@@
 The key findings of the students surveys reveal that they prefer to use messaging applications, such as Telegram or WhatsApp as they are familiar to them.
-Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course’s resources.
+Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course resources.
 \item The results of the first phase were fed into the second phase of the study, which focused on teachers’ opinions about using chatbots and messaging applications in classes.
@@
 \item RQ3 - Which kind of interaction do teachers prefer with their students?
-\item RQ4 - What kind of interaction media features do teachers value the most?
+\item RQ4 - Which kind of interaction media features do teachers value the most?
 \end{itemize}
@@
 
-The initial survey was done in two separate Google forms, one for university and other for tertiary non-university teachers.
+The initial survey was done in two separate Google forms, one for university and other for tertiary non-university teachers (vocational education).
 Questions and responses were the same, except for the type of tertiary degrees that were taught.
@@
 \item Discipline: Engineering, Social Sciences, Health and Bio, Sciences, Humanities, Other.
-\item Gender: Man, Woman, Rather not say.
+\item Gender: Man, Woman, Prefer not to say.
 \item Age: 25-35, 35-45, 45-55, more than 55.
 \item Experience on the job: up to 5 years, 5-15 years, 15-25 years, more than 25 years.
-\item Type of degree: university, other tertiary education. This question was implicit in the first survey, since one and the other filled different forms, it was explicit in the second survey.
+\item Type of degree: university, other tertiary education (vocational education).
+This question was implicit in the first survey, since one and the other filled different forms, it was explicit in the second survey.
 \end{itemize}
@@
 % Olia- in the text below, we refer to "communucation tools", we should be consisten with the terms we use. Should we refere to communication tools? Messaging apps? Chat tools? 
-Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are their feelings and preferences with regard to the use of communication tools with students, and even using bots or chatbots in the classroom.
+Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what  their feelings and preferences are with regard to the use of communication tools with students, and even using bots or chatbots in the classroom.
 In addition the survey asked about the most relevant \textit{Interaction media features} for the teachers with respect to the potential tool to use in class. These features are:
@@
 
-% Antonio - I'm not sure about the last one (Synchrony)
-
 % ********************** RESULTS ****************************
@@
 Finally, the responses are equally distributed attending to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 26\% for 6-15 years of experience, 30\% for 16-25, and 20\% for teachers with more than 25 years of experience.
-
-% [pedro]  the way these (5) figures are shown is a bit strange: different sizes of plots...
 
@@
 
-%\subsection{RQ4 - What kind of interaction media features do teachers value the most?}
+%\subsection{RQ4 - Which kind of interaction media features do teachers value the most?}
 
@@
 
-\subsection{RQ4 - What kind of interaction media features do teachers value the most? }
+\subsection{RQ4 - Which kind of interaction media features do teachers value the most? }
 

### 2021-07-11 edubots_surveys.Rnw
Changed to teachers

@@
 Despite its (arguably) successful implementation in different higher education institutions, 
-over all in the fringes of educational activity, its implementation or deployment is not trivial.
+over all in the fringes of educational activity, not in the actual interaction student-teacher, its implementation or deployment is not trivial.
 Some authors, for instance \cite{sjostrom2018designing} have proposed a conceptual
@@
 Regarding Gender grouping, both gender agree in their uses, so it seems not relevant at all.
-When looking at the plot containing the sector differentiation it is interesting ot observe how university professors prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational/High School teachers.
+When looking at the plot containing the sector differentiation it is interesting ot observe how university teachers prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational/High School teachers.
 This seems reasonable as the frequency of seeing the students is smaller at the University so, automating the grade notification for continuous evaluation could seem much more comfortable using an automated tool than using the traditional platform.
-Furthermore, the high student/professor ratios that university professors have to deal with could be another reason to have a higher number of them willing to use chatbots for FAQs.
+Furthermore, the high student/teacher ratios that university docents have to deal with could be another reason to have a higher number of them willing to use chatbots for FAQs.
 This could ameliorate the number of misunderstandings and email overload that so many students might generate.
 
-The results, when grouping by experience, confirm the previous observation that experienced professors are not afraid of changes and are willing to accept new technological challenges, at least, in the same way that younger professors are.
-From this concrete plot it is interesting as well the fact that very few young/inexperience professors are willing to use chatbots for other uses.
-This reinforces the hypothesis thrown at the beginning of this section and, as these professors have less experience, they also have less field of view to think about ways of using chatbots.
+The results, when grouping by experience, confirm the previous observation that experienced teachers are not afraid of changes and are willing to accept new technological challenges, at least, in the same way that younger teachers are.
+From this concrete plot it is interesting as well the fact that very few young/inexperience teachers are willing to use chatbots for other uses.
+This reinforces the hypothesis thrown at the beginning of this section and, as these teachers have less experience, they also have less field of view to think about ways of using chatbots.
 
@@
 \begin{itemize}
- \item Professors want to have support from their corresponding institution.
+ \item Teachers want to have support from their corresponding institution.
 This is probably due to the strict European data regulations and to avoid the overhead required to sing up and deleting students from year to year.
 
- \item Professors need sustainability.
+ \item Teachers need sustainability.
 The main reason is that implementing changes is expensive in terms of effort and prone to errors in the first years of implementing new procedures, therefore, it is logical that if chatbots or messaging platforms are to be introduced, they want this change to be as permanent as possible.
@@
 %Olia: be consistent in the terms being used, we refer to teachers, then to professors. I would replace the word "professors" above with the word "teachers". 
+% Done (mostly) - JJ
 

### 2021-07-12 edubots_surveys.Rnw
Fixes during conference

@@
 The focus of these surveys is to collect teachers’ feedback about their opinions of the introduction of the messaging platforms and chatbots in their classes, understand their needs and to gather information about the various educational use cases where these tools are valuable.
-In addition, an analysis of how and when teachers’ attitudes towards the use of these tools can vary across gender, experience, and their discipline of specialisation is presented.
+In addition, an analysis of how and when teachers’ opinions towards the use of these tools can vary across gender, experience, and their discipline of specialisation is presented.
 The key findings of this study highlight the factors that can contribute to the advancement of the adoption of messaging platforms and chatbots in higher education institutions to achieve the desired learning outcomes.
@@
 In most cases, the magnitude of the uptake of the new technology impinges on the collaboration of all the parties using it.
-Hence, examining the users’ attitudes and their opinions is an important first step in boosting this collaboration and reaping the benefits of the technology.
+Hence, examining the users’ opinions and their opinions is an important first step in boosting this collaboration and reaping the benefits of the technology.
 Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp, Telegram and Facebook Messenger took place.
@@
 the most important is the blurring of social and academic life. Examining these
-attitudes will be the objective of RQ3 in this paper.
+opinions will be the objective of RQ3 in this paper.
 
@@
 This is why examining the role of MIM in higher education is still a challenge,
-and why the attitudes of the teaching community towards them have to be
+and why the opinions of the teaching community towards them have to be
 examined, as we do in this paper.
@@
 This paper analyzed conversational chatbots in an one-to-one setting, finding that learning really benefited from it.
-This is, once again, a proof of the benefit of chatbots in certain settings; however, there are some attitudes that might prevent the successful acceptance of the technology, and these are what we are trying to find out in this paper, together with what kind of features would make its acceptance better.
+This is, once again, a proof of the benefit of chatbots in certain settings; however, there are some opinions that might prevent the successful acceptance of the technology, and these are what we are trying to find out in this paper, together with what kind of features would make its acceptance better.
 
@@
 
-We will present next the methodology we have followed to find out teachers' attitudes.
+We will present next the methodology we have followed to find out teachers' opinions.
 
@@
 
-\section{Results}
+\section{Results and analysis}
 \label{sec:res}
@@
 Finally, about 20\% also use Telegram.
-Only 19 teachers (6.7%) replied that they do not use any messaging app in their class.
+Only 19 teachers (6.7\%) replied that they do not use any messaging app in their class.
 Although gender differences are not significant, female teachers answered they use instant messaging apps more than male teachers (about 10\% more).
@@
 
-Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' attitudes towards the instant messaging apps.
+Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' opinions towards the instant messaging apps.
 The 273 answers are summarized in Fig.
@@
 Nevertheless, in higher education, institutions’ role in integrating these tools to their educational systems can improve the uptake of these applications and shape the social and educational experiences of their students.
-This integration, to be fruitful, institutions have to ensure that these messaging applications not only are GDPR compliant to keep students’ data secure but also should provide IT support to all stakeholders who use the applications .
+This integration, to be fruitful, institutions have to ensure that these messaging applications not only are GDPR compliant to keep students’ data secure but also should provide IT support to all stakeholders who use the applications.
+
 Moreover, this study clarifies the differences between the teachers’ perspectives and/or intentions and that of their students when using the messaging applications in higher education.
@@
 Therefore, both perspectives are complementary and play different roles in promoting the learning process.
+
+% What kidn of chatbots are preferred? (suggested by Fran)
+
+% No remarkable differences between different groups.
+
+% Only some COVID-response relationship.
+
+% Future study (suggested by Noorhan): how COVID influenced adoption of these technologies.
+
+% Emotial, mood for future work... Chatbots perform sentiment analysis
+
 %This section is repeated
@@
 The authors declare that they have no competing interests.
-
-% Antonio - If there is any, please indicate.
 

### 2021-07-12 edubots_surveys.Rnw
Small fixes here and there

@@
 
-From a qualitative point of view, these results show comsensus in a few key aspects:
-
+From a qualitative point of view, these results show consensus in a few key aspects:
+% Maybe move to conclusions 
 \begin{itemize}
@@
 \end{itemize}
-%Olia: be consistent in the terms being used, we refer to teachers, then to professors. I would replace the word "professors" above with the word "teachers". 
-% Done (mostly) - JJ
 
@@
 \ref{figure:predictor}).
-Two clusters occurred from the analysis: cluster 1 (n=78, 60.9\%) was comprise of instructors who did not value interaction media pluggability, connectivity, official formation, but valued interaction media analytics, familiarity, officiality, while cluster 2 (n=50, 39.1\%) was comprise of instructors from which the majority did not value media analytics, official formation, familiarity, but valued pluggability, connectivity, and officiality.
+Two clusters occurred from the analysis: cluster 1 (n=78, 60.9\%) was comprise of instructors who did not value interaction media pluggability, connectivity, official formation, but valued interaction media analytics, familiarity, support by the institution, while cluster 2 (n=50, 39.1\%) was comprise of instructors from which the majority did not value media analytics, official formation, familiarity, but valued pluggability, connectivity, and support by the institution.
 Interaction media pluggability appears to have the most important predictor importance in the clustering of cases (predictor importance = 1.0), whilst media unidirectionality was the least important factor (predictor importance = 0.04).
@@
 
+% ********************** Discussion section *******************
+\section{Discussion}
+
 % ********************** CONCLUSIONS ****************************
@@
 All the authors have contributed to the study presented in this manuscript.
+
 JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
+
 PAC has...
@@
 AG has...
+
 All authors have read and approved the final manuscript.

### 2021-07-12 edubots_surveys.Rnw
adds (partial) questions to methodology refs #20

@@
 
+% Including questions in surveys
+The first survey about the use of messaging apps in class include the following questions:
+
+\textit{1. Regarding the use of messaging apps in class, you prefer ...}
+\begin{itemize}
+\item A chat group with the students in the same course
+\item Students self-organize and with the teacher not being part of any chat group
+\item A chat group with the all the students and teachers of the School/High-School/Faculty
+\item A chat group with all the students and teachers of the same study year
+\end{itemize}
+
+\textit{2. Which messaging app platform do you use to communicate with your peers or students?}
+\begin{itemize}
+\item Whatsapp
+\item Telegram
+\item LinkedIn
+\item Twitter messages
+\item Discord
+\item Slack
+\item Snapchat
+\item The platform provided by your own institution
+\item None, I do not use any messaging app to communicate with my students
+\end{itemize}
+
+\textit{3. Which kind of chatbots (software that automatically respond to questions or commands) could be useful to improve the learning results with your students or help you managing your course?}
+\begin{itemize}
+\item Agenda bots that e.g. remind students about project deadlines
+\item Bots that collect and provide answers to frequent questions
+\item Bots that inform students about their grades
+\item Bots that help with the class materials (e.g. searching for topics about a concept, or asking about them)
+\end{itemize}
+
+\textit{4. The virtualization of teaching due to the COVID pandemic during this year and the previous one, did it mean any change in your viewpoint or use of messaging apps in class?}
+\begin{itemize}
+\item No, I did use it before and use it now
+\item Yes, I started using safer alternatives
+\item Yes, I did not use any messaging platform before but I do use it now
+\item No, I did not use any messaging platform before or now
+\end{itemize}
+
 The second survey followed the same paths, only in this case there was a single questionnaire, and with a different scope, focusing on the kind of interaction media features that teachers value the most.
@@
 Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what  their feelings and preferences are with regard to the use of communication tools with students, and even using bots or chatbots in the classroom.
-In addition the survey asked about the most relevant \textit{Interaction media features} for the teachers with respect to the potential tool to use in class. These features are:
+In addition the survey asked about the most relevant \textit{Interaction media features} for the teachers with respect to the potential tool to use in class.
+
+The specific questions included in this second survey are listed below:
+
+\textit{1. You prefer the interaction with your students to be ...}
 \begin{itemize}
-\item \textit{Analytics}: the tool allows to extract data about students performance or development during the academic course on the teacher's subject.
-\item \textit{Connectivity}: it is possible to link or connect the tool with other applications.
-\item \textit{Familiarity}: it is something already known or previously used, so no need to learn something new.
-\item \textit{Hidden Phone}: it is possible to use the tool without showing my phone number, normally using an alias or an own account independent from my physical telephone.
-\item \textit{Horizontally}: all the actors are at the same level (for instance, teacher and students). There is not a hierarchy.
-\item \textit{Official formation}: the university offers some training courses or talks about the tool (mainly for teachers). 
-\item \textit{Pluggability}: the tool offers different pluggins to the teacher, so he/she can deploy his/her own implemented modules.
-\item \textit{Sustainability}: teacher should not be worried about the tool maintenance.
-\item \textit{Unidirectionality}: only the teacher can publish information in the channel, i.e. students are not allowed to ask or answer.
-\item \textit{Officiality}: the tool has been granted by the university where the teacher works. This means normally that there is also technical support by university's staff.
-\item \textit{Synchronous communication}: the interactions between teacher and students take place in real time, i.e. it is not a delayed communication scheme such as e-mail.
+\item Synchronous: students and teacher/s in the same space, simultaneously
+\item Asynchronous: the student asks at anytime, the teacher responds whenever possible
 \end{itemize}
+
+\textit{2. Regarding the interaction with your students, you ...}
+\begin{itemize}
+\item Prefer it to be done by institutional means/tools: office hours, forum/messages via the virtual campus, institutional email
+\item Admit the use of other means/toosl: blogs, chat groups in messaging platforms, any others.
+\end{itemize}
+
+\textit{3. Which media features do you value the most for your interaction with your students?}
+\begin{itemize}
+\item Familiarity with its use i.e. that I do not need to learn a new tool
+\item Familiarity i.e. that I do not need to learn a new tool
+\item Admit the use of other means/toosl: blogs, chat groups in messaging platforms, any others.
+\end{itemize}
+
+%These features are:
+%\begin{itemize}
+%\item \textit{Analytics}: the tool allows to extract data about students performance or development during the academic course on the teacher's subject.
+%\item \textit{Connectivity}: it is possible to link or connect the tool with other applications.
+%\item \textit{Familiarity}: it is something already known or previously used, so no need to learn something new.
+%\item \textit{Hidden Phone}: it is possible to use the tool without showing my phone number, normally using an alias or an own account independent from my physical telephone.
+%\item \textit{Horizontally}: all the actors are at the same level (for instance, teacher and students). There is not a hierarchy.
+%\item \textit{Official formation}: the university offers some training courses or talks about the tool (mainly for teachers). 
+%\item \textit{Pluggability}: the tool offers different pluggins to the teacher, so he/she can deploy his/her own implemented modules.
+%\item \textit{Sustainability}: teacher should not be worried about the tool maintenance.
+%\item \textit{Unidirectionality}: only the teacher can publish information in the channel, i.e. students are not allowed to ask or answer.
+%\item \textit{Officiality}: the tool has been granted by the university where the teacher works. This means normally that there is also technical support by university's staff.
+%\item \textit{Synchronous communication}: the interactions between teacher and students take place in real time, i.e. it is not a delayed communication scheme such as e-mail.
+%\end{itemize}
 

### 2021-07-12 edubots_surveys.Rnw
finishes adding questions to methodology refs #20

@@
 \item Familiarity with its use i.e. that I do not need to learn a new tool
-\item Familiarity i.e. that I do not need to learn a new tool
-\item Admit the use of other means/toosl: blogs, chat groups in messaging platforms, any others.
+\item The official formation/training provided by your institution on its use
+\item That only one-directional communication is allowed (from teachers to students)
+\item Non-hierarchical tools that allowed teacher-to-student and student-to-student communication 
+\item That allow additional functionalities such as interfaces to other tools
+\item That allow teachers to develop/add their own functionalities (e.g. automatic correction tools)
+\item That let me avoid to worry about maintenance and that it is easily sustainable from one year to the next
+\item That allow to extract data to assess the student performance
 \end{itemize}

### 2021-07-16 edubots_surveys.Rnw
Add @oliatsi suggestion

@@
 %%%%%%%%%%%%%%%%%%%%%%%%% start of article main body
-% <put your article body there>
 
@@
 The sample includes mostly teachers from university, although about 32\% and 8\% are from vocational education in the first and second survey respectively.
-Regarding gender, in total 61\% are male teachers and 32\% female (approximately 5\% chose not to disclose it).
-Finally, the responses are equally distributed attending to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 26\% for 6-15 years of experience, 30\% for 16-25, and 20\% for teachers with more than 25 years of experience.
+Regarding gender, 61\% of the teachers were male and 32\% female (approximately 5\% chose not to disclose it).
+Finally, the responses are equally distributed according to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 26\% for 6-15 years of experience, 30\% for 16-25, and 20\% for teachers with more than 25 years of experience.
 
@@
 
+% Olia suggests to delete this, as well as figure 1.
 Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar. %, and as a matter of fact,
@@
 
-For answering RQ1, teachers were queried about whether they use messaging apps in their classes, specifically, Telegram, WhatsApp, Slack, or any other messaging app, and whether they use messaging apps provided by their Academic Institution.
-According to the results summarized in Fig.
-\ref{figure:chatbots_use}, teachers mainly use the instant messaging app provided by their institutions (55\%),  and Whatsapp (44\%), the most popular messaging app in Spain.
-Finally, about 20\% also use Telegram.
+For answering RQ1, teachers were queried about whether they use messaging apps in their classes, specifically, Telegram, WhatsApp, Slack, or any other messaging app, and whether they use messaging apps provided by their academic institution.
+Overall, the majority of the teachers responded that they do use messaging apps in their classrooms, from which apps provided by the academic institution (n=159, 56\%) and WhatsApp (n=124, 44.0\%) were the most common responses.
 Only 19 teachers (6.7\%) replied that they do not use any messaging app in their class.
+
+% Insert first Olia table here
+A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
+The relation between the latter variable and the instructors’ sector was significant, X2 (4, N = 282) = 9.598, p =0.048.
+The frequencies cross tabulated are given in Table 2.
+In effect, this finding indicates that how teachers responded to the use of messaging apps during the pandemic and in particular, whether they changed their habits in the use of apps for teaching purposes, was related to their sector (university vs vocational).
 Although gender differences are not significant, female teachers answered they use instant messaging apps more than male teachers (about 10\% more).
 Also, teachers in vocational Education also use Whatsapp more than university teachers.
-
-With respect to the distribution of the use of messaging apps per age, there are no significant differences for the Whatsapp and apps provided by their institutions.
+%Insert second Olia table here.
+
+With respect to the distribution of the use of messaging apps per age, there are no significant differences for Whatsapp and apps provided by their institutions. % Olia requests support for this.
 However, younger teachers use also Telegram with more than 25\%, a percentage that falls to about 10\% for teachers that are 55 or older.

### 2021-07-16 edubots_surveys.Rnw
Eliminated by agreement, suggested by @oliatsi

@@
 
-\begin{figure}[h!tbp]
-\begin{center}
-    \begin{minipage}[t]{0.3\textwidth}
-        \centering
-<<gender, echo=FALSE, fig.width=3.2, fig.height=2.5>>=
-#ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-freq.Gender$source<-rep("survey1")
-freqInteraction.Gender$source<-rep("survey2")
-freqbinded.Gender <- rbind(freq.Gender, freqInteraction.Gender)
-freqbinded.Gender$source <- factor(freqbinded.Gender$source) 
-freqbinded.Gender[as.character(freqbinded.Gender$Gender)!="No", ] -> df1
-ggplot(df1, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-@
-
-%       \includegraphics[width=\textwidth]{figures/gender.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.3\textwidth}
-        \centering
-<<age,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
-#ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-freq.Age$source<-rep("survey1")
-freqInteraction.Age$source<-rep("survey2")
-freqbinded.Age <- rbind(freq.Age, freqInteraction.Age)
-freqbinded.Age$source <- factor(freqbinded.Age$source) 
-freqbinded.Age[as.character(freqbinded.Age$Age)!="No", ] -> df1
-ggplot(df1, aes(x = Age, y=freqAge, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-@
-
-%       \includegraphics[width=\textwidth]{figures/age.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.3\textwidth}
-        \centering
-<<sector,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
-#ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-freq.Sector$source<-rep("survey1")
-freqInteraction.Sector$source<-rep("survey2")
-freqbinded.Sector <- rbind(freq.Sector, freqInteraction.Sector)
-freqbinded.Sector$source <- factor(freqbinded.Sector$source) 
-ggplot(freqbinded.Sector, aes(x = Sector, y=freqSector, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/sector.pdf}
-    \end{minipage}
-    \vspace{0.5mm}
-    \begin{minipage}[t]{0.38\textwidth}
-        \centering
-<<experience, echo=FALSE, fig.width=4.5, fig.height=3.475>>=
-#ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-freq.Experience$source<-rep("survey1")
-freqInteraction.Experience$source<-rep("survey2")
-freqbinded.Experience <- rbind(freq.Experience, freqInteraction.Experience)
-freqbinded.Experience$source <- factor(freqbinded.Experience$source) 
-freqbinded.Experience[as.character(freqbinded.Experience$Experience)!="No", ] -> df1
-ggplot(df1, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-@        
-%       \includegraphics[width=\textwidth]{figures/experience.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.52\textwidth}
-        \centering
-<<discipline,echo=FALSE, fig.width=8.2, fig.height=4.45>>=
-#ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-freq.Discipline$source<-rep("survey1")
-freqInteraction.Discipline$source<-rep("survey2")
-freqbinded.Discipline <- rbind(freq.Discipline, freqInteraction.Discipline)
-freqbinded.Discipline$source <- factor(freqbinded.Discipline$source) 
-freqbinded.Discipline$Discipline <- factor(freqbinded.Discipline$Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other"))
-ggplot(freqbinded.Discipline, aes(x = Discipline, y=freqDiscipline, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-@
-
-%       \includegraphics[width=\textwidth]{figures/discipline.pdf}
-    \end{minipage}
-\end{center}
-    \caption{Sample population description.
+% \begin{figure}[h!tbp]
+% \begin{center}
+%     \begin{minipage}[t]{0.3\textwidth}
+%         \centering
+% <<gender, echo=FALSE, fig.width=3.2, fig.height=2.5>>=
+% #ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+% freq.Gender$source<-rep("survey1")
+% freqInteraction.Gender$source<-rep("survey2")
+% freqbinded.Gender <- rbind(freq.Gender, freqInteraction.Gender)
+% freqbinded.Gender$source <- factor(freqbinded.Gender$source) 
+% freqbinded.Gender[as.character(freqbinded.Gender$Gender)!="No", ] -> df1
+% ggplot(df1, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+% @
+% 
+% %       \includegraphics[width=\textwidth]{figures/gender.pdf}
+%     \end{minipage}
+%     \begin{minipage}[t]{0.3\textwidth}
+%         \centering
+% <<age,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
+% #ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+% freq.Age$source<-rep("survey1")
+% freqInteraction.Age$source<-rep("survey2")
+% freqbinded.Age <- rbind(freq.Age, freqInteraction.Age)
+% freqbinded.Age$source <- factor(freqbinded.Age$source) 
+% freqbinded.Age[as.character(freqbinded.Age$Age)!="No", ] -> df1
+% ggplot(df1, aes(x = Age, y=freqAge, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+% @
+% 
+% %       \includegraphics[width=\textwidth]{figures/age.pdf}
+%     \end{minipage}
+%     \begin{minipage}[t]{0.3\textwidth}
+%         \centering
+% <<sector,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
+% #ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+% freq.Sector$source<-rep("survey1")
+% freqInteraction.Sector$source<-rep("survey2")
+% freqbinded.Sector <- rbind(freq.Sector, freqInteraction.Sector)
+% freqbinded.Sector$source <- factor(freqbinded.Sector$source) 
+% ggplot(freqbinded.Sector, aes(x = Sector, y=freqSector, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+% @
+% %       \includegraphics[width=\textwidth]{figures/sector.pdf}
+%     \end{minipage}
+%     \vspace{0.5mm}
+%     \begin{minipage}[t]{0.38\textwidth}
+%         \centering
+% <<experience, echo=FALSE, fig.width=4.5, fig.height=3.475>>=
+% #ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+% freq.Experience$source<-rep("survey1")
+% freqInteraction.Experience$source<-rep("survey2")
+% freqbinded.Experience <- rbind(freq.Experience, freqInteraction.Experience)
+% freqbinded.Experience$source <- factor(freqbinded.Experience$source) 
+% freqbinded.Experience[as.character(freqbinded.Experience$Experience)!="No", ] -> df1
+% ggplot(df1, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+% @        
+% %       \includegraphics[width=\textwidth]{figures/experience.pdf}
+%     \end{minipage}
+%     \begin{minipage}[t]{0.52\textwidth}
+%         \centering
+% <<discipline,echo=FALSE, fig.width=8.2, fig.height=4.45>>=
+% #ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+% freq.Discipline$source<-rep("survey1")
+% freqInteraction.Discipline$source<-rep("survey2")
+% freqbinded.Discipline <- rbind(freq.Discipline, freqInteraction.Discipline)
+% freqbinded.Discipline$source <- factor(freqbinded.Discipline$source) 
+% freqbinded.Discipline$Discipline <- factor(freqbinded.Discipline$Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other"))
+% ggplot(freqbinded.Discipline, aes(x = Discipline, y=freqDiscipline, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+% @
+% 
+% %       \includegraphics[width=\textwidth]{figures/discipline.pdf}
+%     \end{minipage}
+% \end{center}
+%     \caption{Sample population description.
 The responses from two surveys were collected amount to 282 for the first survey (\textit{survey1} in red) and 205 for the second (\textit{survey2} in blue).
 Data are shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
-\label{figure:teachers_population}
-\end{figure}
-
-% Olia suggests to delete this, as well as figure 1.
-Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar. %, and as a matter of fact,
-Additionally, as a matter of fact, as Figure \ref{figure:age.vs.exp} shows, age and experience are correlated strongly, with experience being roughly 20-30 years less than age. 
-This might indicate that a differential analysis for age and experience will not yield significant differences, except maybe in the 6-15 years experience group, which is spread over all ages.
+% \label{figure:teachers_population}
+% \end{figure}
+
+% % Olia suggests to delete this, as well as figure 1.
+% Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar. %, and as a matter of fact,
+% Additionally, as a matter of fact, as Figure \ref{figure:age.vs.exp} shows, age and experience are correlated strongly, with experience being roughly 20-30 years less than age. 
+% This might indicate that a differential analysis for age and experience will not yield significant differences, except maybe in the 6-15 years experience group, which is spread over all ages.
 At any rate, experience seems to be the dominating factor here and we'll use experience only unless we detect some significant difference by age.

### 2021-07-16 edubots_surveys.Rnw
Eliminated by agreement

@@
 
-\begin{figure}[h!tbp]
-\begin{center}
-<<interaction,message=FALSE,echo=FALSE, fig.height=2.0, fig.width=4.0>>=
-library(forcats)
-survey.interaction %>%
-    mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
-    mutate(Experience = fct_relevel(Experience, "0-05 years", "06-15 years", "16-25 years", "> 25 years" )) %>%
-    group_by( Age, Experience ) %>% summarise( n = n() ) %>% mutate( freq = n/sum(n)) -> Age.vs.Experience
-
-ggplot(Age.vs.Experience,aes(Age,Experience))+geom_point(aes(size=freq),colour="green")
-@
-\end{center}
-\caption{Correlation between age and experience.}
-\label{figure:age.vs.exp}
-\end{figure}
+% \begin{figure}[h!tbp]
+% \begin{center}
+% <<interaction,message=FALSE,echo=FALSE, fig.height=2.0, fig.width=4.0>>=
+% library(forcats)
+% survey.interaction %>%
+%     mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
+%     mutate(Experience = fct_relevel(Experience, "0-05 years", "06-15 years", "16-25 years", "> 25 years" )) %>%
+%     group_by( Age, Experience ) %>% summarise( n = n() ) %>% mutate( freq = n/sum(n)) -> Age.vs.Experience
+% 
+% ggplot(Age.vs.Experience,aes(Age,Experience))+geom_point(aes(size=freq),colour="green")
+% @
+% \end{center}
+% \caption{Correlation between age and experience.}
+% \label{figure:age.vs.exp}
+% \end{figure}
 

### 2021-07-16 edubots_surveys.Rnw
Check this out @fbarranco

@@
 Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' opinions towards the instant messaging apps.
-The 273 answers are summarized in Fig.
+The 273 % Fran, please check Olia's comment as having 282 answers.
+answers are summarized in Fig.
 \ref{figure:chatbots_use_postcovid}, showing that about 77\% of teachers already used these tools before the pandemic and kept using them during the pandemic lockdowns that forced students and educators to use remote education schemes.
@@
 In this case, blue shows positive contribution and red negative contribution to the test, and saturation shows how large is this contribution in contrast to the expected value by chance.
-Tables on the right side show adjusted standardized residuals that according to \cite{agresti2013categorical}, if greater than +/-2 for cases with few cells, indicate lack of fit of $H_0$ (bolded in our table).
+Tables on the right side show adjusted standardized residuals that according to \cite{agresti2013categorical}, if greater than +/-2 for cases with few cells, indicate lack of fit of $H_0$ (in boldface in our table).
 Also, the table shows the percentage of contribution to the test of each cell.

### 2021-07-16 edubots_surveys.Rnw
Latest comments and suggestions by @noorhanabbas @aguillen @olitsi
sorts things out in RQ1 and adds tables

@@
 
-For answering RQ1, teachers were queried about whether they use messaging apps in their classes, specifically, Telegram, WhatsApp, Slack, or any other messaging app, and whether they use messaging apps provided by their academic institution.
+For answering RQ1, teachers were queried about whether they use messaging apps in their classes, specifically, Telegram, WhatsApp, Slack, or any other messaging app, and whether they use messaging apps provided by their academic institution (see Table \ref{tab:use_messapps}).
 Overall, the majority of the teachers responded that they do use messaging apps in their classrooms, from which apps provided by the academic institution (n=159, 56\%) and WhatsApp (n=124, 44.0\%) were the most common responses.
@@
 
-% Insert first Olia table here
+\begin{table}[h!tbp]
+\begin{tabular}{lllll}
+\hline
+\multicolumn{1}{c}{Messaging App} & \multicolumn{2}{c}{Yes} & \multicolumn{2}{l}{No} \\ \cline{2-5} 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{Frequency} & \multicolumn{1}{c}{\%} & Frequency & \multicolumn{1}{c}{\%} \\ \hline
+Telegram & 62 & 22.0 & 220 & 78.0 \\
+WhatsApp & 124 & 44.0 & 158 & 56.0 \\
+Slack & 15 & 5.3 & 267 & 94.7 \\
+Other & 60 & 21.3 & 222 & 78.7 \\
+\begin{tabular}[c]{@{}l@{}}Provided by the Academic\\ Institution\end{tabular} & 159 & 56.4 & 123 & 43.6 \\
+None & 19 & 6.7 & 263 & 93.3 \\ \hline
+\end{tabular}
+\vspace{0.8em}
+\caption{Use of messaging apps in class}
+\label{tab:use_messapps}
+\end{table}
+
 A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
-The relation between the latter variable and the instructors’ sector was significant, X2 (4, N = 282) = 9.598, p =0.048.
-The frequencies cross tabulated are given in Table 2.
+The relation between the latter variable and the instructors’ sector was significant, $X^{2}_{(4, N = 282)} = 9.598$, $p =0.048$.
+The frequencies cross tabulated are given in Table \ref{tab:sector*covid}.
 In effect, this finding indicates that how teachers responded to the use of messaging apps during the pandemic and in particular, whether they changed their habits in the use of apps for teaching purposes, was related to their sector (university vs vocational).
+\begin{table}[h!tbp]
+\begin{tabular}{llccc}
+\hline
+ & \multicolumn{1}{c}{} & \multicolumn{2}{c}{Sector} & Total \\ \cline{3-5} 
+ & \multicolumn{1}{c}{} & \begin{tabular}[c]{@{}c@{}}University \\ (f)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Vocational\\ (f)\end{tabular} &  \\ \cline{2-5} 
+\multirow{4}{*}{\begin{tabular}[c]{@{}l@{}}Post-covid\\ changes\end{tabular}} & \begin{tabular}[c]{@{}l@{}}Yes, I use a safer messaging \\ app now\end{tabular} & 27 & 13 & 40 \\
+ & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use any \\ messaging app before, but \\ do use it now\end{tabular} & 31 & 13 & 44 \\
+ & \begin{tabular}[c]{@{}l@{}}No, I did use it before and \\ use it now\end{tabular} & 105 & 60 & 165 \\
+ & \begin{tabular}[c]{@{}l@{}}No, I didn’t use it before and \\ don’t use it now\end{tabular} & 22 & 2 & 24 \\
+Total &  & 193 & 89 & 282 \\ \hline
+\end{tabular}
+\vspace{0.8em}
+\caption{Sector * post-covid changes crosstabulation}
+\label{tab:sector*covid}
+\end{table}
+The majority of the teachers (n=165) mentioned that no changes in their habits occured due to the emergency remote teaching, as the use of messaging apps was part of their teaching practices and remains the same, from which 105 teachers come from the university, and 60 teachers from the vocational sector.
+The relationships between changes in the use of messaging apps, due to the covid-19 pandemic, and the instructors’ discipline, $X^{2}_{(24, N = 282)} = 44.856$, $p =0.006$, as well as the gender, $X^{2}_{(8, N = 282)} = 16.249$, p= 0.039 were also significant.
+This finding indicates that how teachers responded to the use of messaging apps during the pandemic was also related to their gender and discipline.
+In fact, from the majority of the teachers who did not change their habits in this respect (n=165), most of them are males (n=114), and come from the technology (n=60) and engineering (n=53) disciplines (see Tables \ref{tab:gender*covid}, \ref{tab:discipline*covid}).
+
+\begin{table}[h!tbp]
+\begin{tabular}{llcccc}
+\hline
+ & \multicolumn{1}{c}{} & \multicolumn{3}{c}{Gender} & Total \\ \cline{3-6} 
+ & \multicolumn{1}{c}{} & \begin{tabular}[c]{@{}c@{}}Male \\ (f)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Female\\ (f)\end{tabular} &  \begin{tabular}[c]{@{}c@{}}PNTS\\ (f)\end{tabular} & \\ \cline{2-6}
+\multirow{4}{*}{\begin{tabular}[c]{@{}l@{}}Post-covid\\ changes\end{tabular}} & \begin{tabular}[c]{@{}l@{}}Yes, I use a safer messaging \\ app now\end{tabular} & 20 & 20 & 0 & 40 \\
+ & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use any \\ messaging app before, but \\ do use it now\end{tabular} & 20 & 23 & 1 & 44 \\
+ & \begin{tabular}[c]{@{}l@{}}No, I did use it before and \\ use it now\end{tabular} & 114 & 47 & 4 & 165 \\
+ & \begin{tabular}[c]{@{}l@{}}No, I didn’t use it before and \\ don’t use it now\end{tabular} & 18 & 6 & 0 & 24 \\
+ & Other & 7 & 2 & 0 & 9 \\
+Total &  & 179 & 98 & 5 & 282 \\ \hline
+\end{tabular}
+\vspace{0.8em}
+\caption{Gender * post-covid changes crosstabulation}
+\label{tab:gender*covid}
+\end{table}
+
+\begin{table}[h!tbp]
+\centering
+\resizebox{\textwidth}{!}{
+\begin{tabular}{llcccccccc}
+\hline
+ & \multicolumn{1}{c}{} & \multicolumn{7}{c}{Disciplines} & Total \\ \cline{3-10} 
+ & \multicolumn{1}{c}{} & \begin{tabular}[c]{@{}c@{}}Engi- \\ neering(f)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Social \\ Sciences (f)\end{tabular} &  \begin{tabular}[c]{@{}c@{}}Sciences\\ (f)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Bio-\\ medicine (f)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Human-\\ ities(f)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Technol-\\ ogy(f)\end{tabular} &  \begin{tabular}[c]{@{}c@{}}Other\\ (f)\end{tabular} & \\ \cline{2-10}
+\multirow{4}{*}{\begin{tabular}[c]{@{}l@{}}Post-covid\\ changes\end{tabular}} & \begin{tabular}[c]{@{}l@{}}Yes, I use a safer \\ messaging app now\end{tabular} & 7 & 11 & 5 & 5 & 1 & 10 & 1 & 40 \\
+ & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use any \\ messaging app before, \\ but do use it now\end{tabular} & 13 & 12 & 5 &  4 &  2 &  7 & 1 & 44 \\
+ & \begin{tabular}[c]{@{}l@{}}No, I did use it before \\ and use it now\end{tabular} &60 &  26 &  20 &  4 & 0 & 53 &  2 &  165\\
+ & \begin{tabular}[c]{@{}l@{}}No, I didn’t use it \\ before and don’t \\ use it now\end{tabular} & 14 &  4 & 1 & 2 & 1 & 1 & 1 & 24 \\
+ & Other & 5  & 0 & 1 & 1 & 1 & 1 & 0 & 9 \\
+Total & & 99 &  53&  32&  16&  5&  72&  5&  282\\ \hline
+\end{tabular}}
+\vspace{0.8em}
+\caption{Discipline * post-covid changes crosstabulation}
+\label{tab:discipline*covid}
+\end{table}
+
 Although gender differences are not significant, female teachers answered they use instant messaging apps more than male teachers (about 10\% more).
 Also, teachers in vocational Education also use Whatsapp more than university teachers.
-%Insert second Olia table here.
-
 With respect to the distribution of the use of messaging apps per age, there are no significant differences for Whatsapp and apps provided by their institutions. % Olia requests support for this.
-However, younger teachers use also Telegram with more than 25\%, a percentage that falls to about 10\% for teachers that are 55 or older.
+However, younger teachers also use Telegram with more than 25\%, a percentage that falls to about 10\% for teachers that are 55 or older.
 The third column compares the use of these apps considering the number of years of experience.
-One interesting result is that, contrarily to the idea of technology adaptation issues when considering older teachers, about 65\% of teachers with more than 25 years of experience use the platforms provided by their institutions while the percentage goes down to less than 50\% for teachers with 6-15 years of experience.
+One interesting result is that, contrary to the idea of technology adaptation issues when considering older teachers, about 65\% of teachers with more than 25 years of experience use the platforms provided by their institutions while the percentage goes down to less than 50\% for teachers with 6-15 years of experience.
 
@@
 
-Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' opinions towards the instant messaging apps.
-The 273 % Fran, please check Olia's comment as having 282 answers.
+Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' viewpoints towards the use of instant messaging apps int their class.
+The 282
+% Fran, please check Olia's comment as having 282 answers -> I did remove some responses that Olia considered 'No' by default. I' ll keep it to 282 to be consistent
 answers are summarized in Fig.
@@
     \caption{Impact of COVID in the use of messaging apps in University and vocational education.}
+    % Have different sub-captions so that we can refer to specific subfigures - Olia
 \label{figure:chatbots_use_postcovid}
@@
 
-A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
+%A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
 The relation between the latter variable and the instructors’ sector was significant, $X^{2}_{(4, N = 282)} = 9.598$, $p =0.048$.
@@
 The relationships between changes in the use of messaging apps, due to the covid-19 pandemic, and the instructors’ discipline, $X^{2}_{(24, N = 282)} = 44.856$, $p =0.006$, as well as the gender, $X^{2}_{(8, N = 282)} = 16.249$, $p= 0.039$ were also significant.
-
-%TODO: This table is not referenced in the text
-\begin{table}[h!tbp]
-\begin{tabular}{lllll}
-\hline
-\multicolumn{1}{c}{Messaging App} & \multicolumn{2}{c}{Yes} & \multicolumn{2}{l}{No} \\ \cline{2-5} 
-\multicolumn{1}{c}{} & \multicolumn{1}{c}{Frequency} & \multicolumn{1}{c}{\%} & Frequency & \multicolumn{1}{c}{\%} \\ \hline
-Telegram & 62 & 22.0 & 220 & 78.0 \\
-WhatsApp & 124 & 44.0 & 158 & 56.0 \\
-Slack & 15 & 5.3 & 267 & 94.7 \\
-Other & 60 & 21.3 & 222 & 78.7 \\
-\begin{tabular}[c]{@{}l@{}}Provided by the Academic\\ Institution\end{tabular} & 159 & 56.4 & 123 & 43.6 \\
-None & 19 & 6.7 & 263 & 93.3 \\ \hline
-\end{tabular}
-\vspace{0.8em}
-\caption{Use of messaging apps in class}
-\label{tab:use_messapps}
-\end{table}
-
-\begin{table}[h!tbp]
-\begin{tabular}{llccc}
-\hline
- & \multicolumn{1}{c}{} & \multicolumn{2}{c}{Sector} & Total \\ \cline{3-5} 
- & \multicolumn{1}{c}{} & \begin{tabular}[c]{@{}c@{}}University \\ (f)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Vocational\\ (f)\end{tabular} &  \\ \cline{2-5} 
-\multirow{4}{*}{\begin{tabular}[c]{@{}l@{}}Post-covid\\ changes\end{tabular}} & \begin{tabular}[c]{@{}l@{}}Yes, I use a safer messaging \\ app now\end{tabular} & 27 & 13 & 40 \\
- & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use any \\ messaging app before, but \\ do use it now\end{tabular} & 31 & 13 & 44 \\
- & \begin{tabular}[c]{@{}l@{}}No, I did use it before and \\ use it now\end{tabular} & 105 & 60 & 165 \\
- & \begin{tabular}[c]{@{}l@{}}No, I didn’t use it before and \\ don’t use it now\end{tabular} & 22 & 2 & 24 \\
-Total &  & 193 & 89 & 282 \\ \hline
-\end{tabular}
-\vspace{0.8em}
-\caption{Sector * post-covid changes crosstabulation}
-\label{tab:sector*covid}
-\end{table}
 
@@
 As it was a multiple choice question, the counts are over the total number of people that answered.
-One of the most interesting questions that can arise from the plots, and the should require further study, is: Are teachers really aware of the possibilities of chatbots in the classroom?
-The reason to ask ourselves this question is due to the fact of the small number of responses for other uses in comparison with the other approaches proposed.
-Another way to look about it is that, unless you provide the specific instructions on how to use a tool, the teaching staff is already too busy or burn out to think about innovation.
-
-Regarding Gender grouping, both gender agree in their uses, so it seems not relevant at all.
-When looking at the plot containing the sector differentiation it is interesting ot observe how university teachers prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational/High School teachers.
-This seems reasonable as the frequency of seeing the students is smaller at the University so, automating the grade notification for continuous evaluation could seem much more comfortable using an automated tool than using the traditional platform.
-Furthermore, the high student/teacher ratios that university docents have to deal with could be another reason to have a higher number of them willing to use chatbots for FAQs.
-This could ameliorate the number of misunderstandings and email overload that so many students might generate.
-
-The results, when grouping by experience, confirm the previous observation that experienced teachers are not afraid of changes and are willing to accept new technological challenges, at least, in the same way that younger teachers are.
-From this concrete plot it is interesting as well the fact that very few young/inexperience teachers are willing to use chatbots for other uses.
-This reinforces the hypothesis thrown at the beginning of this section and, as these teachers have less experience, they also have less field of view to think about ways of using chatbots.
 
@@
 
-As it appears in the responses presented above, teachers’ responses are distributed between positive and negative in relation to the media features: analytics, connectivity, and hidden phone, while for the features: familiarity, horizontally, sustainability and officiality the majority provided a positive response, designating their preference to these features.
-On the other hand, the majority of teachers seems to consider not valuable the presence of official formation, pluggability, unidirectionality and synchrony in the interaction media features of messaging apps.
-
-From a qualitative point of view, these results show consensus in a few key aspects:
-% Maybe move to conclusions 
-\begin{itemize}
- \item Teachers want to have support from their corresponding institution.
-This is probably due to the strict European data regulations and to avoid the overhead required to sing up and deleting students from year to year.
-
- \item Teachers need sustainability.
-The main reason is that implementing changes is expensive in terms of effort and prone to errors in the first years of implementing new procedures, therefore, it is logical that if chatbots or messaging platforms are to be introduced, they want this change to be as permanent as possible.
-
- \item Keep it Simple.
-Media interaction requirements are simple and only a 2.4\% is requesting more features.
-This could be a sign of technological burn out produced by the previous and current courses where, due to the pandemic, the use of computer has increased significantly.
-\end{itemize}
-
 A chi-square test of independence was performed to examine the potential relationship among the various features.
@@
 
+% Add something about intro
+% RQ1 discussion about messaging app: they consider a IM the Moodle messaging
+% Olia: it's not so easy to change habits, even in the case of major crisis. - JJ
+% Relationship between changes, gender and discipline (Olia) - JJ
+
+% Olia: we have something for RQ 2 and 4.
+ One of the most interesting questions that can arise from the plots, and the should require further study, is: Are teachers really aware of the possibilities of chatbots in the classroom?
+The reason to ask ourselves this question is due to the fact of the small number of responses for other uses in comparison with the other approaches proposed.
+Another way to look about it is that, unless you provide the specific instructions on how to use a tool, the teaching staff is already too busy or burn out to think about innovation.
+
+% Noorhan comments negative experience with customer service chatbots, in which case people will not see the value of using it in their classes.
+They are not aware of something like that.
+Teaching chatbots are difficult to develop.
+Using very simple chatbots, or simply conversational interfaces, could help introduce this technology - JJ
+
+Regarding Gender grouping, both gender agree in their uses, so it seems not relevant at all.
+When looking at the plot containing the sector differentiation it is interesting ot observe how university teachers prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational/High School teachers.
+This seems reasonable as the frequency of seeing the students is smaller at the University so, automating the grade notification for continuous evaluation could seem much more comfortable using an automated tool than using the traditional platform.
+Furthermore, the high student/teacher ratios that university docents have to deal with could be another reason to have a higher number of them willing to use chatbots for FAQs.
+This could ameliorate the number of misunderstandings and email overload that so many students might generate.
+
+The results, when grouping by experience, confirm the previous observation that experienced teachers are not afraid of changes and are willing to accept new technological challenges, at least, in the same way that younger teachers are.
+From this concrete plot it is interesting as well the fact that very few young/inexperience teachers are willing to use chatbots for other uses.
+This reinforces the hypothesis thrown at the beginning of this section and, as these teachers have less experience, they also have less field of view to think about ways of using chatbots.
+
+As it appears in the responses presented above, teachers’ responses are distributed between positive and negative in relation to the media features: analytics, connectivity, and hidden phone, while for the features: familiarity, horizontally, sustainability and officiality the majority provided a positive response, designating their preference to these features.
+On the other hand, the majority of teachers seems to consider not valuable the presence of official formation, pluggability, unidirectionality and synchrony in the interaction media features of messaging apps.
+
+From a qualitative point of view, these results show consensus in a few key aspects:
+\begin{itemize}
+ \item Teachers want to have support from their corresponding institution.
+This is probably due to the strict European data regulations and to avoid the overhead required to sing up and deleting students from year to year.
+
+ \item Teachers need sustainability.
+The main reason is that implementing changes is expensive in terms of effort and prone to errors in the first years of implementing new procedures, therefore, it is logical that if chatbots or messaging platforms are to be introduced, they want this change to be as permanent as possible.
+
+ \item Keep it Simple.
+Media interaction requirements are simple and only a 2.4\% is requesting more features.
+This could be a sign of technological burn out produced by the previous and current courses where, due to the pandemic, the use of computer has increased significantly.
+\end{itemize}
+
+% Rq4: they seem to prefer interaction with students - Olia 
+% Alberto: using new metric so grade students, and also abotu horizontality
+
 % ********************** CONCLUSIONS ****************************
@@
 
+% Noorhan suggest that using some simple things could increase the perceived usefulness - JJ
+
 % What kidn of chatbots are preferred? (suggested by Fran)
@@
 
-% Emotial, mood for future work... Chatbots perform sentiment analysis
+% Emotinal, mood for future work... Chatbots perform sentiment analysis
 

### 2021-07-16 edubots_surveys.Rnw
reorganizes part of covid responses

@@
 Only 19 teachers (6.7\%) replied that they do not use any messaging app in their class.
-
+%
 \begin{table}[h!tbp]
@@
 
+% Fran: I think figures with data about the use of messaging apps should come here. Then, we say we also asked about changes after covid and include data about that
+Results in Fig.
+\ref{figure:chatbots_use} do not show significant differences in the use of instant messaging apps between teachers from University and vocational education.
+In general, most teachers prefer messaging apps provided by their own institutions.
+With respect to specific disciplines, Engineering and Technology teachers are more active in their use, although it is also relevant the amount of teachers from Humanities that answered they used these apps in their classes (around 60\% use the apps provided by their institutions).
+
+Although no significant differences were found regarding gender, female teachers answered they use instant messaging apps more than male teachers (about 10\% more).
+Also, teachers in vocational Education use Whatsapp more than university teachers.
+Regarding the distribution of the use of messaging apps per age, there are no significant differences for Whatsapp and apps provided by their own academic institutions.
+% Olia requests support for this.
+However, younger teachers also use Telegram with more than 25\%, a percentage that falls to about 10\% for teachers that are 55 or older.
+%The third column compares the use of these apps considering the number of years of experience.
+One interesting result is that, contrary to the idea of technology adaptation issues when considering older teachers, about 65\% of teachers with more than 25 years of experience use the platforms provided by their institutions while the percentage goes down to less than 50\% for teachers with 6-15 years of experience.
+%
+\begin{figure}[h!tbp]
+\begin{center}
+    \begin{minipage}[t]{0.31\textwidth}
+        \centering
+<<gender_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+survey.pilot[as.character(survey.pilot$Gender)!="No", ] -> df1
+ggplot(df1, aes(x = MessagingPlatformProvided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.31\textwidth}
+        \centering
+<<experience_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
+ggplot(df1, aes(x = MessagingPlatformProvided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.31\textwidth}
+        \centering
+<<sector_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
+    \end{minipage}
+    %----
+    \vspace{0.2mm}
+    \hspace{10mm}
+    \begin{minipage}[t]{0.5\textwidth}
+        \centering
+<<discipline_provided, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
+ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformProvided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/discipline_provided.pdf}
+    \end{minipage}
+    \hspace{10mm}
+    %----
+    %----
+    \vspace{0.5mm}
+    \begin{minipage}[t]{0.31\textwidth}
+        \centering
+<<gender_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+survey.pilot[as.character(survey.pilot$Gender)!="No", ] -> df1
+ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/gender_whatsapp.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.31\textwidth}
+        \centering
+<<experience_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
+ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/experience_whatsapp.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.31\textwidth}
+        \centering
+<<sector_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+ggplot(survey.pilot, aes(x = MessagingPlatformWhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
+    \end{minipage}
+    \vspace{0.2mm}
+    \hspace{10mm}
+    \begin{minipage}[t]{0.5\textwidth}
+        \centering
+<<discipline_whatsapp, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
+ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformWhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
+    \end{minipage}
+    \hspace{10mm}
+    %----
+    %----
+    \vspace{0.5mm}
+    \begin{minipage}[t]{0.31\textwidth}
+        \centering
+<<gender_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+survey.pilot[as.character(survey.pilot$Gender)!="No", ] -> df1
+ggplot(df1, aes(x = MessagingPlatformTelegram, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/gender_telegram.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.31\textwidth}
+        \centering
+<<experience_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
+ggplot(df1, aes(x = MessagingPlatformTelegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/experience_telegram.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.31\textwidth}
+        \centering
+<<sector_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+ggplot(survey.pilot, aes(x = MessagingPlatformTelegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/sector_telegram.pdf}
+    \end{minipage}
+    \vspace{0.2mm}
+    \hspace{10mm}
+    \begin{minipage}[t]{0.5\textwidth}
+        \centering
+<<discipline_telegram, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
+ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformTelegram, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/discipline_telegram.pdf}
+    \end{minipage}
+    \hspace{10mm}
+\end{center}
+    \caption{Use of chatbots in class: distributions per gender, age, years of experience in education, university or vocational education, and discipline.
+Teachers were specifically asked about two popular instant messaging apps (Whatsapp and Telegram), and the use of platforms already provided by their institutions different than these two ones.}
+\label{figure:chatbots_use}
+\end{figure} 
+%
+
+% This is about changes (due to) after covid
+Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' viewpoints towards the use of instant messaging apps int their class.
+The 282
+% Fran, please check Olia's comment as having 282 answers 
+% -> I did remove some responses that Olia considered 'No' by default (i guess). I' ll keep it to 282 to be consistent
+answers are summarized in Fig.
+\ref{figure:chatbots_use_postcovid}, showing that about 77\% of teachers already used these tools before the pandemic and kept using them during the pandemic lockdowns that forced students and educators to use remote education schemes.
+Moreover, approximately 15\% of them switched their messaging app for one that offered a safer interaction with their students.
+According to the responses, an additional 16\% started using messaging apps during the pandemic for the first time in their classes.
+Aggregating the answers, currently 91\% of the teachers are using messaging apps as learning tools.
+%A few relevant facts from the collected data: teachers with 16-25 years of experience seem more worried about the security of messaging apps and teachers with up to 5 years of experience were more open to adopt messaging apps due to the pandemic; female teachers were more willing to adopt new platforms due to the pandemic, and even to start using safer alternatives; finally, university teachers that did not use them were more reluctant to start using them after the pandemic.
+\begin{figure}[h!tbp]
+\begin{center}
+    \begin{minipage}[t]{0.85\textwidth}
+        \centering
+<<gender_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
+survey.pilot.postCOVID <- within(survey.pilot.postCOVID, PostCOVID.changes <- factor(PostCOVID.changes, levels=names(sort(table(PostCOVID.changes), decreasing=TRUE))))
+ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/gender_covid.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.85\textwidth}
+        \centering
+<<sector_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
+ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
+    \end{minipage}
+    \begin{minipage}[t]{0.85\textwidth}
+        \centering
+<<experience_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
+ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/experience_covid.pdf}
+    \end{minipage}
+\end{center}
+    \caption{Impact of COVID in the use of messaging apps in University and vocational education.}
+    % Have different sub-captions so that we can refer to specific subfigures - Olia
+\label{figure:chatbots_use_postcovid}
+\end{figure}
+
 A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
@@
 In effect, this finding indicates that how teachers responded to the use of messaging apps during the pandemic and in particular, whether they changed their habits in the use of apps for teaching purposes, was related to their sector (university vs vocational).
+%
 \begin{table}[h!tbp]
@@
 \end{table}
+
 The majority of the teachers (n=165) mentioned that no changes in their habits occured due to the emergency remote teaching, as the use of messaging apps was part of their teaching practices and remains the same, from which 105 teachers come from the university, and 60 teachers from the vocational sector.
@@
 In fact, from the majority of the teachers who did not change their habits in this respect (n=165), most of them are males (n=114), and come from the technology (n=60) and engineering (n=53) disciplines (see Tables \ref{tab:gender*covid}, \ref{tab:discipline*covid}).
-
+%
 \begin{table}[h!tbp]
@@
 \end{table}
-
+%
 \begin{table}[h!tbp]
@@
 \end{table}
-
-Although gender differences are not significant, female teachers answered they use instant messaging apps more than male teachers (about 10\% more).
-Also, teachers in vocational Education also use Whatsapp more than university teachers.
-With respect to the distribution of the use of messaging apps per age, there are no significant differences for Whatsapp and apps provided by their institutions. % Olia requests support for this.
-However, younger teachers also use Telegram with more than 25\%, a percentage that falls to about 10\% for teachers that are 55 or older.
-The third column compares the use of these apps considering the number of years of experience.
-One interesting result is that, contrary to the idea of technology adaptation issues when considering older teachers, about 65\% of teachers with more than 25 years of experience use the platforms provided by their institutions while the percentage goes down to less than 50\% for teachers with 6-15 years of experience.
-
-\begin{figure}[h!tbp]
-\begin{center}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<gender_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-survey.pilot[as.character(survey.pilot$Gender)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformProvided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<experience_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformProvided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<sector_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
-    \end{minipage}
-    %----
-    \vspace{0.2mm}
-    \hspace{10mm}
-    \begin{minipage}[t]{0.5\textwidth}
-        \centering
-<<discipline_provided, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformProvided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/discipline_provided.pdf}
-    \end{minipage}
-    \hspace{10mm}
-    %----
-    %----
-    \vspace{0.5mm}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<gender_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-survey.pilot[as.character(survey.pilot$Gender)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/gender_whatsapp.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<experience_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/experience_whatsapp.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<sector_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformWhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
-    \end{minipage}
-    \vspace{0.2mm}
-    \hspace{10mm}
-    \begin{minipage}[t]{0.5\textwidth}
-        \centering
-<<discipline_whatsapp, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformWhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
-    \end{minipage}
-    \hspace{10mm}
-    %----
-    %----
-    \vspace{0.5mm}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<gender_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-survey.pilot[as.character(survey.pilot$Gender)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformTelegram, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/gender_telegram.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<experience_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformTelegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/experience_telegram.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<sector_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformTelegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/sector_telegram.pdf}
-    \end{minipage}
-    \vspace{0.2mm}
-    \hspace{10mm}
-    \begin{minipage}[t]{0.5\textwidth}
-        \centering
-<<discipline_telegram, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformTelegram, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/discipline_telegram.pdf}
-    \end{minipage}
-    \hspace{10mm}
-\end{center}
-    \caption{Use of chatbots in class: distributions per gender, age, years of experience in education, university or vocational education, and discipline.
-Teachers were specifically asked about two popular instant messaging apps (Whatsapp and Telegram), and the use of platforms already provided by their institutions different than these two ones.}
-\label{figure:chatbots_use}
-\end{figure}
-
-Results in Fig.
-\ref{figure:chatbots_use} do not show differences in the use of instant messaging apps between teachers from University and vocational education.
-In general, most teachers prefer messaging apps provided by their own institutions.
-With respect to specific disciplines, Engineering and Technology teachers are more active in their use, although it is also relevant the amount of teachers from Humanities that answered they used these apps in their classes (around 60\% use the apps provided by their institutions).
-
+%
 %\begin{figure}[t]
@@
 %\end{figure} 
-
-Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' viewpoints towards the use of instant messaging apps int their class.
-The 282
-% Fran, please check Olia's comment as having 282 answers -> I did remove some responses that Olia considered 'No' by default. I' ll keep it to 282 to be consistent
-answers are summarized in Fig.
-\ref{figure:chatbots_use_postcovid}, showing that about 77\% of teachers already used these tools before the pandemic and kept using them during the pandemic lockdowns that forced students and educators to use remote education schemes.
-Moreover, approximately 15\% of them switched their messaging app for one that offered a safer interaction with their students.
-According to the responses, an additional 16\% started using messaging apps during the pandemic for the first time in their classes.
-Aggregating the answers, currently 91\% of the teachers are using messaging apps as learning tools.
-
-%A few relevant facts from the collected data: teachers with 16-25 years of experience seem more worried about the security of messaging apps and teachers with up to 5 years of experience were more open to adopt messaging apps due to the pandemic; female teachers were more willing to adopt new platforms due to the pandemic, and even to start using safer alternatives; finally, university teachers that did not use them were more reluctant to start using them after the pandemic.
-
-\begin{figure}[h!tbp]
-\begin{center}
-    \begin{minipage}[t]{0.85\textwidth}
-        \centering
-<<gender_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-survey.pilot.postCOVID <- within(survey.pilot.postCOVID, PostCOVID.changes <- factor(PostCOVID.changes, levels=names(sort(table(PostCOVID.changes), decreasing=TRUE))))
-ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/gender_covid.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.85\textwidth}
-        \centering
-<<sector_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
-@
-%       \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.85\textwidth}
-        \centering
-<<experience_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
-@       
-%       \includegraphics[width=\textwidth]{figures/experience_covid.pdf}
-    \end{minipage}
-\end{center}
-    \caption{Impact of COVID in the use of messaging apps in University and vocational education.}
-    % Have different sub-captions so that we can refer to specific subfigures - Olia
-\label{figure:chatbots_use_postcovid}
-\end{figure}
-
+%
 %A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
@@
 In effect, this finding indicates that how teachers responded to the use of messaging apps during the pandemic and in particular, whether they changed their habits in the use of apps for teaching purposes, was related to their sector (university vs vocational).
-The relationships between changes in the use of messaging apps, due to the covid-19 pandemic, and the instructors’ discipline, $X^{2}_{(24, N = 282)} = 44.856$, $p =0.006$, as well as the gender, $X^{2}_{(8, N = 282)} = 16.249$, $p= 0.039$ were also significant.
+%The relationships between changes in the use of messaging apps, due to the covid-19 pandemic, and the instructors’ discipline, $X^{2}_{(24, N = 282)} = 44.856$, $p =0.006$, as well as the gender, $X^{2}_{(8, N = 282)} = 16.249$, $p= 0.039$ were also significant.
 
 % Olia - TODO: check for repetitions in the following paragraph that you added. thank you.
-The first column in Fig.
+Finally, we took a closer look at the chi-square analysis on the post-covid changes and the variables gender, sector, and discipline for which the p-value was less than 0.05.
+In this case, in Fig.
 \ref{figure:postcovid_chisq} shows the Pearson's residuals of the test for these three variables.
@@
 \begin{center}
-    \begin{minipage}[c]{0.45\textwidth}
+    \begin{minipage}[c]{0.40\textwidth}
         \centering
@@
     %round(chisq$stdres, 3)
-    \begin{minipage}[c]{0.45\textwidth}
+    \begin{minipage}[c]{0.55\textwidth}
         \centering
     \resizebox{\textwidth}{!}{%
-    \begin{tabular}{l|r|r|r|r|}
-    \cline{2-5}
-                                 & Did/Do & Didn't/Do & Safer  & Didn' t/Don't \\ \hline
-    \multicolumn{1}{|l|}{Female} & \textbf{-2.850} & \textbf{2.806} & 1.832  & -1.011 \\ 
-    \multicolumn{1}{|l|}{} & 15.15\% & \textbf{31.21\%} &  13.49\% & 4.40\% \\ \hline
-    \multicolumn{1}{|l|}{Male}   & \textbf{2.850} & \textbf{-2.806} & -1.832 & 1.011 \\ 
-    \multicolumn{1}{|l|}{} &  8.43\% &  \textbf{17.36\%} & 7.50\% &  2.45\% \\ \hline
-    \end{tabular}%
+\begin{tabular}{llllll}
+\hline
+ &  & \multicolumn{4}{c}{Gender} \\ \cline{3-6} 
+ &  & \multicolumn{2}{c}{Female} & \multicolumn{2}{c}{Male} \\ \cline{3-6} 
+ &  & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Adjusted \\ Residuals\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Adjusted \\ Residual\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} \\ \cline{2-6}
+\begin{tabular}[c]{@{}l@{}}Post-\\ covid\\ changes\end{tabular} & \begin{tabular}[c]{@{}l@{}}Yes, I use a \\ safer messaging \\ app now\end{tabular} & 1.832 & 13.49\% & -1.832 & 7.50\% \\
+ & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use \\ any messaging \\ app before, but\\ do use it now\end{tabular} & \textbf{2.806} & \textbf{31.21\%} & \textbf{-2.806} & \textbf{17.36\%} \\
+ & \begin{tabular}[c]{@{}l@{}}No, I did use it \\ before and\\ use it now\end{tabular} & \textbf{2.850} & 15.15\% & \textbf{-2.850} & 8.43\% \\
+ & \begin{tabular}[c]{@{}l@{}}No, I didn’t use \\ it before and\\ don’t use it now\end{tabular} & -1.011 & 4.40\% & 1.011 & 2.45\% \\ \hline
+\end{tabular}
+    %\begin{tabular}{l|r|r|r|r|}
+    %\cline{2-5}
+    %                             & Did/Do & Didn't/Do & Safer  & Didn' t/Don't \\ \hline
+    %\multicolumn{1}{|l|}{Female} & \textbf{-2.850} & \textbf{2.806} & 1.832  & -1.011 \\ 
+    %\multicolumn{1}{|l|}{} & 15.15\% & \textbf{31.21\%} &  13.49\% & 4.40\% \\ \hline
+    %\multicolumn{1}{|l|}{Male}   & \textbf{2.850} & \textbf{-2.806} & -1.832 & 1.011 \\ 
+    %\multicolumn{1}{|l|}{} &  8.43\% &  \textbf{17.36\%} & 7.50\% &  2.45\% \\ \hline
+    %\end{tabular}%
     }
     \end{minipage}
-    \begin{minipage}[c]{0.45\textwidth}
+    \begin{minipage}[c]{0.40\textwidth}
         \centering
@@
     \end{minipage}
-    \begin{minipage}[c]{0.45\textwidth}
+    \begin{minipage}[c]{0.55\textwidth}
         \centering
     \resizebox{\textwidth}{!}{%
-    \begin{tabular}{l|r|r|r|r|}
-    \cline{2-5}
-                                 & Did/Do & Didn't/Do & Safer  & Didn' t/Don't \\ \hline
-    \multicolumn{1}{|l|}{University} & \textbf{-2.122} & 0.454 & 0.115  &  \textbf{2.939}\\ 
-    \multicolumn{1}{|l|}{} & 5.71\% & 0.56\% & 0.04\%  &  \textbf{25.26\%}\\ \hline
-    \multicolumn{1}{|l|}{Vocational} & \textbf{2.122} & -0.454 & -0.115 & \textbf{-2.939}\\ 
-    \multicolumn{1}{|l|}{} & 12.38\% & 1.21\% & 0.08\% & \textbf{54.78\%}\\ \hline
+    %\begin{tabular}{l|r|r|r|r|}
+    %\cline{2-5}
+    %                             & Did/Do & Didn't/Do & Safer  & Didn' t/Don't \\ \hline
+    %\multicolumn{1}{|l|}{University} & \textbf{-2.122} & 0.454 & 0.115  &  \textbf{2.939}\\ 
+    %\multicolumn{1}{|l|}{} & 5.71\% & 0.56\% & 0.04\%  &  \textbf{25.26\%}\\ \hline
+    %\multicolumn{1}{|l|}{Vocational} & \textbf{2.122} & -0.454 & -0.115 & \textbf{-2.939}\\ 
+    %\multicolumn{1}{|l|}{} & 12.38\% & 1.21\% & 0.08\% & \textbf{54.78\%}\\ \hline
+    %\end{tabular}%
+    \begin{tabular}{llllll}
+          \hline
+           &  & \multicolumn{4}{c}{Sector} \\ \cline{3-6} 
+           &  & \multicolumn{2}{c}{University} & \multicolumn{2}{c}{Vocational} \\ \cline{3-6} 
+           &  & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Adjusted \\ Residuals\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Adjusted \\ Residual\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} \\ \cline{2-6}
+          \begin{tabular}[c]{@{}l@{}}Post-\\ covid\\ changes\end{tabular} & \begin{tabular}[c]{@{}l@{}}Yes, I use a \\ safer messaging \\ app now\end{tabular} & 0.115 & 0.04\% & -0.115 & 0.08\% \\
+           & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use \\ any messaging \\ app before, but\\ do use it now\end{tabular} & 0.454 & 0.56\% & -0.454 & 1.21\% \\
+           & \begin{tabular}[c]{@{}l@{}}No, I did use it \\ before and\\ use it now\end{tabular} & \textbf{-2.122} & 5.71\% & \textbf{2.122} & 12.38\% \\
+           & \begin{tabular}[c]{@{}l@{}}No, I didn’t use \\ it before and\\ don’t use it now\end{tabular} & \textbf{2.939} & \textbf{25.26\%} & \textbf{-2.939} & \textbf{54.78\%} \\ \hline
           \end{tabular}%
@@
     \end{minipage}
-    \begin{minipage}[c]{0.45\textwidth}
+    \begin{minipage}[c]{0.40\textwidth}
         \centering
@@
     \end{minipage}
-    \begin{minipage}[c]{0.45\textwidth}
+    \begin{minipage}[c]{0.55\textwidth}
         \centering
     \resizebox{\textwidth}{!}{%
-    \begin{tabular}{l|r|r|r|r|}
-    \cline{2-5}
-                                 & Did/Do & Didn't/Do & Safer & Didn' t/Don't \\ \hline
-    \multicolumn{1}{|l|}{Biomed/Sciences} & -1.265 &  0.733 & 1.452 & -0.588 \\ 
-    \multicolumn{1}{|l|}{} & 3.50\% &  2.50\% & 9.94\% & 1.75\% \\ \hline
-    \multicolumn{1}{|l|}{Hum/Social} &  \textbf{-2.729} & \textbf{2.079} &  1.566 & 0.055\\ 
-    \multicolumn{1}{|l|}{} &  15.55\% & \textbf{19.19\%} &  11.04\% & 0.01\%\\ \hline
-    \multicolumn{1}{|l|}{Tech/Engineering} &  \textbf{3.278} &  \textbf{-2.318} &  \textbf{-2.448} & 0.412\\ 
-    \multicolumn{1}{|l|}{} &  11.06\% &  11.76\% &  \textbf{13.29\%} & 0.40\%\\ \hline
-    \end{tabular}%
+\begin{tabular}{llllllll}
+\hline
+ &  & \multicolumn{6}{c}{Discipline} \\ \cline{3-8} 
+ &  & \multicolumn{2}{c}{Biomed/Sciences} & \multicolumn{2}{c}{Hum/Social} & \multicolumn{2}{l}{Tech/Engineering} \\ \cline{3-8} 
+ &  & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Adjusted \\ Residuals\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Adjusted \\ Residual\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} & \begin{tabular}[c]{@{}l@{}}Adjusted \\ Residuals\end{tabular} & \begin{tabular}[c]{@{}l@{}}Contri-\\ bution\end{tabular} \\ \cline{2-8}
+\begin{tabular}[c]{@{}l@{}}Post-\\ covid\\ changes\end{tabular} & \begin{tabular}[c]{@{}l@{}}Yes, I use a \\ safer mes-\\ saging app \\ now\end{tabular} & 1.452 & 9.94\% & 1.566 & 11.04\% & \textbf{-2.448} & \textbf{13.29\%} \\
+ & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t \\ use any mes-\\ saging app \\ before, but\\ do use it now\end{tabular} & 0.733 & 2.50\% & \textbf{2.079} & \textbf{19.19\%} & -2.318 & 11.76\% \\
+ & \begin{tabular}[c]{@{}l@{}}No, I did use \\ it before and\\ use it now\end{tabular} & -1.265 & 3.50\% & \textbf{-2.729} & 15.55\% & \textbf{3.278} & 11.06\% \\
+ & \begin{tabular}[c]{@{}l@{}}No, I didn’t \\ use it before \\ and don’t use \\ it now\end{tabular} & -0.588 & 1.75\% & 0.055 & 0.01\% & 0.412 & 0.40\% \\ \hline
+\end{tabular}
+    %\begin{tabular}{l|r|r|r|r|}
+    %\cline{2-5}
+    %                             & Did/Do & Didn't/Do & Safer & Didn' t/Don't \\ \hline
+    %\multicolumn{1}{|l|}{Biomed/Sciences} & -1.265 &  0.733 & 1.452 & -0.588 \\ 
+    %\multicolumn{1}{|l|}{} & 3.50\% &  2.50\% & 9.94\% & 1.75\% \\ \hline
+    %\multicolumn{1}{|l|}{Hum/Social} &  \textbf{-2.729} & \textbf{2.079} &  1.566 & 0.055\\ 
+    %\multicolumn{1}{|l|}{} &  15.55\% & \textbf{19.19\%} &  11.04\% & 0.01\%\\ \hline
+    %\multicolumn{1}{|l|}{Tech/Engineering} &  \textbf{3.278} &  \textbf{-2.318} &  \textbf{-2.448} & 0.412\\ 
+    %\multicolumn{1}{|l|}{} &  11.06\% &  11.76\% &  \textbf{13.29\%} & 0.40\%\\ \hline
+    %\end{tabular}%
     }

### 2021-07-17 edubots_surveys.Rnw
finishes RQ1 and postcovid results

@@
 % Olia - TODO: check for repetitions in the following paragraph that you added. thank you.
-Finally, we took a closer look at the chi-square analysis on the post-covid changes and the variables gender, sector, and discipline for which the p-value was less than 0.05.
-In this case, in Fig.
-\ref{figure:postcovid_chisq} shows the Pearson's residuals of the test for these three variables.
-Residuals show the difference between the observed and the expected values, with large residuals showing that variables are not truly independent.
-In this case, blue shows positive contribution and red negative contribution to the test, and saturation shows how large is this contribution in contrast to the expected value by chance.
-Tables on the right side show adjusted standardized residuals that according to \cite{agresti2013categorical}, if greater than +/-2 for cases with few cells, indicate lack of fit of $H_0$ (in boldface in our table).
-Also, the table shows the percentage of contribution to the test of each cell.
-
+Finally, we took a closer look at the post-covid changes and the variables gender, sector, and discipline for which the chi-square test is statistically significant as shown in Figures \ref{figure:gender*postcovid_chisq}, \ref{figure:sector*postcovid_chisq}, \ref{figure:discipline*postcovid_chisq} respectively.
+Each figure shows on the left, a graph that represents the Pearson's residuals of the chi-square test results and a table on the right part that shows the contribution of each cell to the test.
+In the Pearson's residual graphs, the responses were shortened for the sake of clarity according to: 1) \textit{Did/do} stands for \textit{Yes, I did use it before and do use it now}; 2) \textit{Didn't/do} for \textit{Yes, I didn’t use any messaging app before, but do use it now}; 3) \textit{safer} for \textit{Yes, I use a safer messaging app now}; 4) \textit{Didn't/Don't} for \textit{No, I didn’t use it before and don’t use it now}.
+%
 \begin{figure}[h!tbp]
@@
 colnames(covidChanges.vs.Gender)<- c("Did/do", "Didn't/do","safer", "Didn't/don't")
+covidChanges.vs.Gender<-covidChanges.vs.Gender[,c(3,2,1,4)]
 chisq<-chisq.test(covidChanges.vs.Gender)
@@
  &  & \multicolumn{2}{c}{Female} & \multicolumn{2}{c}{Male} \\ \cline{3-6} 
- &  & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Adjusted \\ Residuals\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Adjusted \\ Residual\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} \\ \cline{2-6}
+ &  & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Stand.
+\\ Residuals\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Stand.
+\\ Residual\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} \\ \cline{2-6}
 \begin{tabular}[c]{@{}l@{}}Post-\\ covid\\ changes\end{tabular} & \begin{tabular}[c]{@{}l@{}}Yes, I use a \\ safer messaging \\ app now\end{tabular} & 1.832 & 13.49\% & -1.832 & 7.50\% \\
@@
     \end{minipage}
+\end{center}
+    \caption{Analysis for gender and post-covid changes: left) Pearson's residuals for the Chi-square test; right) Gender*post-covid changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized residuals) and contribution percentage to the total Chi-square test of each cell.}
+\label{figure:gender*postcovid_chisq}
+\end{figure}
+
+As mentioned, the graphs on the left represent the Pearson's residuals, showing the difference between the observed and the expected values for each cell.
+Thus, large residuals indicate that variables are not truly independent.
+In our case, the blue shows positive contributions and red negative contributions to the test.
+Moreover, the saturation shows how large the contribution is in contrast to the expected value by chance.
+Additionally, tables on the right side show adjusted standardized residuals that according to \cite{agresti2013categorical}, if greater than +/-2 for cases with few cells, indicate lack of fit of $H_0$ (in boldface in our table).
+Complementary, the table also shows the percentage of contribution to the test of each cell (highest percentage per column also in boldface).
+
+Regarding gender in Fig.
+\ref{figure:gender*postcovid_chisq}, the results show a high positive contribution from female educators that did not use a messaging app before the COVID-19 pandemic but do use it now; approximately 31\% of the test results are explained by this cell.
+In contrast, male educators that respond the same were less than expected (negative contribution that explains 17\% of the test results).
+Also, it is important to highlight the female educators that kept using these apps before and after the pandemic and correspondingly the negative contribution of male educators to the same case (less than expected by chance).
+
+\begin{figure}[h!tbp]
+\begin{center}
     \begin{minipage}[c]{0.40\textwidth}
@@
 colnames(covidChanges.vs.Sector)<- c("Did/do", "Didn't/do","safer", "Didn't/don't")
+covidChanges.vs.Sector<-covidChanges.vs.Sector[,c(3,2,1,4)]
 chisq<-chisq.test(covidChanges.vs.Sector)
@@
            &  & \multicolumn{2}{c}{University} & \multicolumn{2}{c}{Vocational} \\ \cline{3-6} 
-           &  & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Adjusted \\ Residuals\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Adjusted \\ Residual\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} \\ \cline{2-6}
+           &  & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Stand.
+\\ Residuals\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Stand.
+\\ Residual\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} \\ \cline{2-6}
           \begin{tabular}[c]{@{}l@{}}Post-\\ covid\\ changes\end{tabular} & \begin{tabular}[c]{@{}l@{}}Yes, I use a \\ safer messaging \\ app now\end{tabular} & 0.115 & 0.04\% & -0.115 & 0.08\% \\
@@
     \end{minipage}
+\end{center}
+    \caption{Analysis for sector and post-covid changes: left) Pearson's residuals for the Chi-square test; right) Sector*post-covid changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized  residuals) and contribution percentage to the total Chi-square test of each cell.}
+\label{figure:sector*postcovid_chisq}
+\end{figure}
+%
+With respect to the sector, the results in Fig.
+\ref{figure:sector*postcovid_chisq} show a positive contribution from university educators being reluctant to use any messaging apps before or after the pandemic: the positive contribution of their responses explain 25\% of the test results with an adjusted residual of 2.94.
+On the contrary, vocational teachers were more open to it, showing a negative Pearson's residual.
+Also, we find larger values than expected in vocational teachers that kept using these apps after the pandemic.
+
+\begin{figure}[h!tbp]
+\begin{center}
     \begin{minipage}[c]{0.40\textwidth}
@@
 colnames(covidChanges.vs.Discipline)<- c("Did/do", "Didn't/do","safer", "Didn't/don't")
+covidChanges.vs.Discipline<-covidChanges.vs.Discipline[,c(3,2,1,4)]
 chisq<-chisq.test(covidChanges.vs.Discipline)
@@
  &  & \multicolumn{2}{c}{Biomed/Sciences} & \multicolumn{2}{c}{Hum/Social} & \multicolumn{2}{l}{Tech/Engineering} \\ \cline{3-8} 
- &  & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Adjusted \\ Residuals\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Adjusted \\ Residual\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} & \begin{tabular}[c]{@{}l@{}}Adjusted \\ Residuals\end{tabular} & \begin{tabular}[c]{@{}l@{}}Contri-\\ bution\end{tabular} \\ \cline{2-8}
-\begin{tabular}[c]{@{}l@{}}Post-\\ covid\\ changes\end{tabular} & \begin{tabular}[c]{@{}l@{}}Yes, I use a \\ safer mes-\\ saging app \\ now\end{tabular} & 1.452 & 9.94\% & 1.566 & 11.04\% & \textbf{-2.448} & \textbf{13.29\%} \\
+ &  & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Stand.
+\\ Residuals\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Stand.
+\\ Residual\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} & \begin{tabular}[c]{@{}l@{}}Stand.
+\\ Residuals\end{tabular} & \begin{tabular}[c]{@{}l@{}}Contri-\\ bution\end{tabular} \\ \cline{2-8}
+\begin{tabular}[c]{@{}l@{}}Post-\\ covid\\ changes\end{tabular} & \begin{tabular}[c]{@{}l@{}}Yes, I use a \\ safer mes-\\ saging app \\ now\end{tabular} & 1.452 & \textbf{9.94\%} & 1.566 & 11.04\% & \textbf{-2.448} & \textbf{13.29\%} \\
  & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t \\ use any mes-\\ saging app \\ before, but\\ do use it now\end{tabular} & 0.733 & 2.50\% & \textbf{2.079} & \textbf{19.19\%} & -2.318 & 11.76\% \\
@@
 \end{center}
-    \caption{.}
-\label{figure:postcovid_chisq}
+    \caption{Analysis for discipline and post-covid changes: left) Pearson's residuals for the Chi-square test; right) Discipline*post-covid changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized residuals) and contribution percentage to the total Chi-square test of each cell.}
+\label{figure:discipline*postcovid_chisq}
 \end{figure} 
+%
+Finally, statistical significance was found for the discipline and post-covid changes.
+Regarding disciplines (see Fig.
+\ref{figure:discipline*postcovid_chisq}), the number of educators from Humanities and Social Sciences that started using messaging apps after the pandemic is larger than expected and these number of responses explains about 19\% of the chi-square test results.
+Also, the number of educators from Technology or Engineering that started using safer alternatives are less than expected (compared to the educators from other disciplines).
+Bear in mind that some disciplines were merged to avoid very low number of responses for some of the cells.
 

### 2021-07-17 scripts/process.R

@@ -103,9 +103,11 @@ df1[as.character(df1$Sector)!="No", ] -> df1
 df2<- droplevels(df1)
 
 
-covidChanges.vs.Gender<-table(df2$Gender, df2$PostCOVID.changes)
+covidChanges.vs.Gender<-table(df2$Gender,df2$PostCOVID.changes)
 colnames(covidChanges.vs.Gender)<- c("Did/do", "Didn't/do","safer", "Didn't/don't")
-chisq<-chisq.test(covidChanges.vs.Gender)
+covidChanges.vs.Gender<-covidChanges.vs.Gender[,c(3,2,1,4)]
+chisq<-chisq.test(t(covidChanges.vs.Gender))
+
 
 #install.packages("corrplot")
 #http://www.sthda.com/english/wiki/chi-square-test-of-independence-in-r

### 2021-07-18 edubots_surveys.Rnw
Revises and add intro to next section in methdology.
This closes #20 finally. Some revisions are still possible.

@@
 The survey items focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider useful to be used in their teaching, and the type of interactions that teachers prefer to have with their students while using messaging apps in their teaching.
-% Questions should probably be included here.
-
-% Olia - I do not think that we should say here that the first survey was done in two different forms.
-Wasn't the same survey for university and vocational teachers?
-It is just that they had to specify in which sector of education they were teaching, right?
-The second survey is another story...
-this is what I understand.
-
-The initial survey was done in two separate Google forms, one for university and other for tertiary non-university teachers (vocational education).
+
+The {\bf initial survey} was done in two separate Google forms, one for university and other for tertiary non-university teachers (vocational education).
 Questions and responses were the same, except for the type of tertiary degrees that were taught.
@@
 % Including questions in surveys
-The first survey about the use of messaging apps in class include the following questions:
+The {\bf first survey}, which focused about the use of messaging apps in class, and which tried to address mainly RQ2 and R23, includes the following questions:
 
@@
 
-The second survey followed the same paths, only in this case there was a single questionnaire, and with a different scope, focusing on the kind of interaction media features that teachers value the most.
+The {\bf second survey} followed the same paths, only in this case there was a single questionnaire, and with a different scope, focusing on the kind of interaction media features that teachers value the most.
 % Olia - see my comment above.
@@
 We think, however that there's no explicit bias in this selection, although of course specific percentages will vary.
-% Olia - we shoudl say here a few words about the two surveys, and their main difference. Also, which RQs each survey addresses etc. 
-% JJ - Yep...
-
-% Antonio - I include here the description of interaction features. Not sure if it is the best place for it. Move wherever it better fits.
-% Olia- in the text below, we refer to "communucation tools", we should be consisten with the terms we use. Should we refere to communication tools? Messaging apps? Chat tools? 
-Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what  their feelings and preferences are with regard to the use of communication tools with students, and even using bots or chatbots in the classroom.
-In addition the survey asked about the most relevant \textit{Interaction media features} for the teachers with respect to the potential tool to use in class.
+These questions tried to address mainly RQ1 and RQ4.
+
+Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what  their feelings and preferences are with regard to the use of instant messaging applications with students, and even using bots or chatbots in the classroom.
+In addition the survey asked about the most relevant \textit{interaction media features} for the teachers with respect to the potential tool to use in class.
 
@@
 \begin{itemize}
-\item Synchronous: students and teacher/s in the same space, simultaneously
-\item Asynchronous: the student asks at anytime, the teacher responds whenever possible
+\item Synchronous: students and teacher/s in the same space, simultaneously.
+\item Asynchronous: the student asks at anytime, the teacher responds whenever possible.
 \end{itemize}
@@
 
-%These features are:
-%\begin{itemize}
-%\item \textit{Analytics}: the tool allows to extract data about students performance or development during the academic course on the teacher's subject.
-%\item \textit{Connectivity}: it is possible to link or connect the tool with other applications.
-%\item \textit{Familiarity}: it is something already known or previously used, so no need to learn something new.
-%\item \textit{Hidden Phone}: it is possible to use the tool without showing my phone number, normally using an alias or an own account independent from my physical telephone.
-%\item \textit{Horizontally}: all the actors are at the same level (for instance, teacher and students). There is not a hierarchy.
-%\item \textit{Official formation}: the university offers some training courses or talks about the tool (mainly for teachers). 
-%\item \textit{Pluggability}: the tool offers different pluggins to the teacher, so he/she can deploy his/her own implemented modules.
-%\item \textit{Sustainability}: teacher should not be worried about the tool maintenance.
-%\item \textit{Unidirectionality}: only the teacher can publish information in the channel, i.e. students are not allowed to ask or answer.
-%\item \textit{Officiality}: the tool has been granted by the university where the teacher works. This means normally that there is also technical support by university's staff.
-%\item \textit{Synchronous communication}: the interactions between teacher and students take place in real time, i.e. it is not a delayed communication scheme such as e-mail.
-%\end{itemize}
+Responses were stored automatically in a Google Drive spreadsheet.
+Eventually, the results from the two forms we used for the first survey were collated in a single spreadsheet.
+Next we will show the results and analyze them.
 

### 2021-07-18 edubots_surveys.Rnw
adds subcaptions and splits up figures refs #47

--- 2021-07-17 edubots_surveys.Rnw
@@
 \usepackage{rotating}
-
 \usepackage[utf8]{inputenc} %unicode support
@@
  in the classroom and tend to contact their teachers later via email.
- Consequently, this can lead to not only a delay in obtaining answers to their questions butcan also cause a significant increase in their teachers’ workload, especially when factoring in the disproportion between the class size and the number of teachers.
+ Consequently, this can lead to not only a delay in obtaining answers to their questions but can also cause a significant increase in their teachers’ workload, especially when factoring in the disproportion between the class size and the number of teachers.
 Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning experience \cite{Griol2014,kim2020}.
@@
 % Describe the survey and population
-We collected responses from 282 teachers from Spain and Spanish Speaking countries for the first survey (\textit{survey1} in Fig.
-\ref{figure:teachers_population}) and 205 for the second one (\textit{survey2}).
+We collected responses from 282 teachers from Spain and Spanish Speaking countries for the first survey (\textit{survey1} %in Fig. \ref{figure:teachers_population}
+) and 205 for the second one (\textit{survey2}).
 The sample includes mostly teachers from university, although about 32\% and 8\% are from vocational education in the first and second survey respectively.
@@
 % Fran: I think figures with data about the use of messaging apps should come here. Then, we say we also asked about changes after covid and include data about that
-Results in Fig.
-\ref{figure:chatbots_use} do not show significant differences in the use of instant messaging apps between teachers from University and vocational education.
-In general, most teachers prefer messaging apps provided by their own institutions.
+Results in Figs.
+\ref{figure:provided*chatbots_use}, \ref{figure:whatsapp*chatbots_use}, \ref{figure:telegram*chatbots_use} do not show significant differences in the use of instant messaging apps between teachers from University and vocational education.
+In general, most teachers prefer messaging apps provided by their own institutions (we also show the results for the two most popular messaging app platforms: Whatsapp and Telegram).
 With respect to specific disciplines, Engineering and Technology teachers are more active in their use, although it is also relevant the amount of teachers from Humanities that answered they used these apps in their classes (around 60\% use the apps provided by their institutions).
@@
 \begin{center}
-    \begin{minipage}[t]{0.31\textwidth}
+    \begin{minipage}[t]{0.35\textwidth}
     \centering
@@
 survey.pilot[as.character(survey.pilot$Gender)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformProvided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
+df1[as.character(df1$Gender)!="PNTS", ] -> df1
+ggplot(df1, aes(x = MessagingPlatformProvided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male')))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+#+ facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
 @
@@
     \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
+    \begin{minipage}[t]{0.35\textwidth}
     \centering
@@
 survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformProvided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
+ggplot(df1, aes(x = MessagingPlatformProvided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @       
@@
     \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<sector_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+    \begin{minipage}[t]{0.3\textwidth}
+        \centering
+<<sector_provided, echo=FALSE, fig.width=10/2.54, fig.height=8.25/2.54>>=
+ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())+ theme(axis.title.x=element_blank())
 @       
@@
     \end{minipage}
-    %----
-    \vspace{0.2mm}
-    \hspace{10mm}
-    \begin{minipage}[t]{0.5\textwidth}
+    %
+    \begin{minipage}[t]{0.6\textwidth}
         \centering
 <<discipline_provided, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformProvided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
+survey.pilot.Discipline[as.character(survey.pilot.Discipline$Discipline)!="Other", ] -> survey.pilot.Discipline
+ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformProvided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + #facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
+facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering")))+ theme(axis.title.y=element_blank())+ theme(axis.title.x=element_blank())
 @
@@
     \end{minipage}
-    \hspace{10mm}
-    %----
-    %----
-    \vspace{0.5mm}
-    \begin{minipage}[t]{0.31\textwidth}
+\end{center}
+    \caption{Use of chatbots provided by the teachers' academic institutions in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}
+    \label{figure:provided*chatbots_use}
+\end{figure}
+%
+\begin{figure}[h!tbp]
+\begin{center}
+    \begin{minipage}[t]{0.35\textwidth}
     \centering
@@
 survey.pilot[as.character(survey.pilot$Gender)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
+df1[as.character(df1$Gender)!="PNTS", ] -> df1
+ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male')))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @
@@
 survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
+ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @       
@@
     \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<sector_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformWhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+    \begin{minipage}[t]{0.3\textwidth}
+    \centering
+<<sector_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=8.25/2.54>>=
+ggplot(survey.pilot, aes(x = MessagingPlatformWhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @       
@@
     \end{minipage}
-    \vspace{0.2mm}
-    \hspace{10mm}
-    \begin{minipage}[t]{0.5\textwidth}
+    \begin{minipage}[t]{0.6\textwidth}
     \centering
 <<discipline_whatsapp, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformWhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformWhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @
@@
     \end{minipage}
-    \hspace{10mm}
-    %----
-    %----
-    \vspace{0.5mm}
-    \begin{minipage}[t]{0.31\textwidth}
+\end{center}
+    \caption{Use of Whatsapp in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}
+    \label{figure:whatsapp*chatbots_use}
+\end{figure}
+%
+\begin{figure}[h!tbp]
+\begin{center}
+    \begin{minipage}[t]{0.35\textwidth}
     \centering
@@
 survey.pilot[as.character(survey.pilot$Gender)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformTelegram, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
+df1[as.character(df1$Gender)!="PNTS", ] -> df1
+ggplot(df1, aes(x = MessagingPlatformTelegram, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male')))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @
@@
 survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformTelegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
+ggplot(df1, aes(x = MessagingPlatformTelegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @       
@@
     \end{minipage}
-    \begin{minipage}[t]{0.31\textwidth}
-        \centering
-<<sector_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformTelegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
+    \begin{minipage}[t]{0.3\textwidth}
+    \centering
+<<sector_telegram, echo=FALSE, fig.width=10/2.54, fig.height=8.25/2.54>>=
+ggplot(survey.pilot, aes(x = MessagingPlatformTelegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @       
@@
     \end{minipage}
-    \vspace{0.2mm}
-    \hspace{10mm}
-    \begin{minipage}[t]{0.5\textwidth}
+    \begin{minipage}[t]{0.6\textwidth}
     \centering
 <<discipline_telegram, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformTelegram, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformTelegram, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @
@@
     \end{minipage}
-    \hspace{10mm}
 \end{center}
-    \caption{Use of chatbots in class: distributions per gender, age, years of experience in education, university or vocational education, and discipline.
-Teachers were specifically asked about two popular instant messaging apps (Whatsapp and Telegram), and the use of platforms already provided by their institutions different than these two ones.}
-\label{figure:chatbots_use}
+    \caption{Use of Telegram in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}
+    \label{figure:telegram*chatbots_use}
 \end{figure}
-%
 
 % This is about changes (due to) after covid
-Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' viewpoints towards the use of instant messaging apps int their class.
-The 282
+A question in the survey was also focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' viewpoints towards the use of instant messaging apps int their class. The 282 
 % Fran, please check Olia's comment as having 282 answers 
 % -> I did remove some responses that Olia considered 'No' by default (i guess). I' ll keep it to 282 to be consistent
-answers are summarized in Fig.
-\ref{figure:chatbots_use_postcovid}, showing that about 77\% of teachers already used these tools before the pandemic and kept using them during the pandemic lockdowns that forced students and educators to use remote education schemes.
+answers are summarized in Figs.
+\ref{figure:gender*chatbots_use_postcovid}, \ref{figure:sector*chatbots_use_postcovid}, \ref{figure:years*chatbots_use_postcovid}, \ref{figure:disc*chatbots_use_postcovid}, showing that about 77\% of teachers already used these tools before the pandemic and kept using them during the pandemic lockdowns that forced students and educators to use remote education schemes.
 Moreover, approximately 15\% of them switched their messaging app for one that offered a safer interaction with their students.
@@
 \begin{center}
-    \begin{minipage}[t]{0.85\textwidth}
+    \begin{minipage}[t]{0.80\textwidth}
         \centering
@@
 survey.pilot.postCOVID <- within(survey.pilot.postCOVID, PostCOVID.changes <- factor(PostCOVID.changes, levels=names(sort(table(PostCOVID.changes), decreasing=TRUE))))
-ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90), size=7) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
 @
 %       \includegraphics[width=\textwidth]{figures/gender_covid.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.85\textwidth}
+        \vspace{-1cm}
+        \caption{Total count of responses for the use of messaging apps after the COVID-19 pandemic grouped by gender (PNTS stands for Prefer Not To Say).}
+        \label{figure:gender*chatbots_use_postcovid}
+    \end{minipage}
+    \begin{minipage}[t]{0.80\textwidth}
         \centering
@@
 %       \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
-    \end{minipage}
-    \begin{minipage}[t]{0.85\textwidth}
+        \vspace{-1cm}
+        \caption{Total count of responses for the use of messaging apps after the COVID-19 pandemic grouped by sector.}
+        \label{figure:sector*chatbots_use_postcovid}
+    \end{minipage}
+    \begin{minipage}[t]{0.80\textwidth}
         \centering
@@
 %       \includegraphics[width=\textwidth]{figures/experience_covid.pdf}
+        \vspace{-1cm}
+        \caption{Total count of responses for the use of messaging apps after the COVID-19 pandemic grouped by years of experience in teaching.}
+        \label{figure:years*chatbots_use_postcovid}
+    \end{minipage}
+        \begin{minipage}[t]{0.80\textwidth}
+        \centering
+<<discipline_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
+survey.pilot.postCOVID %>%
+  mutate(Discipline = ifelse(as.character(Discipline) == "Engineering", "Tech/Engineering", as.character(Discipline))) %>% 
+  mutate(Discipline = ifelse(as.character(Discipline) == "Technology", "Tech/Engineering", as.character(Discipline)))->survey.pilot.postCOVID
+survey.pilot.postCOVID[as.character(survey.pilot.postCOVID$Discipline)!="No", ] -> survey.pilot.postCOVID
+ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Discipline, fill = Discipline ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+@
+%       \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
+        \vspace{-1cm}
+        \caption{Total count of responses for the use of messaging apps after the COVID-19 pandemic grouped by discipline.}
+        \label{figure:disc*chatbots_use_postcovid}
     \end{minipage}
 \end{center}
-    \caption{Impact of COVID in the use of messaging apps in University and vocational education.}
     % Have different sub-captions so that we can refer to specific subfigures - Olia
-\label{figure:chatbots_use_postcovid}
 \end{figure}
@@
 \begin{center}
-    \begin{minipage}[c]{0.40\textwidth}
+    \begin{minipage}[c]{0.45\textwidth}
         \centering
@@
     %round(chisq$stdres, 3)
-    \begin{minipage}[c]{0.55\textwidth}
+    \begin{minipage}[c]{0.50\textwidth}
         \centering
@@
     \end{minipage}
-    \begin{minipage}[c]{0.55\textwidth}
+    \begin{minipage}[c]{0.50\textwidth}
         \centering
@@
 
-Answer to these questions are plotted in Figure \ref{figure:chatbots_types} grouped by gender, sector and experience.
+Answers to these questions are plotted in Figs.
+\ref{figure:gender*chatbots_types}, \ref{figure:sector*chatbots_types}, \ref{figure:experience*chatbots_types}, \ref{figure:disc*chatbots_types} grouped by gender, sector, years of experience in education, and discipline respectively.
 As it was a multiple choice question, the counts are over the total number of people that answered.
@@
 survey.pilot.ChatbotType <- within(survey.pilot.ChatbotType, ChatbotType <- factor(ChatbotType, levels=names(sort(table(ChatbotType), decreasing=TRUE))))
+survey.pilot.ChatbotType[as.character(survey.pilot.ChatbotType$ChatbotType)!="OtherBot", ] -> survey.pilot.ChatbotType
+#survey.pilot.ChatbotType[as.character(survey.pilot.ChatbotType$Gender)!="PNTS", ] -> survey.pilot.ChatbotType
 ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
@@
 %       \includegraphics[width=\textwidth]{figures/gender_chatbottype.pdf}
+        \vspace{-1cm}
+        \caption{Count of types of chatbots for class perceived as the most useful for teachers grouped by gender (PNTS stands for Prefer Not To Say).}
+        \label{figure:gender*chatbots_types}
     \end{minipage}
@@
 %       \includegraphics[width=\textwidth]{figures/sector_chatbottype.pdf}
+        \vspace{-1cm}
+        \caption{Count of types of chatbots for class perceived as the most useful for teachers grouped by sector.}
+        \label{figure:sector*chatbots_types}
     \end{minipage}
@@
 %       \includegraphics[width=\textwidth]{figures/experience_chatbottype.pdf}
+        \vspace{-1cm}
+        \caption{Count of types of chatbots for class perceived as the most useful for teachers grouped by experience.}
+        \label{figure:experience*chatbots_types}
+    \end{minipage}
+    \begin{minipage}[t]{0.85\textwidth}
+        \centering
+<<discipline_chatbottype, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
+survey.pilot.ChatbotType %>%
+  mutate(Discipline = ifelse(as.character(Discipline) == "Engineering", "Tech/Engineering", as.character(Discipline))) %>% 
+  mutate(Discipline = ifelse(as.character(Discipline) == "Technology", "Tech/Engineering", as.character(Discipline)))->survey.pilot.ChatbotType
+survey.pilot.ChatbotType[as.character(survey.pilot.ChatbotType$Discipline)!="No", ] -> survey.pilot.ChatbotType
+ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Discipline, fill = Discipline ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+@       
+%       \includegraphics[width=\textwidth]{figures/experience_chatbottype.pdf}
+        \vspace{-1cm}
+        \caption{Count of types of chatbots for class perceived as the most useful for teachers grouped by discipline.}
+        \label{figure:disc*chatbots_types}
     \end{minipage}
 \end{center}
-    \caption{Types of chatbots.}
-\label{figure:chatbots_types}
+%    \caption{Counts of chatbots to be used in class perceived as the most useful for teachers.}
+%\label{figure:chatbots_types}
 \end{figure}
@@
 <<gender_synch, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
+survey.interaction[as.character(survey.interaction$Gender)!="PNTS", ] -> survey.interaction
 ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@@
     \end{minipage}
+%    \begin{minipage}[t]{0.3\textwidth}
+%        \centering
+%<<sector_synch, echo=FALSE, fig.width=10/2.54, fig.height=8.25/2.54>>=
+%ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+%@
+%       \includegraphics[width=\textwidth]{figures/sector_synch.pdf}
+%    \end{minipage}
     \begin{minipage}[t]{0.6\textwidth}
@@
 <<discipline_synch, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering","No"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
 @
@@
 \end{center}
-    \caption{Synchronous or asynchronous interaction.}
+    \caption{Results of teachers' communication preferences: synchronous or asynchronous interaction with students (grouped by gender, years of experience, and discipline).}
 \label{figure:chatbots_synch}
@@
 A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
-The majority of the teachers were aged 45-55 years old (70; 34.1\%), followed by individuals aged 35-45 (67, 32.7\%), and 25-35 (42; 20.5\%), while the minority was aged >55 years old (26; 12.7\%).
+The majority of the teachers were aged 45-55 years old (70; 34.1\%), followed by individuals aged 35-45 (67, 32.7\%), and 25-35 (42; 20.5\%), while the minority was aged $>$~55 years old (26; 12.7\%).
 In terms of teaching experience, 59 teachers (28.8\%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9\%), 0-5 years (51; 24.9\%) and more than 25 years of experience (44; 21.5\%).

### 2021-07-18 scripts/process.R

@@ -86,7 +86,7 @@ chisq.test(App.vs.Discipline)$p.value
 
 data %>% group_by( PostCOVID.changes ) %>% filter( n() > 1 ) -> data.postCOVID
 data.postCOVID <- within(data.postCOVID, PostCOVID.changes <- factor(PostCOVID.changes, levels=names(sort(table(PostCOVID.changes), decreasing=TRUE))))
-ggplot(data.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+ggplot(data.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90, size = rel(10))) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
 #ggsave('../figures/sector_covid.pdf', width = 190, height = 50, units = "mm")
 ggplot(data.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
 #ggsave('../figures/gender_covid.pdf', width = 190, height = 50, units = "mm")

### 2021-07-18 edubots_surveys.Rnw
Revised RQ1, possibly closes #13

--- 2021-07-18 edubots_surveys.Rnw
@@
 % Describe the survey and population
-We collected responses from 282 teachers from Spain and Spanish Speaking countries for the first survey (\textit{survey1} in Fig.
-\ref{figure:teachers_population}) and 205 for the second one (\textit{survey2}).
+We collected responses from 282 teachers from Spain and Spanish Speaking countries for the first survey (\textit{survey1} and 205 for the second one (\textit{survey2}).
+The two forms were open for approximately the same amount of time, around two months.
 The sample includes mostly teachers from university, although about 32\% and 8\% are from vocational education in the first and second survey respectively.
-Regarding gender, 61\% of the teachers were male and 32\% female (approximately 5\% chose not to disclose it).
-Finally, the responses are equally distributed according to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 26\% for 6-15 years of experience, 30\% for 16-25, and 20\% for teachers with more than 25 years of experience.
+Regarding gender, 61\% of the teachers were male and 32\% female, while approximately 5\% chose not to disclose it.
+Finally, the responses are more or less equally distributed according to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 26\% for 6-15 years of experience, 30\% for 16-25, and 20\% for teachers with more than 25 years of experience.
 
@@
 
+Well try to find the answers to the four research questions next, by analyzing the response to the different survey questions.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RQ1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %Why messaging apps are relevant here --> connect to the development of chatbots
-Group messaging apps have become a powerful tool for keeping touch with students. Also, they are the baseline platform for the development of chatbots to help with the learning process.
-
-For answering RQ1, teachers were queried about whether they use messaging apps in their classes, specifically, Telegram, WhatsApp, Slack, or any other messaging app, and whether they use messaging apps provided by their academic institution (see Table \ref{tab:use_messapps}).
+Group messaging apps have become a powerful tool for keeping touch with students.
+Also, they are the baseline platform for the development of chatbots to help with the learning process.
+After an initial analysis to the answers to the first survey, we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally piggybacks on another, messaging applications.
+In a technology adoption model, perceived ease of use and perceived usefulness are essential.
+But it is going to be very difficult for teachers to find {\em chatbots} easy to use if they, previously, do not consider, or simply use, the messaging tools to which they are attached.
+
+This is why for answering RQ1, teachers were queried about whether they use messaging apps in their classes, specifically, Telegram, WhatsApp, Slack (an application used mainly in IT departments and software development), or any other messaging app, and whether they use messaging apps provided by their academic institution (see Table \ref{tab:use_messapps}).
+In this case, it is maybe in order a certain clarification.
+While we had in mind, as indicated by the possible answers, instant messaging applications when making this question, we included these institution-provided applications mainly for completitude.
+But it should be noted that, in most cases, they are not {\em instant} messaging apps in the way Telegram or Facebook Messenger are; in most cases they are messaging facilities provided by learning management systems such as (usually) Moodle.
+So the answer to this question must be understood in two different ways: their preference for the {\em source} of the technology (university, any company) as well as the {\em type} of technology (instant, app based messaging systems vs.
+web-based systems integrated in another learning management system).
+
 Overall, the majority of the teachers responded that they do use messaging apps in their classrooms, from which apps provided by the academic institution (n=159, 56\%) and WhatsApp (n=124, 44.0\%) were the most common responses.
 Only 19 teachers (6.7\%) replied that they do not use any messaging app in their class.
+%Remember to add something to the discussion below - JJ
 %
@@
 Although no significant differences were found regarding gender, female teachers answered they use instant messaging apps more than male teachers (about 10\% more).
-Also, teachers in vocational Education use Whatsapp more than university teachers.
-Regarding the distribution of the use of messaging apps per age, there are no significant differences for Whatsapp and apps provided by their own academic institutions.
+Also, teachers in vocational Education use WhatsApp more than university teachers.
+Regarding the distribution of the use of messaging apps per age, there are no significant differences for WhatsApp and apps provided by their own academic institutions.
 % Olia requests support for this.
@@
 Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' viewpoints towards the use of instant messaging apps int their class.
+Our main intention in this case was to assess whether a crisis will bring about some kind of change in the use of tools.
 The 282 
@@
 
-As mentioned, the graphs on the left represent the Pearson's residuals, showing the difference between the observed and the expected values for each cell.
+As mentioned, the graphs on the left hand side represent the Pearson's residuals, showing the difference between the observed and the expected values for each cell.
 Thus, large residuals indicate that variables are not truly independent.

### 2021-07-18 edubots_surveys.Rnw

--- 2021-07-18 edubots_surveys.Rnw
@@
 % Describe the survey and population
-We collected responses from 282 teachers from Spain and Spanish Speaking countries for the first survey (\textit{survey1} %in Fig. \ref{figure:teachers_population}
-) and 205 for the second one (\textit{survey2}).
+We collected responses from 282 teachers from Spain and Spanish Speaking countries for the first survey (\textit{survey1} and 205 for the second one (\textit{survey2}).
+The two forms were open for approximately the same amount of time, around two months.
 The sample includes mostly teachers from university, although about 32\% and 8\% are from vocational education in the first and second survey respectively.
-Regarding gender, 61\% of the teachers were male and 32\% female (approximately 5\% chose not to disclose it).
-Finally, the responses are equally distributed according to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 26\% for 6-15 years of experience, 30\% for 16-25, and 20\% for teachers with more than 25 years of experience.
+Regarding gender, 61\% of the teachers were male and 32\% female, while approximately 5\% chose not to disclose it.
+Finally, the responses are more or less equally distributed according to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 26\% for 6-15 years of experience, 30\% for 16-25, and 20\% for teachers with more than 25 years of experience.
 
@@
 % This is about changes (due to) after covid
-A question in the survey was also focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' viewpoints towards the use of instant messaging apps int their class. The 282 
+Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' viewpoints towards the use of instant messaging apps int their class.
+Our main intention in this case was to assess whether a crisis will bring about some kind of change in the use of tools.
+The 282 
 % Fran, please check Olia's comment as having 282 answers 

### 2021-07-18 edubots_surveys.Rnw
Avoid overlap chart-caption
Reincorporating changes in bed254a592265fa45144ce600a47d9ec10b6752e

@@
 The key findings of the students surveys reveal that they prefer to use messaging applications, such as Telegram or WhatsApp as they are familiar to them.
-Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course resources.
+Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course's resources.
 \item The results of the first phase were fed into the second phase of the study, which focused on teachers’ opinions about using chatbots and messaging applications in classes.
@@
 \item RQ3 - Which kind of interaction do teachers prefer with their students?
-\item RQ4 - Which kind of interaction media features do teachers value the most?
+\item RQ4 - What kind of interaction media features do teachers value the most?
 \end{itemize}
@@
 
-The {\bf initial survey} was done in two separate Google forms, one for university and other for tertiary non-university teachers (vocational education).
+The {\bf initial survey} was done in two separate Google forms, one for university and other for tertiary non-university teachers.
 Questions and responses were the same, except for the type of tertiary degrees that were taught.
@@
 \item Discipline: Engineering, Social Sciences, Health and Bio, Sciences, Humanities, Other.
-\item Gender: Man, Woman, Prefer not to say.
+\item Gender: Man, Woman, Rather not say.
 \item Age: 25-35, 35-45, 45-55, more than 55.
 \item Experience on the job: up to 5 years, 5-15 years, 15-25 years, more than 25 years.
-\item Type of degree: university, other tertiary education (vocational education).
-This question was implicit in the first survey, since one and the other filled different forms, it was explicit in the second survey.
+\item Type of degree: university, other tertiary education. This question was implicit in the first survey, since one and the other filled different forms, it was explicit in the second survey.
 \end{itemize}
@@
 
-Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what  their feelings and preferences are with regard to the use of instant messaging applications with students, and even using bots or chatbots in the classroom.
+Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are  their feelings and preferences with regard to the use of instant messaging applications with students, and even using bots or chatbots in the classroom.
 In addition the survey asked about the most relevant \textit{interaction media features} for the teachers with respect to the potential tool to use in class.
@@
 %       \includegraphics[width=\textwidth]{figures/gender_covid.pdf}
-        \vspace{-1cm}
+        \vspace{-0.5cm}
         \caption{Total count of responses for the use of messaging apps after the COVID-19 pandemic grouped by gender (PNTS stands for Prefer Not To Say).}
@@
 %       \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
-        \vspace{-1cm}
+        \vspace{-0.5cm}
         \caption{Total count of responses for the use of messaging apps after the COVID-19 pandemic grouped by sector.}
@@
 %       \includegraphics[width=\textwidth]{figures/experience_covid.pdf}
-        \vspace{-1cm}
+        \vspace{-0.5cm}
         \caption{Total count of responses for the use of messaging apps after the COVID-19 pandemic grouped by years of experience in teaching.}
@@
 %       \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
-        \vspace{-1cm}
+        \vspace{-0.5cm}
         \caption{Total count of responses for the use of messaging apps after the COVID-19 pandemic grouped by discipline.}
@@
 %       \includegraphics[width=\textwidth]{figures/gender_chatbottype.pdf}
-        \vspace{-1cm}
+        \vspace{-0.5cm}
         \caption{Count of types of chatbots for class perceived as the most useful for teachers grouped by gender (PNTS stands for Prefer Not To Say).}
@@
 %       \includegraphics[width=\textwidth]{figures/sector_chatbottype.pdf}
-        \vspace{-1cm}
+        \vspace{-0.5cm}
         \caption{Count of types of chatbots for class perceived as the most useful for teachers grouped by sector.}
@@
 %       \includegraphics[width=\textwidth]{figures/experience_chatbottype.pdf}
-        \vspace{-1cm}
+        \vspace{-0.5cm}
         \caption{Count of types of chatbots for class perceived as the most useful for teachers grouped by experience.}
@@
 %       \includegraphics[width=\textwidth]{figures/experience_chatbottype.pdf}
-        \vspace{-1cm}
+        \vspace{-0.5cm}
         \caption{Count of types of chatbots for class perceived as the most useful for teachers grouped by discipline.}
@@
 
-%\subsection{RQ4 - Which kind of interaction media features do teachers value the most?}
+%\subsection{RQ4 - What kind of interaction media features do teachers value the most?}
 
@@
 
-\subsection{RQ4 - Which kind of interaction media features do teachers value the most? }
+\subsection{RQ4 - What kind of interaction media features do teachers value the most? }
 

### 2021-07-18 edubots_surveys.Rnw
Adds contributions.
If you don't agree with it, just change them. @aguillen @fbarrango @amorag @pacastillo @oliatsi @noorhanabbas

@@
 
-PAC has...
-AMM has ...
-FB has...
-NA has...
-OT has...
-AG has...
+PAC has revised the paper and researched the state of the art, as well as contributed to the survey design.
+AMM has revised the paper and researched the state of the art, as well as contributed to the survey design.
+FB has made the analysis and processed data and contributed to the survey design.
+NA has supervised the state of the art, and written the bulk of it, as well as contributed to discussion and conclusions.
+OT has performed data analysis, and contributed to discussion and conclusions.
+AG has contributed to the design of the survey, analysis, discussion and conclusions.
 
 All authors have read and approved the final manuscript.
-
-% Antonio - here we can explain what we have done author briefly.
 

### 2021-07-18 edubots_surveys.Rnw
Discussing RQ1
Please @oliatsi @noorhanabbas @fbarranco check this.

@@
 % Relationship between changes, gender and discipline (Olia) - JJ
+% 
+Our initial intention in the design of these surveys was to probe the opinions of tertiary education teachers in the introduction of chatbot technologies in the class.
+We wanted to find the answer to four research questions, of which the first was to check whether teachers already used some kind of messaging application, and the one they preferred.
+Depending on the answer, different technologies could be (or not) available for the introduction of chatbots.
+In this case, the design of the survey introduced some ambiguity on what we really consider "messaging technology", that was eventually resolved by the answers; apparently, anything that sends messages (even if they are not instant, even if they don't have a dedicated application) was the concept in the mind of the surveyed.
+
+Additionally, the question on COVID reflected the big challenge that represents changing habits, even in the case of a major crisis.
+Very few people actually changed, with women vs.
+men being an exception, as well as those teaching social sciences standing out among the rest.
+We don't have any kind of explanation for this behavior, other than technologies are perceived, and adopted, in a different depending on background and, apparently, gender.
 

### 2021-07-18 edubots_surveys.Rnw
Adds link to repo. About time
Completing RQ4

@@
 
+This question is mainly answered in the second survey, which, as indicated previously, was designed after initial analysis of the first.
+The kind of interaction is essential to design proper chatbots, or to deploy a technology instead of others; it is related to the perceived usefulness in a technology acceptance model.
+Essentially, if some new chatbot application does not have what teachers perceive as useful for their purposes, they are unlikely to adopt it.
+So knowing these opinions is quite important, and is the reason why we included it in the second survey.
+
 A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
@@
 In terms of teaching experience, 59 teachers (28.8\%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9\%), 0-5 years (51; 24.9\%) and more than 25 years of experience (44; 21.5\%).
-The teachers were asked about what kind of interaction media features they value the most; the frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
+This age distribution is not different from the usual in the Spanish university, which has lately aged due to several reasons, so the answers we obtain can, in principle, be extrapolated to the population at large, at least in this sense.
+
+The teachers were asked about what kind of features of the messaging system they value the most; the frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
 
@@
 \vspace{0.8em}
-\caption{Interaction media features valued by teachers}
+\caption{Messaging platform features valued by teachers}
 \label{tab:interaction}
@@
 \hline
- & Connectivity & Familiarity  & Horizontallity & \begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} & Pluggability & Sustainability & Unidirectionality & Officiality \\ \hline
+ & Connectivity & Familiarity  & Horizontality & \begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} & Pluggability & Sustainability & Unidirectionality & Officiality \\ \hline
 Analytics &  $12.172^{***}$ & $4.855^{*}$ & ns & $4.144^{*}$ &  $12.490^{***}$ & $4.314^{*}$ & ns & ns \\
@@
 Hidden phone &  &  & ns & $5.678^{*}$ & $4.683^{*}$ & ns & $4.515^{*}$ & ns \\
-Horizontallity &  &  - & ns & ns & ns & ns & ns & $5.453^{*}$ \\
+Horizontality &  &  - & ns & ns & ns & ns & ns & $5.453^{*}$ \\
 \begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} &  & &  & - & $8.163^{**}$ & ns & ns & ns  \\
@@
 \ref{figure:predictor}).
-Two clusters occurred from the analysis: cluster 1 (n=78, 60.9\%) was comprise of instructors who did not value interaction media pluggability, connectivity, official formation, but valued interaction media analytics, familiarity, support by the institution, while cluster 2 (n=50, 39.1\%) was comprise of instructors from which the majority did not value media analytics, official formation, familiarity, but valued pluggability, connectivity, and support by the institution.
+Two clusters occurred from the analysis: cluster 1 (n=78, 60.9\%) was comprised of instructors who did not value interaction media pluggability, connectivity, official formation, but valued interaction media analytics, familiarity, support by the institution, while cluster 2 (n=50, 39.1\%) was comprised of instructors from which the majority did not value media analytics, official formation, familiarity, but valued pluggability, connectivity, and support by the institution.
 Interaction media pluggability appears to have the most important predictor importance in the clustering of cases (predictor importance = 1.0), whilst media unidirectionality was the least important factor (predictor importance = 0.04).
@@
 
-%This section is repeated
-%\section*{Acknowledgements}
-
 \bibliographystyle{apalike}
@@
 
-The datasets generated and analysed during the current study are available in the [NAME] repository, accesible from [PERSISTENT WEB LINK TO DATASETS]
+The datasets generated and analysed during the current study are available in Github, from \url{https://github.com/JJ/edubots-paper/tree/main/data}.
 
@@
 The authors want to thank to the educators who participated in the survey, and also people who have distributed the survey in their mailing lists, especially Mario García Valdez, Jesús Moreno León and José Raúl Canay.
-% Antonio - Add other acknowledgements
 

### 2021-07-18 edubots_surveys.Rnw
Discussing RQ4

@@
 % Alberto: using new metric so grade students, and also abotu horizontality
+%
+
+The clustering analysis in RQ4 seems to reflect the possible overrepresentation of teachers in the techonology discipline, which were the majority of tertiary non universitary teachers, and a good amount of the university teachers.
+In general, these teachers feel they are able to use analytics tools, or create and connect homebrew tools to messaging applications, which is why they value those features in them; however, most people value the fact that they are easy to use (perceived ease of use) and the fact that they are official, and thus sustainable through different courses.
 

### 2021-07-19 edubots_surveys.Rnw
minor fixes

--- 2021-07-18 edubots_surveys.Rnw
@@
 % 
-Our initial intention in the design of these surveys was to probe the opinions of tertiary education teachers in the introduction of chatbot technologies in the class.
+Our initial intention in the design of these surveys was to probe the opinions of tertiary education teachers in the introduction of chatbot technologies in class.
 We wanted to find the answer to four research questions, of which the first was to check whether teachers already used some kind of messaging application, and the one they preferred.
 Depending on the answer, different technologies could be (or not) available for the introduction of chatbots.
-In this case, the design of the survey introduced some ambiguity on what we really consider "messaging technology", that was eventually resolved by the answers; apparently, anything that sends messages (even if they are not instant, even if they don't have a dedicated application) was the concept in the mind of the surveyed.
+In this case, the design of the survey introduced some ambiguity on what we really consider "messaging technology", that was eventually resolved by the answers; apparently, anything that sends messages (even if they are not instant, even if they do not have a dedicated application) was the concept in the mind of the surveyed.
 
@@
 men being an exception, as well as those teaching social sciences standing out among the rest.
-We don't have any kind of explanation for this behavior, other than technologies are perceived, and adopted, in a different depending on background and, apparently, gender.
+We do not have any kind of explanation for this behavior, other than technologies are perceived, and adopted, in a different way depending on background and, apparently, gender.
 

### 2021-07-19 edubots_surveys.Rnw
Revise Introduction, SotA and Methodology sections

@@
 Responses from 300 teachers were collected and analysed.
-An initial analysis led to the creation of a second survey, which collected responses from 200 different higher education teachers.
+This initial analysis led to the creation of a second survey, which collected responses from 200 different higher education teachers.
 The questions on this survey focus on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:
@@
 % The Use of Mobile Instant Messaging (MIM) Platforms in Higher Education
-The widespread and rapid adoption of free Mobile Instant messaging
+The widespread and rapid adoption of free Mobile Instant Messaging
 (MIM) tools/platforms such as WhatsApp, Telegram, WeChat and Facebook
@@
 \cite{gachago2015crossing}; however, this last paper also reflects the need for
-learners to "take ownership of the tool" and the advantages of social learning
+learners to ``take ownership of the tool'' and the advantages of social learning
 in general. At the same time, it also mentions different challenges, among which
@@
 Facebook Messenger with the focus to identify characteristics and
-quality metrics such as language, subject matter and platform. Another
-study aimed to categorise educational chatbots according to their
-purpose into service-oriented and teaching-oriented
-\cite{perez2020rediscovering}. The first category includes those that
+quality metrics such as language, subject matter and platform. 
+Whereas study \cite{perez2020rediscovering} aimed to categorise educational chatbots according to their
+purpose into service-oriented and teaching-oriented. The first category includes those that
 provide service support such as the chatbot Ask Holly \cite{meetholly}
@@
 progress. For instance, \cite{fernoagua2018intelligent} reported on
-''eduAssistant'', a virtual teaching assistant chatbot developed on the
+``eduAssistant'', a virtual teaching assistant chatbot developed on the
 Telegram messaging platform. In this study, Telegram platform was
@@
 addition, Telegram could operate on all devices and operating
-systems. The ''eduAssistant'' chatbot acts as an automatic agent
+systems. The ``eduAssistant'' chatbot acts as an automatic agent
 in teacher-content-student, facilitating real-time feedback
@@
 
-Our intention from the beginning was to try and gather a sufficient amount of responses in all sectors, as well as cover different sectors of higher education.
+Our intention from the beginning was to try to gather a sufficient amount of responses in all sectors, as well as cover different sectors of higher education.
 In doing so, an online survey was administered (i.e., Google Form), in Spanish, which was intended to be answered in a very short amount of time.
-Initially, our intention was to mirror the questions used in \cite{MoraChatbots2021}; however, an initial exploration of results led us to create a second survey.
+Initially, our intention was to mirror the questions used in \cite{MoraChatbots2021};
+% Antonio - I would say something like: "but from teachers' perspective"
+however, an initial exploration of results led us to create a second survey.
 The survey items focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider useful to be used in their teaching, and the type of interactions that teachers prefer to have with their students while using messaging apps in their teaching.
@@
 The university form was spread in Spanish (mainly Andaluc\'{\i}a and Galicia) universities, and also Costa Rica and Mexico.
-The tertiary non-university teachers are mainly in Andaluc\'{\i}a.
+The tertiary non-university teachers were mainly in Andaluc\'{\i}a.
 Dissemination and answers took place in the first quarter of 2021, post-pandemic and while, at least in Spain, many universities had mandatory virtual teaching.
+
 A total of 282 teachers responded to the survey: 193 teaching at the University (68.4\%) and 89 at high school (31.6\%).
 
-All surveys had the same common, initial questions for segmentation:\begin{itemize}
+All surveys
+% Antonio - I would say "The two surveys"
+had the same common, initial questions for segmentation:\begin{itemize}
 \item Degrees or titles where the teacher was working, either university or other tertiary education.
@@
 % Including questions in surveys
-The {\bf first survey}, which focused about the use of messaging apps in class, and which tried to address mainly RQ2 and R23, includes the following questions:
+The {\bf first survey}, which focused about the use of messaging apps in class, and which tried to address mainly RQ2 and RQ3, 
+% Antonio - I guess it refers to RQ3. ;)
+includes the following questions:
 
@@
 \end{itemize}
+
+% Antonio - I would suggest to include a kind of reference name to each one of these variables.
+I mean, we could add at the end of their description something like "[Analytics], [Connectivity], [Officiality], etc", maybe in courier font to be remarked; i.e.
+the names used on Table 8.
+Thus it will be easy to recognise every variable, and then, we could refer to them in Table 8 (and Table 9).
 
@@
 Also, only university teachers find interesting a group with all the students and teachers in their own Faculty or School.
-The lack of teachers from vocational education here may be the consequence of using specific language such as "Faculty".
+The lack of teachers from vocational education here may be the consequence of using specific language such as ``Faculty''.
 Moreover, the fact that many universities and schools already use these groups for administrative and social interaction (e.g.
@@
 Depending on the answer, different technologies could be (or not) available for the introduction of chatbots.
-In this case, the design of the survey introduced some ambiguity on what we really consider "messaging technology", that was eventually resolved by the answers; apparently, anything that sends messages (even if they are not instant, even if they do not have a dedicated application) was the concept in the mind of the surveyed.
+In this case, the design of the survey introduced some ambiguity on what we really consider ``messaging technology'', that was eventually resolved by the answers; apparently, anything that sends messages (even if they are not instant, even if they do not have a dedicated application) was the concept in the mind of the surveyed.
 

### 2021-07-20 edubots_surveys.Rnw
Adding names of Interaction Media Features

@@
 
+% Antonio - I have included a reference name to each one of these variables, which are the names used on Tables 8 and 9.
+Thus it will be easy to recognise every variable, and then, we could refer to them in those tables.
+
 \textit{1. You prefer the interaction with your students to be ...}
 \begin{itemize}
-\item Synchronous: students and teacher/s in the same space, simultaneously.
-\item Asynchronous: the student asks at anytime, the teacher responds whenever possible.
+\item Synchronous: students and teacher/s in the same space, simultaneously. [\texttt{Synchrony - Yes}]
+\item Asynchronous: the student asks at anytime, the teacher responds whenever possible. [\texttt{Synchrony - No}]
 \end{itemize}
@@
 \begin{itemize}
-\item Prefer it to be done by institutional means/tools: office hours, forum/messages via the virtual campus, institutional email
-\item Admit the use of other means/toosl: blogs, chat groups in messaging platforms, any others.
+\item Prefer it to be done by institutional means/tools: office hours, forum/messages via the virtual campus, institutional email. [\texttt{Officiality - Yes}]
+\item Admit the use of other means/toosl: blogs, chat groups in messaging platforms, any others. [\texttt{Officiality - No}]
 \end{itemize}
@@
 \begin{itemize}
-\item Familiarity with its use i.e. that I do not need to learn a new tool
-\item The official formation/training provided by your institution on its use
-\item That only one-directional communication is allowed (from teachers to students)
-\item Non-hierarchical tools that allowed teacher-to-student and student-to-student communication 
-\item That allow additional functionalities such as interfaces to other tools
-\item That allow teachers to develop/add their own functionalities (e.g. automatic correction tools)
-\item That let me avoid to worry about maintenance and that it is easily sustainable from one year to the next
-\item That allow to extract data to assess the student performance
+\item Familiarity with its use i.e. that I do not need to learn a new tool. [\texttt{Familiarity}]
+\item The official formation/training provided by your institution on its use. [\texttt{Official formation}]
+\item That only one-directional communication is allowed (from teachers to students). [\texttt{Unidirectionality}]
+\item Non-hierarchical tools that allowed teacher-to-student and student-to-student communication. [\texttt{Horizontally}]
+\item That allow additional functionalities such as interfaces to other tools. [\texttt{Connectivity}]
+\item That allow teachers to develop/add their own functionalities (e.g. automatic correction tools). [\texttt{Pluggability}]
+\item That let me avoid to worry about maintenance and that it is easily sustainable from one year to the next. [\texttt{Sustainability}]
+\item That allow to extract data to assess the student performance. [\texttt{Analytics}]
+% Antonio - Is it missing one feature concerning Hidden Phone Numer???
 \end{itemize}
-
-% Antonio - I would suggest to include a kind of reference name to each one of these variables.
-I mean, we could add at the end of their description something like "[Analytics], [Connectivity], [Officiality], etc", maybe in courier font to be remarked; i.e.
-the names used on Table 8.
-Thus it will be easy to recognise every variable, and then, we could refer to them in Table 8 (and Table 9).
 
@@
 \vspace{0.8em}
-\caption{Interaction media features valued by teachers}
+\caption{Interaction media features valued by teachers. Details about each feature can be read in Section \ref{sec:meth}.}
 \label{tab:interaction}
@@
 Columns and rows with no significant interaction have been suppressed for clarity.
-Every cell value represents $X^{2}_{(1, N = 205)}$.}
+Every cell value represents $X^{2}_{(1, N = 205)}$.
+Details about each feature can be read in Section \ref{sec:meth}.}
 \label{tab:interactionfeatures}

### 2021-07-20 edubots_surveys.Rnw
Adding Hidden Phone Number feature description
Some corrections
Mainly grammar, but also qualifying "High school"

@@
 Responses from 300 teachers were collected and analysed.
-This initial analysis led to the creation of a second survey, which collected responses from 200 different higher education teachers.
+An initial analysis of these responses led to the creation of a second survey, which collected responses from 200 different higher education teachers.
 The questions on this survey focus on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:
@@
 The university form was spread in Spanish (mainly Andaluc\'{\i}a and Galicia) universities, and also Costa Rica and Mexico.
-The tertiary non-university teachers were mainly in Andaluc\'{\i}a.
+The tertiary non-university teachers are based mainly in Andaluc\'{\i}a.
 Dissemination and answers took place in the first quarter of 2021, post-pandemic and while, at least in Spain, many universities had mandatory virtual teaching.
 
-A total of 282 teachers responded to the survey: 193 teaching at the University (68.4\%) and 89 at high school (31.6\%).
-
-All surveys
-% Antonio - I would say "The two surveys"
-had the same common, initial questions for segmentation:\begin{itemize}
+A total of 282 teachers responded to the survey: 193 teaching at the University (68.4\%) and 89 at other tertiary education institutions (31.6\%).
+
+The surveys have the same common, initial questions for segmentation:\begin{itemize}
 \item Degrees or titles where the teacher was working, either university or other tertiary education.
@@
 \item Non-hierarchical tools that allowed teacher-to-student and student-to-student communication. [\texttt{Horizontally}]
-\item That allow additional functionalities such as interfaces to other tools. [\texttt{Connectivity}]
-\item That allow teachers to develop/add their own functionalities (e.g. automatic correction tools). [\texttt{Pluggability}]
-\item That let me avoid to worry about maintenance and that it is easily sustainable from one year to the next. [\texttt{Sustainability}]
-\item That allow to extract data to assess the student performance. [\texttt{Analytics}]
-% Antonio - Is it missing one feature concerning Hidden Phone Numer???
+\item Connectivity to other tools, for instance common login. [\texttt{Connectivity}]
+\item Possibility for teachers to develop/add their own functionalities (e.g. automatic correction tools). [\texttt{Pluggability}]
+\item Possibility for users to hide personal data (such as my telephone number). [\texttt{Hidden Phone Number}]
+\item Not having to worry about maintenance and that it is easily sustainable from one year to the next. [\texttt{Sustainability}]
+\item That it offers the chance to extract data to assess the student performance. [\texttt{Analytics}]
 \end{itemize}
@@
 Regarding Gender grouping, both gender agree in their uses, so it seems not relevant at all.
-When looking at the plot containing the sector differentiation it is interesting ot observe how university teachers prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational/High School teachers.
+When looking at the plot containing the sector differentiation it is interesting ot observe how university teachers prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational High School teachers.
 This seems reasonable as the frequency of seeing the students is smaller at the University so, automating the grade notification for continuous evaluation could seem much more comfortable using an automated tool than using the traditional platform.

### 2021-07-21 edubots_surveys.Rnw
Adds suggestion by @noorhanabbas

@@
 
-% Olia: we have something for RQ 2 and 4.
- One of the most interesting questions that can arise from the plots, and the should require further study, is: Are teachers really aware of the possibilities of chatbots in the classroom?
+ One of the most interesting questions that can arise from the analysis of the results, and that should require further study, is: Are teachers really aware of the possibilities of chatbots in the classroom?
 The reason to ask ourselves this question is due to the fact of the small number of responses for other uses in comparison with the other approaches proposed.
@@
 
-% Noorhan comments negative experience with customer service chatbots, in which case people will not see the value of using it in their classes.
-They are not aware of something like that.
-Teaching chatbots are difficult to develop.
-Using very simple chatbots, or simply conversational interfaces, could help introduce this technology - JJ
+It is also likely that their opinions towards chatbots are informed by negative experiences with customer support chatbots, which is what most people will have experienced.
+This will probably require further study, but also will need to be taken into account when introducing chatbot technologies in the classroom: it will have to be as simple, and as satisfactory, ad possible, to (possibly) delete this existing perception.
 

### 2021-07-21 edubots_surveys.Rnw
Discuss Rq4

@@
 
-Regarding Gender grouping, both gender agree in their uses, so it seems not relevant at all.
+Regarding gender grouping, both genders agree in their uses, so it seems not relevant at all.
 When looking at the plot containing the sector differentiation it is interesting ot observe how university teachers prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational High School teachers.
@@
 % Alberto: using new metric so grade students, and also abotu horizontality
+
+An analysis of survey questions related to RQ4 seems to indicate that teachers prefer to have interaction with their students in a chat "room"; a preference of {\em horizontal} interaction might indicate the need to delegate or offload part of the burden of answering, and attending, every single question posed by students.
+In an horizontal setting, other students can answer if the teacher does not do it immediately.
+This might also be the reason why the possibility of using tools from which analytics can be extracted is also valued by teachers: that way, activity in the chat tool, answering questions, regularity, can all be observed and valued as part of the process of assesing achievement of learning objectives by students.
 

### 2021-07-22 edubots_surveys.Rnw
Completed first draft of paper
Closes #47 (by @fbarranco before
Closes #24 (by @fbarranco and @oliatsi)
Closes #22 (by @fbarranco and @amorag)
Closes #19 (done before)
Closes #17 (not really done, finally eliminated)
Closes #16 Done, discusses, added conclusions
Closes #15 Done, also added results and conclusions

@@
 
-% Add something about intro
-% RQ1 discussion about messaging app: they consider a IM the Moodle messaging
-% Olia: it's not so easy to change habits, even in the case of major crisis. - JJ
-% Relationship between changes, gender and discipline (Olia) - JJ
-% 
 Our initial intention in the design of these surveys was to probe the opinions of tertiary education teachers in the introduction of chatbot technologies in class.
@@
 \end{itemize}
-
-% Rq4: they seem to prefer interaction with students - Olia 
-% Alberto: using new metric so grade students, and also abotu horizontality
 
@@
 % Noorhan suggest that using some simple things could increase the perceived usefulness - JJ
+As in many other methods of technology acceptance, answers to the survey suggest that the introduction of simple, and institution-supported, instant messaging and chatbot technologies would increase the perceived usefulness (which is one of the key metrics in technology acceptance models).
+Since most institutions already have some {\em virtual campus} or learning management system, adding some easy automation, or connection to personal instant messaging tools, could really help onboard the learning community on these new technologies.
 
 % What kidn of chatbots are preferred? (suggested by Fran)
+Once that initial introduction is done, teachers (and students as well) will probably prefer the kind of bots that alleviate bureaucratic or repetitive tasks, such as answering frequent questions or answers on class or assignment schedules.
+These will help the introduction of more complex chatbots that will affect more directly learning outcomes, such as chatbots that help students integrate in the class, or are able to identify (and address) learning problems in students or in groups of them.
+These as well should be accompanied by analytics on student interaction, as well as possibly some natural language processing (in vernacular language) that will help assess the general mood of the class, and how different material (or external factors) affect it.
 
 % No remarkable differences between different groups.
+This introduction of chatbots and chatbot technology will be helped by the fact that no discernible differences are found between different groups.
+Even if chatbots do have some potential for personalization or customization, based on the class material, student and teaching staff, the general introduction of the technology can be done in a general way and for all disciplines, teaching experience and gender.
 
 % Only some COVID-response relationship.
+In our survey, we couldn't find an answer to the right moment for doing this introduction of chatbot technologies.
+Response to questions related to change of behavior during and after the pandemic do not suggest that major (or minor) crisis could be an opportunity to introduce new technologies, since it does not bring major changes in attitude.
+A minor crisis would be, for instance, rollout of a new higher education law\footnote{We seem to have one of these, at least in Spain, every 10 years or so}, or introduction of new degrees.
+Although external changes do offer the chance of piloting new technologies, they do not seem to bring changes in attitudes in the teaching staff (which, after all, is bound to be the same).
+In absence of a clear answer in this direction, the right moment to introduce new technologies is always when the IT and managing staff is ready to support it (since, as we have seen before, "official" support is one of the factors that is most valued by teachers).
+
+At any rate, the general feeling that transpires from the survey is that it is essential for any institution to take into account the stakeholder's opinion when introducing chatbots.
+This is true almost across the board, but in the case of chatbots (and instant messaging applications) their inmediacy and the fact that they can enter into what we could call the private sphere makes this even more necessary.
 
 % Future study (suggested by Noorhan): how COVID influenced adoption of these technologies.
+There are several future lines of work informed by our results of this survey.
+For instance, the rollout of extensive videoconferencing and virtual teaching solutions that the COVID pandemic has brought has also taught us a series of lessons.
+It increases isolation, for instance, and decreases the amount of synchronous contact that happens in the fringes of the classroom: teaching staff offices, before and after class.
+A future line of work would be focused on exactly this, and what kind of needs could be covered by chatbot technology.
+We will create a series of international surveys that will investigate this.
 
 % Emotinal, mood for future work... Chatbots perform sentiment analysis
-
-%This section is repeated
-%\section*{Acknowledgements}
+Finally, the full extent of chatbot technology is not really being examined in these surveys.
+They can be connected to natural language processing engines with sentiment analysis as well as other analytics.
+Examining the mood of the class, as response to new material, assignment, exams or external events might help will help any student-centered teaching strategy, which will help students (and teachers) reach their learning objectives.
+This line of work, however, will be based on the introduction of some pilot study, combined with initial opinion assesment on the students.
 
@@
 
-The datasets generated and analysed during the current study are available in the [NAME] repository, accesible from [PERSISTENT WEB LINK TO DATASETS]
+The datasets generated and analysed during the current study are available in the {\tt edubots-paper} repository, accesible from {\tt https://github.com/JJ/edubots-paper/tree/main/data}.
 

### 2021-07-27 edubots_surveys.Rnw
Changes during conference

@@
 
+% Move a part of this to an appendix: Noorhan
 The {\bf initial survey} was done in two separate Google forms, one for university and other for tertiary non-university teachers.
@@
 % Describe the survey and population
-We collected responses from 282 teachers from Spain and Spanish Speaking countries for the first survey (\textit{survey1} and 205 for the second one (\textit{survey2}).
+We collected responses from 282 teachers from Spain and Spanish Speaking countries for \textit{survey1} and 205 for \textit{survey2}.
 The two forms were open for approximately the same amount of time, around two months.
@@
 
-Well try to find the answers to the four research questions next, by analyzing the response to the different survey questions.
+We will try to find the answers to the four research questions next, by analyzing the response to the different survey questions.
 
@@
 \vspace{0.8em}
-\caption{Use of messaging apps in class}
+\caption{Use of messaging apps to assist the learning process.}
 \label{tab:use_messapps}
@@
 \ref{figure:provided*chatbots_use}, \ref{figure:whatsapp*chatbots_use}, \ref{figure:telegram*chatbots_use} do not show significant differences in the use of instant messaging apps between teachers from University and vocational education.
-In general, most teachers prefer messaging apps provided by their own institutions (we also show the results for the two most popular messaging app platforms: Whatsapp and Telegram).
+In general, most teachers prefer messaging apps provided by their own institutions (we also show the results for the two most popular messaging app platforms: WhatsApp and Telegram).
 With respect to specific disciplines, Engineering and Technology teachers are more active in their use, although it is also relevant the amount of teachers from Humanities that answered they used these apps in their classes (around 60\% use the apps provided by their institutions).
@@
 %The third column compares the use of these apps considering the number of years of experience.
-One interesting result is that, contrary to the idea of technology adaptation issues when considering older teachers, about 65\% of teachers with more than 25 years of experience use the platforms provided by their institutions while the percentage goes down to less than 50\% for teachers with 6-15 years of experience.
+One interesting result is that about 65\% of teachers with more than 25 years of experience use the platforms provided by their institutions while the percentage goes down to less than 50\% for teachers with 6-15 years of experience.
 %
@@
 
-As it can be seen by the answer to the first and last question, in general teachers do not want to participate in a chat group with students; either they want to simply leave leave the students alone in their own chat group, or otherwise they prefer not to be part of that interaction.
+As it can be seen by the answer to the first and last question, in general teachers do not want to participate in a chat group with students; either they want to simply leave the students alone in their own chat group, or otherwise they prefer not to be part of that interaction.
 In general, that is going to be the case no matter what; it is well known that students organize their own chat groups with many (and not always conveyable) intentions, so teachers do not want to take any part in it.
@@
 Examining the mood of the class, as response to new material, assignment, exams or external events might help will help any student-centered teaching strategy, which will help students (and teachers) reach their learning objectives.
-This line of work, however, will be based on the introduction of some pilot study, combined with initial opinion assesment on the students.
+This line of work, however, will be based on the introduction of some pilot study, combined with initial opinion assessment on the students.
 

### 2021-07-27 edubots_surveys.Rnw
clarifies on teachers not being part of student chat groups

@@
 As it can be seen by the answer to the first and last question, in general teachers do not want to participate in a chat group with students; either they want to simply leave the students alone in their own chat group, or otherwise they prefer not to be part of that interaction.
-In general, that is going to be the case no matter what; it is well known that students organize their own chat groups with many (and not always conveyable) intentions, so teachers do not want to take any part in it.
-Overwhelmingly, they don't want to participate in any chat group with students, but even less so if it includes the rest of the faculty.
+In general, that is going to be the case no matter what; it is well known that students organize their own chat groups with many (and not always conveyable) intentions, so teachers do not want to take any part in these informal or non institutionally-supported chat groups.
+Overwhelmingly, they do not want to participate in these kind of chat groups with students, but even less so if it includes the rest of the faculty.
 

### 2021-07-28 edubots_surveys.Rnw
Spin off part of the methodology to analysis
Mainly spell check

@@
 and Dina \cite{santoso2018dinus}; both chatbots respond to students'
-questions about enrollment and registration. Ask L. U.
+questions about enrolment and registration. Ask L. U.
  \cite{LancasterUniversity_2019} answers students' frequently
@@
 University of Granada using an inset character, voiced by a real
-person, who lip-synched the answers. The emphasis in the case of Elvira,
+person, who lip-synced the answers. The emphasis in the case of Elvira,
 however, was on the authenticity of the synchronization more than in
@@
 \cite{fernoagua2018intelligent} studies. In addition, Sj{\"o}str{\"o}m et al. \cite{sjostrom2018designing} 
-argued that a conceptualision of learners' questions could aid designers in integrating the appropriate
+argued that a conceptualisation of learners' questions could aid designers in integrating the appropriate
 types of questions that the chatbots should support for different
@@
 
-Along this line of research, our previous work \cite{MoraChatbots2021} aimed at analysing the expectations of students on this regard; recent papers have also analyzed how the use of chatbots affected the learning outcomes of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
-This paper analyzed conversational chatbots in an one-to-one setting, finding that learning really benefited from it.
+Along this line of research, our previous work \cite{MoraChatbots2021} aimed at analysing the expectations of students on this regard; recent papers have also analysed how the use of chatbots affected the learning outcomes of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
+This paper analysed conversational chatbots in an one-to-one setting, finding that learning really benefited from it.
 This is, once again, a proof of the benefit of chatbots in certain settings; however, there are some opinions that might prevent the successful acceptance of the technology, and these are what we are trying to find out in this paper, together with what kind of features would make its acceptance better.
@@
 Their attitudes have been studied very recently by Chocarro et al.
-\cite{doi:10.1080/03055698.2020.1850426}, who, by analyzing surveys, created a {\em technology acceptance model} that proposed a series of features that would make chatbots easier to accept; among them, formality of language as well as easiness and usefulness.
+\cite{doi:10.1080/03055698.2020.1850426}, who, by analysing surveys, created a {\em technology acceptance model} that proposed a series of features that would make chatbots easier to accept; among them, formality of language as well as easiness and usefulness.
 The survey targeted primary and secondary education teachers, and was also more interested in the general use of chatbots in education, not specifically in a classroom setting, seeking educational outcomes.
@@
 
-A total of 282 teachers responded to the survey: 193 teaching at the University (68.4\%) and 89 at other tertiary education institutions (31.6\%).
-
-The surveys have the same common, initial questions for segmentation:\begin{itemize}
-\item Degrees or titles where the teacher was working, either university or other tertiary education.
-\item Discipline: Engineering, Social Sciences, Health and Bio, Sciences, Humanities, Other.
-\item Gender: Man, Woman, Rather not say.
-\item Age: 25-35, 35-45, 45-55, more than 55.
-\item Experience on the job: up to 5 years, 5-15 years, 15-25 years, more than 25 years.
-\item Type of degree: university, other tertiary education. This question was implicit in the first survey, since one and the other filled different forms, it was explicit in the second survey.
-\end{itemize}
-
-% Including questions in surveys
-The {\bf first survey}, which focused about the use of messaging apps in class, and which tried to address mainly RQ2 and RQ3, 
-% Antonio - I guess it refers to RQ3. ;)
-includes the following questions:
-
-\textit{1. Regarding the use of messaging apps in class, you prefer ...}
-\begin{itemize}
-\item A chat group with the students in the same course
-\item Students self-organize and with the teacher not being part of any chat group
-\item A chat group with the all the students and teachers of the School/High-School/Faculty
-\item A chat group with all the students and teachers of the same study year
-\end{itemize}
-
-\textit{2. Which messaging app platform do you use to communicate with your peers or students?}
-\begin{itemize}
-\item Whatsapp
-\item Telegram
-\item LinkedIn
-\item Twitter messages
-\item Discord
-\item Slack
-\item Snapchat
-\item The platform provided by your own institution
-\item None, I do not use any messaging app to communicate with my students
-\end{itemize}
-
-\textit{3. Which kind of chatbots (software that automatically respond to questions or commands) could be useful to improve the learning results with your students or help you managing your course?}
-\begin{itemize}
-\item Agenda bots that e.g. remind students about project deadlines
-\item Bots that collect and provide answers to frequent questions
-\item Bots that inform students about their grades
-\item Bots that help with the class materials (e.g. searching for topics about a concept, or asking about them)
-\end{itemize}
-
-\textit{4. The virtualization of teaching due to the COVID pandemic during this year and the previous one, did it mean any change in your viewpoint or use of messaging apps in class?}
-\begin{itemize}
-\item No, I did use it before and use it now
-\item Yes, I started using safer alternatives
-\item Yes, I did not use any messaging platform before but I do use it now
-\item No, I did not use any messaging platform before or now
-\end{itemize}
-
-The {\bf second survey} followed the same paths, only in this case there was a single questionnaire, and with a different scope, focusing on the kind of interaction media features that teachers value the most.
-% Olia - see my comment above.
-It was filled by teachers that were also students in a teacher formation course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers who knew about it by emails from the authors, or from the vicedeanship for International Relations that included it in its newsletter.
-This means that there might be a higher proportion of 1) teachers with few years of experience 2) teachers from the computer science faculty and 3) teachers from Granada.
-We think, however that there's no explicit bias in this selection, although of course specific percentages will vary.
-These questions tried to address mainly RQ1 and RQ4.
-
-Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are  their feelings and preferences with regard to the use of instant messaging applications with students, and even using bots or chatbots in the classroom.
-In addition the survey asked about the most relevant \textit{interaction media features} for the teachers with respect to the potential tool to use in class.
-
-The specific questions included in this second survey are listed below:
-
-% Antonio - I have included a reference name to each one of these variables, which are the names used on Tables 8 and 9.
-Thus it will be easy to recognise every variable, and then, we could refer to them in those tables.
-
-\textit{1. You prefer the interaction with your students to be ...}
-\begin{itemize}
-\item Synchronous: students and teacher/s in the same space, simultaneously. [\texttt{Synchrony - Yes}]
-\item Asynchronous: the student asks at anytime, the teacher responds whenever possible. [\texttt{Synchrony - No}]
-\end{itemize}
-
-\textit{2. Regarding the interaction with your students, you ...}
-\begin{itemize}
-\item Prefer it to be done by institutional means/tools: office hours, forum/messages via the virtual campus, institutional email. [\texttt{Officiality - Yes}]
-\item Admit the use of other means/toosl: blogs, chat groups in messaging platforms, any others. [\texttt{Officiality - No}]
-\end{itemize}
-
-\textit{3. Which media features do you value the most for your interaction with your students?}
-\begin{itemize}
-\item Familiarity with its use i.e. that I do not need to learn a new tool. [\texttt{Familiarity}]
-\item The official formation/training provided by your institution on its use. [\texttt{Official formation}]
-\item That only one-directional communication is allowed (from teachers to students). [\texttt{Unidirectionality}]
-\item Non-hierarchical tools that allowed teacher-to-student and student-to-student communication. [\texttt{Horizontally}]
-\item Connectivity to other tools, for instance common login. [\texttt{Connectivity}]
-\item Possibility for teachers to develop/add their own functionalities (e.g. automatic correction tools). [\texttt{Pluggability}]
-\item Possibility for users to hide personal data (such as my telephone number). [\texttt{Hidden Phone Number}]
-\item Not having to worry about maintenance and that it is easily sustainable from one year to the next. [\texttt{Sustainability}]
-\item That it offers the chance to extract data to assess the student performance. [\texttt{Analytics}]
-\end{itemize}
+A total of 282 teachers responded to the survey: 193 teaching at the University (68.4\%) and 89 at other tertiary education institutions (31.6\%). Survey questions are shown in \ref{app:questions}.
 
@@
 Eventually, the results from the two forms we used for the first survey were collated in a single spreadsheet.
-Next we will show the results and analyze them.
+Next we will show the results and analyse them.
 
@@
 
-We will try to find the answers to the four research questions next, by analyzing the response to the different survey questions.
+We will try to find the answers to the four research questions next, by analysing the response to the different survey questions.
 
@@
 % This is about changes (due to) after covid
-Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' viewpoints towards the use of instant messaging apps int their class.
+Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' viewpoints towards the use of instant messaging apps in their class.
 Our main intention in this case was to assess whether a crisis will bring about some kind of change in the use of tools.
@@
 
-The majority of the teachers (n=165) mentioned that no changes in their habits occured due to the emergency remote teaching, as the use of messaging apps was part of their teaching practices and remains the same, from which 105 teachers come from the university, and 60 teachers from the vocational sector.
+The majority of the teachers (n=165) mentioned that no changes in their habits occurred due to the emergency remote teaching, as the use of messaging apps was part of their teaching practices and remains the same, from which 105 teachers come from the university, and 60 teachers from the vocational sector.
 The relationships between changes in the use of messaging apps, due to the covid-19 pandemic, and the instructors’ discipline, $X^{2}_{(24, N = 282)} = 44.856$, $p =0.006$, as well as the gender, $X^{2}_{(8, N = 282)} = 16.249$, p= 0.039 were also significant.
@@
 men being an exception, as well as those teaching social sciences standing out among the rest.
-We do not have any kind of explanation for this behavior, other than technologies are perceived, and adopted, in a different way depending on background and, apparently, gender.
+We do not have any kind of explanation for this behaviour, other than technologies are perceived, and adopted, in a different way depending on background and, apparently, gender.
 
@@
 Regarding gender grouping, both genders agree in their uses, so it seems not relevant at all.
-When looking at the plot containing the sector differentiation it is interesting ot observe how university teachers prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational High School teachers.
+When looking at the plot containing the sector differentiation it is interesting to observe how university teachers prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational High School teachers.
 This seems reasonable as the frequency of seeing the students is smaller at the University so, automating the grade notification for continuous evaluation could seem much more comfortable using an automated tool than using the traditional platform.
-Furthermore, the high student/teacher ratios that university docents have to deal with could be another reason to have a higher number of them willing to use chatbots for FAQs.
+Furthermore, the high student/teacher ratios that university teachers have to deal with could be another reason to have a higher number of them willing to use chatbots for FAQs.
 This could ameliorate the number of misunderstandings and email overload that so many students might generate.
@@
 In an horizontal setting, other students can answer if the teacher does not do it immediately.
-This might also be the reason why the possibility of using tools from which analytics can be extracted is also valued by teachers: that way, activity in the chat tool, answering questions, regularity, can all be observed and valued as part of the process of assesing achievement of learning objectives by students.
+This might also be the reason why the possibility of using tools from which analytics can be extracted is also valued by teachers: that way, activity in the chat tool, answering questions, regularity, can all be observed and valued as part of the process of assessing achievement of learning objectives by students.
 
@@
 
-% What kidn of chatbots are preferred? (suggested by Fran)
+% What kind of chatbots are preferred? (suggested by Fran)
 Once that initial introduction is done, teachers (and students as well) will probably prefer the kind of bots that alleviate bureaucratic or repetitive tasks, such as answering frequent questions or answers on class or assignment schedules.
@@
 In our survey, we couldn't find an answer to the right moment for doing this introduction of chatbot technologies.
-Response to questions related to change of behavior during and after the pandemic do not suggest that major (or minor) crisis could be an opportunity to introduce new technologies, since it does not bring major changes in attitude.
+Response to questions related to change of behaviour during and after the pandemic do not suggest that major (or minor) crisis could be an opportunity to introduce new technologies, since it does not bring major changes in attitude.
 A minor crisis would be, for instance, rollout of a new higher education law\footnote{We seem to have one of these, at least in Spain, every 10 years or so}, or introduction of new degrees.
@@
 
-At any rate, the general feeling that transpires from the survey is that it is essential for any institution to take into account the stakeholder's opinion when introducing chatbots.
-This is true almost across the board, but in the case of chatbots (and instant messaging applications) their inmediacy and the fact that they can enter into what we could call the private sphere makes this even more necessary.
+At any rate, the general feeling that transpires from the survey is that it is essential for any institution to take into account the shareholder's opinion when introducing chatbots.
+This is true almost across the board, but in the case of chatbots (and instant messaging applications) their immediacy and the fact that they can enter into what we could call the private sphere makes this even more necessary.
 
@@
 
-% Emotinal, mood for future work... Chatbots perform sentiment analysis
 Finally, the full extent of chatbot technology is not really being examined in these surveys.
 They can be connected to natural language processing engines with sentiment analysis as well as other analytics.
-Examining the mood of the class, as response to new material, assignment, exams or external events might help will help any student-centered teaching strategy, which will help students (and teachers) reach their learning objectives.
+Examining the mood of the class, as response to new material, assignment, exams or external events might help will help any student-centred teaching strategy, which will help students (and teachers) reach their learning objectives.
 This line of work, however, will be based on the introduction of some pilot study, combined with initial opinion assessment on the students.
@@
 
-The datasets generated and analysed during the current study are available in the {\tt edubots-paper} repository, accesible from {\tt https://github.com/JJ/edubots-paper/tree/main/data}.
+The datasets generated and analysed during the current study are available in the {\tt edubots-paper} repository, accessible from {\tt https://github.com/JJ/edubots-paper/tree/main/data}.
 
@@
 
+\section{Appendix I: Survey questions}
+\label{app:questions}
+
+The surveys have the same common, initial questions for segmentation:\begin{itemize}
+\item Degrees or titles where the teacher was working, either university or other tertiary education.
+\item Discipline: Engineering, Social Sciences, Health and Bio, Sciences, Humanities, Other.
+\item Gender: Man, Woman, Rather not say.
+\item Age: 25-35, 35-45, 45-55, more than 55.
+\item Experience on the job: up to 5 years, 5-15 years, 15-25 years, more than 25 years.
+\item Type of degree: university, other tertiary education. This question was implicit in the first survey, since one and the other filled different forms, it was explicit in the second survey.
+\end{itemize}
+
+% Including questions in surveys
+The {\bf first survey}, which focused about the use of messaging apps in class, and which tried to address mainly RQ2 and RQ3, 
+% Antonio - I guess it refers to RQ3. ;)
+includes the following questions:
+
+\textit{1. Regarding the use of messaging apps in class, you prefer ...}
+\begin{itemize}
+\item A chat group with the students in the same course
+\item Students self-organize and with the teacher not being part of any chat group
+\item A chat group with the all the students and teachers of the School/High-School/Faculty
+\item A chat group with all the students and teachers of the same study year
+\end{itemize}
+
+\textit{2. Which messaging app platform do you use to communicate with your peers or students?}
+\begin{itemize}
+\item WhatsApp
+\item Telegram
+\item LinkedIn
+\item Twitter messages
+\item Discord
+\item Slack
+\item Snapchat
+\item The platform provided by your own institution
+\item None, I do not use any messaging app to communicate with my students
+\end{itemize}
+
+\textit{3. Which kind of chatbots (software that automatically respond to questions or commands) could be useful to improve the learning results with your students or help you managing your course?}
+\begin{itemize}
+\item Agenda bots that e.g. remind students about project deadlines
+\item Bots that collect and provide answers to frequent questions
+\item Bots that inform students about their grades
+\item Bots that help with the class materials (e.g. searching for topics about a concept, or asking about them)
+\end{itemize}
+
+\textit{4. The virtualization of teaching due to the COVID pandemic during this year and the previous one, did it mean any change in your viewpoint or use of messaging apps in class?}
+\begin{itemize}
+\item No, I did use it before and use it now
+\item Yes, I started using safer alternatives
+\item Yes, I did not use any messaging platform before but I do use it now
+\item No, I did not use any messaging platform before or now
+\end{itemize}
+
+The {\bf second survey} followed the same paths, only in this case there was a single questionnaire, and with a different scope, focusing on the kind of interaction media features that teachers value the most.
+% Olia - see my comment above.
+It was filled by teachers that were also students in a teacher formation course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers who knew about it by emails from the authors, or from the vicedeanship for International Relations that included it in its newsletter.
+This means that there might be a higher proportion of 1) teachers with few years of experience 2) teachers from the computer science faculty and 3) teachers from Granada.
+We think, however that there's no explicit bias in this selection, although of course specific percentages will vary.
+These questions tried to address mainly RQ1 and RQ4.
+
+Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are  their feelings and preferences with regard to the use of instant messaging applications with students, and even using bots or chatbots in the classroom.
+In addition the survey asked about the most relevant \textit{interaction media features} for the teachers with respect to the potential tool to use in class.
+
+The specific questions included in this second survey are listed below:
+
+% Antonio - I have included a reference name to each one of these variables, which are the names used on Tables 8 and 9.
+Thus it will be easy to recognise every variable, and then, we could refer to them in those tables.
+
+\textit{1. You prefer the interaction with your students to be ...}
+\begin{itemize}
+\item Synchronous: students and teacher/s in the same space, simultaneously. [\texttt{Synchrony - Yes}]
+\item Asynchronous: the student asks at anytime, the teacher responds whenever possible. [\texttt{Synchrony - No}]
+\end{itemize}
+
+\textit{2. Regarding the interaction with your students, you ...}
+\begin{itemize}
+\item Prefer it to be done by institutional means/tools: office hours, forum/messages via the virtual campus, institutional email. [\texttt{Officiality - Yes}]
+\item Admit the use of other means/tools: blogs, chat groups in messaging platforms, any others. [\texttt{Officiality - No}]
+\end{itemize}
+
+\textit{3. Which media features do you value the most for your interaction with your students?}
+\begin{itemize}
+\item Familiarity with its use i.e. that I do not need to learn a new tool. [\texttt{Familiarity}]
+\item The official formation/training provided by your institution on its use. [\texttt{Official formation}]
+\item That only one-directional communication is allowed (from teachers to students). [\texttt{Unidirectionality}]
+\item Non-hierarchical tools that allowed teacher-to-student and student-to-student communication. [\texttt{Horizontally}]
+\item Connectivity to other tools, for instance common login. [\texttt{Connectivity}]
+\item Possibility for teachers to develop/add their own functionalities (e.g. automatic correction tools). [\texttt{Pluggability}]
+\item Possibility for users to hide personal data (such as my telephone number). [\texttt{Hidden Phone Number}]
+\item Not having to worry about maintenance and that it is easily sustainable from one year to the next. [\texttt{Sustainability}]
+\item That it offers the chance to extract data to assess the student performance. [\texttt{Analytics}]
+\end{itemize}
+
 \end{backmatter}

### 2021-07-28 edubots_surveys.Rnw
Made double blind

@@
 \author[
-  addressref={aff1},                  
-  corref={aff1},                      
-  email={jmerelo@ugr.es}  
-]{\inits{JJM}\fnm{Juan J.} \snm{Merelo}}
+   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
+   corref={aff1},                       % id of corresponding address, if any
+   noteref={n1},                        % id's of article notes, if any
+   email={jane.e.doe@cambridge.co.uk}   % email address
+]{\inits{JE}\fnm{Jane E} \snm{Doe}}
 \author[
-  addressref={aff1},
-  email={pacv@ugr.es}
-]{\inits{PAC}\fnm{Pedro A.} \snm{Castillo}}
-\author[
-  addressref={aff2},
-  email={amorag@ugr.es}
-]{\inits{AMM}\fnm{Antonio M.} \snm{Mora}}
-\author[
-  addressref={aff1},
-  email={fbarranco@ugr.es}
-]{\inits{FB}\fnm{Francisco} \snm{Barranco}}
-\author[
-  addressref={aff3},
-  email={n.h.abbas@leeds.ac.uk}
-]{\inits{NA}\fnm{Noorhan} \snm{Abbas}}
-\author[
-  addressref={aff1},
-  email={aguillen@ugr.es}
-]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
-\author[
-  addressref={aff4},
-  email={o.tsivitanidou@cyens.org.cy}
-]{\inits{OT}\fnm{Olia} \snm{Tsivitanidou}}
-
-\address[id=aff1]{%                           
-  \orgdiv{Department of Computer Architecture and Technology},           
-  \orgname{University of Granada},
-  \city{Granada},
-  \cny{Spain}
+   addressref={aff1,aff2},
+   email={john.RS.Smith@cambridge.co.uk}
+]{\inits{JRS}\fnm{John RS} \snm{Smith}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the authors' addresses here        %%
+%%                                          %%
+%% Repeat \address commands as much as      %%
+%% required.                                %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\address[id=aff1]{%                           % unique id
+  \orgname{Department of Zoology, Cambridge}, % university, etc
+  \street{Waterloo Road},                     %
+  %\postcode{}                                % post or zip code
+  \city{London},                              % city
+  \cny{UK}                                    % country
 }
 \address[id=aff2]{%
-  \orgdiv{Department of Signal Theory, Telematics and Communications},
-  \orgname{University of Granada},
-  \city{Granada},
-  \cny{Spain}
+  \orgname{Marine Ecology Department, Institute of Marine Sciences Kiel},
+  \street{D\"{u}sternbrooker Weg 20},
+  \postcode{24105}
+  \city{Kiel},
+  \cny{Germany}
 }
-\address[id=aff3]{%
-  \orgdiv{School of Computing},
-  \orgname{University of Leeds},
-  \city{Leeds},
-  \cny{UK}
-}
-\address[id=aff4]{%
-  \orgname{CYENS},         
-  \city{Nicosia},
-  \cny{Cyprus} 
-}
+
+% \author[
+%   addressref={aff1},                  
+%   corref={aff1},                      
+%   email={jmerelo@ugr.es}  
+% ]{\inits{JJM}\fnm{Juan J.} \snm{Merelo}}
+% \author[
+%   addressref={aff1},
+%   email={pacv@ugr.es}
+% ]{\inits{PAC}\fnm{Pedro A.} \snm{Castillo}}
+% \author[
+%   addressref={aff2},
+%   email={amorag@ugr.es}
+% ]{\inits{AMM}\fnm{Antonio M.} \snm{Mora}}
+% \author[
+%   addressref={aff1},
+%   email={fbarranco@ugr.es}
+% ]{\inits{FB}\fnm{Francisco} \snm{Barranco}}
+% \author[
+%   addressref={aff3},
+%   email={n.h.abbas@leeds.ac.uk}
+% ]{\inits{NA}\fnm{Noorhan} \snm{Abbas}}
+% \author[
+%   addressref={aff1},
+%   email={aguillen@ugr.es}
+% ]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
+% \author[
+%   addressref={aff4},
+%   email={o.tsivitanidou@cyens.org.cy}
+% ]{\inits{OT}\fnm{Olia} \snm{Tsivitanidou}}
+% 
+% \address[id=aff1]{%                           
+%   \orgdiv{Department of Computer Architecture and Technology},           
+%   \orgname{University of Granada},
+%   \city{Granada},
+%   \cny{Spain}
+% }
+% \address[id=aff2]{%
+%   \orgdiv{Department of Signal Theory, Telematics and Communications},
+%   \orgname{University of Granada},
+%   \city{Granada},
+%   \cny{Spain}
+% }
+% \address[id=aff3]{%
+%   \orgdiv{School of Computing},
+%   \orgname{University of Leeds},
+%   \city{Leeds},
+%   \cny{UK}
+% }
+% \address[id=aff4]{%
+%   \orgname{CYENS},         
+%   \city{Nicosia},
+%   \cny{Cyprus} 
+% }
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The datasets generated and analysed during the current study are available in the {\tt edubots-paper} repository, accessible from {\tt https://github.com/JJ/edubots-paper/tree/main/data}.
+The datasets generated and analysed during the current study are available in the {\tt edubots-paper} repository, accessible from https://anonymous.url
+% {\tt https://github.com/JJ/edubots-paper/tree/main/data}.
 
@@
 
-All the authors have contributed to the study presented in this manuscript.
-
-JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
-
-PAC has revised the paper and researched the state of the art, as well as contributed to the survey design.
-AMM has revised the paper and researched the state of the art, as well as contributed to the survey design.
-FB has made the analysis and processed data and contributed to the survey design.
-NA has supervised the state of the art, and written the bulk of it, as well as contributed to discussion and conclusions.
-OT has performed data analysis, and contributed to discussion and conclusions.
-AG has contributed to the design of the survey, analysis, discussion and conclusions.
+All the authors have contributed to the study presented in this manuscript. (Rest hidden for double blind)
+
+% JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
+% 
+% PAC has revised the paper and researched the state of the art, as well as contributed to the survey design.
+% AMM has revised the paper and researched the state of the art, as well as contributed to the survey design.
+% FB has made the analysis and processed data and contributed to the survey design.
+% NA has supervised the state of the art, and written the bulk of it, as well as contributed to discussion and conclusions.
+% OT has performed data analysis, and contributed to discussion and conclusions.
+% AG has contributed to the design of the survey, analysis, discussion and conclusions.
 

### 2021-07-29 edubots_surveys.Rnw
Fix problems indicated by editor

@@
 
-\section{Declarations}
-\label{sec:decl}
-
-\subsection{Availability of data and materials}
-
-The datasets generated and analysed during the current study are available in the {\tt edubots-paper} repository, accessible from https://anonymous.url
-% {\tt https://github.com/JJ/edubots-paper/tree/main/data}.
-
-\subsection{Competing interests}
-
-The authors declare that they have no competing interests.
-
-\subsection{Funding}
-
-This work has been supported by EDUBOTS project, funded under the scheme Erasmus + KA2: Cooperation for innovation and the exchange of good practices - Knowledge Alliances (grant agreement no: 612446).
-
-\subsection{Authors' contributions}
-
-All the authors have contributed to the study presented in this manuscript. (Rest hidden for double blind)
-
+% \section{Declarations}
+% \label{sec:decl}
+% 
+% \subsection{Availability of data and materials}
+% 
+% The datasets generated and analysed during the current study are available in the {\tt edubots-paper} repository, accessible from https://anonymous.url
+% % {\tt https://github.com/JJ/edubots-paper/tree/main/data}.
+% 
+% 
+% \subsection{Competing interests}
+% 
+% The authors declare that they have no competing interests.
+% 
+% 
+% \subsection{Funding}
+% 
+% This work has been supported by EDUBOTS project, funded under the scheme Erasmus + KA2: Cooperation for innovation and the exchange of good practices - Knowledge Alliances (grant agreement no: 612446).
+% 
+% \subsection{Authors' contributions}
+% 
+% All the authors have contributed to the study presented in this manuscript. (Rest hidden for double blind)
+% 
 % JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
@@
 % AG has contributed to the design of the survey, analysis, discussion and conclusions.
-
-All authors have read and approved the final manuscript.
-
-\subsection{Acknowledgements}
-
-The authors want to thank to the educators who participated in the survey, and also people who have distributed the survey in their mailing lists, especially Mario García Valdez, Jesús Moreno León and José Raúl Canay.
-% Antonio - Add other acknowledgements
+% 
+% All authors have read and approved the final manuscript.
+% 
+% \subsection{Acknowledgements}
+% 
+% The authors want to thank to the educators who participated in the survey, and also people who have distributed the survey in their mailing lists, especially Mario García Valdez, Jesús Moreno León and José Raúl Canay.
+% % Antonio - Add other acknowledgements
 

### 2021-07-30 edubots_surveys.Rnw
Anonymized throughout

@@
 
-Given the potential benefits that chatbots could bring to the classroom, the focus of the EDUBOTS KA2 European project \footnote{https://www.edubots.eu}, the sponsor of this study, is to gather, analyse and disseminate best practices on the use of chatbots in higher education institutions.
+Given the potential benefits that chatbots could bring to the classroom, the focus of the 
+% EDUBOTS KA2 European project \footnote{https://www.edubots.eu}, 
+{\sf anonymized European Project}, the sponsor of this study, is to gather, analyse and disseminate best practices on the use of chatbots in higher education institutions.
 
@@
  \begin{itemize}
-\item The first phase aimed to collect feedback from students about their actual needs \cite{MoraChatbots2021}.
+\item The first phase aimed to collect feedback from students about their actual needs \cite{MoraChatbots2021:anon}.
 Hence, the objective was to collect information about students’ preferences of tools/applications for chatting and messaging, how they use them in educational context, who do they like to be with in the class messaging groups, and their expectations of the chatbots in terms of assisting them during their learning process.
@@
 
-Along this line of research, our previous work \cite{MoraChatbots2021} aimed at analysing the expectations of students on this regard; recent papers have also analysed how the use of chatbots affected the learning outcomes of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
+Along this line of research, our previous work \cite{MoraChatbots2021:anon} aimed at analysing the expectations of students on this regard; recent papers have also analysed how the use of chatbots affected the learning outcomes of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
 This paper analysed conversational chatbots in an one-to-one setting, finding that learning really benefited from it.
@@
 In doing so, an online survey was administered (i.e., Google Form), in Spanish, which was intended to be answered in a very short amount of time.
-Initially, our intention was to mirror the questions used in \cite{MoraChatbots2021};
+Initially, our intention was to mirror the questions used in \cite{MoraChatbots2021:anon};
 % Antonio - I would say something like: "but from teachers' perspective"

### 2021-07-30 edubots_surveys.Rnw
Making it use the same directory for figures or it will not find them

@@
 <<setup, echo=FALSE,message=FALSE>>=
+knitr::opts_chunk$set(fig.path='figures/')
 library(ggplot2)

### 2021-08-16 edubots_surveys.Rnw
Move figures to same place
Removed all author information, including boilerplate

@@
 \title{Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective}
-
-\author[
-   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
-   corref={aff1},                       % id of corresponding address, if any
-   noteref={n1},                        % id's of article notes, if any
-   email={jane.e.doe@cambridge.co.uk}   % email address
-]{\inits{JE}\fnm{Jane E} \snm{Doe}}
-\author[
-   addressref={aff1,aff2},
-   email={john.RS.Smith@cambridge.co.uk}
-]{\inits{JRS}\fnm{John RS} \snm{Smith}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Enter the authors' addresses here        %%
-%%                                          %%
-%% Repeat \address commands as much as      %%
-%% required.                                %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\address[id=aff1]{%                           % unique id
-  \orgname{Department of Zoology, Cambridge}, % university, etc
-  \street{Waterloo Road},                     %
-  %\postcode{}                                % post or zip code
-  \city{London},                              % city
-  \cny{UK}                                    % country
-}
-\address[id=aff2]{%
-  \orgname{Marine Ecology Department, Institute of Marine Sciences Kiel},
-  \street{D\"{u}sternbrooker Weg 20},
-  \postcode{24105}
-  \city{Kiel},
-  \cny{Germany}
-}
 
@@
 \begin{center}
-\includegraphics[width=\textwidth]{figure/2clusteranalysis.pdf}
+\includegraphics[width=\textwidth]{figures/2clusteranalysis.pdf}
 \end{center}

### 2021-11-04 edubots_surveys.Rnw
Add clarification
Changed adapted to adopted
Update edubots_surveys.Rnw

@@
 
+% Remember to substitute figures/ by nothing in the generated PDF
 % \author[
@@
 
-% TODO: introduction
 The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new skills by both.
-Some technologies are readily adapted, but others require longer time for full adoption.
+Some technologies are readily adopted, but others require longer time for full adoption.
 In most cases, the magnitude of the uptake of the new technology impinges on the collaboration of all the parties using it.
-Hence, examining the users’ opinions and their opinions is an important first step in boosting this collaboration and reaping the benefits of the technology.
+Hence, examining the users’ opinions and
+is an important first step in boosting this collaboration and reaping the benefits of the technology.
 Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp, Telegram and Facebook Messenger took place.

### 2021-11-05 edubots_surveys.Rnw
deleted a comment
Users' opinions
Built-in

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%% start of article main body
-
 <<setup, echo=FALSE,message=FALSE>>=
@@
 Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp, Telegram and Facebook Messenger took place.
-Some messaging applications have built in chatbots that are able to support a synchronous conversation between the different parties \cite{differ.chat}, while other chatbots are developed as standalone systems and can possibly be attached to a messaging application using an API (Application Program Interface).
+Some messaging applications have built-in chatbots to support a synchronous conversation between the different parties \cite{differ.chat}, while other chatbots are developed as standalone systems and can possibly be attached to a messaging application using an API (Application Program Interface).
 

### 2021-11-05 edubots_surveys.Rnw
First sentence in intro

--- 2021-11-04 edubots_surveys.Rnw
@@
 
-The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new skills by both.
+The introduction of new technologies in the classroom, to be successful, involves extra teacher training, devising methods for enhancing student engagment with the new technology and in deed acquiring new skills by both.
 Some technologies are readily adopted, but others require longer time for full adoption.

### 2021-11-05 edubots_surveys.Rnw
Adoption/adaptation sentence changed
Purpose of the study

--- 2021-11-04 edubots_surveys.Rnw
@@
 
-Given the potential benefits that chatbots could bring to the classroom, the focus of the 
-% EDUBOTS KA2 European project \footnote{https://www.edubots.eu}, 
-{\sf anonymized European Project}, the sponsor of this study, is to gather, analyse and disseminate best practices on the use of chatbots in higher education institutions.
-
- The line of research of which this paper is a part has involved two phases of data collection.
+Given the potential benefits that chatbots could bring to the classroom, the focus of the % EDUBOTS KA2 European project \footnote{https://www.edubots.eu}, 
+{\sf anonymized European Project}, the sponsor of this study, is to explore best practices and innovative use of chatbots, and to create a learning 
+community of educators in higher education institutions. The majority of studies conducted so far have studied how these 
+messaging applications and/or chatbots are used to deliver persosnalised learning in classrooms that occurs anytime anywhere, 
+promote collaborative learning experiences, group discussions \cite{panah2020study} and for boosting students' sense of belonging to their 
+institutions\cite{abbas2021onlinechat}. Hence, due to the paucity of research that explores the use of these technologies from the teachers' perspectives,
+this paper aims to investigate their opinions/needs and the challenges/opportunities of adopting these technologies in classrooms
+to paint a better picture of how they can positively contribute to enhancing the learning process in higher education institutions.
+In this study, data collection involved two phases:
  \begin{itemize}

### 2021-11-05 edubots_surveys.Rnw
Correcting students' survey

--- 2021-11-05 edubots_surveys.Rnw
@@
 Therefore, two surveys for bachelor and master degree students at the University of Granada (Spain) were designed and answers from more than 250 students were collected.
-The key findings of the students surveys reveal that they prefer to use messaging applications, such as Telegram or WhatsApp as they are familiar to them.
+The key findings of the students' surveys reveal that they prefer to use messaging applications, such as Telegram or WhatsApp as they are familiar to them.
 Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course's resources.
@@
 
-Initially, a single survey was developed for this purpose.
-Responses from 300 teachers were collected and analysed.
-An initial analysis of these responses led to the creation of a second survey, which collected responses from 200 different higher education teachers.
-The questions on this survey focus on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:
+Initially, a single survey was developed for this purpose and responses from 300 higher education teachers were collected and analysed. 
+The responses' analysis entailed the creation of a second survey to which 200 teachers' responses were collected. The questions of the second 
+survey focussed on discussing teachers' needs, opinions and preferences of the development of future technology-enhanced tools 
+and its potential impact on educational institutions’ policies. Therefore, this paper investigated the following research questions:
 
@@
 \item RQ1 - Are teachers already using messaging apps in their classes? 
-\item RQ2 - Which kind of chatbots would teachers find useful in their classes? 
+\item RQ2 - Which chatbots' features would teachers find useful in their classes? 
 \item RQ3 - Which kind of interaction do teachers prefer with their students?
@@
 % The Use of Chatbots in Higher Education
-The use of MIM, although possibly valuable by itself, can be enhanced via the use of chatbots, which, being conversational agents, usually dwell in systems where synchronous conversations take place. 
+The use of MIM, although possibly valuable by itself, can be enhanced via the use of chatbots, which, being conversational agents, usually dwell
+in systems where synchronous conversations take place. 
 The use of conversational agents (chatbots) in higher education is
@@
 gamification \cite{Yildirim2017} can improve student motivation. In
-this sense, the authors in \cite{Pimmer2019} carried out a series of experiments with
-technological tools whose results showed positive perception and
-acceptance of the use of technology in teaching and learning.
+this sense, the authors in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
+report the positive impact of using instant messaging tools in boosting students' knowledge and mitigating their feelings of isolation.
 
@@
 quality metrics such as language, subject matter and platform. 
-Whereas study \cite{perez2020rediscovering} aimed to categorise educational chatbots according to their
+Whereas the study undertaken by \cite{perez2020rediscovering} aimed to categorise educational chatbots according to their
 purpose into service-oriented and teaching-oriented. The first category includes those that
@@
 Therefore, to develop efficient chatbots for higher education, all stakeholders'
-(i.e. educators, students, institutions, etc) expectations needs to be
+(i.e. educators, students, institutions, etc) needs should be
 carefully collected and taken into consideration
@@
 %Why messaging apps are relevant here --> connect to the development of chatbots
-Group messaging apps have become a powerful tool for keeping touch with students.
-Also, they are the baseline platform for the development of chatbots to help with the learning process.
-After an initial analysis to the answers to the first survey, we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally piggybacks on another, messaging applications.
+Group messaging apps have become a powerful tool for keeping touch with students. Also, many of them have built-in chatbots 
+to enhance the learning process. After an initial analysis to the answers to the first survey, 
+we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally 
+piggybacks on another, messaging applications.
 In a technology adoption model, perceived ease of use and perceived usefulness are essential.
@@
 In this case, it is maybe in order a certain clarification.
-While we had in mind, as indicated by the possible answers, instant messaging applications when making this question, we included these institution-provided applications mainly for completitude.
+While we had in mind, as indicated by the possible answers, instant messaging applications when making this question, we included these institution-provided applications mainly for completion.
 But it should be noted that, in most cases, they are not {\em instant} messaging apps in the way Telegram or Facebook Messenger are; in most cases they are messaging facilities provided by learning management systems such as (usually) Moodle.

### 2021-11-05 edubots_surveys.Rnw
Correcting students' survey

--- 2021-11-05 edubots_surveys.Rnw
@@
 
-The introduction of new technologies in the classroom, to be successful, involves extra teacher training, devising methods for enhancing student engagment with the new technology and in deed acquiring new skills by both.
+The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new skills by both.
 Some technologies are readily adopted, but others require longer time for full adoption.

### 2021-11-05 edubots_surveys.Rnw
Research questions

--- 2021-11-05 edubots_surveys.Rnw
@@
 Therefore, two surveys for bachelor and master degree students at the University of Granada (Spain) were designed and answers from more than 250 students were collected.
-The key findings of the students' surveys reveal that they prefer to use messaging applications, such as Telegram or WhatsApp as they are familiar to them.
+The key findings of the students surveys reveal that they prefer to use messaging applications, such as Telegram or WhatsApp as they are familiar to them.
 Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course's resources.
@@
 survey focussed on discussing teachers' needs, opinions and preferences of the development of future technology-enhanced tools 
-and its potential impact on educational institutions’ policies. Therefore, this paper investigated the following research questions:
+and its' potential impact on educational institutions’ policies. Therefore, this paper investigated the following research questions:
 

### 2021-11-05 edubots_surveys.Rnw
Research questions

--- 2021-11-05 edubots_surveys.Rnw
@@
 
-Initially, a single survey was developed for this purpose.
-Responses from 300 teachers were collected and analysed.
-An initial analysis of these responses led to the creation of a second survey, which collected responses from 200 different higher education teachers.
-The questions on this survey focus on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:
+Initially, a single survey was developed for this purpose and responses from 300 higher education teachers were collected and analysed. 
+The responses' analysis entailed the creation of a second survey to which 200 teachers' responses were collected. The questions of the second 
+survey focussed on discussing teachers' needs, opinions and preferences of the development of future technology-enhanced tools 
+and its' potential impact on educational institutions’ policies. Therefore, this paper investigated the following research questions:
 

### 2021-11-05 edubots_surveys.Rnw
give assignments' feedback

--- 2021-11-05 edubots_surveys.Rnw
@@
 
-The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new skills by both.
+The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new 
+skills by both.
 Some technologies are readily adopted, but others require longer time for full adoption.
@@
 
-We will try to answer these questions through the analysis of questions and answers in the two surveys.
-Eventually, what we want to obtain is a series of recommendations to make a successful deployment of chatbot technologies (and, in some cases, general instant messaging applications) in higher education.
+We will try to answer these questions through the analysis of questions and answers in the two surveys. Eventually, what we want 
+to obtain is a series of recommendations to make a successful deployment of chatbot technologies (and, in some cases, general instant messaging 
+applications) in higher education.
 
@@
 WhatsApp is, at least in most Western countries,
-the most popular MIM platform used by educators to give assignments'
+the most popular MIM platform used by educators to provide assignments'
 feedback to students, support course discussions, and provide learning

### 2021-11-05 edubots_surveys.Rnw
Pimmer et al. update in the literature review section

--- 2021-11-05 edubots_surveys.Rnw
@@
 
-Initially, a single survey was developed for this purpose and responses from 300 higher education teachers were collected and analysed. 
-The responses' analysis entailed the creation of a second survey to which 200 teachers' responses were collected. The questions of the second 
-survey focussed on discussing teachers' needs, opinions and preferences of the development of future technology-enhanced tools 
-and its' potential impact on educational institutions’ policies. Therefore, this paper investigated the following research questions:
+Initially, a single survey was developed for this purpose.
+Responses from 300 teachers were collected and analysed.
+An initial analysis of these responses led to the creation of a second survey, which collected responses from 200 different higher education teachers.
+The questions on this survey focus on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:
 
@@
 \item RQ1 - Are teachers already using messaging apps in their classes? 
-\item RQ2 - Which chatbots' features would teachers find useful in their classes? 
+\item RQ2 - Which kind of chatbots would teachers find useful in their classes? 
 \item RQ3 - Which kind of interaction do teachers prefer with their students?

### 2021-11-05 edubots_surveys.Rnw
Pimmer et al. update in the literature review section

--- 2021-11-05 edubots_surveys.Rnw
@@
 
-The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new 
-skills by both.
+The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new skills by both.
 Some technologies are readily adopted, but others require longer time for full adoption.
@@
 
-We will try to answer these questions through the analysis of questions and answers in the two surveys. Eventually, what we want 
-to obtain is a series of recommendations to make a successful deployment of chatbot technologies (and, in some cases, general instant messaging 
-applications) in higher education.
+We will try to answer these questions through the analysis of questions and answers in the two surveys.
+Eventually, what we want to obtain is a series of recommendations to make a successful deployment of chatbot technologies (and, in some cases, general instant messaging applications) in higher education.
 
@@
 WhatsApp is, at least in most Western countries,
-the most popular MIM platform used by educators to provide assignments'
+the most popular MIM platform used by educators to give assignments'
 feedback to students, support course discussions, and provide learning

### 2021-11-05 edubots_surveys.Rnw
study [Pérez..." ] fixed

@@
 % The Use of Chatbots in Higher Education
-The use of MIM, although possibly valuable by itself, can be enhanced via the use of chatbots, which, being conversational agents, usually dwell
-in systems where synchronous conversations take place. 
+The use of MIM, although possibly valuable by itself, can be enhanced via the use of chatbots, which, being conversational agents, usually dwell in systems where synchronous conversations take place. 
 The use of conversational agents (chatbots) in higher education is
@@
 gamification \cite{Yildirim2017} can improve student motivation. In
-this sense, the authors in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
-report the positive impact of using instant messaging tools in boosting students' knowledge and mitigating their feelings of isolation.
+this sense, the authors in \cite{Pimmer2019} carried out a series of experiments with
+technological tools whose results showed positive perception and
+acceptance of the use of technology in teaching and learning.
 

### 2021-11-05 edubots_surveys.Rnw
efficient chatbots changed to effective

--- 2021-11-05 edubots_surveys.Rnw
@@
 quality metrics such as language, subject matter and platform. 
-Whereas the study undertaken by \cite{perez2020rediscovering} aimed to categorise educational chatbots according to their
+Whereas study \cite{perez2020rediscovering} aimed to categorise educational chatbots according to their
 purpose into service-oriented and teaching-oriented. The first category includes those that
@@
 specific pedagogical factors such as learning success or increased motivation are more important.  
-Therefore, to develop efficient chatbots for higher education, all stakeholders'
+Therefore, to develop effective chatbots for higher education, all stakeholders'
 (i.e. educators, students, institutions, etc) expectations needs to be

### 2021-11-05 edubots_surveys.Rnw
expectations needs [fixed]

@@
 specific pedagogical factors such as learning success or increased motivation are more important.  
-Therefore, to develop effective chatbots for higher education, all stakeholders'
-(i.e. educators, students, institutions, etc) expectations needs to be
+Therefore, to develop efficient chatbots for higher education, all stakeholders'
+(i.e. educators, students, institutions, etc) needs should be
 carefully collected and taken into consideration

### 2021-11-05 edubots_surveys.Rnw
Rephrasing of the attitudes
Rephrased the last paragraph in the state of the art section to avoid the multiple use of opinions and clarify the use of attitudes in the TAM study.

--- 2021-11-05 edubots_surveys.Rnw
@@
 progress. For instance, \cite{fernoagua2018intelligent} reported on
-``eduAssistant'', a virtual teaching assistant chatbot developed on the
-Telegram messaging platform. In this study, Telegram platform was
+''eduAssistant'', a virtual teaching assistant chatbot developed on the
+Telegram messaging platform. In this study, Telegram platform is
 chosen because it is easy to use, students are familiar with its
@@
 addition, Telegram could operate on all devices and operating
-systems. The ``eduAssistant'' chatbot acts as an automatic agent
+systems. The ''eduAssistant'' chatbot acts as an automatic agent
 in teacher-content-student, facilitating real-time feedback
@@
 educator's dashboard \cite{fernoagua2018intelligent}. This can help 
-educators to locate those students that need their attention and send to 
+educators locate those students that need more attention and send
 them more educational resources relevant to their academic attainment.
+In addition, a recent study has analysed how the use of chatbots positively affected the learning outcomes of students in a Chinese 
+class \cite{doi:10.1177/0735633120929622}.
 
@@
 higher education is a special domain where, according to Hobert \cite{hobert2019you}, 
-specific pedagogical factors such as learning success or increased motivation are more important.  
+specific pedagogical factors such as learning success and increased motivation are more important.  
 Therefore, to develop efficient chatbots for higher education, all stakeholders'
-(i.e. educators, students, institutions, etc) needs should be
-carefully collected and taken into consideration
-\cite{sjostrom2018designing,tsivitanidouusers}.
-
-Along this line of research, our previous work \cite{MoraChatbots2021:anon} aimed at analysing the expectations of students on this regard; recent papers have also analysed how the use of chatbots affected the learning outcomes of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
-This paper analysed conversational chatbots in an one-to-one setting, finding that learning really benefited from it.
-This is, once again, a proof of the benefit of chatbots in certain settings; however, there are some opinions that might prevent the successful acceptance of the technology, and these are what we are trying to find out in this paper, together with what kind of features would make its acceptance better.
-
-Besides, the present work is focused on the other key actor in this challenge, i.e.
-educators.
-Their attitudes have been studied very recently by Chocarro et al.
-\cite{doi:10.1080/03055698.2020.1850426}, who, by analysing surveys, created a {\em technology acceptance model} that proposed a series of features that would make chatbots easier to accept; among them, formality of language as well as easiness and usefulness.
-The survey targeted primary and secondary education teachers, and was also more interested in the general use of chatbots in education, not specifically in a classroom setting, seeking educational outcomes.
-However, they establish a series of results that are obviously interesting and relevant for this work.
-
-We will present next the methodology we have followed to find out teachers' opinions.
+(i.e. educators, students, institutions, etc) expectations needs to be
+carefully collected and taken into consideration \cite{sjostrom2018designing,tsivitanidouusers}. 
+As our previous work \cite{MoraChatbots2021:anon} aimed to present a detailed analysis of students' expectations and needs in this regard, the
+present study focuses on investigating the needs of educators. In a recent study, Chocarro et al. \cite{doi:10.1080/03055698.2020.1850426} 
+examined educators' acceptance of chatbots using TAM (Technology Acceptance Model) and proposed a series of features such as formality
+ of language as well as usefulness to make chatbots easier to adopt.
+
+In the next section, we will present the methodology adopted to collect teachers' responses.
 

### 2021-11-05 edubots_surveys.Rnw
keeping touch [fixed]

--- 2021-11-05 edubots_surveys.Rnw
@@
 Therefore, to develop efficient chatbots for higher education, all stakeholders'
-(i.e. educators, students, institutions, etc) needs should be
+(i.e. educators, students, institutions, etc) expectations needs to be
 carefully collected and taken into consideration
@@
 %Why messaging apps are relevant here --> connect to the development of chatbots
-Group messaging apps have become a powerful tool for keeping touch with students.
-Also, they are the baseline platform for the development of chatbots to help with the learning process.
+Group messaging apps have become a powerful tool to communicate with students. Also, they are the baseline platform for the development of 
+chatbots to help with the learning process.
 After an initial analysis to the answers to the first survey, we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally piggybacks on another, messaging applications.

### 2021-11-05 edubots_surveys.Rnw
They are the baseline....

@@
 %Why messaging apps are relevant here --> connect to the development of chatbots
-Group messaging apps have become a powerful tool to communicate with students. Also, they are the baseline platform for the development of 
-chatbots to help with the learning process.
-After an initial analysis to the answers to the first survey, we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally piggybacks on another, messaging applications.
+Group messaging apps have become a powerful tool for keeping touch with students. Also, many of them have built-in chatbots 
+to enhance the learning process. After an initial analysis to the answers to the first survey, 
+we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally 
+piggybacks on another, messaging applications.
 In a technology adoption model, perceived ease of use and perceived usefulness are essential.

### 2021-11-05 edubots_surveys.Rnw
complititude [fixed]

--- 2021-11-05 edubots_surveys.Rnw
@@
 %Why messaging apps are relevant here --> connect to the development of chatbots
-Group messaging apps have become a powerful tool to communicate with students. Also, they are the baseline platform for the development of 
-chatbots to help with the learning process.
+Group messaging apps have become a powerful tool for keeping touch with students.
+Also, they are the baseline platform for the development of chatbots to help with the learning process.
 After an initial analysis to the answers to the first survey, we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally piggybacks on another, messaging applications.

### 2021-11-07 edubots_surveys.Rnw
Typo

--- 2021-11-05 edubots_surveys.Rnw
@@
 
-The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new skills by both.
+The introduction of new technologies in the classroom, to be successful, involves extra teacher training, devising methods for enhancing student engagement with the new technology and in deed acquiring new skills by both.
 Some technologies are readily adopted, but others require longer time for full adoption.
@@
 %Why messaging apps are relevant here --> connect to the development of chatbots
-Group messaging apps have become a powerful tool for keeping touch with students. Also, many of them have built-in chatbots 
-to enhance the learning process. After an initial analysis to the answers to the first survey, 
-we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally 
-piggybacks on another, messaging applications.
+Group messaging apps have become a powerful tool for keeping touch with students.
+Also, they are the baseline platform for the development of chatbots to help with the learning process.
+After an initial analysis to the answers to the first survey, we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally piggybacks on another, messaging applications.
 In a technology adoption model, perceived ease of use and perceived usefulness are essential.

### 2021-11-07 edubots_surveys.Rnw
typo

@@
 
-The introduction of new technologies in the classroom, to be successful, involves extra teacher training, devising methods for enhancing student engagement with the new technology and in deed acquiring new skills by both.
+The introduction of new technologies in the classroom, to be successful, involves extra teacher training, devising methods for enhancing student engagement with the new technology and indeed acquiring new skills by both.
 Some technologies are readily adopted, but others require longer time for full adoption.

### 2021-11-07 edubots_surveys.Rnw
typo

--- 2021-11-07 edubots_surveys.Rnw
@@
 
-The introduction of new technologies in the classroom, to be successful, involves extra teacher training, devising methods for enhancing student engagement with the new technology and indeed acquiring new skills by both.
+The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new skills by both.
 Some technologies are readily adopted, but others require longer time for full adoption.

### 2021-11-08 edubots_surveys.Rnw
Some comments deleted, also reflow #50

--- 2021-11-07 edubots_surveys.Rnw
@@
 \begin{abstract} % abstract
-Introducing new technologies such as messaging platforms, and the chatbots attached to them, in higher education, is rapidly growing.
-This introduction entails a careful consideration of the potential opportunities and/or challenges of adopting these tools.
-Hence, a thorough examination of the teachers’ experiences in this discipline can shed the light on the effective ways of enhancing students’ learning and boosting their progress.
-In this contribution, we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish-speaking countries.
-The focus of these surveys is to collect teachers’ feedback about their opinions of the introduction of the messaging platforms and chatbots in their classes, understand their needs and to gather information about the various educational use cases where these tools are valuable.
-In addition, an analysis of how and when teachers’ opinions towards the use of these tools can vary across gender, experience, and their discipline of specialisation is presented.
-The key findings of this study highlight the factors that can contribute to the advancement of the adoption of messaging platforms and chatbots in higher education institutions to achieve the desired learning outcomes.
+Introducing new technologies such as messaging platforms, and the chatbots
+attached to them, in higher education, is rapidly growing. This introduction
+entails a careful consideration of the potential opportunities and/or challenges
+of adopting these tools. Hence, a thorough examination of the teachers’
+experiences in this discipline can shed the light on the effective ways of
+enhancing students’ learning and boosting their progress. In this contribution,
+we have surveyed the opinions of tertiary education teachers based mainly in
+Spain and Spanish-speaking countries. The focus of these surveys is to collect
+teachers’ feedback about their opinions of the introduction of the messaging
+platforms and chatbots in their classes, understand their needs and to gather
+information about the various educational use cases where these tools are
+valuable. In addition, an analysis of how and when teachers’ opinions towards
+the use of these tools can vary across gender, experience, and their discipline
+of specialisation is presented. The key findings of this study highlight the
+factors that can contribute to the advancement of the adoption of messaging
+platforms and chatbots in higher education institutions to achieve the desired
+learning outcomes.
 \end{abstract}
@@
 
-The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new skills by both.
-Some technologies are readily adopted, but others require longer time for full adoption.
-In most cases, the magnitude of the uptake of the new technology impinges on the collaboration of all the parties using it.
-Hence, examining the users’ opinions and
-is an important first step in boosting this collaboration and reaping the benefits of the technology.
-Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp, Telegram and Facebook Messenger took place.
-Some messaging applications have built-in chatbots to support a synchronous conversation between the different parties \cite{differ.chat}, while other chatbots are developed as standalone systems and can possibly be attached to a messaging application using an API (Application Program Interface).
-
-A \textit{chatbot} is a program, sometimes developed using Artificial Intelligence techniques, able to communicate in a similar way as humans do \cite{Gong2008}, using, in some cases, natural language.
-Indeed, most of these applications would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any question fluently, and even pose own questions in their conversations.
-The recent advancement in this discipline has played an important role in many fields especially in education and online tutoring \cite{clarizia2018,Smutny2020}.
-These automatic systems facilitate the delivery of personalized learning by adapting to students’ pace of learning and providing customized online tutoring outside the classroom.
-Thus, chatbots can significantly contribute to providing interactive learning experiences as well as improving individual attention \cite{agarwal2020}.
- In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor.
-In fact, in many cases, some students experience stress because of their need to ask a question in front of the entire class.
-This is why many students resort to silence
- % Antonio - I guess refrain to silence is the opposite of what we wanted to say, isn't it? :D
- % mistaking "resort" for "refrain". You don't say "refrain to", but refrain from.
- in the classroom and tend to contact their teachers later via email.
- Consequently, this can lead to not only a delay in obtaining answers to their questions but can also cause a significant increase in their teachers’ workload, especially when factoring in the disproportion between the class size and the number of teachers.
-Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning experience \cite{Griol2014,kim2020}.
-In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding.
-
-Given the potential benefits that chatbots could bring to the classroom, the focus of the 
+The introduction of new technologies in the classroom involves a combination of
+teacher training, student enthusiasm and possibly acquiring new skills by
+both. Some technologies are readily adopted, but others require longer time for
+full adoption. In most cases, the magnitude of the uptake of the new technology
+impinges on the collaboration of all the parties using it. Hence, examining the
+users’ opinions and is an important first step in boosting this collaboration
+and reaping the benefits of the technology.  Recently, a surge in the use of
+synchronous instant messaging tools in higher education such as WhatsApp,
+Telegram and Facebook Messenger took place. Some messaging applications have
+built-in chatbots to support a synchronous conversation between the different
+parties \cite{differ.chat}, while other chatbots are developed as standalone
+systems and can possibly be attached to a messaging application using an API
+(Application Program Interface).
+
+A \textit{chatbot} is a program, sometimes developed using Artificial
+Intelligence techniques, able to communicate in a similar way as humans do
+\cite{Gong2008}, using, in some cases, natural language. Indeed, most of these
+applications would be, apparently, close to passing a classic Turing test
+\cite{moor2003turing}, since they are able to answer almost any question
+fluently, and even pose own questions in their conversations. The recent
+advancement in this discipline has played an important role in many fields
+especially in education and online tutoring
+\cite{clarizia2018,Smutny2020}. These automatic systems facilitate the delivery
+of personalized learning by adapting to students’ pace of learning and providing
+customized online tutoring outside the classroom. Thus, chatbots can
+significantly contribute to providing interactive learning experiences as well
+as improving individual attention \cite{agarwal2020}.  In this sense, chatbot
+technology offers a great opportunity for the improvement of tutoring systems
+\cite{Daniel2016,agarwal2020}, as not all students are comfortable with
+face-to-face tutoring with the instructor. In fact, in many cases, some students
+experience stress because of their need to ask a question in front of the entire
+class. This is why many students resort to silence in the classroom and tend to
+contact their teachers later via email.  Consequently, this can lead to not only
+a delay in obtaining answers to their questions but can also cause a significant
+increase in their teachers’ workload, especially when factoring in the
+disproportion between the class size and the number of teachers. Hence, the
+chatbot technology has a potential to mitigate this problem by providing answers
+to students’ questions and facilitating a dynamic and autonomous learning
+experience \cite{Griol2014,kim2020}. In addition, using an automated system such
+as a chatbot, can draw teachers’ attention to topics that students struggle to
+comprehend or need further assistance in understanding.
+
+Given the potential benefits that chatbots could bring to the classroom, the
+focus of the
 % EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
-{\sf anonymized European Project}, the sponsor of this study, is to gather, analyse and disseminate best practices on the use of chatbots in higher education institutions.
-
- The line of research of which this paper is a part has involved two phases of data collection.
+{\sf anonymized European Project}, the sponsor of this study, is to gather,
+analyse and disseminate best practices on the use of chatbots in higher
+education institutions.
+
+ The line of research of which this paper is a part has involved two phases of
+ data collection.
  \begin{itemize}
-\item The first phase aimed to collect feedback from students about their actual needs \cite{MoraChatbots2021:anon}.
-Hence, the objective was to collect information about students’ preferences of tools/applications for chatting and messaging, how they use them in educational context, who do they like to be with in the class messaging groups, and their expectations of the chatbots in terms of assisting them during their learning process.
-Therefore, two surveys for bachelor and master degree students at the University of Granada (Spain) were designed and answers from more than 250 students were collected.
-The key findings of the students surveys reveal that they prefer to use messaging applications, such as Telegram or WhatsApp as they are familiar to them.
-Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course's resources.
-\item The results of the first phase were fed into the second phase of the study, which focused on teachers’ opinions about using chatbots and messaging applications in classes.
-This is what is going to be presented in this paper.
+\item The first phase aimed to collect feedback from students about their actual
+  needs \cite{MoraChatbots2021:anon}. Hence, the objective was to collect
+  information about students’ preferences of tools/applications for chatting and
+  messaging, how they use them in educational context, who do they like to be
+  with in the class messaging groups, and their expectations of the chatbots in
+  terms of assisting them during their learning process. Therefore, two surveys
+  for bachelor and master degree students at the University of Granada (Spain)
+  were designed and answers from more than 250 students were collected. The key
+  findings of the students' surveys reveal that they prefer to use messaging
+  applications, such as Telegram or WhatsApp as they are familiar to
+  them. Students also expressed interest in chatbots that can assist them with
+  organizing their course schedules, help them access their assignment grades
+  and facilitate searching for course's resources.
+\item The results of the first phase were fed into the second phase of the
+  study, which focused on teachers’ opinions about using chatbots and messaging
+  applications in classes. This is what is going to be presented in this paper.
 \end{itemize}
 
-Initially, a single survey was developed for this purpose and responses from 300 higher education teachers were collected and analysed. 
-The responses' analysis entailed the creation of a second survey to which 200 teachers' responses were collected. The questions of the second 
-survey focussed on discussing teachers' needs, opinions and preferences of the development of future technology-enhanced tools 
-and its potential impact on educational institutions’ policies. Therefore, this paper investigated the following research questions:
+Initially, a single survey was developed for this purpose and responses from 300
+higher education teachers were collected and analysed.  The responses' analysis
+entailed the creation of a second survey to which 200 teachers' responses were
+collected. The questions of the second survey focussed on discussing teachers'
+needs, opinions and preferences of the development of future technology-enhanced
+tools and its potential impact on educational institutions’ policies. Therefore,
+this paper investigated the following research questions:
 
@@
 \item RQ1 - Are teachers already using messaging apps in their classes?
-\item RQ2 - Which chatbots' features would teachers find useful in their classes? 
+\item RQ2 - Which chatbots' features would teachers find useful in their
+  classes?
 \item RQ3 - Which kind of interaction do teachers prefer with their students?
@@
 
-We will try to answer these questions through the analysis of questions and answers in the two surveys.
-Eventually, what we want to obtain is a series of recommendations to make a successful deployment of chatbot technologies (and, in some cases, general instant messaging applications) in higher education.
-
-The remainder of the paper is organized as follows: Next is an overview of what current research has found about the use of messaging applications, including chatbots, in the classroom.
-The methodology used in the surveys is presented in Section \ref{sec:meth}, and the results of the surveys are presented next in Section \ref{sec:res}.
-Finally, we discuss these results and conclude with a series of recommendations in the section that closes the paper.
+We will try to answer these questions through the analysis of questions and
+answers in the two surveys. Eventually, what we want to obtain is a series of
+recommendations to make a successful deployment of chatbot technologies (and, in
+some cases, general instant messaging applications) in higher education.
+
+The remainder of the paper is organized as follows: Next is an overview of what
+current research has found about the use of messaging applications, including
+chatbots, in the classroom. The methodology used in the surveys is presented in
+Section \ref{sec:meth}, and the results of the surveys are presented next in
+Section \ref{sec:res}. Finally, we discuss these results and conclude with a
+series of recommendations in the section that closes the paper.
 
@@
 
-WhatsApp is, at least in most Western countries,
-the most popular MIM platform used by educators to give assignments'
-feedback to students, support course discussions, and provide learning
-resources in informal learning settings \cite{panah2020study}.  Moreover, the
-use of WhatsApp in higher education could enhance social presence
-\cite{tang2017mobile} and foster trust relationships between educators
-and students embedded in the social learning process
+WhatsApp is, at least in most Western countries, the most popular MIM platform
+used by educators to give assignments' feedback to students, support course
+discussions, and provide learning resources in informal learning settings
+\cite{panah2020study}.  Moreover, the use of WhatsApp in higher education could
+enhance social presence \cite{tang2017mobile} and foster trust relationships
+between educators and students embedded in the social learning process
 \cite{gachago2015crossing}; however, this last paper also reflects the need for
@@
 
-Nevertheless, there are challenges when using MIM tools that occur due
-to the blurring of boundaries between academic and private life. This
-can lead to technostress \cite{gachago2015crossing}, difficulty in
-managing responsibilities, especially among mature students, and lack of
-privacy \cite{tang2017mobile}.  Students' dropout of the MIM groups,
-as they can leave groups at any time, can hinder their learning and
-undermine educators' efforts \cite{mwakapina2016whatsapp}.  In
-addition, there is a need to set rules and norms for these MIM groups
-in order to maintain the safety of these online communities for
-students \cite{abbas2021onlinechat}. However, these rules should not affect students'
-ownership and control, since it is vital to advance in their learning
-\cite{gachago2015crossing} process. 
-This is why examining the role of MIM in higher education is still a challenge,
-and why the opinions of the teaching community towards them have to be
-examined, as we do in this paper.
+Nevertheless, there are challenges when using MIM tools that occur due to the
+blurring of boundaries between academic and private life. This can lead to
+technostress \cite{gachago2015crossing}, difficulty in managing
+responsibilities, especially among mature students, and lack of privacy
+\cite{tang2017mobile}.  Students' dropout of the MIM groups, as they can leave
+groups at any time, can hinder their learning and undermine educators' efforts
+\cite{mwakapina2016whatsapp}.  In addition, there is a need to set rules and
+norms for these MIM groups in order to maintain the safety of these online
+communities for students \cite{abbas2021onlinechat}. However, these rules should
+not affect students' ownership and control, since it is vital to advance in
+their learning \cite{gachago2015crossing} process.  This is why examining the
+role of MIM in higher education is still a challenge, and why the opinions of
+the teaching community towards them have to be examined, as we do in this paper.
 
 % The Use of Chatbots in Higher Education
-The use of MIM, although possibly valuable by itself, can be enhanced via the use of chatbots, which, being conversational agents, usually dwell
-in systems where synchronous conversations take place. 
-The use of conversational agents (chatbots) in higher education is
-still at its infancy \cite{yang2019opportunities}. Nevertheless,
-recent studies examining their positive impact on students' academic
-performance \cite{perez2020rediscovering} and engagement
-\cite{differ.chat,abbas2021onlinechat} have led to a growing interest
-in using this technology in the (possibly virtual) classroom. Indeed, the use of chatbots in
-collecting course feedback from students in higher education improved
-students' response quality and boosted their enjoyment levels
-\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using
-either tools such as mobile devices or teaching strategies based on
-gamification \cite{Yildirim2017} can improve student motivation. In
-this sense, the authors in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
-report the positive impact of using instant messaging tools in boosting students' knowledge and mitigating their feelings of isolation.
-
-Several higher education chatbots' evaluation studies have been 
-undertaken. For instance, a recent evaluation review study presented by Smutny and Schreiberova 
-\cite{Smutny2020} examined 47 educational chatbots implemented in
-Facebook Messenger with the focus to identify characteristics and
-quality metrics such as language, subject matter and platform. 
-Whereas the study undertaken by \cite{perez2020rediscovering} aimed to categorise educational chatbots according to their
-purpose into service-oriented and teaching-oriented. The first category includes those that
-provide service support such as the chatbot Ask Holly \cite{meetholly}
-and Dina \cite{santoso2018dinus}; both chatbots respond to students'
-questions about enrolment and registration. Ask L. U.
- \cite{LancasterUniversity_2019} answers students' frequently
-asked questions about timetables, grades, tutors and societies. LISA
-\cite{dibitonto2018chatbot} and Differ \cite{differ.chat} facilitate
-breaking the ice between new students by introducing them to each
-other. Ranoliya et al. \cite{ranoliya2017chatbot} proposed a generic chatbot for
-university students that is able to answer to their frequently asked
-questions. 
-For some time, the University of Granada had ELVIRA as a
-chatbot in its main web page \cite{MOREO20129}. Besides being able to
-answer pre-established (frequent) questions, it did so from the website of the
-University of Granada using an inset character, voiced by a real
-person, who lip-synced the answers. The emphasis in the case of Elvira,
-however, was on the authenticity of the synchronization more than in
-making the update of questions and answers simpler, or more
-interactive, using actual messaging platforms. 
-In most cases, using the inset search engine was able to give you more up-to-date and
-accurate answers than the ones provided by ELVIRA, which had to be updated by hand (and not too often).
-
-On the other hand, teaching-oriented chatbots are more sophisticated,
-as they set personalised learning outcomes and monitor learning
-progress. For instance, \cite{fernoagua2018intelligent} reported on
-``eduAssistant'', a virtual teaching assistant chatbot developed on the
-Telegram messaging platform. In this study, Telegram platform was
-chosen because it is easy to use, students are familiar with its
-features, and it enables them to exchange messages in different
-formats (text, audio and video) \cite{fernoagua2018intelligent}. In
-addition, Telegram could operate on all devices and operating
-systems. The ``eduAssistant'' chatbot acts as an automatic agent
-in teacher-content-student, facilitating real-time feedback
-loops and providing a personalised learning experience relevant to the
+The use of MIM, although possibly valuable by itself, can be enhanced via the
+use of chatbots, which, being conversational agents, usually dwell in systems
+where synchronous conversations take place.  The use of conversational agents
+(chatbots) in higher education is still at its infancy
+\cite{yang2019opportunities}. Nevertheless, recent studies examining their
+positive impact on students' academic performance \cite{perez2020rediscovering}
+and engagement \cite{differ.chat,abbas2021onlinechat} have led to a growing
+interest in using this technology in the (possibly virtual) classroom. Indeed,
+the use of chatbots in collecting course feedback from students in higher
+education improved students' response quality and boosted their enjoyment levels
+\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using either tools
+such as mobile devices or teaching strategies based on gamification
+\cite{Yildirim2017} can improve student motivation. In this sense, the authors
+in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
+report the positive impact of using instant messaging tools in boosting
+students' knowledge and mitigating their feelings of isolation.
+
+Several higher education chatbots' evaluation studies have been undertaken. For
+instance, a recent evaluation review study presented by Smutny and Schreiberova
+\cite{Smutny2020} examined 47 educational chatbots implemented in Facebook
+Messenger with the focus to identify characteristics and quality metrics such as
+language, subject matter and platform.  Whereas the study undertaken by
+\cite{perez2020rediscovering} aimed to categorise educational chatbots according
+to their purpose into service-oriented and teaching-oriented. The first category
+includes those that provide service support such as the chatbot Ask Holly
+\cite{meetholly} and Dina \cite{santoso2018dinus}; both chatbots respond to
+students' questions about enrolment and registration. Ask L. U.
+\cite{LancasterUniversity_2019} answers students' frequently asked questions
+about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot}
+and Differ \cite{differ.chat} facilitate breaking the ice between new students
+by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
+proposed a generic chatbot for university students that is able to answer to
+their frequently asked questions.  For some time, the University of Granada had
+ELVIRA as a chatbot in its main web page \cite{MOREO20129}. Besides being able
+to answer pre-established (frequent) questions, it did so from the website of
+the University of Granada using an inset character, voiced by a real person, who
+lip-synced the answers. The emphasis in the case of Elvira, however, was on the
+authenticity of the synchronization more than in making the update of questions
+and answers simpler, or more interactive, using actual messaging platforms.  In
+most cases, using the inset search engine was able to give you more up-to-date
+and accurate answers than the ones provided by ELVIRA, which had to be updated
+by hand (and not too often).
+
+On the other hand, teaching-oriented chatbots are more sophisticated, as they
+set personalised learning outcomes and monitor learning progress. For instance,
+\cite{fernoagua2018intelligent} reported on ``eduAssistant'', a virtual teaching
+assistant chatbot developed on the Telegram messaging platform. In this study,
+Telegram platform was chosen because it is easy to use, students are familiar
+with its features, and it enables them to exchange messages in different formats
+(text, audio and video) \cite{fernoagua2018intelligent}. In addition, Telegram
+could operate on all devices and operating systems. The ``eduAssistant'' chatbot
+acts as an automatic agent in teacher-content-student, facilitating real-time
+feedback loops and providing a personalised learning experience relevant to the
 students' acquired skills and knowledge. Using this chatbot, educators can
-create interactive instances in their lectures where they pose
-questions to their students and the chatbot assists those who need
-further help by giving them more hints and reporting it to their
-educator's dashboard \cite{fernoagua2018intelligent}. This can help 
-educators to locate those students that need their attention and send to 
-them more educational resources relevant to their academic attainment.
-
-Despite its (arguably) successful implementation in different higher education institutions, 
-over all in the fringes of educational activity, not in the actual interaction student-teacher, its implementation or deployment is not trivial.
-Some authors, for instance \cite{sjostrom2018designing} have proposed a conceptual
-architecture for the adoption of teaching-oriented chatbots in higher education.  This
-conceptual architecture is based on a systematic literature review of
-previous studies, examining the design of chatbots in higher education, as well as making a content 
-analysis of student emails and discussion forum posts of
-four instances of a Java programming course.  The study outlined
-several design considerations; among them, the authors emphasised the
-importance of developing chatbots in platforms that students and
-educators are familiar with and can easily access (i.e. Facebook
-Messenger) which was confirmed with \cite{hobert2019you} and
-\cite{fernoagua2018intelligent} studies. In addition, Sj{\"o}str{\"o}m et al. \cite{sjostrom2018designing} 
-argued that a conceptualisation of learners' questions could aid designers in integrating the appropriate
-types of questions that the chatbots should support for different
-courses.  Coronado et al. \cite{coronado2018cognitive} proposed agents that store
-learning materials to be provided on demand to students, whereas the authors in
-\cite{crockett2017predicting} reported on tutoring systems,
-which can perform initial assessments of students' understanding and
-provide learning material that would advance their understanding to
-the next level.
-
-Regarding the factors for the adoption of chatbots in higher
-education, many studies have focused on the evaluation of technology
-acceptance and usability \cite{Roblyer2010,Pimmer2019}. However,
-higher education is a special domain where, according to Hobert \cite{hobert2019you}, 
-specific pedagogical factors such as learning success or increased motivation are more important.  
-Therefore, to develop efficient chatbots for higher education, all stakeholders'
-(i.e. educators, students, institutions, etc) needs should be
-carefully collected and taken into consideration
+create interactive instances in their lectures where they pose questions to
+their students and the chatbot assists those who need further help by giving
+them more hints and reporting it to their educator's dashboard
+\cite{fernoagua2018intelligent}. This can help educators to locate those
+students that need their attention and send to them more educational resources
+relevant to their academic attainment.
+
+Despite its (arguably) successful implementation in different higher education
+institutions, over all in the fringes of educational activity, not in the actual
+interaction student-teacher, its implementation or deployment is not trivial.
+Some authors, for instance \cite{sjostrom2018designing} have proposed a
+conceptual architecture for the adoption of teaching-oriented chatbots in higher
+education.  This conceptual architecture is based on a systematic literature
+review of previous studies, examining the design of chatbots in higher
+education, as well as making a content analysis of student emails and discussion
+forum posts of four instances of a Java programming course.  The study outlined
+several design considerations; among them, the authors emphasised the importance
+of developing chatbots in platforms that students and educators are familiar
+with and can easily access (i.e. Facebook Messenger) which was confirmed with
+\cite{hobert2019you} and \cite{fernoagua2018intelligent} studies. In addition,
+Sj{\"o}str{\"o}m et al. \cite{sjostrom2018designing} argued that a
+conceptualisation of learners' questions could aid designers in integrating the
+appropriate types of questions that the chatbots should support for different
+courses.  Coronado et al. \cite{coronado2018cognitive} proposed agents that
+store learning materials to be provided on demand to students, whereas the
+authors in \cite{crockett2017predicting} reported on tutoring systems, which can
+perform initial assessments of students' understanding and provide learning
+material that would advance their understanding to the next level.
+
+Regarding the factors for the adoption of chatbots in higher education, many
+studies have focused on the evaluation of technology acceptance and usability
+\cite{Roblyer2010,Pimmer2019}. However, higher education is a special domain
+where, according to Hobert \cite{hobert2019you}, specific pedagogical factors
+such as learning success or increased motivation are more important.  Therefore,
+to develop efficient chatbots for higher education, all stakeholders'
+(i.e. educators, students, institutions, etc) needs should be carefully
+collected and taken into consideration
 \cite{sjostrom2018designing,tsivitanidouusers}.
 
-Along this line of research, our previous work \cite{MoraChatbots2021:anon} aimed at analysing the expectations of students on this regard; recent papers have also analysed how the use of chatbots affected the learning outcomes of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
-This paper analysed conversational chatbots in an one-to-one setting, finding that learning really benefited from it.
-This is, once again, a proof of the benefit of chatbots in certain settings; however, there are some opinions that might prevent the successful acceptance of the technology, and these are what we are trying to find out in this paper, together with what kind of features would make its acceptance better.
-
-Besides, the present work is focused on the other key actor in this challenge, i.e.
-educators.
-Their attitudes have been studied very recently by Chocarro et al.
-\cite{doi:10.1080/03055698.2020.1850426}, who, by analysing surveys, created a {\em technology acceptance model} that proposed a series of features that would make chatbots easier to accept; among them, formality of language as well as easiness and usefulness.
-The survey targeted primary and secondary education teachers, and was also more interested in the general use of chatbots in education, not specifically in a classroom setting, seeking educational outcomes.
-However, they establish a series of results that are obviously interesting and relevant for this work.
-
-We will present next the methodology we have followed to find out teachers' opinions.
+Along this line of research, our previous work \cite{MoraChatbots2021:anon}
+aimed at analysing the expectations of students on this regard; recent papers
+have also analysed how the use of chatbots affected the learning outcomes of
+students in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper
+analysed conversational chatbots in an one-to-one setting, finding that learning
+really benefited from it. This is, once again, a proof of the benefit of
+chatbots in certain settings; however, there are some opinions that might
+prevent the successful acceptance of the technology, and these are what we are
+trying to find out in this paper, together with what kind of features would make
+its acceptance better.
+
+Besides, the present work is focused on the other key actor in this challenge,
+i.e. educators. Their attitudes have been studied very recently by Chocarro et
+al. \cite{doi:10.1080/03055698.2020.1850426}, who, by analysing surveys, created
+a {\em technology acceptance model} that proposed a series of features that
+would make chatbots easier to accept; among them, formality of language as well
+as easiness and usefulness. The survey targeted primary and secondary education
+teachers, and was also more interested in the general use of chatbots in
+education, not specifically in a classroom setting, seeking educational
+outcomes. However, they establish a series of results that are obviously
+interesting and relevant for this work.
+
+We will present next the methodology we have followed to find out teachers'
+opinions.
 
@@
 
-Our intention from the beginning was to try to gather a sufficient amount of responses in all sectors, as well as cover different sectors of higher education.
-In doing so, an online survey was administered (i.e., Google Form), in Spanish, which was intended to be answered in a very short amount of time.
-Initially, our intention was to mirror the questions used in \cite{MoraChatbots2021:anon};
-% Antonio - I would say something like: "but from teachers' perspective"
-however, an initial exploration of results led us to create a second survey.
-The survey items focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider useful to be used in their teaching, and the type of interactions that teachers prefer to have with their students while using messaging apps in their teaching.
-
-% Move a part of this to an appendix: Noorhan
-The {\bf initial survey} was done in two separate Google forms, one for university and other for tertiary non-university teachers.
-Questions and responses were the same, except for the type of tertiary degrees that were taught.
-In both cases, we used mainly mailing lists, as well as Telegram groups, to spread the link to the form.
-The university form was spread in Spanish (mainly Andaluc\'{\i}a and Galicia) universities, and also Costa Rica and Mexico.
-The tertiary non-university teachers are based mainly in Andaluc\'{\i}a.
-Dissemination and answers took place in the first quarter of 2021, post-pandemic and while, at least in Spain, many universities had mandatory virtual teaching.
-
-A total of 282 teachers responded to the survey: 193 teaching at the University (68.4\%) and 89 at other tertiary education institutions (31.6\%). Survey questions are shown in \ref{app:questions}.
-
-Responses were stored automatically in a Google Drive spreadsheet.
-Eventually, the results from the two forms we used for the first survey were collated in a single spreadsheet.
-Next we will show the results and analyse them.
+Our intention from the beginning was to try to gather a sufficient amount of
+responses in all sectors, as well as cover different sectors of higher
+education. In doing so, an online survey was administered (i.e., Google Form),
+in Spanish, which was intended to be answered in a very short amount of
+time. Initially, our intention was to mirror the questions used in
+\cite{MoraChatbots2021:anon}; however, an initial exploration of results led us
+to create a second survey. The survey items focused on the use of messaging apps
+in the teaching practice, the type of chatbot use cases that teachers consider
+useful to be used in their teaching, and the type of interactions that teachers
+prefer to have with their students while using messaging apps in their teaching.
+
+The {\bf initial survey} was done in two separate Google forms, one for
+university and other for tertiary non-university teachers. Questions and
+responses were the same, except for the type of tertiary degrees that were
+taught. In both cases, we used mainly mailing lists, as well as Telegram groups,
+to spread the link to the form. The university form was spread in Spanish
+(mainly Andaluc\'{\i}a and Galicia) universities, and also Costa Rica and
+Mexico. The tertiary non-university teachers are based mainly in
+Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of
+2021, post-pandemic and while, at least in Spain, many universities had
+mandatory virtual teaching.
+
+A total of 282 teachers responded to the survey: 193 teaching at the University
+(68.4\%) and 89 at other tertiary education institutions (31.6\%). Survey
+questions are shown in \ref{app:questions}.
+
+Responses were stored automatically in a Google Drive spreadsheet. Eventually,
+the results from the two forms we used for the first survey were collated in a
+single spreadsheet. Next we will show the results and analyse them.
 
@@
 % Describe the survey and population
-We collected responses from 282 teachers from Spain and Spanish Speaking countries for \textit{survey1} and 205 for \textit{survey2}.
-The two forms were open for approximately the same amount of time, around two months.
-The sample includes mostly teachers from university, although about 32\% and 8\% are from vocational education in the first and second survey respectively.
-Regarding gender, 61\% of the teachers were male and 32\% female, while approximately 5\% chose not to disclose it.
-Finally, the responses are more or less equally distributed according to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 26\% for 6-15 years of experience, 30\% for 16-25, and 20\% for teachers with more than 25 years of experience.
+We collected responses from 282 teachers from Spain and Spanish Speaking
+countries for \textit{survey1} and 205 for \textit{survey2}. The two forms were
+open for approximately the same amount of time, around two months. The sample
+includes mostly teachers from university, although about 32\% and 8\% are from
+vocational education in the first and second survey respectively. Regarding
+gender, 61\% of the teachers were male and 32\% female, while approximately 5\%
+chose not to disclose it. Finally, the responses are more or less equally
+distributed according to the teaching experience, showing 24\% of responses from
+teachers with 5 or less years of experience, 26\% for 6-15 years of experience,
+30\% for 16-25, and 20\% for teachers with more than 25 years of experience.
 
@@
 
-We will try to find the answers to the four research questions next, by analysing the response to the different survey questions.
+We will try to find the answers to the four research questions next, by
+analysing the response to the different survey questions.
 
@@
 %Why messaging apps are relevant here --> connect to the development of chatbots
-Group messaging apps have become a powerful tool for keeping touch with students. Also, many of them have built-in chatbots 
-to enhance the learning process. After an initial analysis to the answers to the first survey, 
-we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally 
-piggybacks on another, messaging applications.
-In a technology adoption model, perceived ease of use and perceived usefulness are essential.
-But it is going to be very difficult for teachers to find {\em chatbots} easy to use if they, previously, do not consider, or simply use, the messaging tools to which they are attached.
-
-This is why for answering RQ1, teachers were queried about whether they use messaging apps in their classes, specifically, Telegram, WhatsApp, Slack (an application used mainly in IT departments and software development), or any other messaging app, and whether they use messaging apps provided by their academic institution (see Table \ref{tab:use_messapps}).
-In this case, it is maybe in order a certain clarification.
-While we had in mind, as indicated by the possible answers, instant messaging applications when making this question, we included these institution-provided applications mainly for completion.
-But it should be noted that, in most cases, they are not {\em instant} messaging apps in the way Telegram or Facebook Messenger are; in most cases they are messaging facilities provided by learning management systems such as (usually) Moodle.
-So the answer to this question must be understood in two different ways: their preference for the {\em source} of the technology (university, any company) as well as the {\em type} of technology (instant, app based messaging systems vs.
-web-based systems integrated in another learning management system).
-
-Overall, the majority of the teachers responded that they do use messaging apps in their classrooms, from which apps provided by the academic institution (n=159, 56\%) and WhatsApp (n=124, 44.0\%) were the most common responses.
-Only 19 teachers (6.7\%) replied that they do not use any messaging app in their class.
-%Remember to add something to the discussion below - JJ
+Group messaging apps have become a powerful tool for keeping touch with
+students. Also, many of them have built-in chatbots to enhance the learning
+process. After an initial analysis to the answers to the first survey, we
+realized that there were some prior issues mainly related to the adoption of a
+technology, chatbots, that generally piggybacks on another, messaging
+applications. In a technology adoption model, perceived ease of use and
+perceived usefulness are essential. But it is going to be very difficult for
+teachers to find {\em chatbots} easy to use if they, previously, do not
+consider, or simply use, the messaging tools to which they are attached.
+
+This is why for answering RQ1, teachers were queried about whether they use
+messaging apps in their classes, specifically, Telegram, WhatsApp, Slack (an
+application used mainly in IT departments and software development), or any
+other messaging app, and whether they use messaging apps provided by their
+academic institution (see Table \ref{tab:use_messapps}). In this case, it is
+maybe in order a certain clarification. While we had in mind, as indicated by
+the possible answers, instant messaging applications when making this question,
+we included these institution-provided applications mainly for completion. But
+it should be noted that, in most cases, they are not {\em instant} messaging
+apps in the way Telegram or Facebook Messenger are; in most cases they are
+messaging facilities provided by learning management systems such as (usually)
+Moodle. So the answer to this question must be understood in two different ways:
+their preference for the {\em source} of the technology (university, any
+company) as well as the {\em type} of technology (instant, app based messaging
+systems vs. web-based systems integrated in another learning management system).
+
+Overall, the majority of the teachers responded that they do use messaging apps
+in their classrooms, from which apps provided by the academic institution
+(n=159, 56\%) and WhatsApp (n=124, 44.0\%) were the most common responses. Only
+19 teachers (6.7\%) replied that they do not use any messaging app in their
+class.
 %
@@
 % Fran: I think figures with data about the use of messaging apps should come here. Then, we say we also asked about changes after covid and include data about that
-Results in Figs.
-\ref{figure:provided*chatbots_use}, \ref{figure:whatsapp*chatbots_use}, \ref{figure:telegram*chatbots_use} do not show significant differences in the use of instant messaging apps between teachers from University and vocational education.
-In general, most teachers prefer messaging apps provided by their own institutions (we also show the results for the two most popular messaging app platforms: WhatsApp and Telegram).
-With respect to specific disciplines, Engineering and Technology teachers are more active in their use, although it is also relevant the amount of teachers from Humanities that answered they used these apps in their classes (around 60\% use the apps provided by their institutions).
-
-Although no significant differences were found regarding gender, female teachers answered they use instant messaging apps more than male teachers (about 10\% more).
-Also, teachers in vocational Education use WhatsApp more than university teachers.
-Regarding the distribution of the use of messaging apps per age, there are no significant differences for WhatsApp and apps provided by their own academic institutions.
-% Olia requests support for this.
-However, younger teachers also use Telegram with more than 25\%, a percentage that falls to about 10\% for teachers that are 55 or older.
-%The third column compares the use of these apps considering the number of years of experience.
-One interesting result is that about 65\% of teachers with more than 25 years of experience use the platforms provided by their institutions while the percentage goes down to less than 50\% for teachers with 6-15 years of experience.
+Results in Figs. \ref{figure:provided*chatbots_use},
+\ref{figure:whatsapp*chatbots_use}, \ref{figure:telegram*chatbots_use} do not
+show significant differences in the use of instant messaging apps between
+teachers from University and vocational education. In general, most teachers
+prefer messaging apps provided by their own institutions (we also show the
+results for the two most popular messaging app platforms: WhatsApp and
+Telegram). With respect to specific disciplines, Engineering and Technology
+teachers are more active in their use, although it is also relevant the amount
+of teachers from Humanities that answered they used these apps in their classes
+(around 60\% use the apps provided by their institutions).
+
+Although no significant differences were found regarding gender, female teachers
+answered they use instant messaging apps more than male teachers (about 10\%
+more). Also, teachers in vocational Education use WhatsApp more than university
+teachers. Regarding the distribution of the use of messaging apps per age, there
+are no significant differences for WhatsApp and apps provided by their own
+academic institutions. % Olia requests support for this. 
+However, younger teachers also use Telegram with more than 25\%, a percentage
+that falls to about 10\% for teachers that are 55 or older. %The third column
+                                %compares the use of these apps considering the
+                                %number of years of experience.
+One interesting result is that about 65\% of teachers with more than 25 years of
+experience use the platforms provided by their institutions while the percentage
+goes down to less than 50\% for teachers with 6-15 years of experience.
 %
@@
 % This is about changes (due to) after covid
-Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' viewpoints towards the use of instant messaging apps in their class.
-Our main intention in this case was to assess whether a crisis will bring about some kind of change in the use of tools.
-The 282 
-% Fran, please check Olia's comment as having 282 answers 
-% -> I did remove some responses that Olia considered 'No' by default (i guess). I' ll keep it to 282 to be consistent
-answers are summarized in Figs.
-\ref{figure:gender*chatbots_use_postcovid}, \ref{figure:sector*chatbots_use_postcovid}, \ref{figure:years*chatbots_use_postcovid}, \ref{figure:disc*chatbots_use_postcovid}, showing that about 77\% of teachers already used these tools before the pandemic and kept using them during the pandemic lockdowns that forced students and educators to use remote education schemes.
-Moreover, approximately 15\% of them switched their messaging app for one that offered a safer interaction with their students.
-According to the responses, an additional 16\% started using messaging apps during the pandemic for the first time in their classes.
-Aggregating the answers, currently 91\% of the teachers are using messaging apps as learning tools.
+Some of the questions in the survey were focused on the impact of the COVID19
+pandemic between 2020 and 2021, in the teachers' viewpoints towards the use of
+instant messaging apps in their class. Our main intention in this case was to
+assess whether a crisis will bring about some kind of change in the use of
+tools. The 282 answers are summarized in
+Figs. \ref{figure:gender*chatbots_use_postcovid},
+\ref{figure:sector*chatbots_use_postcovid},
+\ref{figure:years*chatbots_use_postcovid},
+\ref{figure:disc*chatbots_use_postcovid}, showing that about 77\% of teachers
+already used these tools before the pandemic and kept using them during the
+pandemic lockdowns that forced students and educators to use remote education
+schemes. Moreover, approximately 15\% of them switched their messaging app for
+one that offered a safer interaction with their students. According to the
+responses, an additional 16\% started using messaging apps during the pandemic
+for the first time in their classes. Aggregating the answers, currently 91\% of
+the teachers are using messaging apps as learning tools.
 %A few relevant facts from the collected data: teachers with 16-25 years of experience seem more worried about the security of messaging apps and teachers with up to 5 years of experience were more open to adopt messaging apps due to the pandemic; female teachers were more willing to adopt new platforms due to the pandemic, and even to start using safer alternatives; finally, university teachers that did not use them were more reluctant to start using them after the pandemic.
@@
 % Olia - TODO: check for repetitions in the following paragraph that you added. thank you.
-Finally, we took a closer look at the post-covid changes and the variables gender, sector, and discipline for which the chi-square test is statistically significant as shown in Figures \ref{figure:gender*postcovid_chisq}, \ref{figure:sector*postcovid_chisq}, \ref{figure:discipline*postcovid_chisq} respectively.
-Each figure shows on the left, a graph that represents the Pearson's residuals of the chi-square test results and a table on the right part that shows the contribution of each cell to the test.
-In the Pearson's residual graphs, the responses were shortened for the sake of clarity according to: 1) \textit{Did/do} stands for \textit{Yes, I did use it before and do use it now}; 2) \textit{Didn't/do} for \textit{Yes, I didn’t use any messaging app before, but do use it now}; 3) \textit{safer} for \textit{Yes, I use a safer messaging app now}; 4) \textit{Didn't/Don't} for \textit{No, I didn’t use it before and don’t use it now}.
+Finally, we took a closer look at the post-covid changes and the variables
+gender, sector, and discipline for which the chi-square test is statistically
+significant as shown in Figures \ref{figure:gender*postcovid_chisq},
+\ref{figure:sector*postcovid_chisq}, \ref{figure:discipline*postcovid_chisq}
+respectively. Each figure shows on the left, a graph that represents the
+Pearson's residuals of the chi-square test results and a table on the right part
+that shows the contribution of each cell to the test. In the Pearson's residual
+graphs, the responses were shortened for the sake of clarity according to: 1)
+\textit{Did/do} stands for \textit{Yes, I did use it before and do use it now};
+2) \textit{Didn't/do} for \textit{Yes, I didn’t use any messaging app before,
+  but do use it now}; 3) \textit{safer} for \textit{Yes, I use a safer messaging
+  app now}; 4) \textit{Didn't/Don't} for \textit{No, I didn’t use it before and
+  don’t use it now}.
 %
@@
 
-As mentioned, the graphs on the left hand side represent the Pearson's residuals, showing the difference between the observed and the expected values for each cell.
-Thus, large residuals indicate that variables are not truly independent.
-In our case, the blue shows positive contributions and red negative contributions to the test.
-Moreover, the saturation shows how large the contribution is in contrast to the expected value by chance.
-Additionally, tables on the right side show adjusted standardized residuals that according to \cite{agresti2013categorical}, if greater than +/-2 for cases with few cells, indicate lack of fit of $H_0$ (in boldface in our table).
-Complementary, the table also shows the percentage of contribution to the test of each cell (highest percentage per column also in boldface).
-
-Regarding gender in Fig.
-\ref{figure:gender*postcovid_chisq}, the results show a high positive contribution from female educators that did not use a messaging app before the COVID-19 pandemic but do use it now; approximately 31\% of the test results are explained by this cell.
-In contrast, male educators that respond the same were less than expected (negative contribution that explains 17\% of the test results).
-Also, it is important to highlight the female educators that kept using these apps before and after the pandemic and correspondingly the negative contribution of male educators to the same case (less than expected by chance).
+As mentioned, the graphs on the left hand side represent the Pearson's
+residuals, showing the difference between the observed and the expected values
+for each cell. Thus, large residuals indicate that variables are not truly
+independent. In our case, the blue shows positive contributions and red negative
+contributions to the test. Moreover, the saturation shows how large the
+contribution is in contrast to the expected value by chance. Additionally,
+tables on the right side show adjusted standardized residuals that according to
+\cite{agresti2013categorical}, if greater than +/-2 for cases with few cells,
+indicate lack of fit of $H_0$ (in boldface in our table). Complementary, the
+table also shows the percentage of contribution to the test of each cell
+(highest percentage per column also in boldface).
+
+Regarding gender in Fig. \ref{figure:gender*postcovid_chisq}, the results show a
+high positive contribution from female educators that did not use a messaging
+app before the COVID-19 pandemic but do use it now; approximately 31\% of the
+test results are explained by this cell. In contrast, male educators that
+respond the same were less than expected (negative contribution that explains
+17\% of the test results). Also, it is important to highlight the female
+educators that kept using these apps before and after the pandemic and
+correspondingly the negative contribution of male educators to the same case
+(less than expected by chance).
 
@@
 %
-Finally, statistical significance was found for the discipline and post-covid changes.
-Regarding disciplines (see Fig.
-\ref{figure:discipline*postcovid_chisq}), the number of educators from Humanities and Social Sciences that started using messaging apps after the pandemic is larger than expected and these number of responses explains about 19\% of the chi-square test results.
-Also, the number of educators from Technology or Engineering that started using safer alternatives are less than expected (compared to the educators from other disciplines).
-Bear in mind that some disciplines were merged to avoid very low number of responses for some of the cells.
+Finally, statistical significance was found for the discipline and post-covid
+changes. Regarding disciplines (see
+Fig. \ref{figure:discipline*postcovid_chisq}), the number of educators from
+Humanities and Social Sciences that started using messaging apps after the
+pandemic is larger than expected and these number of responses explains about
+19\% of the chi-square test results. Also, the number of educators from
+Technology or Engineering that started using safer alternatives are less than
+expected (compared to the educators from other disciplines). Bear in mind that
+some disciplines were merged to avoid very low number of responses for some of
+the cells.
 
@@
 
-For the findings it occurs that the most favourable use case for chatbots in Higher Education and vocational training is their use for the facilitation of an agenda formation (171 positive response, 60.6\%), followed by the FAQs use case (148 positive responses, 52.5\%) and the sharing class material use case (136; 48.2\%).
-A chi-square test of independence was performed to examine the relation among participants’ preferences for particular chatbot use cases.
-The relation between agenda and the FAQs use case was significant, $X^{2}_{(1, N = 282)} = 10.467$, $p =0.001$.
-The frequencies cross tabulated are given in Table \ref{tab:agenda*faq}.
-Out of the 171 teachers who consider useful the use of chatbots for agenda preparation in the class, 103 also consider useful chatbots’ use for FAQs.
+For the findings it occurs that the most favourable use case for chatbots in
+Higher Education and vocational training is their use for the facilitation of an
+agenda formation (171 positive response, 60.6\%), followed by the FAQs use case
+(148 positive responses, 52.5\%) and the sharing class material use case (136;
+48.2\%). A chi-square test of independence was performed to examine the relation
+among participants’ preferences for particular chatbot use cases. The relation
+between agenda and the FAQs use case was significant, $X^{2}_{(1, N = 282)} =
+10.467$, $p =0.001$. The frequencies cross tabulated are given in Table
+\ref{tab:agenda*faq}. Out of the 171 teachers who consider useful the use of
+chatbots for agenda preparation in the class, 103 also consider useful chatbots’
+use for FAQs.
 
@@
 
-Answers to these questions are plotted in Figs.
-\ref{figure:gender*chatbots_types}, \ref{figure:sector*chatbots_types}, \ref{figure:experience*chatbots_types}, \ref{figure:disc*chatbots_types} grouped by gender, sector, years of experience in education, and discipline respectively.
-As it was a multiple choice question, the counts are over the total number of people that answered.
+Answers to these questions are plotted in
+Figs. \ref{figure:gender*chatbots_types}, \ref{figure:sector*chatbots_types},
+\ref{figure:experience*chatbots_types}, \ref{figure:disc*chatbots_types} grouped
+by gender, sector, years of experience in education, and discipline
+respectively. As it was a multiple choice question, the counts are over the
+total number of people that answered.
 
@@
 
-%Olia - move figure 7 elsewhere, not at the beginning of this section (RQ3). 
-Since chatbots are intended to mediate or help in this interaction, it is essential to understand the kind of interaction teachers prefer.
-Chatbots should address those modes, and not others.
-In order to find out these modes, and thus answering RQ3, teachers were provided with a list of different kind of interactions that may take place among students and between students and the teacher, with the use of messaging apps.
-The findings are summarized in Table \ref{tab:kindinteractions}.
+Since chatbots are intended to mediate or help in this interaction, it is
+essential to understand the kind of interaction teachers prefer. Chatbots should
+address those modes, and not others. In order to find out these modes, and thus
+answering RQ3, teachers were provided with a list of different kind of
+interactions that may take place among students and between students and the
+teacher, with the use of messaging apps. The findings are summarized in Table
+\ref{tab:kindinteractions}.
 
@@
 
-As it can be seen by the answer to the first and last question, in general teachers do not want to participate in a chat group with students; either they want to simply leave the students alone in their own chat group, or otherwise they prefer not to be part of that interaction.
-In general, that is going to be the case no matter what; it is well known that students organize their own chat groups with many (and not always conveyable) intentions, so teachers do not want to take any part in these informal or non institutionally-supported chat groups.
-Overwhelmingly, they do not want to participate in these kind of chat groups with students, but even less so if it includes the rest of the faculty.
-
-The answer, then, to this research question, is that, in general, teachers do {\em not} want to have interaction with students in a chat group.
-To a certain point, this would seem to contradict results by Gachago et al.
-\cite{gachago2015crossing}, although this might be due to cultural attitudes, or other factors such as the average size of classes.
-It does confirm, however, that the challenges cited in that study, and possibly others, are an obstacle to the adoption of mobile (and other) instant messaging among the community of surveyed teachers.
-
-Regarding the social factor of chat groups that teachers use in class, according to Fig.
-\ref{figure:chatbots_messagingorganization} the vast majority prefer small groups only with the students from the same course.
-These are more focused groups with specific goals and dedicated to the organization of the course and its tasks, and from the pedagogic point of view seem more appropriate to improve the learning process.
-Interestingly, and as a cross-check of the answers above, about 30\% of teachers consider they should not be part of the chat group.
-This might seem to contradict the results of the other survey, but in fact, being a result of different surveys, to a certain point affirms the same thing: there is a great amount of teachers that would be against being in a chat group with students.
-Whether that's a slim majority or not, that's open to debate (and would probably need a more pointed survey focused on this), but what is clear is that forcing teachers to create chat groups with students and participate in them would create a certain amount of resistance.
-Also, only university teachers find interesting a group with all the students and teachers in their own Faculty or School.
-The lack of teachers from vocational education here may be the consequence of using specific language such as ``Faculty''.
-Moreover, the fact that many universities and schools already use these groups for administrative and social interaction (e.g.
-\cite{dibitonto2018chatbot}) might be the reason for the low percentage of teachers that selected this response.
+As it can be seen by the answer to the first and last question, in general
+teachers do not want to participate in a chat group with students; either they
+want to simply leave the students alone in their own chat group, or otherwise
+they prefer not to be part of that interaction. In general, that is going to be
+the case no matter what; it is well known that students organize their own chat
+groups with many (and not always conveyable) intentions, so teachers do not want
+to take any part in these informal or non institutionally-supported chat
+groups. Overwhelmingly, they do not want to participate in these kind of chat
+groups with students, but even less so if it includes the rest of the faculty.
+
+The answer, then, to this research question, is that, in general, teachers do
+{\em not} want to have interaction with students in a chat group. To a certain
+point, this would seem to contradict results by Gachago et
+al. \cite{gachago2015crossing}, although this might be due to cultural
+attitudes, or other factors such as the average size of classes. It does
+confirm, however, that the challenges cited in that study, and possibly others,
+are an obstacle to the adoption of mobile (and other) instant messaging among
+the community of surveyed teachers.
+
+Regarding the social factor of chat groups that teachers use in class, according
+to Fig. \ref{figure:chatbots_messagingorganization} the vast majority prefer
+small groups only with the students from the same course. These are more focused
+groups with specific goals and dedicated to the organization of the course and
+its tasks, and from the pedagogic point of view seem more appropriate to improve
+the learning process. Interestingly, and as a cross-check of the answers above,
+about 30\% of teachers consider they should not be part of the chat group. This
+might seem to contradict the results of the other survey, but in fact, being a
+result of different surveys, to a certain point affirms the same thing: there is
+a great amount of teachers that would be against being in a chat group with
+students. Whether that's a slim majority or not, that's open to debate (and
+would probably need a more pointed survey focused on this), but what is clear is
+that forcing teachers to create chat groups with students and participate in
+them would create a certain amount of resistance. Also, only university teachers
+find interesting a group with all the students and teachers in their own Faculty
+or School. The lack of teachers from vocational education here may be the
+consequence of using specific language such as ``Faculty''. Moreover, the fact
+that many universities and schools already use these groups for administrative
+and social interaction (e.g. \cite{dibitonto2018chatbot}) might be the reason
+for the low percentage of teachers that selected this response.
 
@@
 
-Finally, a two-step cluster analysis was conducted, with a log-likelihood distance measure adopted, to explore how the cases could be grouped based on their preferences of specific interaction media features, and which features have larger predictor importance for the clustering (see Fig.
-\ref{figure:predictor}).
-Two clusters occurred from the analysis: cluster 1 (n=78, 60.9\%) was comprise of instructors who did not value interaction media pluggability, connectivity, official formation, but valued interaction media analytics, familiarity, support by the institution, while cluster 2 (n=50, 39.1\%) was comprise of instructors from which the majority did not value media analytics, official formation, familiarity, but valued pluggability, connectivity, and support by the institution.
-Interaction media pluggability appears to have the most important predictor importance in the clustering of cases (predictor importance = 1.0), whilst media unidirectionality was the least important factor (predictor importance = 0.04).
-The cluster quality is fair, but not a good one (silhouette measure of cohesion and separation).
+Finally, a two-step cluster analysis was conducted, with a log-likelihood
+distance measure adopted, to explore how the cases could be grouped based on
+their preferences of specific interaction media features, and which features
+have larger predictor importance for the clustering (see
+Fig. \ref{figure:predictor}). Two clusters occurred from the analysis: cluster 1
+(n=78, 60.9\%) was comprise of instructors who did not value interaction media
+pluggability, connectivity, official formation, but valued interaction media
+analytics, familiarity, support by the institution, while cluster 2 (n=50,
+39.1\%) was comprise of instructors from which the majority did not value media
+analytics, official formation, familiarity, but valued pluggability,
+connectivity, and support by the institution. Interaction media pluggability
+appears to have the most important predictor importance in the clustering of
+cases (predictor importance = 1.0), whilst media unidirectionality was the least
+important factor (predictor importance = 0.04). The cluster quality is fair, but
+not a good one (silhouette measure of cohesion and separation).
 
@@
 
-Our initial intention in the design of these surveys was to probe the opinions of tertiary education teachers in the introduction of chatbot technologies in class.
-We wanted to find the answer to four research questions, of which the first was to check whether teachers already used some kind of messaging application, and the one they preferred.
-Depending on the answer, different technologies could be (or not) available for the introduction of chatbots.
-In this case, the design of the survey introduced some ambiguity on what we really consider ``messaging technology'', that was eventually resolved by the answers; apparently, anything that sends messages (even if they are not instant, even if they do not have a dedicated application) was the concept in the mind of the surveyed.
-
-Additionally, the question on COVID reflected the big challenge that represents changing habits, even in the case of a major crisis.
-Very few people actually changed, with women vs.
-men being an exception, as well as those teaching social sciences standing out among the rest.
-We do not have any kind of explanation for this behaviour, other than technologies are perceived, and adopted, in a different way depending on background and, apparently, gender.
-
- One of the most interesting questions that can arise from the analysis of the results, and that should require further study, is: Are teachers really aware of the possibilities of chatbots in the classroom?
-The reason to ask ourselves this question is due to the fact of the small number of responses for other uses in comparison with the other approaches proposed.
-Another way to look about it is that, unless you provide the specific instructions on how to use a tool, the teaching staff is already too busy or burn out to think about innovation.
-
-It is also likely that their opinions towards chatbots are informed by negative experiences with customer support chatbots, which is what most people will have experienced.
-This will probably require further study, but also will need to be taken into account when introducing chatbot technologies in the classroom: it will have to be as simple, and as satisfactory, ad possible, to (possibly) delete this existing perception.
-
-Regarding gender grouping, both genders agree in their uses, so it seems not relevant at all.
-When looking at the plot containing the sector differentiation it is interesting to observe how university teachers prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational High School teachers.
-This seems reasonable as the frequency of seeing the students is smaller at the University so, automating the grade notification for continuous evaluation could seem much more comfortable using an automated tool than using the traditional platform.
-Furthermore, the high student/teacher ratios that university teachers have to deal with could be another reason to have a higher number of them willing to use chatbots for FAQs.
-This could ameliorate the number of misunderstandings and email overload that so many students might generate.
-
-The results, when grouping by experience, confirm the previous observation that experienced teachers are not afraid of changes and are willing to accept new technological challenges, at least, in the same way that younger teachers are.
-From this concrete plot it is interesting as well the fact that very few young/inexperience teachers are willing to use chatbots for other uses.
-This reinforces the hypothesis thrown at the beginning of this section and, as these teachers have less experience, they also have less field of view to think about ways of using chatbots.
-
-As it appears in the responses presented above, teachers’ responses are distributed between positive and negative in relation to the media features: analytics, connectivity, and hidden phone, while for the features: familiarity, horizontally, sustainability and officiality the majority provided a positive response, designating their preference to these features.
-On the other hand, the majority of teachers seems to consider not valuable the presence of official formation, pluggability, unidirectionality and synchrony in the interaction media features of messaging apps.
+Our initial intention in the design of these surveys was to probe the opinions
+of tertiary education teachers in the introduction of chatbot technologies in
+class. We wanted to find the answer to four research questions, of which the
+first was to check whether teachers already used some kind of messaging
+application, and the one they preferred. Depending on the answer, different
+technologies could be (or not) available for the introduction of chatbots. In
+this case, the design of the survey introduced some ambiguity on what we really
+consider ``messaging technology'', that was eventually resolved by the answers;
+apparently, anything that sends messages (even if they are not instant, even if
+they do not have a dedicated application) was the concept in the mind of the
+surveyed.
+
+Additionally, the question on COVID reflected the big challenge that represents
+changing habits, even in the case of a major crisis. Very few people actually
+changed, with women vs. men being an exception, as well as those teaching social
+sciences standing out among the rest. We do not have any kind of explanation for
+this behaviour, other than technologies are perceived, and adopted, in a
+different way depending on background and, apparently, gender.
+
+ One of the most interesting questions that can arise from the analysis of the
+ results, and that should require further study, is: Are teachers really aware
+ of the possibilities of chatbots in the classroom? The reason to ask ourselves
+ this question is due to the fact of the small number of responses for other
+ uses in comparison with the other approaches proposed. Another way to look
+ about it is that, unless you provide the specific instructions on how to use a
+ tool, the teaching staff is already too busy or burn out to think about
+ innovation.
+
+It is also likely that their opinions towards chatbots are informed by negative
+experiences with customer support chatbots, which is what most people will have
+experienced. This will probably require further study, but also will need to be
+taken into account when introducing chatbot technologies in the classroom: it
+will have to be as simple, and as satisfactory, ad possible, to (possibly)
+delete this existing perception.
+
+Regarding gender grouping, both genders agree in their uses, so it seems not
+relevant at all. When looking at the plot containing the sector differentiation
+it is interesting to observe how university teachers prefer in a higher
+proportion to use them for grades and FAQs in comparison with Vocational High
+School teachers. This seems reasonable as the frequency of seeing the students
+is smaller at the University so, automating the grade notification for
+continuous evaluation could seem much more comfortable using an automated tool
+than using the traditional platform. Furthermore, the high student/teacher
+ratios that university teachers have to deal with could be another reason to
+have a higher number of them willing to use chatbots for FAQs. This could
+ameliorate the number of misunderstandings and email overload that so many
+students might generate.
+
+The results, when grouping by experience, confirm the previous observation that
+experienced teachers are not afraid of changes and are willing to accept new
+technological challenges, at least, in the same way that younger teachers
+are. From this concrete plot it is interesting as well the fact that very few
+young/inexperience teachers are willing to use chatbots for other uses. This
+reinforces the hypothesis thrown at the beginning of this section and, as these
+teachers have less experience, they also have less field of view to think about
+ways of using chatbots.
+
+As it appears in the responses presented above, teachers’ responses are
+distributed between positive and negative in relation to the media features:
+analytics, connectivity, and hidden phone, while for the features: familiarity,
+horizontally, sustainability and officiality the majority provided a positive
+response, designating their preference to these features. On the other hand, the
+majority of teachers seems to consider not valuable the presence of official
+formation, pluggability, unidirectionality and synchrony in the interaction
+media features of messaging apps.
 
@@
 \begin{itemize}
- \item Teachers want to have support from their corresponding institution.
-This is probably due to the strict European data regulations and to avoid the overhead required to sing up and deleting students from year to year.
-
- \item Teachers need sustainability.
-The main reason is that implementing changes is expensive in terms of effort and prone to errors in the first years of implementing new procedures, therefore, it is logical that if chatbots or messaging platforms are to be introduced, they want this change to be as permanent as possible.
-
+ \item Teachers want to have support from their corresponding institution. This
+   is probably due to the strict European data regulations and to avoid the
+   overhead required to sing up and deleting students from year to year.
+ \item Teachers need sustainability. The main reason is that implementing
+   changes is expensive in terms of effort and prone to errors in the first
+   years of implementing new procedures, therefore, it is logical that if
+   chatbots or messaging platforms are to be introduced, they want this change
+   to be as permanent as possible.
  \item Keep it Simple.
@@
 
-An analysis of survey questions related to RQ4 seems to indicate that teachers prefer to have interaction with their students in a chat "room"; a preference of {\em horizontal} interaction might indicate the need to delegate or offload part of the burden of answering, and attending, every single question posed by students.
-In an horizontal setting, other students can answer if the teacher does not do it immediately.
-This might also be the reason why the possibility of using tools from which analytics can be extracted is also valued by teachers: that way, activity in the chat tool, answering questions, regularity, can all be observed and valued as part of the process of assessing achievement of learning objectives by students.
+An analysis of survey questions related to RQ4 seems to indicate that teachers
+prefer to have interaction with their students in a chat "room"; a preference of
+{\em horizontal} interaction might indicate the need to delegate or offload part
+of the burden of answering, and attending, every single question posed by
+students. In an horizontal setting, other students can answer if the teacher
+does not do it immediately. This might also be the reason why the possibility of
+using tools from which analytics can be extracted is also valued by teachers:
+that way, activity in the chat tool, answering questions, regularity, can all be
+observed and valued as part of the process of assessing achievement of learning
+objectives by students.
 
@@
 
-The key findings of this study shed the light on educators’ preference to use messaging applications that their institutions support.
-Technology adoption literature often focus on users’ perceptions of the technology’s usefulness and ease of use as important prerequisites for successful adoption and utilization.
-Nevertheless, in higher education, institutions’ role in integrating these tools to their educational systems can improve the uptake of these applications and shape the social and educational experiences of their students.
-This integration, to be fruitful, institutions have to ensure that these messaging applications not only are GDPR compliant to keep students’ data secure but also should provide IT support to all stakeholders who use the applications.
-
-Moreover, this study clarifies the differences between the teachers’ perspectives and/or intentions and that of their students when using the messaging applications in higher education.
-Teachers tend to adopt technologies supported by their institutions.
-This could be to ensure that their universities can oversee their efforts in supporting their students during the learning process.
-Another reason could be their familiarity with the technology provided by their institutions.
-On the other hand, students use the non-institution messaging applications to form informal discussion groups with their peers.
-It is worth noting that peer support and collaboration is inseparable from learning \cite{timmis2012constant} and correlates positively with higher retention in higher education \cite{o2014front}.
-Therefore, both perspectives are complementary and play different roles in promoting the learning process.
+The key findings of this study shed the light on educators’ preference to use
+messaging applications that their institutions support.  Technology adoption
+literature often focus on users’ perceptions of the technology’s usefulness and
+ease of use as important prerequisites for successful adoption and
+utilization. Nevertheless, in higher education, institutions’ role in
+integrating these tools to their educational systems can improve the uptake of
+these applications and shape the social and educational experiences of their
+students.  This integration, to be fruitful, institutions have to ensure that
+these messaging applications not only are GDPR compliant to keep students’ data
+secure but also should provide IT support to all stakeholders who use the
+applications.
+
+Moreover, this study clarifies the differences between the teachers’
+perspectives and/or intentions and that of their students when using the
+messaging applications in higher education.  Teachers tend to adopt technologies
+supported by their institutions.  This could be to ensure that their
+universities can oversee their efforts in supporting their students during the
+learning process.  Another reason could be their familiarity with the technology
+provided by their institutions. On the other hand, students use the
+non-institution messaging applications to form informal discussion groups with
+their peers.  It is worth noting that peer support and collaboration is
+inseparable from learning \cite{timmis2012constant} and correlates positively
+with higher retention in higher education \cite{o2014front}.  Therefore, both
+perspectives are complementary and play different roles in promoting the
+learning process.
 
 % Noorhan suggest that using some simple things could increase the perceived usefulness - JJ
-As in many other methods of technology acceptance, answers to the survey suggest that the introduction of simple, and institution-supported, instant messaging and chatbot technologies would increase the perceived usefulness (which is one of the key metrics in technology acceptance models).
-Since most institutions already have some {\em virtual campus} or learning management system, adding some easy automation, or connection to personal instant messaging tools, could really help onboard the learning community on these new technologies.
+As in many other methods of technology acceptance, answers to the survey suggest
+that the introduction of simple, and institution-supported, instant messaging
+and chatbot technologies would increase the perceived usefulness (which is one
+of the key metrics in technology acceptance models). Since most institutions
+already have some {\em virtual campus} or learning management system, adding
+some easy automation, or connection to personal instant messaging tools, could
+really help onboard the learning community on these new technologies.
 
 % What kind of chatbots are preferred? (suggested by Fran)
-Once that initial introduction is done, teachers (and students as well) will probably prefer the kind of bots that alleviate bureaucratic or repetitive tasks, such as answering frequent questions or answers on class or assignment schedules.
-These will help the introduction of more complex chatbots that will affect more directly learning outcomes, such as chatbots that help students integrate in the class, or are able to identify (and address) learning problems in students or in groups of them.
-These as well should be accompanied by analytics on student interaction, as well as possibly some natural language processing (in vernacular language) that will help assess the general mood of the class, and how different material (or external factors) affect it.
+Once that initial introduction is done, teachers (and students as well) will
+probably prefer the kind of bots that alleviate bureaucratic or repetitive
+tasks, such as answering frequent questions or answers on class or assignment
+schedules. These will help the introduction of more complex chatbots that will
+affect more directly learning outcomes, such as chatbots that help students
+integrate in the class, or are able to identify (and address) learning problems
+in students or in groups of them. These as well should be accompanied by
+analytics on student interaction, as well as possibly some natural language
+processing (in vernacular language) that will help assess the general mood of
+the class, and how different material (or external factors) affect it.
 
 % No remarkable differences between different groups.
-This introduction of chatbots and chatbot technology will be helped by the fact that no discernible differences are found between different groups.
-Even if chatbots do have some potential for personalization or customization, based on the class material, student and teaching staff, the general introduction of the technology can be done in a general way and for all disciplines, teaching experience and gender.
+This introduction of chatbots and chatbot technology will be helped by the fact
+that no discernible differences are found between different groups. Even if
+chatbots do have some potential for personalization or customization, based on
+the class material, student and teaching staff, the general introduction of the
+technology can be done in a general way and for all disciplines, teaching
+experience and gender.
 
 % Only some COVID-response relationship.
-In our survey, we couldn't find an answer to the right moment for doing this introduction of chatbot technologies.
-Response to questions related to change of behaviour during and after the pandemic do not suggest that major (or minor) crisis could be an opportunity to introduce new technologies, since it does not bring major changes in attitude.
-A minor crisis would be, for instance, rollout of a new higher education law\footnote{We seem to have one of these, at least in Spain, every 10 years or so}, or introduction of new degrees.
-Although external changes do offer the chance of piloting new technologies, they do not seem to bring changes in attitudes in the teaching staff (which, after all, is bound to be the same).
-In absence of a clear answer in this direction, the right moment to introduce new technologies is always when the IT and managing staff is ready to support it (since, as we have seen before, "official" support is one of the factors that is most valued by teachers).
-
-At any rate, the general feeling that transpires from the survey is that it is essential for any institution to take into account the shareholder's opinion when introducing chatbots.
-This is true almost across the board, but in the case of chatbots (and instant messaging applications) their immediacy and the fact that they can enter into what we could call the private sphere makes this even more necessary.
+In our survey, we couldn't find an answer to the right moment for doing this
+introduction of chatbot technologies. Response to questions related to change of
+behaviour during and after the pandemic do not suggest that major (or minor)
+crisis could be an opportunity to introduce new technologies, since it does not
+bring major changes in attitude. A minor crisis would be, for instance, rollout
+of a new higher education law\footnote{We seem to have one of these, at least in
+  Spain, every 10 years or so}, or introduction of new degrees. Although
+external changes do offer the chance of piloting new technologies, they do not
+seem to bring changes in attitudes in the teaching staff (which, after all, is
+bound to be the same). In absence of a clear answer in this direction, the right
+moment to introduce new technologies is always when the IT and managing staff is
+ready to support it (since, as we have seen before, "official" support is one of
+the factors that is most valued by teachers).
+
+At any rate, the general feeling that transpires from the survey is that it is
+essential for any institution to take into account the shareholder's opinion
+when introducing chatbots. This is true almost across the board, but in the case
+of chatbots (and instant messaging applications) their immediacy and the fact
+that they can enter into what we could call the private sphere makes this even
+more necessary.
 
 % Future study (suggested by Noorhan): how COVID influenced adoption of these technologies.
-There are several future lines of work informed by our results of this survey.
-For instance, the rollout of extensive videoconferencing and virtual teaching solutions that the COVID pandemic has brought has also taught us a series of lessons.
-It increases isolation, for instance, and decreases the amount of synchronous contact that happens in the fringes of the classroom: teaching staff offices, before and after class.
-A future line of work would be focused on exactly this, and what kind of needs could be covered by chatbot technology.
-We will create a series of international surveys that will investigate this.
-
-Finally, the full extent of chatbot technology is not really being examined in these surveys.
-They can be connected to natural language processing engines with sentiment analysis as well as other analytics.
-Examining the mood of the class, as response to new material, assignment, exams or external events might help will help any student-centred teaching strategy, which will help students (and teachers) reach their learning objectives.
-This line of work, however, will be based on the introduction of some pilot study, combined with initial opinion assessment on the students.
+There are several future lines of work informed by our results of this
+survey. For instance, the rollout of extensive videoconferencing and virtual
+teaching solutions that the COVID pandemic has brought has also taught us a
+series of lessons. It increases isolation, for instance, and decreases the
+amount of synchronous contact that happens in the fringes of the classroom:
+teaching staff offices, before and after class. A future line of work would be
+focused on exactly this, and what kind of needs could be covered by chatbot
+technology. We will create a series of international surveys that will
+investigate this.
+
+Finally, the full extent of chatbot technology is not really being examined in
+these surveys. They can be connected to natural language processing engines with
+sentiment analysis as well as other analytics. Examining the mood of the class,
+as response to new material, assignment, exams or external events might help
+will help any student-centred teaching strategy, which will help students (and
+teachers) reach their learning objectives. This line of work, however, will be
+based on the introduction of some pilot study, combined with initial opinion
+assessment on the students.
 

### 2021-11-08 edubots_surveys.Rnw
Defined macro 'change' for changes
Deletes comments refs #50
Deletes comments refs #50 addresses first comment closes #53

@@
 \kwd{Higher education}
-% Antonio - add something related to "survey", "teachers' opinion" or so?
 \end{keyword}
 
-% MSC classifications codes, if any
-%\begin{keyword}[class=AMS]
-%\kwd[Primary ]{}
-%\kwd{}
-%\kwd[; secondary ]{}
-%\end{keyword}
-
 \end{abstractbox}
@@
 \end{frontmatter}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                            %%
-%% The Main Body begins here                  %%
-%%                                            %%
-%% Please refer to the instructions for       %%
-%% authors on:                                %%
-%% https://www.biomedcentral.com/getpublished %%
-%% and include the section headings           %%
-%% accordingly for your article type.         %%
-%%                                            %%
-%% See the Results and Discussion section     %%
-%% for details on how to create sub-sections  %%
-%%                                            %%
-%% use \cite{...} to cite references          %%
-%%  \cite{koon} and                           %%
-%%  \cite{oreg,khar,zvai,xjon,schn,pond}      %%
-%%                                            %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-The introduction of new technologies in the classroom involves a combination of
-teacher training, student enthusiasm and possibly acquiring new skills by
-both. Some technologies are readily adopted, but others require longer time for
+The introduction of new technologies in the classroom, \textcolor{blue}{to be successful, involves extra
+teacher training, devising methods for enhancing student engagement with the new
+technology, and indeed acquiring new skills by students and teachers alike}.
+Some technologies are readily adopted, but others require longer time for
 full adoption. In most cases, the magnitude of the uptake of the new technology

### 2021-11-08 edubots_surveys.Rnw
Including more text by @noorhanabbas, #48, closes #55

@@
 % EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
-{\sf anonymized European Project}, the sponsor of this study, is to gather,
-analyse and disseminate best practices on the use of chatbots in higher
-education institutions.
-
- The line of research of which this paper is a part has involved two phases of
- data collection.
+{\sf anonymized European Project}, the sponsor of this study, is to
+\textcolor{blue}{explore best practices and innovative use of chatbots, and to create 
+a learning community of educators in higher education institutions.
+The majority of studies conducted so far have studied how these 
+messaging applications and/or chatbots are used to deliver personalised
+learning in classrooms that occurs anytime anywhere, 
+promote collaborative learning experiences, group discussions \cite{panah2020study}
+and for boosting students' sense of belonging to their 
+institutions\cite{abbas2021onlinechat}. Hence, due to the paucity of research
+that explores the use of these technologies from the teachers' perspectives,
+this paper aims to investigate their opinions/needs and the
+challenges/opportunities of adopting these technologies in classrooms
+to paint a better picture of how they can positively contribute to enhancing
+the learning process in higher education institutions.}
+
+\textcolor{blue}{In this study, data collection involved two phases}
  \begin{itemize}

### 2021-11-08 edubots_surveys.Rnw
Fix by @noorhanabbas closes #58

@@
 WhatsApp is, at least in most Western countries, the most popular MIM platform
-used by educators to give assignments' feedback to students, support course
+used by educators to \textcolor{blue}{provide} assignments' feedback to students, support course
 discussions, and provide learning resources in informal learning settings

### 2021-11-08 edubots_surveys.Rnw
Fix by @noorhanabbas closes #61
Fix by @noorhanabbas closes #63

@@
 assistant chatbot developed on the Telegram messaging platform. In this study,
-Telegram platform was chosen because it is easy to use, students are familiar
+the Telegram platform is chosen because it is easy to use, students are familiar
 with its features, and it enables them to exchange messages in different formats
@@
 them more hints and reporting it to their educator's dashboard
-\cite{fernoagua2018intelligent}. This can help educators to locate those
-students that need their attention and send to them more educational resources
-relevant to their academic attainment.
+\cite{fernoagua2018intelligent}. This can help educators locate those
+students that need more attention and send them more educational resources
+relevant to their academic attainment. \textcolor{blue}{In addition, a recent study
+has analysed how the use of chatbots positively affected the learning outcomes
+of students in a Chinese class \cite{doi:10.1177/0735633120929622}}.
 
@@
 where, according to Hobert \cite{hobert2019you}, specific pedagogical factors
-such as learning success or increased motivation are more important.  Therefore,
-to develop efficient chatbots for higher education, all stakeholders'
+such as learning success and increased motivation are more important.  Therefore,
+to develop \textcolor{blue}{effective} chatbots for higher education, all stakeholders'
 (i.e. educators, students, institutions, etc) needs should be carefully
@@
 Besides, the present work is focused on the other key actor in this challenge,
-i.e. educators. Their attitudes have been studied very recently by Chocarro et
+i.e. educators. \textcolor{blue}{How they accepted chatbots} has been studied very recently by Chocarro et
 al. \cite{doi:10.1080/03055698.2020.1850426}, who, by analysing surveys, created

### 2021-11-08 edubots_surveys.Rnw
Fix by @noorhanabbas closes #64 also #50
Add highlight
minor fixes refs#48

@@
 
-%Why messaging apps are relevant here --> connect to the development of chatbots
-Group messaging apps have become a powerful tool for keeping touch with
+Group messaging apps have become a powerful tool for \textcolor{blue}{communicating} with
 students. Also, many of them have built-in chatbots to enhance the learning
@@
 Fig. \ref{figure:predictor}). Two clusters occurred from the analysis: cluster 1
-(n=78, 60.9\%) was comprise of instructors who did not value interaction media
+(n=78, 60.9\%) is formed with instructors who did not value interaction media
 pluggability, connectivity, official formation, but valued interaction media
-analytics, familiarity, support by the institution, while cluster 2 (n=50,
-39.1\%) was comprise of instructors from which the majority did not value media
+analytics, familiarity, support by the institution; cluster 2 (n=50,
+39.1\%) groups instructors that did not value media
 analytics, official formation, familiarity, but valued pluggability,
@@
 results, and that should require further study, is: Are teachers really aware
- of the possibilities of chatbots in the classroom? The reason to ask ourselves
- this question is due to the fact of the small number of responses for other
- uses in comparison with the other approaches proposed. Another way to look
- about it is that, unless you provide the specific instructions on how to use a
+of the possibilities of chatbots in the classroom? \textcolor{blue}{The survey 
+only listed a few functionalities for the chatbots and only a few subjects selected 
+the option "Others". This may suggest  that most teachers did not really understand 
+at this point the actual potential of chatbots.} Another way to look about it is 
+that, unless you provide the specific instructions on how to use a
 tool, the teaching staff is already too busy or burn out to think about
@@
 experienced. This will probably require further study, but also will need to be
-taken into account when introducing chatbot technologies in the classroom: it
-will have to be as simple, and as satisfactory, ad possible, to (possibly)
-delete this existing perception.
+taken into account when introducing chatbot technologies in the classroom: 
+\textcolor{blue}{it will have to be as simple, and as satisfactory, as possible, 
+to (possibly) change this existing perception}.
 

### 2021-11-08 edubots_surveys.Rnw
fixes in p19 and p20 refs#48

@@
 proportion to use them for grades and FAQs in comparison with Vocational High
-School teachers. This seems reasonable as the frequency of seeing the students
-is smaller at the University so, automating the grade notification for
-continuous evaluation could seem much more comfortable using an automated tool
-than using the traditional platform. Furthermore, the high student/teacher
+School teachers. \textcolor{blue}{
+This seems reasonable as the frequency of seeing the students
+is lower at the University so, an automatic tool for grade notification for
+continuous evaluation seems more helpful}. 
+Furthermore, the high student/teacher
 ratios that university teachers have to deal with could be another reason to
@@
 are. From this concrete plot it is interesting as well the fact that very few
-young/inexperience teachers are willing to use chatbots for other uses. This
-reinforces the hypothesis thrown at the beginning of this section and, as these
-teachers have less experience, they also have less field of view to think about
-ways of using chatbots.
+young/inexperience teachers are willing to use chatbots for other uses. \textcolor{blue}{This
+reinforces the hypothesis thrown at the beginning of this section that younger teachers have less experience to consider new ways of using chatbots in their daily work.}
 
@@
    is probably due to the strict European data regulations and to avoid the
-   overhead required to sing up and deleting students from year to year.
+   overhead required to \textcolor{blue}{sign up new students every year}.
  \item Teachers need sustainability. The main reason is that implementing
@@
 messaging applications that their institutions support.  Technology adoption
-literature often focus on users’ perceptions of the technology’s usefulness and
+literature often \textcolor{blue}{focuses} on users’ perceptions of the technology’s usefulness and
 ease of use as important prerequisites for successful adoption and
@@
 these applications and shape the social and educational experiences of their
-students.  This integration, to be fruitful, institutions have to ensure that
+students. \textcolor{blue}{To accomplish this fruitful integration}, institutions have to ensure that
 these messaging applications not only are GDPR compliant to keep students’ data

### 2021-11-08 edubots_surveys.Rnw
fixes more typos in p20 and 21 refs#48

@@
 \item Experience on the job: up to 5 years, 5-15 years, 15-25 years, more than 25 years.
-\item Type of degree: university, other tertiary education. This question was implicit in the first survey, since one and the other filled different forms, it was explicit in the second survey.
+\textcolor{blue}{
+\item Type of degree: university, other tertiary education.
+This question was implicit in the first survey: there were two different versions of the survey.
+However, it was and explicit question in the second survey.}
 \end{itemize}
@@
 % Including questions in surveys
-The {\bf first survey}, which focused about the use of messaging apps in class, and which tried to address mainly RQ2 and RQ3, 
+The {\bf first survey}, which \textcolor{blue}{focused on} the use of messaging apps in class, and which tried to address mainly RQ2 and RQ3, 
 % Antonio - I guess it refers to RQ3. ;)
@@
 \item Students self-organize and with the teacher not being part of any chat group
-\item A chat group with the all the students and teachers of the School/High-School/Faculty
+\textcolor{blue}{
+\item A chat group with all the students and teachers of the School/High-School/Faculty
+}
 \item A chat group with all the students and teachers of the same study year

### 2021-11-09 edubots_surveys.Rnw
Addressed   P24: "using safer alternatives": This expression is unclear. On the other hand, it is unclear what you were aiming to find out through this option.

@@
 19\% of the chi-square test results. Also, the number of educators from
-Technology or Engineering that started using safer alternatives are less than
+Technology or Engineering that started using safer alternatives \footnote{This addresses the issue of insecure/unsafe applications which do not cipher messages or can be easily compromised exposing information} are less than
 expected (compared to the educators from other disciplines). Bear in mind that

### 2021-11-09 edubots_surveys.Rnw
Addressed  P24, l10: "teacher formation course": Probable the expression "Professional Development course" might be used.

@@
 % Olia - see my comment above.
-It was filled by teachers that were also students in a teacher formation course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers who knew about it by emails from the authors, or from the vicedeanship for International Relations that included it in its newsletter.
+It was filled by teachers that were also students in a Professional Development course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers who knew about it by emails from the authors, or from the vicedeanship for International Relations that included it in its newsletter.
 This means that there might be a higher proportion of 1) teachers with few years of experience 2) teachers from the computer science faculty and 3) teachers from Granada.

### 2021-11-09 edubots_surveys.Rnw
Fixing reference to 7
Reference to Section 7 (Appendix I) is now clearer
Adding "i.e."
Addresing another comment

@@
 (68.4\%) and 89 at other tertiary education institutions (31.6\%). Survey
-questions are shown in \ref{app:questions}.
+questions are shown in Appendix I (Section \ref{app:questions}).
 
@@
 realized that there were some prior issues mainly related to the adoption of a
-technology, chatbots, that generally piggybacks on another, messaging
+technology, i.e. chatbots, that generally piggybacks on another, i.e. messaging
 applications. In a technology adoption model, perceived ease of use and

### 2021-11-09 edubots_surveys.Rnw
Rephrasing sentence about clarification of RQ1
Addresing another reviewer's comment
Rephrasing about teachers in Humanities
Addresing another comment

@@
 other messaging app, and whether they use messaging apps provided by their
-academic institution (see Table \ref{tab:use_messapps}). In this case, it is
-maybe in order a certain clarification. While we had in mind, as indicated by
-the possible answers, instant messaging applications when making this question,
+academic institution (see Table \ref{tab:use_messapps}). In this case, we would like 
+to add a clarification. While we had in mind, as indicated by the possible answers, 
+instant messaging applications when making this question,
 we included these institution-provided applications mainly for completion. But
@@
 Telegram). With respect to specific disciplines, Engineering and Technology
-teachers are more active in their use, although it is also relevant the amount
-of teachers from Humanities that answered they used these apps in their classes
+teachers are more active in their use, but the amount of teachers from Humanities 
+who answered they used these apps in their classes is also remarkable
 (around 60\% use the apps provided by their institutions).

### 2021-11-09 edubots_surveys.Rnw
Clarify the survey to which we refer to
Addressing another comment

@@
 \cite{MoraChatbots2021:anon}; however, an initial exploration of results led us
-to create a second survey. The survey items focused on the use of messaging apps
+to create a second survey. The new survey items focused on the use of messaging apps
 in the teaching practice, the type of chatbot use cases that teachers consider

### 2021-11-09 edubots_surveys.Rnw
Colouring changes
I forgot to do it before. :_D

--- 2021-11-09 edubots_surveys.Rnw
@@
 \cite{MoraChatbots2021:anon}; however, an initial exploration of results led us
-to create a second survey. The survey items focused on the use of messaging apps
+to create a second survey. The \textcolor{blue}{new survey} items focused on the use of messaging apps
 in the teaching practice, the type of chatbot use cases that teachers consider
@@
 (68.4\%) and 89 at other tertiary education institutions (31.6\%). Survey
-questions are shown in Appendix I (Section \ref{app:questions}).
+questions \textcolor{blue}{are shown in Appendix I (Section \ref{app:questions})}.
 
@@
 realized that there were some prior issues mainly related to the adoption of a
-technology, i.e. chatbots, that generally piggybacks on another, i.e. messaging
-applications. In a technology adoption model, perceived ease of use and
+technology, \textcolor{blue}{i.e. chatbots}, that generally piggybacks on another, \textcolor{blue}{i.e. messaging
+applications}. In a technology adoption model, perceived ease of use and
 perceived usefulness are essential. But it is going to be very difficult for
@@
 other messaging app, and whether they use messaging apps provided by their
-academic institution (see Table \ref{tab:use_messapps}). In this case, we would like 
-to add a clarification. While we had in mind, as indicated by the possible answers, 
+academic institution (see Table \ref{tab:use_messapps}). \textcolor{blue}{In this case, we would like 
+to add a clarification}. While we had in mind, as indicated by the possible answers, 
 instant messaging applications when making this question,
@@
 Telegram). With respect to specific disciplines, Engineering and Technology
-teachers are more active in their use, but the amount of teachers from Humanities 
-who answered they used these apps in their classes is also remarkable
+teachers are more active in their use, \textcolor{blue}{but the amount of teachers from Humanities 
+who answered they used these apps in their classes is also remarkable}
 (around 60\% use the apps provided by their institutions).

### 2021-11-13 edubots_surveys.Rnw
Changing a word
Fixing one suggestion
Restructured the Discussion and Conclusion sections
I have collated the discussion and the conclusion sections into one section.  All the extra text I copied it at the bottom of the page in a section marked 'Extra'.  I will work again on it tomorrow.

@@
 university and other for tertiary non-university teachers. Questions and
-responses were the same, except for the type of tertiary degrees that were
-taught. In both cases, we used mainly mailing lists, as well as Telegram groups,
+responses were the same, except for the type of tertiary degrees that
+\textcolor{blue}{were considered}. In both cases, we used mainly mailing lists, as well as Telegram groups,
 to spread the link to the form. The university form was spread in Spanish
@@
 The frequencies cross tabulated are given in Table \ref{tab:sector*covid}.
-In effect, this finding indicates that how teachers responded to the use of messaging apps during the pandemic and in particular, whether they changed their habits in the use of apps for teaching purposes, was related to their sector (university vs vocational).
+In effect, this finding indicates that how teachers
+responded to the use of messaging apps during the pandemic and in particular, whether they changed their habits in the use of apps for teaching purposes, was related to their sector (university vs vocational).
 %
@@
 % ********************** Discussion section *******************
-\section{Discussion}
-
-Our initial intention in the design of these surveys was to probe the opinions
-of tertiary education teachers in the introduction of chatbot technologies in
-class. We wanted to find the answer to four research questions, of which the
-first was to check whether teachers already used some kind of messaging
-application, and the one they preferred. Depending on the answer, different
-technologies could be (or not) available for the introduction of chatbots. In
-this case, the design of the survey introduced some ambiguity on what we really
-consider ``messaging technology'', that was eventually resolved by the answers;
-apparently, anything that sends messages (even if they are not instant, even if
-they do not have a dedicated application) was the concept in the mind of the
-surveyed.
-
-Additionally, the question on COVID reflected the big challenge that represents
-changing habits, even in the case of a major crisis. Very few people actually
-changed, with women vs. men being an exception, as well as those teaching social
-sciences standing out among the rest. We do not have any kind of explanation for
-this behaviour, other than technologies are perceived, and adopted, in a
-different way depending on background and, apparently, gender.
-
-One of the most interesting questions that can arise from the analysis of the
-results, and that should require further study, is: Are teachers really aware
-of the possibilities of chatbots in the classroom? \textcolor{blue}{The survey 
-only listed a few functionalities for the chatbots and only a few subjects selected 
-the option "Others". This may suggest  that most teachers did not really understand 
-at this point the actual potential of chatbots.} Another way to look about it is 
-that, unless you provide the specific instructions on how to use a
-tool, the teaching staff is already too busy or burn out to think about
-innovation.
-
-It is also likely that their opinions towards chatbots are informed by negative
-experiences with customer support chatbots, which is what most people will have
-experienced. This will probably require further study, but also will need to be
-taken into account when introducing chatbot technologies in the classroom: 
-\textcolor{blue}{it will have to be as simple, and as satisfactory, as possible, 
-to (possibly) change this existing perception}.
-
-Regarding gender grouping, both genders agree in their uses, so it seems not
-relevant at all. When looking at the plot containing the sector differentiation
-it is interesting to observe how university teachers prefer in a higher
-proportion to use them for grades and FAQs in comparison with Vocational High
-School teachers. \textcolor{blue}{
-This seems reasonable as the frequency of seeing the students
-is lower at the University so, an automatic tool for grade notification for
-continuous evaluation seems more helpful}. 
-Furthermore, the high student/teacher
-ratios that university teachers have to deal with could be another reason to
-have a higher number of them willing to use chatbots for FAQs. This could
-ameliorate the number of misunderstandings and email overload that so many
-students might generate.
-
-The results, when grouping by experience, confirm the previous observation that
-experienced teachers are not afraid of changes and are willing to accept new
-technological challenges, at least, in the same way that younger teachers
-are. From this concrete plot it is interesting as well the fact that very few
-young/inexperience teachers are willing to use chatbots for other uses. \textcolor{blue}{This
-reinforces the hypothesis thrown at the beginning of this section that younger teachers have less experience to consider new ways of using chatbots in their daily work.}
-
+\section{Discussion and Conclusion}
+
+This study sheds the light on educators' growing usage of messaging applications in classrooms even before COVID19.  Recent research \cite{panah2020study} 
+examining the use of messaging applications in higher education claimed that WhatsApp is widely used by educators. 
+However, in this study, although 44% of educators reported using WhatsApp in their classrooms, more than half of the survey responses (nearly 56%)
+claim using technologies supported by their institutions. One possible explanation for this finding could be that educators wanted to ensure that 
+their institutions can oversee their efforts in supporting their students during the learning process.  Another reason could be attributed to 
+institutions mandating the use of specific technologies that they support.  Hence, this finding probes more queries about the actual reasons 
+contributing to this shift in technology preference among educators and its implications on the students/educators interaction and learning. 
+In addition, as recent research examining students' usage of messaging applications with their peers in higher education \cite{abbas2021onlinechat}
+argue that students prefer to use the non-institution messaging applications to form informal discussion groups with their peers, further 
+research should aim to investigate this wide spectrum of usage of these applications and their impact on the learning process.
+
+The question examining the use of messaging applications during the pandemic (COVID19) reflects the big challenge of having to 
+change habits during a major crisis. The survey responses reveal some gender differences in this respect as 31% of female educators 
+reported moving to using messaging applications to cope with the new virtual mode of learning during the pandemic compared to only 17% of male educators.
+Moreover, the survey responses to the question that lists the different functionalities that a chatbot can be used for indicate that nearly 60%
+of educators favoured using chatbots in grading and 47.5% in answering students' FAQs.
+
+The survey results, when grouping by experience, confirm the previous observation that
+experienced teachers are willing to accept new technological challenges, at least, similar to younger teachers. Younger educators 
+are also willing to use chatbots for other uses.
+
+Therefore, as in many other methods of technology acceptance, answers to the survey suggest
+that the introduction of simple, and institution-supported, instant messaging
+and chatbot technologies would increase the perceived usefulness (which is one
+of the key metrics in technology acceptance models). Since most institutions
+already have some {\em virtual campus} or learning management system, adding
+some easy automation, or connection to personal instant messaging tools, could
+really help on board the learning community on these new technologies.
+
+% What kind of chatbots are preferred? (suggested by Fran)
+Once that initial introduction is done, teachers (and students as well) will
+probably prefer the kind of chatbots that alleviate bureaucratic or repetitive
+tasks, such as answering frequent questions or answers on class or assignment
+schedules. These will help the introduction of more complex chatbots that will
+affect more directly learning outcomes, such as chatbots that help students
+integrate in the class, or are able to identify (and address) learning problems
+in students or in groups of them. These as well should be accompanied by
+analytics on student interaction, as well as possibly some natural language
+processing (in vernacular language) that will help assess the general mood of
+the class, and how different material (or external factors) affect it.
+
+% No remarkable differences between different groups.
+This introduction of chatbots and chatbot technology will be helped by the fact
+that no discernible differences are found between different groups. Even if
+chatbots do have some potential for personalization or customization, based on
+the class material, student and teaching staff, the general introduction of the
+technology can be done in a general way and for all disciplines, teaching
+experience and gender.
+
+% Only some COVID-response relationship.
+In our survey, we couldn't find an answer to the right moment for doing this
+introduction of chatbot technologies. Response to questions related to change of
+behaviour during and after the pandemic do not suggest that major (or minor)
+crisis could be an opportunity to introduce new technologies, since it does not
+bring major changes in attitude. A minor crisis would be, for instance, rollout
+of a new higher education law\footnote{We seem to have one of these, at least in
+  Spain, every 10 years or so}, or introduction of new degrees. Although
+external changes do offer the chance of piloting new technologies, they do not
+seem to bring changes in attitudes in the teaching staff (which, after all, is
+bound to be the same). In absence of a clear answer in this direction, the right
+moment to introduce new technologies is always when the IT and managing staff is
+ready to support it (since, as we have seen before, "official" support is one of
+the factors that is most valued by teachers).
+
+At any rate, the general feeling that transpires from the survey is that it is
+essential for any institution to take into account the shareholder's opinion
+when introducing chatbots. This is true almost across the board, but in the case
+of chatbots (and instant messaging applications) their immediacy and the fact
+that they can enter into what we could call the private sphere makes this even
+more necessary.
+
+% Future study (suggested by Noorhan): how COVID influenced adoption of these technologies.
+There are several future lines of work informed by our results of this
+survey. For instance, the rollout of extensive videoconferencing and virtual
+teaching solutions that the COVID pandemic has brought has also taught us a
+series of lessons. It increases isolation, for instance, and decreases the
+amount of synchronous contact that happens in the fringes of the classroom:
+teaching staff offices, before and after class. A future line of work would be
+focused on exactly this, and what kind of needs could be covered by chatbot
+technology. We will create a series of international surveys that will
+investigate this.
+
+Finally, the full extent of chatbot technology is not really being examined in
+these surveys. They can be connected to natural language processing engines with
+sentiment analysis as well as other analytics. Examining the mood of the class,
+as response to new material, assignment, exams or external events might help
+will help any student-centred teaching strategy, which will help students (and
+teachers) reach their learning objectives. This line of work, however, will be
+based on the introduction of some pilot study, combined with initial opinion
+assessment on the students.
+
+%***********************************Extra************************************************
+
+Technology adoption literature often \textcolor{blue}{focuses} on users’ perceptions of the technology’s usefulness and
+ease of use as important prerequisites for successful adoption and
+utilization. Nevertheless, in higher education, institutions’ role in
+integrating these tools to their educational systems can improve the uptake of
+these applications and shape the social and educational experiences of their
+students. \textcolor{blue}{To accomplish this fruitful integration}, institutions have to ensure that
+these messaging applications not only are GDPR compliant to keep students’ data
+secure but also should provide IT support to all stakeholders who use the
+applications.
 As it appears in the responses presented above, teachers’ responses are
@@
 media features of messaging apps.
-
 From a qualitative point of view, these results show consensus in a few key aspects:
@@
 \end{itemize}
-
 An analysis of survey questions related to RQ4 seems to indicate that teachers
@@
 
-The key findings of this study shed the light on educators’ preference to use
-messaging applications that their institutions support.  Technology adoption
-literature often \textcolor{blue}{focuses} on users’ perceptions of the technology’s usefulness and
-ease of use as important prerequisites for successful adoption and
-utilization. Nevertheless, in higher education, institutions’ role in
-integrating these tools to their educational systems can improve the uptake of
-these applications and shape the social and educational experiences of their
-students. \textcolor{blue}{To accomplish this fruitful integration}, institutions have to ensure that
-these messaging applications not only are GDPR compliant to keep students’ data
-secure but also should provide IT support to all stakeholders who use the
-applications.
-
-Moreover, this study clarifies the differences between the teachers’
-perspectives and/or intentions and that of their students when using the
-messaging applications in higher education.  Teachers tend to adopt technologies
-supported by their institutions.  This could be to ensure that their
-universities can oversee their efforts in supporting their students during the
-learning process.  Another reason could be their familiarity with the technology
-provided by their institutions. On the other hand, students use the
-non-institution messaging applications to form informal discussion groups with
-their peers.  It is worth noting that peer support and collaboration is
-inseparable from learning \cite{timmis2012constant} and correlates positively
-with higher retention in higher education \cite{o2014front}.  Therefore, both
-perspectives are complementary and play different roles in promoting the
-learning process.
-
 % Noorhan suggest that using some simple things could increase the perceived usefulness - JJ
-As in many other methods of technology acceptance, answers to the survey suggest
-that the introduction of simple, and institution-supported, instant messaging
-and chatbot technologies would increase the perceived usefulness (which is one
-of the key metrics in technology acceptance models). Since most institutions
-already have some {\em virtual campus} or learning management system, adding
-some easy automation, or connection to personal instant messaging tools, could
-really help onboard the learning community on these new technologies.
-
-% What kind of chatbots are preferred? (suggested by Fran)
-Once that initial introduction is done, teachers (and students as well) will
-probably prefer the kind of bots that alleviate bureaucratic or repetitive
-tasks, such as answering frequent questions or answers on class or assignment
-schedules. These will help the introduction of more complex chatbots that will
-affect more directly learning outcomes, such as chatbots that help students
-integrate in the class, or are able to identify (and address) learning problems
-in students or in groups of them. These as well should be accompanied by
-analytics on student interaction, as well as possibly some natural language
-processing (in vernacular language) that will help assess the general mood of
-the class, and how different material (or external factors) affect it.
-
-% No remarkable differences between different groups.
-This introduction of chatbots and chatbot technology will be helped by the fact
-that no discernible differences are found between different groups. Even if
-chatbots do have some potential for personalization or customization, based on
-the class material, student and teaching staff, the general introduction of the
-technology can be done in a general way and for all disciplines, teaching
-experience and gender.
-
-% Only some COVID-response relationship.
-In our survey, we couldn't find an answer to the right moment for doing this
-introduction of chatbot technologies. Response to questions related to change of
-behaviour during and after the pandemic do not suggest that major (or minor)
-crisis could be an opportunity to introduce new technologies, since it does not
-bring major changes in attitude. A minor crisis would be, for instance, rollout
-of a new higher education law\footnote{We seem to have one of these, at least in
-  Spain, every 10 years or so}, or introduction of new degrees. Although
-external changes do offer the chance of piloting new technologies, they do not
-seem to bring changes in attitudes in the teaching staff (which, after all, is
-bound to be the same). In absence of a clear answer in this direction, the right
-moment to introduce new technologies is always when the IT and managing staff is
-ready to support it (since, as we have seen before, "official" support is one of
-the factors that is most valued by teachers).
-
-At any rate, the general feeling that transpires from the survey is that it is
-essential for any institution to take into account the shareholder's opinion
-when introducing chatbots. This is true almost across the board, but in the case
-of chatbots (and instant messaging applications) their immediacy and the fact
-that they can enter into what we could call the private sphere makes this even
-more necessary.
-
-% Future study (suggested by Noorhan): how COVID influenced adoption of these technologies.
-There are several future lines of work informed by our results of this
-survey. For instance, the rollout of extensive videoconferencing and virtual
-teaching solutions that the COVID pandemic has brought has also taught us a
-series of lessons. It increases isolation, for instance, and decreases the
-amount of synchronous contact that happens in the fringes of the classroom:
-teaching staff offices, before and after class. A future line of work would be
-focused on exactly this, and what kind of needs could be covered by chatbot
-technology. We will create a series of international surveys that will
-investigate this.
-
-Finally, the full extent of chatbot technology is not really being examined in
-these surveys. They can be connected to natural language processing engines with
-sentiment analysis as well as other analytics. Examining the mood of the class,
-as response to new material, assignment, exams or external events might help
-will help any student-centred teaching strategy, which will help students (and
-teachers) reach their learning objectives. This line of work, however, will be
-based on the introduction of some pilot study, combined with initial opinion
-assessment on the students.
 

### 2021-11-14 edubots_surveys.Rnw
Added 'Generally' to the TAM

--- 2021-11-09 edubots_surveys.Rnw
@@
 
-Our intention from the beginning was to try to gather a sufficient amount of
-responses in all sectors, as well as cover different sectors of higher
-education. In doing so, an online survey was administered (i.e., Google Form),
-in Spanish, which was intended to be answered in a very short amount of
-time. Initially, our intention was to mirror the questions used in
-\cite{MoraChatbots2021:anon}; however, an initial exploration of results led us
-to create a second survey. The \textcolor{blue}{new survey} items focused on the use of messaging apps
-in the teaching practice, the type of chatbot use cases that teachers consider
+This study aims to collect rich data about the use of messaging applications and chatbots
+by educators in both universities and colleges. To achieve this goal, an online survey was designed and developed using Google Forms
+in Spanish. Initially, the intention was to mirror the questions used in
+\cite{MoraChatbots2021:anon}; which explored students' views about the use of messaging applications in classrooms.
+However, the initial exploration of results led us
+to create a second survey in order to collect more data about educators' preferences in particular. The \textcolor{blue}{new survey} items 
+focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider
 useful to be used in their teaching, and the type of interactions that teachers
@@
 university and other for tertiary non-university teachers. Questions and
-responses were the same, except for the type of tertiary degrees that were
-taught. In both cases, we used mainly mailing lists, as well as Telegram groups,
-to spread the link to the form. The university form was spread in Spanish
-(mainly Andaluc\'{\i}a and Galicia) universities, and also Costa Rica and
-Mexico. The tertiary non-university teachers are based mainly in
+responses were the same, except for the type of tertiary degrees that
+\textcolor{blue}{were considered}. The survey was piloted by the authors of the paper and their colleagues before using it in the 
+study.  All the comments collected from this trial were incorporated in the survey.
+We used mainly mailing lists, as well as Telegram groups,
+to post the survey link to reach out to more educators. The university form was sent to Spanish
+(mainly Andaluc\'{\i}a and Galicia) universities, and also  universities in Costa Rica and
+Mexico. The tertiary (non-university/college) teachers were based mainly in
 Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of
@@
 technology, \textcolor{blue}{i.e. chatbots}, that generally piggybacks on another, \textcolor{blue}{i.e. messaging
-applications}. In a technology adoption model, perceived ease of use and
+applications}. Generally, in a technology adoption model, perceived ease of use and
 perceived usefulness are essential. But it is going to be very difficult for

### 2021-11-17 edubots_surveys.Rnw
Added a sentence about survey validation
Update edubots_surveys.Rnw
I changed the methods and the results

@@
 
-Our intention from the beginning was to try to gather a sufficient amount of
-responses in all sectors, as well as cover different sectors of higher
-education. In doing so, an online survey was administered (i.e., Google Form),
-in Spanish, which was intended to be answered in a very short amount of
-time. Initially, our intention was to mirror the questions used in
-\cite{MoraChatbots2021:anon}; however, an initial exploration of results led us
-to create a second survey. The \textcolor{blue}{new survey} items focused on the use of messaging apps
+This study followed a quantitative approach towards addressing it research objectives. In doing so, an online survey was administered (i.e., Google Form),
+in Spanish, comprised by six questions focusing on demographic data (i.e., sector, gender, degrees, discipline, age, teaching experience), followed by four multiple choice questions allowing the participants to choose multiple answers in each of those.
+Thee multiple choice questions focused on the use of messaging apps
 in the teaching practice, the type of chatbot use cases that teachers consider
@@
 
-The {\bf initial survey} was done in two separate Google forms, one for
-university and other for tertiary non-university teachers. Questions and
-responses were the same, except for the type of tertiary degrees that
-\textcolor{blue}{were considered}. In both cases, we used mainly mailing lists, as well as Telegram groups,
-to spread the link to the form. The university form was spread in Spanish
-(mainly Andaluc\'{\i}a and Galicia) universities, and also Costa Rica and
-Mexico. The tertiary non-university teachers are based mainly in
-Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of
+This survey was administered to both university and tertiary non-university teachers (i.e., teaching in the vocational sector).
+The responders were reached out through the use of mailing lists and Telegram groups.
+The survey was shared among university teachers that teach in
+Spanish (mainly Andaluc\'{\i}a and Galicia) universities, and also Costa Rica and
+Mexico, and tertiary non-university teachers who are based mainly in
+Andaluc\'{\i}a. Data collection with the use of the survey took place in the first quarter of
 2021, post-pandemic and while, at least in Spain, many universities had
-mandatory virtual teaching.
+mandatory virtual teaching.Survey questions \textcolor{blue}{are shown in Appendix I (Section \ref{app:questions})}. 
+Responses were stored automatically in a Google Drive spreadsheet.
 
 A total of 282 teachers responded to the survey: 193 teaching at the University
-(68.4\%) and 89 at other tertiary education institutions (31.6\%). Survey
-questions \textcolor{blue}{are shown in Appendix I (Section \ref{app:questions})}.
-
-Responses were stored automatically in a Google Drive spreadsheet. Eventually,
-the results from the two forms we used for the first survey were collated in a
-single spreadsheet. Next we will show the results and analyse them.
+(68.4\%) and 89 at other tertiary education institutions (31.6\%).From those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%) and 5 teachers preferred not to indicate their gender (1.8\%).
+In terms of age, the majority of the participants (n=111) in this survey was 45-55 years old (39.4\%), while 91 teachers were 35-45 (32.3\%), 46 were 25-35 (16.3\%) and 34 teachers were older than 55 (12.1\%).
+Last, 84 teachers had a teaching experience of 16-25 years (29.8\%), 75 teachers 6-15 years of experience (26.6\%), 69 teachers had 0-5 years of experience (24.5\%) and finally, 54 teachers had more than 25 years of teaching experience (19.1\%).
+
+For addressing the 4th research question, a second online survey was administered (i.e., Google Form), in Spanish, comprised by four questions focusing on demographic data (i.e., gender, age, degrees, teaching experience), followed two multiple choice questions with single answers and one multiple choice questions allowing the participants to choose multiple answers.
+The items of this survey focused on the kind of interaction media features that the teachers value the most.
+The survey was administered to university teachers teaching at the University of Granada, but also student teachers who attended a teacher formation course (on the use of new technologies in higher education).
+The responders were reached out through the use of mailing lists, while an invitation to participate in the survey was also promoted in the newsletter of the vice deanship for International Relations of the University of Granada.
+Survey questions \textcolor{blue}{are shown in Appendix I (Section \ref{app:questions})}.
+%make this appendix 2 and delete the paragraph before the questions. 
+Responses were stored automatically in a Google Drive spreadsheet.
+A total of 205 teachers responded to the second survey: 187 graduate teachers (91.2%) and 18 student teachers (8.8%).
+From those, 124 were (60.5\%), 65 female (31.7\%) and 16 teachers preferred not to indicate their gender (7.8\%).
+In terms of age, the majority of the participants (n=70) was again, as in the first survey, 45-55 years old (34.1\%), while 67 teachers were 35-45 (32.7\%), 42 were 25-35 (20.5\%) and 26 teachers were older than 55 (12.7\%).
+In terms of teaching experience, 59 teachers had a teaching experience of 16-25 years (28.8\%), 51 teachers had 6-15 years (24.9\%) and 0-5 years of experience (24.9\%), and 44 teachers more than 25 years of teaching experience (21.5\%).
 
@@
 \label{sec:res}
-
-% Describe the survey and population
-We collected responses from 282 teachers from Spain and Spanish Speaking
-countries for \textit{survey1} and 205 for \textit{survey2}. The two forms were
-open for approximately the same amount of time, around two months. The sample
-includes mostly teachers from university, although about 32\% and 8\% are from
-vocational education in the first and second survey respectively. Regarding
-gender, 61\% of the teachers were male and 32\% female, while approximately 5\%
-chose not to disclose it. Finally, the responses are more or less equally
-distributed according to the teaching experience, showing 24\% of responses from
-teachers with 5 or less years of experience, 26\% for 6-15 years of experience,
-30\% for 16-25, and 20\% for teachers with more than 25 years of experience.
 
@@
 
-% % Olia suggests to delete this, as well as figure 1.
-% Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar. %, and as a matter of fact,
-% Additionally, as a matter of fact, as Figure \ref{figure:age.vs.exp} shows, age and experience are correlated strongly, with experience being roughly 20-30 years less than age. 
-% This might indicate that a differential analysis for age and experience will not yield significant differences, except maybe in the 6-15 years experience group, which is spread over all ages.
-At any rate, experience seems to be the dominating factor here and we'll use experience only unless we detect some significant difference by age.
-
 % \begin{figure}[h!tbp]
@@
 
-We will try to find the answers to the four research questions next, by
-analysing the response to the different survey questions.
+The data analysis methods followed for addressing each one of the four research questions (RQ), as well as the respective results, are presented per RQ in the sections that follow.
 
@@
 
-Group messaging apps have become a powerful tool for \textcolor{blue}{communicating} with
-students. Also, many of them have built-in chatbots to enhance the learning
-process. After an initial analysis to the answers to the first survey, we
-realized that there were some prior issues mainly related to the adoption of a
-technology, \textcolor{blue}{i.e. chatbots}, that generally piggybacks on another, \textcolor{blue}{i.e. messaging
-applications}. Generally, in a technology adoption model, perceived ease of use and
-perceived usefulness are essential. But it is going to be very difficult for
-teachers to find {\em chatbots} easy to use if they, previously, do not
-consider, or simply use, the messaging tools to which they are attached.
-
-This is why for answering RQ1, teachers were queried about whether they use
+%Delete and transfer whatever is useful in the discussion section
+
+For answering RQ1, teachers were queried about whether they use
 messaging apps in their classes, specifically, Telegram, WhatsApp, Slack (an
@@
 other messaging app, and whether they use messaging apps provided by their
-academic institution (see Table \ref{tab:use_messapps}). \textcolor{blue}{In this case, we would like 
-to add a clarification}. While we had in mind, as indicated by the possible answers, 
-instant messaging applications when making this question,
-we included these institution-provided applications mainly for completion. But
-it should be noted that, in most cases, they are not {\em instant} messaging
-apps in the way Telegram or Facebook Messenger are; in most cases they are
-messaging facilities provided by learning management systems such as (usually)
-Moodle. So the answer to this question must be understood in two different ways:
-their preference for the {\em source} of the technology (university, any
-company) as well as the {\em type} of technology (instant, app based messaging
-systems vs. web-based systems integrated in another learning management system).
+academic institution (see Table \ref{tab:use_messapps}). \textcolor{blue}
+%OT: Why did we include these multiple ways of interpretation? In any case I suggest deleting this from here and moving it into the discussion section, if needed.
 
@@
 
-Although no significant differences were found regarding gender, female teachers
-answered they use instant messaging apps more than male teachers (about 10\%
-more). Also, teachers in vocational Education use WhatsApp more than university
-teachers. Regarding the distribution of the use of messaging apps per age, there
-are no significant differences for WhatsApp and apps provided by their own
-academic institutions. % Olia requests support for this. 
-However, younger teachers also use Telegram with more than 25\%, a percentage
-that falls to about 10\% for teachers that are 55 or older. %The third column
-                                %compares the use of these apps considering the
-                                %number of years of experience.
-One interesting result is that about 65\% of teachers with more than 25 years of
-experience use the platforms provided by their institutions while the percentage
-goes down to less than 50\% for teachers with 6-15 years of experience.
+%if you keep the sentence that follows, you should add evidence. Otherwise delete. 
+%delete the figure 
 %
@@
 assess whether a crisis will bring about some kind of change in the use of
-tools. The 282 answers are summarized in
+digital tools in the teaching practice. 
+%delete the following paragraph and the figures 
+The 282 answers are summarized in
 Figs. \ref{figure:gender*chatbots_use_postcovid},
@@
 
-A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
+Furthermore, a chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
 The relation between the latter variable and the instructors’ sector was significant, $X^{2}_{(4, N = 282)} = 9.598$, $p =0.048$.
@@
 
-% Olia - TODO: check for repetitions in the following paragraph that you added. thank you.
-Finally, we took a closer look at the post-covid changes and the variables
-gender, sector, and discipline for which the chi-square test is statistically
-significant as shown in Figures \ref{figure:gender*postcovid_chisq},
-\ref{figure:sector*postcovid_chisq}, \ref{figure:discipline*postcovid_chisq}
-respectively. Each figure shows on the left, a graph that represents the
-Pearson's residuals of the chi-square test results and a table on the right part
-that shows the contribution of each cell to the test. In the Pearson's residual
-graphs, the responses were shortened for the sake of clarity according to: 1)
-\textit{Did/do} stands for \textit{Yes, I did use it before and do use it now};
-2) \textit{Didn't/do} for \textit{Yes, I didn’t use any messaging app before,
-  but do use it now}; 3) \textit{safer} for \textit{Yes, I use a safer messaging
-  app now}; 4) \textit{Didn't/Don't} for \textit{No, I didn’t use it before and
-  don’t use it now}.
-%
-\begin{figure}[h!tbp]
-\begin{center}
-    \begin{minipage}[c]{0.45\textwidth}
-        \centering
-<<gender_postcovid_chisq, echo=FALSE, fig.width=17/2.54, fig.height=10/2.54>>=
-df <-select(survey.pilot.postCOVID, PostCOVID.changes, Gender, Sector, Experience, Discipline)
-df[as.character(df$Gender)!="PNTS", ] -> df1
-df1[as.character(df1$Gender)!="No", ] -> df1
-df1[as.character(df1$Discipline)!="No", ] -> df1
-df1[as.character(df1$Experience)!="No", ] -> df1
-df1[as.character(df1$Sector)!="No", ] -> df1
-survey.pilot.postCovidChisq<- droplevels(df1)
-
-covidChanges.vs.Gender<-table(survey.pilot.postCovidChisq$Gender, survey.pilot.postCovidChisq$PostCOVID.changes)
-colnames(covidChanges.vs.Gender)<- c("Did/do", "Didn't/do","safer", "Didn't/don't")
-covidChanges.vs.Gender<-covidChanges.vs.Gender[,c(3,2,1,4)]
-chisq<-chisq.test(covidChanges.vs.Gender)
-corrplot(chisq$residuals, is.corr = FALSE)
-@
-    \end{minipage}
-    %This tables comes from (TODO: generate them automatically from the data)
-    %contrib <- 100*chisq$residuals^2/chisq$statistic
-    %round(contrib, 2)
-    %round(chisq$stdres, 3)
-    \begin{minipage}[c]{0.50\textwidth}
-        \centering
-    \resizebox{\textwidth}{!}{%
-\begin{tabular}{llllll}
-\hline
- &  & \multicolumn{4}{c}{Gender} \\ \cline{3-6} 
- &  & \multicolumn{2}{c}{Female} & \multicolumn{2}{c}{Male} \\ \cline{3-6} 
- &  & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Stand.
-\\ Residuals\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Stand.
-\\ Residual\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} \\ \cline{2-6}
-\begin{tabular}[c]{@{}l@{}}Post-\\ covid\\ changes\end{tabular} & \begin{tabular}[c]{@{}l@{}}Yes, I use a \\ safer messaging \\ app now\end{tabular} & 1.832 & 13.49\% & -1.832 & 7.50\% \\
- & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use \\ any messaging \\ app before, but\\ do use it now\end{tabular} & \textbf{2.806} & \textbf{31.21\%} & \textbf{-2.806} & \textbf{17.36\%} \\
- & \begin{tabular}[c]{@{}l@{}}No, I did use it \\ before and\\ use it now\end{tabular} & \textbf{2.850} & 15.15\% & \textbf{-2.850} & 8.43\% \\
- & \begin{tabular}[c]{@{}l@{}}No, I didn’t use \\ it before and\\ don’t use it now\end{tabular} & -1.011 & 4.40\% & 1.011 & 2.45\% \\ \hline
-\end{tabular}
-    %\begin{tabular}{l|r|r|r|r|}
-    %\cline{2-5}
-    %                             & Did/Do & Didn't/Do & Safer  & Didn' t/Don't \\ \hline
-    %\multicolumn{1}{|l|}{Female} & \textbf{-2.850} & \textbf{2.806} & 1.832  & -1.011 \\ 
-    %\multicolumn{1}{|l|}{} & 15.15\% & \textbf{31.21\%} &  13.49\% & 4.40\% \\ \hline
-    %\multicolumn{1}{|l|}{Male}   & \textbf{2.850} & \textbf{-2.806} & -1.832 & 1.011 \\ 
-    %\multicolumn{1}{|l|}{} &  8.43\% &  \textbf{17.36\%} & 7.50\% &  2.45\% \\ \hline
-    %\end{tabular}%
-    }
-    \end{minipage}
-\end{center}
-    \caption{Analysis for gender and post-covid changes: left) Pearson's residuals for the Chi-square test; right) Gender*post-covid changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized residuals) and contribution percentage to the total Chi-square test of each cell.}
-\label{figure:gender*postcovid_chisq}
-\end{figure}
-
-As mentioned, the graphs on the left hand side represent the Pearson's
-residuals, showing the difference between the observed and the expected values
-for each cell. Thus, large residuals indicate that variables are not truly
-independent. In our case, the blue shows positive contributions and red negative
-contributions to the test. Moreover, the saturation shows how large the
-contribution is in contrast to the expected value by chance. Additionally,
-tables on the right side show adjusted standardized residuals that according to
-\cite{agresti2013categorical}, if greater than +/-2 for cases with few cells,
-indicate lack of fit of $H_0$ (in boldface in our table). Complementary, the
-table also shows the percentage of contribution to the test of each cell
-(highest percentage per column also in boldface).
-
-Regarding gender in Fig. \ref{figure:gender*postcovid_chisq}, the results show a
-high positive contribution from female educators that did not use a messaging
-app before the COVID-19 pandemic but do use it now; approximately 31\% of the
-test results are explained by this cell. In contrast, male educators that
-respond the same were less than expected (negative contribution that explains
-17\% of the test results). Also, it is important to highlight the female
-educators that kept using these apps before and after the pandemic and
-correspondingly the negative contribution of male educators to the same case
-(less than expected by chance).
-
-\begin{figure}[h!tbp]
-\begin{center}
-    \begin{minipage}[c]{0.45\textwidth}
-        \centering
-<<sector_postcovid_chisq, echo=FALSE, fig.width=17/2.54, fig.height=10/2.54, warning=FALSE>>=
-covidChanges.vs.Sector<-table(survey.pilot.postCovidChisq$Sector, survey.pilot.postCovidChisq$PostCOVID.changes)
-colnames(covidChanges.vs.Sector)<- c("Did/do", "Didn't/do","safer", "Didn't/don't")
-covidChanges.vs.Sector<-covidChanges.vs.Sector[,c(3,2,1,4)]
-chisq<-chisq.test(covidChanges.vs.Sector)
-corrplot(chisq$residuals, is.corr = FALSE)
-@
-    \end{minipage}
-    \begin{minipage}[c]{0.50\textwidth}
-        \centering
-    \resizebox{\textwidth}{!}{%
-    %\begin{tabular}{l|r|r|r|r|}
-    %\cline{2-5}
-    %                             & Did/Do & Didn't/Do & Safer  & Didn' t/Don't \\ \hline
-    %\multicolumn{1}{|l|}{University} & \textbf{-2.122} & 0.454 & 0.115  &  \textbf{2.939}\\ 
-    %\multicolumn{1}{|l|}{} & 5.71\% & 0.56\% & 0.04\%  &  \textbf{25.26\%}\\ \hline
-    %\multicolumn{1}{|l|}{Vocational} & \textbf{2.122} & -0.454 & -0.115 & \textbf{-2.939}\\ 
-    %\multicolumn{1}{|l|}{} & 12.38\% & 1.21\% & 0.08\% & \textbf{54.78\%}\\ \hline
-    %\end{tabular}%
-    \begin{tabular}{llllll}
-          \hline
-           &  & \multicolumn{4}{c}{Sector} \\ \cline{3-6} 
-           &  & \multicolumn{2}{c}{University} & \multicolumn{2}{c}{Vocational} \\ \cline{3-6} 
-           &  & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Stand.
-\\ Residuals\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Stand.
-\\ Residual\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} \\ \cline{2-6}
-          \begin{tabular}[c]{@{}l@{}}Post-\\ covid\\ changes\end{tabular} & \begin{tabular}[c]{@{}l@{}}Yes, I use a \\ safer messaging \\ app now\end{tabular} & 0.115 & 0.04\% & -0.115 & 0.08\% \\
-           & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use \\ any messaging \\ app before, but\\ do use it now\end{tabular} & 0.454 & 0.56\% & -0.454 & 1.21\% \\
-           & \begin{tabular}[c]{@{}l@{}}No, I did use it \\ before and\\ use it now\end{tabular} & \textbf{-2.122} & 5.71\% & \textbf{2.122} & 12.38\% \\
-           & \begin{tabular}[c]{@{}l@{}}No, I didn’t use \\ it before and\\ don’t use it now\end{tabular} & \textbf{2.939} & \textbf{25.26\%} & \textbf{-2.939} & \textbf{54.78\%} \\ \hline
-          \end{tabular}%
-    }
-    \end{minipage}
-\end{center}
-    \caption{Analysis for sector and post-covid changes: left) Pearson's residuals for the Chi-square test; right) Sector*post-covid changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized  residuals) and contribution percentage to the total Chi-square test of each cell.}
-\label{figure:sector*postcovid_chisq}
-\end{figure}
-%
-With respect to the sector, the results in Fig.
-\ref{figure:sector*postcovid_chisq} show a positive contribution from university educators being reluctant to use any messaging apps before or after the pandemic: the positive contribution of their responses explain 25\% of the test results with an adjusted residual of 2.94.
-On the contrary, vocational teachers were more open to it, showing a negative Pearson's residual.
-Also, we find larger values than expected in vocational teachers that kept using these apps after the pandemic.
-
-\begin{figure}[h!tbp]
-\begin{center}
-    \begin{minipage}[c]{0.45\textwidth}
-        \centering
-<<discipline_postcovid_chisq, echo=FALSE, fig.width=17/2.54, fig.height=10/2.54, warning=FALSE>>=
-survey.pilot.postCovidChisq %>%mutate(Discipline = ifelse(as.character(Discipline) == "No", "Hum/Social Sciences", as.character(Discipline))) %>%
-  mutate(Discipline = ifelse(as.character(Discipline) == "Other", "Hum/Social Sciences", as.character(Discipline))) %>%
-  mutate(Discipline = ifelse(as.character(Discipline) == "Engineering", "Tech/Engineering", as.character(Discipline))) %>%
-  mutate(Discipline = ifelse(as.character(Discipline) == "Technology", "Tech/Engineering", as.character(Discipline))) %>%
-  mutate(Discipline = ifelse(as.character(Discipline) == "Humanities", "Hum/Social Sciences", as.character(Discipline))) %>%
-  mutate(Discipline = ifelse(as.character(Discipline) == "Social Sciences", "Hum/Social Sciences", as.character(Discipline))) %>%
-  mutate(Discipline = ifelse(as.character(Discipline) == "Sciences", "Biomed/Sciences", as.character(Discipline))) %>%
-  mutate(Discipline = ifelse(as.character(Discipline) == "Biomedicine", "Biomed/Sciences", as.character(Discipline)))->survey.pilot.postCovidChisq
-covidChanges.vs.Discipline<-table(survey.pilot.postCovidChisq$Discipline, survey.pilot.postCovidChisq$PostCOVID.changes)
-colnames(covidChanges.vs.Discipline)<- c("Did/do", "Didn't/do","safer", "Didn't/don't")
-covidChanges.vs.Discipline<-covidChanges.vs.Discipline[,c(3,2,1,4)]
-chisq<-chisq.test(covidChanges.vs.Discipline)
-corrplot(chisq$residuals, is.corr = FALSE)
-@
-    \end{minipage}
-    \begin{minipage}[c]{0.50\textwidth}
-        \centering
-    \resizebox{\textwidth}{!}{%
-\begin{tabular}{llllllll}
-\hline
- &  & \multicolumn{6}{c}{Discipline} \\ \cline{3-8} 
- &  & \multicolumn{2}{c}{Biomed/Sciences} & \multicolumn{2}{c}{Hum/Social} & \multicolumn{2}{l}{Tech/Engineering} \\ \cline{3-8} 
- &  & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Stand.
-\\ Residuals\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Stand.
-\\ Residual\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Contri-\\ bution\end{tabular}} & \begin{tabular}[c]{@{}l@{}}Stand.
-\\ Residuals\end{tabular} & \begin{tabular}[c]{@{}l@{}}Contri-\\ bution\end{tabular} \\ \cline{2-8}
-\begin{tabular}[c]{@{}l@{}}Post-\\ covid\\ changes\end{tabular} & \begin{tabular}[c]{@{}l@{}}Yes, I use a \\ safer mes-\\ saging app \\ now\end{tabular} & 1.452 & \textbf{9.94\%} & 1.566 & 11.04\% & \textbf{-2.448} & \textbf{13.29\%} \\
- & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t \\ use any mes-\\ saging app \\ before, but\\ do use it now\end{tabular} & 0.733 & 2.50\% & \textbf{2.079} & \textbf{19.19\%} & -2.318 & 11.76\% \\
- & \begin{tabular}[c]{@{}l@{}}No, I did use \\ it before and\\ use it now\end{tabular} & -1.265 & 3.50\% & \textbf{-2.729} & 15.55\% & \textbf{3.278} & 11.06\% \\
- & \begin{tabular}[c]{@{}l@{}}No, I didn’t \\ use it before \\ and don’t use \\ it now\end{tabular} & -0.588 & 1.75\% & 0.055 & 0.01\% & 0.412 & 0.40\% \\ \hline
-\end{tabular}
-    %\begin{tabular}{l|r|r|r|r|}
-    %\cline{2-5}
-    %                             & Did/Do & Didn't/Do & Safer & Didn' t/Don't \\ \hline
-    %\multicolumn{1}{|l|}{Biomed/Sciences} & -1.265 &  0.733 & 1.452 & -0.588 \\ 
-    %\multicolumn{1}{|l|}{} & 3.50\% &  2.50\% & 9.94\% & 1.75\% \\ \hline
-    %\multicolumn{1}{|l|}{Hum/Social} &  \textbf{-2.729} & \textbf{2.079} &  1.566 & 0.055\\ 
-    %\multicolumn{1}{|l|}{} &  15.55\% & \textbf{19.19\%} &  11.04\% & 0.01\%\\ \hline
-    %\multicolumn{1}{|l|}{Tech/Engineering} &  \textbf{3.278} &  \textbf{-2.318} &  \textbf{-2.448} & 0.412\\ 
-    %\multicolumn{1}{|l|}{} &  11.06\% &  11.76\% &  \textbf{13.29\%} & 0.40\%\\ \hline
-    %\end{tabular}%
-    }
-    \end{minipage}
-\end{center}
-    \caption{Analysis for discipline and post-covid changes: left) Pearson's residuals for the Chi-square test; right) Discipline*post-covid changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized residuals) and contribution percentage to the total Chi-square test of each cell.}
-\label{figure:discipline*postcovid_chisq}
-\end{figure} 
-%
-Finally, statistical significance was found for the discipline and post-covid
-changes. Regarding disciplines (see
-Fig. \ref{figure:discipline*postcovid_chisq}), the number of educators from
-Humanities and Social Sciences that started using messaging apps after the
-pandemic is larger than expected and these number of responses explains about
-19\% of the chi-square test results. Also, the number of educators from
-Technology or Engineering that started using safer alternatives \footnote{This addresses the issue of insecure/unsafe applications which do not cipher messages or can be easily compromised exposing information} are less than
-expected (compared to the educators from other disciplines). Bear in mind that
-some disciplines were merged to avoid very low number of responses for some of
-the cells.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RQ2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-For the findings it occurs that the most favourable use case for chatbots in
-Higher Education and vocational training is their use for the facilitation of an
+From the findings it occurs that the most favourable use case for chatbots in
+Higher Education and vocational training is the use of chatbots for the facilitation of an
 agenda formation (171 positive response, 60.6\%), followed by the FAQs use case
@@
 
+The majority of the teachers (n=269, 95.4%) responded negatively to the kind of interactions that take place in chat tools and involve students, teachers and the faculty, while most of them (n=171, 60.6%) prefer the kind of interactions that take place among students in the same course.
 As it can be seen by the answer to the first and last question, in general
@@
 want to simply leave the students alone in their own chat group, or otherwise
-they prefer not to be part of that interaction. In general, that is going to be
-the case no matter what; it is well known that students organize their own chat
-groups with many (and not always conveyable) intentions, so teachers do not want
-to take any part in these informal or non institutionally-supported chat
-groups. Overwhelmingly, they do not want to participate in these kind of chat
-groups with students, but even less so if it includes the rest of the faculty.
-
-The answer, then, to this research question, is that, in general, teachers do
-{\em not} want to have interaction with students in a chat group. To a certain
-point, this would seem to contradict results by Gachago et
-al. \cite{gachago2015crossing}, although this might be due to cultural
-attitudes, or other factors such as the average size of classes. It does
-confirm, however, that the challenges cited in that study, and possibly others,
-are an obstacle to the adoption of mobile (and other) instant messaging among
-the community of surveyed teachers.
-
-Regarding the social factor of chat groups that teachers use in class, according
-to Fig. \ref{figure:chatbots_messagingorganization} the vast majority prefer
-small groups only with the students from the same course. These are more focused
-groups with specific goals and dedicated to the organization of the course and
-its tasks, and from the pedagogic point of view seem more appropriate to improve
-the learning process. Interestingly, and as a cross-check of the answers above,
-about 30\% of teachers consider they should not be part of the chat group. This
-might seem to contradict the results of the other survey, but in fact, being a
-result of different surveys, to a certain point affirms the same thing: there is
-a great amount of teachers that would be against being in a chat group with
-students. Whether that's a slim majority or not, that's open to debate (and
-would probably need a more pointed survey focused on this), but what is clear is
-that forcing teachers to create chat groups with students and participate in
-them would create a certain amount of resistance. Also, only university teachers
-find interesting a group with all the students and teachers in their own Faculty
-or School. The lack of teachers from vocational education here may be the
-consequence of using specific language such as ``Faculty''. Moreover, the fact
-that many universities and schools already use these groups for administrative
-and social interaction (e.g. \cite{dibitonto2018chatbot}) might be the reason
-for the low percentage of teachers that selected this response.
+they prefer not to be part of that interaction.
+
+%what followed, should be part of the discussion
 
@@
 
+%delete the figure
 \begin{figure}[h!tbp]
@@
 
-A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
-The majority of the teachers were aged 45-55 years old (70; 34.1\%), followed by individuals aged 35-45 (67, 32.7\%), and 25-35 (42; 20.5\%), while the minority was aged $>$~55 years old (26; 12.7\%).
-In terms of teaching experience, 59 teachers (28.8\%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9\%), 0-5 years (51; 24.9\%) and more than 25 years of experience (44; 21.5\%).
-The teachers were asked about what kind of interaction media features they value the most; the frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
+Data from the second survey were used for addressing RQ4, as already mentioned in the Methodology.
+A total of 205 teachers responded to the second survey, who were asked about what kind of interaction media features they value the most; the frequencies and percentages of their responses are given in the table that follows.
 

### 2021-11-22 edubots_surveys.Rnw
Grammar and typographic update.

@@
 
-This study followed a quantitative approach towards addressing it research objectives. In doing so, an online survey was administered (i.e., Google Form),
-in Spanish, comprised by six questions focusing on demographic data (i.e., sector, gender, degrees, discipline, age, teaching experience), followed by four multiple choice questions allowing the participants to choose multiple answers in each of those.
-Thee multiple choice questions focused on the use of messaging apps
+This study followed a quantitative approach towards addressing its research objectives.
+In doing so, an online survey was administered (i.e., Google Form),
+in Spanish, comprised of six questions focusing on demographic data
+(i.e., sector, gender, degrees, discipline, age, teaching experience)
+followed by four multiple choice questions allowing the participants to choose multiple answers. 
+These questions focused on the use of messaging apps
 in the teaching practice, the type of chatbot use cases that teachers consider

### 2021-11-22 edubots_surveys.Rnw
Highlight changes

--- 2021-11-14 edubots_surveys.Rnw
@@
 
-Our intention from the beginning was to try to gather a sufficient amount of
-responses in all sectors, as well as cover different sectors of higher
-education. In doing so, an online survey was administered (i.e., Google Form),
-in Spanish, which was intended to be answered in a very short amount of
-time. Initially, our intention was to mirror the questions used in
-\cite{MoraChatbots2021:anon}; however, an initial exploration of results led us
-to create a second survey. The \textcolor{blue}{new survey} items focused on the use of messaging apps
-in the teaching practice, the type of chatbot use cases that teachers consider
+\textcolor{blue}{This study aims to collect rich data about the use of messaging applications and chatbots
+by educators in both universities and colleges\footnote{In Spain, they are called simply high schools, and deliver
+tertiary or associated degrees that do not have the consideration of university degrees}.
+To achieve this goal, an online survey was designed and developed using Google Forms
+in Spanish}. Initially, the intention was to mirror the questions used in
+\cite{MoraChatbots2021:anon}; which explored students' views about the use of messaging applications in classrooms.
+However, the initial exploration of results led us
+to create a second survey in order to collect more data about educators' preferences in particular. The \textcolor{blue}{new survey} items 
+focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider
 useful to be used in their teaching, and the type of interactions that teachers
@@
 responses were the same, except for the type of tertiary degrees that
-\textcolor{blue}{were considered}. In both cases, we used mainly mailing lists, as well as Telegram groups,
-to spread the link to the form. The university form was spread in Spanish
-(mainly Andaluc\'{\i}a and Galicia) universities, and also Costa Rica and
-Mexico. The tertiary non-university teachers are based mainly in
+\textcolor{blue}{were considered. The survey was piloted by the authors of the paper and their colleagues before using it in the 
+study.  All the comments collected from this trial were incorporated in the survey.
+We used mainly mailing lists, as well as Telegram groups,
+to post the survey link to reach out to more educators}. The university form was sent to Spanish
+(mainly Andaluc\'{\i}a and Galicia) universities, and also  universities in Costa Rica and
+Mexico. The tertiary (non-university/college) teachers were based mainly in
 Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of

### 2021-11-22 edubots_surveys.Rnw
Extend changes
Typographical separation

@@
 and for boosting students' sense of belonging to their 
-institutions\cite{abbas2021onlinechat}. Hence, due to the paucity of research
+institutions \cite{abbas2021onlinechat}. Hence, due to the paucity of research
 that explores the use of these technologies from the teachers' perspectives,
@@
 technology, \textcolor{blue}{i.e. chatbots}, that generally piggybacks on another, \textcolor{blue}{i.e. messaging
-applications}. Generally, in a technology adoption model, perceived ease of use and
+applications. Generally,} in a technology adoption model, perceived ease of use and
 perceived usefulness are essential. But it is going to be very difficult for

### 2021-11-22 edubots_surveys.Rnw
More issues addressed (also in response), refs #48

@@
 
-\textcolor{blue}{In this study, data collection involved two phases}
+\textcolor{blue}{In this study, data collection involved two phases:}
  \begin{itemize}
@@
 Initially, a single survey was developed for this purpose and responses from 300
-higher education teachers were collected and analysed.  The responses' analysis
+higher education teachers were collected and analysed\textcolor{blue}{; this will be explained more fully in the corresponding section}.  The responses' analysis
 entailed the creation of a second survey to which 200 teachers' responses were
-collected. The questions of the second survey focussed on discussing teachers'
+collected\textcolor{blue}{, with the methodology and collective characteristics that will be explained below}. The questions of the second survey focussed on discussing teachers'
 needs, opinions and preferences of the development of future technology-enhanced

### 2021-11-22 edubots_surveys.Rnw
Rewriting and highlighting @noorhanabbas sentence

@@
 entailed the creation of a second survey to which 200 teachers' responses were
-collected\textcolor{blue}{, with the methodology and collective characteristics that will be explained below}. The questions of the second survey focussed on discussing teachers'
+collected\textcolor{blue}{, with the methodology and collective characteristics that will be explained below. The questions of the second survey focussed on discussing teachers'
 needs, opinions and preferences of the development of future technology-enhanced
-tools and its potential impact on educational institutions’ policies. Therefore,
-this paper investigated the following research questions:
+tools and its potential impact on educational institutions’ policies. In order to assess these, this paper investigated the following research questions}:
 

### 2021-11-22 edubots_surveys.Rnw
Adding a response about relationship q/recommendations
Addresses #48

@@
 recommendations to make a successful deployment of chatbot technologies (and, in
-some cases, general instant messaging applications) in higher education.
+some cases, general instant messaging applications) in higher education\textcolor{blue}{; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be used in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from R3 we will also try to find best practices in the adoption of messaging platforms and they accompanying chatbots.}
 

### 2021-11-22 edubots_surveys.Rnw
Again, highlighting and responding in the letter #48

@@
 \cite{Yildirim2017} can improve student motivation. In this sense, the authors
-in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
+in \cite{Pimmer2019} \textcolor{blue}{adopted a quasi-experimental, survey-based approach to
 report the positive impact of using instant messaging tools in boosting
-students' knowledge and mitigating their feelings of isolation.
+students' knowledge and mitigating their feelings of isolation}.
 

### 2021-11-22 edubots_surveys.Rnw
Answer about insertion of citation #48

@@
 Messenger with the focus to identify characteristics and quality metrics such as
-language, subject matter and platform.  Whereas the study undertaken by
-\cite{perez2020rediscovering} aimed to categorise educational chatbots according
-to their purpose into service-oriented and teaching-oriented. The first category
+language, subject matter and platform\textcolor{blue}{, whereas the study undertaken by Pérez and collaborators
+\cite{perez2020rediscovering} aimed to categorise educational chatbots, according
+to their, purpose into service-oriented and teaching-oriented}. The first category
 includes those that provide service support such as the chatbot Ask Holly

### 2021-11-22 edubots_surveys.Rnw
Correct and expand biblio
And add justification for finding out the needs of the user #48

@@
 proposed a generic chatbot for university students that is able to answer to
-their frequently asked questions.  For some time, the University of Granada had
-ELVIRA as a chatbot in its main web page \cite{MOREO20129}. Besides being able
+their frequently asked questions \textcolor{blue}{and, for some time, the University of Granada had
+\textcolor{blue}{Elvira} as a chatbot in its main web page \cite{MOREO20129} to perform that duty.} Besides being able
 to answer pre-established (frequent) questions, it did so from the website of
-the University of Granada using an inset character, voiced by a real person, who
+the University of Granada using an inset \textcolor{blue}{persona, voiced by a real person, who
 lip-synced the answers. The emphasis in the case of Elvira, however, was on the
 authenticity of the synchronization more than in making the update of questions
-and answers simpler, or more interactive, using actual messaging platforms.  In
-most cases, using the inset search engine was able to give you more up-to-date
-and accurate answers than the ones provided by ELVIRA, which had to be updated
+answered simpler, or more interactive, or more open to the rest of the university staff, using actual messaging platforms.  In
+most cases, using the embedded search engine was able to give you more up-to-date
+and accurate answers than the ones provided by Elvira, which had to be updated
 by hand (and not too often).
+It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide an useful service.
+Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in an university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, something which is the focus of this paper}.
 
@@
 with and can easily access (i.e. Facebook Messenger) which was confirmed with
-\cite{hobert2019you} and \cite{fernoagua2018intelligent} studies. In addition,
-Sj{\"o}str{\"o}m et al. \cite{sjostrom2018designing} argued that a
+\cite{hobert2019you} and \cite{fernoagua2018intelligent} studies. In addition, \cite{sjostrom2018designing} argued that a
 conceptualisation of learners' questions could aid designers in integrating the
 appropriate types of questions that the chatbots should support for different
-courses.  Coronado et al. \cite{coronado2018cognitive} proposed agents that
+courses.  \textcolor{blue}{Some other authors}, like \cite{coronado2018cognitive}, proposed agents that
 store learning materials to be provided on demand to students, whereas the
@@
 such as learning success and increased motivation are more important.  Therefore,
-to develop \textcolor{blue}{effective} chatbots for higher education, all stakeholders'
+to develop \textcolor{blue}{effective chatbots for higher education, all stakeholders'
 (i.e. educators, students, institutions, etc) needs should be carefully
@@
 \cite{sjostrom2018designing,tsivitanidouusers}.
+These needs include, but are not limited to, student's learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance; this is why we focus in this paper on what the teachers are looking for in a TAM and associated technologies like chatbots; both authors focus on what the teachers need in terms of the latter; this paper will focus on a wider perspective trying to ascertain what they are looking for in terms of general messaging technology.
+The classical literature \cite{tam91} already proposes that any adoption of technology must be tuned in to the user needs and experience.
+In this paper we will try to find out what those are in order to propose a successful model of adoption of chatbot technology}.
 

### 2021-11-22 edubots_surveys.Rnw
Changes to needs

@@
 really benefited from it. This is, once again, a proof of the benefit of
-chatbots in certain settings; however, there are some opinions that might
+chatbots in certain settings; however, there are some \textcolor{blue}{prior experiences, as well as needs} that might
 prevent the successful acceptance of the technology, and these are what we are

### 2021-11-22 edubots_surveys.Rnw
Use proper word

@@
 19\% of the chi-square test results. Also, the number of educators from
-Technology or Engineering that started using safer alternatives \footnote{This addresses the issue of insecure/unsafe applications which do not cipher messages or can be easily compromised exposing information} are less than
+Technology or Engineering that started using safer alternatives \footnote{\textcolor{blue}{This addresses the issue of insecure/unsafe applications which do not encrypt messages or can be easily compromised exposing information}} are less than
 expected (compared to the educators from other disciplines). Bear in mind that

### 2021-11-22 edubots_surveys.Rnw
Address another #48

@@
 {\em not} want to have interaction with students in a chat group. To a certain
-point, this would seem to contradict results by Gachago et
-al. \cite{gachago2015crossing}, although this might be due to cultural
+point, this would seem to contradict results \cite{gachago2015crossing}, although this might be due to cultural
 attitudes, or other factors such as the average size of classes. It does
@@
 
-Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are  their feelings and preferences with regard to the use of instant messaging applications with students, and even using bots or chatbots in the classroom.
+Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are  their \textcolor{blue}{past experiences and needs} with regard to the use of instant messaging applications with students, and even using bots or chatbots in the classroom.
 In addition the survey asked about the most relevant \textit{interaction media features} for the teachers with respect to the potential tool to use in class.

### 2021-11-22 edubots_surveys.Rnw
Minor changes

@@
 of a new higher education law\footnote{We seem to have one of these, at least in
-  Spain, every 10 years or so}, or introduction of new degrees. Although
+  Spain, every 10 years or so.}, or introduction of new degrees. Although
 external changes do offer the chance of piloting new technologies, they do not
@@
 % 
-% The authors want to thank to the educators who participated in the survey, and also people who have distributed the survey in their mailing lists, especially Mario García Valdez, Jesús Moreno León and José Raúl Canay.
-% % Antonio - Add other acknowledgements
+% The authors want to thank to the educators who participated in the survey, and also people who have distributed the survey in their mailing lists, especially Mario García Valdez, Jesús Moreno León and the late José Raúl Canay.
+% We would also like to thank the anonymous reviewers that have contributed greatly to the improvement of this paper.
 

### 2021-11-22 edubots_surveys.Rnw
Adds survey questions in Spanish

@@
 
+\begin{figure}[h!tbp]
+\begin{center}
+\includegraphics[width=\textwidth]{figures/survey-2.png}
+\end{center}
+    \caption{\textcolor{blue}{Screen capture of the Spanish-language form used for the survey}}
+\label{figure:survey2}
+\end{figure}
 The {\bf second survey} followed the same paths, only in this case there was a single questionnaire, and with a different scope, focusing on the kind of interaction media features that teachers value the most.
+\textcolor{blue}{A capture of these questions is included in Figure \ref{fig:survey2}}
 % Olia - see my comment above.

### 2021-11-23 edubots_surveys.Rnw
Corrected a typo and grammar

@@
 messaging applications and/or chatbots are used to deliver personalised
-learning in classrooms that occurs anytime anywhere, 
+learning in classrooms that occurs anytime anywhere, to
 promote collaborative learning experiences, group discussions \cite{panah2020study}
-and for boosting students' sense of belonging to their 
-institutions \cite{abbas2021onlinechat}. Hence, due to the paucity of research
+and to boost students' sense of belonging to their institutions \cite{abbas2021onlinechat}. Hence, due to the paucity of research
 that explores the use of these technologies from the teachers' perspectives,
@@
 Initially, a single survey was developed for this purpose and responses from 300
-higher education teachers were collected and analysed\textcolor{blue}{; this will be explained more fully in the corresponding section}. The responses' analysis
+higher education teachers were collected and analysed\textcolor{blue}{; this will be explained more fully in the methodology section}. The responses' analysis
 entailed the creation of a second survey to which 200 teachers' responses were
@@
 
-\textcolor{blue}{This study aims to collect rich data about the use of messaging applications and chatbots
+\textcolor{blue}{This study followed a quantitative approach towards addressing its research objective, by collecting rich data about the use of messaging applications and chatbots
 by educators in both universities and colleges\footnote{In Spain, they are called simply high schools, and deliver
 tertiary or associated degrees that do not have the consideration of university degrees}.
-To achieve this goal, an online survey was designed and developed using Google Forms
-in Spanish}. Initially, the intention was to mirror the questions used in
-\cite{MoraChatbots2021:anon}; which explored students' views about the use of messaging applications in classrooms.
-However, the initial exploration of results led us
-to create a second survey in order to collect more data about educators' preferences in particular. The \textcolor{blue}{new survey} items 
+To achieve this goal two online surveys were designed and developed using Google Forms
+in Spanish. They are comprised of six questions focusing on demographic data
+(i.e., sector, gender, degrees, discipline, age, teaching experience)
+followed by several multiple choice questions allowing the participants to choose multiple answers.}
+
+\textcolor{blue}{In the first survey, the multiple choice questions are
 focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider
-useful to be used in their teaching, and the type of interactions that teachers
-prefer to have with their students while using messaging apps in their teaching.
-
-The {\bf initial survey} was done in two separate Google forms, one for
+useful to be used in their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
 university and other for tertiary non-university teachers. Questions and
 responses were the same, except for the type of tertiary degrees that
-\textcolor{blue}{were considered. The survey was piloted by the authors of the paper and their colleagues before using it in the 
+were considered.}}
+
+\textcolor{blue}{This survey was piloted by the authors of the paper and their colleagues before using it in the 
 study.  All the comments collected from this trial were incorporated in the survey.
 We used mainly mailing lists, as well as Telegram groups,
-to post the survey link to reach out to more educators}. The university form was sent to Spanish
+to post the survey link to reach out to more educators. The university form was sent to Spanish
 (mainly Andaluc\'{\i}a and Galicia) universities, and also  universities in Costa Rica and
@@
 2021, post-pandemic and while, at least in Spain, many universities had
-mandatory virtual teaching.
+mandatory virtual teaching.}
 
@@
 Telegram). With respect to specific disciplines, Engineering and Technology
-teachers are more active in their use, \textcolor{blue}{but the amount of teachers from Humanities 
+teachers are more active in their use, \textcolor{blue}{but the number of teachers from Humanities 
 who answered they used these apps in their classes is also remarkable}
@@
 In terms of teaching experience, 59 teachers (28.8\%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9\%), 0-5 years (51; 24.9\%) and more than 25 years of experience (44; 21.5\%).
-The teachers were asked about what kind of interaction media features they value the most; the frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
+The teachers were asked about what kind of interaction media features they value the most \textcolor{blue}{; i.e.
+what are their preferred utilities in the applications/tools they use to interact with their students.} The frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
 
@@
 \vspace{0.8em}
-\caption{Interaction media features valued by teachers. Details about each feature can be read in Section \ref{sec:meth}.}
+\caption{Interaction media features valued by teachers. \textcolor{blue}{Details about each of these features can be read in Appendix I (Section \ref{app:questions}, second survey)}.}
 \label{tab:interaction}
 \end{table}
+
+\textcolor{blue}{As it can be seen in the table, the main responses aim to use a sustainable and official application, i.e.
+both being approved or provided by the University (or the educational centre), and also maintained by the technical staff of the centre instead of giving this responsability/task to the teacher.
+In addition, it is very important for the teachers that the used tools allow to communicate all the members of the classroom, including themselves; as well as being already known or used in everyday tasks, e.g.
+Telegram or WhatsApp.}
 
@@
 these messaging applications not only are GDPR compliant to keep students’ data
-secure but also should provide IT support to all stakeholders who use the
+secure, but also should provide IT support to all stakeholders who use the
 applications.
@@
 
+\begin{figure}[h!tbp]
+\begin{center}
+\includegraphics[width=0.85\textwidth]{figures/survey-1.png}
+\end{center}
+    \caption{\textcolor{blue}{Screen capture of the Spanish-language form used for the first survey}}
+\label{figure:survey1}
+\end{figure}
 % Including questions in surveys
-The {\bf first survey}, which \textcolor{blue}{focused on} the use of messaging apps in class, and which tried to address mainly RQ2 and RQ3, 
+The {\bf first survey}, shown in its original form in Figure \ref{figure:survey1}, which \textcolor{blue}{focused on} the use of messaging apps in class, and which tried to address mainly RQ2 and RQ3,
 % Antonio - I guess it refers to RQ3. ;)
@@
 \end{figure}
-The {\bf second survey} followed the same paths, only in this case there was a single questionnaire, and with a different scope, focusing on the kind of interaction media features that teachers value the most.
+The {\bf second survey}, shown in its original form in Figure \ref{figure:survey2}, followed the same paths, only in this case there was a single questionnaire, and with a different scope, focusing on the kind of interaction media features that teachers value the most.
 \textcolor{blue}{A capture of these questions is included in Figure \ref{fig:survey2}}

### 2021-11-29 edubots_surveys.Rnw
Adapt @noorhanabbas incorporation

@@
 promote collaborative learning experiences, group discussions \cite{panah2020study}
-and for boosting students' sense of belonging to their 
-institutions \cite{abbas2021onlinechat}. Hence, due to the paucity of research
+and boost students' sense of belonging to their institutions
+\cite{abbas2021onlinechat}. Hence, due to the paucity of research
 that explores the use of these technologies from the teachers' perspectives,

### 2021-11-29 edubots_surveys.Rnw
Utilites are the electrical company

@@
 The teachers were asked about what kind of interaction media features they value the most \textcolor{blue}{; i.e.
-what are their preferred utilities in the applications/tools they use to interact with their students.} The frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
+what are their preferred features in the applications/tools they use to interact with their students.} The frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
 

### 2021-11-30 edubots_surveys.Rnw
Minor change

@@
 useful to be used in their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
-university and other for tertiary non-university teachers. Questions and
+university and \textcolor{blue}{other for teachers of in tertiary education institutions, outside the university system (vocational training, including 1 and 2 year degrees)}. Questions and
 responses were the same, except for the type of tertiary degrees that

### 2021-11-30 edubots_surveys.Rnw
fixes minor typos in Section 1,2

@@
 full adoption. In most cases, the magnitude of the uptake of the new technology
-impinges on the collaboration of all the parties using it. Hence, examining the
-users’ opinions and is an important first step in boosting this collaboration
-and reaping the benefits of the technology.  Recently, a surge in the use of
+impinges on the collaboration of all the parties using it. \textcolor{blue}{Hence, examining the
+users’ opinions is an important first step in boosting this collaboration
+and reaping the benefits of the technology}.  Recently, a surge in the use of
 synchronous instant messaging tools in higher education such as WhatsApp,
@@
 recommendations to make a successful deployment of chatbot technologies (and, in
-some cases, general instant messaging applications) in higher education\textcolor{blue}{; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be used in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from R3 we will also try to find best practices in the adoption of messaging platforms and they accompanying chatbots.}
-
-The remainder of the paper is organized as follows: Next is an overview of what
+some cases, general instant messaging applications) in higher education\textcolor{blue}{; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be used in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from RQ3 we will also try to find best practices in the adoption of messaging platforms and they accompanying chatbots.}
+
+The remainder of the paper is organized as follows: \textcolor{blue}{first, an overview of what
 current research has found about the use of messaging applications, including
-chatbots, in the classroom. The methodology used in the surveys is presented in
+chatbots, in the classroom is described}. The methodology used in the surveys is presented in
 Section \ref{sec:meth}, and the results of the surveys are presented next in
@@
 answered simpler, or more interactive, or more open to the rest of the university staff, using actual messaging platforms. In
-most cases, using the embedded search engine was able to give you more up-to-date
+most cases, the embedded search engine was able to provide more up-to-date
 and accurate answers than the ones provided by Elvira, which had to be updated
@@
 It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide an useful service.
-Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in an university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, something which is the focus of this paper}.
+Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, something which is the focus of this paper}.
 
@@
 \cite{sjostrom2018designing,tsivitanidouusers}.
-These needs include, but are not limited to, student's learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance; this is why we focus in this paper on what the teachers are looking for in a TAM and associated technologies like chatbots; both authors focus on what the teachers need in terms of the latter; this paper will focus on a wider perspective trying to ascertain what they are looking for in terms of general messaging technology.
+These needs include, but are not limited to, student's learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance; this is why we focus in this paper on what the teachers are looking for in a TAM  (Technology Acceptance Model) and associated technologies like chatbots; both authors focus on what the teachers need in terms of the latter; this paper will focus on a wider perspective trying to ascertain what they are looking for in terms of general messaging technology.
 The classical literature \cite{tam91} already proposes that any adoption of technology must be tuned in to the user needs and experience.
@@
 prevent the successful acceptance of the technology, and these are what we are
-trying to find out in this paper, together with what kind of features would make
-its acceptance better.
+trying to find out in this paper, together with what kind of features would \textcolor{blue}{improve
+its acceptance}.
 

### 2021-11-30 edubots_surveys.Rnw
fixes more minor typos in Sections 3,4

@@
 useful to be used in their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
-university and \textcolor{blue}{other for teachers of in tertiary education institutions, outside the university system (vocational training, including 1 and 2 year degrees)}. Questions and
+university and \textcolor{blue}{the other for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees)}. Questions and
 responses were the same, except for the type of tertiary degrees that
@@
 the results from the two forms we used for the first survey were collated in a
-single spreadsheet. Next we will show the results and analyse them.
+single spreadsheet. Next, we show the results and analyse them.
 
@@
 that shows the contribution of each cell to the test. In the Pearson's residual
-graphs, the responses were shortened for the sake of clarity according to: 1)
+graphs, \textcolor{blue}{the responses to the question about the use of messaging apps were shortened for the sake of clarity according to}: 1)
 \textit{Did/do} stands for \textit{Yes, I did use it before and do use it now};
@@
 groups with specific goals and dedicated to the organization of the course and
-its tasks, and from the pedagogic point of view seem more appropriate to improve
-the learning process. Interestingly, and as a cross-check of the answers above,
+its tasks, and from the pedagogic point of view \textcolor{blue}{it also seems more appropriate to improve
+the learning process}. Interestingly, and as a cross-check of the answers above,
 about 30\% of teachers consider they should not be part of the chat group. This
@@
 The teachers were asked about what kind of interaction media features they value the most \textcolor{blue}{; i.e.
-what are their preferred features in the applications/tools they use to interact with their students.} The frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
+what their preferred features are in the applications/tools that they use to interact with their students.} The frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
 
@@
 The {\bf second survey}, shown in its original form in Figure \ref{figure:survey2}, followed the same paths, only in this case there was a single questionnaire, and with a different scope, focusing on the kind of interaction media features that teachers value the most.
-\textcolor{blue}{A capture of these questions is included in Figure \ref{fig:survey2}}
+%\textcolor{blue}{A capture of these questions is included in Figure \ref{fig:survey2}} % this sentence is repeated
 % Olia - see my comment above.

### 2021-11-30 edubots_surveys.Rnw
Added description of the second survey
closes #75

--- 2021-11-30 edubots_surveys.Rnw
@@
 the results from the two forms we used for the first survey were collated in a
-single spreadsheet. Next we will show the results and analyse them.
+single spreadsheet.
+
+\textcolor{blue}{The second survey was designed after initial results to the first survey arrived,
+and pointed to necessities and experiences of teachers not being addressed by the first one; namely
+their experience with messaging platforms and the way they were used to interact with students.
+It was piloted in a group of university teachers attending to a formation course, and validated with them.
+It was then extended to the rest of the responders, using the same media: Telegram groups, email and
+and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
+(Section \ref{app:questions}).}
+
+Next we will show the results and analyse them.
 

### 2021-11-30 edubots_surveys.Rnw

--- 2021-11-30 edubots_surveys.Rnw
@@
 the results from the two forms we used for the first survey were collated in a
-single spreadsheet. Next, we show the results and analyse them.
+single spreadsheet.
+
+\textcolor{blue}{The second survey was designed after initial results to the first survey arrived,
+and pointed to necessities and experiences of teachers not being addressed by the first one; namely
+their experience with messaging platforms and the way they were used to interact with students.
+It was piloted in a group of university teachers attending to a formation course, and validated with them.
+It was then extended to the rest of the responders, using the same media: Telegram groups, email and
+and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
+(Section \ref{app:questions}).}
+
+Next, we show the results and analyse them.
 

### 2021-12-01 edubots_surveys.Rnw
Incorporates demographics from @oliatsi PR

@@
 A total of 282 teachers responded to the survey: 193 teaching at the University
-(68.4\%) and 89 at other tertiary education institutions (31.6\%). Survey
+(68.4\%) and 89 at other tertiary education institutions (31.6\%).
+\textcolor{blue}{From those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%) and 5 teachers preferred not to indicate their gender (1.8\%).
+In terms of age, the majority of the participants (n=111) in this survey was 45-55 years old (39.4\%), while 91 teachers were 35-45 (32.3\%), 46 were 25-35 (16.3\%) and 34 teachers were older than 55 (12.1\%).
+Last, 84 teachers had a teaching experience of 16-25 years (29.8\%), 75 teachers 6-15 years of experience (26.6\%), 69 teachers had 0-5 years of experience (24.5\%) and finally, 54 teachers had more than 25 years of teaching experience (19.1\%).}
+
+Survey
 questions \textcolor{blue}{are shown in Appendix I (Section \ref{app:questions})}.

### 2021-12-01 edubots_surveys.Rnw
Incorporates demographics from @oliatsi PR for 2nd survey

@@
 (Section \ref{app:questions}).}
+
+\textcolor{blue}{A total of 205 teachers responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%).
+From those, 124 were (60.5\%), 65 female (31.7\%) and 16 teachers preferred not to indicate their gender (7.8\%).
+In terms of age, the majority of the participants (n=70) was again, as in the first survey, 45-55 years old (34.1\%), while 67 teachers were 35-45 (32.7\%), 42 were 25-35 (20.5\%) and 26 teachers were older than 55 (12.7\%).
+In terms of teaching experience, 59 teachers had a teaching experience of 16-25 years (28.8\%), 51 teachers had 6-15 years (24.9\%) and 0-5 years of experience (24.9\%), and 44 teachers more than 25 years of teaching experience (21.5\%).}
 

### 2021-12-01 edubots_surveys.Rnw
Adds items related to the messaging question
Mainly as future work

@@
 other messaging app, and whether they use messaging apps provided by their
-academic institution (see Table \ref{tab:use_messapps}). \textcolor{blue}{In this case, we would like 
-to add a clarification}. While we had in mind, as indicated by the possible answers, 
-instant messaging applications when making this question,
-we included these institution-provided applications mainly for completion. But
-it should be noted that, in most cases, they are not {\em instant} messaging
-apps in the way Telegram or Facebook Messenger are; in most cases they are
-messaging facilities provided by learning management systems such as (usually)
-Moodle. So the answer to this question must be understood in two different ways:
-their preference for the {\em source} of the technology (university, any
-company) as well as the {\em type} of technology (instant, app based messaging
-systems vs. web-based systems integrated in another learning management system).
-
+academic institution (see Table \ref{tab:use_messapps}).
 Overall, the majority of the teachers responded that they do use messaging apps
@@
 they do not have a dedicated application) was the concept in the mind of the
-surveyed.
+surveyed.  \textcolor{blue}{In this case, we would like 
+to add a clarification. While we had in mind, as indicated by the possible answers, 
+instant messaging applications when making this question,
+we included these institution-provided applications mainly for completion. But
+it should be noted that, in most cases, they are not {\em instant} messaging
+apps in the way Telegram or Facebook Messenger are; in most cases they are
+messaging facilities provided by learning management systems such as (usually)
+Moodle. So the answer to this question must be understood in two different ways:
+their preference for the {\em source} of the technology (university, any
+company) as well as the {\em type} of technology (instant, app based messaging
+systems vs. web-based systems integrated in another learning management system).}
+
+\textcolor{blue}{This inclusion of university provided messaging applications in
+the survey might explain why there are so few, just 6.7\%, that answer they do not 
+use any messaging application. In general, universities provide official channels
+to communicate with students official academic information such as the exam schedule
+or the grades. The statistical mode is to use that kind of messaging. Some other
+people might not use it, but use some extraofficial or opt-in channels such as the other included in the survey; at the end, between these official and extraofficial channels most people cover their needs to communicate with students.
+This matches
+our subjective experience, in general.}
 
@@
 
+\textcolor{blue}{One of the questions we made in the second survey, related to
+the messaging applications used by tertiary education teachers, opens a new line
+of inquiry about what they {\em perceive} as such, and about how it is used.
+Namely, the responses indicated that the teachers perceived as messaging
+application not only what is usually called a chat or instant messaging app such
+as WhatsApp or Microsoft Teams, but also the means provided by the university for
+communicating with the student, such as a feature of grading applications that
+will email the grade to the student. This implies that there is a need by
+teachers, communication with students, also mostly unidirectional, and that it
+does not matter so much how that need is covered. However, this will need careful
+consideration, including how it ties with the automation of the learning
+experience that the chatbots bring.}
+
 % Future study (suggested by Noorhan): how COVID influenced adoption of these technologies.

### 2021-12-01 edubots_surveys.Rnw
:bug: caption

@@
 \end{center}
-    \caption{Use of chatbots provided by the teachers' academic institutions in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}
+    \caption{Use of \textcolor{blue}{messaging platforms} provided by the teachers' academic institutions in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}
     \label{figure:provided*chatbots_use}

### 2021-12-01 edubots_surveys.Rnw
Fixes caption

--- 2021-12-01 edubots_surveys.Rnw
@@
 \end{center}
-    \caption{Use of chatbots provided by the teachers' academic institutions in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}
+    \caption{Use of \textcolor{blue}{messaging platforms either external or} provided by the teachers' academic institutions in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}
     \label{figure:provided*chatbots_use}

### 2021-12-01 edubots_surveys.Rnw
Eliminates deleted code
Changing order of experiences

@@
 
-% \begin{figure}[h!tbp]
-% \begin{center}
-%     \begin{minipage}[t]{0.3\textwidth}
-%         \centering
-% <<gender, echo=FALSE, fig.width=3.2, fig.height=2.5>>=
-% #ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-% freq.Gender$source<-rep("survey1")
-% freqInteraction.Gender$source<-rep("survey2")
-% freqbinded.Gender <- rbind(freq.Gender, freqInteraction.Gender)
-% freqbinded.Gender$source <- factor(freqbinded.Gender$source) 
-% freqbinded.Gender[as.character(freqbinded.Gender$Gender)!="No", ] -> df1
-% ggplot(df1, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-% @
-% 
-% %       \includegraphics[width=\textwidth]{figures/gender.pdf}
-%     \end{minipage}
-%     \begin{minipage}[t]{0.3\textwidth}
-%         \centering
-% <<age,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
-% #ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-% freq.Age$source<-rep("survey1")
-% freqInteraction.Age$source<-rep("survey2")
-% freqbinded.Age <- rbind(freq.Age, freqInteraction.Age)
-% freqbinded.Age$source <- factor(freqbinded.Age$source) 
-% freqbinded.Age[as.character(freqbinded.Age$Age)!="No", ] -> df1
-% ggplot(df1, aes(x = Age, y=freqAge, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-% @
-% 
-% %       \includegraphics[width=\textwidth]{figures/age.pdf}
-%     \end{minipage}
-%     \begin{minipage}[t]{0.3\textwidth}
-%         \centering
-% <<sector,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
-% #ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-% freq.Sector$source<-rep("survey1")
-% freqInteraction.Sector$source<-rep("survey2")
-% freqbinded.Sector <- rbind(freq.Sector, freqInteraction.Sector)
-% freqbinded.Sector$source <- factor(freqbinded.Sector$source) 
-% ggplot(freqbinded.Sector, aes(x = Sector, y=freqSector, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-% @
-% %       \includegraphics[width=\textwidth]{figures/sector.pdf}
-%     \end{minipage}
-%     \vspace{0.5mm}
-%     \begin{minipage}[t]{0.38\textwidth}
-%         \centering
-% <<experience, echo=FALSE, fig.width=4.5, fig.height=3.475>>=
-% #ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-% freq.Experience$source<-rep("survey1")
-% freqInteraction.Experience$source<-rep("survey2")
-% freqbinded.Experience <- rbind(freq.Experience, freqInteraction.Experience)
-% freqbinded.Experience$source <- factor(freqbinded.Experience$source) 
-% freqbinded.Experience[as.character(freqbinded.Experience$Experience)!="No", ] -> df1
-% ggplot(df1, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-% @        
-% %       \includegraphics[width=\textwidth]{figures/experience.pdf}
-%     \end{minipage}
-%     \begin{minipage}[t]{0.52\textwidth}
-%         \centering
-% <<discipline,echo=FALSE, fig.width=8.2, fig.height=4.45>>=
-% #ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
-% freq.Discipline$source<-rep("survey1")
-% freqInteraction.Discipline$source<-rep("survey2")
-% freqbinded.Discipline <- rbind(freq.Discipline, freqInteraction.Discipline)
-% freqbinded.Discipline$source <- factor(freqbinded.Discipline$source) 
-% freqbinded.Discipline$Discipline <- factor(freqbinded.Discipline$Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other"))
-% ggplot(freqbinded.Discipline, aes(x = Discipline, y=freqDiscipline, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
-% @
-% 
-% %       \includegraphics[width=\textwidth]{figures/discipline.pdf}
-%     \end{minipage}
-% \end{center}
-%     \caption{Sample population description.
-The responses from two surveys were collected amount to 282 for the first survey (\textit{survey1} in red) and 205 for the second (\textit{survey2} in blue).
-Data are shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
-% \label{figure:teachers_population}
-% \end{figure}
-
-% % Olia suggests to delete this, as well as figure 1.
-% Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar. %, and as a matter of fact,
-% Additionally, as a matter of fact, as Figure \ref{figure:age.vs.exp} shows, age and experience are correlated strongly, with experience being roughly 20-30 years less than age. 
-% This might indicate that a differential analysis for age and experience will not yield significant differences, except maybe in the 6-15 years experience group, which is spread over all ages.
-At any rate, experience seems to be the dominating factor here and we'll use experience only unless we detect some significant difference by age.
-
-% \begin{figure}[h!tbp]
-% \begin{center}
-% <<interaction,message=FALSE,echo=FALSE, fig.height=2.0, fig.width=4.0>>=
-% library(forcats)
-% survey.interaction %>%
-%     mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
-%     mutate(Experience = fct_relevel(Experience, "0-05 years", "06-15 years", "16-25 years", "> 25 years" )) %>%
-%     group_by( Age, Experience ) %>% summarise( n = n() ) %>% mutate( freq = n/sum(n)) -> Age.vs.Experience
-% 
-% ggplot(Age.vs.Experience,aes(Age,Experience))+geom_point(aes(size=freq),colour="green")
-% @
-% \end{center}
-% \caption{Correlation between age and experience.}
-% \label{figure:age.vs.exp}
-% \end{figure}
-
 We will try to find the answers to the four research questions next, by
@@
 survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformProvided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+ggplot(df1, aes(x = MessagingPlatformProvided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Experience, levels=c("0-05 years","06-15 years", "16-25 years", "> 25 years")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @       
@@
 survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Experience, levels=c("0-05 years","06-15 years", "16-25 years", "> 25 years")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @       
@@
 survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformTelegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+ggplot(df1, aes(x = MessagingPlatformTelegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Experience, levels=c("0-05 years","06-15 years", "16-25 years", "> 25 years")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @       
@@
 <<experience_sync, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Experience, levels=c("0-05 years","06-15 years", "16-25 years", "> 25 years"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
 @

### 2021-12-02 edubots_surveys.Rnw
Responds to question on support

@@
 responses, an additional 16\% started using messaging apps during the pandemic
-for the first time in their classes. Aggregating the answers, currently 91\% of
-the teachers are using messaging apps as learning tools.
+for the first time in their classes. % Aggregating the answers, currently 91\% of
+% the teachers are using messaging apps as learning tools.
 %A few relevant facts from the collected data: teachers with 16-25 years of experience seem more worried about the security of messaging apps and teachers with up to 5 years of experience were more open to adopt messaging apps due to the pandemic; female teachers were more willing to adopt new platforms due to the pandemic, and even to start using safer alternatives; finally, university teachers that did not use them were more reluctant to start using them after the pandemic.
@@
 a great amount of teachers that would be against being in a chat group with
-students. Whether that's a slim majority or not, that's open to debate (and
+students. \textcolor{blue}{However, students will still need to get the services
+that the university, through chatbots, provide, thus opening the door for implantation of chatbots
+without the intervention of the professor, simply tapping university provided
+services \cite{bernier2002services}.}
+Whether that's a slim majority or not, that's open to debate (and
 would probably need a more pointed survey focused on this), but what is clear is
@@
  \item Teachers want to have support from their corresponding institution. This
-   is probably due to the strict European data regulations and to avoid the
-   overhead required to \textcolor{blue}{sign up new students every year}.
+   is probably due to the strict European data regulations \textcolor{blue}{on data protection},
+   gut also to avoid the overhead required to \textcolor{blue}{sign up new students every year.
+   In general support from specific formation to access to IT help desk for specific features
+   enhances the possibility of adoption by the teachers or the possibility of a successful
+   adoption that improves the learning outcomes. This is supported by the result of the two
+   surveys: they prefer whatever "messaging" application is provided by the university, and
+   also they value sustainability as well as "officiality" of the platform, as shown in
+   Table \ref{tab:interaction}}.
  \item Teachers need sustainability. The main reason is that implementing
@@
 An analysis of survey questions related to RQ4 seems to indicate that teachers
-prefer to have interaction with their students in a chat "room"; a preference of
-{\em horizontal} interaction might indicate the need to delegate or offload part
+prefer to \textcolor{blue}{share an interaction space with their student, as 
+as shown in Tables \ref{tab:kindinteraction} and \ref{tab:interaction}, where a majority of responders
+indicate they {\em don't} want unidirectional communication};a preference of
+{\em horizontal} interaction, \textcolor{blue}{but also the answer to the kind of
+chatbots preferred that features FAQ bots prominently, which might indicate a} 
+need to delegate or offload part
 of the burden of answering, and attending, every single question posed by

### 2021-12-02 edubots_surveys.Rnw
Latest changes

@@
 
-Moreover, this study clarifies the differences between the teachers’
+\textcolor{blue}{Comparing these results with those obtained in student surveys
+in \cite{MoraChatbots2021:anon}, we have understood better} the differences between the teachers’
 perspectives and/or intentions and that of their students when using the
@@
 
-% What kind of chatbots are preferred? (suggested by Fran)
-Once that initial introduction is done, teachers (and students as well) will
+\textcolor{blue}{What we are going to propose next is a possible process of
+technology introduction that is compatible with the conclusions of this study,
+but that would have to be piloted in order to check its value, and its
+relationship with better learning outcomes, as well as higher teacher
+satisfaction.}
+Once that initial introduction \textcolor{blue}{of institutional messaging
+automation tools} is done, teachers (and students as well) will
 probably prefer the kind of bots that alleviate bureaucratic or repetitive
 tasks, such as answering frequent questions or answers on class or assignment
-schedules. These will help the introduction of more complex chatbots that will
+schedules \textcolor{blue}{, as indicated by their answers to the respective
+questions}. These will help the introduction of more complex chatbots that will
 affect more directly learning outcomes, such as chatbots that help students
@@
 % Including questions in surveys
-The {\bf first survey}, shown in its original form in Figure \ref{figure:survey1}, which \textcolor{blue}{focused on} the use of messaging apps in class, and which tried to address mainly RQ2 and RQ3,
-% Antonio - I guess it refers to RQ3. ;)
-includes the following questions:
+The {\bf first survey}, shown in its original form in Figure \ref{figure:survey1}, which \textcolor{blue}{focused on} the use of messaging apps in class, includes the following questions:
 
@@
 We think, however that there's no explicit bias in this selection, although of course specific percentages will vary.
-These questions tried to address mainly RQ1 and RQ4.
 

### 2021-12-08 edubots_surveys.Rnw
fixes more minor typos in Sections 5-7

@@
 
-\textcolor{blue}{In the first survey, the multiple choice questions are
+\textcolor{blue}{In the {\bf first survey}, the multiple choice questions are
 focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider
-useful to be used in their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
+useful for their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
 university and \textcolor{blue}{the other for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees)}. Questions and
@@
 study.  All the comments collected from this trial were incorporated in the survey.
-We used mainly mailing lists, as well as Telegram groups,
+We mainly used mailing lists, as well as Telegram groups,
 to post the survey link to reach out to more educators. The university form was sent to Spanish
@@
 
-Survey
-questions \textcolor{blue}{are shown in Appendix I (Section \ref{app:questions})}.
-
 Responses were stored automatically in a Google Drive spreadsheet. Eventually,
 the results from the two forms we used for the first survey were collated in a
-single spreadsheet.
-
-\textcolor{blue}{The second survey was designed after initial results to the first survey arrived,
+single spreadsheet. Survey questions \textcolor{blue}{are shown in Appendix I (Section \ref{app:questions})}.
+
+\textcolor{blue}{The \bf{second survey} was designed after initial results to the first survey arrived,
 and pointed to necessities and experiences of teachers not being addressed by the first one; namely
@@
 It was piloted in a group of university teachers attending to a formation course, and validated with them.
-It was then extended to the rest of the responders, using the same media: Telegram groups, email and
-and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
+It was then extended to the rest of the responders, using the same media: Telegram groups, email and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
 (Section \ref{app:questions}).}
@@
 
-For the findings it occurs that the most favourable use case for chatbots in
+The most favourable use case for chatbots in
 Higher Education and vocational training is their use for the facilitation of an
@@
 48.2\%). A chi-square test of independence was performed to examine the relation
-among participants’ preferences for particular chatbot use cases. The relation
-between agenda and the FAQs use case was significant, $X^{2}_{(1, N = 282)} =
+among participants’ preferences for particular chatbot use cases. Out of the 171 teachers who consider useful the use of
+chatbots for agenda preparation in the class, 103 also consider useful chatbots’
+use for FAQs. The relation between agenda and the FAQs use case was significant, $X^{2}_{(1, N = 282)} =
 10.467$, $p =0.001$. The frequencies cross tabulated are given in Table
-\ref{tab:agenda*faq}. Out of the 171 teachers who consider useful the use of
-chatbots for agenda preparation in the class, 103 also consider useful chatbots’
-use for FAQs.
+\ref{tab:agenda*faq}.
 
@@
 to add a clarification. While we had in mind, as indicated by the possible answers, 
-instant messaging applications when making this question,
+instant messaging applications when we elaborated this question,
 we included these institution-provided applications mainly for completion. But
@@
 
-\textcolor{blue}{This inclusion of university provided messaging applications in
+\textcolor{blue}{This inclusion of university-provided messaging applications in
 the survey might explain why there are so few, just 6.7\%, that answer they do not 
@@
 prefer to \textcolor{blue}{share an interaction space with their student, as 
-as shown in Tables \ref{tab:kindinteraction} and \ref{tab:interaction}, where a majority of responders
-indicate they {\em don't} want unidirectional communication};a preference of
+shown in Tables \ref{tab:kindinteractions} and \ref{tab:interaction}, where a majority of responders
+indicate they {\em don't} want unidirectional communication}; a preference of
 {\em horizontal} interaction, \textcolor{blue}{but also the answer to the kind of
@@
 % Only some COVID-response relationship.
-In our survey, we couldn't find an answer to the right moment for doing this
+In our survey, we could not find an answer to the right moment for doing this
 introduction of chatbot technologies. Response to questions related to change of
@@
 
-\textcolor{blue}{One of the questions we made in the second survey, related to
+\textcolor{blue}{One of the questions we made in the \bf{second survey}, related to
 the messaging applications used by tertiary education teachers, opens a new line
@@
 \end{center}
-    \caption{\textcolor{blue}{Screen capture of the Spanish-language form used for the first survey}}
+    \caption{\textcolor{blue}{Screen capture of the Spanish-language form used for the \bf{first survey}}
 \label{figure:survey1}
@@
 \end{center}
-    \caption{\textcolor{blue}{Screen capture of the Spanish-language form used for the survey}}
+    \caption{\textcolor{blue}{Screen capture of the Spanish-language form used for the \bf{second survey}}
 \label{figure:survey2}

### 2022-01-25 edubots_surveys.Rnw
Addressing some typos

--- 2021-12-02 edubots_surveys.Rnw
@@
 of adopting these tools. Hence, a thorough examination of the teachers’
-experiences in this discipline can shed the light on the effective ways of
+experiences in this discipline can shed light on the effective ways of
 enhancing students’ learning and boosting their progress. In this contribution,
-we have surveyed the opinions of tertiary education teachers based mainly in
-Spain and Spanish-speaking countries. The focus of these surveys is to collect
-teachers’ feedback about their opinions of the introduction of the messaging
+we have surveyed the opinions of tertiary education teachers based in
+Spain (mainly) and Spanish-speaking countries. The focus of these surveys is to collect
+teachers’ feedback about their opinions regarding the introduction of the messaging
 platforms and chatbots in their classes, understand their needs and to gather
@@
 in general. At the same time, it also mentions different challenges, among which
-the most important is the blurring of social and academic life. Examining these
-opinions will be the objective of RQ3 in this paper.
-
-Nevertheless, there are challenges when using MIM tools that occur due to the
+the most important is the blurring of social and academic life; indeed, there are challenges when using MIM tools that occur due to the
 blurring of boundaries between academic and private life. This can lead to

### 2022-01-25 edubots_surveys.Rnw
Stopping to address formatting challenges

@@
 institutions, over all in the fringes of educational activity, not in the actual
-interaction student-teacher, its implementation or deployment is not trivial.
+student-teacher interaction, its implementation or deployment is not trivial.
 Some authors, for instance \cite{sjostrom2018designing} have proposed a
@@
 \cite{Roblyer2010,Pimmer2019}. However, higher education is a special domain
-where, according to Hobert \cite{hobert2019you}, specific pedagogical factors
+where, according to \cite{hobert2019you}, specific pedagogical factors
 such as learning success and increased motivation are more important.  Therefore,
@@
 Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of
-2021, post-pandemic and while, at least in Spain, many universities had
+2021, during the Covid-19 pandemic and while, at least in Spain, many universities had
 mandatory virtual teaching.}
@@
 \textcolor{blue}{A total of 205 teachers responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%).
-From those, 124 were (60.5\%), 65 female (31.7\%) and 16 teachers preferred not to indicate their gender (7.8\%).
-In terms of age, the majority of the participants (n=70) was again, as in the first survey, 45-55 years old (34.1\%), while 67 teachers were 35-45 (32.7\%), 42 were 25-35 (20.5\%) and 26 teachers were older than 55 (12.7\%).
+From those, 124 were male (60.5\%), 65 female (31.7\%) and 16 teachers preferred not to indicate their gender (7.8\%).
+In terms of age, the majority of the participants (n=70) was again, as in the first survey, 45-55 years old (34.1\%), while 67 teachers were 35-45 years old (32.7\%), 42 were 25-35 (20.5\%) and 26 teachers were older than 55 (12.7\%).
 In terms of teaching experience, 59 teachers had a teaching experience of 16-25 years (28.8\%), 51 teachers had 6-15 years (24.9\%) and 0-5 years of experience (24.9\%), and 44 teachers more than 25 years of teaching experience (21.5\%).}
@@
 includes mostly teachers from university, although about 32\% and 8\% are from
-vocational education in the first and second survey respectively. Regarding
+non-universitary tertiary education in the first and second survey respectively. Regarding
 gender, 61\% of the teachers were male and 32\% female, while approximately 5\%
@@
 Overall, the majority of the teachers responded that they do use messaging apps
-in their classrooms, from which apps provided by the academic institution
+in their classrooms, from which apps (or, more probably, messaging solutions) provided by the academic institution
 (n=159, 56\%) and WhatsApp (n=124, 44.0\%) were the most common responses. Only
@@
 academic institutions. % Olia requests support for this. 
-However, younger teachers also use Telegram with more than 25\%, a percentage
+However, younger teachers also use Telegram with more than 25\% responding they do, a percentage
 that falls to about 10\% for teachers that are 55 or older. %The third column
@@
 Some of the questions in the survey were focused on the impact of the COVID19
-pandemic between 2020 and 2021, in the teachers' viewpoints towards the use of
+pandemic between the 2020 and 2021 academic years in the teachers' attitudes towards the use of
 instant messaging apps in their class. Our main intention in this case was to
@@
 \vspace{0.8em}
-\caption{Sector * post-covid changes crosstabulation}
+\caption{Sector * post-covid changes cross-tabulation}
 \label{tab:sector*covid}
@@
 
-The majority of the teachers (n=165) mentioned that no changes in their habits occurred due to the emergency remote teaching, as the use of messaging apps was part of their teaching practices and remains the same, from which 105 teachers come from the university, and 60 teachers from the vocational sector.
+The majority of the teachers (n=165) mentioned that no changes in their habits occurred due to the emergency remote teaching, as the use of messaging apps was part of their teaching practices and remains the same, from which 105 teachers come from the university, and 60 teachers from the non-universitary tertiary sector.
 The relationships between changes in the use of messaging apps, due to the covid-19 pandemic, and the instructors’ discipline, $X^{2}_{(24, N = 282)} = 44.856$, $p =0.006$, as well as the gender, $X^{2}_{(8, N = 282)} = 16.249$, p= 0.039 were also significant.
@@
 students. \textcolor{blue}{However, students will still need to get the services
-that the university, through chatbots, provide, thus opening the door for implantation of chatbots
+that the university, through chatbots, provide, thus opening the door for deployment of chatbots
 without the intervention of the professor, simply tapping university provided
@@
 
-A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
+%A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
 The majority of the teachers were aged 45-55 years old (70; 34.1\%), followed by individuals aged 35-45 (67, 32.7\%), and 25-35 (42; 20.5\%), while the minority was aged $>$~55 years old (26; 12.7\%).
@@
 
-\textcolor{blue}{As it can be seen in the table, the main responses aim to use a sustainable and official application, i.e.
+\textcolor{blue}{As it can be seen in the table, the bulk of responders express their wish to use a sustainable and official application, i.e.
 both being approved or provided by the University (or the educational centre), and also maintained by the technical staff of the centre instead of giving this responsability/task to the teacher.
-In addition, it is very important for the teachers that the used tools allow to communicate all the members of the classroom, including themselves; as well as being already known or used in everyday tasks, e.g.
+In addition, it is very important for the teachers that the used tools that all the members of the class communicate, including themselves; as well as being already known or used in everyday tasks, e.g.
 Telegram or WhatsApp.}
@@
 Finally, a two-step cluster analysis was conducted, with a log-likelihood
-distance measure adopted, to explore how the cases could be grouped based on
+distance measure adopted, to explore how the use cases could be grouped based on
 their preferences of specific interaction media features, and which features
@@
 Moodle. So the answer to this question must be understood in two different ways:
-their preference for the {\em source} of the technology (university, any
+their preference for the {\em provider} of the technology (the university itself, any
 company) as well as the {\em type} of technology (instant, app based messaging

### 2022-01-25 edubots_surveys.Rnw
Changed to black closes #77
We can eliminate formatting later if needed

@@
 
-The introduction of new technologies in the classroom, \textcolor{blue}{to be successful, involves extra
+The introduction of new technologies in the classroom, \textcolor{black}{to be successful, involves extra
 teacher training, devising methods for enhancing student engagement with the new
@@
 full adoption. In most cases, the magnitude of the uptake of the new technology
-impinges on the collaboration of all the parties using it. \textcolor{blue}{Hence, examining the
+impinges on the collaboration of all the parties using it. \textcolor{black}{Hence, examining the
 users’ opinions is an important first step in boosting this collaboration
@@
 {\sf anonymized European Project}, the sponsor of this study, is to
-\textcolor{blue}{explore best practices and innovative use of chatbots, and to create 
+\textcolor{black}{explore best practices and innovative use of chatbots, and to create 
 a learning community of educators in higher education institutions.
@@
 
-\textcolor{blue}{In this study, data collection involved two phases:}
+\textcolor{black}{In this study, data collection involved two phases:}
  \begin{itemize}
@@
 Initially, a single survey was developed for this purpose and responses from 300
-higher education teachers were collected and analysed\textcolor{blue}{; this will be explained more fully in the methodology section}. The responses' analysis
+higher education teachers were collected and analysed\textcolor{black}{; this will be explained more fully in the methodology section}. The responses' analysis
 entailed the creation of a second survey to which 200 teachers' responses were
-collected\textcolor{blue}{, with the methodology and collective characteristics that will be explained below. The questions of the second survey focussed on discussing teachers'
+collected\textcolor{black}{, with the methodology and collective characteristics that will be explained below. The questions of the second survey focussed on discussing teachers'
 needs, opinions and preferences of the development of future technology-enhanced
@@
 recommendations to make a successful deployment of chatbot technologies (and, in
-some cases, general instant messaging applications) in higher education\textcolor{blue}{; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be used in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from RQ3 we will also try to find best practices in the adoption of messaging platforms and they accompanying chatbots.}
-
-The remainder of the paper is organized as follows: \textcolor{blue}{first, an overview of what
+some cases, general instant messaging applications) in higher education\textcolor{black}{; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be used in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from RQ3 we will also try to find best practices in the adoption of messaging platforms and they accompanying chatbots.}
+
+The remainder of the paper is organized as follows: \textcolor{black}{first, an overview of what
 current research has found about the use of messaging applications, including
@@
 WhatsApp is, at least in most Western countries, the most popular MIM platform
-used by educators to \textcolor{blue}{provide} assignments' feedback to students, support course
+used by educators to \textcolor{black}{provide} assignments' feedback to students, support course
 discussions, and provide learning resources in informal learning settings
@@
 \cite{Yildirim2017} can improve student motivation. In this sense, the authors
-in \cite{Pimmer2019} \textcolor{blue}{adopted a quasi-experimental, survey-based approach to
+in \cite{Pimmer2019} \textcolor{black}{adopted a quasi-experimental, survey-based approach to
 report the positive impact of using instant messaging tools in boosting
@@
 Messenger with the focus to identify characteristics and quality metrics such as
-language, subject matter and platform\textcolor{blue}{, whereas the study undertaken by Pérez and collaborators
+language, subject matter and platform\textcolor{black}{, whereas the study undertaken by Pérez and collaborators
 \cite{perez2020rediscovering} aimed to categorise educational chatbots, according
@@
 proposed a generic chatbot for university students that is able to answer to
-their frequently asked questions \textcolor{blue}{and, for some time, the University of Granada had
-\textcolor{blue}{Elvira} as a chatbot in its main web page \cite{MOREO20129} to perform that duty.} Besides being able
+their frequently asked questions \textcolor{black}{and, for some time, the University of Granada had
+\textcolor{black}{Elvira} as a chatbot in its main web page \cite{MOREO20129} to perform that duty.} Besides being able
 to answer pre-established (frequent) questions, it did so from the website of
-the University of Granada using an inset \textcolor{blue}{persona, voiced by a real person, who
+the University of Granada using an inset \textcolor{black}{persona, voiced by a real person, who
 lip-synced the answers. The emphasis in the case of Elvira, however, was on the
@@
 students that need more attention and send them more educational resources
-relevant to their academic attainment. \textcolor{blue}{In addition, a recent study
+relevant to their academic attainment. \textcolor{black}{In addition, a recent study
 has analysed how the use of chatbots positively affected the learning outcomes
@@
 appropriate types of questions that the chatbots should support for different
-courses.  \textcolor{blue}{Some other authors}, like \cite{coronado2018cognitive}, proposed agents that
+courses.  \textcolor{black}{Some other authors}, like \cite{coronado2018cognitive}, proposed agents that
 store learning materials to be provided on demand to students, whereas the
@@
 such as learning success and increased motivation are more important.  Therefore,
-to develop \textcolor{blue}{effective chatbots for higher education, all stakeholders'
+to develop \textcolor{black}{effective chatbots for higher education, all stakeholders'
 (i.e. educators, students, institutions, etc) needs should be carefully
@@
 really benefited from it. This is, once again, a proof of the benefit of
-chatbots in certain settings; however, there are some \textcolor{blue}{prior experiences, as well as needs} that might
+chatbots in certain settings; however, there are some \textcolor{black}{prior experiences, as well as needs} that might
 prevent the successful acceptance of the technology, and these are what we are
-trying to find out in this paper, together with what kind of features would \textcolor{blue}{improve
+trying to find out in this paper, together with what kind of features would \textcolor{black}{improve
 its acceptance}.
@@
 Besides, the present work is focused on the other key actor in this challenge,
-i.e. educators. \textcolor{blue}{How they accepted chatbots} has been studied very recently by Chocarro et
+i.e. educators. \textcolor{black}{How they accepted chatbots} has been studied very recently by Chocarro et
 al. \cite{doi:10.1080/03055698.2020.1850426}, who, by analysing surveys, created
@@
 
-\textcolor{blue}{This study followed a quantitative approach towards addressing its research objective, by collecting rich data about the use of messaging applications and chatbots
+\textcolor{black}{This study followed a quantitative approach towards addressing its research objective, by collecting rich data about the use of messaging applications and chatbots
 by educators in both universities and colleges\footnote{In Spain, they are called simply high schools, and deliver
@@
 
-\textcolor{blue}{In the first survey, the multiple choice questions are
+\textcolor{black}{In the first survey, the multiple choice questions are
 focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider
 useful to be used in their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
-university and \textcolor{blue}{the other for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees)}. Questions and
+university and \textcolor{black}{the other for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees)}. Questions and
 responses were the same, except for the type of tertiary degrees that
@@
 
-\textcolor{blue}{This survey was piloted by the authors of the paper and their colleagues before using it in the 
+\textcolor{black}{This survey was piloted by the authors of the paper and their colleagues before using it in the 
 study.  All the comments collected from this trial were incorporated in the survey.
@@
 (68.4\%) and 89 at other tertiary education institutions (31.6\%).
-\textcolor{blue}{From those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%) and 5 teachers preferred not to indicate their gender (1.8\%).
+\textcolor{black}{From those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%) and 5 teachers preferred not to indicate their gender (1.8\%).
 In terms of age, the majority of the participants (n=111) in this survey was 45-55 years old (39.4\%), while 91 teachers were 35-45 (32.3\%), 46 were 25-35 (16.3\%) and 34 teachers were older than 55 (12.1\%).
@@
 Survey
-questions \textcolor{blue}{are shown in Appendix I (Section \ref{app:questions})}.
+questions \textcolor{black}{are shown in Appendix I (Section \ref{app:questions})}.
 
@@
 
-\textcolor{blue}{The second survey was designed after initial results to the first survey arrived,
+\textcolor{black}{The second survey was designed after initial results to the first survey arrived,
 and pointed to necessities and experiences of teachers not being addressed by the first one; namely
@@
 
-\textcolor{blue}{A total of 205 teachers responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%).
+\textcolor{black}{A total of 205 teachers responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%).
 From those, 124 were male (60.5\%), 65 female (31.7\%) and 16 teachers preferred not to indicate their gender (7.8\%).
@@
 
-Group messaging apps have become a powerful tool for \textcolor{blue}{communicating} with
+Group messaging apps have become a powerful tool for \textcolor{black}{communicating} with
 students. Also, many of them have built-in chatbots to enhance the learning
@@
 realized that there were some prior issues mainly related to the adoption of a
-technology, \textcolor{blue}{i.e. chatbots}, that generally piggybacks on another, \textcolor{blue}{i.e. messaging
+technology, \textcolor{black}{i.e. chatbots}, that generally piggybacks on another, \textcolor{black}{i.e. messaging
 applications. Generally,} in a technology adoption model, perceived ease of use and
@@
 Telegram). With respect to specific disciplines, Engineering and Technology
-teachers are more active in their use, \textcolor{blue}{but the number of teachers from Humanities 
+teachers are more active in their use, \textcolor{black}{but the number of teachers from Humanities 
 who answered they used these apps in their classes is also remarkable}
@@
 \end{center}
-    \caption{Use of \textcolor{blue}{messaging platforms either external or} provided by the teachers' academic institutions in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}
+    \caption{Use of \textcolor{black}{messaging platforms either external or} provided by the teachers' academic institutions in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}
     \label{figure:provided*chatbots_use}
@@
 that shows the contribution of each cell to the test. In the Pearson's residual
-graphs, \textcolor{blue}{the responses to the question about the use of messaging apps were shortened for the sake of clarity according to}: 1)
+graphs, \textcolor{black}{the responses to the question about the use of messaging apps were shortened for the sake of clarity according to}: 1)
 \textit{Did/do} stands for \textit{Yes, I did use it before and do use it now};
@@
 19\% of the chi-square test results. Also, the number of educators from
-Technology or Engineering that started using safer alternatives \footnote{\textcolor{blue}{This addresses the issue of insecure/unsafe applications which do not encrypt messages or can be easily compromised exposing information}} are less than
+Technology or Engineering that started using safer alternatives \footnote{\textcolor{black}{This addresses the issue of insecure/unsafe applications which do not encrypt messages or can be easily compromised exposing information}} are less than
 expected (compared to the educators from other disciplines). Bear in mind that
@@
 groups with specific goals and dedicated to the organization of the course and
-its tasks, and from the pedagogic point of view \textcolor{blue}{it also seems more appropriate to improve
+its tasks, and from the pedagogic point of view \textcolor{black}{it also seems more appropriate to improve
 the learning process}. Interestingly, and as a cross-check of the answers above,
@@
 a great amount of teachers that would be against being in a chat group with
-students. \textcolor{blue}{However, students will still need to get the services
+students. \textcolor{black}{However, students will still need to get the services
 that the university, through chatbots, provide, thus opening the door for deployment of chatbots
@@
 In terms of teaching experience, 59 teachers (28.8\%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9\%), 0-5 years (51; 24.9\%) and more than 25 years of experience (44; 21.5\%).
-The teachers were asked about what kind of interaction media features they value the most \textcolor{blue}{; i.e.
+The teachers were asked about what kind of interaction media features they value the most \textcolor{black}{; i.e.
 what their preferred features are in the applications/tools that they use to interact with their students.} The frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
@@
 \vspace{0.8em}
-\caption{Interaction media features valued by teachers. \textcolor{blue}{Details about each of these features can be read in Appendix I (Section \ref{app:questions}, second survey)}.}
+\caption{Interaction media features valued by teachers. \textcolor{black}{Details about each of these features can be read in Appendix I (Section \ref{app:questions}, second survey)}.}
 \label{tab:interaction}
@@
 
-\textcolor{blue}{As it can be seen in the table, the bulk of responders express their wish to use a sustainable and official application, i.e.
+\textcolor{black}{As it can be seen in the table, the bulk of responders express their wish to use a sustainable and official application, i.e.
 both being approved or provided by the University (or the educational centre), and also maintained by the technical staff of the centre instead of giving this responsability/task to the teacher.
@@
 they do not have a dedicated application) was the concept in the mind of the
-surveyed.  \textcolor{blue}{In this case, we would like 
+surveyed.  \textcolor{black}{In this case, we would like 
 to add a clarification. While we had in mind, as indicated by the possible answers, 
@@
 company) as well as the {\em type} of technology (instant, app based messaging
-systems vs. web-based systems integrated in another learning management system).}
-
-\textcolor{blue}{This inclusion of university provided messaging applications in
+systems vs. web-based messaging systems integrated in another learning management system).}
+
+\textcolor{black}{This inclusion of university provided messaging applications in
 the survey might explain why there are so few, just 6.7\%, that answer they do not 
@@
 results, and that should require further study, is: Are teachers really aware
-of the possibilities of chatbots in the classroom? \textcolor{blue}{The survey 
+of the possibilities of chatbots in the classroom? \textcolor{black}{The survey 
 only listed a few functionalities for the chatbots and only a few subjects selected 
@@
 taken into account when introducing chatbot technologies in the classroom: 
-\textcolor{blue}{it will have to be as simple, and as satisfactory, as possible, 
+\textcolor{black}{it will have to be as simple, and as satisfactory, as possible, 
 to (possibly) change this existing perception}.
@@
 proportion to use them for grades and FAQs in comparison with Vocational High
-School teachers. \textcolor{blue}{
+School teachers. \textcolor{black}{
 This seems reasonable as the frequency of seeing the students
@@
 are. From this concrete plot it is interesting as well the fact that very few
-young/inexperience teachers are willing to use chatbots for other uses. \textcolor{blue}{This
+young/inexperience teachers are willing to use chatbots for other uses. \textcolor{black}{This
 reinforces the hypothesis thrown at the beginning of this section that younger teachers have less experience to consider new ways of using chatbots in their daily work.}
@@
  \item Teachers want to have support from their corresponding institution. This
-   is probably due to the strict European data regulations \textcolor{blue}{on data protection},
-   gut also to avoid the overhead required to \textcolor{blue}{sign up new students every year.
+   is probably due to the strict European data regulations \textcolor{black}{on data protection},
+   gut also to avoid the overhead required to \textcolor{black}{sign up new students every year.
    In general support from specific formation to access to IT help desk for specific features
@@
 An analysis of survey questions related to RQ4 seems to indicate that teachers
-prefer to \textcolor{blue}{share an interaction space with their student, as 
+prefer to \textcolor{black}{share an interaction space with their student, as 
 as shown in Tables \ref{tab:kindinteraction} and \ref{tab:interaction}, where a majority of responders
 indicate they {\em don't} want unidirectional communication};a preference of
-{\em horizontal} interaction, \textcolor{blue}{but also the answer to the kind of
+{\em horizontal} interaction, \textcolor{black}{but also the answer to the kind of
 chatbots preferred that features FAQ bots prominently, which might indicate a} 
@@
 messaging applications that their institutions support.  Technology adoption
-literature often \textcolor{blue}{focuses} on users’ perceptions of the technology’s usefulness and
+literature often \textcolor{black}{focuses} on users’ perceptions of the technology’s usefulness and
 ease of use as important prerequisites for successful adoption and
@@
 these applications and shape the social and educational experiences of their
-students. \textcolor{blue}{To accomplish this fruitful integration}, institutions have to ensure that
+students. \textcolor{black}{To accomplish this fruitful integration}, institutions have to ensure that
 these messaging applications not only are GDPR compliant to keep students’ data
@@
 
-\textcolor{blue}{Comparing these results with those obtained in student surveys
+\textcolor{black}{Comparing these results with those obtained in student surveys
 in \cite{MoraChatbots2021:anon}, we have understood better} the differences between the teachers’
@@
 
-\textcolor{blue}{What we are going to propose next is a possible process of
+\textcolor{black}{What we are going to propose next is a possible process of
 technology introduction that is compatible with the conclusions of this study,
@@
 satisfaction.}
-Once that initial introduction \textcolor{blue}{of institutional messaging
+Once that initial introduction \textcolor{black}{of institutional messaging
 automation tools} is done, teachers (and students as well) will
@@
 tasks, such as answering frequent questions or answers on class or assignment
-schedules \textcolor{blue}{, as indicated by their answers to the respective
+schedules \textcolor{black}{, as indicated by their answers to the respective
 questions}. These will help the introduction of more complex chatbots that will
@@
 
-\textcolor{blue}{One of the questions we made in the second survey, related to
+\textcolor{black}{One of the questions we made in the second survey, related to
 the messaging applications used by tertiary education teachers, opens a new line
@@
 \item Experience on the job: up to 5 years, 5-15 years, 15-25 years, more than 25 years.
-\textcolor{blue}{
+\textcolor{black}{
 \item Type of degree: university, other tertiary education.
@@
 \end{center}
-    \caption{\textcolor{blue}{Screen capture of the Spanish-language form used for the first survey}}
+    \caption{\textcolor{black}{Screen capture of the Spanish-language form used for the first survey}}
 \label{figure:survey1}
@@
 % Including questions in surveys
-The {\bf first survey}, shown in its original form in Figure \ref{figure:survey1}, which \textcolor{blue}{focused on} the use of messaging apps in class, includes the following questions:
+The {\bf first survey}, shown in its original form in Figure \ref{figure:survey1}, which \textcolor{black}{focused on} the use of messaging apps in class, includes the following questions:
 
@@
 \item Students self-organize and with the teacher not being part of any chat group
-\textcolor{blue}{
+\textcolor{black}{
 \item A chat group with all the students and teachers of the School/High-School/Faculty
@@
 \end{center}
-    \caption{\textcolor{blue}{Screen capture of the Spanish-language form used for the survey}}
+    \caption{\textcolor{black}{Screen capture of the Spanish-language form used for the survey}}
 \label{figure:survey2}
@@
 The {\bf second survey}, shown in its original form in Figure \ref{figure:survey2}, followed the same paths, only in this case there was a single questionnaire, and with a different scope, focusing on the kind of interaction media features that teachers value the most.
-%\textcolor{blue}{A capture of these questions is included in Figure \ref{fig:survey2}} % this sentence is repeated
+%\textcolor{black}{A capture of these questions is included in Figure \ref{fig:survey2}} % this sentence is repeated
 % Olia - see my comment above.
@@
 
-Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are  their \textcolor{blue}{past experiences and needs} with regard to the use of instant messaging applications with students, and even using bots or chatbots in the classroom.
+Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are  their \textcolor{black}{past experiences and needs} with regard to the use of instant messaging applications with students, and even using bots or chatbots in the classroom.
 In addition the survey asked about the most relevant \textit{interaction media features} for the teachers with respect to the potential tool to use in class.

### 2022-01-25 edubots_surveys.Rnw

@@
 
-\textcolor{black}{In the first survey, the multiple choice questions are
+In the {\bf first survey}, the multiple choice questions are
 focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider
-useful to be used in their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
-university and \textcolor{black}{the other for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees)}. Questions and
+useful for their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
+university and the other for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees). Questions and
 responses were the same, except for the type of tertiary degrees that
-were considered.}}
+were considered.}
 
@@
 
-Survey
-questions \textcolor{black}{are shown in Appendix I (Section \ref{app:questions})}.
-
 Responses were stored automatically in a Google Drive spreadsheet. Eventually,
 the results from the two forms we used for the first survey were collated in a
-single spreadsheet.
-
-\textcolor{black}{The second survey was designed after initial results to the first survey arrived,
+single spreadsheet. Survey questions are shown in Appendix I (Section \ref{app:questions}).
+
+The \bf{second survey} was designed after initial results to the first survey arrived,
 and pointed to necessities and experiences of teachers not being addressed by the first one; namely
@@
 It was piloted in a group of university teachers attending to a formation course, and validated with them.
-It was then extended to the rest of the responders, using the same media: Telegram groups, email and
-and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
-(Section \ref{app:questions}).}
+It was then extended to the rest of the responders, using the same media: Telegram groups, email and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
+(Section \ref{app:questions}).
 
@@
 
-\textcolor{black}{This inclusion of university provided messaging applications in
+This inclusion of university-provided messaging applications in
 the survey might explain why there are so few, just 6.7\%, that answer they do not 
@@
 This matches
-our subjective experience, in general.}
+our subjective experience, in general.
 
@@
 An analysis of survey questions related to RQ4 seems to indicate that teachers
-prefer to \textcolor{black}{share an interaction space with their student, as 
-as shown in Tables \ref{tab:kindinteraction} and \ref{tab:interaction}, where a majority of responders
-indicate they {\em don't} want unidirectional communication};a preference of
-{\em horizontal} interaction, \textcolor{black}{but also the answer to the kind of
-chatbots preferred that features FAQ bots prominently, which might indicate a} 
+prefer to share an interaction space with their student, as 
+shown in Tables \ref{tab:kindinteractions} and \ref{tab:interaction}, where a majority of responders
+indicate they {\em don't} want unidirectional communication; a preference of
+{\em horizontal} interaction, but also the answer to the kind of
+chatbots preferred that features FAQ bots prominently, which might indicate a
 need to delegate or offload part
@@
 
-\textcolor{black}{One of the questions we made in the second survey, related to
+One of the questions we made in the \bf{second survey}, related to
 the messaging applications used by tertiary education teachers, opens a new line
@@
 consideration, including how it ties with the automation of the learning
-experience that the chatbots bring.}
+experience that the chatbots bring.
 
@@
 \end{center}
-    \caption{\textcolor{black}{Screen capture of the Spanish-language form used for the first survey}}
+    \caption{Screen capture of the Spanish-language form used for the \bf{first survey}}
 \label{figure:survey1}
@@
 \end{center}
-    \caption{\textcolor{black}{Screen capture of the Spanish-language form used for the survey}}
+    \caption{Screen capture of the Spanish-language form used for the \bf{second survey}}
 \label{figure:survey2}

### 2022-01-25 edubots_surveys.Rnw
Uncomment names refs #78

@@
 % Remember to substitute figures/ by nothing in the generated PDF
-% \author[
-%   addressref={aff1},                  
-%   corref={aff1},                      
-%   email={jmerelo@ugr.es}  
-% ]{\inits{JJM}\fnm{Juan J.} \snm{Merelo}}
-% \author[
-%   addressref={aff1},
-%   email={pacv@ugr.es}
-% ]{\inits{PAC}\fnm{Pedro A.} \snm{Castillo}}
-% \author[
-%   addressref={aff2},
-%   email={amorag@ugr.es}
-% ]{\inits{AMM}\fnm{Antonio M.} \snm{Mora}}
-% \author[
-%   addressref={aff1},
-%   email={fbarranco@ugr.es}
-% ]{\inits{FB}\fnm{Francisco} \snm{Barranco}}
-% \author[
-%   addressref={aff3},
-%   email={n.h.abbas@leeds.ac.uk}
-% ]{\inits{NA}\fnm{Noorhan} \snm{Abbas}}
-% \author[
-%   addressref={aff1},
-%   email={aguillen@ugr.es}
-% ]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
-% \author[
-%   addressref={aff4},
-%   email={o.tsivitanidou@cyens.org.cy}
-% ]{\inits{OT}\fnm{Olia} \snm{Tsivitanidou}}
-% 
-% \address[id=aff1]{%                           
-%   \orgdiv{Department of Computer Architecture and Technology},           
-%   \orgname{University of Granada},
-%   \city{Granada},
-%   \cny{Spain}
-% }
-% \address[id=aff2]{%
-%   \orgdiv{Department of Signal Theory, Telematics and Communications},
-%   \orgname{University of Granada},
-%   \city{Granada},
-%   \cny{Spain}
-% }
-% \address[id=aff3]{%
-%   \orgdiv{School of Computing},
-%   \orgname{University of Leeds},
-%   \city{Leeds},
-%   \cny{UK}
-% }
-% \address[id=aff4]{%
-%   \orgname{CYENS},         
-%   \city{Nicosia},
-%   \cny{Cyprus} 
-% }
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Enter short notes here                   %%
-%%                                          %%
-%% Short notes will be after addresses      %%
-%% on first page.                           %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\begin{artnotes}
-%%\note{Sample of title note}     % note to the article
-%\note[id=n1]{Equal contributor} % note, connected to author
-%\end{artnotes}
+\author[
+  addressref={aff1},
+  corref={aff1},
+  email={jmerelo@ugr.es}
+]{\inits{JJM}\fnm{Juan J.} \snm{Merelo}}
+\author[
+  addressref={aff1},
+  email={pacv@ugr.es}
+]{\inits{PAC}\fnm{Pedro A.} \snm{Castillo}}
+\author[
+  addressref={aff2},
+  email={amorag@ugr.es}
+]{\inits{AMM}\fnm{Antonio M.} \snm{Mora}}
+\author[
+  addressref={aff1},
+  email={fbarranco@ugr.es}
+]{\inits{FB}\fnm{Francisco} \snm{Barranco}}
+\author[
+  addressref={aff3},
+  email={n.h.abbas@leeds.ac.uk}
+]{\inits{NA}\fnm{Noorhan} \snm{Abbas}}
+\author[
+  addressref={aff1},
+  email={aguillen@ugr.es}
+]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
+\author[
+  addressref={aff4},
+  email={o.tsivitanidou@cyens.org.cy}
+]{\inits{OT}\fnm{Olia} \snm{Tsivitanidou}}
+
+\address[id=aff1]{%
+  \orgdiv{Department of Computer Architecture and Technology},
+  \orgname{University of Granada},
+  \city{Granada},
+  \cny{Spain}
+}
+\address[id=aff2]{%
+  \orgdiv{Department of Signal Theory, Telematics and Communications},
+  \orgname{University of Granada},
+  \city{Granada},
+  \cny{Spain}
+}
+\address[id=aff3]{%
+  \orgdiv{School of Computing},
+  \orgname{University of Leeds},
+  \city{Leeds},
+  \cny{UK}
+}
+\address[id=aff4]{%
+  \orgname{CYENS},
+  \city{Nicosia},
+  \cny{Cyprus}
+}
 

### 2022-01-25 edubots_surveys.Rnw
Totally deanonymized, now there are format errors
closes #78

@@
 focus of the
-% EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
-{\sf anonymized European Project}, the sponsor of this study, is to
+EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
+the sponsor of this study, is to
 \textcolor{black}{explore best practices and innovative use of chatbots, and to create 
@@
 \item The first phase aimed to collect feedback from students about their actual
-  needs \cite{MoraChatbots2021:anon}. Hence, the objective was to collect
   information about students’ preferences of tools/applications for chatting and
@@
 
-Along this line of research, our previous work \cite{MoraChatbots2021:anon}
+Along this line of research, our previous work \cite{MoraChatbots2021}
 aimed at analysing the expectations of students on this regard; recent papers
@@
 \textcolor{black}{Comparing these results with those obtained in student surveys
-in \cite{MoraChatbots2021:anon}, we have understood better} the differences between the teachers’
+in \cite{MoraChatbots2021}, we have understood better} the differences between the teachers’
 perspectives and/or intentions and that of their students when using the
@@
 
-% \section{Declarations}
-% \label{sec:decl}
-% 
-% \subsection{Availability of data and materials}
-% 
-% The datasets generated and analysed during the current study are available in the {\tt edubots-paper} repository, accessible from https://anonymous.url
-% % {\tt https://github.com/JJ/edubots-paper/tree/main/data}.
-% 
-% 
-% \subsection{Competing interests}
-% 
-% The authors declare that they have no competing interests.
-% 
-% 
-% \subsection{Funding}
-% 
-% This work has been supported by EDUBOTS project, funded under the scheme Erasmus + KA2: Cooperation for innovation and the exchange of good practices - Knowledge Alliances (grant agreement no: 612446).
-% 
-% \subsection{Authors' contributions}
-% 
-% All the authors have contributed to the study presented in this manuscript. (Rest hidden for double blind)
-% 
-% JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
-% 
-% PAC has revised the paper and researched the state of the art, as well as contributed to the survey design.
-% AMM has revised the paper and researched the state of the art, as well as contributed to the survey design.
-% FB has made the analysis and processed data and contributed to the survey design.
-% NA has supervised the state of the art, and written the bulk of it, as well as contributed to discussion and conclusions.
-% OT has performed data analysis, and contributed to discussion and conclusions.
-% AG has contributed to the design of the survey, analysis, discussion and conclusions.
-% 
-% All authors have read and approved the final manuscript.
-% 
-% \subsection{Acknowledgements}
-% 
-% The authors want to thank to the educators who participated in the survey, and also people who have distributed the survey in their mailing lists, especially Mario García Valdez, Jesús Moreno León and the late José Raúl Canay.
-% We would also like to thank the anonymous reviewers that have contributed greatly to the improvement of this paper.
+\section{Declarations}
+\label{sec:decl}
+
+\subsection{Availability of data and materials}
+
+The datasets generated and analysed during the current study are available in the {\tt edubots-paper} repository, accessible from https://anonymous.url
+% {\tt https://github.com/JJ/edubots-paper/tree/main/data}.
+
+\subsection{Competing interests}
+
+The authors declare that they have no competing interests.
+
+\subsection{Funding}
+
+This work has been supported by EDUBOTS project, funded under the scheme Erasmus + KA2: Cooperation for innovation and the exchange of good practices - Knowledge Alliances (grant agreement no: 612446).
+
+\subsection{Authors' contributions}
+
+All the authors have contributed to the study presented in this manuscript. (Rest hidden for double blind)
+
+JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
+
+PAC has revised the paper and researched the state of the art, as well as contributed to the survey design.
+AMM has revised the paper and researched the state of the art, as well as contributed to the survey design.
+FB has made the analysis and processed data and contributed to the survey design.
+NA has supervised the state of the art, and written the bulk of it, as well as contributed to discussion and conclusions.
+OT has performed data analysis, and contributed to discussion and conclusions.
+AG has contributed to the design of the survey, analysis, discussion and conclusions.
+
+All authors have read and approved the final manuscript.
+
+\subsection{Acknowledgements}
+
+The authors want to thank to the educators who participated in the survey, and also people who have distributed the survey in their mailing lists, especially Mario García Valdez, Jesús Moreno León and the late José Raúl Canay.
+We would also like to thank the anonymous reviewers that have contributed greatly to the improvement of this paper.
 

### 2022-01-25 edubots_surveys.Rnw
Fixed format problems

@@
 
-The \bf{second survey} was designed after initial results to the first survey arrived,
+The {\bf second survey} was designed after initial results to the first survey arrived,
 and pointed to necessities and experiences of teachers not being addressed by the first one; namely
@@
 
-One of the questions we made in the \bf{second survey}, related to
+One of the questions we made in the {\bf second survey}, related to
 the messaging applications used by tertiary education teachers, opens a new line

### 2022-01-25 edubots_surveys.Rnw
Finishing up typos

@@
 \cite{gachago2015crossing}; however, this last paper also reflects the need for
-learners to ``take ownership of the tool'' and the advantages of social learning
+learners to "take ownership of the tool" and the advantages of social learning
 in general. At the same time, it also mentions different challenges, among which
@@
 19\% of the chi-square test results. Also, the number of educators from
-Technology or Engineering that started using safer alternatives \footnote{\textcolor{black}{This addresses the issue of insecure/unsafe applications which do not encrypt messages or can be easily compromised exposing information}} are less than
+Technology or Engineering that started using safer alternatives \footnote{This addresses the issue of insecure/unsafe applications which do not encrypt messages or can be easily compromised exposing information} are less than
 expected (compared to the educators from other disciplines). Bear in mind that
@@
 \vspace{0.8em}
-\caption{Interaction media features valued by teachers. \textcolor{black}{Details about each of these features can be read in Appendix I (Section \ref{app:questions}, second survey)}.}
+\caption{Interaction media features valued by teachers. Details about each of these features can be read in Appendix I (Section \ref{app:questions}, second survey).}
 \label{tab:interaction}
@@
 Every cell value represents $X^{2}_{(1, N = 205)}$.
-Details about each feature can be read in Section \ref{sec:meth}.}
+Details about each feature can be read in Appendix I.}
 \label{tab:interactionfeatures}
@@
 Additionally, the question on COVID reflected the big challenge that represents
-changing habits, even in the case of a major crisis. Very few people actually
-changed, with women vs. men being an exception, as well as those teaching social
-sciences standing out among the rest. We do not have any kind of explanation for
+changing habits, even in the case of a major crisis. Very few responders actually
+changed their habits, although comparing women vs. men as well as those teaching social
+sciences show some significant difference. We do not have any kind of explanation for
 this behaviour, other than technologies are perceived, and adopted, in a
@@
 results, and that should require further study, is: Are teachers really aware
-of the possibilities of chatbots in the classroom? \textcolor{black}{The survey 
-only listed a few functionalities for the chatbots and only a few subjects selected 
+of the possibilities of chatbots in the classroom? The survey 
+only listed a few functionalities for the chatbots and just a few subjects selected 
 the option "Others". This may suggest  that most teachers did not really understand 
-at this point the actual potential of chatbots.} Another way to look about it is 
+at this point the actual potential of chatbots, since the responses listed were by no means exhaustive, and if the responders were more acquainted with the possibilities of the technology, possibly this response would have shown up many more times.
+Another way to look about it is
 that, unless you provide the specific instructions on how to use a
@@
 
-It is also likely that their opinions towards chatbots are informed by negative
+We can speculate that their opinions towards chatbots are informed by negative
 experiences with customer support chatbots, which is what most people will have
@@
 taken into account when introducing chatbot technologies in the classroom: 
-\textcolor{black}{it will have to be as simple, and as satisfactory, as possible, 
-to (possibly) change this existing perception}.
+it will have to be as simple, and as satisfactory, as possible, 
+to (possibly) change this existing perception.
 
@@
 it is interesting to observe how university teachers prefer in a higher
-proportion to use them for grades and FAQs in comparison with Vocational High
-School teachers. \textcolor{black}{
+proportion to use them for grades and FAQs in comparison with other tertiary education teachers. 
 This seems reasonable as the frequency of seeing the students
 is lower at the University so, an automatic tool for grade notification for
-continuous evaluation seems more helpful}. 
+continuous evaluation seems more helpful. 
 Furthermore, the high student/teacher
@@
 
-The results, when grouping by experience, confirm the previous observation that
+The results, when grouping by experience, confirm that
 experienced teachers are not afraid of changes and are willing to accept new
-technological challenges, at least, in the same way that younger teachers
-are. From this concrete plot it is interesting as well the fact that very few
-young/inexperience teachers are willing to use chatbots for other uses. \textcolor{black}{This
-reinforces the hypothesis thrown at the beginning of this section that younger teachers have less experience to consider new ways of using chatbots in their daily work.}
-
-As it appears in the responses presented above, teachers’ responses are
+technological challenges; at least, in the same way that younger teachers
+are. From this concrete plot it is interesting as well to observe the fact that very few
+young/inexperience teachers are willing to use chatbots for other uses. This
+reinforces the hypothesis thrown at the beginning of this section that younger
+teachers have less experience to consider new ways of using chatbots in their daily work.
+
+As it appears in the responses presented above, teachers’ responses are equally
 distributed between positive and negative in relation to the media features:
-analytics, connectivity, and hidden phone, while for the features: familiarity,
+analytics, connectivity, and hidden phone number; that is, none of them is a
+prevailing factor on choosing one technology over another. However, for the features: familiarity,
 horizontally, sustainability and officiality the majority provided a positive
@@
    is probably due to the strict European data regulations \textcolor{black}{on data protection},
-   gut also to avoid the overhead required to \textcolor{black}{sign up new students every year.
-   In general support from specific formation to access to IT help desk for specific features
+   but also to avoid the overhead required to \textcolor{black}{sign up new students every year.
+   In general support from specific formation and access to IT help desk for specific features
    enhances the possibility of adoption by the teachers or the possibility of a successful
@@
 students. \textcolor{black}{To accomplish this fruitful integration}, institutions have to ensure that
-these messaging applications not only are GDPR compliant to keep students’ data
+these messaging applications not only are GDPR (General Data Protection Regulation) compliant to keep students’ data
 secure, but also should provide IT support to all stakeholders who use the
@@
 
-\textcolor{black}{Comparing these results with those obtained in student surveys
-in \cite{MoraChatbots2021}, we have understood better} the differences between the teachers’
-perspectives and/or intentions and that of their students when using the
+Comparing these results with those obtained in student surveys
+in \cite{MoraChatbots2021}, we have understood better the differences between the teachers’
+points of view and/or intentions and that of their students when using the
 messaging applications in higher education.  Teachers tend to adopt technologies
-supported by their institutions.  This could be to ensure that their
+supported by their institutions.  The fact they do so could be caused by a desire to ensure that their
 universities can oversee their efforts in supporting their students during the
@@
 % Noorhan suggest that using some simple things could increase the perceived usefulness - JJ
-As in many other methods of technology acceptance, answers to the survey suggest
+As in many other methodologies that try to assess technology acceptance, answers to the survey suggest
 that the introduction of simple, and institution-supported, instant messaging
@@
 
-\textcolor{black}{What we are going to propose next is a possible process of
+What we are going to propose next is a possible process of
 technology introduction that is compatible with the conclusions of this study,
@@
 relationship with better learning outcomes, as well as higher teacher
-satisfaction.}
-Once that initial introduction \textcolor{black}{of institutional messaging
-automation tools} is done, teachers (and students as well) will
+satisfaction.
+Once that initial introduction of institutional messaging
+automation tools is done, teachers (and students as well) will
 probably prefer the kind of bots that alleviate bureaucratic or repetitive
 tasks, such as answering frequent questions or answers on class or assignment
-schedules \textcolor{black}{, as indicated by their answers to the respective
-questions}. These will help the introduction of more complex chatbots that will
+deadlines, as indicated by their answers to the respective
+questions. These will help the introduction of more complex chatbots that will
 affect more directly learning outcomes, such as chatbots that help students
 integrate in the class, or are able to identify (and address) learning problems
-in students or in groups of them. These as well should be accompanied by
+in students or in groups of them. These should also be accompanied by
 analytics on student interaction, as well as possibly some natural language
@@
 % Only some COVID-response relationship.
-In our survey, we could not find an answer to the right moment for doing this
-introduction of chatbot technologies. Response to questions related to change of
-behaviour during and after the pandemic do not suggest that major (or minor)
+In our survey, we could not find an answer about the right moment introducing chatbot technologies. Response to questions related to change of
+behaviour during and after the first, stay at home, stage of the pandemic do not suggest that major (or minor)
 crisis could be an opportunity to introduce new technologies, since it does not

### 2022-02-14 title-page.tex
Adds title page for new journal

% molde para cartas con membrete Dpto. y para sobres con ventana direcci¢n
\documentclass{letter}
\usepackage{graphicx}
\usepackage[spanish]{babel}      % castellano
\usepackage[latin1]{inputenc}    % tildes
\usepackage{url}

% para cartas en ingl‚s comentar la linea anterior e incluir la siguiente:
%\documentstyle[12pt]{a4letter}
% cabecera para hojas con membrete del Departamento y JJ
% Set left margin - The default is 1 inch, so the following 
% command sets a 0.5-inch left margin.
\setlength{\oddsidemargin}{0.0in}

% Set width of the text - What is left will be the right margin.
% In this case, right margin is 8.5in - 0.0in - 6.5in = 2.0in.
\setlength{\textwidth}{6.5in}

% Set top margin - The default is 1 inch, so the following 
% command sets a 0.5-inch top margin.
\setlength{\topmargin}{-1in}

% Set height of the text - What is left will be the bottom margin.
% In this case, bottom margin is 11in - 0.75in - 9.5in = 0.75in
\setlength{\textheight}{10in}

% cambiar estas definiciones para personalizar el documento
\def\yo{\sc Juan J. Merelo}
\def\email{\tt jmerelo@geneura.ugr.es}
\def\tel{34-958-243162}
\def\fax{34-958-248993}

% definiciones comunes
\def\granada{18071 Granada (Spain)}
\def\ucm{Universidad de Granada}
\def\fac{ETS Ingenierías Informática y Telecomucnicaciones}
\def\dpto{Departamento de Arquitectura y Tecnolog\'ia de Computadores}

\def\cabecera{

\begin{minipage}{2.5cm}
\centerline{  \includegraphics[width=2.5cm,height=2.5cm]{escudo.eps} }
\end{minipage}
\ \
\begin{minipage}{13cm}
 \rule{13cm}{0.6mm}
 \vspace*{0.3cm}
 {\small{\bf \dpto \hfill}} \\
 {\footnotesize{\bf \fac \hfill Fax: \fax}} \\
 {\footnotesize{\bf \ucm \hfill Tel. / Phone: \tel}} \\
 {\footnotesize{\bf \granada \hfill E-mail: \email}}\\
 \rule{13cm}{0.6mm}
\end{minipage}
}

%\input cabecera
\pagestyle{empty}

\begin{document}

\cabecera

\vspace{0.5cm}

\hspace{7cm}

\hfill Granada, \today

\vspace{0.5cm}
\ \
% **** si no se quiere recuadro en la direcci¢n, comentar la linea siguiente
%\framebox[9cm][l]
{
\begin{minipage}[t]{9cm}
To whom it may concern
% ******* Poner aqu¡ nombre y direcci¢n del destinatario
\end{minipage}
 }

\vspace{0.5cm}

% ********** comienzo del texto  *******************
Please find in this submission the manuscript for our research paper  to be
considered for publication in your esteemed journal. I have tried to address all
concerns that caused the initial manuscript to be sent back, I would ask again to
be a bit more precise if this is not accepted either. In this submission I have
eliminated all author information, including the (fake) authors that were
included in the sample file provided by the journal.

This information required in the cover letter:
\begin{itemize}
\item {\bf Title of the manuscript} {\em
  Chatbots and messaging platforms in the classroom: an analysis from the
  teacher's perspective}.
\item {Authors} Juan J. Merelo (1), Pedro A. Castillo (1)
  , Antonio
M. Mora (2) , Francisco Barranco (1) ,
Noorhan Abbas (3), Alberto Guillén (1) and Olia
Tsivitanidou (4).
\item {\bf Author Affiliationa}: Numbers refer to the digits in parentheses
  above:\begin{enumerate}
  \item Department of Computer Architecture and Technology,
  University of Granada, Spain;
\item  Departamento of Signal Theory and
  Telecommunications, University of Granada, Spain;
\item Leeds University,
  Leeds, UK,
\item  CYENS, Nicosia, Cyprus.
  \end{enumerate}
\item {\bf Corresponding author details} Corresponding authors are JJ Merelo
  (jmerelo@ugr.es) and Francisco Barranco (fbarranco@ugr.es). Please address all
  communications to us both.
\item {\bf Complete co-authors email addresses} In author order (marked with an
  asterisk, corresponding authors):\begin{itemize}
  \item Juan J. Merelo* {\tt jmerelo@ugr.es}, 
  \item Pedro A. Castillo 
  {\tt pacv@ugr.es}, 
\item Antonio
M. Mora {\tt amorag@ugr.es}, 
\item Francisco Barranco*  {\tt fbarranco@ugr.es},
\item 
Noorhan Abbas  {\tt n.h.abbas@leeds.ac.uk}, 
\item Alberto Guillén  {\tt
  aguillen@ugr.es} 
\item and Olia
  Tsivitanidou  {\tt o.tsivitanidou@cyens.org.cy}.
  \end{itemize}
\end{itemize}

\newpage

\textsc{Declarations}

\textbf{Competing interests}

The authors declare that they have no competing interests.

\textbf{Authors' contributions}

All the authors have contributed to the study presented in this manuscript.

JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.

PAC has revised the paper and researched the state of the art, as well as
contributed to the survey design.

AMM has revised the paper and researched the state of the art, as well as contributed to the survey design.

FB has made the analysis and processed data and contributed to the survey design.

NA has supervised the state of the art, and written the bulk of it, as well as contributed to discussion and conclusions.

OT has performed data analysis, and contributed to discussion and conclusions.

AG has contributed to the design of the survey, analysis, discussion and conclusions.

All authors have read and approved the final manuscript.

\textbf{Availability of data and materials}

The datasets generated and analysed during the current study are available in
the {\tt edubots-paper} repository, accessible from {\tt https://github.com/JJ/edubots-paper/tree/main/data}.

\textbf{Funding}

This work has been supported by EDUBOTS project, funded under the scheme Erasmus + KA2: Cooperation for innovation and the exchange of good practices - Knowledge Alliances (grant agreement no: 612446).

\textbf{Acknowledgements}

The authors want to thank to the educators who participated in the survey, and
also people who have distributed the survey in their mailing lists, especially
Mario García Valdez, Jesús Moreno León and José Raúl Canay.

% ********** fin del texto  *******************

\hspace*{8cm} Yours,  \\

\centerline{\includegraphics[width=2.5cm,height=2.5cm]{jj_sign.eps}}

\hspace*{8cm} Juan J. Merelo\\
\hspace*{8cm} Catedrático de Universidad (Full professor)

\end{document}

### 2022-02-15 edubots_surveys.Rnw
Finished text revision
Anonymizing again

@@
 % Remember to substitute figures/ by nothing in the generated PDF
-\author[
-  addressref={aff1},
-  corref={aff1},
-  email={jmerelo@ugr.es}
-]{\inits{JJM}\fnm{Juan J.} \snm{Merelo}}
-\author[
-  addressref={aff1},
-  email={pacv@ugr.es}
-]{\inits{PAC}\fnm{Pedro A.} \snm{Castillo}}
-\author[
-  addressref={aff2},
-  email={amorag@ugr.es}
-]{\inits{AMM}\fnm{Antonio M.} \snm{Mora}}
-\author[
-  addressref={aff1},
-  email={fbarranco@ugr.es}
-]{\inits{FB}\fnm{Francisco} \snm{Barranco}}
-\author[
-  addressref={aff3},
-  email={n.h.abbas@leeds.ac.uk}
-]{\inits{NA}\fnm{Noorhan} \snm{Abbas}}
-\author[
-  addressref={aff1},
-  email={aguillen@ugr.es}
-]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
-\author[
-  addressref={aff4},
-  email={o.tsivitanidou@cyens.org.cy}
-]{\inits{OT}\fnm{Olia} \snm{Tsivitanidou}}
-
-\address[id=aff1]{%
-  \orgdiv{Department of Computer Architecture and Technology},
-  \orgname{University of Granada},
-  \city{Granada},
-  \cny{Spain}
-}
-\address[id=aff2]{%
-  \orgdiv{Department of Signal Theory, Telematics and Communications},
-  \orgname{University of Granada},
-  \city{Granada},
-  \cny{Spain}
-}
-\address[id=aff3]{%
-  \orgdiv{School of Computing},
-  \orgname{University of Leeds},
-  \city{Leeds},
-  \cny{UK}
-}
-\address[id=aff4]{%
-  \orgname{CYENS},
-  \city{Nicosia},
-  \cny{Cyprus}
-}
+% \author[
+%   addressref={aff1},
+%   corref={aff1},
+%   email={jmerelo@ugr.es}
+% ]{\inits{JJM}\fnm{Juan J.} \snm{Merelo}}
+% \author[
+%   addressref={aff1},
+%   email={pacv@ugr.es}
+% ]{\inits{PAC}\fnm{Pedro A.} \snm{Castillo}}
+% \author[
+%   addressref={aff2},
+%   email={amorag@ugr.es}
+% ]{\inits{AMM}\fnm{Antonio M.} \snm{Mora}}
+% \author[
+%   addressref={aff1},
+%   email={fbarranco@ugr.es}
+% ]{\inits{FB}\fnm{Francisco} \snm{Barranco}}
+% \author[
+%   addressref={aff3},
+%   email={n.h.abbas@leeds.ac.uk}
+% ]{\inits{NA}\fnm{Noorhan} \snm{Abbas}}
+% \author[
+%   addressref={aff1},
+%   email={aguillen@ugr.es}
+% ]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
+% \author[
+%   addressref={aff4},
+%   email={o.tsivitanidou@cyens.org.cy}
+% ]{\inits{OT}\fnm{Olia} \snm{Tsivitanidou}}
+% 
+% \address[id=aff1]{%
+%   \orgdiv{Department of Computer Architecture and Technology},
+%   \orgname{University of Granada},
+%   \city{Granada},
+%   \cny{Spain}
+% }
+% \address[id=aff2]{%
+%   \orgdiv{Department of Signal Theory, Telematics and Communications},
+%   \orgname{University of Granada},
+%   \city{Granada},
+%   \cny{Spain}
+% }
+% \address[id=aff3]{%
+%   \orgdiv{School of Computing},
+%   \orgname{University of Leeds},
+%   \city{Leeds},
+%   \cny{UK}
+% }
+% \address[id=aff4]{%
+%   \orgname{CYENS},
+%   \city{Nicosia},
+%   \cny{Cyprus}
+% }
 
@@
 
-Along this line of research, our previous work \cite{MoraChatbots2021}
+Along this line of research, our previous work \cite{MoraChatbots2021:anon}
 aimed at analysing the expectations of students on this regard; recent papers
@@
 Comparing these results with those obtained in student surveys
-in \cite{MoraChatbots2021}, we have understood better the differences between the teachers’
+in \cite{MoraChatbots2021:anon}, we have understood better the differences between the teachers’
 points of view and/or intentions and that of their students when using the
@@
 
-The datasets generated and analysed during the current study are available in the {\tt edubots-paper} repository, accessible from https://anonymous.url
+The datasets generated and analysed during the current study are available in the {\tt anonymous} repository, accessible from https://anonymous.url
 % {\tt https://github.com/JJ/edubots-paper/tree/main/data}.
@@
 
-This work has been supported by EDUBOTS project, funded under the scheme Erasmus + KA2: Cooperation for innovation and the exchange of good practices - Knowledge Alliances (grant agreement no: 612446).
+Suppressed for double blind review
+% This work has been supported by EDUBOTS project, funded under the scheme Erasmus + KA2: Cooperation for innovation and the exchange of good practices - Knowledge Alliances (grant agreement no: 612446).
 
@@
 
-JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
-
-PAC has revised the paper and researched the state of the art, as well as contributed to the survey design.
-AMM has revised the paper and researched the state of the art, as well as contributed to the survey design.
-FB has made the analysis and processed data and contributed to the survey design.
-NA has supervised the state of the art, and written the bulk of it, as well as contributed to discussion and conclusions.
-OT has performed data analysis, and contributed to discussion and conclusions.
-AG has contributed to the design of the survey, analysis, discussion and conclusions.
+% JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
+% 
+% PAC has revised the paper and researched the state of the art, as well as contributed to the survey design.
+% AMM has revised the paper and researched the state of the art, as well as contributed to the survey design.
+% FB has made the analysis and processed data and contributed to the survey design.
+% NA has supervised the state of the art, and written the bulk of it, as well as contributed to discussion and conclusions.
+% OT has performed data analysis, and contributed to discussion and conclusions.
+% AG has contributed to the design of the survey, analysis, discussion and conclusions.
 
@@
 
-The authors want to thank to the educators who participated in the survey, and also people who have distributed the survey in their mailing lists, especially Mario García Valdez, Jesús Moreno León and the late José Raúl Canay.
+% The authors want to thank to the educators who participated in the survey, and also people who have distributed the survey in their mailing lists, especially Mario García Valdez, Jesús Moreno León and the late José Raúl Canay.
 We would also like to thank the anonymous reviewers that have contributed greatly to the improvement of this paper.
@@
 
-The surveys have the same common, initial questions for segmentation:\begin{itemize}
+The surveys have the same common initial demographic questions:\begin{itemize}
 \item Degrees or titles where the teacher was working, either university or other tertiary education.
-\item Discipline: Engineering, Social Sciences, Health and Bio, Sciences, Humanities, Other.
+\item Discipline: Engineering, Social Sciences, Health and Bio, General Sciences, Humanities, Other.
 \item Gender: Man, Woman, Rather not say.
@@
 This question was implicit in the first survey: there were two different versions of the survey.
-However, it was and explicit question in the second survey.}
+However, it was an explicit question in the second survey.}
 \end{itemize}

### 2022-02-15 edubots_surveys.Rnw
Eliminates markers

@@
 really benefited from it. This is, once again, a proof of the benefit of
-chatbots in certain settings; however, there are some \textcolor{black}{prior experiences, as well as needs} that might
+chatbots in certain settings; however, there are some prior experiences, as well as needs, that might
 prevent the successful acceptance of the technology, and these are what we are
-trying to find out in this paper, together with what kind of features would \textcolor{black}{improve
-its acceptance}.
+trying to find out in this paper, together with what kind of features would improve
+its acceptance.
 

### 2022-09-14 edubots_surveys.Rnw
Preparing adaptation
Rewrites abstract

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                     %%
-%%  LaTeX template for BioMed Central  %%
-%%     journal article submissions     %%
-%%                                     %%
-%%          <8 June 2012>              %%
-%%                                     %%
-%%                                     %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                                                 %%
-%% For instructions on how to fill out this Tex template           %%
-%% document please refer to Readme.html and the instructions for   %%
-%% authors page on the biomed central website                      %%
-%% https://www.biomedcentral.com/getpublished                      %%
-%%                                                                 %%
-%% Please do not use \input{...} to include other tex files.       %%
-%% Submit your LaTeX manuscript as one .tex document.              %%
-%%                                                                 %%
-%% All additional figures and files should be attached             %%
-%% separately and not embedded in the \TeX\ document itself.       %%
-%%                                                                 %%
-%% BioMed Central currently use the MikTex distribution of         %%
-%% TeX for Windows) of TeX and LaTeX.  This is available from      %%
-%% https://miktex.org/                                             %%
-%%                                                                 %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%% additional documentclass options:
-%  [doublespacing]
-%  [linenumbers]   - put the line numbers on margins
-
-%%% loading packages, author definitions
-
-%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
 \documentclass{bmcart}
@@
 \begin{abstract} % abstract
-Introducing new technologies such as messaging platforms, and the chatbots
-attached to them, in higher education, is rapidly growing. This introduction
-entails a careful consideration of the potential opportunities and/or challenges
-of adopting these tools. Hence, a thorough examination of the teachers’
-experiences in this discipline can shed light on the effective ways of
-enhancing students’ learning and boosting their progress. In this contribution,
-we have surveyed the opinions of tertiary education teachers based in
-Spain (mainly) and Spanish-speaking countries. The focus of these surveys is to collect
-teachers’ feedback about their opinions regarding the introduction of the messaging
-platforms and chatbots in their classes, understand their needs and to gather
-information about the various educational use cases where these tools are
+Messaging platforms are applications, generally mediated by an app, desktop program or the web, mainly used for synchronous communication among users.
+As such, they have been widely adopted officially by higher education establishments, after little or no study of their impact and perception by the teachers.
+We think that the introduction of these new tools and the opportunities and challenges they have needs to be studied carefully in order to adopt the model, as well as the tool, that is the most adequate for all parties involved.
+We already studied the perception of these tools by students, in this paper we examine the teachers’
+experiences and perceptions through a survey that we validated with peers, and what they think these tools should make or serve so that it enhances students learning and helps them achieve their learning objectives.
+The survey has been distributed among tertiary education teachers, both in universitary and other kind of tertiary establishments, based in
+Spain (mainly) and Spanish-speaking countries. We have focused on collecting
+teachers' preferences and opinions on the introduction of messaging platforms in their day-to-day work, as well as other services attached to them, such as  chatbots.
+What we intend with this survey is to understand their needs and to gather
+information about the various educational use cases where these tools could be 
 valuable. In addition, an analysis of how and when teachers’ opinions towards
-the use of these tools can vary across gender, experience, and their discipline
+the use of these tools varies across gender, experience, and their discipline
 of specialisation is presented. The key findings of this study highlight the

### 2022-09-14 response-reviewers-2.tex
Starting to write a response to the reviewers

% molde para cartas con membrete Dpto. y para sobres con ventana direcci¢n
\documentclass{letter}
\usepackage{graphicx}
\usepackage[spanish]{babel}      % castellano
\usepackage[latin1]{inputenc}    % tildes
\usepackage{url}

% para cartas en ingls comentar la linea anterior e incluir la siguiente:
%\documentstyle[12pt]{a4letter}
% cabecera para hojas con membrete del Departamento y JJ
% Set left margin - The default is 1 inch, so the following 
% command sets a 0.5-inch left margin.
\setlength{\oddsidemargin}{0.0in}

% Set width of the text - What is left will be the right margin.
% In this case, right margin is 8.5in - 0.0in - 6.5in = 2.0in.
\setlength{\textwidth}{6.5in}

% Set top margin - The default is 1 inch, so the following 
% command sets a 0.5-inch top margin.
\setlength{\topmargin}{-1in}

% Set height of the text - What is left will be the bottom margin.
% In this case, bottom margin is 11in - 0.75in - 9.5in = 0.75in
\setlength{\textheight}{10in}

% cambiar estas definiciones para personalizar el documento
\def\yo{\sc Juan J. Merelo}
\def\email{\tt jmerelo@geneura.ugr.es}
\def\tel{34-958-243162}
\def\fax{34-958-248993}

% definiciones comunes
\def\granada{18071 Granada (Spain)}
\def\ucm{Universidad de Granada}
\def\fac{ETS Ingenierías Informática y Telecomucnicaciones}
\def\dpto{Departamento de Arquitectura y Tecnolog\'ia de Computadores}

\def\cabecera{

\begin{minipage}{2.5cm}
\centerline{  \includegraphics[width=2.5cm,height=2.5cm]{escudo.eps} }
\end{minipage}
\ \
\begin{minipage}{13cm}
 \rule{13cm}{0.6mm}
 \vspace*{0.3cm}
 {\small{\bf \dpto \hfill}} \\
 {\footnotesize{\bf \fac \hfill Fax: \fax}} \\
 {\footnotesize{\bf \ucm \hfill Tel. / Phone: \tel}} \\
 {\footnotesize{\bf \granada \hfill E-mail: \email}}\\
 \rule{13cm}{0.6mm}
\end{minipage}
}

%\input cabecera
\pagestyle{empty}

\begin{document}

\cabecera

\vspace{0.5cm}

\hspace{7cm}

\hfill Granada, \today

\vspace{0.5cm}
\ \
% **** si no se quiere recuadro en la direcci¢n, comentar la linea siguiente
%\framebox[9cm][l]
{
\begin{minipage}[t]{9cm}
To whom it may concern
% ******* Poner aqu¡ nombre y direcci¢n del destinatario
\end{minipage}
 }

\vspace{0.5cm}

% ********** comienzo del texto  *******************

{\bf Response to reviewers' comments}

We are very grateful to the reviewers for their kind comments. We have rewritten
the paper quite extensively, incorporating requested changes, but also
attempting to give another angle that makes this paper apart from what was
already published in this paper

Merelo, J.J. et al. (2022). Exploring the Role of Chatbots and Messaging
Applications in Higher Education: A Teacher’s Perspective. In: Zaphiris, P.,
Ioannou, A. (eds) Learning and Collaboration Technologies. Novel Technological
Environments. HCII 2022. Lecture Notes in Computer Science, vol 13329. Springer,
Cham. https://doi.org/10.1007/978-3-031-05675-8_16

This explains that, in some cases, conclusions have been extended or
reinterpreted over the ones published in that paper. Additionally, we validated
the survey, as was also requested by the reviewers.

Next we will address the concerns of the reviewers individually.

% ********** fin del texto  *******************

\hspace*{8cm} Yours,  \\

\centerline{\includegraphics[width=2.5cm,height=2.5cm]{jj_sign.eps}}

\hspace*{8cm} Juan J. Merelo\\
\hspace*{8cm} Catedrático de Universidad (Full professor)

\end{document}

### 2022-09-24 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Starting to rewrite Introduction

@@
 
-The introduction of new technologies in the classroom, \textcolor{black}{to be successful, involves extra
-teacher training, devising methods for enhancing student engagement with the new
-technology, and indeed acquiring new skills by students and teachers alike}.
-Some technologies are readily adopted, but others require longer time for
-full adoption. In most cases, the magnitude of the uptake of the new technology
-impinges on the collaboration of all the parties using it. \textcolor{black}{Hence, examining the
-users’ opinions is an important first step in boosting this collaboration
-and reaping the benefits of the technology}.  Recently, a surge in the use of
-synchronous instant messaging tools in higher education such as WhatsApp,
+\textcolor{blue}{New technologies are being introduced and widely adopted into the classroom in the last years. However, in order to be successful, their application 
+will require (many) extra work and training for the teacher, as well as for the students. Thus, both of them will acquire new skills and, potentially, pupils will 
+get a higher engagement to the subject, which is usually the main objective. Even if several technologies are already in use inside the classroom, there is still room for adopting others.
+Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Given this, 
+asking and analysing user's opinions with regard to this scenario will help reaping the expected benefits of the technology}.
+
+Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp,
 Telegram and Facebook Messenger took place. Some messaging applications have

### 2022-09-24 edubots_surveys.Rnw
Update edubots_surveys.Rnw

@@
 
-Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp,
-Telegram and Facebook Messenger took place. Some messaging applications have
-built-in chatbots to support a synchronous conversation between the different
-parties \cite{differ.chat}, while other chatbots are developed as standalone
-systems and can possibly be attached to a messaging application using an API
-(Application Program Interface).
-
-A \textit{chatbot} is a program, sometimes developed using Artificial
-Intelligence techniques, able to communicate in a similar way as humans do
-\cite{Gong2008}, using, in some cases, natural language. Indeed, most of these
-applications would be, apparently, close to passing a classic Turing test
-\cite{moor2003turing}, since they are able to answer almost any question
-fluently, and even pose own questions in their conversations. The recent
-advancement in this discipline has played an important role in many fields
-especially in education and online tutoring
-\cite{clarizia2018,Smutny2020}. These automatic systems facilitate the delivery
-of personalized learning by adapting to students’ pace of learning and providing
-customized online tutoring outside the classroom. Thus, chatbots can
-significantly contribute to providing interactive learning experiences as well
-as improving individual attention \cite{agarwal2020}.  In this sense, chatbot
-technology offers a great opportunity for the improvement of tutoring systems
-\cite{Daniel2016,agarwal2020}, as not all students are comfortable with
-face-to-face tutoring with the instructor. In fact, in many cases, some students
-experience stress because of their need to ask a question in front of the entire
-class. This is why many students resort to silence in the classroom and tend to
+\textcolor{blue}{In the last years, messaging applications such as WhatsApp or Telegram are being used in teaching scenarios mainly at secondary and higher education.
+In addition to their main use, some of these tools offer the possibility of interact with \textit{chatbots} (or just bots), even supporting synchronous conversation between the different
+parties \cite{differ.chat}. There is also possible to create a standalone chatbot application and attach it to a messaging tool through an API (Application Program Interface).}
+
+\textcolor{blue}{\textit{chatbots} are autonomous agents able to communicate and interact with humans (or other chatbots) in a huma-like way \cite{Gong2008}, answering question and even posing their own ones to the user.
+Thus, we can say that they are close to passing a Turing Test \cite{moor2003turing}. They are implemented by means of different Artificial Intelligence techniques, such as natural language processing.
+Inside the plethora of possible applications of chatbots, education is one of the most prolific nowadays \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called 
+\textit{personalized learning}, i.e.
+they adapt themselves to students’ pace of learning and provide online tutoring outside the classroom, which have been proved to be very effective increasing their
+engagement and participation in the subjects \cite{agarwal2020}.
+Moreover chatbots' tutoring possibilities aid to reduce the stress of students \cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their teacher,
+or asking questions in front of the class. 
+}
+
+This is why many students resort to silence in the classroom and tend to
 contact their teachers later via email.  Consequently, this can lead to not only

### 2022-09-24 response-reviewers-2.tex

@@
 
+%%%% Rev 3
+
+{\it
+
+{\bf Reviewer \#3}: Paper Summary:
+This study surveyed teachers' feedback about their opinions regarding introducing the messaging platforms and chatbots in their classes, understand their needs, and gathering information about the various educational use cases where these tools are valuable.
+There are some suggestions below to improve the research work.
+1.
+Does the article address a topic of current concern about the aims of the journal and to what you perceive to be the current state of ICT concerning education?
+The article addresses issues bothering the introduction of messaging platforms and chatbots to augment teaching and learning, which I consider important concerning the current state of ICT education.}
+
+% -> answer 1
+
+The authors thank the comment for noticing the relevance of the topic and how it suits the journal scope.
+
+{\it 2.
+Does the abstract give a clear account of the scope of the paper?
+The abstract gave an overview of the paper.
+However, the key findings of the paper were not reported in the abstract.
+I suggest the authors summarize the study's findings and report them briefly in the abstract.}
+
+% -> answer 2
+
+The abstract as well as other sections in the paper have been rewritten. The abstract now summarizes the study's findings and reports them briefly.
+
+% -> answer 3
+
+{\it 3.      Do the keywords adequately reflect the paper? The authors should consider replacing Tutorship with teachers.}
+
+After consideration, the authors agree with the comment and we have replaced teachers for Tutorship in the keywords.
+
+% -> answer 4
+
+{\it 4.
+If the article is concerned with research activity, has a sound methodology been utilized and described?
+A sound methodology was utilized and described.
+However, it was observed that prior studies have not previously validated the measurement instrument used in collecting data.
+Thus, the authors need to conduct reliability and validity tests for their proposed measurement instrument used in collecting data.}
+
+TO DO
+
+% -> answer 5,6,7,8
+
+{\it 5.      Does the article distinguish clearly between opinion and empirical evidence? Yes
+6.      Does the article contribute to a critical understanding of the issues? Yes
+7.      Does the article alert readers to significant new developments in the subject area? Yes
+8.      Does the article take into account relevant contemporary literature in the area? Yes.}
+
+The authors want to thank the reviewer for evaluating positively those aspect of the paper.
+
+% -> answer 9
+
+9.
+Does the article clearly reference citations and quotations using the APA 7th edition?
+Partly, some of the references do not follow APA 7th edition.
+For example, the following references don't follow APA 7th edition referencing style
+     a.   O'Boyle, 2014. O'Boyle, N. (2014). Front row friendships: Relational dialectics and identity negotiations by mature students at univerty. Communication Education, 63(3):169-191
+     b.
+Panah and Babar, 2020.
+Panah, E.
+and Babar, M.
+Y.
+(2020).
+A survey of WhatsApp as a tool for instructor-learner dialogue, learner-content dialogue, and learner-learner dialogue.
+International Journal of Educational and Pedagogical
+ Sciences, 14(12):1198 - 1205.
+     c.
+Perez et al., 2020.
+Perez, J.
+Q., Daradoumis, T., and Puig, J.
+M.
+M.
+(2020).
+Rediscovering the use of chatbots in education: A systematic literature review.
+Computer Applications in Engineering Education, 28(6):1549- 1565.
+     d.
+Ranoliya et al., 2017.
+Ranoliya, B.
+R., Raghuwanshi, N., and Singh, S.
+(2017).
+Chatbot for university related faqs.
+In 2017 International Conference on Advances in Computing, Communications and Informatics (ICACCI), pages 1525-1530.
+IEEE.
+     e.
+Roblyer et al., 2010.
+Roblyer, M., McDaniel, M., Webb, M., Herman, J., and Witty, J.
+V.
+(2010).
+Findings on facebook in higher education: A comparison of college faculty and student uses and perceptions of social networking sites.
+The Internet and Higher Education, 13(3):134 - 140.
+
+% https://www.scribbr.com/apa-style/apa-seventh-edition-changes/
+
+% -> answer 10      
+{\it 10.
+Is the article written in a clear and intelligible style to a reasonably well-informed international professional readership?
+Yes.
+However, there are a few grammatical errors.
+I suggest the authors proofread the manuscript to correct them.}
+
+The authors apologise for the grammatical errors and have strived to fix them and to avoid them in the new paragraphs.
+
+% -> answer 11
+{\it 11.     Other few comments the authors should consider:
+   a.   Reorganize the conclusion section to highlight the main aim of the research work briefly, key findings and the significance of the work, and future research work.
+   b.
+Some of the paragraphs in the conclusion section can be moved to Discussion.
+The Discussion section can be captioned as Discussion and Implications to cater for some of the paragraphs that will be moved to this section.
+For example, paragraphs on Page 23, Line 16, "In our survey…" and Page 23, Line 37, "One of the questions we made in the second survey…" should be moved to the Discussion and Implication section.}
+
+To address these final comments:
+    a. as cited before, the abstrac and other sections have been rewritten highlighting the key findings and the significance of the work.
+
+    b. TO DO
+
+%%%%%% Rev 4
+
+{\bf Reviewer \#4}: {\it First of all, this paper seems to be the main topic of 'Analysis from the teacher's perspective of chatbots and messaging platforms in class'.
+It seems that simple survey results were analyzed and grouped.
+It seems like a lot of effort was put into it, but I doubt whether it has any academic significance.
+Why did you choose 4 questions? Is it appropriate for a chatbot and messaging platform if I just ask and group this? I am not sure.
+Looking at the research results and conclusions, there are some contents that are difficult to see as valid because the evidence for the researcher's conclusions is so abrupt and abstract.}
+
 \end{document}

### 2022-09-24 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Introduction completely rewritten

@@
 
-\textcolor{blue}{\textit{chatbots} are autonomous agents able to communicate and interact with humans (or other chatbots) in a huma-like way \cite{Gong2008}, answering question and even posing their own ones to the user.
+\textcolor{blue}{\textit{Chatbots} are autonomous agents able to communicate and interact with humans (or other chatbots) in a huma-like way \cite{Gong2008}, answering question and even posing their own ones to the user.
 Thus, we can say that they are close to passing a Turing Test \cite{moor2003turing}. They are implemented by means of different Artificial Intelligence techniques, such as natural language processing.
@@
 or asking questions in front of the class.
+This situation normally conducts to a silence of the student and a later contact with the teacher by e-mail, which, in turn, will mean a workload for the teacher, that could be very
+significant given the existing disproportion between number of students per each teacher.  
 }
-
-This is why many students resort to silence in the classroom and tend to
-contact their teachers later via email.  Consequently, this can lead to not only
-a delay in obtaining answers to their questions but can also cause a significant
-increase in their teachers’ workload, especially when factoring in the
-disproportion between the class size and the number of teachers. Hence, the
-chatbot technology has a potential to mitigate this problem by providing answers
-to students’ questions and facilitating a dynamic and autonomous learning
-experience \cite{Griol2014,kim2020}. In addition, using an automated system such
-as a chatbot, can draw teachers’ attention to topics that students struggle to
-comprehend or need further assistance in understanding.
+Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning
+experience \cite{Griol2014,kim2020}.
+In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding.
 
 Given the potential benefits that chatbots could bring to the classroom, the
-focus of the
-EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
-the sponsor of this study, is to
-\textcolor{black}{explore best practices and innovative use of chatbots, and to create 
-a learning community of educators in higher education institutions.
-The majority of studies conducted so far have studied how these 
-messaging applications and/or chatbots are used to deliver personalised
-learning in classrooms that occurs anytime anywhere,
-promote collaborative learning experiences, group discussions \cite{panah2020study}
-and boost students' sense of belonging to their institutions
-\cite{abbas2021onlinechat}. Hence, due to the paucity of research
-that explores the use of these technologies from the teachers' perspectives,
-this paper aims to investigate their opinions/needs and the
-challenges/opportunities of adopting these technologies in classrooms
-to paint a better picture of how they can positively contribute to enhancing
-the learning process in higher education institutions.}
-
-\textcolor{black}{In this study, data collection involved two phases:}
+focus of the EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
+the main sponsor of this study, is to explore best practices and innovative use of chatbots, 
+and to create a learning community of educators in higher education institutions.
+\textcolor{blue}{Researchers and teachers participating in this project have developed several studies. Most of these works have been focused on how the 
+messaging applications and/or chatbots are normally applied to deliver personalised learning in classrooms that occurs anytime anywhere,
+promote collaborative learning experiences, group discussions \cite{panah2020study} and boost students' sense of belonging to their institutions
+\cite{abbas2021onlinechat}.}
+\textcolor{blue}{The majority of these studies were conducted focusing on the teachers' perspectives, so this paper aims to provide more conclusions regarding 
+their opinions and needs, as well as the existing challenges or opportunities that arise when adopting these technologies in classrooms. This will lead to clarify
+how they can positively contribute to enhancing the learning process in higher education institutions.}
+
+In this study, data collection involved two phases:
  \begin{itemize}
@@
 \begin{itemize}
-\item RQ1 - Are teachers already using messaging apps in their classes?
-\item RQ2 - Which chatbots' features would teachers find useful in their
-  classes?
+\item RQ1 - Do teachers use now or want to use messaging apps in their classes?
+\item RQ2 - Which chatbots' features would teachers find useful for this purpose?
 \item RQ3 - Which kind of interaction do teachers prefer with their students?
@@
 We will try to answer these questions through the analysis of questions and
-answers in the two surveys. Eventually, what we want to obtain is a series of
+answers in the two aforementioned surveys. Eventually, what we want to obtain is a series of
 recommendations to make a successful deployment of chatbot technologies (and, in

### 2022-09-27 response-reviewers-2.tex
new subsection 3.1 for survey validation and new answers to reviewers

@@
 
-TO DO
+The authors thank the reviewer for pointing out that flaw which was addressed, improving the quality of the paper.
+
+A new subsection whithin the methodology (Section 3.1 Survery validation) deals with the procedure to validate the tests by using a board of experts for the questionaire.
 
@@
 
+The authors thank the reviewer for provinding useful feedback to improve the quality of the paper.
+
+Regarding the first issue (the lack of academic significance), we want to stress the importance of the topic of how AI tools are going to modify our lifestyle in the comming years.
+This study shares experiences from the academic and educational point of view and analyses the results obtained.
+Nonetheless, the Introduction (as well as other sections) has been rewritten with the hope of addressing the academic significance in a clearer way.
+
+Regarding the validation of the methodology, there is a new subsection that presents the validation procedure by means of an expert board which agrees with the procedure and contents presented.
+
+For the final comment, we have rewritten the conclusions and abstract to improve the way the content is explained.
+
 \end{document}

### 2022-09-27 edubots_surveys.Rnw
new subsection 3.1 for survey validation and new answers to reviewers

@@
 
+\subsection{Survey validation}
+\textcolor{blue}{
+
+To avoid any bias and to be sure about the quality of the questionnaire, a panel board was consulted.
+There were three items for each of the items of the questionnaire which were: Clarity, Importance, Adequateness.
+Clarity was measured as an answer to the question: Is the item well presented and without ambiguity?
+\footnote{Original text: ¿El ítem está bien redactado y sin ambigüedad?} with two choices: Yes or No.
+Both Importance and Adequateness were measured in a Likert scale from 1 to 4 (1 low, 4 high).
+
+The panel board was composed by 7 volunteer experts that have wide experience as educators and researchers. The results obtained are summarized in Table \ref{tab:validation}.
+
+As validation shows, all expert agree without any doubt about the clarity of each question.
+Furthermore, there is a large consensus regarding the Importance and Adequateness of all the eight questions in the questionnaire.
+
+\begin{table}
+\begin{tabular}{|c|ccc|}
+    \hline
+    Questions & Clarity (Yes/No) & Avg. Importance & Avg. Adequateness \\
+    \hline
+    Q1 &  Yes (100\%)  &  3,571 (0,53) & 3,571 (0,53) \\
+    Q2 &  Yes (100\%)  &  3,714 (0,49) & 3,571 (0,53) \\
+    Q3 &  Yes (100\%)  &  3,857 (0,38) & 3,857 (0,38) \\
+    Q4 &  Yes (100\%)  &  3,571 (0,79) & 3,857 (0,38) \\
+    Q5 &  Yes (100\%)  &  3,714 (0,49) & 3,714 (0,49) \\
+    Q6 &  Yes (100\%)  &  3,714 (0,49) & 3,857 (0,38) \\
+    Q7 &  Yes (100\%)  &  3,714 (0,49) & 3,714 (0,49) \\
+    Q8 &  Yes (100\%)  &  4 (0) & 4,000 (0) \\
+    \hline
+\end{tabular}
+\caption{Validation results from the panel board (7 experts) for each question in the research questionnaire.
+The range of values for Importance and Adequateness is from 1 to 4 (higher is better).}\label{tab:validation}
+\end{table}
+
+}
+
 Next, we show the results and analyse them.

### 2022-09-30 edubots_surveys.Rnw
Fix error

@@
 \subsection{Survey validation}
-\textcolor{blue}{
 
 To avoid any bias and to be sure about the quality of the questionnaire, a panel board was consulted.
-There were three items for each of the items of the questionnaire which were: Clarity, Importance, Adequateness.
+There were three questions for each of the items of the questionnaire which were: Clarity, Importance, Adequateness.
 Clarity was measured as an answer to the question: Is the item well presented and without ambiguity?
@@
 Telegram). With respect to specific disciplines, Engineering and Technology
-teachers are more active in their use, \textcolor{black}{but the number of teachers from Humanities 
-who answered they used these apps in their classes is also remarkable}
+teachers are more active in their use, but the number of teachers from Humanities 
+who answered they used these apps in their classes is also remarkable
 (around 60\% use the apps provided by their institutions).
@@
 \end{center}
-    \caption{Use of \textcolor{black}{messaging platforms either external or} provided by the teachers' academic institutions in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}
+    \caption{Use of messaging platforms either external or provided by the teachers' academic institutions in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}
     \label{figure:provided*chatbots_use}

### 2022-09-30 response-reviewers-2.tex
Change back coding system
Arregla codificación

@@
 attempting to give another angle that makes this paper apart from what was
-already published in this paper
+already published in this other one
 
 Merelo, J.J. et al. (2022). Exploring the Role of Chatbots and Messaging
-Applications in Higher Education: A Teacher’s Perspective. In: Zaphiris, P.,
+Applications in Higher Education: A Teacher's Perspective. In: Zaphiris, P.,
 Ioannou, A. (eds) Learning and Collaboration Technologies. Novel Technological
 Environments. HCII 2022. Lecture Notes in Computer Science, vol 13329. Springer,
-Cham. https://doi.org/10.1007/978-3-031-05675-8_16
+Cham. https://doi.org/10.1007/978-3-031-05675-8\_16
 
@@
 The Discussion section can be captioned as Discussion and Implications to cater for some of the paragraphs that will be moved to this section.
-For example, paragraphs on Page 23, Line 16, "In our survey…" and Page 23, Line 37, "One of the questions we made in the second survey…" should be moved to the Discussion and Implication section.}
+For example, paragraphs on Page 23, Line 16, "In our survey..." and Page 23, Line 37, "One of the questions we made in the second survey..." should be moved to the Discussion and Implication section.}
 
 To address these final comments:
-    a. as cited before, the abstrac and other sections have been rewritten highlighting the key findings and the significance of the work.
+    a. as cited before, the abstrac and other sections have been rewritten
+    highlighting the key findings and the significance of this work as compared
+    with the others.
 

### 2022-09-30 response-reviewers-2.tex
Revisado lo del APA 7

@@
 
-% https://www.scribbr.com/apa-style/apa-seventh-edition-changes/
+{\it We have used, as instructed by the template, the {\tt apalike} style in our
+  LaTeX source, as well as used standard BiBTeX files downloaded from the
+  publication itself. No tweaking has been mede on these, so I don't see what we
+  can do about it, other than report a bug in the style to the authors.
+
+We have been checking out the issue, and apparently the problem is that the 7th
+edition is not well covered by the current LaTeX styles, which are stuck at the
+6th edition. A pretty extensive change in tooling is needed, unfortunately,
+including the style of bibliography citation and the tool used for doing
+that. So while there's a path for doing this, we do not think it is something we
+should devote our time in the current version of the paper, if the reviewer does
+not mind. We will certainly do so as required by publication when (or if) this
+paper is finally accepted}
 

### 2022-09-30 response-reviewers-2.tex
Addressing last question

@@
 To address these final comments:
-    a. as cited before, the abstrac and other sections have been rewritten
+    a. as cited before, the abstract and other sections have been rewritten
     highlighting the key findings and the significance of this work as compared
@@
 
-    b. TO DO
+    b. We have changed the title and moved the indicated paragraph. Thanks for
+    the suggestion.
 

### 2022-09-30 edubots_surveys.Rnw
Addressing last question

@@
 
-\textcolor{black}{A total of 205 teachers responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%).
+A total of 205 teachers responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%).
 From those, 124 were male (60.5\%), 65 female (31.7\%) and 16 teachers preferred not to indicate their gender (7.8\%).
 In terms of age, the majority of the participants (n=70) was again, as in the first survey, 45-55 years old (34.1\%), while 67 teachers were 35-45 years old (32.7\%), 42 were 25-35 (20.5\%) and 26 teachers were older than 55 (12.7\%).
-In terms of teaching experience, 59 teachers had a teaching experience of 16-25 years (28.8\%), 51 teachers had 6-15 years (24.9\%) and 0-5 years of experience (24.9\%), and 44 teachers more than 25 years of teaching experience (21.5\%).}
+In terms of teaching experience, 59 teachers had a teaching experience of 16-25 years (28.8\%), 51 teachers had 6-15 years (24.9\%) and 0-5 years of experience (24.9\%), and 44 teachers more than 25 years of teaching experience (21.5\%).
 
@@
 \end{table}
-
-}
 
@@
 % ********************** Discussion section *******************
-\section{Discussion}
+\section{Discussion and implications}
 
@@
 
+% Only some COVID-response relationship.
+In our survey, we could not find an answer about the right moment for introducing chatbot technologies. Response to questions related to change of
+behaviour during and after the first stay at home, stage of the pandemic do not suggest that a major (or minor)
+crisis could be an opportunity to introduce new technologies, since it does not
+bring major changes in attitude (as a minor "crisis" we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in
+  Spain, every 10 years or so.}), or simply introduction of new degrees. Although
+changes driven by external forces do offer the chance of piloting new technologies, they do not
+seem to bring internal changes in attitudes in the teaching staff (which, after all, is
+bound to be the same). In absence of a clear answer in this direction, the right
+moment to introduce new technologies is always when the IT and managing staff is
+ready to support it (since, as we have seen before, "official" support is one of
+the factors that is most valued by teachers).
+
 % ********************** CONCLUSIONS ****************************
@@
 
-% Only some COVID-response relationship.
-In our survey, we could not find an answer about the right moment introducing chatbot technologies. Response to questions related to change of
-behaviour during and after the first, stay at home, stage of the pandemic do not suggest that major (or minor)
-crisis could be an opportunity to introduce new technologies, since it does not
-bring major changes in attitude. A minor crisis would be, for instance, rollout
-of a new higher education law\footnote{We seem to have one of these, at least in
-  Spain, every 10 years or so.}, or introduction of new degrees. Although
-external changes do offer the chance of piloting new technologies, they do not
-seem to bring changes in attitudes in the teaching staff (which, after all, is
-bound to be the same). In absence of a clear answer in this direction, the right
-moment to introduce new technologies is always when the IT and managing staff is
-ready to support it (since, as we have seen before, "official" support is one of
-the factors that is most valued by teachers).
-
 At any rate, the general feeling that transpires from the survey is that it is

### 2022-09-30 edubots_surveys.Rnw
Spell check, including change to American spelling

@@
 %%It must be present to enable the BMC Submission system to
-%%recognise this template!!
+%%recognize this template!!
 
@@
 the use of these tools varies across gender, experience, and their discipline
-of specialisation is presented. The key findings of this study highlight the
+of specialization is presented. The key findings of this study highlight the
 factors that can contribute to the advancement of the adoption of messaging
@@
 Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Given this, 
-asking and analysing user's opinions with regard to this scenario will help reaping the expected benefits of the technology}.
+asking and analyzing user's opinions with regard to this scenario will help reaping the expected benefits of the technology}.
 
@@
 
-\textcolor{blue}{\textit{Chatbots} are autonomous agents able to communicate and interact with humans (or other chatbots) in a huma-like way \cite{Gong2008}, answering question and even posing their own ones to the user.
+\textcolor{blue}{\textit{Chatbots} are autonomous agents able to communicate and interact with humans (or other chatbots) in a human-like way \cite{Gong2008}, answering question and even posing their own ones to the user.
 Thus, we can say that they are close to passing a Turing Test \cite{moor2003turing}. They are implemented by means of different Artificial Intelligence techniques, such as natural language processing.
@@
 \textcolor{blue}{Researchers and teachers participating in this project have developed several studies. Most of these works have been focused on how the 
-messaging applications and/or chatbots are normally applied to deliver personalised learning in classrooms that occurs anytime anywhere,
+messaging applications and/or chatbots are normally applied to deliver personalized learning in classrooms that occurs anytime anywhere,
 promote collaborative learning experiences, group discussions \cite{panah2020study} and boost students' sense of belonging to their institutions
@@
 entailed the creation of a second survey to which 200 teachers' responses were
-collected\textcolor{black}{, with the methodology and collective characteristics that will be explained below. The questions of the second survey focussed on discussing teachers'
+collected\textcolor{black}{, with the methodology and collective characteristics that will be explained below. The questions of the second survey focused on discussing teachers'
 needs, opinions and preferences of the development of future technology-enhanced
@@
 (i.e. video, audio, text) \cite{tang2017mobile}. Using these tools in
-higher education can facilitate the delivery of personalised learning
+higher education can facilitate the delivery of personalized learning
 that occurs anytime anywhere, promote collaborative learning
@@
 language, subject matter and platform\textcolor{black}{, whereas the study undertaken by Pérez and collaborators
-\cite{perez2020rediscovering} aimed to categorise educational chatbots, according
+\cite{perez2020rediscovering} aimed to categorize educational chatbots, according
 to their, purpose into service-oriented and teaching-oriented}. The first category
@@
 \cite{meetholly} and Dina \cite{santoso2018dinus}; both chatbots respond to
-students' questions about enrolment and registration. Ask L. U.
+students' questions about enrollment and registration. Ask L. U.
 \cite{LancasterUniversity_2019} answers students' frequently asked questions
@@
 On the other hand, teaching-oriented chatbots are more sophisticated, as they
-set personalised learning outcomes and monitor learning progress. For instance,
+set personalized learning outcomes and monitor learning progress. For instance,
 \cite{fernoagua2018intelligent} reported on ``eduAssistant'', a virtual teaching
@@
 acts as an automatic agent in teacher-content-student, facilitating real-time
-feedback loops and providing a personalised learning experience relevant to the
+feedback loops and providing a personalized learning experience relevant to the
 students' acquired skills and knowledge. Using this chatbot, educators can
@@
 forum posts of four instances of a Java programming course.  The study outlined
-several design considerations; among them, the authors emphasised the importance
+several design considerations; among them, the authors emphasized the importance
 of developing chatbots in platforms that students and educators are familiar
@@
 \cite{hobert2019you} and \cite{fernoagua2018intelligent} studies. In addition, \cite{sjostrom2018designing} argued that a
-conceptualisation of learners' questions could aid designers in integrating the
+conceptualization of learners' questions could aid designers in integrating the
 appropriate types of questions that the chatbots should support for different
@@
 Along this line of research, our previous work \cite{MoraChatbots2021:anon}
-aimed at analysing the expectations of students on this regard; recent papers
+aimed at analyzing the expectations of students on this regard; recent papers
 have also analysed how the use of chatbots affected the learning outcomes of
@@
 i.e. educators. \textcolor{black}{How they accepted chatbots} has been studied very recently by Chocarro et
-al. \cite{doi:10.1080/03055698.2020.1850426}, who, by analysing surveys, created
+al. \cite{doi:10.1080/03055698.2020.1850426}, who, by analyzing surveys, created
 a {\em technology acceptance model} that proposed a series of features that
@@
 We will try to find the answers to the four research questions next, by
-analysing the response to the different survey questions.
+analyzing the response to the different survey questions.
 
@@
 
-The most favourable use case for chatbots in
+The most favorable use case for chatbots in
 Higher Education and vocational training is their use for the facilitation of an
@@
 \textcolor{black}{As it can be seen in the table, the bulk of responders express their wish to use a sustainable and official application, i.e.
-both being approved or provided by the University (or the educational centre), and also maintained by the technical staff of the centre instead of giving this responsability/task to the teacher.
+both being approved or provided by the University (or the educational center), and also maintained by the technical staff of the center instead of giving this responsibility/task to the teacher.
 In addition, it is very important for the teachers that the used tools that all the members of the class communicate, including themselves; as well as being already known or used in everyday tasks, e.g.
@@
 sciences show some significant difference. We do not have any kind of explanation for
-this behaviour, other than technologies are perceived, and adopted, in a
+this behavior, other than technologies are perceived, and adopted, in a
 different way depending on background and, apparently, gender.
@@
 In our survey, we could not find an answer about the right moment for introducing chatbot technologies. Response to questions related to change of
-behaviour during and after the first stay at home, stage of the pandemic do not suggest that a major (or minor)
+behavior during and after the first stay at home, stage of the pandemic do not suggest that a major (or minor)
 crisis could be an opportunity to introduce new technologies, since it does not
@@
 as response to new material, assignment, exams or external events might help
-will help any student-centred teaching strategy, which will help students (and
+will help any student-centered teaching strategy, which will help students (and
 teachers) reach their learning objectives. This line of work, however, will be
@@
 
-The datasets generated and analysed during the current study are available in the {\tt anonymous} repository, accessible from https://anonymous.url
+The datasets generated and analysed during the current study are available in the {\tt anonymous} repository, accessible from https://anonymous.URL
 % {\tt https://github.com/JJ/edubots-paper/tree/main/data}.
@@
 % Antonio - I have included a reference name to each one of these variables, which are the names used on Tables 8 and 9.
-Thus it will be easy to recognise every variable, and then, we could refer to them in those tables.
+Thus it will be easy to recognize every variable, and then, we could refer to them in those tables.
 
@@
 \item Non-hierarchical tools that allowed teacher-to-student and student-to-student communication. [\texttt{Horizontally}]
-\item Connectivity to other tools, for instance common login. [\texttt{Connectivity}]
+\item Connectivity to other tools, for instance common log in. [\texttt{Connectivity}]
 \item Possibility for teachers to develop/add their own functionalities (e.g. automatic correction tools). [\texttt{Pluggability}]

### 2022-09-30 response-reviewers-2.tex
Minor format changes

@@
 This explains that, in some cases, conclusions have been extended or
-reinterpreted over the ones published in that paper. Additionally, we validated
+reinterpreted over the ones published in that paper. Some of these extensive
+changes have been noted in blue for their easy identification.
+Additionally, we validated
 the survey, as was also requested by the reviewers.
@@
 
-The authors thank the reviewer for provinding useful feedback to improve the quality of the paper.
+The authors thank the reviewer for provinding useful feedback that has allowed
+us to improve the quality of the paper.
 
-Regarding the first issue (the lack of academic significance), we want to stress the importance of the topic of how AI tools are going to modify our lifestyle in the comming years.
-This study shares experiences from the academic and educational point of view and analyses the results obtained.
-Nonetheless, the Introduction (as well as other sections) has been rewritten with the hope of addressing the academic significance in a clearer way.
+Regarding the first issue (the lack of academic significance), we would like to
+stress the importance of the topic of artificial intelligence tools bringing
+changes in our lifestyle in the comming years. This study shares experiences
+from the academic and educational point of view and analyses the results
+obtained. Nonetheless, the Introduction (as well as other sections) has been
+rewritten with the hope of addressing the academic significance in a clearer
+way.
 
-Regarding the validation of the methodology, there is a new subsection that presents the validation procedure by means of an expert board which agrees with the procedure and contents presented.
+Regarding the validation of the methodology, there is a new subsection that
+presents the validation procedure by means of an expert board which agrees with,
+in general, agrees with the questions and answers we used in the survey.
 
-For the final comment, we have rewritten the conclusions and abstract to improve the way the content is explained.
+For the final comment, we have rewritten the conclusions and abstract to improve
+the way the content is explained.
 

### 2022-09-30 response-reviewers-2.tex
Only the questions are in italics

@@
 
-9.
+{\it 9.
 Does the article clearly reference citations and quotations using the APA 7th edition?
@@
 Findings on facebook in higher education: A comparison of college faculty and student uses and perceptions of social networking sites.
-The Internet and Higher Education, 13(3):134 - 140.
+The Internet and Higher Education, 13(3):134 - 140.}
 
-{\it We have used, as instructed by the template, the {\tt apalike} style in our
+ We have used, as instructed by the template, the {\tt apalike} style in our
   LaTeX source, as well as used standard BiBTeX files downloaded from the
@@
 not mind. We will certainly do so as required by publication when (or if) this
-paper is finally accepted}
+paper is finally accepted
 

### 2022-09-30 edubots_surveys.Rnw
anonymize project

@@
 Given the potential benefits that chatbots could bring to the classroom, the
-focus of the EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
-the main sponsor of this study, is to explore best practices and innovative use of chatbots, 
+focus of the % EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
+unnamed European project, the main sponsor of this study, is to explore best practices and innovative use of chatbots, 
 and to create a learning community of educators in higher education institutions.

### 2022-10-03 response-reviewers-2.tex
Format corrections
Hidden everything for double blind review

@@
 
-\def\cabecera{
-
-\begin{minipage}{2.5cm}
-\centerline{  \includegraphics[width=2.5cm,height=2.5cm]{escudo.eps} }
-\end{minipage}
-\ \
-\begin{minipage}{13cm}
- \rule{13cm}{0.6mm}
- \vspace*{0.3cm}
- {\small{\bf \dpto \hfill}} \\
- {\footnotesize{\bf \fac \hfill Fax: \fax}} \\
- {\footnotesize{\bf \ucm \hfill Tel. / Phone: \tel}} \\
- {\footnotesize{\bf \granada \hfill E-mail: \email}}\\
- \rule{13cm}{0.6mm}
-\end{minipage}
-}
-
 %\input cabecera
@@
 
-\cabecera
-
 \vspace{0.5cm}
-
-\hspace{7cm}
-
-\hfill Granada, \today
 
@@
 attempting to give another angle that makes this paper apart from what was
-already published in this other one
-
-Merelo, J.J. et al. (2022). Exploring the Role of Chatbots and Messaging
-Applications in Higher Education: A Teacher's Perspective. In: Zaphiris, P.,
-Ioannou, A. (eds) Learning and Collaboration Technologies. Novel Technological
-Environments. HCII 2022. Lecture Notes in Computer Science, vol 13329. Springer,
-Cham. https://doi.org/10.1007/978-3-031-05675-8\_16
+already published in another (hidden for double blind review).
 
@@
 
-\centerline{\includegraphics[width=2.5cm,height=2.5cm]{jj_sign.eps}}
+\hspace*{8cm} The authors
 
-\hspace*{8cm} Juan J. Merelo\\
-\hspace*{8cm} Catedrático de Universidad (Full professor)
+\newpage
 

### 2023-01-06 edubots_surveys.Rnw
Fix grammar error and typos

@@
 
-\textcolor{blue}{New technologies are being introduced and widely adopted into the classroom in the last years. However, in order to be successful, their application 
-will require (many) extra work and training for the teacher, as well as for the students. Thus, both of them will acquire new skills and, potentially, pupils will 
-get a higher engagement to the subject, which is usually the main objective. Even if several technologies are already in use inside the classroom, there is still room for adopting others.
-Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Given this, 
-asking and analyzing user's opinions with regard to this scenario will help reaping the expected benefits of the technology}.
+\textcolor{blue}{In recent years, new technologies are being widely adopted and introduced into the classroom. However, in order to be successful, their application 
+will require additional work and training for the teacher, as well as for the students. Thus, both of them will acquire new skills and, potentially, pupils will be more 
+engaged to the subject, which is usually the main objective. Even if several technologies are already in use in the classroom, there is still room for adopting new others.
+Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Asking and analyzing users' 
+opinions with regard to this scenario will help reaping the expected benefits of the technology}.
 

### 2023-01-06 edubots_surveys.Rnw
fix errors and grammar - introduction par2

@@
 
-\textcolor{blue}{In the last years, messaging applications such as WhatsApp or Telegram are being used in teaching scenarios mainly at secondary and higher education.
-In addition to their main use, some of these tools offer the possibility of interact with \textit{chatbots} (or just bots), even supporting synchronous conversation between the different
-parties \cite{differ.chat}. There is also possible to create a standalone chatbot application and attach it to a messaging tool through an API (Application Program Interface).}
+\textcolor{blue}{Messaging applications such as WhatsApp or Telegram are becoming very popular in teaching scenarios mainly at secondary and higher education.
+In addition to their main use, some of these tools offer the possibility to interact with \textit{chatbots} (or just bots), even supporting synchronous conversations between the different
+parties \cite{differ.chat}. It is also possible to create a standalone chatbot application and attach it to a messaging tool through an API (Application Programming Interface).}
 

### 2023-01-06 edubots_surveys.Rnw
Fix grammar and typos - intro p3

@@
 
-\textcolor{blue}{\textit{Chatbots} are autonomous agents able to communicate and interact with humans (or other chatbots) in a human-like way \cite{Gong2008}, answering question and even posing their own ones to the user.
+\textcolor{blue}{\textit{Chatbots} are autonomous agents that are able to communicate and interact in a human-like way \cite{Gong2008}, answering question and even posing their own ones to the user. 
 Thus, we can say that they are close to passing a Turing Test \cite{moor2003turing}. They are implemented by means of different Artificial Intelligence techniques, such as natural language processing.
-Inside the plethora of possible applications of chatbots, education is one of the most prolific nowadays \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called 
+Within the plethora of possible applications of chatbots, education is one of the most prolific nowadays \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called 
 \textit{personalized learning}, i.e.
-they adapt themselves to students’ pace of learning and provide online tutoring outside the classroom, which have been proved to be very effective increasing their
-engagement and participation in the subjects \cite{agarwal2020}.
-Moreover chatbots' tutoring possibilities aid to reduce the stress of students \cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their teacher,
-or asking questions in front of the class.
-This situation normally conducts to a silence of the student and a later contact with the teacher by e-mail, which, in turn, will mean a workload for the teacher, that could be very
-significant given the existing disproportion between number of students per each teacher.  
+they adapt themselves to students' self-pace learning and provide online tutoring.
+Personalized learning has been proved to be very effective increasing students course engagement and participation \cite{agarwal2020}.
+Moreover, chatbots also reduce students' stress \cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their teachers,
+or asking questions in front of the class. This situation usually results in a later contact with the teacher by e-mail, which in turn, will mean a workload for the teacher that could be very 
+significant given the disproportionate ratio of number of students to teachers.  
 }
 Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning
-experience \cite{Griol2014,kim2020}.
-In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding.
+experience \cite{Griol2014,kim2020}. In addition, using an automated system such as a chatbot will allow teachers to spend more time on  other topics that students struggle with.
 

### 2023-01-06 edubots_surveys.Rnw
Fix gramma and typos - Introduction p3-4

@@
 focus of the % EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
-unnamed European project, the main sponsor of this study, is to explore best practices and innovative use of chatbots, 
+unnamed European project, the main sponsor of this study, is to explore the best practices and innovative use of chatbots, 
 and to create a learning community of educators in higher education institutions.
-\textcolor{blue}{Researchers and teachers participating in this project have developed several studies. Most of these works have been focused on how the 
+\textcolor{blue}{Researchers and teachers participating in this project have developed several studies. Most of these works are focused on how  
 messaging applications and/or chatbots are normally applied to deliver personalized learning in classrooms that occurs anytime anywhere,
@@
  \begin{itemize}
-\item The first phase aimed to collect feedback from students about their actual
-  information about students’ preferences of tools/applications for chatting and
-  messaging, how they use them in educational context, who do they like to be
-  with in the class messaging groups, and their expectations of the chatbots in
-  terms of assisting them during their learning process. Therefore, two surveys
+\item The first phase aimed to collect feedback from students about their
+  students’ preferences of tools/applications for chatting and
+  messaging, how they use them in educational context, who they like to be
+  with in the class messaging groups, and their expectations of chatbots 
+  in assisting them during their learning process. Therefore, two surveys
   for bachelor and master degree students at the University of Granada (Spain)
@@
   findings of the students' surveys reveal that they prefer to use messaging
-  applications, such as Telegram or WhatsApp as they are familiar to
-  them. Students also expressed interest in chatbots that can assist them with
+  familiar applications, such as Telegram or WhatsApp. 
+  Students also expressed interest in chatbots that can assist them with
   organizing their course schedules, help them access their assignment grades
-  and facilitate searching for course's resources.
+  and facilitate searching for resources.
 \item The results of the first phase were fed into the second phase of the
   study, which focused on teachers’ opinions about using chatbots and messaging
-  applications in classes. This is what is going to be presented in this paper.
+  applications in classes. These results are the main focus of this paper.
 \end{itemize}

### 2023-01-06 edubots_surveys.Rnw
fix grammar and typos - Introduction p5-6

@@
 Initially, a single survey was developed for this purpose and responses from 300
-higher education teachers were collected and analysed\textcolor{black}{; this will be explained more fully in the methodology section}. The responses' analysis
-entailed the creation of a second survey to which 200 teachers' responses were
-collected\textcolor{black}{, with the methodology and collective characteristics that will be explained below. The questions of the second survey focused on discussing teachers'
+higher education teachers were collected and analysed\textcolor{black}{; this will be detailed in Section \ref{sec:meth}}. The responses' analysis
+led to the preparation of a second survey for teachers and 200 responses were
+collected\textcolor{black}{, again following the methodology that will be explained later. The questions of the second survey focused on asking about teachers'
 needs, opinions and preferences of the development of future technology-enhanced
-tools and its potential impact on educational institutions’ policies. In order to assess these, this paper investigated the following research questions}:
+tools and its potential impact on educational institutions policies. In order to assess these, this paper layed out the following research questions}:
 

### 2023-01-06 edubots_surveys.Rnw
fix grammar and typos - Introduction last par

@@
 
-We will try to answer these questions through the analysis of questions and
-answers in the two aforementioned surveys. Eventually, what we want to obtain is a series of
+We will try to answer these research questions through the analysis of the two aforementioned surveys. 
+Eventually, what we want to obtain is a series of
 recommendations to make a successful deployment of chatbot technologies (and, in
-some cases, general instant messaging applications) in higher education\textcolor{black}{; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be used in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from RQ3 we will also try to find best practices in the adoption of messaging platforms and they accompanying chatbots.}
-
-The remainder of the paper is organized as follows: \textcolor{black}{first, an overview of what
-current research has found about the use of messaging applications, including
-chatbots, in the classroom is described}. The methodology used in the surveys is presented in
-Section \ref{sec:meth}, and the results of the surveys are presented next in
+some cases, general instant messaging applications) in higher education\textcolor{black}{; from the response to RQ1 and RQ4 we will recommend specific technologies or applications to be used in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from RQ3 we will also try to find best practices in the adoption of messaging platforms and their accompanying chatbots.}
+
+The paper is organized as follows: \textcolor{black}{first, an overview of what
+current research has found about the use of messaging applications in the classrom, including
+chatbots is presented}. Next, the methodology used in the surveys is described in
+Section \ref{sec:meth}, and the results of the surveys are presented in
 Section \ref{sec:res}. Finally, we discuss these results and conclude with a
-series of recommendations in the section that closes the paper.
+series of recommendations for the successful deployment of chatbots in higher education.
 

### 2023-01-07 edubots_surveys.Rnw
Local changes

--- 2023-01-06 edubots_surveys.Rnw
@@
 %%It must be present to enable the BMC Submission system to
-%%recognize this template!!
-
+%%recognise this template!!
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                     %%
+%%  LaTeX template for BioMed Central  %%
+%%     journal article submissions     %%
+%%                                     %%
+%%          <8 June 2012>              %%
+%%                                     %%
+%%                                     %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                                 %%
+%% For instructions on how to fill out this Tex template           %%
+%% document please refer to Readme.html and the instructions for   %%
+%% authors page on the biomed central website                      %%
+%% https://www.biomedcentral.com/getpublished                      %%
+%%                                                                 %%
+%% Please do not use \input{...} to include other tex files.       %%
+%% Submit your LaTeX manuscript as one .tex document.              %%
+%%                                                                 %%
+%% All additional figures and files should be attached             %%
+%% separately and not embedded in the \TeX\ document itself.       %%
+%%                                                                 %%
+%% BioMed Central currently use the MikTex distribution of         %%
+%% TeX for Windows) of TeX and LaTeX.  This is available from      %%
+%% https://miktex.org/                                             %%
+%%                                                                 %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% additional documentclass options:
+%  [doublespacing]
+%  [linenumbers]   - put the line numbers on margins
+
+%%% loading packages, author definitions
+
+%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
 \documentclass{bmcart}
@@
 \usepackage[utf8]{inputenc} %unicode support
+\usepackage{hyperref} % for URL
 
@@
 
-% Remember to substitute figures/ by nothing in the generated PDF
-% \author[
-%   addressref={aff1},
-%   corref={aff1},
-%   email={jmerelo@ugr.es}
-% ]{\inits{JJM}\fnm{Juan J.} \snm{Merelo}}
-% \author[
-%   addressref={aff1},
-%   email={pacv@ugr.es}
-% ]{\inits{PAC}\fnm{Pedro A.} \snm{Castillo}}
-% \author[
-%   addressref={aff2},
-%   email={amorag@ugr.es}
-% ]{\inits{AMM}\fnm{Antonio M.} \snm{Mora}}
-% \author[
-%   addressref={aff1},
-%   email={fbarranco@ugr.es}
-% ]{\inits{FB}\fnm{Francisco} \snm{Barranco}}
-% \author[
-%   addressref={aff3},
-%   email={n.h.abbas@leeds.ac.uk}
-% ]{\inits{NA}\fnm{Noorhan} \snm{Abbas}}
-% \author[
-%   addressref={aff1},
-%   email={aguillen@ugr.es}
-% ]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
-% \author[
-%   addressref={aff4},
-%   email={o.tsivitanidou@cyens.org.cy}
-% ]{\inits{OT}\fnm{Olia} \snm{Tsivitanidou}}
-% 
-% \address[id=aff1]{%
-%   \orgdiv{Department of Computer Architecture and Technology},
-%   \orgname{University of Granada},
-%   \city{Granada},
-%   \cny{Spain}
-% }
-% \address[id=aff2]{%
-%   \orgdiv{Department of Signal Theory, Telematics and Communications},
-%   \orgname{University of Granada},
-%   \city{Granada},
-%   \cny{Spain}
-% }
-% \address[id=aff3]{%
-%   \orgdiv{School of Computing},
-%   \orgname{University of Leeds},
-%   \city{Leeds},
-%   \cny{UK}
-% }
-% \address[id=aff4]{%
-%   \orgname{CYENS},
-%   \city{Nicosia},
-%   \cny{Cyprus}
-% }
+\author[
+  addressref={aff1},                  
+  corref={aff1},                      
+  email={jmerelo@ugr.es}  
+]{\inits{JJM}\fnm{Juan J.} \snm{Merelo}}
+\author[
+  addressref={aff1},
+  email={pacv@ugr.es}
+]{\inits{PAC}\fnm{Pedro A.} \snm{Castillo}}
+\author[
+  addressref={aff2},
+  email={amorag@ugr.es}
+]{\inits{AMM}\fnm{Antonio M.} \snm{Mora}}
+\author[
+  addressref={aff1},
+  email={fbarranco@ugr.es}
+]{\inits{FB}\fnm{Francisco} \snm{Barranco}}
+\author[
+  addressref={aff3},
+  email={n.h.abbas@leeds.ac.uk}
+]{\inits{NA}\fnm{Noorhan} \snm{Abbas}}
+\author[
+  addressref={aff1},
+  email={aguillen@ugr.es}
+]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
+\author[
+  addressref={aff4},
+  email={o.tsivitanidou@cyens.org.cy}
+]{\inits{OT}\fnm{Olia} \snm{Tsivitanidou}}
+
+\address[id=aff1]{%                           
+  \orgdiv{Department of Computer Architecture and Technology},           
+  \orgname{University of Granada},
+  \city{Granada},
+  \cny{Spain}
+}
+\address[id=aff2]{%
+  \orgdiv{Department of Signal Theory, Telematics and Communications},
+  \orgname{University of Granada},
+  \city{Granada},
+  \cny{Spain}
+}
+\address[id=aff3]{%
+  \orgdiv{School of Computing},
+  \orgname{University of Leeds},
+  \city{Leeds},
+  \cny{UK}
+}
+\address[id=aff4]{%
+  \orgname{CYENS},         
+  \city{Nicosia},
+  \cny{Cyprus} 
+}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter short notes here                   %%
+%%                                          %%
+%% Short notes will be after addresses      %%
+%% on first page.                           %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\begin{artnotes}
+%%\note{Sample of title note}     % note to the article
+%\note[id=n1]{Equal contributor} % note, connected to author
+%\end{artnotes}
 
@@
 \begin{abstract} % abstract
-Messaging platforms are applications, generally mediated by an app, desktop program or the web, mainly used for synchronous communication among users.
-As such, they have been widely adopted officially by higher education establishments, after little or no study of their impact and perception by the teachers.
-We think that the introduction of these new tools and the opportunities and challenges they have needs to be studied carefully in order to adopt the model, as well as the tool, that is the most adequate for all parties involved.
-We already studied the perception of these tools by students, in this paper we examine the teachers’
-experiences and perceptions through a survey that we validated with peers, and what they think these tools should make or serve so that it enhances students learning and helps them achieve their learning objectives.
-The survey has been distributed among tertiary education teachers, both in universitary and other kind of tertiary establishments, based in
-Spain (mainly) and Spanish-speaking countries. We have focused on collecting
-teachers' preferences and opinions on the introduction of messaging platforms in their day-to-day work, as well as other services attached to them, such as  chatbots.
-What we intend with this survey is to understand their needs and to gather
-information about the various educational use cases where these tools could be 
-valuable. In addition, an analysis of how and when teachers’ opinions towards
-the use of these tools varies across gender, experience, and their discipline
-of specialization is presented. The key findings of this study highlight the
-factors that can contribute to the advancement of the adoption of messaging
-platforms and chatbots in higher education institutions to achieve the desired
-learning outcomes.
+Introducing new technologies such as messaging platforms, and the chatbots attached to them, in higher education, is rapidly growing.
+This introduction entails a careful consideration of the potential opportunities and/or challenges of adopting these tools.
+Hence, a thorough examination of the teachers’ experiences in this discipline can shed the light on the effective ways of enhancing students’ learning and boosting their progress.
+In this contribution, we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish-speaking countries.
+The focus of these surveys is to collect teachers’ feedback about their opinions of the introduction of the messaging platforms and chatbots in their classes, understand their needs and to gather information about the various educational use cases where these tools are valuable.
+In addition, an analysis of how and when teachers’ opinions towards the use of these tools can vary across gender, experience, and their discipline of specialisation is presented.
+The key findings of this study highlight the factors that can contribute to the advancement of the adoption of messaging platforms and chatbots in higher education institutions to achieve the desired learning outcomes.
 \end{abstract}
@@
 \kwd{Higher education}
+% Antonio - add something related to "survey", "teachers' opinion" or so?
 \end{keyword}
 
+% MSC classifications codes, if any
+%\begin{keyword}[class=AMS]
+%\kwd[Primary ]{}
+%\kwd{}
+%\kwd[; secondary ]{}
+%\end{keyword}
+
 \end{abstractbox}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                            %%
+%% The Main Body begins here                  %%
+%%                                            %%
+%% Please refer to the instructions for       %%
+%% authors on:                                %%
+%% https://www.biomedcentral.com/getpublished %%
+%% and include the section headings           %%
+%% accordingly for your article type.         %%
+%%                                            %%
+%% See the Results and Discussion section     %%
+%% for details on how to create sub-sections  %%
+%%                                            %%
+%% use \cite{...} to cite references          %%
+%%  \cite{koon} and                           %%
+%%  \cite{oreg,khar,zvai,xjon,schn,pond}      %%
+%%                                            %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%% start of article main body
+
 <<setup, echo=FALSE,message=FALSE>>=
-knitr::opts_chunk$set(fig.path='figures/')
 library(ggplot2)
@@
 
-\textcolor{blue}{In recent years, new technologies are being widely adopted and introduced into the classroom. However, in order to be successful, their application 
-will require additional work and training for the teacher, as well as for the students. Thus, both of them will acquire new skills and, potentially, pupils will be more 
-engaged to the subject, which is usually the main objective. Even if several technologies are already in use in the classroom, there is still room for adopting new others.
-Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Asking and analyzing users' 
-opinions with regard to this scenario will help reaping the expected benefits of the technology}.
-
-\textcolor{blue}{Messaging applications such as WhatsApp or Telegram are becoming very popular in teaching scenarios mainly at secondary and higher education.
-In addition to their main use, some of these tools offer the possibility to interact with \textit{chatbots} (or just bots), even supporting synchronous conversations between the different
-parties \cite{differ.chat}. It is also possible to create a standalone chatbot application and attach it to a messaging tool through an API (Application Programming Interface).}
-
-\textcolor{blue}{\textit{Chatbots} are autonomous agents that are able to communicate and interact in a human-like way \cite{Gong2008}, answering question and even posing their own ones to the user. 
-Thus, we can say that they are close to passing a Turing Test \cite{moor2003turing}. They are implemented by means of different Artificial Intelligence techniques, such as natural language processing.
-Within the plethora of possible applications of chatbots, education is one of the most prolific nowadays \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called 
-\textit{personalized learning}, i.e.
-they adapt themselves to students' self-pace learning and provide online tutoring.
-Personalized learning has been proved to be very effective increasing students course engagement and participation \cite{agarwal2020}.
-Moreover, chatbots also reduce students' stress \cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their teachers,
-or asking questions in front of the class. This situation usually results in a later contact with the teacher by e-mail, which in turn, will mean a workload for the teacher that could be very 
-significant given the disproportionate ratio of number of students to teachers.  
-}
-Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning
-experience \cite{Griol2014,kim2020}. In addition, using an automated system such as a chatbot will allow teachers to spend more time on  other topics that students struggle with.
-
-Given the potential benefits that chatbots could bring to the classroom, the
-focus of the % EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
-unnamed European project, the main sponsor of this study, is to explore the best practices and innovative use of chatbots, 
-and to create a learning community of educators in higher education institutions.
-\textcolor{blue}{Researchers and teachers participating in this project have developed several studies. Most of these works are focused on how  
-messaging applications and/or chatbots are normally applied to deliver personalized learning in classrooms that occurs anytime anywhere,
-promote collaborative learning experiences, group discussions \cite{panah2020study} and boost students' sense of belonging to their institutions
-\cite{abbas2021onlinechat}.}
-\textcolor{blue}{The majority of these studies were conducted focusing on the teachers' perspectives, so this paper aims to provide more conclusions regarding 
-their opinions and needs, as well as the existing challenges or opportunities that arise when adopting these technologies in classrooms. This will lead to clarify
-how they can positively contribute to enhancing the learning process in higher education institutions.}
-
-In this study, data collection involved two phases:
+% TODO: introduction
+The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new skills by both.
+Some technologies are readily adapted, but others require longer time for full adoption.
+In most cases, the magnitude of the uptake of the new technology impinges on the collaboration of all the parties using it.
+Hence, examining the users’ opinions and their opinions is an important first step in boosting this collaboration and reaping the benefits of the technology.
+Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp, Telegram and Facebook Messenger took place.
+Some messaging applications have built in chatbots that are able to support a synchronous conversation between the different parties \cite{differ.chat}, while other chatbots are developed as standalone systems and can possibly be attached to a messaging application using an API (Application Program Interface).
+
+A \textit{chatbot} is a program, sometimes developed using Artificial Intelligence techniques, able to communicate in a similar way as humans do \cite{Gong2008}, using, in some cases, natural language.
+Indeed, most of these applications would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any question fluently, and even pose own questions in their conversations.
+The recent advancement in this discipline has played an important role in many fields especially in education and online tutoring \cite{clarizia2018,Smutny2020}.
+These automatic systems facilitate the delivery of personalized learning by adapting to students’ pace of learning and providing customized online tutoring outside the classroom.
+Thus, chatbots can significantly contribute to providing interactive learning experiences as well as improving individual attention \cite{agarwal2020}.
+ In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor.
+In fact, in many cases, some students experience stress because of their need to ask a question in front of the entire class.
+This is why many students resort to silence
+ % Antonio - I guess refrain to silence is the opposite of what we wanted to say, isn't it? :D
+ % mistaking "resort" for "refrain". You don't say "refrain to", but refrain from.
+ in the classroom and tend to contact their teachers later via email.
+ Consequently, this can lead to not only a delay in obtaining answers to their questions but can also cause a significant increase in their teachers’ workload, especially when factoring in the disproportion between the class size and the number of teachers.
+Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning experience \cite{Griol2014,kim2020}.
+In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding.
+
+Given the potential benefits that chatbots could bring to the classroom, the focus of the EDUBOTS KA2 European project \footnote{https://www.edubots.eu}, the sponsor of this study, is to gather, analyse and disseminate best practices on the use of chatbots in higher education institutions.
+
+ The line of research of which this paper is a part has involved two phases of data collection.
  \begin{itemize}
-\item The first phase aimed to collect feedback from students about their
-  students’ preferences of tools/applications for chatting and
-  messaging, how they use them in educational context, who they like to be
-  with in the class messaging groups, and their expectations of chatbots 
-  in assisting them during their learning process. Therefore, two surveys
-  for bachelor and master degree students at the University of Granada (Spain)
-  were designed and answers from more than 250 students were collected. The key
-  findings of the students' surveys reveal that they prefer to use messaging
-  familiar applications, such as Telegram or WhatsApp. 
-  Students also expressed interest in chatbots that can assist them with
-  organizing their course schedules, help them access their assignment grades
-  and facilitate searching for resources.
-\item The results of the first phase were fed into the second phase of the
-  study, which focused on teachers’ opinions about using chatbots and messaging
-  applications in classes. These results are the main focus of this paper.
+\item The first phase aimed to collect feedback from students about their actual needs \cite{MoraChatbots2021}.
+Hence, the objective was to collect information about students’ preferences of tools/applications for chatting and messaging, how they use them in educational context, who do they like to be with in the class messaging groups, and their expectations of the chatbots in terms of assisting them during their learning process.
+Therefore, two surveys for bachelor and master degree students at the University of Granada (Spain) were designed and answers from more than 250 students were collected.
+The key findings of the students surveys reveal that they prefer to use messaging applications, such as Telegram or WhatsApp as they are familiar to them.
+Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course's resources.
+\item The results of the first phase were fed into the second phase of the study, which focused on teachers’ opinions about using chatbots and messaging applications in classes.
+This is what is going to be presented in this paper.
 \end{itemize}
 
-Initially, a single survey was developed for this purpose and responses from 300
-higher education teachers were collected and analysed\textcolor{black}{; this will be explained more fully in the methodology section}. The responses' analysis
-entailed the creation of a second survey to which 200 teachers' responses were
-collected\textcolor{black}{, with the methodology and collective characteristics that will be explained below. The questions of the second survey focused on discussing teachers'
-needs, opinions and preferences of the development of future technology-enhanced
-tools and its potential impact on educational institutions’ policies. In order to assess these, this paper investigated the following research questions}:
+Initially, a single survey was developed for this purpose.
+Responses from 300 teachers were collected and analysed.
+An initial analysis led to the creation of a second survey, which collected responses from 200 different higher education teachers.
+The questions on this survey focus on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:
 
 \begin{itemize}
-\item RQ1 - Do teachers use now or want to use messaging apps in their classes?
-\item RQ2 - Which chatbots' features would teachers find useful for this purpose?
+\item RQ1 - Are teachers already using messaging apps in their classes? 
+\item RQ2 - Which kind of chatbots would teachers find useful in their classes? 
 \item RQ3 - Which kind of interaction do teachers prefer with their students?
@@
 
-We will try to answer these questions through the analysis of questions and
-answers in the two aforementioned surveys. Eventually, what we want to obtain is a series of
-recommendations to make a successful deployment of chatbot technologies (and, in
-some cases, general instant messaging applications) in higher education\textcolor{black}{; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be used in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from RQ3 we will also try to find best practices in the adoption of messaging platforms and they accompanying chatbots.}
-
-The remainder of the paper is organized as follows: \textcolor{black}{first, an overview of what
-current research has found about the use of messaging applications, including
-chatbots, in the classroom is described}. The methodology used in the surveys is presented in
-Section \ref{sec:meth}, and the results of the surveys are presented next in
-Section \ref{sec:res}. Finally, we discuss these results and conclude with a
-series of recommendations in the section that closes the paper.
+We will try to answer these questions through the analysis of questions and answers in the two surveys.
+Eventually, what we want to obtain is a series of recommendations to make a successful deployment of chatbot technologies (and, in some cases, general instant messaging applications) in higher education.
+
+The remainder of the paper is organized as follows: Next is an overview of what current research has found about the use of messaging applications, including chatbots, in the classroom.
+The methodology used in the surveys is presented in Section \ref{sec:meth}, and the results of the surveys are presented next in Section \ref{sec:res}.
+Finally, we discuss these results and conclude with a series of recommendations in the section that closes the paper.
 
@@
 % The Use of Mobile Instant Messaging (MIM) Platforms in Higher Education
-The widespread and rapid adoption of free Mobile Instant Messaging
+The widespread and rapid adoption of free Mobile Instant messaging
 (MIM) tools/platforms such as WhatsApp, Telegram, WeChat and Facebook
@@
 (i.e. video, audio, text) \cite{tang2017mobile}. Using these tools in
-higher education can facilitate the delivery of personalized learning
+higher education can facilitate the delivery of personalised learning
 that occurs anytime anywhere, promote collaborative learning
@@
 
-WhatsApp is, at least in most Western countries, the most popular MIM platform
-used by educators to \textcolor{black}{provide} assignments' feedback to students, support course
-discussions, and provide learning resources in informal learning settings
-\cite{panah2020study}.  Moreover, the use of WhatsApp in higher education could
-enhance social presence \cite{tang2017mobile} and foster trust relationships
-between educators and students embedded in the social learning process
+WhatsApp is, at least in most Western countries,
+the most popular MIM platform used by educators to give assignments'
+feedback to students, support course discussions, and provide learning
+resources in informal learning settings \cite{panah2020study}.  Moreover, the
+use of WhatsApp in higher education could enhance social presence
+\cite{tang2017mobile} and foster trust relationships between educators
+and students embedded in the social learning process
 \cite{gachago2015crossing}; however, this last paper also reflects the need for
@@
 in general. At the same time, it also mentions different challenges, among which
-the most important is the blurring of social and academic life; indeed, there are challenges when using MIM tools that occur due to the
-blurring of boundaries between academic and private life. This can lead to
-technostress \cite{gachago2015crossing}, difficulty in managing
-responsibilities, especially among mature students, and lack of privacy
-\cite{tang2017mobile}.  Students' dropout of the MIM groups, as they can leave
-groups at any time, can hinder their learning and undermine educators' efforts
-\cite{mwakapina2016whatsapp}.  In addition, there is a need to set rules and
-norms for these MIM groups in order to maintain the safety of these online
-communities for students \cite{abbas2021onlinechat}. However, these rules should
-not affect students' ownership and control, since it is vital to advance in
-their learning \cite{gachago2015crossing} process.  This is why examining the
-role of MIM in higher education is still a challenge, and why the opinions of
-the teaching community towards them have to be examined, as we do in this paper.
+the most important is the blurring of social and academic life. Examining these
+opinions will be the objective of RQ3 in this paper.
+
+Nevertheless, there are challenges when using MIM tools that occur due
+to the blurring of boundaries between academic and private life. This
+can lead to technostress \cite{gachago2015crossing}, difficulty in
+managing responsibilities, especially among mature students, and lack of
+privacy \cite{tang2017mobile}.  Students' dropout of the MIM groups,
+as they can leave groups at any time, can hinder their learning and
+undermine educators' efforts \cite{mwakapina2016whatsapp}.  In
+addition, there is a need to set rules and norms for these MIM groups
+in order to maintain the safety of these online communities for
+students \cite{abbas2021onlinechat}. However, these rules should not affect students'
+ownership and control, since it is vital to advance in their learning
+\cite{gachago2015crossing} process. 
+This is why examining the role of MIM in higher education is still a challenge,
+and why the opinions of the teaching community towards them have to be
+examined, as we do in this paper.
 
 % The Use of Chatbots in Higher Education
-The use of MIM, although possibly valuable by itself, can be enhanced via the
-use of chatbots, which, being conversational agents, usually dwell in systems
-where synchronous conversations take place.  The use of conversational agents
-(chatbots) in higher education is still at its infancy
-\cite{yang2019opportunities}. Nevertheless, recent studies examining their
-positive impact on students' academic performance \cite{perez2020rediscovering}
-and engagement \cite{differ.chat,abbas2021onlinechat} have led to a growing
-interest in using this technology in the (possibly virtual) classroom. Indeed,
-the use of chatbots in collecting course feedback from students in higher
-education improved students' response quality and boosted their enjoyment levels
-\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using either tools
-such as mobile devices or teaching strategies based on gamification
-\cite{Yildirim2017} can improve student motivation. In this sense, the authors
-in \cite{Pimmer2019} \textcolor{black}{adopted a quasi-experimental, survey-based approach to
-report the positive impact of using instant messaging tools in boosting
-students' knowledge and mitigating their feelings of isolation}.
-
-Several higher education chatbots' evaluation studies have been undertaken. For
-instance, a recent evaluation review study presented by Smutny and Schreiberova
-\cite{Smutny2020} examined 47 educational chatbots implemented in Facebook
-Messenger with the focus to identify characteristics and quality metrics such as
-language, subject matter and platform\textcolor{black}{, whereas the study undertaken by Pérez and collaborators
-\cite{perez2020rediscovering} aimed to categorize educational chatbots, according
-to their, purpose into service-oriented and teaching-oriented}. The first category
-includes those that provide service support such as the chatbot Ask Holly
-\cite{meetholly} and Dina \cite{santoso2018dinus}; both chatbots respond to
-students' questions about enrollment and registration. Ask L. U.
-\cite{LancasterUniversity_2019} answers students' frequently asked questions
-about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot}
-and Differ \cite{differ.chat} facilitate breaking the ice between new students
-by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
-proposed a generic chatbot for university students that is able to answer to
-their frequently asked questions \textcolor{black}{and, for some time, the University of Granada had
-\textcolor{black}{Elvira} as a chatbot in its main web page \cite{MOREO20129} to perform that duty.} Besides being able
-to answer pre-established (frequent) questions, it did so from the website of
-the University of Granada using an inset \textcolor{black}{persona, voiced by a real person, who
-lip-synced the answers. The emphasis in the case of Elvira, however, was on the
-authenticity of the synchronization more than in making the update of questions
-answered simpler, or more interactive, or more open to the rest of the university staff, using actual messaging platforms. In
-most cases, the embedded search engine was able to provide more up-to-date
-and accurate answers than the ones provided by Elvira, which had to be updated
-by hand (and not too often).
-It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide an useful service.
-Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, something which is the focus of this paper}.
-
-On the other hand, teaching-oriented chatbots are more sophisticated, as they
-set personalized learning outcomes and monitor learning progress. For instance,
-\cite{fernoagua2018intelligent} reported on ``eduAssistant'', a virtual teaching
-assistant chatbot developed on the Telegram messaging platform. In this study,
-the Telegram platform is chosen because it is easy to use, students are familiar
-with its features, and it enables them to exchange messages in different formats
-(text, audio and video) \cite{fernoagua2018intelligent}. In addition, Telegram
-could operate on all devices and operating systems. The ``eduAssistant'' chatbot
-acts as an automatic agent in teacher-content-student, facilitating real-time
-feedback loops and providing a personalized learning experience relevant to the
+The use of MIM, although possibly valuable by itself, can be enhanced via the use of chatbots, which, being conversational agents, usually dwell in systems where synchronous conversations take place. 
+The use of conversational agents (chatbots) in higher education is
+still at its infancy \cite{yang2019opportunities}. Nevertheless,
+recent studies examining their positive impact on students' academic
+performance \cite{perez2020rediscovering} and engagement
+\cite{differ.chat,abbas2021onlinechat} have led to a growing interest
+in using this technology in the (possibly virtual) classroom. Indeed, the use of chatbots in
+collecting course feedback from students in higher education improved
+students' response quality and boosted their enjoyment levels
+\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using
+either tools such as mobile devices or teaching strategies based on
+gamification \cite{Yildirim2017} can improve student motivation. In
+this sense, the authors in \cite{Pimmer2019} carried out a series of experiments with
+technological tools whose results showed positive perception and
+acceptance of the use of technology in teaching and learning.
+
+Several higher education chatbots' evaluation studies have been 
+undertaken. For instance, a recent evaluation review study presented by Smutny and Schreiberova 
+\cite{Smutny2020} examined 47 educational chatbots implemented in
+Facebook Messenger with the focus to identify characteristics and
+quality metrics such as language, subject matter and platform. Another
+study aimed to categorise educational chatbots according to their
+purpose into service-oriented and teaching-oriented
+\cite{perez2020rediscovering}. The first category includes those that
+provide service support such as the chatbot Ask Holly \cite{meetholly}
+and Dina \cite{santoso2018dinus}; both chatbots respond to students'
+questions about enrollment and registration. Ask L. U.
+ \cite{LancasterUniversity_2019} answers students' frequently
+asked questions about timetables, grades, tutors and societies. LISA
+\cite{dibitonto2018chatbot} and Differ \cite{differ.chat} facilitate
+breaking the ice between new students by introducing them to each
+other. Ranoliya et al. \cite{ranoliya2017chatbot} proposed a generic chatbot for
+university students that is able to answer to their frequently asked
+questions. 
+For some time, the University of Granada had ELVIRA as a
+chatbot in its main web page \cite{MOREO20129}. Besides being able to
+answer pre-established (frequent) questions, it did so from the website of the
+University of Granada using an inset character, voiced by a real
+person, who lip-synched the answers. The emphasis in the case of Elvira,
+however, was on the authenticity of the synchronization more than in
+making the update of questions and answers simpler, or more
+interactive, using actual messaging platforms. 
+In most cases, using the inset search engine was able to give you more up-to-date and
+accurate answers than the ones provided by ELVIRA, which had to be updated by hand (and not too often).
+
+On the other hand, teaching-oriented chatbots are more sophisticated,
+as they set personalised learning outcomes and monitor learning
+progress. For instance, \cite{fernoagua2018intelligent} reported on
+''eduAssistant'', a virtual teaching assistant chatbot developed on the
+Telegram messaging platform. In this study, Telegram platform was
+chosen because it is easy to use, students are familiar with its
+features, and it enables them to exchange messages in different
+formats (text, audio and video) \cite{fernoagua2018intelligent}. In
+addition, Telegram could operate on all devices and operating
+systems. The ''eduAssistant'' chatbot acts as an automatic agent
+in teacher-content-student, facilitating real-time feedback
+loops and providing a personalised learning experience relevant to the
 students' acquired skills and knowledge. Using this chatbot, educators can
-create interactive instances in their lectures where they pose questions to
-their students and the chatbot assists those who need further help by giving
-them more hints and reporting it to their educator's dashboard
-\cite{fernoagua2018intelligent}. This can help educators locate those
-students that need more attention and send them more educational resources
-relevant to their academic attainment. \textcolor{black}{In addition, a recent study
-has analysed how the use of chatbots positively affected the learning outcomes
-of students in a Chinese class \cite{doi:10.1177/0735633120929622}}.
-
-Despite its (arguably) successful implementation in different higher education
-institutions, over all in the fringes of educational activity, not in the actual
-student-teacher interaction, its implementation or deployment is not trivial.
-Some authors, for instance \cite{sjostrom2018designing} have proposed a
-conceptual architecture for the adoption of teaching-oriented chatbots in higher
-education.  This conceptual architecture is based on a systematic literature
-review of previous studies, examining the design of chatbots in higher
-education, as well as making a content analysis of student emails and discussion
-forum posts of four instances of a Java programming course.  The study outlined
-several design considerations; among them, the authors emphasized the importance
-of developing chatbots in platforms that students and educators are familiar
-with and can easily access (i.e. Facebook Messenger) which was confirmed with
-\cite{hobert2019you} and \cite{fernoagua2018intelligent} studies. In addition, \cite{sjostrom2018designing} argued that a
-conceptualization of learners' questions could aid designers in integrating the
-appropriate types of questions that the chatbots should support for different
-courses.  \textcolor{black}{Some other authors}, like \cite{coronado2018cognitive}, proposed agents that
-store learning materials to be provided on demand to students, whereas the
-authors in \cite{crockett2017predicting} reported on tutoring systems, which can
-perform initial assessments of students' understanding and provide learning
-material that would advance their understanding to the next level.
-
-Regarding the factors for the adoption of chatbots in higher education, many
-studies have focused on the evaluation of technology acceptance and usability
-\cite{Roblyer2010,Pimmer2019}. However, higher education is a special domain
-where, according to \cite{hobert2019you}, specific pedagogical factors
-such as learning success and increased motivation are more important.  Therefore,
-to develop \textcolor{black}{effective chatbots for higher education, all stakeholders'
-(i.e. educators, students, institutions, etc) needs should be carefully
-collected and taken into consideration
+create interactive instances in their lectures where they pose
+questions to their students and the chatbot assists those who need
+further help by giving them more hints and reporting it to their
+educator's dashboard \cite{fernoagua2018intelligent}. This can help 
+educators to locate those students that need their attention and send to 
+them more educational resources relevant to their academic attainment.
+
+Despite its (arguably) successful implementation in different higher education institutions, 
+over all in the fringes of educational activity, not in the actual interaction student-teacher, its implementation or deployment is not trivial.
+Some authors, for instance \cite{sjostrom2018designing} have proposed a conceptual
+architecture for the adoption of teaching-oriented chatbots in higher education.  This
+conceptual architecture is based on a systematic literature review of
+previous studies, examining the design of chatbots in higher education, as well as making a content 
+analysis of student emails and discussion forum posts of
+four instances of a Java programming course.  The study outlined
+several design considerations; among them, the authors emphasised the
+importance of developing chatbots in platforms that students and
+educators are familiar with and can easily access (i.e. Facebook
+Messenger) which was confirmed with \cite{hobert2019you} and
+\cite{fernoagua2018intelligent} studies. In addition, Sj{\"o}str{\"o}m et al. \cite{sjostrom2018designing} 
+argued that a conceptualision of learners' questions could aid designers in integrating the appropriate
+types of questions that the chatbots should support for different
+courses.  Coronado et al. \cite{coronado2018cognitive} proposed agents that store
+learning materials to be provided on demand to students, whereas the authors in
+\cite{crockett2017predicting} reported on tutoring systems,
+which can perform initial assessments of students' understanding and
+provide learning material that would advance their understanding to
+the next level.
+
+Regarding the factors for the adoption of chatbots in higher
+education, many studies have focused on the evaluation of technology
+acceptance and usability \cite{Roblyer2010,Pimmer2019}. However,
+higher education is a special domain where, according to Hobert \cite{hobert2019you}, 
+specific pedagogical factors such as learning success or increased motivation are more important.  
+Therefore, to develop efficient chatbots for higher education, all stakeholders'
+(i.e. educators, students, institutions, etc) expectations needs to be
+carefully collected and taken into consideration
 \cite{sjostrom2018designing,tsivitanidouusers}.
-These needs include, but are not limited to, student's learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance; this is why we focus in this paper on what the teachers are looking for in a TAM  (Technology Acceptance Model) and associated technologies like chatbots; both authors focus on what the teachers need in terms of the latter; this paper will focus on a wider perspective trying to ascertain what they are looking for in terms of general messaging technology.
-The classical literature \cite{tam91} already proposes that any adoption of technology must be tuned in to the user needs and experience.
-In this paper we will try to find out what those are in order to propose a successful model of adoption of chatbot technology}.
-
-Along this line of research, our previous work \cite{MoraChatbots2021:anon}
-aimed at analyzing the expectations of students on this regard; recent papers
-have also analysed how the use of chatbots affected the learning outcomes of
-students in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper
-analysed conversational chatbots in an one-to-one setting, finding that learning
-really benefited from it. This is, once again, a proof of the benefit of
-chatbots in certain settings; however, there are some prior experiences, as well as needs, that might
-prevent the successful acceptance of the technology, and these are what we are
-trying to find out in this paper, together with what kind of features would improve
-its acceptance.
-
-Besides, the present work is focused on the other key actor in this challenge,
-i.e. educators. \textcolor{black}{How they accepted chatbots} has been studied very recently by Chocarro et
-al. \cite{doi:10.1080/03055698.2020.1850426}, who, by analyzing surveys, created
-a {\em technology acceptance model} that proposed a series of features that
-would make chatbots easier to accept; among them, formality of language as well
-as easiness and usefulness. The survey targeted primary and secondary education
-teachers, and was also more interested in the general use of chatbots in
-education, not specifically in a classroom setting, seeking educational
-outcomes. However, they establish a series of results that are obviously
-interesting and relevant for this work.
-
-We will present next the methodology we have followed to find out teachers'
-opinions.
+
+Along this line of research, our previous work \cite{MoraChatbots2021} aimed at analysing the expectations of students on this regard; recent papers have also analyzed how the use of chatbots affected the learning outcomes of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
+This paper analyzed conversational chatbots in an one-to-one setting, finding that learning really benefited from it.
+This is, once again, a proof of the benefit of chatbots in certain settings; however, there are some opinions that might prevent the successful acceptance of the technology, and these are what we are trying to find out in this paper, together with what kind of features would make its acceptance better.
+
+Besides, the present work is focused on the other key actor in this challenge, i.e.
+educators.
+Their attitudes have been studied very recently by Chocarro et al.
+\cite{doi:10.1080/03055698.2020.1850426}, who, by analyzing surveys, created a {\em technology acceptance model} that proposed a series of features that would make chatbots easier to accept; among them, formality of language as well as easiness and usefulness.
+The survey targeted primary and secondary education teachers, and was also more interested in the general use of chatbots in education, not specifically in a classroom setting, seeking educational outcomes.
+However, they establish a series of results that are obviously interesting and relevant for this work.
+
+We will present next the methodology we have followed to find out teachers' opinions.
 
@@
 
-\textcolor{black}{This study followed a quantitative approach towards addressing its research objective, by collecting rich data about the use of messaging applications and chatbots
-by educators in both universities and colleges\footnote{In Spain, they are called simply high schools, and deliver
-tertiary or associated degrees that do not have the consideration of university degrees}.
-To achieve this goal two online surveys were designed and developed using Google Forms
-in Spanish. They are comprised of six questions focusing on demographic data
-(i.e., sector, gender, degrees, discipline, age, teaching experience)
-followed by several multiple choice questions allowing the participants to choose multiple answers.}
-
-In the {\bf first survey}, the multiple choice questions are
-focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider
-useful for their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
-university and the other for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees). Questions and
-responses were the same, except for the type of tertiary degrees that
-were considered.}
-
-\textcolor{black}{This survey was piloted by the authors of the paper and their colleagues before using it in the 
-study.  All the comments collected from this trial were incorporated in the survey.
-We mainly used mailing lists, as well as Telegram groups,
-to post the survey link to reach out to more educators. The university form was sent to Spanish
-(mainly Andaluc\'{\i}a and Galicia) universities, and also  universities in Costa Rica and
-Mexico. The tertiary (non-university/college) teachers were based mainly in
-Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of
-2021, during the Covid-19 pandemic and while, at least in Spain, many universities had
-mandatory virtual teaching.}
-
-A total of 282 teachers responded to the survey: 193 teaching at the University
-(68.4\%) and 89 at other tertiary education institutions (31.6\%).
-\textcolor{black}{From those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%) and 5 teachers preferred not to indicate their gender (1.8\%).
-In terms of age, the majority of the participants (n=111) in this survey was 45-55 years old (39.4\%), while 91 teachers were 35-45 (32.3\%), 46 were 25-35 (16.3\%) and 34 teachers were older than 55 (12.1\%).
-Last, 84 teachers had a teaching experience of 16-25 years (29.8\%), 75 teachers 6-15 years of experience (26.6\%), 69 teachers had 0-5 years of experience (24.5\%) and finally, 54 teachers had more than 25 years of teaching experience (19.1\%).}
-
-Responses were stored automatically in a Google Drive spreadsheet. Eventually,
-the results from the two forms we used for the first survey were collated in a
-single spreadsheet. Survey questions are shown in Appendix I (Section \ref{app:questions}).
-
-The {\bf second survey} was designed after initial results to the first survey arrived,
-and pointed to necessities and experiences of teachers not being addressed by the first one; namely
-their experience with messaging platforms and the way they were used to interact with students.
-It was piloted in a group of university teachers attending to a formation course, and validated with them.
-It was then extended to the rest of the responders, using the same media: Telegram groups, email and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
-(Section \ref{app:questions}).
-
-A total of 205 teachers responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%).
-From those, 124 were male (60.5\%), 65 female (31.7\%) and 16 teachers preferred not to indicate their gender (7.8\%).
-In terms of age, the majority of the participants (n=70) was again, as in the first survey, 45-55 years old (34.1\%), while 67 teachers were 35-45 years old (32.7\%), 42 were 25-35 (20.5\%) and 26 teachers were older than 55 (12.7\%).
-In terms of teaching experience, 59 teachers had a teaching experience of 16-25 years (28.8\%), 51 teachers had 6-15 years (24.9\%) and 0-5 years of experience (24.9\%), and 44 teachers more than 25 years of teaching experience (21.5\%).
-
-\subsection{Survey validation}
-
-To avoid any bias and to be sure about the quality of the questionnaire, a panel board was consulted.
-There were three questions for each of the items of the questionnaire which were: Clarity, Importance, Adequateness.
-Clarity was measured as an answer to the question: Is the item well presented and without ambiguity?
-\footnote{Original text: ¿El ítem está bien redactado y sin ambigüedad?} with two choices: Yes or No.
-Both Importance and Adequateness were measured in a Likert scale from 1 to 4 (1 low, 4 high).
-
-The panel board was composed by 7 volunteer experts that have wide experience as educators and researchers. The results obtained are summarized in Table \ref{tab:validation}.
-
-As validation shows, all expert agree without any doubt about the clarity of each question.
-Furthermore, there is a large consensus regarding the Importance and Adequateness of all the eight questions in the questionnaire.
-
-\begin{table}
-\begin{tabular}{|c|ccc|}
-    \hline
-    Questions & Clarity (Yes/No) & Avg. Importance & Avg. Adequateness \\
-    \hline
-    Q1 &  Yes (100\%)  &  3,571 (0,53) & 3,571 (0,53) \\
-    Q2 &  Yes (100\%)  &  3,714 (0,49) & 3,571 (0,53) \\
-    Q3 &  Yes (100\%)  &  3,857 (0,38) & 3,857 (0,38) \\
-    Q4 &  Yes (100\%)  &  3,571 (0,79) & 3,857 (0,38) \\
-    Q5 &  Yes (100\%)  &  3,714 (0,49) & 3,714 (0,49) \\
-    Q6 &  Yes (100\%)  &  3,714 (0,49) & 3,857 (0,38) \\
-    Q7 &  Yes (100\%)  &  3,714 (0,49) & 3,714 (0,49) \\
-    Q8 &  Yes (100\%)  &  4 (0) & 4,000 (0) \\
-    \hline
-\end{tabular}
-\caption{Validation results from the panel board (7 experts) for each question in the research questionnaire.
-The range of values for Importance and Adequateness is from 1 to 4 (higher is better).}\label{tab:validation}
-\end{table}
-
-Next, we show the results and analyse them.
+Our intention from the beginning was to try and gather a sufficient amount of responses in all sectors, as well as cover different sectors of higher education.
+In doing so, an online survey was administered (i.e., Google Form), in Spanish, which was intended to be answered in a very short amount of time.
+Initially, our intention was to mirror the questions used in \cite{MoraChatbots2021}; however, an initial exploration of results led us to create a second survey.
+The survey items focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider useful to be used in their teaching, and the type of interactions that teachers prefer to have with their students while using messaging apps in their teaching.
+
+The {\bf initial survey} was done in two separate Google forms, one for university and other for tertiary non-university teachers.
+Questions and responses were the same, except for the type of tertiary degrees that were taught.
+In both cases, we used mainly mailing lists, as well as Telegram groups, to spread the link to the form.
+The university form was spread in Spanish (mainly Andaluc\'{\i}a and Galicia) universities, and also Costa Rica and Mexico.
+The tertiary non-university teachers are mainly in Andaluc\'{\i}a.
+Dissemination and answers took place in the first quarter of 2021, post-pandemic and while, at least in Spain, many universities had mandatory virtual teaching.
+A total of 282 teachers responded to the survey: 193 teaching at the University (68.4\%) and 89 at high school (31.6\%).
+
+All surveys had the same common, initial questions for segmentation:\begin{itemize}
+\item Degrees or titles where the teacher was working, either university or other tertiary education.
+\item Discipline: Engineering, Social Sciences, Health and Bio, Sciences, Humanities, Other.
+\item Gender: Man, Woman, Rather not say.
+\item Age: 25-35, 35-45, 45-55, more than 55.
+\item Experience on the job: up to 5 years, 5-15 years, 15-25 years, more than 25 years.
+\item Type of degree: university, other tertiary education. This question was implicit in the first survey, since one and the other filled different forms, it was explicit in the second survey.
+\end{itemize}
+
+% Including questions in surveys
+The {\bf first survey}, which focused about the use of messaging apps in class, and which tried to address mainly RQ2 and R23, includes the following questions:
+
+\textit{1. Regarding the use of messaging apps in class, you prefer ...}
+\begin{itemize}
+\item A chat group with the students in the same course
+\item Students self-organize and with the teacher not being part of any chat group
+\item A chat group with the all the students and teachers of the School/High-School/Faculty
+\item A chat group with all the students and teachers of the same study year
+\end{itemize}
+
+\textit{2. Which messaging app platform do you use to communicate with your peers or students?}
+\begin{itemize}
+\item Whatsapp
+\item Telegram
+\item LinkedIn
+\item Twitter messages
+\item Discord
+\item Slack
+\item Snapchat
+\item The platform provided by your own institution
+\item None, I do not use any messaging app to communicate with my students
+\end{itemize}
+
+\textit{3. Which kind of chatbots (software that automatically respond to questions or commands) could be useful to improve the learning results with your students or help you managing your course?}
+\begin{itemize}
+\item Agenda bots that e.g. remind students about project deadlines
+\item Bots that collect and provide answers to frequent questions
+\item Bots that inform students about their grades
+\item Bots that help with the class materials (e.g. searching for topics about a concept, or asking about them)
+\end{itemize}
+
+\textit{4. The virtualization of teaching due to the COVID pandemic during this year and the previous one, did it mean any change in your viewpoint or use of messaging apps in class?}
+\begin{itemize}
+\item No, I did use it before and use it now
+\item Yes, I started using safer alternatives
+\item Yes, I did not use any messaging platform before but I do use it now
+\item No, I did not use any messaging platform before or now
+\end{itemize}
+
+The {\bf second survey} followed the same paths, only in this case there was a single questionnaire, and with a different scope, focusing on the kind of interaction media features that teachers value the most.
+% Olia - see my comment above.
+It was filled by teachers that were also students in a teacher formation course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers who knew about it by emails from the authors, or from the vicedeanship for International Relations that included it in its newsletter.
+This means that there might be a higher proportion of 1) teachers with few years of experience 2) teachers from the computer science faculty and 3) teachers from Granada.
+We think, however that there's no explicit bias in this selection, although of course specific percentages will vary.
+These questions tried to address mainly RQ1 and RQ4.
+
+Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are  their feelings and preferences with regard to the use of instant messaging applications with students, and even using bots or chatbots in the classroom.
+In addition the survey asked about the most relevant \textit{interaction media features} for the teachers with respect to the potential tool to use in class.
+
+The specific questions included in this second survey are listed below:
+
+\textit{1. You prefer the interaction with your students to be ...}
+\begin{itemize}
+\item Synchronous: students and teacher/s in the same space, simultaneously.
+\item Asynchronous: the student asks at anytime, the teacher responds whenever possible.
+\end{itemize}
+
+\textit{2. Regarding the interaction with your students, you ...}
+\begin{itemize}
+\item Prefer it to be done by institutional means/tools: office hours, forum/messages via the virtual campus, institutional email
+\item Admit the use of other means/toosl: blogs, chat groups in messaging platforms, any others.
+\end{itemize}
+
+\textit{3. Which media features do you value the most for your interaction with your students?}
+\begin{itemize}
+\item Familiarity with its use i.e. that I do not need to learn a new tool
+\item The official formation/training provided by your institution on its use
+\item That only one-directional communication is allowed (from teachers to students)
+\item Non-hierarchical tools that allowed teacher-to-student and student-to-student communication 
+\item That allow additional functionalities such as interfaces to other tools
+\item That allow teachers to develop/add their own functionalities (e.g. automatic correction tools)
+\item That let me avoid to worry about maintenance and that it is easily sustainable from one year to the next
+\item That allow to extract data to assess the student performance
+\end{itemize}
+
+Responses were stored automatically in a Google Drive spreadsheet.
+Eventually, the results from the two forms we used for the first survey were collated in a single spreadsheet.
+Next we will show the results and analyze them.
 
@@
 % Describe the survey and population
-We collected responses from 282 teachers from Spain and Spanish Speaking
-countries for \textit{survey1} and 205 for \textit{survey2}. The two forms were
-open for approximately the same amount of time, around two months. The sample
-includes mostly teachers from university, although about 32\% and 8\% are from
-non-universitary tertiary education in the first and second survey respectively. Regarding
-gender, 61\% of the teachers were male and 32\% female, while approximately 5\%
-chose not to disclose it. Finally, the responses are more or less equally
-distributed according to the teaching experience, showing 24\% of responses from
-teachers with 5 or less years of experience, 26\% for 6-15 years of experience,
-30\% for 16-25, and 20\% for teachers with more than 25 years of experience.
-
-We will try to find the answers to the four research questions next, by
-analyzing the response to the different survey questions.
+We collected responses from 282 teachers from Spain and Spanish Speaking countries for the first survey (\textit{survey1} and 205 for the second one (\textit{survey2}).
+The two forms were open for approximately the same amount of time, around two months.
+The sample includes mostly teachers from university, although about 32\% and 8\% are from vocational education in the first and second survey respectively.
+Regarding gender, 61\% of the teachers were male and 32\% female, while approximately 5\% chose not to disclose it.
+Finally, the responses are more or less equally distributed according to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 26\% for 6-15 years of experience, 30\% for 16-25, and 20\% for teachers with more than 25 years of experience.
+
+% \begin{figure}[h!tbp]
+% \begin{center}
+%     \begin{minipage}[t]{0.3\textwidth}
+%         \centering
+% <<gender, echo=FALSE, fig.width=3.2, fig.height=2.5>>=
+% #ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+% freq.Gender$source<-rep("survey1")
+% freqInteraction.Gender$source<-rep("survey2")
+% freqbinded.Gender <- rbind(freq.Gender, freqInteraction.Gender)
+% freqbinded.Gender$source <- factor(freqbinded.Gender$source) 
+% freqbinded.Gender[as.character(freqbinded.Gender$Gender)!="No", ] -> df1
+% ggplot(df1, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+% @
+% 
+% %       \includegraphics[width=\textwidth]{figures/gender.pdf}
+%     \end{minipage}
+%     \begin{minipage}[t]{0.3\textwidth}
+%         \centering
+% <<age,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
+% #ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+% freq.Age$source<-rep("survey1")
+% freqInteraction.Age$source<-rep("survey2")
+% freqbinded.Age <- rbind(freq.Age, freqInteraction.Age)
+% freqbinded.Age$source <- factor(freqbinded.Age$source) 
+% freqbinded.Age[as.character(freqbinded.Age$Age)!="No", ] -> df1
+% ggplot(df1, aes(x = Age, y=freqAge, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+% @
+% 
+% %       \includegraphics[width=\textwidth]{figures/age.pdf}
+%     \end{minipage}
+%     \begin{minipage}[t]{0.3\textwidth}
+%         \centering
+% <<sector,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
+% #ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+% freq.Sector$source<-rep("survey1")
+% freqInteraction.Sector$source<-rep("survey2")
+% freqbinded.Sector <- rbind(freq.Sector, freqInteraction.Sector)
+% freqbinded.Sector$source <- factor(freqbinded.Sector$source) 
+% ggplot(freqbinded.Sector, aes(x = Sector, y=freqSector, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+% @
+% %       \includegraphics[width=\textwidth]{figures/sector.pdf}
+%     \end{minipage}
+%     \vspace{0.5mm}
+%     \begin{minipage}[t]{0.38\textwidth}
+%         \centering
+% <<experience, echo=FALSE, fig.width=4.5, fig.height=3.475>>=
+% #ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+% freq.Experience$source<-rep("survey1")
+% freqInteraction.Experience$source<-rep("survey2")
+% freqbinded.Experience <- rbind(freq.Experience, freqInteraction.Experience)
+% freqbinded.Experience$source <- factor(freqbinded.Experience$source) 
+% freqbinded.Experience[as.character(freqbinded.Experience$Experience)!="No", ] -> df1
+% ggplot(df1, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+% @        
+% %       \includegraphics[width=\textwidth]{figures/experience.pdf}
+%     \end{minipage}
+%     \begin{minipage}[t]{0.52\textwidth}
+%         \centering
+% <<discipline,echo=FALSE, fig.width=8.2, fig.height=4.45>>=
+% #ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
+% freq.Discipline$source<-rep("survey1")
+% freqInteraction.Discipline$source<-rep("survey2")
+% freqbinded.Discipline <- rbind(freq.Discipline, freqInteraction.Discipline)
+% freqbinded.Discipline$source <- factor(freqbinded.Discipline$source) 
+% freqbinded.Discipline$Discipline <- factor(freqbinded.Discipline$Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other"))
+% ggplot(freqbinded.Discipline, aes(x = Discipline, y=freqDiscipline, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
+% @
+% 
+% %       \includegraphics[width=\textwidth]{figures/discipline.pdf}
+%     \end{minipage}
+% \end{center}
+%     \caption{Sample population description.
+The responses from two surveys were collected amount to 282 for the first survey (\textit{survey1} in red) and 205 for the second (\textit{survey2} in blue).
+Data are shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
+% \label{figure:teachers_population}
+% \end{figure}
+
+% % Olia suggests to delete this, as well as figure 1.
+% Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar. %, and as a matter of fact,
+% Additionally, as a matter of fact, as Figure \ref{figure:age.vs.exp} shows, age and experience are correlated strongly, with experience being roughly 20-30 years less than age. 
+% This might indicate that a differential analysis for age and experience will not yield significant differences, except maybe in the 6-15 years experience group, which is spread over all ages.
+At any rate, experience seems to be the dominating factor here and we'll use experience only unless we detect some significant difference by age.
+
+% \begin{figure}[h!tbp]
+% \begin{center}
+% <<interaction,message=FALSE,echo=FALSE, fig.height=2.0, fig.width=4.0>>=
+% library(forcats)
+% survey.interaction %>%
+%     mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
+%     mutate(Experience = fct_relevel(Experience, "0-05 years", "06-15 years", "16-25 years", "> 25 years" )) %>%
+%     group_by( Age, Experience ) %>% summarise( n = n() ) %>% mutate( freq = n/sum(n)) -> Age.vs.Experience
+% 
+% ggplot(Age.vs.Experience,aes(Age,Experience))+geom_point(aes(size=freq),colour="green")
+% @
+% \end{center}
+% \caption{Correlation between age and experience.}
+% \label{figure:age.vs.exp}
+% \end{figure}
+
+Well try to find the answers to the four research questions next, by analyzing the response to the different survey questions.
 
@@
 
-Group messaging apps have become a powerful tool for \textcolor{black}{communicating} with
-students. Also, many of them have built-in chatbots to enhance the learning
-process. After an initial analysis to the answers to the first survey, we
-realized that there were some prior issues mainly related to the adoption of a
-technology, \textcolor{black}{i.e. chatbots}, that generally piggybacks on another, \textcolor{black}{i.e. messaging
-applications. Generally,} in a technology adoption model, perceived ease of use and
-perceived usefulness are essential. But it is going to be very difficult for
-teachers to find {\em chatbots} easy to use if they, previously, do not
-consider, or simply use, the messaging tools to which they are attached.
-
-This is why for answering RQ1, teachers were queried about whether they use
-messaging apps in their classes, specifically, Telegram, WhatsApp, Slack (an
-application used mainly in IT departments and software development), or any
-other messaging app, and whether they use messaging apps provided by their
-academic institution (see Table \ref{tab:use_messapps}).
-Overall, the majority of the teachers responded that they do use messaging apps
-in their classrooms, from which apps (or, more probably, messaging solutions) provided by the academic institution
-(n=159, 56\%) and WhatsApp (n=124, 44.0\%) were the most common responses. Only
-19 teachers (6.7\%) replied that they do not use any messaging app in their
-class.
+%Why messaging apps are relevant here --> connect to the development of chatbots
+Group messaging apps have become a powerful tool for keeping touch with students.
+Also, they are the baseline platform for the development of chatbots to help with the learning process.
+After an initial analysis to the answers to the first survey, we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally piggybacks on another, messaging applications.
+In a technology adoption model, perceived ease of use and perceived usefulness are essential.
+But it is going to be very difficult for teachers to find {\em chatbots} easy to use if they, previously, do not consider, or simply use, the messaging tools to which they are attached.
+
+This is why for answering RQ1, teachers were queried about whether they use messaging apps in their classes, specifically, Telegram, WhatsApp, Slack (an application used mainly in IT departments and software development), or any other messaging app, and whether they use messaging apps provided by their academic institution (see Table \ref{tab:use_messapps}).
+In this case, it is maybe in order a certain clarification.
+While we had in mind, as indicated by the possible answers, instant messaging applications when making this question, we included these institution-provided applications mainly for completitude.
+But it should be noted that, in most cases, they are not {\em instant} messaging apps in the way Telegram or Facebook Messenger are; in most cases they are messaging facilities provided by learning management systems such as (usually) Moodle.
+So the answer to this question must be understood in two different ways: their preference for the {\em source} of the technology (university, any company) as well as the {\em type} of technology (instant, app based messaging systems vs.
+web-based systems integrated in another learning management system).
+
+Overall, the majority of the teachers responded that they do use messaging apps in their classrooms, from which apps provided by the academic institution (n=159, 56\%) and WhatsApp (n=124, 44.0\%) were the most common responses.
+Only 19 teachers (6.7\%) replied that they do not use any messaging app in their class.
+%Remember to add something to the discussion below - JJ
 %
@@
 \vspace{0.8em}
-\caption{Use of messaging apps to assist the learning process.}
+\caption{Use of messaging apps in class}
 \label{tab:use_messapps}
@@
 % Fran: I think figures with data about the use of messaging apps should come here. Then, we say we also asked about changes after covid and include data about that
-Results in Figs. \ref{figure:provided*chatbots_use},
-\ref{figure:whatsapp*chatbots_use}, \ref{figure:telegram*chatbots_use} do not
-show significant differences in the use of instant messaging apps between
-teachers from University and vocational education. In general, most teachers
-prefer messaging apps provided by their own institutions (we also show the
-results for the two most popular messaging app platforms: WhatsApp and
-Telegram). With respect to specific disciplines, Engineering and Technology
-teachers are more active in their use, but the number of teachers from Humanities 
-who answered they used these apps in their classes is also remarkable
-(around 60\% use the apps provided by their institutions).
-
-Although no significant differences were found regarding gender, female teachers
-answered they use instant messaging apps more than male teachers (about 10\%
-more). Also, teachers in vocational Education use WhatsApp more than university
-teachers. Regarding the distribution of the use of messaging apps per age, there
-are no significant differences for WhatsApp and apps provided by their own
-academic institutions. % Olia requests support for this. 
-However, younger teachers also use Telegram with more than 25\% responding they do, a percentage
-that falls to about 10\% for teachers that are 55 or older. %The third column
-                                %compares the use of these apps considering the
-                                %number of years of experience.
-One interesting result is that about 65\% of teachers with more than 25 years of
-experience use the platforms provided by their institutions while the percentage
-goes down to less than 50\% for teachers with 6-15 years of experience.
+Results in Figs.
+\ref{figure:provided*chatbots_use}, \ref{figure:whatsapp*chatbots_use}, \ref{figure:telegram*chatbots_use} do not show significant differences in the use of instant messaging apps between teachers from University and vocational education.
+In general, most teachers prefer messaging apps provided by their own institutions (we also show the results for the two most popular messaging app platforms: Whatsapp and Telegram).
+With respect to specific disciplines, Engineering and Technology teachers are more active in their use, although it is also relevant the amount of teachers from Humanities that answered they used these apps in their classes (around 60\% use the apps provided by their institutions).
+
+Although no significant differences were found regarding gender, female teachers answered they use instant messaging apps more than male teachers (about 10\% more).
+Also, teachers in vocational Education use WhatsApp more than university teachers.
+Regarding the distribution of the use of messaging apps per age, there are no significant differences for WhatsApp and apps provided by their own academic institutions.
+% Olia requests support for this.
+However, younger teachers also use Telegram with more than 25\%, a percentage that falls to about 10\% for teachers that are 55 or older.
+%The third column compares the use of these apps considering the number of years of experience.
+One interesting result is that, contrary to the idea of technology adaptation issues when considering older teachers, about 65\% of teachers with more than 25 years of experience use the platforms provided by their institutions while the percentage goes down to less than 50\% for teachers with 6-15 years of experience.
 %
@@
 survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformProvided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Experience, levels=c("0-05 years","06-15 years", "16-25 years", "> 25 years")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+ggplot(df1, aes(x = MessagingPlatformProvided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @       
@@
 \end{center}
-    \caption{Use of messaging platforms either external or provided by the teachers' academic institutions in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}
+    \caption{Use of chatbots provided by the teachers' academic institutions in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}
     \label{figure:provided*chatbots_use}
@@
 survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Experience, levels=c("0-05 years","06-15 years", "16-25 years", "> 25 years")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @       
@@
 survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformTelegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Experience, levels=c("0-05 years","06-15 years", "16-25 years", "> 25 years")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+ggplot(df1, aes(x = MessagingPlatformTelegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @       
@@
 % This is about changes (due to) after covid
-Some of the questions in the survey were focused on the impact of the COVID19
-pandemic between the 2020 and 2021 academic years in the teachers' attitudes towards the use of
-instant messaging apps in their class. Our main intention in this case was to
-assess whether a crisis will bring about some kind of change in the use of
-tools. The 282 answers are summarized in
-Figs. \ref{figure:gender*chatbots_use_postcovid},
-\ref{figure:sector*chatbots_use_postcovid},
-\ref{figure:years*chatbots_use_postcovid},
-\ref{figure:disc*chatbots_use_postcovid}, showing that about 77\% of teachers
-already used these tools before the pandemic and kept using them during the
-pandemic lockdowns that forced students and educators to use remote education
-schemes. Moreover, approximately 15\% of them switched their messaging app for
-one that offered a safer interaction with their students. According to the
-responses, an additional 16\% started using messaging apps during the pandemic
-for the first time in their classes. % Aggregating the answers, currently 91\% of
-% the teachers are using messaging apps as learning tools.
+Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' viewpoints towards the use of instant messaging apps int their class.
+Our main intention in this case was to assess whether a crisis will bring about some kind of change in the use of tools.
+The 282 
+% Fran, please check Olia's comment as having 282 answers 
+% -> I did remove some responses that Olia considered 'No' by default (i guess). I' ll keep it to 282 to be consistent
+answers are summarized in Figs.
+\ref{figure:gender*chatbots_use_postcovid}, \ref{figure:sector*chatbots_use_postcovid}, \ref{figure:years*chatbots_use_postcovid}, \ref{figure:disc*chatbots_use_postcovid}, showing that about 77\% of teachers already used these tools before the pandemic and kept using them during the pandemic lockdowns that forced students and educators to use remote education schemes.
+Moreover, approximately 15\% of them switched their messaging app for one that offered a safer interaction with their students.
+According to the responses, an additional 16\% started using messaging apps during the pandemic for the first time in their classes.
+Aggregating the answers, currently 91\% of the teachers are using messaging apps as learning tools.
 %A few relevant facts from the collected data: teachers with 16-25 years of experience seem more worried about the security of messaging apps and teachers with up to 5 years of experience were more open to adopt messaging apps due to the pandemic; female teachers were more willing to adopt new platforms due to the pandemic, and even to start using safer alternatives; finally, university teachers that did not use them were more reluctant to start using them after the pandemic.
@@
 \vspace{0.8em}
-\caption{Sector * post-covid changes cross-tabulation}
+\caption{Sector * post-covid changes crosstabulation}
 \label{tab:sector*covid}
@@
 
-The majority of the teachers (n=165) mentioned that no changes in their habits occurred due to the emergency remote teaching, as the use of messaging apps was part of their teaching practices and remains the same, from which 105 teachers come from the university, and 60 teachers from the non-universitary tertiary sector.
+The majority of the teachers (n=165) mentioned that no changes in their habits occured due to the emergency remote teaching, as the use of messaging apps was part of their teaching practices and remains the same, from which 105 teachers come from the university, and 60 teachers from the vocational sector.
 The relationships between changes in the use of messaging apps, due to the covid-19 pandemic, and the instructors’ discipline, $X^{2}_{(24, N = 282)} = 44.856$, $p =0.006$, as well as the gender, $X^{2}_{(8, N = 282)} = 16.249$, p= 0.039 were also significant.
@@
 % Olia - TODO: check for repetitions in the following paragraph that you added. thank you.
-Finally, we took a closer look at the post-covid changes and the variables
-gender, sector, and discipline for which the chi-square test is statistically
-significant as shown in Figures \ref{figure:gender*postcovid_chisq},
-\ref{figure:sector*postcovid_chisq}, \ref{figure:discipline*postcovid_chisq}
-respectively. Each figure shows on the left, a graph that represents the
-Pearson's residuals of the chi-square test results and a table on the right part
-that shows the contribution of each cell to the test. In the Pearson's residual
-graphs, \textcolor{black}{the responses to the question about the use of messaging apps were shortened for the sake of clarity according to}: 1)
-\textit{Did/do} stands for \textit{Yes, I did use it before and do use it now};
-2) \textit{Didn't/do} for \textit{Yes, I didn’t use any messaging app before,
-  but do use it now}; 3) \textit{safer} for \textit{Yes, I use a safer messaging
-  app now}; 4) \textit{Didn't/Don't} for \textit{No, I didn’t use it before and
-  don’t use it now}.
+Finally, we took a closer look at the post-covid changes and the variables gender, sector, and discipline for which the chi-square test is statistically significant as shown in Figures \ref{figure:gender*postcovid_chisq}, \ref{figure:sector*postcovid_chisq}, \ref{figure:discipline*postcovid_chisq} respectively.
+Each figure shows on the left, a graph that represents the Pearson's residuals of the chi-square test results and a table on the right part that shows the contribution of each cell to the test.
+In the Pearson's residual graphs, the responses were shortened for the sake of clarity according to: 1) \textit{Did/do} stands for \textit{Yes, I did use it before and do use it now}; 2) \textit{Didn't/do} for \textit{Yes, I didn’t use any messaging app before, but do use it now}; 3) \textit{safer} for \textit{Yes, I use a safer messaging app now}; 4) \textit{Didn't/Don't} for \textit{No, I didn’t use it before and don’t use it now}.
 %
@@
 
-As mentioned, the graphs on the left hand side represent the Pearson's
-residuals, showing the difference between the observed and the expected values
-for each cell. Thus, large residuals indicate that variables are not truly
-independent. In our case, the blue shows positive contributions and red negative
-contributions to the test. Moreover, the saturation shows how large the
-contribution is in contrast to the expected value by chance. Additionally,
-tables on the right side show adjusted standardized residuals that according to
-\cite{agresti2013categorical}, if greater than +/-2 for cases with few cells,
-indicate lack of fit of $H_0$ (in boldface in our table). Complementary, the
-table also shows the percentage of contribution to the test of each cell
-(highest percentage per column also in boldface).
-
-Regarding gender in Fig. \ref{figure:gender*postcovid_chisq}, the results show a
-high positive contribution from female educators that did not use a messaging
-app before the COVID-19 pandemic but do use it now; approximately 31\% of the
-test results are explained by this cell. In contrast, male educators that
-respond the same were less than expected (negative contribution that explains
-17\% of the test results). Also, it is important to highlight the female
-educators that kept using these apps before and after the pandemic and
-correspondingly the negative contribution of male educators to the same case
-(less than expected by chance).
+As mentioned, the graphs on the left hand side represent the Pearson's residuals, showing the difference between the observed and the expected values for each cell.
+Thus, large residuals indicate that variables are not truly independent.
+In our case, the blue shows positive contributions and red negative contributions to the test.
+Moreover, the saturation shows how large the contribution is in contrast to the expected value by chance.
+Additionally, tables on the right side show adjusted standardized residuals that according to \cite{agresti2013categorical}, if greater than +/-2 for cases with few cells, indicate lack of fit of $H_0$ (in boldface in our table).
+Complementary, the table also shows the percentage of contribution to the test of each cell (highest percentage per column also in boldface).
+
+Regarding gender in Fig.
+\ref{figure:gender*postcovid_chisq}, the results show a high positive contribution from female educators that did not use a messaging app before the COVID-19 pandemic but do use it now; approximately 31\% of the test results are explained by this cell.
+In contrast, male educators that respond the same were less than expected (negative contribution that explains 17\% of the test results).
+Also, it is important to highlight the female educators that kept using these apps before and after the pandemic and correspondingly the negative contribution of male educators to the same case (less than expected by chance).
 
@@
 %
-Finally, statistical significance was found for the discipline and post-covid
-changes. Regarding disciplines (see
-Fig. \ref{figure:discipline*postcovid_chisq}), the number of educators from
-Humanities and Social Sciences that started using messaging apps after the
-pandemic is larger than expected and these number of responses explains about
-19\% of the chi-square test results. Also, the number of educators from
-Technology or Engineering that started using safer alternatives \footnote{This addresses the issue of insecure/unsafe applications which do not encrypt messages or can be easily compromised exposing information} are less than
-expected (compared to the educators from other disciplines). Bear in mind that
-some disciplines were merged to avoid very low number of responses for some of
-the cells.
+Finally, statistical significance was found for the discipline and post-covid changes.
+Regarding disciplines (see Fig.
+\ref{figure:discipline*postcovid_chisq}), the number of educators from Humanities and Social Sciences that started using messaging apps after the pandemic is larger than expected and these number of responses explains about 19\% of the chi-square test results.
+Also, the number of educators from Technology or Engineering that started using safer alternatives are less than expected (compared to the educators from other disciplines).
+Bear in mind that some disciplines were merged to avoid very low number of responses for some of the cells.
 
@@
 
-The most favorable use case for chatbots in
-Higher Education and vocational training is their use for the facilitation of an
-agenda formation (171 positive response, 60.6\%), followed by the FAQs use case
-(148 positive responses, 52.5\%) and the sharing class material use case (136;
-48.2\%). A chi-square test of independence was performed to examine the relation
-among participants’ preferences for particular chatbot use cases. Out of the 171 teachers who consider useful the use of
-chatbots for agenda preparation in the class, 103 also consider useful chatbots’
-use for FAQs. The relation between agenda and the FAQs use case was significant, $X^{2}_{(1, N = 282)} =
-10.467$, $p =0.001$. The frequencies cross tabulated are given in Table
-\ref{tab:agenda*faq}.
+For the findings it occurs that the most favourable use case for chatbots in Higher Education and vocational training is their use for the facilitation of an agenda formation (171 positive response, 60.6\%), followed by the FAQs use case (148 positive responses, 52.5\%) and the sharing class material use case (136; 48.2\%).
+A chi-square test of independence was performed to examine the relation among participants’ preferences for particular chatbot use cases.
+The relation between agenda and the FAQs use case was significant, $X^{2}_{(1, N = 282)} = 10.467$, $p =0.001$.
+The frequencies cross tabulated are given in Table \ref{tab:agenda*faq}.
+Out of the 171 teachers who consider useful the use of chatbots for agenda preparation in the class, 103 also consider useful chatbots’ use for FAQs.
 
@@
 
-Answers to these questions are plotted in
-Figs. \ref{figure:gender*chatbots_types}, \ref{figure:sector*chatbots_types},
-\ref{figure:experience*chatbots_types}, \ref{figure:disc*chatbots_types} grouped
-by gender, sector, years of experience in education, and discipline
-respectively. As it was a multiple choice question, the counts are over the
-total number of people that answered.
+Answers to these questions are plotted in Figs.
+\ref{figure:gender*chatbots_types}, \ref{figure:sector*chatbots_types}, \ref{figure:experience*chatbots_types}, \ref{figure:disc*chatbots_types} grouped by gender, sector, years of experience in education, and discipline respectively.
+As it was a multiple choice question, the counts are over the total number of people that answered.
 
@@
 
-Since chatbots are intended to mediate or help in this interaction, it is
-essential to understand the kind of interaction teachers prefer. Chatbots should
-address those modes, and not others. In order to find out these modes, and thus
-answering RQ3, teachers were provided with a list of different kind of
-interactions that may take place among students and between students and the
-teacher, with the use of messaging apps. The findings are summarized in Table
-\ref{tab:kindinteractions}.
+%Olia - move figure 7 elsewhere, not at the beginning of this section (RQ3). 
+Since chatbots are intended to mediate or help in this interaction, it is essential to understand the kind of interaction teachers prefer.
+Chatbots should address those modes, and not others.
+In order to find out these modes, and thus answering RQ3, teachers were provided with a list of different kind of interactions that may take place among students and between students and the teacher, with the use of messaging apps.
+The findings are summarized in Table \ref{tab:kindinteractions}.
 
@@
 
-As it can be seen by the answer to the first and last question, in general
-teachers do not want to participate in a chat group with students; either they
-want to simply leave the students alone in their own chat group, or otherwise
-they prefer not to be part of that interaction. In general, that is going to be
-the case no matter what; it is well known that students organize their own chat
-groups with many (and not always conveyable) intentions, so teachers do not want
-to take any part in these informal or non institutionally-supported chat
-groups. Overwhelmingly, they do not want to participate in these kind of chat
-groups with students, but even less so if it includes the rest of the faculty.
-
-The answer, then, to this research question, is that, in general, teachers do
-{\em not} want to have interaction with students in a chat group. To a certain
-point, this would seem to contradict results \cite{gachago2015crossing}, although this might be due to cultural
-attitudes, or other factors such as the average size of classes. It does
-confirm, however, that the challenges cited in that study, and possibly others,
-are an obstacle to the adoption of mobile (and other) instant messaging among
-the community of surveyed teachers.
-
-Regarding the social factor of chat groups that teachers use in class, according
-to Fig. \ref{figure:chatbots_messagingorganization} the vast majority prefer
-small groups only with the students from the same course. These are more focused
-groups with specific goals and dedicated to the organization of the course and
-its tasks, and from the pedagogic point of view \textcolor{black}{it also seems more appropriate to improve
-the learning process}. Interestingly, and as a cross-check of the answers above,
-about 30\% of teachers consider they should not be part of the chat group. This
-might seem to contradict the results of the other survey, but in fact, being a
-result of different surveys, to a certain point affirms the same thing: there is
-a great amount of teachers that would be against being in a chat group with
-students. \textcolor{black}{However, students will still need to get the services
-that the university, through chatbots, provide, thus opening the door for deployment of chatbots
-without the intervention of the professor, simply tapping university provided
-services \cite{bernier2002services}.}
-Whether that's a slim majority or not, that's open to debate (and
-would probably need a more pointed survey focused on this), but what is clear is
-that forcing teachers to create chat groups with students and participate in
-them would create a certain amount of resistance. Also, only university teachers
-find interesting a group with all the students and teachers in their own Faculty
-or School. The lack of teachers from vocational education here may be the
-consequence of using specific language such as ``Faculty''. Moreover, the fact
-that many universities and schools already use these groups for administrative
-and social interaction (e.g. \cite{dibitonto2018chatbot}) might be the reason
-for the low percentage of teachers that selected this response.
+As it can be seen by the answer to the first and last question, in general teachers do not want to participate in a chat group with students; either they want to simply leave leave the students alone in their own chat group, or otherwise they prefer not to be part of that interaction.
+In general, that is going to be the case no matter what; it is well known that students organize their own chat groups with many (and not always conveyable) intentions, so teachers do not want to take any part in it.
+Overwhelmingly, they don't want to participate in any chat group with students, but even less so if it includes the rest of the faculty.
+
+The answer, then, to this research question, is that, in general, teachers do {\em not} want to have interaction with students in a chat group.
+To a certain point, this would seem to contradict results by Gachago et al.
+\cite{gachago2015crossing}, although this might be due to cultural attitudes, or other factors such as the average size of classes.
+It does confirm, however, that the challenges cited in that study, and possibly others, are an obstacle to the adoption of mobile (and other) instant messaging among the community of surveyed teachers.
+
+Regarding the social factor of chat groups that teachers use in class, according to Fig.
+\ref{figure:chatbots_messagingorganization} the vast majority prefer small groups only with the students from the same course.
+These are more focused groups with specific goals and dedicated to the organization of the course and its tasks, and from the pedagogic point of view seem more appropriate to improve the learning process.
+Interestingly, and as a cross-check of the answers above, about 30\% of teachers consider they should not be part of the chat group.
+This might seem to contradict the results of the other survey, but in fact, being a result of different surveys, to a certain point affirms the same thing: there is a great amount of teachers that would be against being in a chat group with students.
+Whether that's a slim majority or not, that's open to debate (and would probably need a more pointed survey focused on this), but what is clear is that forcing teachers to create chat groups with students and participate in them would create a certain amount of resistance.
+Also, only university teachers find interesting a group with all the students and teachers in their own Faculty or School.
+The lack of teachers from vocational education here may be the consequence of using specific language such as "Faculty".
+Moreover, the fact that many universities and schools already use these groups for administrative and social interaction (e.g.
+\cite{dibitonto2018chatbot}) might be the reason for the low percentage of teachers that selected this response.
 
@@
 <<experience_sync, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Experience, levels=c("0-05 years","06-15 years", "16-25 years", "> 25 years"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
 @
@@
 
-%A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
+This question is mainly answered in the second survey, which, as indicated previously, was designed after initial analysis of the first.
+The kind of interaction is essential to design proper chatbots, or to deploy a technology instead of others; it is related to the perceived usefulness in a technology acceptance model.
+Essentially, if some new chatbot application does not have what teachers perceive as useful for their purposes, they are unlikely to adopt it.
+So knowing these opinions is quite important, and is the reason why we included it in the second survey.
+
+A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
 The majority of the teachers were aged 45-55 years old (70; 34.1\%), followed by individuals aged 35-45 (67, 32.7\%), and 25-35 (42; 20.5\%), while the minority was aged $>$~55 years old (26; 12.7\%).
 In terms of teaching experience, 59 teachers (28.8\%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9\%), 0-5 years (51; 24.9\%) and more than 25 years of experience (44; 21.5\%).
-The teachers were asked about what kind of interaction media features they value the most \textcolor{black}{; i.e.
-what their preferred features are in the applications/tools that they use to interact with their students.} The frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
+This age distribution is not different from the usual in the Spanish university, which has lately aged due to several reasons, so the answers we obtain can, in principle, be extrapolated to the population at large, at least in this sense.
+
+The teachers were asked about what kind of features of the messaging system they value the most; the frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
 
@@
 \vspace{0.8em}
-\caption{Interaction media features valued by teachers. Details about each of these features can be read in Appendix I (Section \ref{app:questions}, second survey).}
+\caption{Messaging platform features valued by teachers}
 \label{tab:interaction}
 \end{table}
-
-\textcolor{black}{As it can be seen in the table, the bulk of responders express their wish to use a sustainable and official application, i.e.
-both being approved or provided by the University (or the educational center), and also maintained by the technical staff of the center instead of giving this responsibility/task to the teacher.
-In addition, it is very important for the teachers that the used tools that all the members of the class communicate, including themselves; as well as being already known or used in everyday tasks, e.g.
-Telegram or WhatsApp.}
 
@@
 Columns and rows with no significant interaction have been suppressed for clarity.
-Every cell value represents $X^{2}_{(1, N = 205)}$.
-Details about each feature can be read in Appendix I.}
+Every cell value represents $X^{2}_{(1, N = 205)}$.}
 \label{tab:interactionfeatures}
@@
 
-Finally, a two-step cluster analysis was conducted, with a log-likelihood
-distance measure adopted, to explore how the use cases could be grouped based on
-their preferences of specific interaction media features, and which features
-have larger predictor importance for the clustering (see
-Fig. \ref{figure:predictor}). Two clusters occurred from the analysis: cluster 1
-(n=78, 60.9\%) is formed with instructors who did not value interaction media
-pluggability, connectivity, official formation, but valued interaction media
-analytics, familiarity, support by the institution; cluster 2 (n=50,
-39.1\%) groups instructors that did not value media
-analytics, official formation, familiarity, but valued pluggability,
-connectivity, and support by the institution. Interaction media pluggability
-appears to have the most important predictor importance in the clustering of
-cases (predictor importance = 1.0), whilst media unidirectionality was the least
-important factor (predictor importance = 0.04). The cluster quality is fair, but
-not a good one (silhouette measure of cohesion and separation).
+Finally, a two-step cluster analysis was conducted, with a log-likelihood distance measure adopted, to explore how the cases could be grouped based on their preferences of specific interaction media features, and which features have larger predictor importance for the clustering (see Fig.
+\ref{figure:predictor}).
+Two clusters occurred from the analysis: cluster 1 (n=78, 60.9\%) was comprised of instructors who did not value interaction media pluggability, connectivity, official formation, but valued interaction media analytics, familiarity, support by the institution, while cluster 2 (n=50, 39.1\%) was comprised of instructors from which the majority did not value media analytics, official formation, familiarity, but valued pluggability, connectivity, and support by the institution.
+Interaction media pluggability appears to have the most important predictor importance in the clustering of cases (predictor importance = 1.0), whilst media unidirectionality was the least important factor (predictor importance = 0.04).
+The cluster quality is fair, but not a good one (silhouette measure of cohesion and separation).
 
@@
 \begin{center}
-\includegraphics[width=\textwidth]{figures/2clusteranalysis.pdf}
+\includegraphics[width=\textwidth]{figure/2clusteranalysis.pdf}
 \end{center}
@@
 % ********************** Discussion section *******************
-\section{Discussion and implications}
-
-Our initial intention in the design of these surveys was to probe the opinions
-of tertiary education teachers in the introduction of chatbot technologies in
-class. We wanted to find the answer to four research questions, of which the
-first was to check whether teachers already used some kind of messaging
-application, and the one they preferred. Depending on the answer, different
-technologies could be (or not) available for the introduction of chatbots. In
-this case, the design of the survey introduced some ambiguity on what we really
-consider ``messaging technology'', that was eventually resolved by the answers;
-apparently, anything that sends messages (even if they are not instant, even if
-they do not have a dedicated application) was the concept in the mind of the
-surveyed.  \textcolor{black}{In this case, we would like 
-to add a clarification. While we had in mind, as indicated by the possible answers, 
-instant messaging applications when we elaborated this question,
-we included these institution-provided applications mainly for completion. But
-it should be noted that, in most cases, they are not {\em instant} messaging
-apps in the way Telegram or Facebook Messenger are; in most cases they are
-messaging facilities provided by learning management systems such as (usually)
-Moodle. So the answer to this question must be understood in two different ways:
-their preference for the {\em provider} of the technology (the university itself, any
-company) as well as the {\em type} of technology (instant, app based messaging
-systems vs. web-based messaging systems integrated in another learning management system).}
-
-This inclusion of university-provided messaging applications in
-the survey might explain why there are so few, just 6.7\%, that answer they do not 
-use any messaging application. In general, universities provide official channels
-to communicate with students official academic information such as the exam schedule
-or the grades. The statistical mode is to use that kind of messaging. Some other
-people might not use it, but use some extraofficial or opt-in channels such as the other included in the survey; at the end, between these official and extraofficial channels most people cover their needs to communicate with students.
-This matches
-our subjective experience, in general.
-
-Additionally, the question on COVID reflected the big challenge that represents
-changing habits, even in the case of a major crisis. Very few responders actually
-changed their habits, although comparing women vs. men as well as those teaching social
-sciences show some significant difference. We do not have any kind of explanation for
-this behavior, other than technologies are perceived, and adopted, in a
-different way depending on background and, apparently, gender.
-
-One of the most interesting questions that can arise from the analysis of the
-results, and that should require further study, is: Are teachers really aware
-of the possibilities of chatbots in the classroom? The survey 
-only listed a few functionalities for the chatbots and just a few subjects selected 
-the option "Others". This may suggest  that most teachers did not really understand 
-at this point the actual potential of chatbots, since the responses listed were by no means exhaustive, and if the responders were more acquainted with the possibilities of the technology, possibly this response would have shown up many more times.
-Another way to look about it is
-that, unless you provide the specific instructions on how to use a
-tool, the teaching staff is already too busy or burn out to think about
-innovation.
-
-We can speculate that their opinions towards chatbots are informed by negative
-experiences with customer support chatbots, which is what most people will have
-experienced. This will probably require further study, but also will need to be
-taken into account when introducing chatbot technologies in the classroom: 
-it will have to be as simple, and as satisfactory, as possible, 
-to (possibly) change this existing perception.
-
-Regarding gender grouping, both genders agree in their uses, so it seems not
-relevant at all. When looking at the plot containing the sector differentiation
-it is interesting to observe how university teachers prefer in a higher
-proportion to use them for grades and FAQs in comparison with other tertiary education teachers. 
-This seems reasonable as the frequency of seeing the students
-is lower at the University so, an automatic tool for grade notification for
-continuous evaluation seems more helpful. 
-Furthermore, the high student/teacher
-ratios that university teachers have to deal with could be another reason to
-have a higher number of them willing to use chatbots for FAQs. This could
-ameliorate the number of misunderstandings and email overload that so many
-students might generate.
-
-The results, when grouping by experience, confirm that
-experienced teachers are not afraid of changes and are willing to accept new
-technological challenges; at least, in the same way that younger teachers
-are. From this concrete plot it is interesting as well to observe the fact that very few
-young/inexperience teachers are willing to use chatbots for other uses. This
-reinforces the hypothesis thrown at the beginning of this section that younger
-teachers have less experience to consider new ways of using chatbots in their daily work.
-
-As it appears in the responses presented above, teachers’ responses are equally
-distributed between positive and negative in relation to the media features:
-analytics, connectivity, and hidden phone number; that is, none of them is a
-prevailing factor on choosing one technology over another. However, for the features: familiarity,
-horizontally, sustainability and officiality the majority provided a positive
-response, designating their preference to these features. On the other hand, the
-majority of teachers seems to consider not valuable the presence of official
-formation, pluggability, unidirectionality and synchrony in the interaction
-media features of messaging apps.
+\section{Discussion}
+
+% Add something about intro
+% RQ1 discussion about messaging app: they consider a IM the Moodle messaging
+% Olia: it's not so easy to change habits, even in the case of major crisis. - JJ
+% Relationship between changes, gender and discipline (Olia) - JJ
+% 
+Our initial intention in the design of these surveys was to probe the opinions of tertiary education teachers in the introduction of chatbot technologies in the class.
+We wanted to find the answer to four research questions, of which the first was to check whether teachers already used some kind of messaging application, and the one they preferred.
+Depending on the answer, different technologies could be (or not) available for the introduction of chatbots.
+In this case, the design of the survey introduced some ambiguity on what we really consider "messaging technology", that was eventually resolved by the answers; apparently, anything that sends messages (even if they are not instant, even if they don't have a dedicated application) was the concept in the mind of the surveyed.
+
+Additionally, the question on COVID reflected the big challenge that represents changing habits, even in the case of a major crisis.
+Very few people actually changed, with women vs.
+men being an exception, as well as those teaching social sciences standing out among the rest.
+We don't have any kind of explanation for this behavior, other than technologies are perceived, and adopted, in a different depending on background and, apparently, gender.
+
+% Olia: we have something for RQ 2 and 4.
+ One of the most interesting questions that can arise from the plots, and the should require further study, is: Are teachers really aware of the possibilities of chatbots in the classroom?
+The reason to ask ourselves this question is due to the fact of the small number of responses for other uses in comparison with the other approaches proposed.
+Another way to look about it is that, unless you provide the specific instructions on how to use a tool, the teaching staff is already too busy or burn out to think about innovation.
+
+% Noorhan comments negative experience with customer service chatbots, in which case people will not see the value of using it in their classes.
+They are not aware of something like that.
+Teaching chatbots are difficult to develop.
+Using very simple chatbots, or simply conversational interfaces, could help introduce this technology - JJ
+
+Regarding Gender grouping, both gender agree in their uses, so it seems not relevant at all.
+When looking at the plot containing the sector differentiation it is interesting ot observe how university teachers prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational/High School teachers.
+This seems reasonable as the frequency of seeing the students is smaller at the University so, automating the grade notification for continuous evaluation could seem much more comfortable using an automated tool than using the traditional platform.
+Furthermore, the high student/teacher ratios that university docents have to deal with could be another reason to have a higher number of them willing to use chatbots for FAQs.
+This could ameliorate the number of misunderstandings and email overload that so many students might generate.
+
+The results, when grouping by experience, confirm the previous observation that experienced teachers are not afraid of changes and are willing to accept new technological challenges, at least, in the same way that younger teachers are.
+From this concrete plot it is interesting as well the fact that very few young/inexperience teachers are willing to use chatbots for other uses.
+This reinforces the hypothesis thrown at the beginning of this section and, as these teachers have less experience, they also have less field of view to think about ways of using chatbots.
+
+As it appears in the responses presented above, teachers’ responses are distributed between positive and negative in relation to the media features: analytics, connectivity, and hidden phone, while for the features: familiarity, horizontally, sustainability and officiality the majority provided a positive response, designating their preference to these features.
+On the other hand, the majority of teachers seems to consider not valuable the presence of official formation, pluggability, unidirectionality and synchrony in the interaction media features of messaging apps.
 
@@
 \begin{itemize}
- \item Teachers want to have support from their corresponding institution. This
-   is probably due to the strict European data regulations \textcolor{black}{on data protection},
-   but also to avoid the overhead required to \textcolor{black}{sign up new students every year.
-   In general support from specific formation and access to IT help desk for specific features
-   enhances the possibility of adoption by the teachers or the possibility of a successful
-   adoption that improves the learning outcomes. This is supported by the result of the two
-   surveys: they prefer whatever "messaging" application is provided by the university, and
-   also they value sustainability as well as "officiality" of the platform, as shown in
-   Table \ref{tab:interaction}}.
- \item Teachers need sustainability. The main reason is that implementing
-   changes is expensive in terms of effort and prone to errors in the first
-   years of implementing new procedures, therefore, it is logical that if
-   chatbots or messaging platforms are to be introduced, they want this change
-   to be as permanent as possible.
+ \item Teachers want to have support from their corresponding institution.
+This is probably due to the strict European data regulations and to avoid the overhead required to sing up and deleting students from year to year.
+
+ \item Teachers need sustainability.
+The main reason is that implementing changes is expensive in terms of effort and prone to errors in the first years of implementing new procedures, therefore, it is logical that if chatbots or messaging platforms are to be introduced, they want this change to be as permanent as possible.
+
  \item Keep it Simple.
@@
 
-An analysis of survey questions related to RQ4 seems to indicate that teachers
-prefer to share an interaction space with their student, as 
-shown in Tables \ref{tab:kindinteractions} and \ref{tab:interaction}, where a majority of responders
-indicate they {\em don't} want unidirectional communication; a preference of
-{\em horizontal} interaction, but also the answer to the kind of
-chatbots preferred that features FAQ bots prominently, which might indicate a
-need to delegate or offload part
-of the burden of answering, and attending, every single question posed by
-students. In an horizontal setting, other students can answer if the teacher
-does not do it immediately. This might also be the reason why the possibility of
-using tools from which analytics can be extracted is also valued by teachers:
-that way, activity in the chat tool, answering questions, regularity, can all be
-observed and valued as part of the process of assessing achievement of learning
-objectives by students.
-
-% Only some COVID-response relationship.
-In our survey, we could not find an answer about the right moment for introducing chatbot technologies. Response to questions related to change of
-behavior during and after the first stay at home, stage of the pandemic do not suggest that a major (or minor)
-crisis could be an opportunity to introduce new technologies, since it does not
-bring major changes in attitude (as a minor "crisis" we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in
-  Spain, every 10 years or so.}), or simply introduction of new degrees. Although
-changes driven by external forces do offer the chance of piloting new technologies, they do not
-seem to bring internal changes in attitudes in the teaching staff (which, after all, is
-bound to be the same). In absence of a clear answer in this direction, the right
-moment to introduce new technologies is always when the IT and managing staff is
-ready to support it (since, as we have seen before, "official" support is one of
-the factors that is most valued by teachers).
+% Rq4: they seem to prefer interaction with students - Olia 
+% Alberto: using new metric so grade students, and also abotu horizontality
+%
+
+The clustering analysis in RQ4 seems to reflect the possible overrepresentation of teachers in the techonology discipline, which were the majority of tertiary non universitary teachers, and a good amount of the university teachers.
+In general, these teachers feel they are able to use analytics tools, or create and connect homebrew tools to messaging applications, which is why they value those features in them; however, most people value the fact that they are easy to use (perceived ease of use) and the fact that they are official, and thus sustainable through different courses.
 
@@
 
-The key findings of this study shed the light on educators’ preference to use
-messaging applications that their institutions support.  Technology adoption
-literature often \textcolor{black}{focuses} on users’ perceptions of the technology’s usefulness and
-ease of use as important prerequisites for successful adoption and
-utilization. Nevertheless, in higher education, institutions’ role in
-integrating these tools to their educational systems can improve the uptake of
-these applications and shape the social and educational experiences of their
-students. \textcolor{black}{To accomplish this fruitful integration}, institutions have to ensure that
-these messaging applications not only are GDPR (General Data Protection Regulation) compliant to keep students’ data
-secure, but also should provide IT support to all stakeholders who use the
-applications.
-
-Comparing these results with those obtained in student surveys
-in \cite{MoraChatbots2021:anon}, we have understood better the differences between the teachers’
-points of view and/or intentions and that of their students when using the
-messaging applications in higher education.  Teachers tend to adopt technologies
-supported by their institutions.  The fact they do so could be caused by a desire to ensure that their
-universities can oversee their efforts in supporting their students during the
-learning process.  Another reason could be their familiarity with the technology
-provided by their institutions. On the other hand, students use the
-non-institution messaging applications to form informal discussion groups with
-their peers.  It is worth noting that peer support and collaboration is
-inseparable from learning \cite{timmis2012constant} and correlates positively
-with higher retention in higher education \cite{o2014front}.  Therefore, both
-perspectives are complementary and play different roles in promoting the
-learning process.
+The key findings of this study shed the light on educators’ preference to use messaging applications that their institutions support.
+Technology adoption literature often focus on users’ perceptions of the technology’s usefulness and ease of use as important prerequisites for successful adoption and utilization.
+Nevertheless, in higher education, institutions’ role in integrating these tools to their educational systems can improve the uptake of these applications and shape the social and educational experiences of their students.
+This integration, to be fruitful, institutions have to ensure that these messaging applications not only are GDPR compliant to keep students’ data secure but also should provide IT support to all stakeholders who use the applications.
+
+Moreover, this study clarifies the differences between the teachers’ perspectives and/or intentions and that of their students when using the messaging applications in higher education.
+Teachers tend to adopt technologies supported by their institutions.
+This could be to ensure that their universities can oversee their efforts in supporting their students during the learning process.
+Another reason could be their familiarity with the technology provided by their institutions.
+On the other hand, students use the non-institution messaging applications to form informal discussion groups with their peers.
+It is worth noting that peer support and collaboration is inseparable from learning \cite{timmis2012constant} and correlates positively with higher retention in higher education \cite{o2014front}.
+Therefore, both perspectives are complementary and play different roles in promoting the learning process.
 
 % Noorhan suggest that using some simple things could increase the perceived usefulness - JJ
-As in many other methodologies that try to assess technology acceptance, answers to the survey suggest
-that the introduction of simple, and institution-supported, instant messaging
-and chatbot technologies would increase the perceived usefulness (which is one
-of the key metrics in technology acceptance models). Since most institutions
-already have some {\em virtual campus} or learning management system, adding
-some easy automation, or connection to personal instant messaging tools, could
-really help onboard the learning community on these new technologies.
-
-What we are going to propose next is a possible process of
-technology introduction that is compatible with the conclusions of this study,
-but that would have to be piloted in order to check its value, and its
-relationship with better learning outcomes, as well as higher teacher
-satisfaction.
-Once that initial introduction of institutional messaging
-automation tools is done, teachers (and students as well) will
-probably prefer the kind of bots that alleviate bureaucratic or repetitive
-tasks, such as answering frequent questions or answers on class or assignment
-deadlines, as indicated by their answers to the respective
-questions. These will help the introduction of more complex chatbots that will
-affect more directly learning outcomes, such as chatbots that help students
-integrate in the class, or are able to identify (and address) learning problems
-in students or in groups of them. These should also be accompanied by
-analytics on student interaction, as well as possibly some natural language
-processing (in vernacular language) that will help assess the general mood of
-the class, and how different material (or external factors) affect it.
+
+% What kidn of chatbots are preferred? (suggested by Fran)
 
 % No remarkable differences between different groups.
-This introduction of chatbots and chatbot technology will be helped by the fact
-that no discernible differences are found between different groups. Even if
-chatbots do have some potential for personalization or customization, based on
-the class material, student and teaching staff, the general introduction of the
-technology can be done in a general way and for all disciplines, teaching
-experience and gender.
-
-At any rate, the general feeling that transpires from the survey is that it is
-essential for any institution to take into account the shareholder's opinion
-when introducing chatbots. This is true almost across the board, but in the case
-of chatbots (and instant messaging applications) their immediacy and the fact
-that they can enter into what we could call the private sphere makes this even
-more necessary.
-
-One of the questions we made in the {\bf second survey}, related to
-the messaging applications used by tertiary education teachers, opens a new line
-of inquiry about what they {\em perceive} as such, and about how it is used.
-Namely, the responses indicated that the teachers perceived as messaging
-application not only what is usually called a chat or instant messaging app such
-as WhatsApp or Microsoft Teams, but also the means provided by the university for
-communicating with the student, such as a feature of grading applications that
-will email the grade to the student. This implies that there is a need by
-teachers, communication with students, also mostly unidirectional, and that it
-does not matter so much how that need is covered. However, this will need careful
-consideration, including how it ties with the automation of the learning
-experience that the chatbots bring.
+
+% Only some COVID-response relationship.
 
 % Future study (suggested by Noorhan): how COVID influenced adoption of these technologies.
-There are several future lines of work informed by our results of this
-survey. For instance, the rollout of extensive videoconferencing and virtual
-teaching solutions that the COVID pandemic has brought has also taught us a
-series of lessons. It increases isolation, for instance, and decreases the
-amount of synchronous contact that happens in the fringes of the classroom:
-teaching staff offices, before and after class. A future line of work would be
-focused on exactly this, and what kind of needs could be covered by chatbot
-technology. We will create a series of international surveys that will
-investigate this.
-
-Finally, the full extent of chatbot technology is not really being examined in
-these surveys. They can be connected to natural language processing engines with
-sentiment analysis as well as other analytics. Examining the mood of the class,
-as response to new material, assignment, exams or external events might help
-will help any student-centered teaching strategy, which will help students (and
-teachers) reach their learning objectives. This line of work, however, will be
-based on the introduction of some pilot study, combined with initial opinion
-assessment on the students.
+
+% Emotinal, mood for future work... Chatbots perform sentiment analysis
 
@@
 
-The datasets generated and analysed during the current study are available in the {\tt anonymous} repository, accessible from https://anonymous.URL
-% {\tt https://github.com/JJ/edubots-paper/tree/main/data}.
+The datasets generated and analysed during the current study are available in Github, from \url{https://github.com/JJ/edubots-paper/tree/main/data}.
 
@@
 
-Suppressed for double blind review
-% This work has been supported by EDUBOTS project, funded under the scheme Erasmus + KA2: Cooperation for innovation and the exchange of good practices - Knowledge Alliances (grant agreement no: 612446).
+This work has been supported by EDUBOTS project, funded under the scheme Erasmus + KA2: Cooperation for innovation and the exchange of good practices - Knowledge Alliances (grant agreement no: 612446).
 
@@
 
-All the authors have contributed to the study presented in this manuscript. (Rest hidden for double blind)
-
-% JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
-% 
-% PAC has revised the paper and researched the state of the art, as well as contributed to the survey design.
-% AMM has revised the paper and researched the state of the art, as well as contributed to the survey design.
-% FB has made the analysis and processed data and contributed to the survey design.
-% NA has supervised the state of the art, and written the bulk of it, as well as contributed to discussion and conclusions.
-% OT has performed data analysis, and contributed to discussion and conclusions.
-% AG has contributed to the design of the survey, analysis, discussion and conclusions.
+All the authors have contributed to the study presented in this manuscript.
+
+JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
+
+PAC has revised the paper and researched the state of the art, as well as contributed to the survey design.
+AMM has revised the paper and researched the state of the art, as well as contributed to the survey design.
+FB has made the analysis and processed data and contributed to the survey design.
+NA has supervised the state of the art, and written the bulk of it, as well as contributed to discussion and conclusions.
+OT has performed data analysis, and contributed to discussion and conclusions.
+AG has contributed to the design of the survey, analysis, discussion and conclusions.
 
@@
 
-% The authors want to thank to the educators who participated in the survey, and also people who have distributed the survey in their mailing lists, especially Mario García Valdez, Jesús Moreno León and the late José Raúl Canay.
-We would also like to thank the anonymous reviewers that have contributed greatly to the improvement of this paper.
-
-\section{Appendix I: Survey questions}
-\label{app:questions}
-
-The surveys have the same common initial demographic questions:\begin{itemize}
-\item Degrees or titles where the teacher was working, either university or other tertiary education.
-\item Discipline: Engineering, Social Sciences, Health and Bio, General Sciences, Humanities, Other.
-\item Gender: Man, Woman, Rather not say.
-\item Age: 25-35, 35-45, 45-55, more than 55.
-\item Experience on the job: up to 5 years, 5-15 years, 15-25 years, more than 25 years.
-\textcolor{black}{
-\item Type of degree: university, other tertiary education.
-This question was implicit in the first survey: there were two different versions of the survey.
-However, it was an explicit question in the second survey.}
-\end{itemize}
-
-\begin{figure}[h!tbp]
-\begin{center}
-\includegraphics[width=0.85\textwidth]{figures/survey-1.png}
-\end{center}
-    \caption{Screen capture of the Spanish-language form used for the \bf{first survey}}
-\label{figure:survey1}
-\end{figure}
-% Including questions in surveys
-The {\bf first survey}, shown in its original form in Figure \ref{figure:survey1}, which \textcolor{black}{focused on} the use of messaging apps in class, includes the following questions:
-
-\textit{1. Regarding the use of messaging apps in class, you prefer ...}
-\begin{itemize}
-\item A chat group with the students in the same course
-\item Students self-organize and with the teacher not being part of any chat group
-\textcolor{black}{
-\item A chat group with all the students and teachers of the School/High-School/Faculty
-}
-\item A chat group with all the students and teachers of the same study year
-\end{itemize}
-
-\textit{2. Which messaging app platform do you use to communicate with your peers or students?}
-\begin{itemize}
-\item WhatsApp
-\item Telegram
-\item LinkedIn
-\item Twitter messages
-\item Discord
-\item Slack
-\item Snapchat
-\item The platform provided by your own institution
-\item None, I do not use any messaging app to communicate with my students
-\end{itemize}
-
-\textit{3. Which kind of chatbots (software that automatically respond to questions or commands) could be useful to improve the learning results with your students or help you managing your course?}
-\begin{itemize}
-\item Agenda bots that e.g. remind students about project deadlines
-\item Bots that collect and provide answers to frequent questions
-\item Bots that inform students about their grades
-\item Bots that help with the class materials (e.g. searching for topics about a concept, or asking about them)
-\end{itemize}
-
-\textit{4. The virtualization of teaching due to the COVID pandemic during this year and the previous one, did it mean any change in your viewpoint or use of messaging apps in class?}
-\begin{itemize}
-\item No, I did use it before and use it now
-\item Yes, I started using safer alternatives
-\item Yes, I did not use any messaging platform before but I do use it now
-\item No, I did not use any messaging platform before or now
-\end{itemize}
-
-\begin{figure}[h!tbp]
-\begin{center}
-\includegraphics[width=\textwidth]{figures/survey-2.png}
-\end{center}
-    \caption{Screen capture of the Spanish-language form used for the \bf{second survey}}
-\label{figure:survey2}
-\end{figure}
-The {\bf second survey}, shown in its original form in Figure \ref{figure:survey2}, followed the same paths, only in this case there was a single questionnaire, and with a different scope, focusing on the kind of interaction media features that teachers value the most.
-%\textcolor{black}{A capture of these questions is included in Figure \ref{fig:survey2}} % this sentence is repeated
-% Olia - see my comment above.
-It was filled by teachers that were also students in a Professional Development course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers who knew about it by emails from the authors, or from the vicedeanship for International Relations that included it in its newsletter.
-This means that there might be a higher proportion of 1) teachers with few years of experience 2) teachers from the computer science faculty and 3) teachers from Granada.
-We think, however that there's no explicit bias in this selection, although of course specific percentages will vary.
-
-Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are  their \textcolor{black}{past experiences and needs} with regard to the use of instant messaging applications with students, and even using bots or chatbots in the classroom.
-In addition the survey asked about the most relevant \textit{interaction media features} for the teachers with respect to the potential tool to use in class.
-
-The specific questions included in this second survey are listed below:
-
-% Antonio - I have included a reference name to each one of these variables, which are the names used on Tables 8 and 9.
-Thus it will be easy to recognize every variable, and then, we could refer to them in those tables.
-
-\textit{1. You prefer the interaction with your students to be ...}
-\begin{itemize}
-\item Synchronous: students and teacher/s in the same space, simultaneously. [\texttt{Synchrony - Yes}]
-\item Asynchronous: the student asks at anytime, the teacher responds whenever possible. [\texttt{Synchrony - No}]
-\end{itemize}
-
-\textit{2. Regarding the interaction with your students, you ...}
-\begin{itemize}
-\item Prefer it to be done by institutional means/tools: office hours, forum/messages via the virtual campus, institutional email. [\texttt{Officiality - Yes}]
-\item Admit the use of other means/tools: blogs, chat groups in messaging platforms, any others. [\texttt{Officiality - No}]
-\end{itemize}
-
-\textit{3. Which media features do you value the most for your interaction with your students?}
-\begin{itemize}
-\item Familiarity with its use i.e. that I do not need to learn a new tool. [\texttt{Familiarity}]
-\item The official formation/training provided by your institution on its use. [\texttt{Official formation}]
-\item That only one-directional communication is allowed (from teachers to students). [\texttt{Unidirectionality}]
-\item Non-hierarchical tools that allowed teacher-to-student and student-to-student communication. [\texttt{Horizontally}]
-\item Connectivity to other tools, for instance common log in. [\texttt{Connectivity}]
-\item Possibility for teachers to develop/add their own functionalities (e.g. automatic correction tools). [\texttt{Pluggability}]
-\item Possibility for users to hide personal data (such as my telephone number). [\texttt{Hidden Phone Number}]
-\item Not having to worry about maintenance and that it is easily sustainable from one year to the next. [\texttt{Sustainability}]
-\item That it offers the chance to extract data to assess the student performance. [\texttt{Analytics}]
-\end{itemize}
+The authors want to thank to the educators who participated in the survey, and also people who have distributed the survey in their mailing lists, especially Mario García Valdez, Jesús Moreno León and José Raúl Canay.
 

### 2023-01-07 edubots_surveys.Rnw

--- 2023-01-06 edubots_surveys.Rnw
@@
 
-\textcolor{blue}{In recent years, new technologies are being widely adopted and introduced into the classroom. However, in order to be successful, their application 
-will require additional work and training for the teacher, as well as for the students. Thus, both of them will acquire new skills and, potentially, pupils will be more 
-engaged to the subject, which is usually the main objective. Even if several technologies are already in use in the classroom, there is still room for adopting new others.
-Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Asking and analyzing users' 
-opinions with regard to this scenario will help reaping the expected benefits of the technology}.
-
-\textcolor{blue}{Messaging applications such as WhatsApp or Telegram are becoming very popular in teaching scenarios mainly at secondary and higher education.
-In addition to their main use, some of these tools offer the possibility to interact with \textit{chatbots} (or just bots), even supporting synchronous conversations between the different
-parties \cite{differ.chat}. It is also possible to create a standalone chatbot application and attach it to a messaging tool through an API (Application Programming Interface).}
-
-\textcolor{blue}{\textit{Chatbots} are autonomous agents that are able to communicate and interact in a human-like way \cite{Gong2008}, answering question and even posing their own ones to the user. 
+\textcolor{blue}{New technologies are being introduced and widely adopted into the classroom in the last years. However, in order to be successful, their application 
+will require (many) extra work and training for the teacher, as well as for the students. Thus, both of them will acquire new skills and, potentially, pupils will 
+get a higher engagement to the subject, which is usually the main objective. Even if several technologies are already in use inside the classroom, there is still room for adopting others.
+Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Given this, 
+asking and analyzing user's opinions with regard to this scenario will help reaping the expected benefits of the technology}.
+
+\textcolor{blue}{In the last years, messaging applications such as WhatsApp or Telegram are being used in teaching scenarios mainly at secondary and higher education.
+In addition to their main use, some of these tools offer the possibility of interact with \textit{chatbots} (or just bots), even supporting synchronous conversation between the different
+parties \cite{differ.chat}. There is also possible to create a standalone chatbot application and attach it to a messaging tool through an API (Application Program Interface).}
+
+\textcolor{blue}{\textit{Chatbots} are autonomous agents able to communicate and interact with humans (or other chatbots) in a human-like way \cite{Gong2008}, answering question and even posing their own ones to the user.
 Thus, we can say that they are close to passing a Turing Test \cite{moor2003turing}. They are implemented by means of different Artificial Intelligence techniques, such as natural language processing.
-Within the plethora of possible applications of chatbots, education is one of the most prolific nowadays \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called 
+Inside the plethora of possible applications of chatbots, education is one of the most prolific nowadays \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called 
 \textit{personalized learning}, i.e.
-they adapt themselves to students' self-pace learning and provide online tutoring.
-Personalized learning has been proved to be very effective increasing students course engagement and participation \cite{agarwal2020}.
-Moreover, chatbots also reduce students' stress \cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their teachers,
-or asking questions in front of the class. This situation usually results in a later contact with the teacher by e-mail, which in turn, will mean a workload for the teacher that could be very 
-significant given the disproportionate ratio of number of students to teachers.  
+they adapt themselves to students’ pace of learning and provide online tutoring outside the classroom, which have been proved to be very effective increasing their
+engagement and participation in the subjects \cite{agarwal2020}.
+Moreover chatbots' tutoring possibilities aid to reduce the stress of students \cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their teacher,
+or asking questions in front of the class.
+This situation normally conducts to a silence of the student and a later contact with the teacher by e-mail, which, in turn, will mean a workload for the teacher, that could be very
+significant given the existing disproportion between number of students per each teacher.  
 }
 Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning
-experience \cite{Griol2014,kim2020}. In addition, using an automated system such as a chatbot will allow teachers to spend more time on  other topics that students struggle with.
+experience \cite{Griol2014,kim2020}.
+In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding.
 
@@
 focus of the % EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
-unnamed European project, the main sponsor of this study, is to explore the best practices and innovative use of chatbots, 
+unnamed European project, the main sponsor of this study, is to explore best practices and innovative use of chatbots, 
 and to create a learning community of educators in higher education institutions.
-\textcolor{blue}{Researchers and teachers participating in this project have developed several studies. Most of these works are focused on how  
+\textcolor{blue}{Researchers and teachers participating in this project have developed several studies. Most of these works have been focused on how the 
 messaging applications and/or chatbots are normally applied to deliver personalized learning in classrooms that occurs anytime anywhere,
@@
  \begin{itemize}
-\item The first phase aimed to collect feedback from students about their
-  students’ preferences of tools/applications for chatting and
-  messaging, how they use them in educational context, who they like to be
-  with in the class messaging groups, and their expectations of chatbots 
-  in assisting them during their learning process. Therefore, two surveys
+\item The first phase aimed to collect feedback from students about their actual
+  information about students’ preferences of tools/applications for chatting and
+  messaging, how they use them in educational context, who do they like to be
+  with in the class messaging groups, and their expectations of the chatbots in
+  terms of assisting them during their learning process. Therefore, two surveys
   for bachelor and master degree students at the University of Granada (Spain)
@@
   findings of the students' surveys reveal that they prefer to use messaging
-  familiar applications, such as Telegram or WhatsApp. 
-  Students also expressed interest in chatbots that can assist them with
+  applications, such as Telegram or WhatsApp as they are familiar to
+  them. Students also expressed interest in chatbots that can assist them with
   organizing their course schedules, help them access their assignment grades
-  and facilitate searching for resources.
+  and facilitate searching for course's resources.
 \item The results of the first phase were fed into the second phase of the
   study, which focused on teachers’ opinions about using chatbots and messaging
-  applications in classes. These results are the main focus of this paper.
+  applications in classes. This is what is going to be presented in this paper.
 \end{itemize}
@@
 Initially, a single survey was developed for this purpose and responses from 300
-higher education teachers were collected and analysed\textcolor{black}{; this will be detailed in Section \ref{sec:meth}}. The responses' analysis
-led to the preparation of a second survey for teachers and 200 responses were
-collected\textcolor{black}{, again following the methodology that will be explained later. The questions of the second survey focused on asking about teachers'
+higher education teachers were collected and analysed\textcolor{black}{; this will be explained more fully in the methodology section}. The responses' analysis
+entailed the creation of a second survey to which 200 teachers' responses were
+collected\textcolor{black}{, with the methodology and collective characteristics that will be explained below. The questions of the second survey focused on discussing teachers'
 needs, opinions and preferences of the development of future technology-enhanced
-tools and its potential impact on educational institutions policies. In order to assess these, this paper layed out the following research questions}:
+tools and its potential impact on educational institutions’ policies. In order to assess these, this paper investigated the following research questions}:
 
@@
 
-%A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
-The majority of the teachers were aged 45-55 years old (70; 34.1\%), followed by individuals aged 35-45 (67, 32.7\%), and 25-35 (42; 20.5\%), while the minority was aged $>$~55 years old (26; 12.7\%).
-In terms of teaching experience, 59 teachers (28.8\%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9\%), 0-5 years (51; 24.9\%) and more than 25 years of experience (44; 21.5\%).
-The teachers were asked about what kind of interaction media features they value the most \textcolor{black}{; i.e.
-what their preferred features are in the applications/tools that they use to interact with their students.} The frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
+This question is mainly answered in the second survey, which, as indicated previously, was designed after initial analysis of the first.
+The kind of interaction is essential to design proper chatbots, or to deploy a technology instead of others; it is related to the perceived usefulness in a technology acceptance model.
+Essentially, if some new chatbot application does not have what teachers perceive as useful for their purposes, they are unlikely to adopt it.
+So knowing these opinions is quite important, and is the reason why we included it in the second survey.
+
+The teachers were asked about what kind of features of the messaging system they value the most; the frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
 
@@
                     \cline{2-5}
-
 Analytics & 108 & 52.7 & 97 & 47.3 \\
@@
 The datasets generated and analysed during the current study are available in the {\tt anonymous} repository, accessible from https://anonymous.URL
-% {\tt https://github.com/JJ/edubots-paper/tree/main/data}.
 

### 2023-01-07 edubots_surveys.Rnw
Eliminates blue color

@@
 \usepackage[utf8]{inputenc} %unicode support
-\usepackage{hyperref} % for URL
 
@@
 
-\textcolor{blue}{New technologies are being introduced and widely adopted into the classroom in the last years. However, in order to be successful, their application 
+New technologies are being introduced and widely adopted into the classroom in the last years. However, in order to be successful, their application
 will require (many) extra work and training for the teacher, as well as for the students. Thus, both of them will acquire new skills and, potentially, pupils will
@@
 Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Given this,
-asking and analyzing user's opinions with regard to this scenario will help reaping the expected benefits of the technology}.
-
-\textcolor{blue}{In the last years, messaging applications such as WhatsApp or Telegram are being used in teaching scenarios mainly at secondary and higher education.
+asking and analyzing user's opinions with regard to this scenario will help reaping the expected benefits of the technology.
+
+In the last years, messaging applications such as WhatsApp or Telegram are being used in teaching scenarios mainly at secondary and higher education.
 In addition to their main use, some of these tools offer the possibility of interact with \textit{chatbots} (or just bots), even supporting synchronous conversation between the different
-parties \cite{differ.chat}. There is also possible to create a standalone chatbot application and attach it to a messaging tool through an API (Application Program Interface).}
-
-\textcolor{blue}{\textit{Chatbots} are autonomous agents able to communicate and interact with humans (or other chatbots) in a human-like way \cite{Gong2008}, answering question and even posing their own ones to the user.
+parties \cite{differ.chat}. There is also possible to create a standalone chatbot application and attach it to a messaging tool through an API (Application Program Interface).
+
+\textit{Chatbots} are autonomous agents able to communicate and interact with humans (or other chatbots) in a human-like way \cite{Gong2008}, answering question and even posing their own ones to the user.
 Thus, we can say that they are close to passing a Turing Test \cite{moor2003turing}. They are implemented by means of different Artificial Intelligence techniques, such as natural language processing.
 Inside the plethora of possible applications of chatbots, education is one of the most prolific nowadays \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called
-\textit{personalized learning}, i.e.
-they adapt themselves to students’ pace of learning and provide online tutoring outside the classroom, which have been proved to be very effective increasing their
+\textit{personalized learning}, i.e. they adapt themselves to students’ pace of learning and provide online tutoring outside the classroom, which have been proved to be very effective increasing their
 engagement and participation in the subjects \cite{agarwal2020}.
@@
 significant given the existing disproportion between number of students per each teacher.
-}
+
 Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning
@@
 and to create a learning community of educators in higher education institutions.
-\textcolor{blue}{Researchers and teachers participating in this project have developed several studies. Most of these works have been focused on how the 
+Researchers and teachers participating in this project have developed several studies. Most of these works have been focused on how the
 messaging applications and/or chatbots are normally applied to deliver personalized learning in classrooms that occurs anytime anywhere,
 promote collaborative learning experiences, group discussions \cite{panah2020study} and boost students' sense of belonging to their institutions
-\cite{abbas2021onlinechat}.}
-\textcolor{blue}{The majority of these studies were conducted focusing on the teachers' perspectives, so this paper aims to provide more conclusions regarding 
+\cite{abbas2021onlinechat}.
+The majority of these studies were conducted focusing on the teachers' perspectives, so this paper aims to provide more conclusions regarding
 their opinions and needs, as well as the existing challenges or opportunities that arise when adopting these technologies in classrooms. This will lead to clarify
-how they can positively contribute to enhancing the learning process in higher education institutions.}
+how they can positively contribute to enhancing the learning process in higher education institutions.
 
@@
 recommendations to make a successful deployment of chatbot technologies (and, in
-some cases, general instant messaging applications) in higher education\textcolor{black}{; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be used in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from RQ3 we will also try to find best practices in the adoption of messaging platforms and they accompanying chatbots.}
-
-The remainder of the paper is organized as follows: \textcolor{black}{first, an overview of what
+some cases, general instant messaging applications) in higher education; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be used in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from RQ3 we will also try to find best practices in the adoption of messaging platforms and they accompanying chatbots.
+
+The remainder of the paper is organized as follows: first, an overview of what
 current research has found about the use of messaging applications, including
-chatbots, in the classroom is described}. The methodology used in the surveys is presented in
+chatbots, in the classroom is described. The methodology used in the surveys is presented in
 Section \ref{sec:meth}, and the results of the surveys are presented next in
@@
 
-This question is mainly answered in the second survey, which, as indicated previously, was designed after initial analysis of the first.
-The kind of interaction is essential to design proper chatbots, or to deploy a technology instead of others; it is related to the perceived usefulness in a technology acceptance model.
-Essentially, if some new chatbot application does not have what teachers perceive as useful for their purposes, they are unlikely to adopt it.
-So knowing these opinions is quite important, and is the reason why we included it in the second survey.
-
-The teachers were asked about what kind of features of the messaging system they value the most; the frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
+%A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
+The majority of the teachers were aged 45-55 years old (70; 34.1\%), followed by individuals aged 35-45 (67, 32.7\%), and 25-35 (42; 20.5\%), while the minority was aged $>$~55 years old (26; 12.7\%).
+In terms of teaching experience, 59 teachers (28.8\%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9\%), 0-5 years (51; 24.9\%) and more than 25 years of experience (44; 21.5\%).
+The teachers were asked about what kind of interaction media features they value the most \textcolor{black}{; i.e.
+what their preferred features are in the applications/tools that they use to interact with their students.} The frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
 
@@
                     \cline{2-5}
+
 Analytics & 108 & 52.7 & 97 & 47.3 \\
@@
 The datasets generated and analysed during the current study are available in the {\tt anonymous} repository, accessible from https://anonymous.URL
+% {\tt https://github.com/JJ/edubots-paper/tree/main/data}.
 

### 2023-01-07 edubots_surveys_future_paper.Rnw
explaining what each author have done

@@
 This work has been supported by EDUBOTS project, funded under the scheme Erasmus + KA2: Cooperation for innovation and the exchange of good practices - Knowledge Alliances (grant agreement no: 612446).
+It has also been supported by DemocratAI::UGR project (PID2020-115570GB-C22).
 
@@
 All the authors have contributed to the study presented in this manuscript. 
-JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
-PAC has...
-AMM has ...
-FB has...
-NA has...
-OT has...
-AG has...
+JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript; 
+AMM, FB, PAC, NA, OT, AG have done editing, writing and proofreading tasks.
 All authors have read and approved the final manuscript.

### 2023-01-07 edubots_surveys.Rnw
Address sentences that the reviewer has pointed out
Using ChatGPT to improve them

@@
 
-New technologies are being introduced and widely adopted into the classroom in the last years. However, in order to be successful, their application
-will require (many) extra work and training for the teacher, as well as for the students. Thus, both of them will acquire new skills and, potentially, pupils will
-get a higher engagement to the subject, which is usually the main objective. Even if several technologies are already in use inside the classroom, there is still room for adopting others.
+New technologies have been introduced and widely adopted into the classroom in recent years. However, in order to be successful, their application
+will require a certain amount of extra work and training for the teacher, as well as for the students.
+Training will help the two collectives involved acquire new skills and, potentially, pupils will acquire a greater level of engagement with the subject matter, which is usually the main objective.
+Even if several technologies are already in use inside the classroom, there is still room for adopting others.
 Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Given this,
@@
 
-In the last years, messaging applications such as WhatsApp or Telegram are being used in teaching scenarios mainly at secondary and higher education.
-In addition to their main use, some of these tools offer the possibility of interact with \textit{chatbots} (or just bots), even supporting synchronous conversation between the different
-parties \cite{differ.chat}. There is also possible to create a standalone chatbot application and attach it to a messaging tool through an API (Application Program Interface).
-
-\textit{Chatbots} are autonomous agents able to communicate and interact with humans (or other chatbots) in a human-like way \cite{Gong2008}, answering question and even posing their own ones to the user.
-Thus, we can say that they are close to passing a Turing Test \cite{moor2003turing}. They are implemented by means of different Artificial Intelligence techniques, such as natural language processing.
-Inside the plethora of possible applications of chatbots, education is one of the most prolific nowadays \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called
+Over the past decade, messaging apps like WhatsApp and Telegram have become increasingly popular in teaching at the secondary and higher education levels \cite{gachago2015crossing,mwakapina2016whatsapp,yin2016adoption,panah2020study}.
+By creating groups at various levels (e.g.
+class, assignment, course), teachers and students have been able to use these apps for bilateral or group-level communication.
+In addition to their primary function of communication, many messaging programs also allow the creation of applications that can act as users through open application programming interfaces (APIs), which are often available through a free or freemium model.
+
+This opens the door to the introduction of \textit{chatbots}, that is, autonomous agents able to communicate and interact with humans (or other chatbots) in a natural way \cite{Gong2008}, answering question and even posing their own ones to the user, in the classroom; in this limited environment, chatbots can appear as regular users, thus being close to passing a Turing Test \cite{moor2003turing}, which gives them certain characteristics that, again, can enhance student engagement.
+Chatbots implement different Artificial Intelligence techniques, such as natural language processing as well as, in some cases, learning; this is not a requirement, however, and in most cases they are simply applications that have a conversational interface, as opposed to a graphical user interface.
+
+These qualities have made education one of the most promising areas for chatbot applications today \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called
 \textit{personalized learning}, i.e. they adapt themselves to students’ pace of learning and provide online tutoring outside the classroom, which have been proved to be very effective increasing their

### 2023-01-07 edubots_surveys.Rnw
Reinstitutes eliminated citation

@@
 
-This opens the door to the introduction of \textit{chatbots}, that is, autonomous agents able to communicate and interact with humans (or other chatbots) in a natural way \cite{Gong2008}, answering question and even posing their own ones to the user, in the classroom; in this limited environment, chatbots can appear as regular users, thus being close to passing a Turing Test \cite{moor2003turing}, which gives them certain characteristics that, again, can enhance student engagement.
+This opens the door to the introduction of \textit{chatbots}, that is, autonomous agents able to communicate and interact with humans (or other chatbots) in a natural way \cite{Gong2008,differ.chat}, answering question and even posing their own ones to the user, in the classroom; in this limited environment, chatbots can appear as regular users, thus being close to passing a Turing Test \cite{moor2003turing}, which gives them certain characteristics that, again, can enhance student engagement.
 Chatbots implement different Artificial Intelligence techniques, such as natural language processing as well as, in some cases, learning; this is not a requirement, however, and in most cases they are simply applications that have a conversational interface, as opposed to a graphical user interface.

### 2023-01-07 edubots_surveys.Rnw

--- 2023-01-07 edubots_surveys.Rnw
@@
 Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning
-experience \cite{Griol2014,kim2020}.
-In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding.
+experience \cite{Griol2014,kim2020}. In addition, using an automated system such as a chatbot will allow teachers to spend more time on  other topics that students struggle with.
 
@@
 \item RQ3 - Which kind of interaction do teachers prefer with their students?
-\item RQ4 - What kind of interaction media features do teachers value the most?
+\item RQ4 - Which kind of interaction media features do teachers value the most?
 \end{itemize}
 
-We will try to answer these questions through the analysis of questions and
-answers in the two aforementioned surveys. Eventually, what we want to obtain is a series of
+We will try to answer these research questions through the analysis of the two aforementioned surveys. 
+Eventually, what we want to obtain is a series of
 recommendations to make a successful deployment of chatbot technologies (and, in
@@
 Section \ref{sec:res}. Finally, we discuss these results and conclude with a
-series of recommendations in the section that closes the paper.
+series of recommendations for the successful deployment of chatbots in higher education.
 

### 2023-01-07 edubots_surveys.Rnw

@@
 
-New technologies are being introduced and widely adopted into the classroom in the last years. However, in order to be successful, their application
-will require (many) extra work and training for the teacher, as well as for the students. Thus, both of them will acquire new skills and, potentially, pupils will
-get a higher engagement to the subject, which is usually the main objective. Even if several technologies are already in use inside the classroom, there is still room for adopting others.
+New technologies have been introduced and widely adopted into the classroom in recent years. However, in order to be successful, their application
+will require a certain amount of extra work and training for the teacher, as well as for the students.
+Training will help the two collectives involved acquire new skills and, potentially, pupils will acquire a greater level of engagement with the subject matter, which is usually the main objective.
+Even if several technologies are already in use inside the classroom, there is still room for adopting others.
+
 Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Given this,
@@
 
-In the last years, messaging applications such as WhatsApp or Telegram are being used in teaching scenarios mainly at secondary and higher education.
-In addition to their main use, some of these tools offer the possibility of interact with \textit{chatbots} (or just bots), even supporting synchronous conversation between the different
-parties \cite{differ.chat}. There is also possible to create a standalone chatbot application and attach it to a messaging tool through an API (Application Program Interface).
-
-\textit{Chatbots} are autonomous agents able to communicate and interact with humans (or other chatbots) in a human-like way \cite{Gong2008}, answering question and even posing their own ones to the user.
-Thus, we can say that they are close to passing a Turing Test \cite{moor2003turing}. They are implemented by means of different Artificial Intelligence techniques, such as natural language processing.
-Inside the plethora of possible applications of chatbots, education is one of the most prolific nowadays \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called
+Over the past decade, messaging apps like WhatsApp and Telegram have become increasingly popular in teaching at the secondary and higher education levels \cite{gachago2015crossing,mwakapina2016whatsapp,yin2016adoption,panah2020study}.
+By creating groups at various levels (e.g.
+class, assignment, course), teachers and students have been able to use these apps for bilateral or group-level communication.
+In addition to their primary function of communication, many messaging programs also allow the creation of applications that can act as users through open application programming interfaces (APIs), which are often available through a free or freemium model.
+
+This opens the door to the introduction of \textit{chatbots}, that is, autonomous agents able to communicate and interact with humans (or other chatbots) in a natural way \cite{Gong2008,differ.chat}, answering question and even posing their own ones to the user, in the classroom; in this limited environment, chatbots can appear as regular users, thus being close to passing a Turing Test \cite{moor2003turing}, which gives them certain characteristics that, again, can enhance student engagement.
+Chatbots implement different Artificial Intelligence techniques, such as natural language processing as well as, in some cases, learning; this is not a requirement, however, and in most cases they are simply applications that have a conversational interface, as opposed to a graphical user interface.
+
+These qualities have made education one of the most promising areas for chatbot applications today \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called
 \textit{personalized learning}, i.e. they adapt themselves to students’ pace of learning and provide online tutoring outside the classroom, which have been proved to be very effective increasing their

### 2023-01-07 edubots_surveys.Rnw
reviewed SotA - first paragraphs

--- 2023-01-07 edubots_surveys.Rnw
@@
 (i.e. video, audio, text) \cite{tang2017mobile}. Using these tools in
-higher education can facilitate the delivery of personalized learning
-that occurs anytime anywhere, promote collaborative learning
+higher education facilitates the delivery of personalized learning
+that occurs anytime anywhere, and promotes collaborative learning
 experiences and group discussions \cite{panah2020study}.
@@
 WhatsApp is, at least in most Western countries, the most popular MIM platform
-used by educators to \textcolor{black}{provide} assignments' feedback to students, support course
-discussions, and provide learning resources in informal learning settings
+used by educators to provide assignments' feedback to students, support course
+discussions, and contribute resources in informal learning settings
 \cite{panah2020study}.  Moreover, the use of WhatsApp in higher education could
@@
 between educators and students embedded in the social learning process
-\cite{gachago2015crossing}; however, this last paper also reflects the need for
+\cite{gachago2015crossing}. However, this last paper also reflects the need for
 learners to "take ownership of the tool" and the advantages of social learning
@@
 their learning \cite{gachago2015crossing} process.  This is why examining the
-role of MIM in higher education is still a challenge, and why the opinions of
+role of MIM platforms in higher education is still a challenge, and why the opinions of
 the teaching community towards them have to be examined, as we do in this paper.

### 2023-01-07 edubots_surveys.Rnw
removed black coloring and reviewed grammar

@@
 % The Use of Chatbots in Higher Education
-The use of MIM, although possibly valuable by itself, can be enhanced via the
-use of chatbots, which, being conversational agents, usually dwell in systems
-where synchronous conversations take place.  The use of conversational agents
-(chatbots) in higher education is still at its infancy
-\cite{yang2019opportunities}. Nevertheless, recent studies examining their
+The use of MIM platforms, although possibly valuable by itself, can be enhanced with the
+use of chatbots, which are conversational agents that normally dwell 
+synchronous conversations systems. The use of chatbots in higher education is still in its early stages
+\cite{yang2019opportunities}. Nevertheless, recent studies have shown their
 positive impact on students' academic performance \cite{perez2020rediscovering}
-and engagement \cite{differ.chat,abbas2021onlinechat} have led to a growing
+and engagement \cite{differ.chat,abbas2021onlinechat}, leading to a growing
 interest in using this technology in the (possibly virtual) classroom. Indeed,
-the use of chatbots in collecting course feedback from students in higher
-education improved students' response quality and boosted their enjoyment levels
-\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using either tools
-such as mobile devices or teaching strategies based on gamification
+the using chatbots to collect course feedback from students in higher
+education improved response quality and boosted enjoyment levels
+\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
+mobile devices or teaching strategies based on gamification
 \cite{Yildirim2017} can improve student motivation. In this sense, the authors
-in \cite{Pimmer2019} \textcolor{black}{adopted a quasi-experimental, survey-based approach to
+in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
 report the positive impact of using instant messaging tools in boosting
-students' knowledge and mitigating their feelings of isolation}.
+students' knowledge and mitigating their feelings of isolation.
 

### 2023-01-07 edubots_surveys.Rnw
SotA - par 5

@@
 
-Several higher education chatbots' evaluation studies have been undertaken. For
-instance, a recent evaluation review study presented by Smutny and Schreiberova
-\cite{Smutny2020} examined 47 educational chatbots implemented in Facebook
-Messenger with the focus to identify characteristics and quality metrics such as
-language, subject matter and platform\textcolor{black}{, whereas the study undertaken by Pérez and collaborators
-\cite{perez2020rediscovering} aimed to categorize educational chatbots, according
-to their, purpose into service-oriented and teaching-oriented}. The first category
-includes those that provide service support such as the chatbot Ask Holly
-\cite{meetholly} and Dina \cite{santoso2018dinus}; both chatbots respond to
+Several studies have been conducted to evaluate chatbots in higher education. For
+instance, a recent study was presented by Smutny and Schreiberova
+\cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
+Messenger, with a focus on identifying characteristics and quality metrics such as
+language, subject matter, and platform. Pérez and collaborators
+\cite{perez2020rediscovering} attempted to categorize educational chatbots attending to their purpose 
+as service-oriented or teaching-oriented. Service-oriented chatbots
+include those that provide service support, such as Ask Holly
+\cite{meetholly} and Dina \cite{santoso2018dinus}, which responds to
 students' questions about enrollment and registration. Ask L. U.
 \cite{LancasterUniversity_2019} answers students' frequently asked questions
-about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot}
+about schedules, grades, tutors, and societies. LISA \cite{dibitonto2018chatbot}
 and Differ \cite{differ.chat} facilitate breaking the ice between new students
 by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
-proposed a generic chatbot for university students that is able to answer to
-their frequently asked questions \textcolor{black}{and, for some time, the University of Granada had
-\textcolor{black}{Elvira} as a chatbot in its main web page \cite{MOREO20129} to perform that duty.} Besides being able
-to answer pre-established (frequent) questions, it did so from the website of
-the University of Granada using an inset \textcolor{black}{persona, voiced by a real person, who
-lip-synced the answers. The emphasis in the case of Elvira, however, was on the
-authenticity of the synchronization more than in making the update of questions
-answered simpler, or more interactive, or more open to the rest of the university staff, using actual messaging platforms. In
+proposed a generic chatbot for university students that is able to answer 
+frequently asked questions. The University of Granada had
+Elvira, a built-in chatbot in its main web page \cite{MOREO20129} to perform the same task. In addition to being able
+to answer pre-established frequent questions, it did so from the website of
+the University of Granada using an inset persona, voiced by a real person, who
+lip-synced the answers. However, in the case of Elvira, the emphasis was on the
+authenticity of the synchronization rather than making the updated 
+of answered questions simpler, more interactive, or more open to the rest of the university staff using actual messaging platforms. In
 most cases, the embedded search engine was able to provide more up-to-date
-and accurate answers than the ones provided by Elvira, which had to be updated
+and accurate answers than those provided by Elvira, which had to be updated
 by hand (and not too often).
-It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide an useful service.
-Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, something which is the focus of this paper}.
+It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide a useful service.
+Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, which is the focus of this paper.
 

### 2023-01-07 edubots_surveys.Rnw
reviewed SotA - par 6

@@
 assistant chatbot developed on the Telegram messaging platform. In this study,
-the Telegram platform is chosen because it is easy to use, students are familiar
+the Telegram platform was chosen because it is easy to use, students are familiar
 with its features, and it enables them to exchange messages in different formats
 (text, audio and video) \cite{fernoagua2018intelligent}. In addition, Telegram
-could operate on all devices and operating systems. The ``eduAssistant'' chatbot
-acts as an automatic agent in teacher-content-student, facilitating real-time
-feedback loops and providing a personalized learning experience relevant to the
+can operate on all devices and operating systems. The ``eduAssistant'' chatbot
+acts as an automatic agent in the teacher-content-student relationship, providing real-time
+feedback loops and a personalized learning experience relevant to the
 students' acquired skills and knowledge. Using this chatbot, educators can
@@
 their students and the chatbot assists those who need further help by giving
-them more hints and reporting it to their educator's dashboard
-\cite{fernoagua2018intelligent}. This can help educators locate those
-students that need more attention and send them more educational resources
-relevant to their academic attainment. \textcolor{black}{In addition, a recent study
+them more hints and reporting it to the educator's dashboard
+\cite{fernoagua2018intelligent}. This can help educators identify
+students who need more attention and provide them with more educational resources
+relevant to their academic achievement. In addition, a recent study
 has analysed how the use of chatbots positively affected the learning outcomes
-of students in a Chinese class \cite{doi:10.1177/0735633120929622}}.
+of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
 

### 2023-01-07 edubots_surveys.Rnw
reviewed SotA - par 6 and 7

@@
 Despite its (arguably) successful implementation in different higher education
-institutions, over all in the fringes of educational activity, not in the actual
+institutions, particularly on the fringes of educational activity rather than actual
 student-teacher interaction, its implementation or deployment is not trivial.
-Some authors, for instance \cite{sjostrom2018designing} have proposed a
+Some authors, for instance \cite{sjostrom2018designing}, have proposed a
 conceptual architecture for the adoption of teaching-oriented chatbots in higher
 education.  This conceptual architecture is based on a systematic literature
-review of previous studies, examining the design of chatbots in higher
+review of previous studies examining the design of chatbots in higher
 education, as well as making a content analysis of student emails and discussion
-forum posts of four instances of a Java programming course.  The study outlined
+forum posts from four instances of a Java programming course.  The study outlined
 several design considerations; among them, the authors emphasized the importance
 of developing chatbots in platforms that students and educators are familiar
-with and can easily access (i.e. Facebook Messenger) which was confirmed with
-\cite{hobert2019you} and \cite{fernoagua2018intelligent} studies. In addition, \cite{sjostrom2018designing} argued that a
-conceptualization of learners' questions could aid designers in integrating the
-appropriate types of questions that the chatbots should support for different
-courses.  \textcolor{black}{Some other authors}, like \cite{coronado2018cognitive}, proposed agents that
-store learning materials to be provided on demand to students, whereas the
-authors in \cite{crockett2017predicting} reported on tutoring systems, which can
+with and can easily access (i.e. Facebook Messenger), which was confirmed by
+\cite{hobert2019you} and \cite{fernoagua2018intelligent}. In addition, \cite{sjostrom2018designing} argued that 
+conceptualizing learners' questions could help designers integrate the
+appropriate types of questions that chatbots should support for different
+courses. Other authors, such as \cite{coronado2018cognitive}, have proposed agents that
+store learning materials to be provided on demand to students, while \cite{crockett2017predicting} 
+reported on tutoring systems that can
 perform initial assessments of students' understanding and provide learning
-material that would advance their understanding to the next level.
+materials to advance their understanding to the next level.
 
@@
 such as learning success and increased motivation are more important.  Therefore,
-to develop \textcolor{black}{effective chatbots for higher education, all stakeholders'
-(i.e. educators, students, institutions, etc) needs should be carefully
+to develop effective chatbots for higher education, the needs of all stakeholders
+(i.e. educators, students, institutions, etc) should be carefully
 collected and taken into consideration
 \cite{sjostrom2018designing,tsivitanidouusers}.
-These needs include, but are not limited to, student's learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance; this is why we focus in this paper on what the teachers are looking for in a TAM  (Technology Acceptance Model) and associated technologies like chatbots; both authors focus on what the teachers need in terms of the latter; this paper will focus on a wider perspective trying to ascertain what they are looking for in terms of general messaging technology.
-The classical literature \cite{tam91} already proposes that any adoption of technology must be tuned in to the user needs and experience.
-In this paper we will try to find out what those are in order to propose a successful model of adoption of chatbot technology}.
+These needs include, but are not limited to, student learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance.
+This is why we focus in this paper on what  teachers are looking for in a Technology Acceptance Model (TAM) and associated technologies like chatbots.
+Both authors focus on what teachers need in terms of the latter; this paper will focus on a wider perspective, trying to determine what they are looking for in terms of general messaging technology.
+The classical literature \cite{tam91} already proposes that any adoption of technology must be tuned to the user needs and experience.
+In this paper, we will try to find out what those are in order to propose a successful model of adoption of chatbot technology.
 

### 2023-01-07 edubots_surveys.Rnw
SotA - last paragraphs

@@
 students who need more attention and provide them with more educational resources
-relevant to their academic achievement. In addition, a recent study
-has analysed how the use of chatbots positively affected the learning outcomes
-of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
+relevant to their academic achievement. %In addition, a recent study
+%has analysed how the use of chatbots positively affected the learning outcomes
+%of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
 
@@
 
-Along this line of research, our previous work \cite{MoraChatbots2021:anon}
-aimed at analyzing the expectations of students on this regard; recent papers
+In line with this research, our previous work \cite{MoraChatbots2021:anon}
+aimed at analyzing the expectations of students in this regard. Recent papers
 have also analysed how the use of chatbots affected the learning outcomes of
 students in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper
-analysed conversational chatbots in an one-to-one setting, finding that learning
-really benefited from it. This is, once again, a proof of the benefit of
-chatbots in certain settings; however, there are some prior experiences, as well as needs, that might
+analysed conversational chatbots in a one-to-one setting, finding that learning
+truly benefited from it. This is, once again, an evidence of the benefit of
+chatbots in certain settings; however, there are some prior experiences, as well as needs, that may
 prevent the successful acceptance of the technology, and these are what we are
-trying to find out in this paper, together with what kind of features would improve
+trying to find out in this paper, alng with what kind of features would improve
 its acceptance.
 
-Besides, the present work is focused on the other key actor in this challenge,
-i.e. educators. \textcolor{black}{How they accepted chatbots} has been studied very recently by Chocarro et
+Besides, this work is focused on the other key actor in this challenge: 
+educators. How they accept chatbots has been studied very recently by Chocarro et
 al. \cite{doi:10.1080/03055698.2020.1850426}, who, by analyzing surveys, created
-a {\em technology acceptance model} that proposed a series of features that
-would make chatbots easier to accept; among them, formality of language as well
+a TAM that proposed a series of features that
+would make chatbots easier to accept, including formality of language as well
 as easiness and usefulness. The survey targeted primary and secondary education
-teachers, and was also more interested in the general use of chatbots in
+teachers and was also more interested in the general use of chatbots in
 education, not specifically in a classroom setting, seeking educational
-outcomes. However, they establish a series of results that are obviously
+outcomes. However, their results are obviously
 interesting and relevant for this work.
 
-We will present next the methodology we have followed to find out teachers'
-opinions.
+We will present next the methodology we followed to find out teachers' opinions.
 

### 2023-01-07 edubots_surveys.Rnw
:recycle: some sentences

--- 2023-01-07 edubots_surveys.Rnw
@@
 (i.e. video, audio, text) \cite{tang2017mobile}. Using these tools in
-higher education facilitates the delivery of personalized learning
-that occurs anytime anywhere, and promotes collaborative learning
+higher education can facilitate the delivery of personalized learning
+that occurs anytime anywhere, promote collaborative learning
 experiences and group discussions \cite{panah2020study}.
@@
 WhatsApp is, at least in most Western countries, the most popular MIM platform
-used by educators to provide assignments' feedback to students, support course
-discussions, and contribute resources in informal learning settings
+used by educators to \textcolor{black}{provide} assignments' feedback to students, support course
+discussions, and provide learning resources in informal learning settings
 \cite{panah2020study}.  Moreover, the use of WhatsApp in higher education could
@@
 between educators and students embedded in the social learning process
-\cite{gachago2015crossing}. However, this last paper also reflects the need for
+\cite{gachago2015crossing}; however, this last paper also reflects the need for
 learners to "take ownership of the tool" and the advantages of social learning
@@
 their learning \cite{gachago2015crossing} process.  This is why examining the
-role of MIM platforms in higher education is still a challenge, and why the opinions of
+role of MIM in higher education is still a challenge, and why the opinions of
 the teaching community towards them have to be examined, as we do in this paper.
@@
 % The Use of Chatbots in Higher Education
-The use of MIM platforms, although possibly valuable by itself, can be enhanced with the
-use of chatbots, which are conversational agents that normally dwell 
-synchronous conversations systems. The use of chatbots in higher education is still in its early stages
-\cite{yang2019opportunities}. Nevertheless, recent studies have shown their
+The use of MIM, although possibly valuable by itself, can be enhanced via the
+use of chatbots, which, being conversational agents, usually dwell in systems
+where synchronous conversations take place.  The use of conversational agents
+(chatbots) in higher education is still at its infancy
+\cite{yang2019opportunities}. Nevertheless, recent studies examining their
 positive impact on students' academic performance \cite{perez2020rediscovering}
-and engagement \cite{differ.chat,abbas2021onlinechat}, leading to a growing
+and engagement \cite{differ.chat,abbas2021onlinechat} have led to a growing
 interest in using this technology in the (possibly virtual) classroom. Indeed,
-the using chatbots to collect course feedback from students in higher
-education improved response quality and boosted enjoyment levels
-\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
-mobile devices or teaching strategies based on gamification
+the use of chatbots in collecting course feedback from students in higher
+education improved students' response quality and boosted their enjoyment levels
+\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using either tools
+such as mobile devices or teaching strategies based on gamification
 \cite{Yildirim2017} can improve student motivation. In this sense, the authors
-in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
+in \cite{Pimmer2019} \textcolor{black}{adopted a quasi-experimental, survey-based approach to
 report the positive impact of using instant messaging tools in boosting
-students' knowledge and mitigating their feelings of isolation.
-
-Several studies have been conducted to evaluate chatbots in higher education. For
-instance, a recent study was presented by Smutny and Schreiberova
-\cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
-Messenger, with a focus on identifying characteristics and quality metrics such as
-language, subject matter, and platform. Pérez and collaborators
-\cite{perez2020rediscovering} attempted to categorize educational chatbots attending to their purpose 
-as service-oriented or teaching-oriented. Service-oriented chatbots
-include those that provide service support, such as Ask Holly
-\cite{meetholly} and Dina \cite{santoso2018dinus}, which responds to
+students' knowledge and mitigating their feelings of isolation}.
+
+Several higher education chatbots' evaluation studies have been undertaken. For
+instance, a recent evaluation review study presented by Smutny and Schreiberova
+\cite{Smutny2020} examined 47 educational chatbots implemented in Facebook
+Messenger with the focus to identify characteristics and quality metrics such as
+language, subject matter and platform\textcolor{black}{, whereas the study undertaken by Pérez and collaborators
+\cite{perez2020rediscovering} aimed to categorize educational chatbots, according
+to their, purpose into service-oriented and teaching-oriented}. The first category
+includes those that provide service support such as the chatbot Ask Holly
+\cite{meetholly} and Dina \cite{santoso2018dinus}; both chatbots respond to
 students' questions about enrollment and registration. Ask L. U.
 \cite{LancasterUniversity_2019} answers students' frequently asked questions
-about schedules, grades, tutors, and societies. LISA \cite{dibitonto2018chatbot}
+about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot}
 and Differ \cite{differ.chat} facilitate breaking the ice between new students
 by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
-proposed a generic chatbot for university students that is able to answer 
-frequently asked questions. The University of Granada had
-Elvira, a built-in chatbot in its main web page \cite{MOREO20129} to perform the same task. In addition to being able
-to answer pre-established frequent questions, it did so from the website of
-the University of Granada using an inset persona, voiced by a real person, who
-lip-synced the answers. However, in the case of Elvira, the emphasis was on the
-authenticity of the synchronization rather than making the updated 
-of answered questions simpler, more interactive, or more open to the rest of the university staff using actual messaging platforms. In
+proposed a generic chatbot for university students that is able to answer to
+their frequently asked questions \textcolor{black}{and, for some time, the University of Granada had
+\textcolor{black}{Elvira} as a chatbot in its main web page \cite{MOREO20129} to perform that duty.} Besides being able
+to answer pre-established (frequent) questions, it did so from the website of
+the University of Granada using an inset \textcolor{black}{persona, voiced by a real person, who
+lip-synced the answers. The emphasis in the case of Elvira, however, was on the
+authenticity of the synchronization more than in making the update of questions
+answered simpler, or more interactive, or more open to the rest of the university staff, using actual messaging platforms. In
 most cases, the embedded search engine was able to provide more up-to-date
-and accurate answers than those provided by Elvira, which had to be updated
+and accurate answers than the ones provided by Elvira, which had to be updated
 by hand (and not too often).
-It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide a useful service.
-Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, which is the focus of this paper.
+It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide an useful service.
+Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, something which is the focus of this paper}.
 
@@
 assistant chatbot developed on the Telegram messaging platform. In this study,
-the Telegram platform was chosen because it is easy to use, students are familiar
+the Telegram platform is chosen because it is easy to use, students are familiar
 with its features, and it enables them to exchange messages in different formats
 (text, audio and video) \cite{fernoagua2018intelligent}. In addition, Telegram
-can operate on all devices and operating systems. The ``eduAssistant'' chatbot
-acts as an automatic agent in the teacher-content-student relationship, providing real-time
-feedback loops and a personalized learning experience relevant to the
+could operate on all devices and operating systems. The ``eduAssistant'' chatbot
+acts as an automatic agent in teacher-content-student, facilitating real-time
+feedback loops and providing a personalized learning experience relevant to the
 students' acquired skills and knowledge. Using this chatbot, educators can
@@
 their students and the chatbot assists those who need further help by giving
-them more hints and reporting it to the educator's dashboard
-\cite{fernoagua2018intelligent}. This can help educators identify
-students who need more attention and provide them with more educational resources
-relevant to their academic achievement. In addition, a recent study
+them more hints and reporting it to their educator's dashboard
+\cite{fernoagua2018intelligent}. This can help educators locate those
+students that need more attention and send them more educational resources
+relevant to their academic attainment. \textcolor{black}{In addition, a recent study
 has analysed how the use of chatbots positively affected the learning outcomes
-of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
+of students in a Chinese class \cite{doi:10.1177/0735633120929622}}.
 
@@
 
-A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
+A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the COVID-19 pandemic.
 The relation between the latter variable and the instructors’ sector was significant, $X^{2}_{(4, N = 282)} = 9.598$, $p =0.048$.
-The frequencies cross tabulated are given in Table \ref{tab:sector*covid}.
-In effect, this finding indicates that how teachers responded to the use of messaging apps during the pandemic and in particular, whether they changed their habits in the use of apps for teaching purposes, was related to their sector (university vs vocational).
+Table \ref{tab:sector*covid} shows the frequencies that are cross-tabulated vs.
+changes undertaken after the COVID pandemic.
+This finding suggests that how teachers used messaging apps during the pandemic, specifically whether they changed their habits for teaching purposes, was related to the sector (university vs vocational) in which they were working.
 %
@@
 % FB has made the analysis and processed data and contributed to the survey design.
-% NA has supervised the state of the art, and written the bulk of it, as well as contributed to discussion and conclusions.
+% NA has supervised the writing  of the section devoted to the state of the art and written the bulk of it, as well as contributed to discussion and conclusions.
 % OT has performed data analysis, and contributed to discussion and conclusions.

### 2023-01-07 edubots_surveys.Rnw
:recycle: some more sentences

@@
 
-The key findings of this study shed the light on educators’ preference to use
+The key findings of this study shed light on educators’ preference to use
 messaging applications that their institutions support. Technology adoption
@@
 
-% Noorhan suggest that using some simple things could increase the perceived usefulness - JJ
 As in many other methodologies that try to assess technology acceptance, answers to the survey suggest
@@
 
-% Future study (suggested by Noorhan): how COVID influenced adoption of these technologies.
-There are several future lines of work informed by our results of this
-survey. For instance, the rollout of extensive videoconferencing and virtual
+Our analysis of the results of this survey can be fed into several potential avenues for future research. For instance, the rollout of extensive videoconferencing and virtual
 teaching solutions that the COVID pandemic has brought has also taught us a

### 2023-01-07 edubots_surveys.Rnw
:warning: eliminate warnings with ggplot version 3.4.0

--- 2023-01-07 edubots_surveys.Rnw
@@
 df1[as.character(df1$Gender)!="PNTS", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformProvided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male')))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+ggplot(df1, aes(x = MessagingPlatformProvided, group = Gender)) + geom_bar(aes(y = after_stat(prop), fill = factor(after_stat(x))), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male')))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 #+ facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
@@
 survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformProvided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Experience, levels=c("0-05 years","06-15 years", "16-25 years", "> 25 years")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+ggplot(df1, aes(x = MessagingPlatformProvided, group = Experience)) + geom_bar(aes(y = after_stat(prop), fill = factor(after_stat(x))), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Experience, levels=c("0-05 years","06-15 years", "16-25 years", "> 25 years")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @
@@
 <<sector_provided, echo=FALSE, fig.width=10/2.54, fig.height=8.25/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())+ theme(axis.title.x=element_blank())
+ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Sector)) + geom_bar(aes(y = after_stat(prop), fill = factor(after_stat(x))), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())+ theme(axis.title.x=element_blank())
 @
@@
 survey.pilot.Discipline[as.character(survey.pilot.Discipline$Discipline)!="Other", ] -> survey.pilot.Discipline
-ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformProvided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + #facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other")))+ theme(axis.title.y=element_blank())
-facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering")))+ theme(axis.title.y=element_blank())+ theme(axis.title.x=element_blank())
+ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformProvided, group = Discipline)) +  geom_bar(aes(y = after_stat(prop), fill = factor(after_stat(x))), stat="count", show.legend = FALSE) +  scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") +   facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering"))) + theme(axis.title.y=element_blank(),axis.title.x=element_blank())
 @
@@
 df1[as.character(df1$Gender)!="PNTS", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male')))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Gender)) + geom_bar(aes(y = after_stat(prop), fill = factor(after_stat(x))), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male')))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @
@@
 survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Experience, levels=c("0-05 years","06-15 years", "16-25 years", "> 25 years")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Experience)) + geom_bar(aes(y = after_stat(prop), fill = factor(after_stat(x))), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Experience, levels=c("0-05 years","06-15 years", "16-25 years", "> 25 years")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @
@@
 <<sector_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=8.25/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformWhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+ggplot(survey.pilot, aes(x = MessagingPlatformWhatsApp, group = Sector)) + geom_bar(aes(y = after_stat(prop), fill = factor(after_stat(x))), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @
@@
 <<discipline_whatsapp, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformWhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformWhatsApp, group = Discipline)) + geom_bar(aes(y = after_stat(prop), fill = factor(after_stat(x))), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @
@@
 df1[as.character(df1$Gender)!="PNTS", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformTelegram, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male')))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+ggplot(df1, aes(x = MessagingPlatformTelegram, group = Gender)) + geom_bar(aes(y = after_stat(prop), fill = factor(after_stat(x))), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male')))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @
@@
 survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
-ggplot(df1, aes(x = MessagingPlatformTelegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Experience, levels=c("0-05 years","06-15 years", "16-25 years", "> 25 years")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+ggplot(df1, aes(x = MessagingPlatformTelegram, group = Experience)) + geom_bar(aes(y = after_stat(prop), fill = factor(after_stat(x))), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Experience, levels=c("0-05 years","06-15 years", "16-25 years", "> 25 years")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @
@@
 <<sector_telegram, echo=FALSE, fig.width=10/2.54, fig.height=8.25/2.54>>=
-ggplot(survey.pilot, aes(x = MessagingPlatformTelegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+ggplot(survey.pilot, aes(x = MessagingPlatformTelegram, group = Sector)) + geom_bar(aes(y = after_stat(prop), fill = factor(after_stat(x))), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @
@@
 <<discipline_telegram, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformTelegram, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
+ggplot(survey.pilot.Discipline, aes(x = MessagingPlatformTelegram, group = Discipline)) + geom_bar(aes(y = after_stat(prop), fill = factor(after_stat(x))), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering")))+ theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
 @
@@
 survey.pilot.postCOVID <- within(survey.pilot.postCOVID, PostCOVID.changes <- factor(PostCOVID.changes, levels=names(sort(table(PostCOVID.changes), decreasing=TRUE))))
-ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90), size=7) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = after_stat(count), group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90), size=7) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
 @
@@
 <<sector_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = after_stat(count), group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
 @
@@
 <<experience_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = after_stat(count), group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
 @
@@
 survey.pilot.postCOVID[as.character(survey.pilot.postCOVID$Discipline)!="No", ] -> survey.pilot.postCOVID
-ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Discipline, fill = Discipline ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = after_stat(count), group=Discipline, fill = Discipline ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
 @
@@
 
-A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the COVID-19 pandemic.
+A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the covid-19 pandemic.
 The relation between the latter variable and the instructors’ sector was significant, $X^{2}_{(4, N = 282)} = 9.598$, $p =0.048$.
-Table \ref{tab:sector*covid} shows the frequencies that are cross-tabulated vs.
-changes undertaken after the COVID pandemic.
-This finding suggests that how teachers used messaging apps during the pandemic, specifically whether they changed their habits for teaching purposes, was related to the sector (university vs vocational) in which they were working.
+The frequencies cross tabulated are given in Table \ref{tab:sector*covid}.
+In effect, this finding indicates that how teachers responded to the use of messaging apps during the pandemic and in particular, whether they changed their habits in the use of apps for teaching purposes, was related to their sector (university vs vocational).
 %
@@
 #survey.pilot.ChatbotType[as.character(survey.pilot.ChatbotType$Gender)!="PNTS", ] -> survey.pilot.ChatbotType
-ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = after_stat(count), group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
 @
@@
 <<sector_chatbottype, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = after_stat(count), group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
 @
@@
 <<experience_chatbottype, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
-ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = after_stat(count), group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
 @
@@
 survey.pilot.ChatbotType[as.character(survey.pilot.ChatbotType$Discipline)!="No", ] -> survey.pilot.ChatbotType
-ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Discipline, fill = Discipline ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
+ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = after_stat(count), group=Discipline, fill = Discipline ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
 @
@@
 df2 <- within(df2, Messaging.Organization <- factor(Messaging.Organization, levels=names(sort(table(Messaging.Organization), decreasing=TRUE))))
-ggplot(df2, aes( x = Messaging.Organization, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90))+coord_flip()+ theme(axis.title.y=element_blank())
+ggplot(df2, aes( x = Messaging.Organization, y = after_stat(count), group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90))+coord_flip()+ theme(axis.title.y=element_blank())
 @
@@
 survey.interaction[as.character(survey.interaction$Gender)!="PNTS", ] -> survey.interaction
-ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = after_stat(prop), fill = factor(after_stat(x))), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
 @
@@
 <<experience_sync, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
-ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Experience, levels=c("0-05 years","06-15 years", "16-25 years", "> 25 years"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = after_stat(prop), fill = factor(after_stat(x))), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Experience, levels=c("0-05 years","06-15 years", "16-25 years", "> 25 years"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
 @
@@
 %<<sector_synch, echo=FALSE, fig.width=10/2.54, fig.height=8.25/2.54>>=
-%ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+%ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Sector)) + geom_bar(aes(y = after_stat(prop), fill = factor(after_stat(x))), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
 %@
@@
 <<discipline_synch, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
-ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
+ggplot(survey.interaction, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = after_stat(prop), fill = factor(after_stat(x))), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
 @
@@
 % FB has made the analysis and processed data and contributed to the survey design.
-% NA has supervised the writing  of the section devoted to the state of the art and written the bulk of it, as well as contributed to discussion and conclusions.
+% NA has supervised the state of the art, and written the bulk of it, as well as contributed to discussion and conclusions.
 % OT has performed data analysis, and contributed to discussion and conclusions.

### 2023-01-08 edubots_surveys.Rnw

--- 2023-01-07 edubots_surveys.Rnw
@@
 % The Use of Chatbots in Higher Education
-The use of MIM, although possibly valuable by itself, can be enhanced via the
-use of chatbots, which, being conversational agents, usually dwell in systems
-where synchronous conversations take place.  The use of conversational agents
-(chatbots) in higher education is still at its infancy
-\cite{yang2019opportunities}. Nevertheless, recent studies examining their
+The use of MIM platforms, although possibly valuable by itself, can be enhanced with the
+use of chatbots, which are conversational agents that normally dwell 
+synchronous conversations systems. The use of chatbots in higher education is still in its early stages
+\cite{yang2019opportunities}. Nevertheless, recent studies have shown their
 positive impact on students' academic performance \cite{perez2020rediscovering}
-and engagement \cite{differ.chat,abbas2021onlinechat} have led to a growing
+and engagement \cite{differ.chat,abbas2021onlinechat}, leading to a growing
 interest in using this technology in the (possibly virtual) classroom. Indeed,
-the use of chatbots in collecting course feedback from students in higher
-education improved students' response quality and boosted their enjoyment levels
-\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using either tools
-such as mobile devices or teaching strategies based on gamification
+the using chatbots to collect course feedback from students in higher
+education improved response quality and boosted enjoyment levels
+\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
+mobile devices or teaching strategies based on gamification
 \cite{Yildirim2017} can improve student motivation. In this sense, the authors
-in \cite{Pimmer2019} \textcolor{black}{adopted a quasi-experimental, survey-based approach to
+in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
 report the positive impact of using instant messaging tools in boosting
-students' knowledge and mitigating their feelings of isolation}.
-
-Several higher education chatbots' evaluation studies have been undertaken. For
-instance, a recent evaluation review study presented by Smutny and Schreiberova
-\cite{Smutny2020} examined 47 educational chatbots implemented in Facebook
-Messenger with the focus to identify characteristics and quality metrics such as
-language, subject matter and platform\textcolor{black}{, whereas the study undertaken by Pérez and collaborators
-\cite{perez2020rediscovering} aimed to categorize educational chatbots, according
-to their, purpose into service-oriented and teaching-oriented}. The first category
-includes those that provide service support such as the chatbot Ask Holly
-\cite{meetholly} and Dina \cite{santoso2018dinus}; both chatbots respond to
+students' knowledge and mitigating their feelings of isolation.
+
+Several studies have been conducted to evaluate chatbots in higher education. For
+instance, a recent study was presented by Smutny and Schreiberova
+\cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
+Messenger, with a focus on identifying characteristics and quality metrics such as
+language, subject matter, and platform. Pérez and collaborators
+\cite{perez2020rediscovering} attempted to categorize educational chatbots attending to their purpose 
+as service-oriented or teaching-oriented. Service-oriented chatbots
+include those that provide service support, such as Ask Holly
+\cite{meetholly} and Dina \cite{santoso2018dinus}, which responds to
 students' questions about enrollment and registration. Ask L. U.
 \cite{LancasterUniversity_2019} answers students' frequently asked questions
-about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot}
+about schedules, grades, tutors, and societies. LISA \cite{dibitonto2018chatbot}
 and Differ \cite{differ.chat} facilitate breaking the ice between new students
 by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
-proposed a generic chatbot for university students that is able to answer to
-their frequently asked questions \textcolor{black}{and, for some time, the University of Granada had
-\textcolor{black}{Elvira} as a chatbot in its main web page \cite{MOREO20129} to perform that duty.} Besides being able
-to answer pre-established (frequent) questions, it did so from the website of
-the University of Granada using an inset \textcolor{black}{persona, voiced by a real person, who
-lip-synced the answers. The emphasis in the case of Elvira, however, was on the
-authenticity of the synchronization more than in making the update of questions
-answered simpler, or more interactive, or more open to the rest of the university staff, using actual messaging platforms. In
+proposed a generic chatbot for university students that is able to answer 
+frequently asked questions. The University of Granada had
+Elvira, a built-in chatbot in its main web page \cite{MOREO20129} to perform the same task. In addition to being able
+to answer pre-established frequent questions, it did so from the website of
+the University of Granada using an inset persona, voiced by a real person, who
+lip-synced the answers. However, in the case of Elvira, the emphasis was on the
+authenticity of the synchronization rather than making the updated 
+of answered questions simpler, more interactive, or more open to the rest of the university staff using actual messaging platforms. In
 most cases, the embedded search engine was able to provide more up-to-date
-and accurate answers than the ones provided by Elvira, which had to be updated
+and accurate answers than those provided by Elvira, which had to be updated
 by hand (and not too often).
-It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide an useful service.
-Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, something which is the focus of this paper}.
+It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide a useful service.
+Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, which is the focus of this paper.
 
@@
 their students and the chatbot assists those who need further help by giving
-them more hints and reporting it to their educator's dashboard
-\cite{fernoagua2018intelligent}. This can help educators locate those
-students that need more attention and send them more educational resources
-relevant to their academic attainment. \textcolor{black}{In addition, a recent study
-has analysed how the use of chatbots positively affected the learning outcomes
-of students in a Chinese class \cite{doi:10.1177/0735633120929622}}.
+them more hints and reporting it to the educator's dashboard
+\cite{fernoagua2018intelligent}. This can help educators identify
+students who need more attention and provide them with more educational resources
+relevant to their academic achievement. %In addition, a recent study
+%has analysed how the use of chatbots positively affected the learning outcomes
+%of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
 
 Despite its (arguably) successful implementation in different higher education
-institutions, over all in the fringes of educational activity, not in the actual
+institutions, particularly on the fringes of educational activity rather than actual
 student-teacher interaction, its implementation or deployment is not trivial.
-Some authors, for instance \cite{sjostrom2018designing} have proposed a
+Some authors, for instance \cite{sjostrom2018designing}, have proposed a
 conceptual architecture for the adoption of teaching-oriented chatbots in higher
 education.  This conceptual architecture is based on a systematic literature
-review of previous studies, examining the design of chatbots in higher
+review of previous studies examining the design of chatbots in higher
 education, as well as making a content analysis of student emails and discussion
-forum posts of four instances of a Java programming course.  The study outlined
+forum posts from four instances of a Java programming course.  The study outlined
 several design considerations; among them, the authors emphasized the importance
 of developing chatbots in platforms that students and educators are familiar
-with and can easily access (i.e. Facebook Messenger) which was confirmed with
-\cite{hobert2019you} and \cite{fernoagua2018intelligent} studies. In addition, \cite{sjostrom2018designing} argued that a
-conceptualization of learners' questions could aid designers in integrating the
-appropriate types of questions that the chatbots should support for different
-courses.  \textcolor{black}{Some other authors}, like \cite{coronado2018cognitive}, proposed agents that
-store learning materials to be provided on demand to students, whereas the
-authors in \cite{crockett2017predicting} reported on tutoring systems, which can
+with and can easily access (i.e. Facebook Messenger), which was confirmed by
+\cite{hobert2019you} and \cite{fernoagua2018intelligent}. In addition, \cite{sjostrom2018designing} argued that 
+conceptualizing learners' questions could help designers integrate the
+appropriate types of questions that chatbots should support for different
+courses. Other authors, such as \cite{coronado2018cognitive}, have proposed agents that
+store learning materials to be provided on demand to students, while \cite{crockett2017predicting} 
+reported on tutoring systems that can
 perform initial assessments of students' understanding and provide learning
-material that would advance their understanding to the next level.
+materials to advance their understanding to the next level.
 
@@
 such as learning success and increased motivation are more important.  Therefore,
-to develop \textcolor{black}{effective chatbots for higher education, all stakeholders'
-(i.e. educators, students, institutions, etc) needs should be carefully
+to develop effective chatbots for higher education, the needs of all stakeholders
+(i.e. educators, students, institutions, etc) should be carefully
 collected and taken into consideration
 \cite{sjostrom2018designing,tsivitanidouusers}.
-These needs include, but are not limited to, student's learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance; this is why we focus in this paper on what the teachers are looking for in a TAM  (Technology Acceptance Model) and associated technologies like chatbots; both authors focus on what the teachers need in terms of the latter; this paper will focus on a wider perspective trying to ascertain what they are looking for in terms of general messaging technology.
-The classical literature \cite{tam91} already proposes that any adoption of technology must be tuned in to the user needs and experience.
-In this paper we will try to find out what those are in order to propose a successful model of adoption of chatbot technology}.
-
-Along this line of research, our previous work \cite{MoraChatbots2021:anon}
-aimed at analyzing the expectations of students on this regard; recent papers
+These needs include, but are not limited to, student learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance.
+This is why we focus in this paper on what  teachers are looking for in a Technology Acceptance Model (TAM) and associated technologies like chatbots.
+Both authors focus on what teachers need in terms of the latter; this paper will focus on a wider perspective, trying to determine what they are looking for in terms of general messaging technology.
+The classical literature \cite{tam91} already proposes that any adoption of technology must be tuned to the user needs and experience.
+In this paper, we will try to find out what those are in order to propose a successful model of adoption of chatbot technology.
+
+In line with this research, our previous work \cite{MoraChatbots2021:anon}
+aimed at analyzing the expectations of students in this regard. Recent papers
 have also analysed how the use of chatbots affected the learning outcomes of
 students in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper
-analysed conversational chatbots in an one-to-one setting, finding that learning
-really benefited from it. This is, once again, a proof of the benefit of
-chatbots in certain settings; however, there are some prior experiences, as well as needs, that might
+analysed conversational chatbots in a one-to-one setting, finding that learning
+truly benefited from it. This is, once again, an evidence of the benefit of
+chatbots in certain settings; however, there are some prior experiences, as well as needs, that may
 prevent the successful acceptance of the technology, and these are what we are
-trying to find out in this paper, together with what kind of features would improve
+trying to find out in this paper, alng with what kind of features would improve
 its acceptance.
 
-Besides, the present work is focused on the other key actor in this challenge,
-i.e. educators. \textcolor{black}{How they accepted chatbots} has been studied very recently by Chocarro et
+Besides, this work is focused on the other key actor in this challenge: 
+educators. How they accept chatbots has been studied very recently by Chocarro et
 al. \cite{doi:10.1080/03055698.2020.1850426}, who, by analyzing surveys, created
-a {\em technology acceptance model} that proposed a series of features that
-would make chatbots easier to accept; among them, formality of language as well
+a TAM that proposed a series of features that
+would make chatbots easier to accept, including formality of language as well
 as easiness and usefulness. The survey targeted primary and secondary education
-teachers, and was also more interested in the general use of chatbots in
+teachers and was also more interested in the general use of chatbots in
 education, not specifically in a classroom setting, seeking educational
-outcomes. However, they establish a series of results that are obviously
+outcomes. However, their results are obviously
 interesting and relevant for this work.
 
-We will present next the methodology we have followed to find out teachers'
-opinions.
+We will present next the methodology we followed to find out teachers' opinions.
 

### 2023-01-08 edubots_surveys.Rnw
Accept suggestion
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>
Reviewed first discussion paragraphs

@@
 \cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
-mobile devices or teaching strategies based on gamification
+mobile devices along with gamification strategies
 \cite{Yildirim2017} can improve student motivation. In this sense, the authors
@@
 this case, the design of the survey introduced some ambiguity on what we really
-consider ``messaging technology'', that was eventually resolved by the answers;
-apparently, anything that sends messages (even if they are not instant, even if
-they do not have a dedicated application) was the concept in the mind of the
-surveyed.  \textcolor{black}{In this case, we would like
+consider ``messaging technology'', that was eventually resolved by the answers.
+Apparently, anything that sends messages (even if they are not instant, even if
+they do not have a dedicated application) was the concept in the minds of the
+surveyed. In this case, we would like
 to add a clarification. While we had in mind, as indicated by the possible answers,
@@
 it should be noted that, in most cases, they are not {\em instant} messaging
-apps in the way Telegram or Facebook Messenger are; in most cases they are
+apps in the way Telegram or Facebook Messenger are; in most cases, they are
 messaging facilities provided by learning management systems such as (usually)
@@
 their preference for the {\em provider} of the technology (the university itself, any
-company) as well as the {\em type} of technology (instant, app based messaging
-systems vs. web-based messaging systems integrated in another learning management system).}
+company) as well as the {\em type} of technology (instant, app-based messaging
+systems vs. web-based messaging systems integrated in another learning management system).
 
 This inclusion of university-provided messaging applications in
-the survey might explain why there are so few, just 6.7\%, that answer they do not
+the survey might explain why there are so few teachers, just 6.7\%, that answered they did not
 use any messaging application. In general, universities provide official channels
@@
 or the grades. The statistical mode is to use that kind of messaging. Some other
-people might not use it, but use some extraofficial or opt-in channels such as the other included in the survey; at the end, between these official and extraofficial channels most people cover their needs to communicate with students.
+teachers might not use it, but use some extraofficial or opt-in channels such as the others included in the survey; in the end, between these official and extra-official channels, most people cover their needs to communicate with students.
 This matches
@@
 changed their habits, although comparing women vs. men as well as those teaching social
-sciences show some significant difference. We do not have any kind of explanation for
+sciences show some significant differences. We do not have any kind of explanation for
 this behavior, other than technologies are perceived, and adopted, in a
@@
 
-The key findings of this study shed light on educators’ preference to use
+The key findings of this study shed light on educators’ preferences to use
 messaging applications that their institutions support. Technology adoption

### 2023-01-08 edubots_surveys.Rnw
rev discussion - following paragraphs

@@
 
-One of the most interesting questions that can arise from the analysis of the
+One of the most interesting questions arising from the analysis of the
 results, and that should require further study, is: Are teachers really aware
 of the possibilities of chatbots in the classroom? The survey
-only listed a few functionalities for the chatbots and just a few subjects selected
+only listed a few functionalities for the chatbots, and just a few subjects selected
 the option "Others". This may suggest that most teachers did not really understand
-at this point the actual potential of chatbots, since the responses listed were by no means exhaustive, and if the responders were more acquainted with the possibilities of the technology, possibly this response would have shown up many more times.
-Another way to look about it is
-that, unless you provide the specific instructions on how to use a
-tool, the teaching staff is already too busy or burn out to think about
-innovation.
-
-We can speculate that their opinions towards chatbots are informed by negative
-experiences with customer support chatbots, which is what most people will have
-experienced. This will probably require further study, but also will need to be
-taken into account when introducing chatbot technologies in the classroom:
-it will have to be as simple, and as satisfactory, as possible,
-to (possibly) change this existing perception.
+at this point the actual potential of chatbots, since the responses listed were by no means exhaustive.
+If the responders were more acquainted with the possibilities of this technology, this response would possibly have shown up many more times.
+Another way to look at it is that, unless you provide the specific instructions on how to use a
+tool, the teaching staff is already too busy or burnt out to think about innovation.
+
+We can speculate that teachers' opinions of chatbots are influenced by negative
+experiences with customer support chatbots, which is what most people are likely to have
+experienced. Further study may be needed to confirm this, but it is important to 
+keep in mind when introducing chatbot technologies in the classroom.
+To potentially change this existing perception, it will be necessary to make the chatbot as simple and satisfying to use as possible.
 
 Regarding gender grouping, both genders agree in their uses, so it seems not
-relevant at all. When looking at the plot containing the sector differentiation
-it is interesting to observe how university teachers prefer in a higher
-proportion to use them for grades and FAQs in comparison with other tertiary education teachers.
+relevant at all. However, when we look at the plot containing the sector differentiation,
+it is interesting to note that university teachers are more likely to use chatbots 
+for grades and FAQs compared to other tertiary education teachers.
 This seems reasonable as the frequency of seeing the students
 is lower at the University so, an automatic tool for grade notification for
-continuous evaluation seems more helpful.
-Furthermore, the high student/teacher
-ratios that university teachers have to deal with could be another reason to
-have a higher number of them willing to use chatbots for FAQs. This could
-ameliorate the number of misunderstandings and email overload that so many
-students might generate.
+continuous evaluation would be more helpful.
+Furthermore, the high student-to-teacher
+ratios that university teachers often face could be another reason why
+a higher number of them are willing to use chatbots for FAQs, as this could
+reduce misunderstandings and email overload from students.
 

### 2023-01-08 edubots_surveys.Rnw
rev conclusions - par 6-7

@@
 
-The results, when grouping by experience, confirm that
-experienced teachers are not afraid of changes and are willing to accept new
-technological challenges; at least, in the same way that younger teachers
-are. From this concrete plot it is interesting as well to observe the fact that very few
-young/inexperience teachers are willing to use chatbots for other uses. This
+The results, when grouping by teaching experience, confirm that
+experienced teachers are just as open to change and willing to embrace new
+technological challenges as younger teachers. 
+From this concrete plot it is interesting as well to observe the fact that very few
+young teachers are willing to use chatbots for other uses. This
 reinforces the hypothesis thrown at the beginning of this section that younger
@@
 
-As it appears in the responses presented above, teachers’ responses are equally
-distributed between positive and negative in relation to the media features:
-analytics, connectivity, and hidden phone number; that is, none of them is a
-prevailing factor on choosing one technology over another. However, for the features: familiarity,
-horizontally, sustainability and officiality the majority provided a positive
-response, designating their preference to these features. On the other hand, the
-majority of teachers seems to consider not valuable the presence of official
-formation, pluggability, unidirectionality and synchrony in the interaction
-media features of messaging apps.
+According to the responses presented above, teachers’ responses are evenly
+split between positive and negative in relation to the media features:
+analytics, connectivity, and hidden phone number. This means that none of these features is a
+deciding factor in their choice of technology. However, for features such as familiarity,
+horizontality, sustainability, and officiality the majority provided a positive
+response, designating their preference to these features. On the other hand, the majority of teachers
+do not seem to see the media features of official certification, pluggability, unidirectionality, 
+and synchrony as valuable in messaging apps.
 

### 2023-01-08 edubots_surveys.Rnw
rev conclusions - list
- Removed duplicates
- Simplified text

@@
 \begin{itemize}
- \item Teachers want to have support from their corresponding institution. This
-   is probably due to the strict European data regulations \textcolor{black}{on data protection},
-   but also to avoid the overhead required to \textcolor{black}{sign up new students every year.
-   In general support from specific formation and access to IT help desk for specific features
-   enhances the possibility of adoption by the teachers or the possibility of a successful
-   adoption that improves the learning outcomes. This is supported by the result of the two
-   surveys: they prefer whatever "messaging" application is provided by the university, and
-   also they value sustainability as well as "officiality" of the platform, as shown in
-   Table \ref{tab:interaction}}.
+ \item Teachers want to have support from their institutions. This
+   is probably due to the strict European data regulations on data protection,
+   but also to avoid the overhead required to sign up new students every year.
+   In general, additional support with specific formation and access to IT help desk for specific features
+   enhance the possibility of a successful adoption that improves the learning outcomes. This is supported by the result of the two
+   surveys: they prefer whatever "messaging" application is provided by their university, and
+   they the "officiality" of the platform, as shown in
+   Table \ref{tab:interaction}.
  \item Teachers need sustainability. The main reason is that implementing
    changes is expensive in terms of effort and prone to errors in the first
-   years of implementing new procedures, therefore, it is logical that if
-   chatbots or messaging platforms are to be introduced, they want this change
+   years. Therefore, it is logical that if
+   chatbots or messaging platforms are to be introduced, teachers want this change
    to be as permanent as possible.
  \item Keep it Simple.
-Media interaction requirements are simple and only a 2.4\% is requesting more features.
-This could be a sign of technological burn out produced by the previous and current courses where, due to the pandemic, the use of computer has increased significantly.
+Media interaction requirements are simple and only 2.4\% of teachers are requesting more features.
+This could be a sign of technological burnt out produced by the previous pandemic courses, when the use of computers significantly increased.
 \end{itemize}

### 2023-01-08 edubots_surveys.Rnw
last changes in discussion
- Removed part of the last paragraph and tried to simplify it
(specifically, the analysis regarding teachers' attitudes)

@@
 
-An analysis of survey questions related to RQ4 seems to indicate that teachers
-prefer to share an interaction space with their student, as
-shown in Tables \ref{tab:kindinteractions} and \ref{tab:interaction}, where a majority of responders
-indicate they {\em don't} want unidirectional communication; a preference of
-{\em horizontal} interaction, but also the answer to the kind of
-chatbots preferred that features FAQ bots prominently, which might indicate a
-need to delegate or offload part
-of the burden of answering, and attending, every single question posed by
-students. In an horizontal setting, other students can answer if the teacher
+The analysis of the questions related to RQ4 seems to indicate that teachers
+prefer to share an interaction space with their students. As
+shown in Tables \ref{tab:kindinteractions} and \ref{tab:interaction}, the majority of responders
+indicated that they {\em do not} want unidirectional communication, and that they prefer
+{\em horizontal} interaction. This point is reinforced by results on the kind of
+chatbots they preferred: most of them indicated FAQ bots, which might indicate a
+need to offload part of the burden of answering every single question posed by
+their students. In a horizontal setting, other students would answer if the teacher
 does not do it immediately. This might also be the reason why the possibility of
 using tools from which analytics can be extracted is also valued by teachers:
-that way, activity in the chat tool, answering questions, regularity, can all be
-observed and valued as part of the process of assessing achievement of learning
-objectives by students.
+in that way, the student activity in the chat tool, answering questions, or their regularity can all be
+assessed as part of the process of achieving learning objectives.
 
 % Only some COVID-response relationship.
-In our survey, we could not find an answer about the right moment for introducing chatbot technologies. Response to questions related to change of
-behavior during and after the first stay at home, stage of the pandemic do not suggest that a major (or minor)
-crisis could be an opportunity to introduce new technologies, since it does not
-bring major changes in attitude (as a minor "crisis" we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in
-  Spain, every 10 years or so.}), or simply introduction of new degrees. Although
-changes driven by external forces do offer the chance of piloting new technologies, they do not
-seem to bring internal changes in attitudes in the teaching staff (which, after all, is
+In our survey, we could not find an answer about the right moment to introducing chatbot technologies. The response to questions regarding to change of
+behavior during and after the first stay-at-home stage of the pandemic do not suggest that a major (or minor, such as new higher education laws or the introduction of new degrees) crisis could be an opportunity to introduce new technologies.
+The reason being that it does not
+bring major changes in attitude 
+%(as a minor "crisis" we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.}),
+%or simply the introduction of new degrees. 
+Although changes driven by external forces do offer the chance of piloting new technologies, they do not
+seem to bring internal changes in teachers' attitudes (which, after all, is
 bound to be the same). In absence of a clear answer in this direction, the right

### 2023-01-08 edubots_surveys.Rnw
Changes contributions

--- 2023-01-08 edubots_surveys.Rnw
@@
 % The Use of Chatbots in Higher Education
-The use of MIM platforms, although possibly valuable by itself, can be enhanced with the
-use of chatbots, which are conversational agents that normally dwell 
-synchronous conversations systems. The use of chatbots in higher education is still in its early stages
-\cite{yang2019opportunities}. Nevertheless, recent studies have shown their
+The use of MIM, although possibly valuable by itself, can be enhanced via the
+use of chatbots, which, being conversational agents, usually dwell in systems
+where synchronous conversations take place.  The use of conversational agents
+(chatbots) in higher education is still at its infancy
+\cite{yang2019opportunities}. Nevertheless, recent studies examining their
 positive impact on students' academic performance \cite{perez2020rediscovering}
-and engagement \cite{differ.chat,abbas2021onlinechat}, leading to a growing
+and engagement \cite{differ.chat,abbas2021onlinechat} have led to a growing
 interest in using this technology in the (possibly virtual) classroom. Indeed,
-the using chatbots to collect course feedback from students in higher
-education improved response quality and boosted enjoyment levels
-\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
-mobile devices along with gamification strategies
+the use of chatbots in collecting course feedback from students in higher
+education improved students' response quality and boosted their enjoyment levels
+\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using either tools
+such as mobile devices or teaching strategies based on gamification
 \cite{Yildirim2017} can improve student motivation. In this sense, the authors
-in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
+in \cite{Pimmer2019} \textcolor{black}{adopted a quasi-experimental, survey-based approach to
 report the positive impact of using instant messaging tools in boosting
-students' knowledge and mitigating their feelings of isolation.
-
-Several studies have been conducted to evaluate chatbots in higher education. For
-instance, a recent study was presented by Smutny and Schreiberova
-\cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
-Messenger, with a focus on identifying characteristics and quality metrics such as
-language, subject matter, and platform. Pérez and collaborators
-\cite{perez2020rediscovering} attempted to categorize educational chatbots attending to their purpose 
-as service-oriented or teaching-oriented. Service-oriented chatbots
-include those that provide service support, such as Ask Holly
-\cite{meetholly} and Dina \cite{santoso2018dinus}, which responds to
+students' knowledge and mitigating their feelings of isolation}.
+
+Several higher education chatbots' evaluation studies have been undertaken. For
+instance, a recent evaluation review study presented by Smutny and Schreiberova
+\cite{Smutny2020} examined 47 educational chatbots implemented in Facebook
+Messenger with the focus to identify characteristics and quality metrics such as
+language, subject matter and platform\textcolor{black}{, whereas the study undertaken by Pérez and collaborators
+\cite{perez2020rediscovering} aimed to categorize educational chatbots, according
+to their, purpose into service-oriented and teaching-oriented}. The first category
+includes those that provide service support such as the chatbot Ask Holly
+\cite{meetholly} and Dina \cite{santoso2018dinus}; both chatbots respond to
 students' questions about enrollment and registration. Ask L. U.
 \cite{LancasterUniversity_2019} answers students' frequently asked questions
-about schedules, grades, tutors, and societies. LISA \cite{dibitonto2018chatbot}
+about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot}
 and Differ \cite{differ.chat} facilitate breaking the ice between new students
 by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
-proposed a generic chatbot for university students that is able to answer 
-frequently asked questions. The University of Granada had
-Elvira, a built-in chatbot in its main web page \cite{MOREO20129} to perform the same task. In addition to being able
-to answer pre-established frequent questions, it did so from the website of
-the University of Granada using an inset persona, voiced by a real person, who
-lip-synced the answers. However, in the case of Elvira, the emphasis was on the
-authenticity of the synchronization rather than making the updated 
-of answered questions simpler, more interactive, or more open to the rest of the university staff using actual messaging platforms. In
+proposed a generic chatbot for university students that is able to answer to
+their frequently asked questions \textcolor{black}{and, for some time, the University of Granada had
+\textcolor{black}{Elvira} as a chatbot in its main web page \cite{MOREO20129} to perform that duty.} Besides being able
+to answer pre-established (frequent) questions, it did so from the website of
+the University of Granada using an inset \textcolor{black}{persona, voiced by a real person, who
+lip-synced the answers. The emphasis in the case of Elvira, however, was on the
+authenticity of the synchronization more than in making the update of questions
+answered simpler, or more interactive, or more open to the rest of the university staff, using actual messaging platforms. In
 most cases, the embedded search engine was able to provide more up-to-date
-and accurate answers than those provided by Elvira, which had to be updated
+and accurate answers than the ones provided by Elvira, which had to be updated
 by hand (and not too often).
-It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide a useful service.
-Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, which is the focus of this paper.
+It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide an useful service.
+Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, something which is the focus of this paper}.
 
@@
 their students and the chatbot assists those who need further help by giving
-them more hints and reporting it to the educator's dashboard
-\cite{fernoagua2018intelligent}. This can help educators identify
-students who need more attention and provide them with more educational resources
-relevant to their academic achievement. %In addition, a recent study
-%has analysed how the use of chatbots positively affected the learning outcomes
-%of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
+them more hints and reporting it to their educator's dashboard
+\cite{fernoagua2018intelligent}. This can help educators locate those
+students that need more attention and send them more educational resources
+relevant to their academic attainment. \textcolor{black}{In addition, a recent study
+has analysed how the use of chatbots positively affected the learning outcomes
+of students in a Chinese class \cite{doi:10.1177/0735633120929622}}.
 
 Despite its (arguably) successful implementation in different higher education
-institutions, particularly on the fringes of educational activity rather than actual
+institutions, over all in the fringes of educational activity, not in the actual
 student-teacher interaction, its implementation or deployment is not trivial.
-Some authors, for instance \cite{sjostrom2018designing}, have proposed a
+Some authors, for instance \cite{sjostrom2018designing} have proposed a
 conceptual architecture for the adoption of teaching-oriented chatbots in higher
 education.  This conceptual architecture is based on a systematic literature
-review of previous studies examining the design of chatbots in higher
+review of previous studies, examining the design of chatbots in higher
 education, as well as making a content analysis of student emails and discussion
-forum posts from four instances of a Java programming course.  The study outlined
+forum posts of four instances of a Java programming course.  The study outlined
 several design considerations; among them, the authors emphasized the importance
 of developing chatbots in platforms that students and educators are familiar
-with and can easily access (i.e. Facebook Messenger), which was confirmed by
-\cite{hobert2019you} and \cite{fernoagua2018intelligent}. In addition, \cite{sjostrom2018designing} argued that 
-conceptualizing learners' questions could help designers integrate the
-appropriate types of questions that chatbots should support for different
-courses. Other authors, such as \cite{coronado2018cognitive}, have proposed agents that
-store learning materials to be provided on demand to students, while \cite{crockett2017predicting} 
-reported on tutoring systems that can
+with and can easily access (i.e. Facebook Messenger) which was confirmed with
+\cite{hobert2019you} and \cite{fernoagua2018intelligent} studies. In addition, \cite{sjostrom2018designing} argued that a
+conceptualization of learners' questions could aid designers in integrating the
+appropriate types of questions that the chatbots should support for different
+courses.  \textcolor{black}{Some other authors}, like \cite{coronado2018cognitive}, proposed agents that
+store learning materials to be provided on demand to students, whereas the
+authors in \cite{crockett2017predicting} reported on tutoring systems, which can
 perform initial assessments of students' understanding and provide learning
-materials to advance their understanding to the next level.
+material that would advance their understanding to the next level.
 
@@
 such as learning success and increased motivation are more important.  Therefore,
-to develop effective chatbots for higher education, the needs of all stakeholders
-(i.e. educators, students, institutions, etc) should be carefully
+to develop \textcolor{black}{effective chatbots for higher education, all stakeholders'
+(i.e. educators, students, institutions, etc) needs should be carefully
 collected and taken into consideration
 \cite{sjostrom2018designing,tsivitanidouusers}.
-These needs include, but are not limited to, student learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance.
-This is why we focus in this paper on what  teachers are looking for in a Technology Acceptance Model (TAM) and associated technologies like chatbots.
-Both authors focus on what teachers need in terms of the latter; this paper will focus on a wider perspective, trying to determine what they are looking for in terms of general messaging technology.
-The classical literature \cite{tam91} already proposes that any adoption of technology must be tuned to the user needs and experience.
-In this paper, we will try to find out what those are in order to propose a successful model of adoption of chatbot technology.
-
-In line with this research, our previous work \cite{MoraChatbots2021:anon}
-aimed at analyzing the expectations of students in this regard. Recent papers
+These needs include, but are not limited to, student's learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance; this is why we focus in this paper on what the teachers are looking for in a TAM  (Technology Acceptance Model) and associated technologies like chatbots; both authors focus on what the teachers need in terms of the latter; this paper will focus on a wider perspective trying to ascertain what they are looking for in terms of general messaging technology.
+The classical literature \cite{tam91} already proposes that any adoption of technology must be tuned in to the user needs and experience.
+In this paper we will try to find out what those are in order to propose a successful model of adoption of chatbot technology}.
+
+Along this line of research, our previous work \cite{MoraChatbots2021:anon}
+aimed at analyzing the expectations of students on this regard; recent papers
 have also analysed how the use of chatbots affected the learning outcomes of
 students in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper
-analysed conversational chatbots in a one-to-one setting, finding that learning
-truly benefited from it. This is, once again, an evidence of the benefit of
-chatbots in certain settings; however, there are some prior experiences, as well as needs, that may
+analysed conversational chatbots in an one-to-one setting, finding that learning
+really benefited from it. This is, once again, a proof of the benefit of
+chatbots in certain settings; however, there are some prior experiences, as well as needs, that might
 prevent the successful acceptance of the technology, and these are what we are
-trying to find out in this paper, alng with what kind of features would improve
+trying to find out in this paper, together with what kind of features would improve
 its acceptance.
 
-Besides, this work is focused on the other key actor in this challenge: 
-educators. How they accept chatbots has been studied very recently by Chocarro et
+Besides, the present work is focused on the other key actor in this challenge,
+i.e. educators. \textcolor{black}{How they accepted chatbots} has been studied very recently by Chocarro et
 al. \cite{doi:10.1080/03055698.2020.1850426}, who, by analyzing surveys, created
-a TAM that proposed a series of features that
-would make chatbots easier to accept, including formality of language as well
+a {\em technology acceptance model} that proposed a series of features that
+would make chatbots easier to accept; among them, formality of language as well
 as easiness and usefulness. The survey targeted primary and secondary education
-teachers and was also more interested in the general use of chatbots in
+teachers, and was also more interested in the general use of chatbots in
 education, not specifically in a classroom setting, seeking educational
-outcomes. However, their results are obviously
+outcomes. However, they establish a series of results that are obviously
 interesting and relevant for this work.
 
-We will present next the methodology we followed to find out teachers' opinions.
+We will present next the methodology we have followed to find out teachers'
+opinions.
 
@@
 this case, the design of the survey introduced some ambiguity on what we really
-consider ``messaging technology'', that was eventually resolved by the answers.
-Apparently, anything that sends messages (even if they are not instant, even if
-they do not have a dedicated application) was the concept in the minds of the
-surveyed. In this case, we would like
+consider ``messaging technology'', that was eventually resolved by the answers;
+apparently, anything that sends messages (even if they are not instant, even if
+they do not have a dedicated application) was the concept in the mind of the
+surveyed.  \textcolor{black}{In this case, we would like
 to add a clarification. While we had in mind, as indicated by the possible answers,
@@
 it should be noted that, in most cases, they are not {\em instant} messaging
-apps in the way Telegram or Facebook Messenger are; in most cases, they are
+apps in the way Telegram or Facebook Messenger are; in most cases they are
 messaging facilities provided by learning management systems such as (usually)
@@
 their preference for the {\em provider} of the technology (the university itself, any
-company) as well as the {\em type} of technology (instant, app-based messaging
-systems vs. web-based messaging systems integrated in another learning management system).
+company) as well as the {\em type} of technology (instant, app based messaging
+systems vs. web-based messaging systems integrated in another learning management system).}
 
 This inclusion of university-provided messaging applications in
-the survey might explain why there are so few teachers, just 6.7\%, that answered they did not
+the survey might explain why there are so few, just 6.7\%, that answer they do not
 use any messaging application. In general, universities provide official channels
@@
 or the grades. The statistical mode is to use that kind of messaging. Some other
-teachers might not use it, but use some extraofficial or opt-in channels such as the others included in the survey; in the end, between these official and extra-official channels, most people cover their needs to communicate with students.
+people might not use it, but use some extraofficial or opt-in channels such as the other included in the survey; at the end, between these official and extraofficial channels most people cover their needs to communicate with students.
 This matches
@@
 changed their habits, although comparing women vs. men as well as those teaching social
-sciences show some significant differences. We do not have any kind of explanation for
+sciences show some significant difference. We do not have any kind of explanation for
 this behavior, other than technologies are perceived, and adopted, in a
@@
 
-One of the most interesting questions arising from the analysis of the
+One of the most interesting questions that can arise from the analysis of the
 results, and that should require further study, is: Are teachers really aware
 of the possibilities of chatbots in the classroom? The survey
-only listed a few functionalities for the chatbots, and just a few subjects selected
+only listed a few functionalities for the chatbots and just a few subjects selected
 the option "Others". This may suggest  that most teachers did not really understand
-at this point the actual potential of chatbots, since the responses listed were by no means exhaustive.
-If the responders were more acquainted with the possibilities of this technology, this response would possibly have shown up many more times.
-Another way to look at it is that, unless you provide the specific instructions on how to use a
-tool, the teaching staff is already too busy or burnt out to think about innovation.
-
-We can speculate that teachers' opinions of chatbots are influenced by negative
-experiences with customer support chatbots, which is what most people are likely to have
-experienced. Further study may be needed to confirm this, but it is important to 
-keep in mind when introducing chatbot technologies in the classroom.
-To potentially change this existing perception, it will be necessary to make the chatbot as simple and satisfying to use as possible.
+at this point the actual potential of chatbots, since the responses listed were by no means exhaustive, and if the responders were more acquainted with the possibilities of the technology, possibly this response would have shown up many more times.
+Another way to look about it is
+that, unless you provide the specific instructions on how to use a
+tool, the teaching staff is already too busy or burn out to think about
+innovation.
+
+We can speculate that their opinions towards chatbots are informed by negative
+experiences with customer support chatbots, which is what most people will have
+experienced. This will probably require further study, but also will need to be
+taken into account when introducing chatbot technologies in the classroom:
+it will have to be as simple, and as satisfactory, as possible,
+to (possibly) change this existing perception.
 
 Regarding gender grouping, both genders agree in their uses, so it seems not
-relevant at all. However, when we look at the plot containing the sector differentiation,
-it is interesting to note that university teachers are more likely to use chatbots 
-for grades and FAQs compared to other tertiary education teachers.
+relevant at all. When looking at the plot containing the sector differentiation
+it is interesting to observe how university teachers prefer in a higher
+proportion to use them for grades and FAQs in comparison with other tertiary education teachers.
 This seems reasonable as the frequency of seeing the students
 is lower at the University so, an automatic tool for grade notification for
-continuous evaluation would be more helpful.
-Furthermore, the high student-to-teacher
-ratios that university teachers often face could be another reason why
-a higher number of them are willing to use chatbots for FAQs, as this could
-reduce misunderstandings and email overload from students.
-
-The results, when grouping by teaching experience, confirm that
-experienced teachers are just as open to change and willing to embrace new
-technological challenges as younger teachers. 
-From this concrete plot it is interesting as well to observe the fact that very few
-young teachers are willing to use chatbots for other uses. This
+continuous evaluation seems more helpful.
+Furthermore, the high student/teacher
+ratios that university teachers have to deal with could be another reason to
+have a higher number of them willing to use chatbots for FAQs. This could
+ameliorate the number of misunderstandings and email overload that so many
+students might generate.
+
+The results, when grouping by experience, confirm that
+experienced teachers are not afraid of changes and are willing to accept new
+technological challenges; at least, in the same way that younger teachers
+are. From this concrete plot it is interesting as well to observe the fact that very few
+young/inexperience teachers are willing to use chatbots for other uses. This
 reinforces the hypothesis thrown at the beginning of this section that younger
@@
 
-According to the responses presented above, teachers’ responses are evenly
-split between positive and negative in relation to the media features:
-analytics, connectivity, and hidden phone number. This means that none of these features is a
-deciding factor in their choice of technology. However, for features such as familiarity,
-horizontality, sustainability, and officiality the majority provided a positive
-response, designating their preference to these features. On the other hand, the majority of teachers
-do not seem to see the media features of official certification, pluggability, unidirectionality, 
-and synchrony as valuable in messaging apps.
+As it appears in the responses presented above, teachers’ responses are equally
+distributed between positive and negative in relation to the media features:
+analytics, connectivity, and hidden phone number; that is, none of them is a
+prevailing factor on choosing one technology over another. However, for the features: familiarity,
+horizontally, sustainability and officiality the majority provided a positive
+response, designating their preference to these features. On the other hand, the
+majority of teachers seems to consider not valuable the presence of official
+formation, pluggability, unidirectionality and synchrony in the interaction
+media features of messaging apps.
 
@@
 
-The key findings of this study shed light on educators’ preferences to use
+The key findings of this study shed light on educators’ preference to use
 messaging applications that their institutions support. Technology adoption
@@
 % NA has supervised the writing  of the section devoted to the state of the art and written the bulk of it, as well as contributed to discussion and conclusions.
-% OT has performed data analysis, and contributed to discussion and conclusions.
+% OT has performed data analysis, and contributed to discussion and conclusions, as well as reviewed and rewritten part of the paper.
 % AG has contributed to the design of the survey, analysis, discussion and conclusions.

### 2023-01-08 edubots_surveys.Rnw
Rewriting part of her answers

@@
 
-\textcolor{black}{This study followed a quantitative approach towards addressing its research objective, by collecting rich data about the use of messaging applications and chatbots
-by educators in both universities and colleges\footnote{In Spain, they are called simply high schools, and deliver
-tertiary or associated degrees that do not have the consideration of university degrees}.
+This study has employed a quantitative approach in order to address its research objective.
+A good amount of data was collected on the usage of messaging applications and chatbots by educators in universities and colleges.\footnote{In Spain, higher education institutions generally known elsewhere as colleges, are called simply high schools, and deliver
+tertiary or associate degrees that do not have the consideration of university degrees.}
 To achieve this goal two online surveys were designed and developed using Google Forms
@@
 (i.e., sector, gender, degrees, discipline, age, teaching experience)
-followed by several multiple choice questions allowing the participants to choose multiple answers.}
+followed by several multiple choice questions allowing the participants to choose multiple answers.
 
 In the {\bf first survey}, the multiple choice questions are
-focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider
+focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers would consider
 useful for their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
@@
 
-\textcolor{black}{This survey was piloted by the authors of the paper and their colleagues before using it in the
+This survey was piloted by the authors of the paper and their colleagues before using it in the
 study.  All the comments collected from this trial were incorporated in the survey.
-We mainly used mailing lists, as well as Telegram groups,
-to post the survey link to reach out to more educators. The university form was sent to Spanish
+We primarily used mailing lists and Telegram groups to disseminate the survey link so that it would reach a larger number of educators. The form addressed at university teachers was sent to Spanish
 (mainly Andaluc\'{\i}a and Galicia) universities, and also  universities in Costa Rica and
-Mexico. The tertiary (non-university/college) teachers were based mainly in
+Mexico. The tertiary (non-university/college) teachers who received the form were based mainly in
 Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of
 2021, during the Covid-19 pandemic and while, at least in Spain, many universities had
-mandatory virtual teaching.}
+mandatory virtual teaching.
 

### 2023-01-08 edubots_surveys.Rnw
Eliminating markers

@@
 (68.4\%) and 89 at other tertiary education institutions (31.6\%).
-\textcolor{black}{From those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%) and 5 teachers preferred not to indicate their gender (1.8\%).
+From those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%) and 5 teachers preferred not to indicate their gender (1.8\%).
 In terms of age, the majority of the participants (n=111) in this survey was 45-55 years old (39.4\%), while 91 teachers were 35-45 (32.3\%), 46 were 25-35 (16.3\%) and 34 teachers were older than 55 (12.1\%).
-Last, 84 teachers had a teaching experience of 16-25 years (29.8\%), 75 teachers 6-15 years of experience (26.6\%), 69 teachers had 0-5 years of experience (24.5\%) and finally, 54 teachers had more than 25 years of teaching experience (19.1\%).}
+Last, 84 teachers had a teaching experience of 16-25 years (29.8\%), 75 teachers 6-15 years of experience (26.6\%), 69 teachers had 0-5 years of experience (24.5\%) and finally, 54 teachers had more than 25 years of teaching experience (19.1\%).
 
@@
 
-To avoid any bias and to be sure about the quality of the questionnaire, a panel board was consulted.
+To avoid any kind of bias and to ensure the quality of the questionnaire, a panel board was consulted.
 There were three questions for each of the items of the questionnaire which were: Clarity, Importance, Adequateness.

### 2023-01-08 edubots_surveys.Rnw
Small corrections

@@
 
-Next, we show the results and analyse them.
+In the next section, we present the results and analyse them.
 
@@
 
-A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the COVID-19 pandemic.
+Furthermore, a chi-square test of independence was performed in order to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the COVID-19 pandemic.
 The relation between the latter variable and the instructors’ sector was significant, $X^{2}_{(4, N = 282)} = 9.598$, $p =0.048$.
@@
 
-The most favorable use case for chatbots in
-Higher Education and vocational training is their use for the facilitation of an
-agenda formation (171 positive response, 60.6\%), followed by the FAQs use case
+The most beneficial use case for chatbots in higher education and vocational training is their ability to facilitate agenda formation and communication (171 positive response, 60.6\%), followed by the FAQs use case
 (148 positive responses, 52.5\%) and the sharing class material use case (136;

### 2023-01-08 edubots_surveys.Rnw
Small corrections

@@
 realized that there were some prior issues mainly related to the adoption of a
-technology, \textcolor{black}{i.e. chatbots}, that generally piggybacks on another, \textcolor{black}{i.e. messaging
-applications. Generally,} in a technology adoption model, perceived ease of use and
+technology, \textcolor{black}{i.e. chatbots}, that generally piggybacks on another, i.e. messaging
+applications. Generally, in a technology adoption model, perceived ease of use and
 perceived usefulness are essential. But it is going to be very difficult for

### 2023-01-08 edubots_surveys.Rnw
conclusions - par 1-2

--- 2023-01-08 edubots_surveys.Rnw
@@
 % The Use of Chatbots in Higher Education
-The use of MIM, although possibly valuable by itself, can be enhanced via the
-use of chatbots, which, being conversational agents, usually dwell in systems
-where synchronous conversations take place.  The use of conversational agents
-(chatbots) in higher education is still at its infancy
-\cite{yang2019opportunities}. Nevertheless, recent studies examining their
+The use of MIM platforms, although possibly valuable by itself, can be enhanced with the
+use of chatbots, which are conversational agents that normally dwell 
+synchronous conversations systems. The use of chatbots in higher education is still in its early stages
+\cite{yang2019opportunities}. Nevertheless, recent studies have shown their
 positive impact on students' academic performance \cite{perez2020rediscovering}
-and engagement \cite{differ.chat,abbas2021onlinechat} have led to a growing
+and engagement \cite{differ.chat,abbas2021onlinechat}, leading to a growing
 interest in using this technology in the (possibly virtual) classroom. Indeed,
-the use of chatbots in collecting course feedback from students in higher
-education improved students' response quality and boosted their enjoyment levels
-\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using either tools
-such as mobile devices or teaching strategies based on gamification
+the using chatbots to collect course feedback from students in higher
+education improved response quality and boosted enjoyment levels
+\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
+mobile devices along with gamification strategies
 \cite{Yildirim2017} can improve student motivation. In this sense, the authors
-in \cite{Pimmer2019} \textcolor{black}{adopted a quasi-experimental, survey-based approach to
+in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
 report the positive impact of using instant messaging tools in boosting
-students' knowledge and mitigating their feelings of isolation}.
-
-Several higher education chatbots' evaluation studies have been undertaken. For
-instance, a recent evaluation review study presented by Smutny and Schreiberova
-\cite{Smutny2020} examined 47 educational chatbots implemented in Facebook
-Messenger with the focus to identify characteristics and quality metrics such as
-language, subject matter and platform\textcolor{black}{, whereas the study undertaken by Pérez and collaborators
-\cite{perez2020rediscovering} aimed to categorize educational chatbots, according
-to their, purpose into service-oriented and teaching-oriented}. The first category
-includes those that provide service support such as the chatbot Ask Holly
-\cite{meetholly} and Dina \cite{santoso2018dinus}; both chatbots respond to
+students' knowledge and mitigating their feelings of isolation.
+
+Several studies have been conducted to evaluate chatbots in higher education. For
+instance, a recent study was presented by Smutny and Schreiberova
+\cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
+Messenger, with a focus on identifying characteristics and quality metrics such as
+language, subject matter, and platform. Pérez and collaborators
+\cite{perez2020rediscovering} attempted to categorize educational chatbots attending to their purpose 
+as service-oriented or teaching-oriented. Service-oriented chatbots
+include those that provide service support, such as Ask Holly
+\cite{meetholly} and Dina \cite{santoso2018dinus}, which responds to
 students' questions about enrollment and registration. Ask L. U.
 \cite{LancasterUniversity_2019} answers students' frequently asked questions
-about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot}
+about schedules, grades, tutors, and societies. LISA \cite{dibitonto2018chatbot}
 and Differ \cite{differ.chat} facilitate breaking the ice between new students
 by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
-proposed a generic chatbot for university students that is able to answer to
-their frequently asked questions \textcolor{black}{and, for some time, the University of Granada had
-\textcolor{black}{Elvira} as a chatbot in its main web page \cite{MOREO20129} to perform that duty.} Besides being able
-to answer pre-established (frequent) questions, it did so from the website of
-the University of Granada using an inset \textcolor{black}{persona, voiced by a real person, who
-lip-synced the answers. The emphasis in the case of Elvira, however, was on the
-authenticity of the synchronization more than in making the update of questions
-answered simpler, or more interactive, or more open to the rest of the university staff, using actual messaging platforms. In
+proposed a generic chatbot for university students that is able to answer 
+frequently asked questions. The University of Granada had
+Elvira, a built-in chatbot in its main web page \cite{MOREO20129} to perform the same task. In addition to being able
+to answer pre-established frequent questions, it did so from the website of
+the University of Granada using an inset persona, voiced by a real person, who
+lip-synced the answers. However, in the case of Elvira, the emphasis was on the
+authenticity of the synchronization rather than making the updated 
+of answered questions simpler, more interactive, or more open to the rest of the university staff using actual messaging platforms. In
 most cases, the embedded search engine was able to provide more up-to-date
-and accurate answers than the ones provided by Elvira, which had to be updated
+and accurate answers than those provided by Elvira, which had to be updated
 by hand (and not too often).
-It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide an useful service.
-Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, something which is the focus of this paper}.
+It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide a useful service.
+Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, which is the focus of this paper.
 
@@
 
-This study has employed a quantitative approach in order to address its research objective.
-A good amount of data was collected on the usage of messaging applications and chatbots by educators in universities and colleges.\footnote{In Spain, higher education institutions generally known elsewhere as colleges, are called simply high schools, and deliver
-tertiary or associate degrees that do not have the consideration of university degrees.}
+\textcolor{black}{This study followed a quantitative approach towards addressing its research objective, by collecting rich data about the use of messaging applications and chatbots
+by educators in both universities and colleges\footnote{In Spain, they are called simply high schools, and deliver
+tertiary or associated degrees that do not have the consideration of university degrees}.
 To achieve this goal two online surveys were designed and developed using Google Forms
@@
 (i.e., sector, gender, degrees, discipline, age, teaching experience)
-followed by several multiple choice questions allowing the participants to choose multiple answers.
+followed by several multiple choice questions allowing the participants to choose multiple answers.}
 
 In the {\bf first survey}, the multiple choice questions are
-focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers would consider
+focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider
 useful for their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
@@
 
-This survey was piloted by the authors of the paper and their colleagues before using it in the
+\textcolor{black}{This survey was piloted by the authors of the paper and their colleagues before using it in the
 study.  All the comments collected from this trial were incorporated in the survey.
-We primarily used mailing lists and Telegram groups to disseminate the survey link so that it would reach a larger number of educators. The form addressed at university teachers was sent to Spanish
+We mainly used mailing lists, as well as Telegram groups,
+to post the survey link to reach out to more educators. The university form was sent to Spanish
 (mainly Andaluc\'{\i}a and Galicia) universities, and also  universities in Costa Rica and
-Mexico. The tertiary (non-university/college) teachers who received the form were based mainly in
+Mexico. The tertiary (non-university/college) teachers were based mainly in
 Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of
 2021, during the Covid-19 pandemic and while, at least in Spain, many universities had
-mandatory virtual teaching.
+mandatory virtual teaching.}
 
@@
 (68.4\%) and 89 at other tertiary education institutions (31.6\%).
-From those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%) and 5 teachers preferred not to indicate their gender (1.8\%).
+\textcolor{black}{From those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%) and 5 teachers preferred not to indicate their gender (1.8\%).
 In terms of age, the majority of the participants (n=111) in this survey was 45-55 years old (39.4\%), while 91 teachers were 35-45 (32.3\%), 46 were 25-35 (16.3\%) and 34 teachers were older than 55 (12.1\%).
-Last, 84 teachers had a teaching experience of 16-25 years (29.8\%), 75 teachers 6-15 years of experience (26.6\%), 69 teachers had 0-5 years of experience (24.5\%) and finally, 54 teachers had more than 25 years of teaching experience (19.1\%).
+Last, 84 teachers had a teaching experience of 16-25 years (29.8\%), 75 teachers 6-15 years of experience (26.6\%), 69 teachers had 0-5 years of experience (24.5\%) and finally, 54 teachers had more than 25 years of teaching experience (19.1\%).}
 
@@
 
-To avoid any kind of bias and to ensure the quality of the questionnaire, a panel board was consulted.
+To avoid any bias and to be sure about the quality of the questionnaire, a panel board was consulted.
 There were three questions for each of the items of the questionnaire which were: Clarity, Importance, Adequateness.
@@
 
-One of the most interesting questions that can arise from the analysis of the
+One of the most interesting questions arising from the analysis of the
 results, and that should require further study, is: Are teachers really aware
 of the possibilities of chatbots in the classroom? The survey
-only listed a few functionalities for the chatbots and just a few subjects selected
+only listed a few functionalities for the chatbots, and just a few subjects selected
 the option "Others". This may suggest that most teachers did not really understand
-at this point the actual potential of chatbots, since the responses listed were by no means exhaustive, and if the responders were more acquainted with the possibilities of the technology, possibly this response would have shown up many more times.
-Another way to look about it is
-that, unless you provide the specific instructions on how to use a
-tool, the teaching staff is already too busy or burn out to think about
-innovation.
-
-We can speculate that their opinions towards chatbots are informed by negative
-experiences with customer support chatbots, which is what most people will have
-experienced. This will probably require further study, but also will need to be
-taken into account when introducing chatbot technologies in the classroom:
-it will have to be as simple, and as satisfactory, as possible,
-to (possibly) change this existing perception.
+at this point the actual potential of chatbots, since the responses listed were by no means exhaustive.
+If the responders were more acquainted with the possibilities of this technology, this response would possibly have shown up many more times.
+Another way to look at it is that, unless you provide the specific instructions on how to use a
+tool, the teaching staff is already too busy or burnt out to think about innovation.
+
+We can speculate that teachers' opinions of chatbots are influenced by negative
+experiences with customer support chatbots, which is what most people are likely to have
+experienced. Further study may be needed to confirm this, but it is important to 
+keep in mind when introducing chatbot technologies in the classroom.
+To potentially change this existing perception, it will be necessary to make the chatbot as simple and satisfying to use as possible.
 
 Regarding gender grouping, both genders agree in their uses, so it seems not
-relevant at all. When looking at the plot containing the sector differentiation
-it is interesting to observe how university teachers prefer in a higher
-proportion to use them for grades and FAQs in comparison with other tertiary education teachers.
+relevant at all. However, when we look at the plot containing the sector differentiation,
+it is interesting to note that university teachers are more likely to use chatbots 
+for grades and FAQs compared to other tertiary education teachers.
 This seems reasonable as the frequency of seeing the students
 is lower at the University so, an automatic tool for grade notification for
-continuous evaluation seems more helpful.
-Furthermore, the high student/teacher
-ratios that university teachers have to deal with could be another reason to
-have a higher number of them willing to use chatbots for FAQs. This could
-ameliorate the number of misunderstandings and email overload that so many
-students might generate.
-
-The results, when grouping by experience, confirm that
-experienced teachers are not afraid of changes and are willing to accept new
-technological challenges; at least, in the same way that younger teachers
-are. From this concrete plot it is interesting as well to observe the fact that very few
-young/inexperience teachers are willing to use chatbots for other uses. This
+continuous evaluation would be more helpful.
+Furthermore, the high student-to-teacher
+ratios that university teachers often face could be another reason why
+a higher number of them are willing to use chatbots for FAQs, as this could
+reduce misunderstandings and email overload from students.
+
+The results, when grouping by teaching experience, confirm that
+experienced teachers are just as open to change and willing to embrace new
+technological challenges as younger teachers. 
+From this concrete plot it is interesting as well to observe the fact that very few
+young teachers are willing to use chatbots for other uses. This
 reinforces the hypothesis thrown at the beginning of this section that younger
@@
 \begin{itemize}
- \item Teachers want to have support from their corresponding institution. This
-   is probably due to the strict European data regulations \textcolor{black}{on data protection},
-   but also to avoid the overhead required to \textcolor{black}{sign up new students every year.
-   In general support from specific formation and access to IT help desk for specific features
-   enhances the possibility of adoption by the teachers or the possibility of a successful
-   adoption that improves the learning outcomes. This is supported by the result of the two
-   surveys: they prefer whatever "messaging" application is provided by the university, and
-   also they value sustainability as well as "officiality" of the platform, as shown in
-   Table \ref{tab:interaction}}.
+ \item Teachers want to have support from their institutions. This
+   is probably due to the strict European data regulations on data protection,
+   but also to avoid the overhead required to sign up new students every year.
+   In general, additional support with specific formation and access to IT help desk for specific features
+   enhance the possibility of a successful adoption that improves the learning outcomes. This is supported by the result of the two
+   surveys: they prefer whatever "messaging" application is provided by their university, and
+   they the "officiality" of the platform, as shown in
+   Table \ref{tab:interaction}.
  \item Teachers need sustainability. The main reason is that implementing
    changes is expensive in terms of effort and prone to errors in the first
-   years of implementing new procedures, therefore, it is logical that if
-   chatbots or messaging platforms are to be introduced, they want this change
+   years. Therefore, it is logical that if
+   chatbots or messaging platforms are to be introduced, teachers want this change
    to be as permanent as possible.
  \item Keep it Simple.
-Media interaction requirements are simple and only a 2.4\% is requesting more features.
-This could be a sign of technological burn out produced by the previous and current courses where, due to the pandemic, the use of computer has increased significantly.
+Media interaction requirements are simple and only 2.4\% of teachers are requesting more features.
+This could be a sign of technological burnt out produced by the previous pandemic courses, when the use of computers significantly increased.
 \end{itemize}
 
-An analysis of survey questions related to RQ4 seems to indicate that teachers
-prefer to share an interaction space with their student, as
-shown in Tables \ref{tab:kindinteractions} and \ref{tab:interaction}, where a majority of responders
-indicate they {\em don't} want unidirectional communication; a preference of
-{\em horizontal} interaction, but also the answer to the kind of
-chatbots preferred that features FAQ bots prominently, which might indicate a
-need to delegate or offload part
-of the burden of answering, and attending, every single question posed by
-students. In an horizontal setting, other students can answer if the teacher
+The analysis of the questions related to RQ4 seems to indicate that teachers
+prefer to share an interaction space with their students. As
+shown in Tables \ref{tab:kindinteractions} and \ref{tab:interaction}, the majority of responders
+indicated that they {\em do not} want unidirectional communication, and that they prefer
+{\em horizontal} interaction. This point is reinforced by results on the kind of
+chatbots they preferred: most of them indicated FAQ bots, which might indicate a
+need to offload part of the burden of answering every single question posed by
+their students. In a horizontal setting, other students would answer if the teacher
 does not do it immediately. This might also be the reason why the possibility of
 using tools from which analytics can be extracted is also valued by teachers:
-that way, activity in the chat tool, answering questions, regularity, can all be
-observed and valued as part of the process of assessing achievement of learning
-objectives by students.
+in that way, the student activity in the chat tool, answering questions, or their regularity can all be
+assessed as part of the process of achieving learning objectives.
 
 % Only some COVID-response relationship.
-In our survey, we could not find an answer about the right moment for introducing chatbot technologies. Response to questions related to change of
-behavior during and after the first stay at home, stage of the pandemic do not suggest that a major (or minor)
-crisis could be an opportunity to introduce new technologies, since it does not
-bring major changes in attitude (as a minor "crisis" we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in
-  Spain, every 10 years or so.}), or simply introduction of new degrees. Although
-changes driven by external forces do offer the chance of piloting new technologies, they do not
-seem to bring internal changes in attitudes in the teaching staff (which, after all, is
+In our survey, we could not find an answer about the right moment to introducing chatbot technologies. The response to questions regarding to change of
+behavior during and after the first stay-at-home stage of the pandemic do not suggest that a major (or minor, such as new higher education laws or the introduction of new degrees) crisis could be an opportunity to introduce new technologies.
+The reason being that it does not
+bring major changes in attitude 
+%(as a minor "crisis" we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.}),
+%or simply the introduction of new degrees. 
+Although changes driven by external forces do offer the chance of piloting new technologies, they do not
+seem to bring internal changes in teachers' attitudes (which, after all, is
 bound to be the same). In absence of a clear answer in this direction, the right
@@
 
-The key findings of this study shed light on educators’ preference to use
-messaging applications that their institutions support. Technology adoption
-literature often \textcolor{black}{focuses} on users’ perceptions of the technology’s usefulness and
-ease of use as important prerequisites for successful adoption and
-utilization. Nevertheless, in higher education, institutions’ role in
-integrating these tools to their educational systems can improve the uptake of
-these applications and shape the social and educational experiences of their
-students. \textcolor{black}{To accomplish this fruitful integration}, institutions have to ensure that
-these messaging applications not only are GDPR (General Data Protection Regulation) compliant to keep students’ data
-secure, but also should provide IT support to all stakeholders who use the
-applications.
-
-Comparing these results with those obtained in student surveys
-in \cite{MoraChatbots2021:anon}, we have understood better the differences between the teachers’
-points of view and/or intentions and that of their students when using the
+The key findings of this study shed light on educators’ preferences for using
+messaging applications supported by their institutions. Technology adoption
+literature often focuses on users’ perceptions of the technology usefulness and
+ease of use as important factors for its successful adoption and
+utilization. Nevertheless, in higher education, institutions play a role in
+integrating these tools into their educational systems, which can improve the uptake of
+these applications and shape the social and educational experiences of 
+students. To achieve this successful integration, institutions should ensure that
+these messaging applications GDPR- (General Data Protection Regulation) compliant to protect students’ data and 
+provide IT support to all stakeholders who use the applications.
+
+Comparing these results with those obtained from student surveys
+in \cite{MoraChatbots2021:anon}, we have better understood the differences between teachers’
+and students' points of view and intentions when using the
 messaging applications in higher education.  Teachers tend to adopt technologies
-supported by their institutions.  The fact they do so could be caused by a desire to ensure that their
+supported by their institutions, which could be motivated by a desire to ensure that their
 universities can oversee their efforts in supporting their students during the
 learning process.  Another reason could be their familiarity with the technology
-provided by their institutions. On the other hand, students use the
-non-institution messaging applications to form informal discussion groups with
-their peers.  It is worth noting that peer support and collaboration is
+provided by their institutions. Meanwhile, students use 
+non-institution messaging applications to create informal discussion groups with
+their peers.  It is worth noting that peer support and collaboration are
 inseparable from learning \cite{timmis2012constant} and correlates positively
@@
 % NA has supervised the writing  of the section devoted to the state of the art and written the bulk of it, as well as contributed to discussion and conclusions.
-% OT has performed data analysis, and contributed to discussion and conclusions, as well as reviewed and rewritten part of the paper.
+% OT has performed data analysis, and contributed to discussion and conclusions.
 % AG has contributed to the design of the survey, analysis, discussion and conclusions.

### 2023-01-08 edubots_surveys.Rnw
reviewed conclusions - par 3,4

@@
 
-As in many other methodologies that try to assess technology acceptance, answers to the survey suggest
-that the introduction of simple, and institution-supported, instant messaging
+As with many other methodologies for assessing technology acceptance, the survey results suggest
+that the introduction of simple, and institution-supported instant messaging
 and chatbot technologies would increase the perceived usefulness (which is one
-of the key metrics in technology acceptance models). Since most institutions
+of the key metrics in technology acceptance models). Given that most institutions
 already have some {\em virtual campus} or learning management system, adding
-some easy automation, or connection to personal instant messaging tools, could
-really help onboard the learning community on these new technologies.
-
-What we are going to propose next is a possible process of
-technology introduction that is compatible with the conclusions of this study,
-but that would have to be piloted in order to check its value, and its
-relationship with better learning outcomes, as well as higher teacher
-satisfaction.
-Once that initial introduction of institutional messaging
-automation tools is done, teachers (and students as well) will
-probably prefer the kind of bots that alleviate bureaucratic or repetitive
-tasks, such as answering frequent questions or answers on class or assignment
-deadlines, as indicated by their answers to the respective
-questions. These will help the introduction of more complex chatbots that will
-affect more directly learning outcomes, such as chatbots that help students
-integrate in the class, or are able to identify (and address) learning problems
-in students or in groups of them. These should also be accompanied by
-analytics on student interaction, as well as possibly some natural language
-processing (in vernacular language) that will help assess the general mood of
-the class, and how different material (or external factors) affect it.
+some easy automation or connection to personal instant messaging tools could
+help introduce these new technologies to the learning community.
+
+Based on the discussion of this study, we propose a potential process for introducing
+technology that would need to be piloted in order to determine its value and its
+relationship to improved learning outcomes and higher teacher satisfaction.
+
+Initially, institutions should introduce messaging automation tools that help with bureaucratic or repetitive tasks, such as answering frequently asked questions or providing information on class or assignment deadlines.
+These chatbots will pave the way for more complex chatbots that will
+have a greater impact on learning outcomes, such as chatbots that help students
+integrate in class or identify and address learning problems
+in individual students or groups of them. These chatbots should also be accompanied by
+analytics on student interaction and possibly some natural language
+processing (in vernacular language) to help assess the general mood of
+the class and how different materials or external factors affect it.
 

### 2023-01-08 edubots_surveys.Rnw
reviewed conclusions - par 5-7

@@
 % No remarkable differences between different groups.
-This introduction of chatbots and chatbot technology will be helped by the fact
-that no discernible differences are found between different groups. Even if
-chatbots do have some potential for personalization or customization, based on
-the class material, student and teaching staff, the general introduction of the
+The introduction of chatbots and chatbot technology will be helped by the fact
+that no discernible differences are found between different groups. Even though
+chatbots do have some potential for personalization or customization based on
+the class material, student, and teaching staff, the general introduction of the
 technology can be done in a general way and for all disciplines, teaching
-experience and gender.
-
-At any rate, the general feeling that transpires from the survey is that it is
-essential for any institution to take into account the shareholder's opinion
+experience, and gender.
+
+Overall, the general feeling that transpires from the survey is that it is
+essential for any institution to take into account shareholders' opinions
 when introducing chatbots. This is true almost across the board, but in the case
@@
 
-One of the questions we made in the {\bf second survey}, related to
+One of the questions in the {\bf second survey}, which asked about 
 the messaging applications used by tertiary education teachers, opens a new line
-of inquiry about what they {\em perceive} as such, and about how it is used.
-Namely, the responses indicated that the teachers perceived as messaging
-application not only what is usually called a chat or instant messaging app such
-as WhatsApp or Microsoft Teams, but also the means provided by the university for
-communicating with the student, such as a feature of grading applications that
-will email the grade to the student. This implies that there is a need by
-teachers, communication with students, also mostly unidirectional, and that it
-does not matter so much how that need is covered. However, this will need careful
+of inquiry about what teachers {\em perceive} as such, and how it is used.
+Namely, the responses indicated that teachers perceived as messaging
+application not only traditional chats or instant messaging app such
+as WhatsApp or Microsoft Teams, but also the means provided by their university for
+communicating with students, such as a feature of grading applications that
+emails grades to students. This suggests that teachers have a need for communication with students, 
+which is mostly unidirectional, and that it
+does not matter as much how that need is met. However, this will need careful
 consideration, including how it ties with the automation of the learning
-experience that the chatbots bring.
+experience provided by chatbots.
 

### 2023-01-08 edubots_surveys.Rnw
reviewed conclusions - last paragraphs

@@
 
-Our analysis of the results of this survey can be fed into several potential avenues for future research. For instance, the rollout of extensive videoconferencing and virtual
+Our analysis of the survey results can inform several potential avenues for future research. 
+For instance, the rollout of extensive videoconferencing and virtual
 teaching solutions that the COVID pandemic has brought has also taught us a
-series of lessons. It increases isolation, for instance, and decreases the
-amount of synchronous contact that happens in the fringes of the classroom:
-teaching staff offices, before and after class. A future line of work would be
-focused on exactly this, and what kind of needs could be covered by chatbot
-technology. We will create a series of international surveys that will
-investigate this.
-
-Finally, the full extent of chatbot technology is not really being examined in
+series of lessons: it increases isolation, for instance, and decreases the
+amount of synchronous contact that happens in the fringes of the classroom (e.g. 
+teaching staff offices, or before and after class). A future line of research could 
+focus on these issues and explore how chatbot technology could address them. 
+%We will create a series of international surveys that will investigate this.
+
+Finally, the full extent of chatbot technology is not really examined in
 these surveys. They can be connected to natural language processing engines with
-sentiment analysis as well as other analytics. Examining the mood of the class,
-as response to new material, assignment, exams or external events might help
-will help any student-centered teaching strategy, which will help students (and
-teachers) reach their learning objectives. This line of work, however, will be
-based on the introduction of some pilot study, combined with initial opinion
-assessment on the students.
+sentiment analysis as well as other analytics. Examining the mood of the class such 
+as responses to new materials, assignments, exams or external events will help
+any student-centered teaching strategy, which will also help students (and
+teachers) achieve their learning objectives. This line of work, however, would require
+the introduction of some pilot study combined with initial opinion
+assessments from students.
 

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

--- 2023-01-08 edubots_surveys.Rnw
@@
 
-The most favorable use case for chatbots in
-Higher Education and vocational training is their use for the facilitation of an
-agenda formation (171 positive response, 60.6\%), followed by the FAQs use case
+The most beneficial use case for chatbots in higher education and vocational training is their ability to facilitate agenda formation and communication (171 positive responses, 60.6\%), followed by the FAQs use case
 (148 positive responses, 52.5\%) and the sharing class material use case (136;
@@
 \begin{itemize}
- \item Teachers want to have support from their institutions. This
-   is probably due to the strict European data regulations on data protection,
-   but also to avoid the overhead required to sign up new students every year.
-   In general, additional support with specific formation and access to IT help desk for specific features
-   enhance the possibility of a successful adoption that improves the learning outcomes. This is supported by the result of the two
-   surveys: they prefer whatever "messaging" application is provided by their university, and
-   they the "officiality" of the platform, as shown in
-   Table \ref{tab:interaction}.
+ \item Teachers want to have support from their corresponding institution. This
+   is probably due to the strict European data regulations \textcolor{black}{on data protection},
+   but also to avoid the overhead required to \textcolor{black}{sign up new students every year.
+   In general support from specific formation and access to IT help desk for specific features
+   enhances the possibility of adoption by the teachers or the possibility of a successful
+   adoption that improves the learning outcomes. This is supported by the result of the two
+   surveys: they prefer whatever "messaging" application is provided by the university, and
+   also they value sustainability as well as "officiality" of the platform, as shown in
+   Table \ref{tab:interaction}}.
  \item Teachers need sustainability. The main reason is that implementing
    changes is expensive in terms of effort and prone to errors in the first
-   years. Therefore, it is logical that if
-   chatbots or messaging platforms are to be introduced, teachers want this change
+   years of implementing new procedures, therefore, it is logical that if
+   chatbots or messaging platforms are to be introduced, they want this change
    to be as permanent as possible.
  \item Keep it Simple.
-Media interaction requirements are simple and only 2.4\% of teachers are requesting more features.
-This could be a sign of technological burnt out produced by the previous pandemic courses, when the use of computers significantly increased.
+Media interaction requirements are simple and only a 2.4\% is requesting more features.
+This could be a sign of technological burn out produced by the previous and current courses where, due to the pandemic, the use of computer has increased significantly.
 \end{itemize}
 
-The analysis of the questions related to RQ4 seems to indicate that teachers
-prefer to share an interaction space with their students. As
-shown in Tables \ref{tab:kindinteractions} and \ref{tab:interaction}, the majority of responders
-indicated that they {\em do not} want unidirectional communication, and that they prefer
-{\em horizontal} interaction. This point is reinforced by results on the kind of
-chatbots they preferred: most of them indicated FAQ bots, which might indicate a
-need to offload part of the burden of answering every single question posed by
-their students. In a horizontal setting, other students would answer if the teacher
+An analysis of survey questions related to RQ4 seems to indicate that teachers
+prefer to share an interaction space with their student, as
+shown in Tables \ref{tab:kindinteractions} and \ref{tab:interaction}, where a majority of responders
+indicate they {\em don't} want unidirectional communication; a preference of
+{\em horizontal} interaction, but also the answer to the kind of
+chatbots preferred that features FAQ bots prominently, which might indicate a
+need to delegate or offload part
+of the burden of answering, and attending, every single question posed by
+students. In an horizontal setting, other students can answer if the teacher
 does not do it immediately. This might also be the reason why the possibility of
 using tools from which analytics can be extracted is also valued by teachers:
-in that way, the student activity in the chat tool, answering questions, or their regularity can all be
-assessed as part of the process of achieving learning objectives.
+that way, activity in the chat tool, answering questions, regularity, can all be
+observed and valued as part of the process of assessing achievement of learning
+objectives by students.
 
 % Only some COVID-response relationship.
-In our survey, we could not find an answer about the right moment to introducing chatbot technologies. The response to questions regarding to change of
-behavior during and after the first stay-at-home stage of the pandemic do not suggest that a major (or minor, such as new higher education laws or the introduction of new degrees) crisis could be an opportunity to introduce new technologies.
-The reason being that it does not
-bring major changes in attitude 
-%(as a minor "crisis" we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.}),
-%or simply the introduction of new degrees. 
-Although changes driven by external forces do offer the chance of piloting new technologies, they do not
-seem to bring internal changes in teachers' attitudes (which, after all, is
+In our survey, we could not find an answer about the right moment for introducing chatbot technologies. Response to questions related to change of
+behavior during and after the first stay at home, stage of the pandemic do not suggest that a major (or minor)
+crisis could be an opportunity to introduce new technologies, since it does not
+bring major changes in attitude (as a minor "crisis" we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in
+  Spain, every 10 years or so.}), or simply introduction of new degrees. Although
+changes driven by external forces do offer the chance of piloting new technologies, they do not
+seem to bring internal changes in attitudes in the teaching staff (which, after all, is
 bound to be the same). In absence of a clear answer in this direction, the right
@@
 
-The key findings of this study shed light on educators’ preferences for using
-messaging applications supported by their institutions. Technology adoption
-literature often focuses on users’ perceptions of the technology usefulness and
-ease of use as important factors for its successful adoption and
-utilization. Nevertheless, in higher education, institutions play a role in
-integrating these tools into their educational systems, which can improve the uptake of
-these applications and shape the social and educational experiences of 
-students. To achieve this successful integration, institutions should ensure that
-these messaging applications GDPR- (General Data Protection Regulation) compliant to protect students’ data and 
-provide IT support to all stakeholders who use the applications.
-
-Comparing these results with those obtained from student surveys
-in \cite{MoraChatbots2021:anon}, we have better understood the differences between teachers’
-and students' points of view and intentions when using the
+The key findings of this study shed light on educators’ preference to use
+messaging applications that their institutions support. Technology adoption
+literature often \textcolor{black}{focuses} on users’ perceptions of the technology’s usefulness and
+ease of use as important prerequisites for successful adoption and
+utilization. Nevertheless, in higher education, institutions’ role in
+integrating these tools to their educational systems can improve the uptake of
+these applications and shape the social and educational experiences of their
+students. \textcolor{black}{To accomplish this fruitful integration}, institutions have to ensure that
+these messaging applications not only are GDPR (General Data Protection Regulation) compliant to keep students’ data
+secure, but also should provide IT support to all stakeholders who use the
+applications.
+
+Comparing these results with those obtained in student surveys
+in \cite{MoraChatbots2021:anon}, we have understood better the differences between the teachers’
+points of view and/or intentions and that of their students when using the
 messaging applications in higher education.  Teachers tend to adopt technologies
-supported by their institutions, which could be motivated by a desire to ensure that their
+supported by their institutions.  The fact they do so could be caused by a desire to ensure that their
 universities can oversee their efforts in supporting their students during the
 learning process.  Another reason could be their familiarity with the technology
-provided by their institutions. Meanwhile, students use 
-non-institution messaging applications to create informal discussion groups with
-their peers.  It is worth noting that peer support and collaboration are
+provided by their institutions. On the other hand, students use the
+non-institution messaging applications to form informal discussion groups with
+their peers.  It is worth noting that peer support and collaboration is
 inseparable from learning \cite{timmis2012constant} and correlates positively
@@
 
-As with many other methodologies for assessing technology acceptance, the survey results suggest
-that the introduction of simple, and institution-supported instant messaging
+As in many other methodologies that try to assess technology acceptance, answers to the survey suggest
+that the introduction of simple, and institution-supported, instant messaging
 and chatbot technologies would increase the perceived usefulness (which is one
-of the key metrics in technology acceptance models). Given that most institutions
+of the key metrics in technology acceptance models). Since most institutions
 already have some {\em virtual campus} or learning management system, adding
-some easy automation or connection to personal instant messaging tools could
-help introduce these new technologies to the learning community.
-
-Based on the discussion of this study, we propose a potential process for introducing
-technology that would need to be piloted in order to determine its value and its
-relationship to improved learning outcomes and higher teacher satisfaction.
-
-Initially, institutions should introduce messaging automation tools that help with bureaucratic or repetitive tasks, such as answering frequently asked questions or providing information on class or assignment deadlines.
-These chatbots will pave the way for more complex chatbots that will
-have a greater impact on learning outcomes, such as chatbots that help students
-integrate in class or identify and address learning problems
-in individual students or groups of them. These chatbots should also be accompanied by
-analytics on student interaction and possibly some natural language
-processing (in vernacular language) to help assess the general mood of
-the class and how different materials or external factors affect it.
+some easy automation, or connection to personal instant messaging tools, could
+really help onboard the learning community on these new technologies.
+
+What we are going to propose next is a possible process of
+technology introduction that is compatible with the conclusions of this study,
+but that would have to be piloted in order to check its value, and its
+relationship with better learning outcomes, as well as higher teacher
+satisfaction.
+Once that initial introduction of institutional messaging
+automation tools is done, teachers (and students as well) will
+probably prefer the kind of bots that alleviate bureaucratic or repetitive
+tasks, such as answering frequent questions or answers on class or assignment
+deadlines, as indicated by their answers to the respective
+questions. These will help the introduction of more complex chatbots that will
+affect more directly learning outcomes, such as chatbots that help students
+integrate in the class, or are able to identify (and address) learning problems
+in students or in groups of them. These should also be accompanied by
+analytics on student interaction, as well as possibly some natural language
+processing (in vernacular language) that will help assess the general mood of
+the class, and how different material (or external factors) affect it.
 

### 2023-01-09 edubots_surveys.Rnw
Just a typo
This fixes #70, found after the revision

@@
 % Describe the survey and population
-We collected responses from 282 teachers from Spain and Spanish Speaking
+We collected responses from 282 teachers from Spain and Spanish-speaking
 countries for \textit{survey1} and 205 for \textit{survey2}. The two forms were

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

--- 2023-01-09 edubots_surveys.Rnw
@@
 
-New technologies have been introduced and widely adopted into the classroom in recent years. However, in order to be successful, their application
-will require a certain amount of extra work and training for the teacher, as well as for the students.
-Training will help the two collectives involved acquire new skills and, potentially, pupils will acquire a greater level of engagement with the subject matter, which is usually the main objective.
-Even if several technologies are already in use inside the classroom, there is still room for adopting others.
-
+New technologies are being introduced and widely adopted into the classroom in the last years. However, in order to be successful, their application
+will require (many) extra work and training for the teacher, as well as for the students. Thus, both of them will acquire new skills and, potentially, pupils will
+get a higher engagement to the subject, which is usually the main objective. Even if several technologies are already in use inside the classroom, there is still room for adopting others.
 Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Given this,
@@
 
-Over the past decade, messaging apps like WhatsApp and Telegram have become increasingly popular in teaching at the secondary and higher education levels \cite{gachago2015crossing,mwakapina2016whatsapp,yin2016adoption,panah2020study}.
-By creating groups at various levels (e.g.
-class, assignment, course), teachers and students have been able to use these apps for bilateral or group-level communication.
-In addition to their primary function of communication, many messaging programs also allow the creation of applications that can act as users through open application programming interfaces (APIs), which are often available through a free or freemium model.
-
-This opens the door to the introduction of \textit{chatbots}, that is, autonomous agents able to communicate and interact with humans (or other chatbots) in a natural way \cite{Gong2008,differ.chat}, answering question and even posing their own ones to the user, in the classroom; in this limited environment, chatbots can appear as regular users, thus being close to passing a Turing Test \cite{moor2003turing}, which gives them certain characteristics that, again, can enhance student engagement.
-Chatbots implement different Artificial Intelligence techniques, such as natural language processing as well as, in some cases, learning; this is not a requirement, however, and in most cases they are simply applications that have a conversational interface, as opposed to a graphical user interface.
-
-These qualities have made education one of the most promising areas for chatbot applications today \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called
+In the last years, messaging applications such as WhatsApp or Telegram are being used in teaching scenarios mainly at secondary and higher education.
+In addition to their main use, some of these tools offer the possibility of interact with \textit{chatbots} (or just bots), even supporting synchronous conversation between the different
+parties \cite{differ.chat}. There is also possible to create a standalone chatbot application and attach it to a messaging tool through an API (Application Program Interface).
+
+\textit{Chatbots} are autonomous agents able to communicate and interact with humans (or other chatbots) in a human-like way \cite{Gong2008}, answering question and even posing their own ones to the user.
+Thus, we can say that they are close to passing a Turing Test \cite{moor2003turing}. They are implemented by means of different Artificial Intelligence techniques, such as natural language processing.
+Inside the plethora of possible applications of chatbots, education is one of the most prolific nowadays \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called
 \textit{personalized learning}, i.e. they adapt themselves to students’ pace of learning and provide online tutoring outside the classroom, which have been proved to be very effective increasing their
@@
 % The Use of Chatbots in Higher Education
-The use of MIM, although possibly valuable by itself, can be enhanced via the
-use of chatbots, which, being conversational agents, usually dwell in systems
-where synchronous conversations take place.  The use of conversational agents
-(chatbots) in higher education is still at its infancy
-\cite{yang2019opportunities}. Nevertheless, recent studies examining their
+The use of MIM platforms, although possibly valuable by itself, can be enhanced with the
+use of chatbots, which are conversational agents that normally dwell 
+synchronous conversations systems. The use of chatbots in higher education is still in its early stages
+\cite{yang2019opportunities}. Nevertheless, recent studies have shown their
 positive impact on students' academic performance \cite{perez2020rediscovering}
-and engagement \cite{differ.chat,abbas2021onlinechat} have led to a growing
+and engagement \cite{differ.chat,abbas2021onlinechat}, leading to a growing
 interest in using this technology in the (possibly virtual) classroom. Indeed,
-the use of chatbots in collecting course feedback from students in higher
-education improved students' response quality and boosted their enjoyment levels
-\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using either tools
-such as mobile devices or teaching strategies based on gamification
+the using chatbots to collect course feedback from students in higher
+education improved response quality and boosted enjoyment levels
+\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
+mobile devices along with gamification strategies
 \cite{Yildirim2017} can improve student motivation. In this sense, the authors
-in \cite{Pimmer2019} \textcolor{black}{adopted a quasi-experimental, survey-based approach to
+in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
 report the positive impact of using instant messaging tools in boosting
-students' knowledge and mitigating their feelings of isolation}.
-
-Several higher education chatbots' evaluation studies have been undertaken. For
-instance, a recent evaluation review study presented by Smutny and Schreiberova
-\cite{Smutny2020} examined 47 educational chatbots implemented in Facebook
-Messenger with the focus to identify characteristics and quality metrics such as
-language, subject matter and platform\textcolor{black}{, whereas the study undertaken by Pérez and collaborators
-\cite{perez2020rediscovering} aimed to categorize educational chatbots, according
-to their, purpose into service-oriented and teaching-oriented}. The first category
-includes those that provide service support such as the chatbot Ask Holly
-\cite{meetholly} and Dina \cite{santoso2018dinus}; both chatbots respond to
+students' knowledge and mitigating their feelings of isolation.
+
+Several studies have been conducted to evaluate chatbots in higher education. For
+instance, a recent study was presented by Smutny and Schreiberova
+\cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
+Messenger, with a focus on identifying characteristics and quality metrics such as
+language, subject matter, and platform. Pérez and collaborators
+\cite{perez2020rediscovering} attempted to categorize educational chatbots attending to their purpose 
+as service-oriented or teaching-oriented. Service-oriented chatbots
+include those that provide service support, such as Ask Holly
+\cite{meetholly} and Dina \cite{santoso2018dinus}, which responds to
 students' questions about enrollment and registration. Ask L. U.
 \cite{LancasterUniversity_2019} answers students' frequently asked questions
-about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot}
+about schedules, grades, tutors, and societies. LISA \cite{dibitonto2018chatbot}
 and Differ \cite{differ.chat} facilitate breaking the ice between new students
 by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
-proposed a generic chatbot for university students that is able to answer to
-their frequently asked questions \textcolor{black}{and, for some time, the University of Granada had
-\textcolor{black}{Elvira} as a chatbot in its main web page \cite{MOREO20129} to perform that duty.} Besides being able
-to answer pre-established (frequent) questions, it did so from the website of
-the University of Granada using an inset \textcolor{black}{persona, voiced by a real person, who
-lip-synced the answers. The emphasis in the case of Elvira, however, was on the
-authenticity of the synchronization more than in making the update of questions
-answered simpler, or more interactive, or more open to the rest of the university staff, using actual messaging platforms. In
+proposed a generic chatbot for university students that is able to answer 
+frequently asked questions. The University of Granada had
+Elvira, a built-in chatbot in its main web page \cite{MOREO20129} to perform the same task. In addition to being able
+to answer pre-established frequent questions, it did so from the website of
+the University of Granada using an inset persona, voiced by a real person, who
+lip-synced the answers. However, in the case of Elvira, the emphasis was on the
+authenticity of the synchronization rather than making the updated 
+of answered questions simpler, more interactive, or more open to the rest of the university staff using actual messaging platforms. In
 most cases, the embedded search engine was able to provide more up-to-date
-and accurate answers than the ones provided by Elvira, which had to be updated
+and accurate answers than those provided by Elvira, which had to be updated
 by hand (and not too often).
-It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide an useful service.
-Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, something which is the focus of this paper}.
-
-On the other hand, teaching-oriented chatbots are more sophisticated, as they
+It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide a useful service.
+Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, which is the focus of this paper.
+
+Contrarily to the mentioned chatbots that are focused on administrative tasks, teaching-oriented chatbots are more sophisticated, as they
 set personalized learning outcomes and monitor learning progress. For instance,
@@
 
-In the next section, we present the results and analyse them.
+Next, we show the results and analyse them.
 
@@
 % Describe the survey and population
-We collected responses from 282 teachers from Spain and Spanish-speaking
+We collected responses from 282 teachers from Spain and Spanish Speaking
 countries for \textit{survey1} and 205 for \textit{survey2}. The two forms were
@@
 realized that there were some prior issues mainly related to the adoption of a
-technology, \textcolor{black}{i.e. chatbots}, that generally piggybacks on another, i.e. messaging
-applications. Generally, in a technology adoption model, perceived ease of use and
+technology, \textcolor{black}{i.e. chatbots}, that generally piggybacks on another, \textcolor{black}{i.e. messaging
+applications. Generally,} in a technology adoption model, perceived ease of use and
 perceived usefulness are essential. But it is going to be very difficult for
@@
 
-Furthermore, a chi-square test of independence was performed in order to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the COVID-19 pandemic.
+A chi-square test of independence was performed to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the COVID-19 pandemic.
 The relation between the latter variable and the instructors’ sector was significant, $X^{2}_{(4, N = 282)} = 9.598$, $p =0.048$.
@@
 
-The most beneficial use case for chatbots in higher education and vocational training is their ability to facilitate agenda formation and communication (171 positive responses, 60.6\%), followed by the FAQs use case
+The most favorable use case for chatbots in
+Higher Education and vocational training is their use for the facilitation of an
+agenda formation (171 positive response, 60.6\%), followed by the FAQs use case
 (148 positive responses, 52.5\%) and the sharing class material use case (136;

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

@@
 Several studies have been conducted to evaluate chatbots in higher education. For
-instance, a recent study was presented by Smutny and Schreiberova
+instance, a thorough study was presented by Smutny and Schreiberova
 \cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
@@
 The classical literature \cite{tam91} already proposes that any adoption of technology must be tuned to the user needs and experience.
-In this paper, we will try to find out what those are in order to propose a successful model of adoption of chatbot technology.
+In this paper, we will try to find out what those are in order to propose a model to facilitate the adoption of chatbot technology.
 

### 2023-01-09 edubots_surveys.Rnw

--- 2023-01-09 edubots_surveys.Rnw
@@
 % The Use of Chatbots in Higher Education
-The use of MIM, although possibly valuable by itself, can be enhanced via the
-use of chatbots, which, being conversational agents, usually dwell in systems
-where synchronous conversations take place.  The use of conversational agents
-(chatbots) in higher education is still at its infancy
-\cite{yang2019opportunities}. Nevertheless, recent studies examining their
+The use of MIM platforms, although possibly valuable by itself, can be enhanced with the
+use of chatbots, which are conversational agents that normally dwell 
+synchronous conversations systems. The use of chatbots in higher education is still in its early stages
+\cite{yang2019opportunities}. Nevertheless, recent studies have shown their
 positive impact on students' academic performance \cite{perez2020rediscovering}
-and engagement \cite{differ.chat,abbas2021onlinechat} have led to a growing
+and engagement \cite{differ.chat,abbas2021onlinechat}, leading to a growing
 interest in using this technology in the (possibly virtual) classroom. Indeed,
-the use of chatbots in collecting course feedback from students in higher
-education improved students' response quality and boosted their enjoyment levels
-\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using either tools
-such as mobile devices or teaching strategies based on gamification
+the using chatbots to collect course feedback from students in higher
+education improved response quality and boosted enjoyment levels
+\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
+mobile devices along with gamification strategies
 \cite{Yildirim2017} can improve student motivation. In this sense, the authors
-in \cite{Pimmer2019} \textcolor{black}{adopted a quasi-experimental, survey-based approach to
+in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
 report the positive impact of using instant messaging tools in boosting
-students' knowledge and mitigating their feelings of isolation}.
-
-Several higher education chatbots' evaluation studies have been undertaken. For
-instance, a recent evaluation review study presented by Smutny and Schreiberova
-\cite{Smutny2020} examined 47 educational chatbots implemented in Facebook
-Messenger with the focus to identify characteristics and quality metrics such as
-language, subject matter and platform\textcolor{black}{, whereas the study undertaken by Pérez and collaborators
-\cite{perez2020rediscovering} aimed to categorize educational chatbots, according
-to their, purpose into service-oriented and teaching-oriented}. The first category
-includes those that provide service support such as the chatbot Ask Holly
-\cite{meetholly} and Dina \cite{santoso2018dinus}; both chatbots respond to
+students' knowledge and mitigating their feelings of isolation.
+
+Several studies have been conducted to evaluate chatbots in higher education. For
+instance, a thorough study was presented by Smutny and Schreiberova
+\cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
+Messenger, with a focus on identifying characteristics and quality metrics such as
+language, subject matter, and platform. Pérez and collaborators
+\cite{perez2020rediscovering} attempted to categorize educational chatbots attending to their purpose 
+as service-oriented or teaching-oriented. Service-oriented chatbots
+include those that provide service support, such as Ask Holly
+\cite{meetholly} and Dina \cite{santoso2018dinus}, which responds to
 students' questions about enrollment and registration. Ask L. U.
 \cite{LancasterUniversity_2019} answers students' frequently asked questions
-about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot}
+about schedules, grades, tutors, and societies. LISA \cite{dibitonto2018chatbot}
 and Differ \cite{differ.chat} facilitate breaking the ice between new students
 by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
-proposed a generic chatbot for university students that is able to answer to
-their frequently asked questions \textcolor{black}{and, for some time, the University of Granada had
-\textcolor{black}{Elvira} as a chatbot in its main web page \cite{MOREO20129} to perform that duty.} Besides being able
-to answer pre-established (frequent) questions, it did so from the website of
-the University of Granada using an inset \textcolor{black}{persona, voiced by a real person, who
-lip-synced the answers. The emphasis in the case of Elvira, however, was on the
-authenticity of the synchronization more than in making the update of questions
-answered simpler, or more interactive, or more open to the rest of the university staff, using actual messaging platforms. In
+proposed a generic chatbot for university students that is able to answer 
+frequently asked questions. The University of Granada had
+Elvira, a built-in chatbot in its main web page \cite{MOREO20129} to perform the same task. In addition to being able
+to answer pre-established frequent questions, it did so from the website of
+the University of Granada using an inset persona, voiced by a real person, who
+lip-synced the answers. However, in the case of Elvira, the emphasis was on the
+authenticity of the synchronization rather than making the updated 
+of answered questions simpler, more interactive, or more open to the rest of the university staff using actual messaging platforms. In
 most cases, the embedded search engine was able to provide more up-to-date
-and accurate answers than the ones provided by Elvira, which had to be updated
+and accurate answers than those provided by Elvira, which had to be updated
 by hand (and not too often).
-It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide an useful service.
-Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, something which is the focus of this paper}.
-
-On the other hand, teaching-oriented chatbots are more sophisticated, as they
+It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide a useful service.
+Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, which is the focus of this paper.
+
+Contrarily to the mentioned chatbots that are focused on administrative tasks, teaching-oriented chatbots are more sophisticated, as they
 set personalized learning outcomes and monitor learning progress. For instance,
@@
 such as learning success and increased motivation are more important.  Therefore,
-to develop \textcolor{black}{effective chatbots for higher education, all stakeholders'
-(i.e. educators, students, institutions, etc) needs should be carefully
+to develop effective chatbots for higher education, the needs of all stakeholders
+(i.e. educators, students, institutions, etc) should be carefully
 collected and taken into consideration
 \cite{sjostrom2018designing,tsivitanidouusers}.
-These needs include, but are not limited to, student's learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance; this is why we focus in this paper on what the teachers are looking for in a TAM  (Technology Acceptance Model) and associated technologies like chatbots; both authors focus on what the teachers need in terms of the latter; this paper will focus on a wider perspective trying to ascertain what they are looking for in terms of general messaging technology.
-The classical literature \cite{tam91} already proposes that any adoption of technology must be tuned in to the user needs and experience.
-In this paper we will try to find out what those are in order to propose a successful model of adoption of chatbot technology}.
-
-Along this line of research, our previous work \cite{MoraChatbots2021:anon}
-aimed at analyzing the expectations of students on this regard; recent papers
+These needs include, but are not limited to, student learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance.
+This is why we focus in this paper on what  teachers are looking for in a Technology Acceptance Model (TAM) and associated technologies like chatbots.
+Both authors focus on what teachers need in terms of the latter; this paper will focus on a wider perspective, trying to determine what they are looking for in terms of general messaging technology.
+The classical literature \cite{tam91} already proposes that any adoption of technology must be tuned to the user needs and experience.
+In this paper, we will try to find out what those are in order to propose a model to facilitate the adoption of chatbot technology.
+
+In line with this research, our previous work \cite{MoraChatbots2021:anon}
+aimed at analyzing the expectations of students in this regard. Recent papers
 have also analysed how the use of chatbots affected the learning outcomes of
 students in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper
-analysed conversational chatbots in an one-to-one setting, finding that learning
-really benefited from it. This is, once again, a proof of the benefit of
-chatbots in certain settings; however, there are some prior experiences, as well as needs, that might
+analysed conversational chatbots in a one-to-one setting, finding that learning
+truly benefited from it. This is, once again, an evidence of the benefit of
+chatbots in certain settings; however, there are some prior experiences, as well as needs, that may
 prevent the successful acceptance of the technology, and these are what we are
-trying to find out in this paper, together with what kind of features would improve
+trying to find out in this paper, alng with what kind of features would improve
 its acceptance.
 
-Besides, the present work is focused on the other key actor in this challenge,
-i.e. educators. \textcolor{black}{How they accepted chatbots} has been studied very recently by Chocarro et
+Besides, this work is focused on the other key actor in this challenge: 
+educators. How they accept chatbots has been studied very recently by Chocarro et
 al. \cite{doi:10.1080/03055698.2020.1850426}, who, by analyzing surveys, created
-a {\em technology acceptance model} that proposed a series of features that
-would make chatbots easier to accept; among them, formality of language as well
+a TAM that proposed a series of features that
+would make chatbots easier to accept, including formality of language as well
 as easiness and usefulness. The survey targeted primary and secondary education
-teachers, and was also more interested in the general use of chatbots in
+teachers and was also more interested in the general use of chatbots in
 education, not specifically in a classroom setting, seeking educational
-outcomes. However, they establish a series of results that are obviously
+outcomes. However, their results are obviously
 interesting and relevant for this work.
 
-We will present next the methodology we have followed to find out teachers'
-opinions.
+We will present next the methodology we followed to find out teachers' opinions.
 

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

--- 2023-01-09 edubots_surveys.Rnw
@@
 
-Contrarily to the mentioned chatbots that are focused on administrative tasks, teaching-oriented chatbots are more sophisticated, as they
+On the other hand, teaching-oriented chatbots are more sophisticated, as they
 set personalized learning outcomes and monitor learning progress. For instance,
@@
 prevent the successful acceptance of the technology, and these are what we are
-trying to find out in this paper, alng with what kind of features would improve
+trying to find out in this paper, along with what kind of features would improve
 its acceptance.
@@
 
-As in many other methodologies that try to assess technology acceptance, answers to the survey suggest
-that the introduction of simple, and institution-supported, instant messaging
+As with many other methodologies for assessing technology acceptance, the survey results suggest
+that the introduction of simple, and institution-supported instant messaging
 and chatbot technologies would increase the perceived usefulness (which is one
-of the key metrics in technology acceptance models). Since most institutions
+of the key metrics in technology acceptance models). Given that most institutions
 already have some {\em virtual campus} or learning management system, adding
-some easy automation, or connection to personal instant messaging tools, could
-really help onboard the learning community on these new technologies.
-
-What we are going to propose next is a possible process of
-technology introduction that is compatible with the conclusions of this study,
-but that would have to be piloted in order to check its value, and its
-relationship with better learning outcomes, as well as higher teacher
-satisfaction.
-Once that initial introduction of institutional messaging
-automation tools is done, teachers (and students as well) will
-probably prefer the kind of bots that alleviate bureaucratic or repetitive
-tasks, such as answering frequent questions or answers on class or assignment
-deadlines, as indicated by their answers to the respective
-questions. These will help the introduction of more complex chatbots that will
-affect more directly learning outcomes, such as chatbots that help students
-integrate in the class, or are able to identify (and address) learning problems
-in students or in groups of them. These should also be accompanied by
-analytics on student interaction, as well as possibly some natural language
-processing (in vernacular language) that will help assess the general mood of
-the class, and how different material (or external factors) affect it.
+some easy automation or connection to personal instant messaging tools could
+help introduce these new technologies to the learning community.
+
+Based on the discussion of this study, we propose a potential process for introducing
+technology that would need to be piloted in order to determine its value and its
+relationship to improved learning outcomes and higher teacher satisfaction.
+
+Initially, institutions should introduce messaging automation tools that help with bureaucratic or repetitive tasks, such as answering frequently asked questions or providing information on class or assignment deadlines.
+These chatbots will pave the way for more complex chatbots that will
+have a greater impact on learning outcomes, such as chatbots that help students
+integrate in class or identify and address learning problems
+in individual students or groups of them. These chatbots should also be accompanied by
+analytics on student interaction and possibly some natural language
+processing (in vernacular language) to help assess the general mood of
+the class and how different materials or external factors affect it.
 
 % No remarkable differences between different groups.
-This introduction of chatbots and chatbot technology will be helped by the fact
-that no discernible differences are found between different groups. Even if
-chatbots do have some potential for personalization or customization, based on
-the class material, student and teaching staff, the general introduction of the
+The introduction of chatbots and chatbot technology will be helped by the fact
+that no discernible differences are found between different groups. Even though
+chatbots do have some potential for personalization or customization based on
+the class material, student, and teaching staff, the general introduction of the
 technology can be done in a general way and for all disciplines, teaching
-experience and gender.
-
-At any rate, the general feeling that transpires from the survey is that it is
-essential for any institution to take into account the shareholder's opinion
+experience, and gender.
+
+Overall, the general feeling that transpires from the survey is that it is
+essential for any institution to take into account shareholders' opinions
 when introducing chatbots. This is true almost across the board, but in the case
@@
 
-One of the questions we made in the {\bf second survey}, related to
+One of the questions in the {\bf second survey}, which asked about 
 the messaging applications used by tertiary education teachers, opens a new line
-of inquiry about what they {\em perceive} as such, and about how it is used.
-Namely, the responses indicated that the teachers perceived as messaging
-application not only what is usually called a chat or instant messaging app such
-as WhatsApp or Microsoft Teams, but also the means provided by the university for
-communicating with the student, such as a feature of grading applications that
-will email the grade to the student. This implies that there is a need by
-teachers, communication with students, also mostly unidirectional, and that it
-does not matter so much how that need is covered. However, this will need careful
+of inquiry about what teachers {\em perceive} as such, and how it is used.
+Namely, the responses indicated that teachers perceived as messaging
+application not only traditional chats or instant messaging app such
+as WhatsApp or Microsoft Teams, but also the means provided by their university for
+communicating with students, such as a feature of grading applications that
+emails grades to students. This suggests that teachers have a need for communication with students, 
+which is mostly unidirectional, and that it
+does not matter as much how that need is met. However, this will need careful
 consideration, including how it ties with the automation of the learning
-experience that the chatbots bring.
-
-Our analysis of the results of this survey can be fed into several potential avenues for future research. For instance, the rollout of extensive videoconferencing and virtual
+experience provided by chatbots.
+
+Our analysis of the survey results can inform several potential avenues for future research. 
+For instance, the rollout of extensive videoconferencing and virtual
 teaching solutions that the COVID pandemic has brought has also taught us a
-series of lessons. It increases isolation, for instance, and decreases the
-amount of synchronous contact that happens in the fringes of the classroom:
-teaching staff offices, before and after class. A future line of work would be
-focused on exactly this, and what kind of needs could be covered by chatbot
-technology. We will create a series of international surveys that will
-investigate this.
-
-Finally, the full extent of chatbot technology is not really being examined in
+series of lessons: it increases isolation, for instance, and decreases the
+amount of synchronous contact that happens in the fringes of the classroom (e.g. 
+teaching staff offices, or before and after class). A future line of research could 
+focus on these issues and explore how chatbot technology could address them. 
+%We will create a series of international surveys that will investigate this.
+
+Finally, the full extent of chatbot technology is not really examined in
 these surveys. They can be connected to natural language processing engines with
-sentiment analysis as well as other analytics. Examining the mood of the class,
-as response to new material, assignment, exams or external events might help
-will help any student-centered teaching strategy, which will help students (and
-teachers) reach their learning objectives. This line of work, however, will be
-based on the introduction of some pilot study, combined with initial opinion
-assessment on the students.
+sentiment analysis as well as other analytics. Examining the mood of the class such 
+as responses to new materials, assignments, exams or external events will help
+any student-centered teaching strategy, which will also help students (and
+teachers) achieve their learning objectives. This line of work, however, would require
+the introduction of some pilot study combined with initial opinion
+assessments from students.
 

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

@@
 (i.e. video, audio, text) \cite{tang2017mobile}. Using these tools in
-higher education facilitates the delivery of personalized learning
+higher education institutions facilitates the delivery of personalized learning
 that occurs anytime anywhere, and promotes collaborative learning

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

@@
 interest in using this technology in the (possibly virtual) classroom. Indeed,
-the using chatbots to collect course feedback from students in higher
+using chatbots to collect course feedback from students in higher
 education improved response quality and boosted enjoyment levels
@@
 These needs include, but are not limited to, student learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance.
-This is why we focus in this paper on what  teachers are looking for in a Technology Acceptance Model (TAM) and associated technologies like chatbots.
 Both authors focus on what teachers need in terms of the latter; this paper will focus on a wider perspective, trying to determine what they are looking for in terms of general messaging technology.

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

@@
 
-Several studies have been conducted to evaluate chatbots in higher education. For
+Several studies to evaluate chatbots in higher education have been conducted. For
 instance, a recent study was presented by Smutny and Schreiberova
@@
 or the grades. The statistical mode is to use that kind of messaging. Some other
-teachers might not use it, but use some extraofficial or opt-in channels such as the others included in the survey; in the end, between these official and extra-official channels, most people cover their needs to communicate with students.
+teaching staff might not use it, but use some extraofficial or opt-in channels such as the others included in the survey; in the end, between these official and extra-official channels, most people cover their needs to communicate with students.
 This matches

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

@@
 
-We can speculate that teachers' opinions of chatbots are influenced by negative
+We can speculate that teaching staff's opinions of chatbots are influenced by negative
 experiences with customer support chatbots, which is what most people are likely to have

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

--- 2023-01-09 edubots_surveys.Rnw
@@
 
-We can speculate that teachers' opinions of chatbots are influenced by negative
-experiences with customer support chatbots, which is what most people are likely to have
+We can speculate that teaching staff's opinions of chatbots are influenced by negative
+experiences with chatbots used in customer support, which is what most people are likely to have
 experienced. Further study may be needed to confirm this, but it is important to 

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

@@
 keep in mind when introducing chatbot technologies in the classroom.
-To potentially change this existing perception, it will be necessary to make the chatbot as simple and satisfying to use as possible.
+To potentially change this existing perception, it will be necessary to make chatbots as simple and satisfying to use as possible.
 
@@
 relevant at all. However, when we look at the plot containing the sector differentiation,
-it is interesting to note that university teachers are more likely to use chatbots 
+it is interesting to note that university teaching staff are more likely to use chatbots 
 for grades and FAQs compared to other tertiary education teachers.

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

@@
 it is interesting to note that university teaching staff are more likely to use chatbots 
-for grades and FAQs compared to other tertiary education teachers.
+for grades and FAQs compared to other tertiary education teaching staff.
 This seems reasonable as the frequency of seeing the students

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

@@
 Furthermore, the high student-to-teacher
-ratios that university teachers often face could be another reason why
+ratios that university educators often face could be another reason why
 a higher number of them are willing to use chatbots for FAQs, as this could

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

@@
 experienced teachers are just as open to change and willing to embrace new
-technological challenges as younger teachers. 
+technological challenges as younger educators. 
 From this concrete plot it is interesting as well to observe the fact that very few

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

@@
 \begin{itemize}
- \item Teachers want to have support from their institutions. This
+ \item Teaching staff want to have support from their institutions. This
    is probably due to the strict European data regulations on data protection,
@@
    enhance the possibility of a successful adoption that improves the learning outcomes. This is supported by the result of the two
-   surveys: they prefer whatever "messaging" application is provided by their university, and
+   surveys: they prefer whatever ``messaging'' application provided by
    they the "officiality" of the platform, as shown in

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

@@
    surveys: they prefer whatever ``messaging'' application provided by
-   they the "officiality" of the platform, as shown in
+  as well as the fact that this application is the ``official'' for the university, as shown in
    Table \ref{tab:interaction}.

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

@@
  \item Keep it Simple.
-Media interaction requirements are simple and only 2.4\% of teachers are requesting more features.
+Media interaction requirements are simple and only 2.4\% of educators are requesting more features.
 This could be a sign of technological burnt out produced by the previous pandemic courses, when the use of computers significantly increased.
@@
 Although changes driven by external forces do offer the chance of piloting new technologies, they do not
-seem to bring internal changes in teachers' attitudes (which, after all, is
+seem to bring internal changes in educators' attitudes (which, after all, is
 bound to be the same). In absence of a clear answer in this direction, the right

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

@@
 
-The analysis of the questions related to RQ4 seems to indicate that teachers
+The analysis of the questions related to RQ4 seems to indicate that teaching staff
 prefer to share an interaction space with their students. As
@@
 the messaging applications used by tertiary education teachers, opens a new line
-of inquiry about what teachers {\em perceive} as such, and how it is used.
+of inquiry about what educators {\em perceive} as such, and how it is used.
 Namely, the responses indicated that teachers perceived as messaging

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

@@
 teaching solutions that the COVID pandemic has brought has also taught us a
-series of lessons: it increases isolation, for instance, and decreases the
+series of lessons: it increases isolation and decreases the
 amount of synchronous contact that happens in the fringes of the classroom (e.g. 

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

@@
 include those that provide service support, such as Ask Holly
-\cite{meetholly} and Dina \cite{santoso2018dinus}, which responds to
+\cite{meetholly} and Dina \cite{santoso2018dinus}, which respond to
 students' questions about enrollment and registration. Ask L. U.
@@
 proposed a generic chatbot for university students that is able to answer 
-frequently asked questions. The University of Granada had
+frequently asked questions. The University of Granada deployed
 Elvira, a built-in chatbot in its main web page \cite{MOREO20129} to perform the same task. In addition to being able

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

@@
 Several studies to evaluate chatbots in higher education have been conducted. For
-instance, a recent study was presented by Smutny and Schreiberova
+instance, a comprehensive study was presented by Smutny and Schreiberova
 \cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
@@
 use any messaging application. In general, universities provide official channels
-to communicate with students official academic information such as the exam schedule
+to send students academic information such as the exam schedule
 or the grades. The statistical mode is to use that kind of messaging. Some other

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

@@
 frequently asked questions. The University of Granada deployed
-Elvira, a built-in chatbot in its main web page \cite{MOREO20129} to perform the same task. In addition to being able
+Elvira, a chatbot embedded in its main web page \cite{MOREO20129} to perform the same task. In addition to being able
 to answer pre-established frequent questions, it did so from the website of
@@
 lip-synced the answers. However, in the case of Elvira, the emphasis was on the
-authenticity of the synchronization rather than making the updated 
+authenticity of the speech-mouth and face gestures synchronization rather than making updating
 of answered questions simpler, more interactive, or more open to the rest of the university staff using actual messaging platforms. In

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

@@
 authenticity of the speech-mouth and face gestures synchronization rather than making updating
-of answered questions simpler, more interactive, or more open to the rest of the university staff using actual messaging platforms. In
+answered questions simpler or more interactive for the administrative staff, or more open to the rest of the university staff using actual messaging platforms. In
 most cases, the embedded search engine was able to provide more up-to-date

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

@@
 them more hints and reporting it to the educator's dashboard
-\cite{fernoagua2018intelligent}. This can help educators identify
+\cite{fernoagua2018intelligent}. This could help educators identify
 students who need more attention and provide them with more educational resources

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

@@
 courses. Other authors, such as \cite{coronado2018cognitive}, have proposed agents that
-store learning materials to be provided on demand to students, while \cite{crockett2017predicting} 
+record learning materials to be provided on demand to students, while \cite{crockett2017predicting} 
 reported on tutoring systems that can

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

@@
    years. Therefore, it is logical that if
-   chatbots or messaging platforms are to be introduced, teachers want this change
+   chatbots or messaging platforms are to be introduced, teaching staff want this change
    to be as permanent as possible.
@@
 technology that would need to be piloted in order to determine its value and its
-relationship to improved learning outcomes and higher teacher satisfaction.
+relationship to improved learning outcomes and higher teacher staff satisfaction.
 

### 2023-01-09 edubots_surveys.Rnw
Review methods - par 1,2

@@
 
-\begin{abstract} % abstract
-Messaging platforms are applications, generally mediated by an app, desktop program or the web, mainly used for synchronous communication among users.
-As such, they have been widely adopted officially by higher education establishments, after little or no study of their impact and perception by the teachers.
-We think that the introduction of these new tools and the opportunities and challenges they have needs to be studied carefully in order to adopt the model, as well as the tool, that is the most adequate for all parties involved.
-We already studied the perception of these tools by students, in this paper we examine the teachers’
-experiences and perceptions through a survey that we validated with peers, and what they think these tools should make or serve so that it enhances students learning and helps them achieve their learning objectives.
-The survey has been distributed among tertiary education teachers, both in universitary and other kind of tertiary establishments, based in
-Spain (mainly) and Spanish-speaking countries. We have focused on collecting
-teachers' preferences and opinions on the introduction of messaging platforms in their day-to-day work, as well as other services attached to them, such as  chatbots.
-What we intend with this survey is to understand their needs and to gather
-information about the various educational use cases where these tools could be
-valuable. In addition, an analysis of how and when teachers’ opinions towards
-the use of these tools varies across gender, experience, and their discipline
-of specialization is presented. The key findings of this study highlight the
-factors that can contribute to the advancement of the adoption of messaging
-platforms and chatbots in higher education institutions to achieve the desired
-learning outcomes.
+\begin{abstract}
+  Messaging platforms are applications, generally mediated by an app, desktop
+  program or the web, mainly used for synchronous communication among users. As
+  such, they have been widely adopted officially by higher education
+  establishments, after little or no study of their impact and perception by the
+  teachers. We think that the introduction of these new tools and the
+  opportunities and challenges they have needs to be studied carefully in order
+  to adopt the model, as well as the tool, that is the most adequate for all
+  parties involved. We already studied the perception of these tools by
+  students, in this paper we examine the teachers’ experiences and perceptions
+  through a survey that we validated with peers, and what they think these tools
+  should make or serve so that it enhances students learning and helps them
+  achieve their learning objectives. The survey has been distributed among
+  tertiary education teachers, both in universitary and other kind of tertiary
+  establishments, based in Spain (mainly) and Spanish-speaking countries. We
+  have focused on collecting teachers' preferences and opinions on the
+  introduction of messaging platforms in their day-to-day work, as well as other
+  services attached to them, such as chatbots. What we intend with this survey
+  is to understand their needs and to gather information about the various
+  educational use cases where these tools could be valuable. In addition, an
+  analysis of how and when teachers’ opinions towards the use of these tools
+  varies across gender, experience, and their discipline of specialization is
+  presented. The key findings of this study highlight the factors that can
+  contribute to the advancement of the adoption of messaging platforms and
+  chatbots in higher education institutions to achieve the desired learning
+  outcomes.
 \end{abstract}
@@
 
-New technologies are being introduced and widely adopted into the classroom in the last years. However, in order to be successful, their application
-will require (many) extra work and training for the teacher, as well as for the students. Thus, both of them will acquire new skills and, potentially, pupils will
-get a higher engagement to the subject, which is usually the main objective. Even if several technologies are already in use inside the classroom, there is still room for adopting others.
-Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Given this,
-asking and analyzing user's opinions with regard to this scenario will help reaping the expected benefits of the technology.
-
-In the last years, messaging applications such as WhatsApp or Telegram are being used in teaching scenarios mainly at secondary and higher education.
-In addition to their main use, some of these tools offer the possibility of interact with \textit{chatbots} (or just bots), even supporting synchronous conversation between the different
-parties \cite{differ.chat}. There is also possible to create a standalone chatbot application and attach it to a messaging tool through an API (Application Program Interface).
-
-\textit{Chatbots} are autonomous agents able to communicate and interact with humans (or other chatbots) in a human-like way \cite{Gong2008}, answering question and even posing their own ones to the user.
-Thus, we can say that they are close to passing a Turing Test \cite{moor2003turing}. They are implemented by means of different Artificial Intelligence techniques, such as natural language processing.
-Inside the plethora of possible applications of chatbots, education is one of the most prolific nowadays \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called
-\textit{personalized learning}, i.e. they adapt themselves to students’ pace of learning and provide online tutoring outside the classroom, which have been proved to be very effective increasing their
-engagement and participation in the subjects \cite{agarwal2020}.
-Moreover chatbots' tutoring possibilities aid to reduce the stress of students \cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their teacher,
-or asking questions in front of the class.
-This situation normally conducts to a silence of the student and a later contact with the teacher by e-mail, which, in turn, will mean a workload for the teacher, that could be very
-significant given the existing disproportion between number of students per each teacher.
-
-Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning
-experience \cite{Griol2014,kim2020}. In addition, using an automated system such as a chatbot will allow teachers to spend more time on  other topics that students struggle with.
+New technologies have been introduced and widely adopted into the classroom in
+recent years. However, in order to be successful, their application will require
+a certain amount of extra work and training for the teacher, as well as for the
+students. Training will help the two collectives involved acquire new skills
+and, potentially, pupils will acquire a greater level of engagement with the
+subject matter, which is usually the main objective. Even if several
+technologies are already in use inside the classroom, there is still room for
+adopting others.
+
+However, the success of this adoption largely depends on the willingness and
+ability of teachers to embrace it, as they are the primary agents in this new
+educational approach. As such, gathering and assessing feedback from these users
+will be crucial in realizing the potential benefits of the technology.
+
+Over the past decade, messaging apps like WhatsApp and Telegram have become
+increasingly popular in teaching at the secondary and higher education levels
+\cite{gachago2015crossing,mwakapina2016whatsapp,yin2016adoption,panah2020study}. By
+creating groups at various levels (e.g. class, assignment, course), teachers and
+students have been able to use these apps for bilateral or group-level
+communication. In addition to their primary function of communication, many
+messaging programs also allow the creation of applications that can act as users
+through open application programming interfaces (APIs), which are often
+available through a free or freemium model.
+
+This opens the door to the introduction of \textit{chatbots}, that is,
+autonomous agents able to communicate and interact with humans (or other
+chatbots) in a natural way \cite{Gong2008,differ.chat}, answering question and
+even posing their own ones to the user, in the classroom; in this limited
+environment, chatbots can appear as regular users, thus being close to passing a
+Turing Test \cite{moor2003turing}, which gives them certain characteristics
+that, again, can enhance student engagement. Chatbots implement different
+Artificial Intelligence techniques, such as natural language processing as well
+as, in some cases, learning; this is not a requirement, however, and in most
+cases they are simply applications that have a conversational interface, as
+opposed to a graphical user interface.
+
+These qualities have made education one of the most promising areas for chatbot
+applications today \cite{clarizia2018,Smutny2020}. In this domain, they
+facilitate the so-called \textit{personalized learning}, i.e. they adapt
+themselves to students’ pace of learning and provide online tutoring outside the
+classroom, which have been proved to be very effective increasing their
+engagement and participation in the subjects \cite{agarwal2020}. Moreover
+chatbots' tutoring possibilities aid to reduce the stress of students
+\cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their
+teacher, or asking questions in front of the class. This situation normally
+conducts to a silence of the student and a later contact with the teacher by
+e-mail, which, in turn, will mean a workload for the teacher, that could be very
+significant given the existing disproportion between number of students per each
+teacher.
+
+Hence, the chatbot technology has a potential to mitigate this problem by
+providing answers to students’ questions and facilitating a dynamic and
+autonomous learning experience \cite{Griol2014,kim2020}. In addition, using an
+automated system such as a chatbot will allow teachers to spend more time on
+other topics that students struggle with.
 
@@
 focus of the % EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
-unnamed European project, the main sponsor of this study, is to explore best practices and innovative use of chatbots,
-and to create a learning community of educators in higher education institutions.
-Researchers and teachers participating in this project have developed several studies. Most of these works have been focused on how the
-messaging applications and/or chatbots are normally applied to deliver personalized learning in classrooms that occurs anytime anywhere,
-promote collaborative learning experiences, group discussions \cite{panah2020study} and boost students' sense of belonging to their institutions
-\cite{abbas2021onlinechat}.
-The majority of these studies were conducted focusing on the teachers' perspectives, so this paper aims to provide more conclusions regarding
-their opinions and needs, as well as the existing challenges or opportunities that arise when adopting these technologies in classrooms. This will lead to clarify
-how they can positively contribute to enhancing the learning process in higher education institutions.
+unnamed European project, the main sponsor of this study, is to explore best
+practices and innovative use of chatbots, and to create a learning community of
+educators in higher education institutions.  Researchers and teachers
+participating in this project have developed several studies. Most of these
+works have been focused on how messaging applications and/or chatbots are
+normally applied to deliver personalized learning in classrooms that occurs
+anytime anywhere, and promote collaborative learning experiences or group
+discussions \cite{panah2020study}, and boost students' sense of belonging to
+their institutions \cite{abbas2021onlinechat}.  The majority of these studies
+were conducted focusing on the teachers' perspectives, so this paper aims to
+provide more conclusions regarding their opinions and needs, as well as the
+existing challenges or opportunities that arise when adopting these technologies
+in classrooms. This will lead to clarify how they can positively contribute to
+enhancing the learning process in higher education institutions.
 
@@
  \item The first phase aimed to collect feedback from students about their
-  students’ preferences of tools/applications for chatting and
-  messaging, how they use them in educational context, who they like to be
-  with in the class messaging groups, and their expectations of chatbots
-  in assisting them during their learning process. Therefore, two surveys
-  for bachelor and master degree students at the University of Granada (Spain)
-  were designed and answers from more than 250 students were collected. The key
-  findings of the students' surveys reveal that they prefer to use messaging
-  familiar applications, such as Telegram or WhatsApp.
-  Students also expressed interest in chatbots that can assist them with
-  organizing their course schedules, help them access their assignment grades
-  and facilitate searching for resources.
+   students’ preferences of tools/applications for chatting and messaging, how
+   they use them in educational context, who they like to be with in the class
+   messaging groups, and their expectations of chatbots in assisting them during
+   their learning process. Therefore, two surveys for bachelor and master degree
+   students at the University of Granada (Spain) were designed and answers from
+   more than 250 students were collected. The key results from the student
+   surveys indicate a preference for using familiar messaging applications, such
+   as Telegram or WhatsApp. Students also expressed interest in using chatbots
+   that can assist them with organizing their course schedules, help them access
+   their assignment grades and facilitate searching for resources.
 \item The results of the first phase were fed into the second phase of the
@@
 Initially, a single survey was developed for this purpose and responses from 300
-higher education teachers were collected and analysed\textcolor{black}{; this will be detailed in Section \ref{sec:meth}}. The responses' analysis
-led to the preparation of a second survey for teachers and 200 responses were
-collected\textcolor{black}{, again following the methodology that will be explained later. The questions of the second survey focused on asking about teachers'
-needs, opinions and preferences of the development of future technology-enhanced
-tools and its potential impact on educational institutions policies. In order to assess these, this paper layed out the following research questions}:
+higher education teachers were collected and analysed; this
+  will be detailed in Section \ref{sec:meth}. The responses' analysis led to
+the preparation of a second survey for teachers and 200 responses were
+collected, again following the methodology that will be
+  explained later. The questions of the second survey focused on asking about
+  teachers' needs, opinions and preferences of the development of future
+  technology-enhanced tools and its potential impact on educational institutions
+  policies. In order to assess these, this paper layed out the following
+  research questions:
 
@@
 
-We will try to answer these research questions through the analysis of the two aforementioned surveys.
-Eventually, what we want to obtain is a series of
-recommendations to make a successful deployment of chatbot technologies (and, in
-some cases, general instant messaging applications) in higher education; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be used in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from RQ3 we will also try to find best practices in the adoption of messaging platforms and they accompanying chatbots.
+We will try to respond to these research questions through the analysis of the
+answers provided by professors to the two aforementioned surveys.  Eventually,
+the main research outcome of this survey should be a series of recommendations
+to make a successful deployment of chatbot technologies (and, in some cases,
+general instant messaging applications) in higher education; from the response
+to RQ1 and RQ4 we will try to recommend specific technologies or applications to
+be deployed in the classroom; the response to RQ2 and RQ3 will help us recommend
+chatbots features or specific platforms; and finally, from RQ3 we will also try
+to find best practices in the adoption of messaging platforms and their matching
+chatbots.
 
@@
 current research has found about the use of messaging applications, including
-chatbots, in the classroom is described. The methodology used in the surveys is presented in
-Section \ref{sec:meth}, and the results of the surveys are presented next in
-Section \ref{sec:res}. Finally, we discuss these results and conclude with a
-series of recommendations for the successful deployment of chatbots in higher education.
+chatbots, in the classroom is described. The methodology used in the surveys is
+presented in Section \ref{sec:meth}, and the results of the surveys are
+presented next in Section \ref{sec:res}. Finally, we discuss these results and
+conclude with a series of recommendations for the successful deployment of
+chatbots in higher education.
 
@@
 
-% The Use of Mobile Instant Messaging (MIM) Platforms in Higher Education
 The widespread and rapid adoption of free Mobile Instant Messaging
@@
 
-WhatsApp is, at least in most Western countries, the most popular MIM platform
+WhatsApp is, at least in most Western countries, the most popular MIM platform. The reason is that it is the tool preferably
 used by educators to provide assignments' feedback to students, support course
-discussions, and contribute resources in informal learning settings
+discussions, and post learning resources in a semi-formal learning context
 \cite{panah2020study}.  Moreover, the use of WhatsApp in higher education could
@@
 their learning \cite{gachago2015crossing} process.  This is why examining the
-role of MIM platforms in higher education is still a challenge, and why the opinions of
+role of MIM platforms in higher education, as well as applications based on them such as chatbots, is still a challenge, and why the opinions of
 the teaching community towards them have to be examined, as we do in this paper.
@@
 The use of MIM platforms, although possibly valuable by itself, can be enhanced with the
-use of chatbots, which are conversational agents that normally dwell 
+use of chatbots, which are conversational agents that normally dwell in
 synchronous conversations systems. The use of chatbots in higher education is still in its early stages
@@
 using chatbots to collect course feedback from students in higher
-education improved response quality and boosted enjoyment levels
+education improved the quality of responses given by students in their assignments, and boosted engagement levels
 \cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
@@
 \cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
-Messenger, with a focus on identifying characteristics and quality metrics such as
-language, subject matter, and platform. Pérez and collaborators
+Messenger, concluding that most of these chatbots were very basic and that programmers require of more support to develop and 
+offer tools for improving coaching methods and students learning. Pérez and collaborators
 \cite{perez2020rediscovering} attempted to categorize educational chatbots attending to their purpose 
@@
 
-On the other hand, teaching-oriented chatbots are more sophisticated, as they
+Contrarily to the mentioned chatbots that are focused on administrative tasks, teaching-oriented chatbots are more sophisticated, as they
 set personalized learning outcomes and monitor learning progress. For instance,
@@
 In line with this research, our previous work \cite{MoraChatbots2021:anon}
-aimed at analyzing the expectations of students in this regard. Recent papers
+aimed at analyzing the expectations of students in this regard. Another paper
 have also analysed how the use of chatbots affected the learning outcomes of
 students in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper
-analysed conversational chatbots in a one-to-one setting, finding that learning
+considered conversational chatbots in a one-to-one setting, finding that learning
 truly benefited from it. This is, once again, an evidence of the benefit of
@@
 
-\textcolor{black}{This study followed a quantitative approach towards addressing its research objective, by collecting rich data about the use of messaging applications and chatbots
-by educators in both universities and colleges\footnote{In Spain, they are called simply high schools, and deliver
-tertiary or associated degrees that do not have the consideration of university degrees}.
+This study has employed a quantitative approach in order to address its research objectives.
+A good amount of data was collected on the usage of messaging applications and chatbots by educators in universities and colleges.\footnote{In Spain, higher education institutions generally known elsewhere as colleges, are called simply high schools, and deliver
+tertiary or associate degrees that do not have the consideration of university degrees.}
 To achieve this goal two online surveys were designed and developed using Google Forms
 in Spanish. They are comprised of six questions focusing on demographic data
-(i.e., sector, gender, degrees, discipline, age, teaching experience)
-followed by several multiple choice questions allowing the participants to choose multiple answers.}
-
-In the {\bf first survey}, the multiple choice questions are
-focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider
-useful for their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
-university and the other for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees). Questions and
+(i.e., sector, gender, degrees, discipline, age, or teaching experience)
+followed by several multiple choice questions allowing the participants to choose multiple answers.
+
+In the {\bf first survey}, multiple choice questions were
+focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that educators would consider
+useful for their teaching and the impact of COVID on the teaching practice; please, check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
+university and another for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees). Questions and
 responses were the same, except for the type of tertiary degrees that
-were considered.}
-
-\textcolor{black}{This survey was piloted by the authors of the paper and their colleagues before using it in the
+were considered.} This survey was piloted by the authors of this paper and their colleagues before using it in the
 study. All the comments collected from this trial were incorporated in the survey.
-We mainly used mailing lists, as well as Telegram groups,
-to post the survey link to reach out to more educators. The university form was sent to Spanish
+We primarily used mailing lists and Telegram groups to disseminate the survey link so that it would reach a larger number of educators. The form targeting university teachers was sent to Spanish
 (mainly Andaluc\'{\i}a and Galicia) universities, and also universities in Costa Rica and
-Mexico. The tertiary (non-university/college) teachers were based mainly in
+Mexico. The tertiary (non-university/college) educators who received the form were based mainly in
 Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of
 2021, during the Covid-19 pandemic and while, at least in Spain, many universities had
-mandatory virtual teaching.}
+mandatory virtual teaching.
 
@@
 \multicolumn{1}{c}{} & \multicolumn{1}{c}{Frequency} & \multicolumn{1}{c}{\%} & Frequency & \multicolumn{1}{c}{\%} \\ \hline
-%\begin{tabular}[c]{@{}l@{}}Chat interactions among \\ students in the same course\end{tabular} & 171 & 60.6 & 110 & 39.0 \\
-%\begin{tabular}[c]{@{}l@{}}Chat interactions among students, \\ teachers of the School/Faculty\end{tabular} & 13 & 4.6 & 269 & 95.4 \\
-%\begin{tabular}[c]{@{}l@{}}Chat interactions among students \\ of the same study year and teachers\end{tabular} & 51 & 18.1 & 231 & 81.9 \\
-%\begin{tabular}[c]{@{}l@{}}Teacher not being part of the \\ interaction\end{tabular} & 113 & 40.1 & 169 & 59.9 \\ \hline
 \begin{tabular}[c]{@{}l@{}}Chat interactions among \\ students in the same course\end{tabular} & 166 & 59.1 & 115& 40.9 \\
@@
 
-%A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
-The majority of the teachers were aged 45-55 years old (70; 34.1\%), followed by individuals aged 35-45 (67, 32.7\%), and 25-35 (42; 20.5\%), while the minority was aged >55 years old (26; 12.7\%).
-In terms of teaching experience, 59 teachers (28.8\%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9\%), 0-5 years (51; 24.9\%) and more than 25 years of experience (44; 21.5\%).
-The teachers were asked about what kind of interaction media features they value the most; the frequencies and percentages of their responses are given in the table that follows.
-
 \begin{figure}[h!tbp]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
-The majority of the teachers were aged 45-55 years old (70; 34.1\%), followed by individuals aged 35-45 (67, 32.7\%), and 25-35 (42; 20.5\%), while the minority was aged $>$~55 years old (26; 12.7\%).
-In terms of teaching experience, 59 teachers (28.8\%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9\%), 0-5 years (51; 24.9\%) and more than 25 years of experience (44; 21.5\%).
-The teachers were asked about what kind of interaction media features they value the most \textcolor{black}{; i.e.
-what their preferred features are in the applications/tools that they use to interact with their students.} The frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
 
@@
 
-% Only some COVID-response relationship.
 In our survey, we could not find an answer about the right moment to introducing chatbot technologies. The response to questions regarding to change of
-behavior during and after the first stay-at-home stage of the pandemic do not suggest that a major (or minor, such as new higher education laws or the introduction of new degrees) crisis could be an opportunity to introduce new technologies.
+behavior during and after the first stay-at-home stage of the pandemic do not suggest that a major (or minor, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.} or the introduction of new degrees) crisis could be an opportunity to introduce new technologies.
 The reason being that it does not
@@
 
-% No remarkable differences between different groups.
 The introduction of chatbots and chatbot technology will be helped by the fact
@@
 focus on these issues and explore how chatbot technology could address them.
-%We will create a series of international surveys that will investigate this.
 
@@
 \end{figure}
-The {\bf second survey}, shown in its original form in Figure \ref{figure:survey2}, followed the same paths, only in this case there was a single questionnaire, and with a different scope, focusing on the kind of interaction media features that teachers value the most.
-%\textcolor{black}{A capture of these questions is included in Figure \ref{fig:survey2}} % this sentence is repeated
-% Olia - see my comment above.
-It was filled by teachers that were also students in a Professional Development course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers who knew about it by emails from the authors, or from the vicedeanship for International Relations that included it in its newsletter.
-This means that there might be a higher proportion of 1) teachers with few years of experience 2) teachers from the computer science faculty and 3) teachers from Granada.
-We think, however that there's no explicit bias in this selection, although of course specific percentages will vary.
-
-Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are  their \textcolor{black}{past experiences and needs} with regard to the use of instant messaging applications with students, and even using bots or chatbots in the classroom.
-In addition the survey asked about the most relevant \textit{interaction media features} for the teachers with respect to the potential tool to use in class.
+
+The {\bf second survey}, shown in its original form in Figure
+\ref{figure:survey2}, followed the same paths, only in this case there was a
+single questionnaire, and with a different scope, focusing on the kind of
+interaction media features that teachers value the most.  It was filled by
+teachers that were also students in a Professional Development course (on the
+use of new technologies in higher education, around 1/4 of them) as well as
+University of Granada teachers who knew about it by emails from the authors, or
+from the vicedeanship for International Relations that included it in its
+newsletter. This means that there might be a higher proportion of 1) teachers
+with few years of experience 2) teachers from the computer science faculty and
+3) teachers from Granada. We think, however that there's no explicit bias in
+this selection, although of course specific percentages will vary.
+
+Specifically, this survey asked the teachers, in addition to general information
+(such as gender, age, experience, etc), what are their \textcolor{black}{past
+  experiences and needs} with regard to the use of instant messaging
+applications with students, and even using bots or chatbots in the classroom. In
+addition the survey asked about the most relevant \textit{interaction media
+  features} for the teachers with respect to the potential tool to use in class.
 
 The specific questions included in this second survey are listed below:
-
-% Antonio - I have included a reference name to each one of these variables, which are the names used on Tables 8 and 9.
-Thus it will be easy to recognize every variable, and then, we could refer to them in those tables.
 

### 2023-01-09 edubots_surveys.Rnw
Review methods - par 1,2

@@
 
-\begin{abstract}
-  Messaging platforms are applications, generally mediated by an app, desktop
-  program or the web, mainly used for synchronous communication among users. As
-  such, they have been widely adopted officially by higher education
-  establishments, after little or no study of their impact and perception by the
-  teachers. We think that the introduction of these new tools and the
-  opportunities and challenges they have needs to be studied carefully in order
-  to adopt the model, as well as the tool, that is the most adequate for all
-  parties involved. We already studied the perception of these tools by
-  students, in this paper we examine the teachers’ experiences and perceptions
-  through a survey that we validated with peers, and what they think these tools
-  should make or serve so that it enhances students learning and helps them
-  achieve their learning objectives. The survey has been distributed among
-  tertiary education teachers, both in universitary and other kind of tertiary
-  establishments, based in Spain (mainly) and Spanish-speaking countries. We
-  have focused on collecting teachers' preferences and opinions on the
-  introduction of messaging platforms in their day-to-day work, as well as other
-  services attached to them, such as chatbots. What we intend with this survey
-  is to understand their needs and to gather information about the various
-  educational use cases where these tools could be valuable. In addition, an
-  analysis of how and when teachers’ opinions towards the use of these tools
-  varies across gender, experience, and their discipline of specialization is
-  presented. The key findings of this study highlight the factors that can
-  contribute to the advancement of the adoption of messaging platforms and
-  chatbots in higher education institutions to achieve the desired learning
-  outcomes.
+\begin{abstract} % abstract
+Messaging platforms are applications, generally mediated by an app, desktop program or the web, mainly used for synchronous communication among users.
+As such, they have been widely adopted officially by higher education establishments, after little or no study of their impact and perception by the teachers.
+We think that the introduction of these new tools and the opportunities and challenges they have needs to be studied carefully in order to adopt the model, as well as the tool, that is the most adequate for all parties involved.
+We already studied the perception of these tools by students, in this paper we examine the teachers’
+experiences and perceptions through a survey that we validated with peers, and what they think these tools should make or serve so that it enhances students learning and helps them achieve their learning objectives.
+The survey has been distributed among tertiary education teachers, both in universitary and other kind of tertiary establishments, based in
+Spain (mainly) and Spanish-speaking countries. We have focused on collecting
+teachers' preferences and opinions on the introduction of messaging platforms in their day-to-day work, as well as other services attached to them, such as  chatbots.
+What we intend with this survey is to understand their needs and to gather
+information about the various educational use cases where these tools could be
+valuable. In addition, an analysis of how and when teachers’ opinions towards
+the use of these tools varies across gender, experience, and their discipline
+of specialization is presented. The key findings of this study highlight the
+factors that can contribute to the advancement of the adoption of messaging
+platforms and chatbots in higher education institutions to achieve the desired
+learning outcomes.
 \end{abstract}
@@
 
-New technologies have been introduced and widely adopted into the classroom in
-recent years. However, in order to be successful, their application will require
-a certain amount of extra work and training for the teacher, as well as for the
-students. Training will help the two collectives involved acquire new skills
-and, potentially, pupils will acquire a greater level of engagement with the
-subject matter, which is usually the main objective. Even if several
-technologies are already in use inside the classroom, there is still room for
-adopting others.
-
-However, the success of this adoption largely depends on the willingness and
-ability of teachers to embrace it, as they are the primary agents in this new
-educational approach. As such, gathering and assessing feedback from these users
-will be crucial in realizing the potential benefits of the technology.
-
-Over the past decade, messaging apps like WhatsApp and Telegram have become
-increasingly popular in teaching at the secondary and higher education levels
-\cite{gachago2015crossing,mwakapina2016whatsapp,yin2016adoption,panah2020study}. By
-creating groups at various levels (e.g. class, assignment, course), teachers and
-students have been able to use these apps for bilateral or group-level
-communication. In addition to their primary function of communication, many
-messaging programs also allow the creation of applications that can act as users
-through open application programming interfaces (APIs), which are often
-available through a free or freemium model.
-
-This opens the door to the introduction of \textit{chatbots}, that is,
-autonomous agents able to communicate and interact with humans (or other
-chatbots) in a natural way \cite{Gong2008,differ.chat}, answering question and
-even posing their own ones to the user, in the classroom; in this limited
-environment, chatbots can appear as regular users, thus being close to passing a
-Turing Test \cite{moor2003turing}, which gives them certain characteristics
-that, again, can enhance student engagement. Chatbots implement different
-Artificial Intelligence techniques, such as natural language processing as well
-as, in some cases, learning; this is not a requirement, however, and in most
-cases they are simply applications that have a conversational interface, as
-opposed to a graphical user interface.
-
-These qualities have made education one of the most promising areas for chatbot
-applications today \cite{clarizia2018,Smutny2020}. In this domain, they
-facilitate the so-called \textit{personalized learning}, i.e. they adapt
-themselves to students’ pace of learning and provide online tutoring outside the
-classroom, which have been proved to be very effective increasing their
-engagement and participation in the subjects \cite{agarwal2020}. Moreover
-chatbots' tutoring possibilities aid to reduce the stress of students
-\cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their
-teacher, or asking questions in front of the class. This situation normally
-conducts to a silence of the student and a later contact with the teacher by
-e-mail, which, in turn, will mean a workload for the teacher, that could be very
-significant given the existing disproportion between number of students per each
-teacher.
-
-Hence, the chatbot technology has a potential to mitigate this problem by
-providing answers to students’ questions and facilitating a dynamic and
-autonomous learning experience \cite{Griol2014,kim2020}. In addition, using an
-automated system such as a chatbot will allow teachers to spend more time on
-other topics that students struggle with.
+New technologies have been introduced and widely adopted into the classroom in recent years. However, in order to be successful, their application
+will require a certain amount of extra work and training for the teacher, as well as for the students.
+Training will help the two collectives involved acquire new skills and, potentially, pupils will acquire a greater level of engagement with the subject matter, which is usually the main objective.
+Even if several technologies are already in use inside the classroom, there is still room for adopting others.
+
+Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Given this,
+asking and analyzing user's opinions with regard to this scenario will help reaping the expected benefits of the technology.
+
+Over the past decade, messaging apps like WhatsApp and Telegram have become increasingly popular in teaching at the secondary and higher education levels \cite{gachago2015crossing,mwakapina2016whatsapp,yin2016adoption,panah2020study}.
+By creating groups at various levels (e.g.
+class, assignment, course), teachers and students have been able to use these apps for bilateral or group-level communication.
+In addition to their primary function of communication, many messaging programs also allow the creation of applications that can act as users through open application programming interfaces (APIs), which are often available through a free or freemium model.
+
+This opens the door to the introduction of \textit{chatbots}, that is, autonomous agents able to communicate and interact with humans (or other chatbots) in a natural way \cite{Gong2008,differ.chat}, answering question and even posing their own ones to the user, in the classroom; in this limited environment, chatbots can appear as regular users, thus being close to passing a Turing Test \cite{moor2003turing}, which gives them certain characteristics that, again, can enhance student engagement.
+Chatbots implement different Artificial Intelligence techniques, such as natural language processing as well as, in some cases, learning; this is not a requirement, however, and in most cases they are simply applications that have a conversational interface, as opposed to a graphical user interface.
+
+These qualities have made education one of the most promising areas for chatbot applications today \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called
+\textit{personalized learning}, i.e. they adapt themselves to students’ pace of learning and provide online tutoring outside the classroom, which have been proved to be very effective increasing their
+engagement and participation in the subjects \cite{agarwal2020}.
+Moreover chatbots' tutoring possibilities aid to reduce the stress of students \cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their teacher,
+or asking questions in front of the class.
+This situation normally conducts to a silence of the student and a later contact with the teacher by e-mail, which, in turn, will mean a workload for the teacher, that could be very
+significant given the existing disproportion between number of students per each teacher.
+
+Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning
+experience \cite{Griol2014,kim2020}. In addition, using an automated system such as a chatbot will allow teachers to spend more time on  other topics that students struggle with.
 
@@
 focus of the % EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
-unnamed European project, the main sponsor of this study, is to explore best
-practices and innovative use of chatbots, and to create a learning community of
-educators in higher education institutions.  Researchers and teachers
-participating in this project have developed several studies. Most of these
-works have been focused on how messaging applications and/or chatbots are
-normally applied to deliver personalized learning in classrooms that occurs
-anytime anywhere, and promote collaborative learning experiences or group
-discussions \cite{panah2020study}, and boost students' sense of belonging to
-their institutions \cite{abbas2021onlinechat}.  The majority of these studies
-were conducted focusing on the teachers' perspectives, so this paper aims to
-provide more conclusions regarding their opinions and needs, as well as the
-existing challenges or opportunities that arise when adopting these technologies
-in classrooms. This will lead to clarify how they can positively contribute to
-enhancing the learning process in higher education institutions.
+unnamed European project, the main sponsor of this study, is to explore best practices and innovative use of chatbots,
+and to create a learning community of educators in higher education institutions.
+Researchers and teachers participating in this project have developed several studies. Most of these works have been focused on how the
+messaging applications and/or chatbots are normally applied to deliver personalized learning in classrooms that occurs anytime anywhere,
+promote collaborative learning experiences, group discussions \cite{panah2020study} and boost students' sense of belonging to their institutions
+\cite{abbas2021onlinechat}.
+The majority of these studies were conducted focusing on the teachers' perspectives, so this paper aims to provide more conclusions regarding
+their opinions and needs, as well as the existing challenges or opportunities that arise when adopting these technologies in classrooms. This will lead to clarify
+how they can positively contribute to enhancing the learning process in higher education institutions.
 
@@
 \item The first phase aimed to collect feedback from students about their
-   students’ preferences of tools/applications for chatting and messaging, how
-   they use them in educational context, who they like to be with in the class
-   messaging groups, and their expectations of chatbots in assisting them during
-   their learning process. Therefore, two surveys for bachelor and master degree
-   students at the University of Granada (Spain) were designed and answers from
-   more than 250 students were collected. The key results from the student
-   surveys indicate a preference for using familiar messaging applications, such
-   as Telegram or WhatsApp. Students also expressed interest in using chatbots
-   that can assist them with organizing their course schedules, help them access
-   their assignment grades and facilitate searching for resources.
+  students’ preferences of tools/applications for chatting and
+  messaging, how they use them in educational context, who they like to be
+  with in the class messaging groups, and their expectations of chatbots
+  in assisting them during their learning process. Therefore, two surveys
+  for bachelor and master degree students at the University of Granada (Spain)
+  were designed and answers from more than 250 students were collected. The key
+  findings of the students' surveys reveal that they prefer to use messaging
+  familiar applications, such as Telegram or WhatsApp.
+  Students also expressed interest in chatbots that can assist them with
+  organizing their course schedules, help them access their assignment grades
+  and facilitate searching for resources.
 \item The results of the first phase were fed into the second phase of the
@@
 Initially, a single survey was developed for this purpose and responses from 300
-higher education teachers were collected and analysed; this
-  will be detailed in Section \ref{sec:meth}. The responses' analysis led to
-the preparation of a second survey for teachers and 200 responses were
-collected, again following the methodology that will be
-  explained later. The questions of the second survey focused on asking about
-  teachers' needs, opinions and preferences of the development of future
-  technology-enhanced tools and its potential impact on educational institutions
-  policies. In order to assess these, this paper layed out the following
-  research questions:
+higher education teachers were collected and analysed\textcolor{black}{; this will be detailed in Section \ref{sec:meth}}. The responses' analysis
+led to the preparation of a second survey for teachers and 200 responses were
+collected\textcolor{black}{, again following the methodology that will be explained later. The questions of the second survey focused on asking about teachers'
+needs, opinions and preferences of the development of future technology-enhanced
+tools and its potential impact on educational institutions policies. In order to assess these, this paper layed out the following research questions}:
 
@@
 
-We will try to respond to these research questions through the analysis of the
-answers provided by professors to the two aforementioned surveys.  Eventually,
-the main research outcome of this survey should be a series of recommendations
-to make a successful deployment of chatbot technologies (and, in some cases,
-general instant messaging applications) in higher education; from the response
-to RQ1 and RQ4 we will try to recommend specific technologies or applications to
-be deployed in the classroom; the response to RQ2 and RQ3 will help us recommend
-chatbots features or specific platforms; and finally, from RQ3 we will also try
-to find best practices in the adoption of messaging platforms and their matching
-chatbots.
+We will try to answer these research questions through the analysis of the two aforementioned surveys.
+Eventually, what we want to obtain is a series of
+recommendations to make a successful deployment of chatbot technologies (and, in
+some cases, general instant messaging applications) in higher education; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be used in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from RQ3 we will also try to find best practices in the adoption of messaging platforms and they accompanying chatbots.
 
@@
 current research has found about the use of messaging applications, including
-chatbots, in the classroom is described. The methodology used in the surveys is
-presented in Section \ref{sec:meth}, and the results of the surveys are
-presented next in Section \ref{sec:res}. Finally, we discuss these results and
-conclude with a series of recommendations for the successful deployment of
-chatbots in higher education.
+chatbots, in the classroom is described. The methodology used in the surveys is presented in
+Section \ref{sec:meth}, and the results of the surveys are presented next in
+Section \ref{sec:res}. Finally, we discuss these results and conclude with a
+series of recommendations for the successful deployment of chatbots in higher education.
 
@@
 
+% The Use of Mobile Instant Messaging (MIM) Platforms in Higher Education
 The widespread and rapid adoption of free Mobile Instant Messaging
@@
 (i.e. video, audio, text) \cite{tang2017mobile}. Using these tools in
-higher education institutions facilitates the delivery of personalized learning
+higher education facilitates the delivery of personalized learning
 that occurs anytime anywhere, and promotes collaborative learning
@@
 
-WhatsApp is, at least in most Western countries, the most popular MIM platform. The reason is that it is the tool preferably
+WhatsApp is, at least in most Western countries, the most popular MIM platform
 used by educators to provide assignments' feedback to students, support course
-discussions, and post learning resources in a semi-formal learning context
+discussions, and contribute resources in informal learning settings
 \cite{panah2020study}.  Moreover, the use of WhatsApp in higher education could
@@
 their learning \cite{gachago2015crossing} process.  This is why examining the
-role of MIM platforms in higher education, as well as applications based on them such as chatbots, is still a challenge, and why the opinions of
+role of MIM platforms in higher education is still a challenge, and why the opinions of
 the teaching community towards them have to be examined, as we do in this paper.
@@
 The use of MIM platforms, although possibly valuable by itself, can be enhanced with the
-use of chatbots, which are conversational agents that normally dwell in
+use of chatbots, which are conversational agents that normally dwell 
 synchronous conversations systems. The use of chatbots in higher education is still in its early stages
@@
 interest in using this technology in the (possibly virtual) classroom. Indeed,
-using chatbots to collect course feedback from students in higher
-education improved the quality of responses given by students in their assignments, and boosted engagement levels
+the using chatbots to collect course feedback from students in higher
+education improved response quality and boosted enjoyment levels
 \cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
@@
 
-Several studies to evaluate chatbots in higher education have been conducted. For
-instance, a comprehensive study was presented by Smutny and Schreiberova
+Several studies have been conducted to evaluate chatbots in higher education. For
+instance, a thorough study was presented by Smutny and Schreiberova
 \cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
-Messenger, concluding that most of these chatbots were very basic and that programmers require of more support to develop and 
-offer tools for improving coaching methods and students learning. Pérez and collaborators
+Messenger, with a focus on identifying characteristics and quality metrics such as
+language, subject matter, and platform. Pérez and collaborators
 \cite{perez2020rediscovering} attempted to categorize educational chatbots attending to their purpose 
@@
 include those that provide service support, such as Ask Holly
-\cite{meetholly} and Dina \cite{santoso2018dinus}, which respond to
+\cite{meetholly} and Dina \cite{santoso2018dinus}, which responds to
 students' questions about enrollment and registration. Ask L. U.
@@
 proposed a generic chatbot for university students that is able to answer 
-frequently asked questions. The University of Granada deployed
-Elvira, a chatbot embedded in its main web page \cite{MOREO20129} to perform the same task. In addition to being able
+frequently asked questions. The University of Granada had
+Elvira, a built-in chatbot in its main web page \cite{MOREO20129} to perform the same task. In addition to being able
 to answer pre-established frequent questions, it did so from the website of
@@
 lip-synced the answers. However, in the case of Elvira, the emphasis was on the
-authenticity of the speech-mouth and face gestures synchronization rather than making updating
-answered questions simpler or more interactive for the administrative staff, or more open to the rest of the university staff using actual messaging platforms. In
+authenticity of the synchronization rather than making the updated 
+of answered questions simpler, more interactive, or more open to the rest of the university staff using actual messaging platforms. In
 most cases, the embedded search engine was able to provide more up-to-date
@@
 them more hints and reporting it to the educator's dashboard
-\cite{fernoagua2018intelligent}. This could help educators identify
+\cite{fernoagua2018intelligent}. This can help educators identify
 students who need more attention and provide them with more educational resources
@@
 courses. Other authors, such as \cite{coronado2018cognitive}, have proposed agents that
-record learning materials to be provided on demand to students, while \cite{crockett2017predicting} 
+store learning materials to be provided on demand to students, while \cite{crockett2017predicting} 
 reported on tutoring systems that can
@@
 These needs include, but are not limited to, student learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance.
+This is why we focus in this paper on what  teachers are looking for in a Technology Acceptance Model (TAM) and associated technologies like chatbots.
 Both authors focus on what teachers need in terms of the latter; this paper will focus on a wider perspective, trying to determine what they are looking for in terms of general messaging technology.
 The classical literature \cite{tam91} already proposes that any adoption of technology must be tuned to the user needs and experience.
-In this paper, we will try to find out what those are in order to propose a successful model of adoption of chatbot technology.
+In this paper, we will try to find out what those are in order to propose a model to facilitate the adoption of chatbot technology.
 
 In line with this research, our previous work \cite{MoraChatbots2021:anon}
-aimed at analyzing the expectations of students in this regard. Another paper
+aimed at analyzing the expectations of students in this regard. Recent papers
 have also analysed how the use of chatbots affected the learning outcomes of
 students in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper
-considered conversational chatbots in a one-to-one setting, finding that learning
+analysed conversational chatbots in a one-to-one setting, finding that learning
 truly benefited from it. This is, once again, an evidence of the benefit of
@@
 prevent the successful acceptance of the technology, and these are what we are
-trying to find out in this paper, along with what kind of features would improve
+trying to find out in this paper, alng with what kind of features would improve
 its acceptance.
@@
 \multicolumn{1}{c}{} & \multicolumn{1}{c}{Frequency} & \multicolumn{1}{c}{\%} & Frequency & \multicolumn{1}{c}{\%} \\ \hline
+%\begin{tabular}[c]{@{}l@{}}Chat interactions among \\ students in the same course\end{tabular} & 171 & 60.6 & 110 & 39.0 \\
+%\begin{tabular}[c]{@{}l@{}}Chat interactions among students, \\ teachers of the School/Faculty\end{tabular} & 13 & 4.6 & 269 & 95.4 \\
+%\begin{tabular}[c]{@{}l@{}}Chat interactions among students \\ of the same study year and teachers\end{tabular} & 51 & 18.1 & 231 & 81.9 \\
+%\begin{tabular}[c]{@{}l@{}}Teacher not being part of the \\ interaction\end{tabular} & 113 & 40.1 & 169 & 59.9 \\ \hline
 \begin{tabular}[c]{@{}l@{}}Chat interactions among \\ students in the same course\end{tabular} & 166 & 59.1 & 115& 40.9 \\
@@
 
+%A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
+The majority of the teachers were aged 45-55 years old (70; 34.1\%), followed by individuals aged 35-45 (67, 32.7\%), and 25-35 (42; 20.5\%), while the minority was aged >55 years old (26; 12.7\%).
+In terms of teaching experience, 59 teachers (28.8\%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9\%), 0-5 years (51; 24.9\%) and more than 25 years of experience (44; 21.5\%).
+The teachers were asked about what kind of interaction media features they value the most; the frequencies and percentages of their responses are given in the table that follows.
+
 \begin{figure}[h!tbp]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
+The majority of the teachers were aged 45-55 years old (70; 34.1\%), followed by individuals aged 35-45 (67, 32.7\%), and 25-35 (42; 20.5\%), while the minority was aged $>$~55 years old (26; 12.7\%).
+In terms of teaching experience, 59 teachers (28.8\%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9\%), 0-5 years (51; 24.9\%) and more than 25 years of experience (44; 21.5\%).
+The teachers were asked about what kind of interaction media features they value the most \textcolor{black}{; i.e.
+what their preferred features are in the applications/tools that they use to interact with their students.} The frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
 
@@
 their preference for the {\em provider} of the technology (the university itself, any
-company) as well as the {\em type} of technology (instant, app-based messaging
-systems vs. web-based messaging systems integrated in another learning management system).
+company) as well as the {\em type} of technology (instant, app based messaging
+systems vs. web-based messaging systems integrated in another learning management system).}
 
 This inclusion of university-provided messaging applications in
-the survey might explain why there are so few teachers, just 6.7\%, that answered they did not
+the survey might explain why there are so few, just 6.7\%, that answer they do not
 use any messaging application. In general, universities provide official channels
-to send students academic information such as the exam schedule
+to communicate with students official academic information such as the exam schedule
 or the grades. The statistical mode is to use that kind of messaging. Some other
-teaching staff might not use it, but use some extraofficial or opt-in channels such as the others included in the survey; in the end, between these official and extra-official channels, most people cover their needs to communicate with students.
+people might not use it, but use some extraofficial or opt-in channels such as the other included in the survey; at the end, between these official and extraofficial channels most people cover their needs to communicate with students.
 This matches
@@
 
-One of the most interesting questions arising from the analysis of the
+One of the most interesting questions that can arise from the analysis of the
 results, and that should require further study, is: Are teachers really aware
 of the possibilities of chatbots in the classroom? The survey
-only listed a few functionalities for the chatbots, and just a few subjects selected
+only listed a few functionalities for the chatbots and just a few subjects selected
 the option "Others". This may suggest  that most teachers did not really understand
-at this point the actual potential of chatbots, since the responses listed were by no means exhaustive.
-If the responders were more acquainted with the possibilities of this technology, this response would possibly have shown up many more times.
-Another way to look at it is that, unless you provide the specific instructions on how to use a
-tool, the teaching staff is already too busy or burnt out to think about innovation.
-
-We can speculate that teaching staff's opinions of chatbots are influenced by negative
-experiences with chatbots used in customer support, which is what most people are likely to have
-experienced. Further study may be needed to confirm this, but it is important to 
-keep in mind when introducing chatbot technologies in the classroom.
-To potentially change this existing perception, it will be necessary to make chatbots as simple and satisfying to use as possible.
+at this point the actual potential of chatbots, since the responses listed were by no means exhaustive, and if the responders were more acquainted with the possibilities of the technology, possibly this response would have shown up many more times.
+Another way to look about it is
+that, unless you provide the specific instructions on how to use a
+tool, the teaching staff is already too busy or burn out to think about
+innovation.
+
+We can speculate that their opinions towards chatbots are informed by negative
+experiences with customer support chatbots, which is what most people will have
+experienced. This will probably require further study, but also will need to be
+taken into account when introducing chatbot technologies in the classroom:
+it will have to be as simple, and as satisfactory, as possible,
+to (possibly) change this existing perception.
 
 Regarding gender grouping, both genders agree in their uses, so it seems not
-relevant at all. However, when we look at the plot containing the sector differentiation,
-it is interesting to note that university teaching staff are more likely to use chatbots 
-for grades and FAQs compared to other tertiary education teaching staff.
+relevant at all. When looking at the plot containing the sector differentiation
+it is interesting to observe how university teachers prefer in a higher
+proportion to use them for grades and FAQs in comparison with other tertiary education teachers.
 This seems reasonable as the frequency of seeing the students
 is lower at the University so, an automatic tool for grade notification for
-continuous evaluation would be more helpful.
-Furthermore, the high student-to-teacher
-ratios that university educators often face could be another reason why
-a higher number of them are willing to use chatbots for FAQs, as this could
-reduce misunderstandings and email overload from students.
-
-The results, when grouping by teaching experience, confirm that
-experienced teachers are just as open to change and willing to embrace new
-technological challenges as younger educators. 
-From this concrete plot it is interesting as well to observe the fact that very few
-young teachers are willing to use chatbots for other uses. This
+continuous evaluation seems more helpful.
+Furthermore, the high student/teacher
+ratios that university teachers have to deal with could be another reason to
+have a higher number of them willing to use chatbots for FAQs. This could
+ameliorate the number of misunderstandings and email overload that so many
+students might generate.
+
+The results, when grouping by experience, confirm that
+experienced teachers are not afraid of changes and are willing to accept new
+technological challenges; at least, in the same way that younger teachers
+are. From this concrete plot it is interesting as well to observe the fact that very few
+young/inexperience teachers are willing to use chatbots for other uses. This
 reinforces the hypothesis thrown at the beginning of this section that younger
@@
 \begin{itemize}
- \item Teaching staff want to have support from their institutions. This
-   is probably due to the strict European data regulations on data protection,
-   but also to avoid the overhead required to sign up new students every year.
-   In general, additional support with specific formation and access to IT help desk for specific features
-   enhance the possibility of a successful adoption that improves the learning outcomes. This is supported by the result of the two
-   surveys: they prefer whatever ``messaging'' application provided by
-  as well as the fact that this application is the ``official'' for the university, as shown in
-   Table \ref{tab:interaction}.
+ \item Teachers want to have support from their corresponding institution. This
+   is probably due to the strict European data regulations \textcolor{black}{on data protection},
+   but also to avoid the overhead required to \textcolor{black}{sign up new students every year.
+   In general support from specific formation and access to IT help desk for specific features
+   enhances the possibility of adoption by the teachers or the possibility of a successful
+   adoption that improves the learning outcomes. This is supported by the result of the two
+   surveys: they prefer whatever "messaging" application is provided by the university, and
+   also they value sustainability as well as "officiality" of the platform, as shown in
+   Table \ref{tab:interaction}}.
  \item Teachers need sustainability. The main reason is that implementing
    changes is expensive in terms of effort and prone to errors in the first
-   years. Therefore, it is logical that if
-   chatbots or messaging platforms are to be introduced, teaching staff want this change
+   years of implementing new procedures, therefore, it is logical that if
+   chatbots or messaging platforms are to be introduced, they want this change
    to be as permanent as possible.
  \item Keep it Simple.
-Media interaction requirements are simple and only 2.4\% of educators are requesting more features.
-This could be a sign of technological burnt out produced by the previous pandemic courses, when the use of computers significantly increased.
+Media interaction requirements are simple and only a 2.4\% is requesting more features.
+This could be a sign of technological burn out produced by the previous and current courses where, due to the pandemic, the use of computer has increased significantly.
 \end{itemize}
 
-The analysis of the questions related to RQ4 seems to indicate that teaching staff
-prefer to share an interaction space with their students. As
-shown in Tables \ref{tab:kindinteractions} and \ref{tab:interaction}, the majority of responders
-indicated that they {\em do not} want unidirectional communication, and that they prefer
-{\em horizontal} interaction. This point is reinforced by results on the kind of
-chatbots they preferred: most of them indicated FAQ bots, which might indicate a
-need to offload part of the burden of answering every single question posed by
-their students. In a horizontal setting, other students would answer if the teacher
+An analysis of survey questions related to RQ4 seems to indicate that teachers
+prefer to share an interaction space with their student, as
+shown in Tables \ref{tab:kindinteractions} and \ref{tab:interaction}, where a majority of responders
+indicate they {\em don't} want unidirectional communication; a preference of
+{\em horizontal} interaction, but also the answer to the kind of
+chatbots preferred that features FAQ bots prominently, which might indicate a
+need to delegate or offload part
+of the burden of answering, and attending, every single question posed by
+students. In an horizontal setting, other students can answer if the teacher
 does not do it immediately. This might also be the reason why the possibility of
 using tools from which analytics can be extracted is also valued by teachers:
-in that way, the student activity in the chat tool, answering questions, or their regularity can all be
-assessed as part of the process of achieving learning objectives.
-
-In our survey, we could not find an answer about the right moment to introducing chatbot technologies. The response to questions regarding to change of
-behavior during and after the first stay-at-home stage of the pandemic do not suggest that a major (or minor, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.} or the introduction of new degrees) crisis could be an opportunity to introduce new technologies.
-The reason being that it does not
-bring major changes in attitude 
-%(as a minor "crisis" we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.}),
-%or simply the introduction of new degrees. 
-Although changes driven by external forces do offer the chance of piloting new technologies, they do not
-seem to bring internal changes in educators' attitudes (which, after all, is
+that way, activity in the chat tool, answering questions, regularity, can all be
+observed and valued as part of the process of assessing achievement of learning
+objectives by students.
+
+% Only some COVID-response relationship.
+In our survey, we could not find an answer about the right moment for introducing chatbot technologies. Response to questions related to change of
+behavior during and after the first stay at home, stage of the pandemic do not suggest that a major (or minor)
+crisis could be an opportunity to introduce new technologies, since it does not
+bring major changes in attitude (as a minor "crisis" we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in
+  Spain, every 10 years or so.}), or simply introduction of new degrees. Although
+changes driven by external forces do offer the chance of piloting new technologies, they do not
+seem to bring internal changes in attitudes in the teaching staff (which, after all, is
 bound to be the same). In absence of a clear answer in this direction, the right
@@
 
-As with many other methodologies for assessing technology acceptance, the survey results suggest
-that the introduction of simple, and institution-supported instant messaging
+As in many other methodologies that try to assess technology acceptance, answers to the survey suggest
+that the introduction of simple, and institution-supported, instant messaging
 and chatbot technologies would increase the perceived usefulness (which is one
-of the key metrics in technology acceptance models). Given that most institutions
+of the key metrics in technology acceptance models). Since most institutions
 already have some {\em virtual campus} or learning management system, adding
-some easy automation or connection to personal instant messaging tools could
-help introduce these new technologies to the learning community.
-
-Based on the discussion of this study, we propose a potential process for introducing
-technology that would need to be piloted in order to determine its value and its
-relationship to improved learning outcomes and higher teacher staff satisfaction.
-
-Initially, institutions should introduce messaging automation tools that help with bureaucratic or repetitive tasks, such as answering frequently asked questions or providing information on class or assignment deadlines.
-These chatbots will pave the way for more complex chatbots that will
-have a greater impact on learning outcomes, such as chatbots that help students
-integrate in class or identify and address learning problems
-in individual students or groups of them. These chatbots should also be accompanied by
-analytics on student interaction and possibly some natural language
-processing (in vernacular language) to help assess the general mood of
-the class and how different materials or external factors affect it.
-
-The introduction of chatbots and chatbot technology will be helped by the fact
-that no discernible differences are found between different groups. Even though
-chatbots do have some potential for personalization or customization based on
-the class material, student, and teaching staff, the general introduction of the
+some easy automation, or connection to personal instant messaging tools, could
+really help onboard the learning community on these new technologies.
+
+What we are going to propose next is a possible process of
+technology introduction that is compatible with the conclusions of this study,
+but that would have to be piloted in order to check its value, and its
+relationship with better learning outcomes, as well as higher teacher
+satisfaction.
+Once that initial introduction of institutional messaging
+automation tools is done, teachers (and students as well) will
+probably prefer the kind of bots that alleviate bureaucratic or repetitive
+tasks, such as answering frequent questions or answers on class or assignment
+deadlines, as indicated by their answers to the respective
+questions. These will help the introduction of more complex chatbots that will
+affect more directly learning outcomes, such as chatbots that help students
+integrate in the class, or are able to identify (and address) learning problems
+in students or in groups of them. These should also be accompanied by
+analytics on student interaction, as well as possibly some natural language
+processing (in vernacular language) that will help assess the general mood of
+the class, and how different material (or external factors) affect it.
+
+% No remarkable differences between different groups.
+This introduction of chatbots and chatbot technology will be helped by the fact
+that no discernible differences are found between different groups. Even if
+chatbots do have some potential for personalization or customization, based on
+the class material, student and teaching staff, the general introduction of the
 technology can be done in a general way and for all disciplines, teaching
-experience, and gender.
-
-Overall, the general feeling that transpires from the survey is that it is
-essential for any institution to take into account shareholders' opinions
+experience and gender.
+
+At any rate, the general feeling that transpires from the survey is that it is
+essential for any institution to take into account the shareholder's opinion
 when introducing chatbots. This is true almost across the board, but in the case
@@
 
-One of the questions in the {\bf second survey}, which asked about 
+One of the questions we made in the {\bf second survey}, related to
 the messaging applications used by tertiary education teachers, opens a new line
-of inquiry about what educators {\em perceive} as such, and how it is used.
-Namely, the responses indicated that teachers perceived as messaging
-application not only traditional chats or instant messaging app such
-as WhatsApp or Microsoft Teams, but also the means provided by their university for
-communicating with students, such as a feature of grading applications that
-emails grades to students. This suggests that teachers have a need for communication with students, 
-which is mostly unidirectional, and that it
-does not matter as much how that need is met. However, this will need careful
+of inquiry about what they {\em perceive} as such, and about how it is used.
+Namely, the responses indicated that the teachers perceived as messaging
+application not only what is usually called a chat or instant messaging app such
+as WhatsApp or Microsoft Teams, but also the means provided by the university for
+communicating with the student, such as a feature of grading applications that
+will email the grade to the student. This implies that there is a need by
+teachers, communication with students, also mostly unidirectional, and that it
+does not matter so much how that need is covered. However, this will need careful
 consideration, including how it ties with the automation of the learning
-experience provided by chatbots.
-
-Our analysis of the survey results can inform several potential avenues for future research. 
-For instance, the rollout of extensive videoconferencing and virtual
+experience that the chatbots bring.
+
+Our analysis of the results of this survey can be fed into several potential avenues for future research. For instance, the rollout of extensive videoconferencing and virtual
 teaching solutions that the COVID pandemic has brought has also taught us a
-series of lessons: it increases isolation and decreases the
-amount of synchronous contact that happens in the fringes of the classroom (e.g. 
-teaching staff offices, or before and after class). A future line of research could 
-focus on these issues and explore how chatbot technology could address them.
-
-Finally, the full extent of chatbot technology is not really examined in
+series of lessons. It increases isolation, for instance, and decreases the
+amount of synchronous contact that happens in the fringes of the classroom:
+teaching staff offices, before and after class. A future line of work would be
+focused on exactly this, and what kind of needs could be covered by chatbot
+technology. We will create a series of international surveys that will
+investigate this.
+
+Finally, the full extent of chatbot technology is not really being examined in
 these surveys. They can be connected to natural language processing engines with
-sentiment analysis as well as other analytics. Examining the mood of the class such 
-as responses to new materials, assignments, exams or external events will help
-any student-centered teaching strategy, which will also help students (and
-teachers) achieve their learning objectives. This line of work, however, would require
-the introduction of some pilot study combined with initial opinion
-assessments from students.
+sentiment analysis as well as other analytics. Examining the mood of the class,
+as response to new material, assignment, exams or external events might help
+will help any student-centered teaching strategy, which will help students (and
+teachers) reach their learning objectives. This line of work, however, will be
+based on the introduction of some pilot study, combined with initial opinion
+assessment on the students.
 
@@
 \end{figure}
-
-The {\bf second survey}, shown in its original form in Figure
-\ref{figure:survey2}, followed the same paths, only in this case there was a
-single questionnaire, and with a different scope, focusing on the kind of
-interaction media features that teachers value the most.  It was filled by
-teachers that were also students in a Professional Development course (on the
-use of new technologies in higher education, around 1/4 of them) as well as
-University of Granada teachers who knew about it by emails from the authors, or
-from the vicedeanship for International Relations that included it in its
-newsletter. This means that there might be a higher proportion of 1) teachers
-with few years of experience 2) teachers from the computer science faculty and
-3) teachers from Granada. We think, however that there's no explicit bias in
-this selection, although of course specific percentages will vary.
-
-Specifically, this survey asked the teachers, in addition to general information
-(such as gender, age, experience, etc), what are their \textcolor{black}{past
-  experiences and needs} with regard to the use of instant messaging
-applications with students, and even using bots or chatbots in the classroom. In
-addition the survey asked about the most relevant \textit{interaction media
-  features} for the teachers with respect to the potential tool to use in class.
+The {\bf second survey}, shown in its original form in Figure \ref{figure:survey2}, followed the same paths, only in this case there was a single questionnaire, and with a different scope, focusing on the kind of interaction media features that teachers value the most.
+%\textcolor{black}{A capture of these questions is included in Figure \ref{fig:survey2}} % this sentence is repeated
+% Olia - see my comment above.
+It was filled by teachers that were also students in a Professional Development course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers who knew about it by emails from the authors, or from the vicedeanship for International Relations that included it in its newsletter.
+This means that there might be a higher proportion of 1) teachers with few years of experience 2) teachers from the computer science faculty and 3) teachers from Granada.
+We think, however that there's no explicit bias in this selection, although of course specific percentages will vary.
+
+Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what are  their \textcolor{black}{past experiences and needs} with regard to the use of instant messaging applications with students, and even using bots or chatbots in the classroom.
+In addition the survey asked about the most relevant \textit{interaction media features} for the teachers with respect to the potential tool to use in class.
 
 The specific questions included in this second survey are listed below:
+
+% Antonio - I have included a reference name to each one of these variables, which are the names used on Tables 8 and 9.
+Thus it will be easy to recognize every variable, and then, we could refer to them in those tables.
 

### 2023-01-09 edubots_surveys.Rnw
Review methods - par 3-5

--- 2023-01-09 edubots_surveys.Rnw
@@
 
-A total of 282 teachers responded to the survey: 193 teaching at the University
+A total of 282 educators responded to the survey: 193 teaching at the University
 (68.4\%) and 89 at other tertiary education institutions (31.6\%).
 From those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%) and 5 teachers preferred not to indicate their gender (1.8\%).
-In terms of age, the majority of the participants (n=111) in this survey was 45-55 years old (39.4\%), while 91 teachers were 35-45 (32.3\%), 46 were 25-35 (16.3\%) and 34 teachers were older than 55 (12.1\%).
-Last, 84 teachers had a teaching experience of 16-25 years (29.8\%), 75 teachers 6-15 years of experience (26.6\%), 69 teachers had 0-5 years of experience (24.5\%) and finally, 54 teachers had more than 25 years of teaching experience (19.1\%).
+In terms of age, the majority of participants (n=111) in this survey were 45-55 years old (39.4\%), while 91 educators were 35-45 (32.3\%), 46 were 25-35 (16.3\%) and 34 were older than 55 (12.1\%).
+Last, 84 educators had a teaching experience of 16-25 years (29.8\%), 75 educators had 6-15 years of experience (26.6\%), 69 educators had 0-5 years of experience (24.5\%) and finally, 54 educators had more than 25 years of teaching experience (19.1\%).
 
@@
 
-The {\bf second survey} was designed after initial results to the first survey arrived,
-and pointed to necessities and experiences of teachers not being addressed by the first one; namely
+The {\bf second survey} was designed after initial results for the first survey arrived,
+and pointed to necessities and experiences of educators not addressed by the first one; namely
 their experience with messaging platforms and the way they were used to interact with students.
-It was piloted in a group of university teachers attending to a formation course, and validated with them.
-It was then extended to the rest of the responders, using the same media: Telegram groups, email and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
+It was piloted in a group of university teaching staff attending to a formation course, and validated with them.
+It was then extended to the rest of responders, using the same media: Telegram groups, e-mail, and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
 (Section \ref{app:questions}).
 
-A total of 205 teachers responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%).
-From those, 124 were male (60.5\%), 65 female (31.7\%) and 16 teachers preferred not to indicate their gender (7.8\%).
-In terms of age, the majority of the participants (n=70) was again, as in the first survey, 45-55 years old (34.1\%), while 67 teachers were 35-45 years old (32.7\%), 42 were 25-35 (20.5\%) and 26 teachers were older than 55 (12.7\%).
-In terms of teaching experience, 59 teachers had a teaching experience of 16-25 years (28.8\%), 51 teachers had 6-15 years (24.9\%) and 0-5 years of experience (24.9\%), and 44 teachers more than 25 years of teaching experience (21.5\%).
+A total of 205 educators responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%).
+From those, 124 were male (60.5\%), 65 female (31.7\%) and 16 participants preferred not to indicate their gender (7.8\%).
+In terms of age, the majority of the participants (n=70) was again, as in the first survey, 45-55 years old (34.1\%), while 67 participants were 35-45 years old (32.7\%), 42 were 25-35 (20.5\%) and 26 participants were older than 55 (12.7\%).
+In terms of teaching experience, 59 participants had a teaching experience of 16-25 years (28.8\%), 51 participants had 6-15 years (24.9\%) and 0-5 years of experience (24.9\%), and 44 participants had more than 25 years of teaching experience (21.5\%).
 

### 2023-01-09 edubots_surveys.Rnw

--- 2023-01-09 edubots_surveys.Rnw
@@
 using chatbots to collect course feedback from students in higher
-education improved the quality of responses given by students in their assignments, and boosted engagement levels
+education improved response quality and boosted enjoyment levels
 \cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
@@
 \cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
-Messenger, concluding that most of these chatbots were very basic and that programmers require of more support to develop and 
-offer tools for improving coaching methods and students learning. Pérez and collaborators
+Messenger, with a focus on identifying characteristics and quality metrics such as
+language, subject matter, and platform. Pérez and collaborators
 \cite{perez2020rediscovering} attempted to categorize educational chatbots attending to their purpose 
@@
 In line with this research, our previous work \cite{MoraChatbots2021:anon}
-aimed at analyzing the expectations of students in this regard. Another paper
+aimed at analyzing the expectations of students in this regard. Recent papers
 have also analysed how the use of chatbots affected the learning outcomes of
 students in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper
-considered conversational chatbots in a one-to-one setting, finding that learning
+analysed conversational chatbots in a one-to-one setting, finding that learning
 truly benefited from it. This is, once again, an evidence of the benefit of
@@
 
-This study has employed a quantitative approach in order to address its research objectives.
+This study has employed a quantitative approach in order to address its research objective.
 A good amount of data was collected on the usage of messaging applications and chatbots by educators in universities and colleges.\footnote{In Spain, higher education institutions generally known elsewhere as colleges, are called simply high schools, and deliver
@@
 in Spanish. They are comprised of six questions focusing on demographic data
-(i.e., sector, gender, degrees, discipline, age, or teaching experience)
+(i.e., sector, gender, degrees, discipline, age, teaching experience)
 followed by several multiple choice questions allowing the participants to choose multiple answers.
 
-In the {\bf first survey}, multiple choice questions were
-focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that educators would consider
-useful for their teaching and the impact of COVID on the teaching practice; please, check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
-university and another for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees). Questions and
+In the {\bf first survey}, the multiple choice questions are
+focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers would consider
+useful for their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
+university and the other for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees). Questions and
 responses were the same, except for the type of tertiary degrees that
-were considered.} This survey was piloted by the authors of this paper and their colleagues before using it in the
+were considered.}
+
+This survey was piloted by the authors of the paper and their colleagues before using it in the
 study.  All the comments collected from this trial were incorporated in the survey.
-We primarily used mailing lists and Telegram groups to disseminate the survey link so that it would reach a larger number of educators. The form targeting university teachers was sent to Spanish
+We primarily used mailing lists and Telegram groups to disseminate the survey link so that it would reach a larger number of educators. The form addressed at university teachers was sent to Spanish
 (mainly Andaluc\'{\i}a and Galicia) universities, and also  universities in Costa Rica and
-Mexico. The tertiary (non-university/college) educators who received the form were based mainly in
+Mexico. The tertiary (non-university/college) teachers who received the form were based mainly in
 Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of
@@
 
-A total of 282 educators responded to the survey: 193 teaching at the University
+A total of 282 teachers responded to the survey: 193 teaching at the University
 (68.4\%) and 89 at other tertiary education institutions (31.6\%).
 From those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%) and 5 teachers preferred not to indicate their gender (1.8\%).
-In terms of age, the majority of participants (n=111) in this survey were 45-55 years old (39.4\%), while 91 educators were 35-45 (32.3\%), 46 were 25-35 (16.3\%) and 34 were older than 55 (12.1\%).
-Last, 84 educators had a teaching experience of 16-25 years (29.8\%), 75 educators had 6-15 years of experience (26.6\%), 69 educators had 0-5 years of experience (24.5\%) and finally, 54 educators had more than 25 years of teaching experience (19.1\%).
+In terms of age, the majority of the participants (n=111) in this survey was 45-55 years old (39.4\%), while 91 teachers were 35-45 (32.3\%), 46 were 25-35 (16.3\%) and 34 teachers were older than 55 (12.1\%).
+Last, 84 teachers had a teaching experience of 16-25 years (29.8\%), 75 teachers 6-15 years of experience (26.6\%), 69 teachers had 0-5 years of experience (24.5\%) and finally, 54 teachers had more than 25 years of teaching experience (19.1\%).
 
@@
 
-The {\bf second survey} was designed after initial results for the first survey arrived,
-and pointed to necessities and experiences of educators not addressed by the first one; namely
+The {\bf second survey} was designed after initial results to the first survey arrived,
+and pointed to necessities and experiences of teachers not being addressed by the first one; namely
 their experience with messaging platforms and the way they were used to interact with students.
-It was piloted in a group of university teaching staff attending to a formation course, and validated with them.
-It was then extended to the rest of responders, using the same media: Telegram groups, e-mail, and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
+It was piloted in a group of university teachers attending to a formation course, and validated with them.
+It was then extended to the rest of the responders, using the same media: Telegram groups, email and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
 (Section \ref{app:questions}).
 
-A total of 205 educators responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%).
-From those, 124 were male (60.5\%), 65 female (31.7\%) and 16 participants preferred not to indicate their gender (7.8\%).
-In terms of age, the majority of the participants (n=70) was again, as in the first survey, 45-55 years old (34.1\%), while 67 participants were 35-45 years old (32.7\%), 42 were 25-35 (20.5\%) and 26 participants were older than 55 (12.7\%).
-In terms of teaching experience, 59 participants had a teaching experience of 16-25 years (28.8\%), 51 participants had 6-15 years (24.9\%) and 0-5 years of experience (24.9\%), and 44 participants had more than 25 years of teaching experience (21.5\%).
+A total of 205 teachers responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%).
+From those, 124 were male (60.5\%), 65 female (31.7\%) and 16 teachers preferred not to indicate their gender (7.8\%).
+In terms of age, the majority of the participants (n=70) was again, as in the first survey, 45-55 years old (34.1\%), while 67 teachers were 35-45 years old (32.7\%), 42 were 25-35 (20.5\%) and 26 teachers were older than 55 (12.7\%).
+In terms of teaching experience, 59 teachers had a teaching experience of 16-25 years (28.8\%), 51 teachers had 6-15 years (24.9\%) and 0-5 years of experience (24.9\%), and 44 teachers more than 25 years of teaching experience (21.5\%).
 
@@
 
+% Only some COVID-response relationship.
 In our survey, we could not find an answer about the right moment to introducing chatbot technologies. The response to questions regarding to change of
-behavior during and after the first stay-at-home stage of the pandemic do not suggest that a major (or minor, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.} or the introduction of new degrees) crisis could be an opportunity to introduce new technologies.
+behavior during and after the first stay-at-home stage of the pandemic do not suggest that a major (or minor, such as new higher education laws or the introduction of new degrees) crisis could be an opportunity to introduce new technologies.
 The reason being that it does not
@@
 
+% No remarkable differences between different groups.
 The introduction of chatbots and chatbot technology will be helped by the fact
@@
 focus on these issues and explore how chatbot technology could address them. 
+%We will create a series of international surveys that will investigate this.
 

### 2023-01-09 edubots_surveys.Rnw
Incorporates changes from previous PR#89

@@
 In our survey, we could not find an answer about the right moment to introducing chatbot technologies. The response to questions regarding to change of
-behavior during and after the first stay-at-home stage of the pandemic do not suggest that a major (or minor, such as new higher education laws or the introduction of new degrees) crisis could be an opportunity to introduce new technologies.
+behavior during and after the first stay-at-home stage of the pandemic do not suggest that a major (or minor, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.} or the introduction of new degrees) crisis could be an opportunity to introduce new technologies.
 The reason being that it does not

### 2023-01-09 edubots_surveys.Rnw
Incorporate changes from PR#79

@@
 
-We will try to answer these research questions through the analysis of the two aforementioned surveys.
-Eventually, what we want to obtain is a series of
+We will try to respond to these research questions through the analysis of the answers provided by professors to the two aforementioned surveys.
+Eventually, the main research outcome of this survey should be a series of
 recommendations to make a successful deployment of chatbot technologies (and, in
-some cases, general instant messaging applications) in higher education; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be used in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from RQ3 we will also try to find best practices in the adoption of messaging platforms and they accompanying chatbots.
+some cases, general instant messaging applications) in higher education; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be deployed in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from RQ3 we will also try to find best practices in the adoption of messaging platforms and their matching chatbots.
 

### 2023-01-09 edubots_surveys.Rnw
incorporates changes from previous review PR#84

@@
 and to create a learning community of educators in higher education institutions.
-Researchers and teachers participating in this project have developed several studies. Most of these works have been focused on how the
-messaging applications and/or chatbots are normally applied to deliver personalized learning in classrooms that occurs anytime anywhere,
-promote collaborative learning experiences, group discussions \cite{panah2020study} and boost students' sense of belonging to their institutions
+Researchers and teachers participating in this project have developed several studies. Most of these works have been focused on how 
+messaging applications and/or chatbots are normally applied to deliver personalized learning in classrooms that occurs anytime anywhere, and
+promote collaborative learning experiences or group discussions \cite{panah2020study}, and boost students' sense of belonging to their institutions
 \cite{abbas2021onlinechat}.

### 2023-01-09 edubots_surveys.Rnw

@@
 
-This study has employed a quantitative approach in order to address its research objective.
+This study has employed a quantitative approach in order to address its research objectives.
 A good amount of data was collected on the usage of messaging applications and chatbots by educators in universities and colleges.\footnote{In Spain, higher education institutions generally known elsewhere as colleges, are called simply high schools, and deliver
@@
 in Spanish. They are comprised of six questions focusing on demographic data
-(i.e., sector, gender, degrees, discipline, age, teaching experience)
+(i.e., sector, gender, degrees, discipline, age, or teaching experience)
 followed by several multiple choice questions allowing the participants to choose multiple answers.
 
-In the {\bf first survey}, the multiple choice questions are
-focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers would consider
-useful for their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
-university and the other for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees). Questions and
+In the {\bf first survey}, multiple choice questions were
+focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that educators would consider
+useful for their teaching and the impact of COVID on the teaching practice; please, check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
+university and another for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees). Questions and
 responses were the same, except for the type of tertiary degrees that
-were considered.}
-
-This survey was piloted by the authors of the paper and their colleagues before using it in the
+were considered.} This survey was piloted by the authors of this paper and their colleagues before using it in the
 study. All the comments collected from this trial were incorporated in the survey.
-We primarily used mailing lists and Telegram groups to disseminate the survey link so that it would reach a larger number of educators. The form addressed at university teachers was sent to Spanish
+We primarily used mailing lists and Telegram groups to disseminate the survey link so that it would reach a larger number of educators. The form targeting university teachers was sent to Spanish
 (mainly Andaluc\'{\i}a and Galicia) universities, and also universities in Costa Rica and
-Mexico. The tertiary (non-university/college) teachers who received the form were based mainly in
+Mexico. The tertiary (non-university/college) educators who received the form were based mainly in
 Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of

### 2023-01-10 edubots_surveys.Rnw
Review again methods, all pars

@@
 
-This study has employed a quantitative approach in order to address its research objectives.
-A good amount of data was collected on the usage of messaging applications and chatbots by educators in universities and colleges.\footnote{In Spain, higher education institutions generally known elsewhere as colleges, are called simply high schools, and deliver
-tertiary or associate degrees that do not have the consideration of university degrees.}
-To achieve this goal two online surveys were designed and developed using Google Forms
-in Spanish. They are comprised of six questions focusing on demographic data
-(i.e., sector, gender, degrees, discipline, age, or teaching experience)
-followed by several multiple choice questions allowing the participants to choose multiple answers.
-
-In the {\bf first survey}, multiple choice questions were
-focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that educators would consider
-useful for their teaching and the impact of COVID on the teaching practice; please, check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
-university and another for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees). Questions and
+This study employed a quantitative approach to address its research objectives.
+A significant amount of data was collected on the usage of messaging applications and chatbots by educators in universities and colleges.\footnote{In Spain, higher education institutions that would generally known as colleges in other places, are simply called high schools, and provide
+tertiary or associate degrees that do not have the same consideration as university degrees.}
+To collect this data, two online surveys were designed and developed using Google Forms
+in Spanish. These surveys consisted of six questions on demographic data
+(such as sector, gender, degrees, discipline, age, or teaching experience)
+followed by several multiple-choice questions allowing participants to choose multiple answers.
+
+The {\bf first survey} consisted of multiple-choice questions 
+focused on the use of messaging apps in teaching practice, the type of chatbot use cases that educators would find
+useful for their teaching and the impact of COVID on teaching practice.
+These questions can be found in their entirity in the Appendix.\footnote{This {\bf first survey} was split into two separate Google forms, one for
+university teachers and another for teachers in tertiary education institutions outside the university system (vocational training, including 1- and 2-year degrees). The questions and
 responses were the same, except for the type of tertiary degrees that
 were considered.} This survey was piloted by the authors of this paper and their colleagues before using it in the
-study. All the comments collected from this trial were incorporated in the survey.
-We primarily used mailing lists and Telegram groups to disseminate the survey link so that it would reach a larger number of educators. The form targeting university teachers was sent to Spanish
-(mainly Andaluc\'{\i}a and Galicia) universities, and also universities in Costa Rica and
-Mexico. The tertiary (non-university/college) educators who received the form were based mainly in
-Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of
-2021, during the Covid-19 pandemic and while, at least in Spain, many universities had
+study, and all feedback from this trial was incorporated into the survey.
+The survey link was primarily distributed via mailing lists and Telegram groups in order to reach a larger number of educators. The form targeting university teachers was sent to university in Spain
+(mainly in Andaluc\'{\i}a and Galicia), and also universities in Costa Rica and
+Mexico. Tertiary (non-university/college) educators who received the form were mainly based in
+Andaluc\'{\i}a. The survey was disseminated and responses were collected in the first quarter of
+2021, during the Covid-19 pandemic, while at least in Spain, many universities were implementing
 mandatory virtual teaching.
@@
 (68.4\%) and 89 at other tertiary education institutions (31.6\%).
-From those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%) and 5 teachers preferred not to indicate their gender (1.8\%).
-In terms of age, the majority of participants (n=111) in this survey were 45-55 years old (39.4\%), while 91 educators were 35-45 (32.3\%), 46 were 25-35 (16.3\%) and 34 were older than 55 (12.1\%).
-Last, 84 educators had a teaching experience of 16-25 years (29.8\%), 75 educators had 6-15 years of experience (26.6\%), 69 educators had 0-5 years of experience (24.5\%) and finally, 54 educators had more than 25 years of teaching experience (19.1\%).
-
-Responses were stored automatically in a Google Drive spreadsheet. Eventually,
-the results from the two forms we used for the first survey were collated in a
-single spreadsheet. Survey questions are shown in Appendix I (Section \ref{app:questions}).
+Of those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%), and 5 teachers preferred not to indicate their gender (1.8\%).
+In terms of age, the majority of participants (n=111) in this survey were 45-55 years old (39.4\%), while 91 educators were 35-45 (32.3\%), 46 were 25-35 (16.3\%), and 34 were older than 55 (12.1\%).
+Lastly, 84 educators had a teaching experience of 16-25 years (29.8\%), 75 educators had 6-15 years of experience (26.6\%), 69 educators had 0-5 years of experience (24.5\%), and finally, 54 educators had more than 25 years of teaching experience (19.1\%).
+
+Responses were automatically stored in a Google Drive spreadsheet. Eventually,
+the results from the two forms used for the first survey were collated in a
+single spreadsheet. Survey questions can be found in Appendix I (Section \ref{app:questions}).
 
 The {\bf second survey} was designed after initial results for the first survey arrived,
-and pointed to necessities and experiences of educators not addressed by the first one; namely
-their experience with messaging platforms and the way they were used to interact with students.
-It was piloted in a group of university teaching staff attending to a formation course, and validated with them.
-It was then extended to the rest of responders, using the same media: Telegram groups, e-mail, and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
+and pointed out necessities and experiences of educators not covered by the first survey, specifically
+their experience with messaging platforms and the ways they were used to interact with students.
+It was piloted with a group of university teaching staff attending a training course, and validated by them.
+The survey was then extended to the rest of responders, using the same media: Telegram groups, email, and announcements in mailing lists.
+The questions asked in this survey can also be found in Appendix I
 (Section \ref{app:questions}).
@@
 A total of 205 educators responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%).
-From those, 124 were male (60.5\%), 65 female (31.7\%) and 16 participants preferred not to indicate their gender (7.8\%).
-In terms of age, the majority of the participants (n=70) was again, as in the first survey, 45-55 years old (34.1\%), while 67 participants were 35-45 years old (32.7\%), 42 were 25-35 (20.5\%) and 26 participants were older than 55 (12.7\%).
-In terms of teaching experience, 59 participants had a teaching experience of 16-25 years (28.8\%), 51 participants had 6-15 years (24.9\%) and 0-5 years of experience (24.9\%), and 44 participants had more than 25 years of teaching experience (21.5\%).
+Of those, 124 were male (60.5\%), 65 female (31.7\%), and 16 participants preferred not to indicate their gender (7.8\%).
+In terms of age, the majority of the participants (n=70) were again, as in the first survey, 45-55 years old (34.1\%), while 67 participants were 35-45 years old (32.7\%), 42 were 25-35 (20.5\%), and 26 participants were older than 55 (12.7\%).
+In terms of teaching experience, 59 participants had a teaching experience of 16-25 years (28.8\%), 51 participants had 6-15 years (24.9\%), 51 had 0-5 years of experience (24.9\%), and 44 participants had more than 25 years of teaching experience (21.5\%).
 

### 2023-01-10 edubots_surveys.Rnw
Review again methods, all pars

@@
 
-New technologies have been introduced and widely adopted into the classroom in recent years. However, in order to be successful, their application
-will require a certain amount of extra work and training for the teacher, as well as for the students.
-Training will help the two collectives involved acquire new skills and, potentially, pupils will acquire a greater level of engagement with the subject matter, which is usually the main objective.
-Even if several technologies are already in use inside the classroom, there is still room for adopting others.
-
-Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Given this,
-asking and analyzing user's opinions with regard to this scenario will help reaping the expected benefits of the technology.
-
-Over the past decade, messaging apps like WhatsApp and Telegram have become increasingly popular in teaching at the secondary and higher education levels \cite{gachago2015crossing,mwakapina2016whatsapp,yin2016adoption,panah2020study}.
-By creating groups at various levels (e.g.
-class, assignment, course), teachers and students have been able to use these apps for bilateral or group-level communication.
-In addition to their primary function of communication, many messaging programs also allow the creation of applications that can act as users through open application programming interfaces (APIs), which are often available through a free or freemium model.
-
-This opens the door to the introduction of \textit{chatbots}, that is, autonomous agents able to communicate and interact with humans (or other chatbots) in a natural way \cite{Gong2008,differ.chat}, answering question and even posing their own ones to the user, in the classroom; in this limited environment, chatbots can appear as regular users, thus being close to passing a Turing Test \cite{moor2003turing}, which gives them certain characteristics that, again, can enhance student engagement.
-Chatbots implement different Artificial Intelligence techniques, such as natural language processing as well as, in some cases, learning; this is not a requirement, however, and in most cases they are simply applications that have a conversational interface, as opposed to a graphical user interface.
-
-These qualities have made education one of the most promising areas for chatbot applications today \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called
-\textit{personalized learning}, i.e. they adapt themselves to students’ pace of learning and provide online tutoring outside the classroom, which have been proved to be very effective increasing their
-engagement and participation in the subjects \cite{agarwal2020}.
-Moreover chatbots' tutoring possibilities aid to reduce the stress of students \cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their teacher,
-or asking questions in front of the class.
-This situation normally conducts to a silence of the student and a later contact with the teacher by e-mail, which, in turn, will mean a workload for the teacher, that could be very
-significant given the existing disproportion between number of students per each teacher.
-
-Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning
-experience \cite{Griol2014,kim2020}. In addition, using an automated system such as a chatbot will allow teachers to spend more time on  other topics that students struggle with.
+New technologies have been introduced and widely adopted into the classroom in
+recent years. However, in order to be successful, their application will require
+a certain amount of extra work and training for the teacher, as well as for the
+students. Training will help the two collectives involved acquire new skills
+and, potentially, pupils will acquire a greater level of engagement with the
+subject matter, which is usually the main objective. Even if several
+technologies are already in use inside the classroom, there is still room for
+adopting others.
+
+However, the success of this adoption largely depends on the willingness and
+ability of teachers to embrace it, as they are the primary agents in this new
+educational approach. As such, gathering and assessing feedback from these users
+will be crucial in realizing the potential benefits of the technology.
+
+Over the past decade, messaging apps like WhatsApp and Telegram have become
+increasingly popular in teaching at the secondary and higher education levels
+\cite{gachago2015crossing,mwakapina2016whatsapp,yin2016adoption,panah2020study}. By
+creating groups at various levels (e.g. class, assignment, course), teachers and
+students have been able to use these apps for bilateral or group-level
+communication. In addition to their primary function of communication, many
+messaging programs also allow the creation of applications that can act as users
+through open application programming interfaces (APIs), which are often
+available through a free or freemium model.
+
+This opens the door to the introduction of \textit{chatbots}, that is,
+autonomous agents able to communicate and interact with humans (or other
+chatbots) in a natural way \cite{Gong2008,differ.chat}, answering question and
+even posing their own ones to the user, in the classroom; in this limited
+environment, chatbots can appear as regular users, thus being close to passing a
+Turing Test \cite{moor2003turing}, which gives them certain characteristics
+that, again, can enhance student engagement. Chatbots implement different
+Artificial Intelligence techniques, such as natural language processing as well
+as, in some cases, learning; this is not a requirement, however, and in most
+cases they are simply applications that have a conversational interface, as
+opposed to a graphical user interface.
+
+These qualities have made education one of the most promising areas for chatbot
+applications today \cite{clarizia2018,Smutny2020}. In this domain, they
+facilitate the so-called \textit{personalized learning}, i.e. they adapt
+themselves to students’ pace of learning and provide online tutoring outside the
+classroom, which have been proved to be very effective increasing their
+engagement and participation in the subjects \cite{agarwal2020}. Moreover
+chatbots' tutoring possibilities aid to reduce the stress of students
+\cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their
+teacher, or asking questions in front of the class. This situation normally
+conducts to a silence of the student and a later contact with the teacher by
+e-mail, which, in turn, will mean a workload for the teacher, that could be very
+significant given the existing disproportion between number of students per each
+teacher.
+
+Hence, the chatbot technology has a potential to mitigate this problem by
+providing answers to students’ questions and facilitating a dynamic and
+autonomous learning experience \cite{Griol2014,kim2020}. In addition, using an
+automated system such as a chatbot will allow teachers to spend more time on
+other topics that students struggle with.
 
@@
 focus of the % EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
-unnamed European project, the main sponsor of this study, is to explore best practices and innovative use of chatbots,
-and to create a learning community of educators in higher education institutions.
-Researchers and teachers participating in this project have developed several studies. Most of these works have been focused on how 
-messaging applications and/or chatbots are normally applied to deliver personalized learning in classrooms that occurs anytime anywhere, and
-promote collaborative learning experiences or group discussions \cite{panah2020study}, and boost students' sense of belonging to their institutions
-\cite{abbas2021onlinechat}.
-The majority of these studies were conducted focusing on the teachers' perspectives, so this paper aims to provide more conclusions regarding
-their opinions and needs, as well as the existing challenges or opportunities that arise when adopting these technologies in classrooms. This will lead to clarify
-how they can positively contribute to enhancing the learning process in higher education institutions.
+unnamed European project, the main sponsor of this study, is to explore best
+practices and innovative use of chatbots, and to create a learning community of
+educators in higher education institutions.  Researchers and teachers
+participating in this project have developed several studies. Most of these
+works have been focused on how messaging applications and/or chatbots are
+normally applied to deliver personalized learning in classrooms that occurs
+anytime anywhere, and promote collaborative learning experiences or group
+discussions \cite{panah2020study}, and boost students' sense of belonging to
+their institutions \cite{abbas2021onlinechat}.  The majority of these studies
+were conducted focusing on the teachers' perspectives, so this paper aims to
+provide more conclusions regarding their opinions and needs, as well as the
+existing challenges or opportunities that arise when adopting these technologies
+in classrooms. This will lead to clarify how they can positively contribute to
+enhancing the learning process in higher education institutions.
 
@@
 
-We will try to respond to these research questions through the analysis of the answers provided by professors to the two aforementioned surveys.
-Eventually, the main research outcome of this survey should be a series of
-recommendations to make a successful deployment of chatbot technologies (and, in
-some cases, general instant messaging applications) in higher education; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be deployed in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from RQ3 we will also try to find best practices in the adoption of messaging platforms and their matching chatbots.
+We will try to respond to these research questions through the analysis of the
+answers provided by professors to the two aforementioned surveys.  Eventually,
+the main research outcome of this survey should be a series of recommendations
+to make a successful deployment of chatbot technologies (and, in some cases,
+general instant messaging applications) in higher education; from the response
+to RQ1 and RQ4 we will try to recommend specific technologies or applications to
+be deployed in the classroom; the response to RQ2 and RQ3 will help us recommend
+chatbots features or specific platforms; and finally, from RQ3 we will also try
+to find best practices in the adoption of messaging platforms and their matching
+chatbots.
 
@@
 
-% Only some COVID-response relationship.
 In our survey, we could not find an answer about the right moment to introducing chatbot technologies. The response to questions regarding to change of

### 2023-01-10 edubots_surveys.Rnw
review survey validation

@@
 
-To avoid any kind of bias and to ensure the quality of the questionnaire, a panel board was consulted.
-There were three questions for each of the items of the questionnaire which were: Clarity, Importance, Adequateness.
-Clarity was measured as an answer to the question: Is the item well presented and without ambiguity?
-\footnote{Original text: ¿El ítem está bien redactado y sin ambigüedad?} with two choices: Yes or No.
-Both Importance and Adequateness were measured in a Likert scale from 1 to 4 (1 low, 4 high).
-
-The panel board was composed by 7 volunteer experts that have wide experience as educators and researchers. The results obtained are summarized in Table \ref{tab:validation}.
-
-As validation shows, all expert agree without any doubt about the clarity of each question.
-Furthermore, there is a large consensus regarding the Importance and Adequateness of all the eight questions in the questionnaire.
+To avoid any kind of bias and to ensure the quality of the questionnaire, a panel of experts was consulted.
+The panel board evaluated three aspects for each item of the questionnaire: Clarity, Importance, and Adequateness.
+Clarity was measured as an answer to the question: ``Is the item well presented and without ambiguity?" \footnote{Original text in Spanish: ¿El ítem está bien redactado y sin ambigüedad?} with two choices: ``Yes" or ``No".
+Both Importance and Adequateness were measured on a Likert scale from 1 to 4 (1 being low and 4 being high).
+
+The panel board was composed of 7 volunteer experts that have wide experience as educators and researchers. The results obtained are summarized in Table \ref{tab:validation}.
+
+As validation shows, all experts agree without any doubt about the clarity of each question.
+Furthermore, there is a large consensus regarding the Importance and Adequateness of all eight questions in the questionnaire.
 

### 2023-01-10 edubots_surveys.Rnw
Review RQ1 - first pars

@@
 open for approximately the same amount of time, around two months. The sample
-includes mostly teachers from university, although about 32\% and 8\% are from
+includes mostly university teachers, although about 32\% and 8\% are from
 non-universitary tertiary education in the first and second survey respectively. Regarding
-gender, 61\% of the teachers were male and 32\% female, while approximately 5\%
+gender, 61\% of teachers were male and 32\% female, while approximately 5\%
 chose not to disclose it. Finally, the responses are more or less equally
@@
 We will try to find the answers to the four research questions next, by
-analyzing the response to the different survey questions.
+analyzing the responses to the different survey questions.
 
@@
 
-Group messaging apps have become a powerful tool for \textcolor{black}{communicating} with
-students. Also, many of them have built-in chatbots to enhance the learning
-process. After an initial analysis to the answers to the first survey, we
+Group messaging apps have become a powerful tool for communicating with
+students. Also, many of them have embedded chatbots to enhance the learning
+process. After an initial analysis of the answers to the first survey, we
 realized that there were some prior issues mainly related to the adoption of a
-technology, \textcolor{black}{i.e. chatbots}, that generally piggybacks on another, i.e. messaging
+technology, i.e. chatbots, that generally piggybacks on another, i.e. messaging
 applications. Generally, in a technology adoption model, perceived ease of use and
-perceived usefulness are essential. But it is going to be very difficult for
-teachers to find {\em chatbots} easy to use if they, previously, do not
-consider, or simply use, the messaging tools to which they are attached.
-
-This is why for answering RQ1, teachers were queried about whether they use
-messaging apps in their classes, specifically, Telegram, WhatsApp, Slack (an
+perceived usefulness are essential. But it will be very difficult for
+teachers to find {\em chatbots} easy to use if they do not already
+consider or simply use, the messaging tools to which they are attached.
+
+This is why, in order to answer RQ1, teachers were queried about whether they use
+messaging apps in their classes, specifically Telegram, WhatsApp, Slack (an
 application used mainly in IT departments and software development), or any
-other messaging app, and whether they use messaging apps provided by their
+other messaging app. They were also asked if they use messaging apps provided by their
 academic institution (see Table \ref{tab:use_messapps}).
-Overall, the majority of the teachers responded that they do use messaging apps
-in their classrooms, from which apps (or, more probably, messaging solutions) provided by the academic institution
-(n=159, 56\%) and WhatsApp (n=124, 44.0\%) were the most common responses. Only
+Overall, the majority of teachers responded that they do use messaging apps
+in their classrooms. The most common respones were messaging apps (or, more probably, messaging solutions) provided by their academic institutions (n=159, 56\%) and WhatsApp (n=124, 44.0\%). Only
 19 teachers (6.7\%) replied that they do not use any messaging app in their
@@
 show significant differences in the use of instant messaging apps between
-teachers from University and vocational education. In general, most teachers
+teachers from universities and vocational education institutions. In general, most teachers
 prefer messaging apps provided by their own institutions (we also show the
@@
 Telegram). With respect to specific disciplines, Engineering and Technology
-teachers are more active in their use, but the number of teachers from Humanities
-who answered they used these apps in their classes is also remarkable
-(around 60\% use the apps provided by their institutions).
+teachers are more active in their use, but it is also remarkable the number of teachers from Humanities
+who answered they used these apps in their classes (around 60\% use the apps provided by their institutions).
 
@@
 academic institutions. % Olia requests support for this.
-However, younger teachers also use Telegram with more than 25\% responding they do, a percentage
+However, younger teachers also use Telegram with more than 25\% responding that they do, a percentage
 that falls to about 10\% for teachers that are 55 or older. %The third column
@@
 % This is about changes (due to) after covid
-Some of the questions in the survey were focused on the impact of the COVID19
-pandemic between the 2020 and 2021 academic years in the teachers' attitudes towards the use of
-instant messaging apps in their class. Our main intention in this case was to
-assess whether a crisis will bring about some kind of change in the use of
-tools. The 282 answers are summarized in
+Some of the questions in the survey were focused on the impact of the COVID-19
+pandemic between the 2020 and 2021 academic years on the teachers' attitudes towards the use of
+instant messaging apps in their classes. Our main intention in this case was to
+assess whether a crisis will bring about a change in the use of
+these tools. The 282 answers are summarized in
 Figs. \ref{figure:gender*chatbots_use_postcovid},
@@
 already used these tools before the pandemic and kept using them during the
-pandemic lockdowns that forced students and educators to use remote education
-schemes. Moreover, approximately 15\% of them switched their messaging app for
+pandemic lockdowns that forced students and educators to use remote education. 
+Additionally, approximately 15\% of them switched their messaging app for
 one that offered a safer interaction with their students. According to the
@@
 
-Furthermore, a chi-square test of independence was performed in order to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the COVID-19 pandemic.
-The relation between the latter variable and the instructors’ sector was significant, $X^{2}_{(4, N = 282)} = 9.598$, $p =0.048$.
-Table \ref{tab:sector*covid} shows the frequencies that are cross-tabulated vs.
-changes undertaken after the COVID pandemic.
-This finding suggests that how teachers used messaging apps during the pandemic, specifically whether they changed their habits for teaching purposes, was related to the sector (university vs vocational) in which they were working.
+Furthermore, a chi-square test of independence was performed in order to examine the relationship between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the COVID-19 pandemic.
+The relationship between the latter variable and the instructors’ sector was significant, $X^{2}_{(4, N = 282)} = 9.598$, $p =0.048$.
+Table \ref{tab:sector*covid} shows the frequencies that are cross-tabulated versus changes undertaken after the COVID-19 pandemic.
+This finding suggests that how teachers used messaging apps during the pandemic, specifically whether they changed their habits for teaching purposes, was related to the sector (university vs.
+vocational) in which they were working.
 %
@@
 \multirow{4}{*}{\begin{tabular}[c]{@{}l@{}}Post-covid\\ changes\end{tabular}} & \begin{tabular}[c]{@{}l@{}}Yes, I use a safer messaging \\ app now\end{tabular} & 27 & 13 & 40 \\
- & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use any \\ messaging app before, but \\ do use it now\end{tabular} & 31 & 13 & 44 \\
+ & \begin{tabular}[c]{@{}l@{}}Yes, I didn't use any \\ messaging app before, but \\ do use it now\end{tabular} & 31 & 13 & 44 \\
  & \begin{tabular}[c]{@{}l@{}}No, I did use it before and \\ use it now\end{tabular} & 105 & 60 & 165 \\
- & \begin{tabular}[c]{@{}l@{}}No, I didn’t use it before and \\ don’t use it now\end{tabular} & 22 & 2 & 24 \\
+ & \begin{tabular}[c]{@{}l@{}}No, I didn't use it before and \\ don’t use it now\end{tabular} & 22 & 2 & 24 \\
 Total &  & 193 & 89 & 282 \\ \hline
@@
 \vspace{0.8em}
-\caption{Sector * post-covid changes cross-tabulation}
+\caption{Sector * post-COVID-19 changes cross-tabulation}
 \label{tab:sector*covid}

### 2023-01-10 edubots_surveys.Rnw
Review RQ1 - last paragraphs

--- 2023-01-10 edubots_surveys.Rnw
@@
 
-The majority of the teachers (n=165) mentioned that no changes in their habits occurred due to the emergency remote teaching, as the use of messaging apps was part of their teaching practices and remains the same, from which 105 teachers come from the university, and 60 teachers from the non-universitary tertiary sector.
-The relationships between changes in the use of messaging apps, due to the covid-19 pandemic, and the instructors’ discipline, $X^{2}_{(24, N = 282)} = 44.856$, $p =0.006$, as well as the gender, $X^{2}_{(8, N = 282)} = 16.249$, p= 0.039 were also significant.
+The majority of the teachers (n=165) mentioned that no changes in their habits occurred due to the emergency remote teaching, as the use of messaging apps was part of their teaching practices and remained the same, from which 105 teachers come from the university and 60 teachers from the non-universitary tertiary sector.
+The relationships between changes in the use of messaging apps, due to the COVID-19 pandemic, and the instructors' discipline, $X^{2}_{(24, N = 282)} = 44.856$, $p =0.006$, as well as the gender, $X^{2}_{(8, N = 282)} = 16.249$, p= 0.039 were also significant.
 This finding indicates that how teachers responded to the use of messaging apps during the pandemic was also related to their gender and discipline.
-In fact, from the majority of the teachers who did not change their habits in this respect (n=165), most of them are males (n=114), and come from the technology (n=60) and engineering (n=53) disciplines (see Tables \ref{tab:gender*covid}, \ref{tab:discipline*covid}).
+In fact, from the majority of the teachers who did not change their habits in this respect (n=165), most of them are males (n=114) and come from the technology (n=60) and engineering (n=53) disciplines (see Tables \ref{tab:gender*covid}, \ref{tab:discipline*covid}).
 %
@@
 \vspace{0.8em}
-\caption{Gender * post-covid changes crosstabulation}
+\caption{Gender * post-COVID-19 changes crosstabulation}
 \label{tab:gender*covid}
@@
 \vspace{0.8em}
-\caption{Discipline * post-covid changes crosstabulation}
+\caption{Discipline * post-COVID-19 changes crosstabulation}
 \label{tab:discipline*covid}
@@
 % Olia - TODO: check for repetitions in the following paragraph that you added. thank you.
-Finally, we took a closer look at the post-covid changes and the variables
+Finally, we took a closer look at the post-COVID-19 changes and the variables
 gender, sector, and discipline for which the chi-square test is statistically
@@
 that shows the contribution of each cell to the test. In the Pearson's residual
-graphs, \textcolor{black}{the responses to the question about the use of messaging apps were shortened for the sake of clarity according to}: 1)
+graphs, the responses to the question about the use of messaging apps were shortened for the sake of clarity according to: 1)
 \textit{Did/do} stands for \textit{Yes, I did use it before and do use it now};
-2) \textit{Didn't/do} for \textit{Yes, I didn’t use any messaging app before,
+2) \textit{Didn't/do} for \textit{Yes, I didn't use any messaging app before,
   but do use it now}; 3) \textit{safer} for \textit{Yes, I use a safer messaging
-  app now}; 4) \textit{Didn't/Don't} for \textit{No, I didn’t use it before and
-  don’t use it now}.
+  app now}; 4) \textit{Didn't/Don't} for \textit{No, I didn't use it before and
+  don't use it now}.
 %
@@
 \begin{tabular}[c]{@{}l@{}}Post-\\ covid\\ changes\end{tabular} & \begin{tabular}[c]{@{}l@{}}Yes, I use a \\ safer messaging \\ app now\end{tabular} & 1.832 & 13.49\% & -1.832 & 7.50\% \\
- & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use \\ any messaging \\ app before, but\\ do use it now\end{tabular} & \textbf{2.806} & \textbf{31.21\%} & \textbf{-2.806} & \textbf{17.36\%} \\
+ & \begin{tabular}[c]{@{}l@{}}Yes, I didn't use \\ any messaging \\ app before, but\\ do use it now\end{tabular} & \textbf{2.806} & \textbf{31.21\%} & \textbf{-2.806} & \textbf{17.36\%} \\
  & \begin{tabular}[c]{@{}l@{}}No, I did use it \\ before and\\ use it now\end{tabular} & \textbf{2.850} & 15.15\% & \textbf{-2.850} & 8.43\% \\
- & \begin{tabular}[c]{@{}l@{}}No, I didn’t use \\ it before and\\ don’t use it now\end{tabular} & -1.011 & 4.40\% & 1.011 & 2.45\% \\ \hline
+ & \begin{tabular}[c]{@{}l@{}}No, I didn't use \\ it before and\\ don't use it now\end{tabular} & -1.011 & 4.40\% & 1.011 & 2.45\% \\ \hline
 \end{tabular}
@@
 \end{center}
-    \caption{Analysis for gender and post-covid changes: left) Pearson's residuals for the Chi-square test; right) Gender*post-covid changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized residuals) and contribution percentage to the total Chi-square test of each cell.}
+    \caption{Analysis for gender and post-COVID-19 changes: left) Pearson's residuals for the Chi-square test; right) Gender*post-COVID-19 changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized residuals) and contribution percentage to the total Chi-square test of each cell.}
 \label{figure:gender*postcovid_chisq}
@@
 
-As mentioned, the graphs on the left hand side represent the Pearson's
+As mentioned, the graphs on the left-hand side represent the Pearson's
 residuals, showing the difference between the observed and the expected values
 for each cell. Thus, large residuals indicate that variables are not truly
-independent. In our case, the blue shows positive contributions and red negative
-contributions to the test. Moreover, the saturation shows how large the
-contribution is in contrast to the expected value by chance. Additionally,
-tables on the right side show adjusted standardized residuals that according to
+independent. In our case, blue shows positive contributions and red negative
+contributions to the test. Additionally, the saturation shows how large the
+contribution is in contrast to the expected value by chance. 
+Tables on the right side show adjusted standardized residuals that according to
 \cite{agresti2013categorical}, if greater than +/-2 for cases with few cells,
-indicate lack of fit of $H_0$ (in boldface in our table). Complementary, the
+indicates lack of fit of $H_0$ (in boldface in our table). Complementarily, the
 table also shows the percentage of contribution to the test of each cell
-(highest percentage per column also in boldface).
+(the highest percentage per column also in boldface).
 
@@
 test results are explained by this cell. In contrast, male educators that
-respond the same were less than expected (negative contribution that explains
+responded the same were less than expected (negative contribution that explains
 17\% of the test results). Also, it is important to highlight the female
-educators that kept using these apps before and after the pandemic and
+educators that continued to use these apps before and after the pandemic and
 correspondingly the negative contribution of male educators to the same case
@@
           \begin{tabular}[c]{@{}l@{}}Post-\\ covid\\ changes\end{tabular} & \begin{tabular}[c]{@{}l@{}}Yes, I use a \\ safer messaging \\ app now\end{tabular} & 0.115 & 0.04\% & -0.115 & 0.08\% \\
-           & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use \\ any messaging \\ app before, but\\ do use it now\end{tabular} & 0.454 & 0.56\% & -0.454 & 1.21\% \\
+           & \begin{tabular}[c]{@{}l@{}}Yes, I didn't use \\ any messaging \\ app before, but\\ do use it now\end{tabular} & 0.454 & 0.56\% & -0.454 & 1.21\% \\
            & \begin{tabular}[c]{@{}l@{}}No, I did use it \\ before and\\ use it now\end{tabular} & \textbf{-2.122} & 5.71\% & \textbf{2.122} & 12.38\% \\
-           & \begin{tabular}[c]{@{}l@{}}No, I didn’t use \\ it before and\\ don’t use it now\end{tabular} & \textbf{2.939} & \textbf{25.26\%} & \textbf{-2.939} & \textbf{54.78\%} \\ \hline
+           & \begin{tabular}[c]{@{}l@{}}No, I didn't use \\ it before and\\ don't use it now\end{tabular} & \textbf{2.939} & \textbf{25.26\%} & \textbf{-2.939} & \textbf{54.78\%} \\ \hline
           \end{tabular}%
@@
 \end{center}
-    \caption{Analysis for sector and post-covid changes: left) Pearson's residuals for the Chi-square test; right) Sector*post-covid changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized  residuals) and contribution percentage to the total Chi-square test of each cell.}
+    \caption{Analysis for sector and post-COVID-19 changes: left) Pearson's residuals for the Chi-square test; right) Sector*post-COVID-19 changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized  residuals) and contribution percentage to the total Chi-square test of each cell.}
 \label{figure:sector*postcovid_chisq}
@@
 %
-With respect to the sector, the results in Fig.
+With respect to the sector, results in Fig.
 \ref{figure:sector*postcovid_chisq} show a positive contribution from university educators being reluctant to use any messaging apps before or after the pandemic: the positive contribution of their responses explain 25\% of the test results with an adjusted residual of 2.94.
 On the contrary, vocational teachers were more open to it, showing a negative Pearson's residual.
-Also, we find larger values than expected in vocational teachers that kept using these apps after the pandemic.
+Also, we find larger values than expected in vocational teachers that continued to use these apps after the pandemic.
 
@@
 \end{center}
-    \caption{Analysis for discipline and post-covid changes: left) Pearson's residuals for the Chi-square test; right) Discipline*post-covid changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized residuals) and contribution percentage to the total Chi-square test of each cell.}
+    \caption{Analysis for discipline and post-COVID-19 changes: left) Pearson's residuals for the Chi-square test; right) Discipline*post-COVID-19 changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized residuals) and contribution percentage to the total Chi-square test of each cell.}
 \label{figure:discipline*postcovid_chisq}
@@
 %
-Finally, statistical significance was found for the discipline and post-covid
+Finally, statistical significance was found for discipline vs. post-COVID-19
 changes. Regarding disciplines (see
@@
 19\% of the chi-square test results. Also, the number of educators from
-Technology or Engineering that started using safer alternatives \footnote{This addresses the issue of insecure/unsafe applications which do not encrypt messages or can be easily compromised exposing information} are less than
+Technology or Engineering that started using safer alternatives \footnote{This addresses the issue of insecure/unsafe applications which do not encrypt messages or can be easily compromised by exposing information} are less than
 expected (compared to the educators from other disciplines). Bear in mind that

### 2023-01-10 edubots_surveys.Rnw
Review RQ2

@@
 
-For answering RQ2, teachers were provided with a list of different potential chatbot functionalities (use cases) and were requested to respond on whether each given use case would be useful in their classes.
+For answering RQ2, teachers were provided with a list of different potential chatbot functionalities (use cases) and were requested to indicate whether each given use case would be useful in their classes.
 The findings are summarized in Table \ref{tab:chatbottypes}.
@@
 The most beneficial use case for chatbots in higher education and vocational training is their ability to facilitate agenda formation and communication (171 positive responses, 60.6\%), followed by the FAQs use case
-(148 positive responses, 52.5\%) and the sharing class material use case (136;
-48.2\%). A chi-square test of independence was performed to examine the relation
-among participants’ preferences for particular chatbot use cases. Out of the 171 teachers who consider useful the use of
-chatbots for agenda preparation in the class, 103 also consider useful chatbots’
-use for FAQs. The relation between agenda and the FAQs use case was significant, $X^{2}_{(1, N = 282)} =
-10.467$, $p =0.001$. The frequencies cross tabulated are given in Table
+(148 positive responses, 52.5\%), and the sharing class material use case (136;
+48.2\%). A chi-square test of independence was performed to examine the relationship
+among participants' preferences for particular chatbot use cases. Out of the 171 teachers who considered useful the use of
+chatbots for agenda preparation in the class, 103 also consider useful chatbots'
+use for FAQs. The relationship between agenda and the FAQs use case was significant, $X^{2}_{(1, N = 282)} =
+10.467$, $p =0.001$. The frequencies cross-tabulated are given in Table
 \ref{tab:agenda*faq}.
@@
 by gender, sector, years of experience in education, and discipline
-respectively. As it was a multiple choice question, the counts are over the
-total number of people that answered.
+respectively. As it was a multiple-choice question, the counts are over the
+total number of educators who answered.
 

### 2023-01-10 edubots_surveys.Rnw
Review RQ3 - small edits

@@
 Since chatbots are intended to mediate or help in this interaction, it is
-essential to understand the kind of interaction teachers prefer. Chatbots should
+essential to understand the kind of interaction that teachers prefer. Chatbots should
 address those modes, and not others. In order to find out these modes, and thus
-answering RQ3, teachers were provided with a list of different kind of
-interactions that may take place among students and between students and the
-teacher, with the use of messaging apps. The findings are summarized in Table
+answering RQ3, teachers were provided with a list of different kinds of
+interactions that may take place among students and between students and their
+teacher, when using messaging apps. The findings are summarized in Table
 \ref{tab:kindinteractions}.
@@
 
-As it can be seen by the answer to the first and last question, in general
-teachers do not want to participate in a chat group with students; either they
+As it can be seen by the answers to the first and last questions, in general
+teachers do not want to participate in a chat group with their students. They either
 want to simply leave the students alone in their own chat group, or otherwise
@@
 to take any part in these informal or non institutionally-supported chat
-groups. Overwhelmingly, they do not want to participate in these kind of chat
+groups. Overwhelmingly, they do not want to participate in this kind of chat
 groups with students, but even less so if it includes the rest of the faculty.
 
-The answer, then, to this research question, is that, in general, teachers do
+Then, the answer to this research question is that in general, teachers do
 {\em not} want to have interaction with students in a chat group. To a certain
@@
 to Fig. \ref{figure:chatbots_messagingorganization} the vast majority prefer
-small groups only with the students from the same course. These are more focused
-groups with specific goals and dedicated to the organization of the course and
-its tasks, and from the pedagogic point of view \textcolor{black}{it also seems more appropriate to improve
-the learning process}. Interestingly, and as a cross-check of the answers above,
+small groups only with their students from the same course. These are more focused
+groups with specific goals and dedicated to the course organization and
+its tasks, and from the pedagogic point of view it also seems more adequate to improve
+the learning process. Interestingly, and as a cross-check of the answers above,
 about 30\% of teachers consider they should not be part of the chat group. This
@@
 a great amount of teachers that would be against being in a chat group with
-students. \textcolor{black}{However, students will still need to get the services
+students. However, students will still need to get the services
 that the university, through chatbots, provide, thus opening the door for deployment of chatbots
-without the intervention of the professor, simply tapping university provided
-services \cite{bernier2002services}.}
-Whether that's a slim majority or not, that's open to debate (and
-would probably need a more pointed survey focused on this), but what is clear is
+without the intervention of their professors, simply tapping university provided
+services \cite{bernier2002services}.
+Whether that is a slim majority or not, that is open to debate (and
+would probably need a more focused survey). However, it is clear 
 that forcing teachers to create chat groups with students and participate in
@@
 and social interaction (e.g. \cite{dibitonto2018chatbot}) might be the reason
-for the low percentage of teachers that selected this response.
+for the low percentage of teachers that chose this response.
 

### 2023-01-10 edubots_surveys.Rnw
Review RQ4 and few small edits all over

--- 2023-01-10 edubots_surveys.Rnw
@@
 \cite{gachago2015crossing}. However, this last paper also reflects the need for
-learners to "take ownership of the tool" and the advantages of social learning
+learners to ``take ownership of the tool'' and the advantages of social learning
 in general. At the same time, it also mentions different challenges, among which
@@
 The panel board evaluated three aspects for each item of the questionnaire: Clarity, Importance, and Adequateness.
-Clarity was measured as an answer to the question: ``Is the item well presented and without ambiguity?" \footnote{Original text in Spanish: ¿El ítem está bien redactado y sin ambigüedad?} with two choices: ``Yes" or ``No".
+Clarity was measured as an answer to the question: ``Is the item well presented and without ambiguity?'' \footnote{Original text in Spanish: ¿El ítem está bien redactado y sin ambigüedad?} with two choices: ``Yes'' or ``No''.
 Both Importance and Adequateness were measured on a Likert scale from 1 to 4 (1 being low and 4 being high).
@@
 
-Furthermore, a chi-square test of independence was performed in order to examine the relationship between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the COVID-19 pandemic.
-The relationship between the latter variable and the instructors’ sector was significant, $X^{2}_{(4, N = 282)} = 9.598$, $p =0.048$.
+Furthermore, a chi-square test of independence was performed in order to examine the relationship between instructors' discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the COVID-19 pandemic.
+The relationship between the latter variable and the instructors' sector was significant, $X^{2}_{(4, N = 282)} = 9.598$, $p =0.048$.
 Table \ref{tab:sector*covid} shows the frequencies that are cross-tabulated versus changes undertaken after the COVID-19 pandemic.
@@
 \multirow{4}{*}{\begin{tabular}[c]{@{}l@{}}Post-covid\\ changes\end{tabular}} & \begin{tabular}[c]{@{}l@{}}Yes, I use a safer messaging \\ app now\end{tabular} & 20 & 20 & 0 & 40 \\
- & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use any \\ messaging app before, but \\ do use it now\end{tabular} & 20 & 23 & 1 & 44 \\
+ & \begin{tabular}[c]{@{}l@{}}Yes, I didn't use any \\ messaging app before, but \\ do use it now\end{tabular} & 20 & 23 & 1 & 44 \\
  & \begin{tabular}[c]{@{}l@{}}No, I did use it before and \\ use it now\end{tabular} & 114 & 47 & 4 & 165 \\
- & \begin{tabular}[c]{@{}l@{}}No, I didn’t use it before and \\ don’t use it now\end{tabular} & 18 & 6 & 0 & 24 \\
+ & \begin{tabular}[c]{@{}l@{}}No, I didn't use it before and \\ don’t use it now\end{tabular} & 18 & 6 & 0 & 24 \\
  & Other & 7 & 2 & 0 & 9 \\
@@
 
-\textcolor{black}{As it can be seen in the table, the bulk of responders express their wish to use a sustainable and official application, i.e.
-both being approved or provided by the University (or the educational center), and also maintained by the technical staff of the center instead of giving this responsibility/task to the teacher.
-In addition, it is very important for the teachers that the used tools that all the members of the class communicate, including themselves; as well as being already known or used in everyday tasks, e.g.
-Telegram or WhatsApp.}
+As show in Table \ref{tab:interaction}, the bulk of responders expressed their wish to use a sustainable and official application, i.e.
+both being approved or provided by their educational institution, and also maintained by the technical staff of the institution instead of giving this responsibility/task to the teacher.
+In addition, it is very important for teachers that used the tools that all the members of the class communicate, including themselves; as well as using tools that are already known or used in everyday tasks, e.g.
+Telegram or WhatsApp.
 
@@
 Every cell value represents $X^{2}_{(1, N = 205)}$.
-Details about each feature can be read in Appendix I.}
+Details about each feature can be found in Appendix I.}
 \label{tab:interactionfeatures}
@@
 have larger predictor importance for the clustering (see
-Fig. \ref{figure:predictor}). Two clusters occurred from the analysis: cluster 1
+Fig. \ref{figure:predictor}). Two clusters resulted from the analysis: cluster 1
 (n=78, 60.9\%) is formed with instructors who did not value interaction media
-pluggability, connectivity, official formation, but valued interaction media
-analytics, familiarity, support by the institution; cluster 2 (n=50,
+pluggability, connectivity, and official formation, but valued interaction media
+analytics, familiarity, and support by their institution; cluster 2 (n=50,
 39.1\%) groups instructors that did not value media
-analytics, official formation, familiarity, but valued pluggability,
-connectivity, and support by the institution. Interaction media pluggability
+analytics, official formation, and familiarity, but valued pluggability,
+connectivity, and support by their institution. Interaction media pluggability
 appears to have the most important predictor importance in the clustering of
@@
 important factor (predictor importance = 0.04). The cluster quality is fair, but
-not a good one (silhouette measure of cohesion and separation).
+not a good one (as indicated by the silhouette measure of cohesion and separation).
 
@@
 only listed a few functionalities for the chatbots, and just a few subjects selected
-the option "Others". This may suggest that most teachers did not really understand
+the option ``Others''. This may suggest that most teachers did not really understand
 at this point the actual potential of chatbots, since the responses listed were by no means exhaustive.
@@
 bring major changes in attitude 
-%(as a minor "crisis" we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.}),
+%(as a minor ``crisis'' we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.}),
 %or simply the introduction of new degrees. 
@@
 moment to introduce new technologies is always when the IT and managing staff is
-ready to support it (since, as we have seen before, "official" support is one of
+ready to support it (since, as we have seen before, ``official'' support is one of
 the factors that is most valued by teachers).

### 2023-01-10 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

@@
 
-The majority of the teachers (n=165) mentioned that no changes in their habits occurred due to the emergency remote teaching, as the use of messaging apps was part of their teaching practices and remained the same, from which 105 teachers come from the university and 60 teachers from the non-universitary tertiary sector.
+The majority of the teachers (n=165) mentioned that no changes in their habits occurred due to the shift to remote teaching due to the lock-down measures taken in their countries, as the use of messaging apps was part of their teaching practices and remained the same.
+Out of those 165 responders, 105 teachers come from the university and 60 teachers from the non-universitary tertiary sector.
 The relationships between changes in the use of messaging apps, due to the COVID-19 pandemic, and the instructors' discipline, $X^{2}_{(24, N = 282)} = 44.856$, $p =0.006$, as well as the gender, $X^{2}_{(8, N = 282)} = 16.249$, p= 0.039 were also significant.

### 2023-01-10 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

--- 2023-01-10 edubots_surveys.Rnw
@@
 contribution is in contrast to the expected value by chance. 
-Tables on the right side show adjusted standardized residuals that according to
+Tables show on the right hand side adjusted standardized residuals that according to
 \cite{agresti2013categorical}, if greater than +/-2 for cases with few cells,
-indicates lack of fit of $H_0$ (in boldface in our table). Complementarily, the
+indicate lack of fit of $H_0$ (in boldface in our table). Complementarily, the
 table also shows the percentage of contribution to the test of each cell

### 2023-01-10 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

--- 2023-01-10 edubots_surveys.Rnw
@@
 \end{center}
-    \caption{Analysis for discipline and post-COVID-19 changes: left) Pearson's residuals for the Chi-square test; right) Discipline*post-COVID-19 changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized residuals) and contribution percentage to the total Chi-square test of each cell.}
+    \caption{Analysis for discipline and post-COVID-19 changes: left) Pearson's residuals for the Chi-square test; right) Discipline*post-COVID-19 changes cross-tabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized residuals) and contribution percentage to the total Chi-square test of each cell.}
 \label{figure:discipline*postcovid_chisq}

### 2023-01-10 edubots_surveys.Rnw
Reformatting and rewriting using ChatGPT
Also eliminates markers

This would close #48 since we are reviewing grammar, but also because it's obsolete

--- 2023-01-10 edubots_surveys.Rnw
@@
 
-New technologies have been introduced and widely adopted into the classroom in recent years. However, in order to be successful, their application
-will require a certain amount of extra work and training for the teacher, as well as for the students.
-Training will help the two collectives involved acquire new skills and, potentially, pupils will acquire a greater level of engagement with the subject matter, which is usually the main objective.
-Even if several technologies are already in use inside the classroom, there is still room for adopting others.
-
-Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Given this,
-asking and analyzing user's opinions with regard to this scenario will help reaping the expected benefits of the technology.
-
-Over the past decade, messaging apps like WhatsApp and Telegram have become increasingly popular in teaching at the secondary and higher education levels \cite{gachago2015crossing,mwakapina2016whatsapp,yin2016adoption,panah2020study}.
-By creating groups at various levels (e.g.
-class, assignment, course), teachers and students have been able to use these apps for bilateral or group-level communication.
-In addition to their primary function of communication, many messaging programs also allow the creation of applications that can act as users through open application programming interfaces (APIs), which are often available through a free or freemium model.
-
-This opens the door to the introduction of \textit{chatbots}, that is, autonomous agents able to communicate and interact with humans (or other chatbots) in a natural way \cite{Gong2008,differ.chat}, answering question and even posing their own ones to the user, in the classroom; in this limited environment, chatbots can appear as regular users, thus being close to passing a Turing Test \cite{moor2003turing}, which gives them certain characteristics that, again, can enhance student engagement.
-Chatbots implement different Artificial Intelligence techniques, such as natural language processing as well as, in some cases, learning; this is not a requirement, however, and in most cases they are simply applications that have a conversational interface, as opposed to a graphical user interface.
-
-These qualities have made education one of the most promising areas for chatbot applications today \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called
-\textit{personalized learning}, i.e. they adapt themselves to students’ pace of learning and provide online tutoring outside the classroom, which have been proved to be very effective increasing their
-engagement and participation in the subjects \cite{agarwal2020}.
-Moreover chatbots' tutoring possibilities aid to reduce the stress of students \cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their teacher,
-or asking questions in front of the class.
-This situation normally conducts to a silence of the student and a later contact with the teacher by e-mail, which, in turn, will mean a workload for the teacher, that could be very
-significant given the existing disproportion between number of students per each teacher.
-
-Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning
-experience \cite{Griol2014,kim2020}. In addition, using an automated system such as a chatbot will allow teachers to spend more time on  other topics that students struggle with.
+New technologies have been introduced and widely adopted into the classroom in
+recent years. However, in order to be successful, their application will require
+a certain amount of extra work and training for the teacher, as well as for the
+students. Training will help the two collectives involved acquire new skills
+and, potentially, pupils will acquire a greater level of engagement with the
+subject matter, which is usually the main objective. Even if several
+technologies are already in use inside the classroom, there is still room for
+adopting others.
+
+The success of this adoption largely depends on the willingness and ability of
+teachers to embrace it, as they are the primary agents in this new educational
+approach. As such, gathering and assessing feedback from these users will be
+crucial in realizing the potential benefits of the technology.
+
+Over the past decade, messaging apps like WhatsApp and Telegram have become
+increasingly popular in teaching at the secondary and higher education levels
+\cite{gachago2015crossing,mwakapina2016whatsapp,yin2016adoption,panah2020study}. By
+creating groups at various levels (e.g. class, assignment, course), teachers and
+students have been able to use these apps for bilateral or group-level
+communication. In addition to their primary function of communication, many
+messaging programs also allow the creation of applications that can act as users
+through open application programming interfaces (APIs), which are often
+available through a free or freemium model.
+
+This opens the door to the introduction of \textit{chatbots}, that is,
+autonomous agents able to communicate and interact with humans (or other
+chatbots) in a natural way \cite{Gong2008,differ.chat}, answering question and
+even posing their own ones to the user, in the classroom; in this limited
+environment, chatbots can appear as regular users, thus being close to passing a
+Turing Test \cite{moor2003turing}, which gives them certain characteristics
+that, again, can enhance student engagement. Chatbots implement different
+Artificial Intelligence techniques, such as natural language processing as well
+as, in some cases, learning; this is not a requirement, however, and in most
+cases they are simply applications that have a conversational interface, as
+opposed to a graphical user interface.
+
+These qualities have made education one of the most promising areas for chatbot
+applications today \cite{clarizia2018,Smutny2020}. In this domain, they
+facilitate the so-called \textit{personalized learning}, i.e. they adapt
+themselves to students’ pace of learning and provide online tutoring outside the
+classroom, which have been proved to be very effective increasing their
+engagement and participation in the subjects \cite{agarwal2020}. Moreover
+chatbots' tutoring possibilities aid to reduce the stress of students
+\cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their
+teacher, or asking questions in front of the class. This situation normally
+conducts to a silence of the student and a later contact with the teacher by
+e-mail, which, in turn, will mean a workload for the teacher, that could be very
+significant given the existing disproportion between number of students per each
+teacher.
+
+Hence, the chatbot technology has a potential to mitigate this problem by
+providing answers to students’ questions and facilitating a dynamic and
+autonomous learning experience \cite{Griol2014,kim2020}. In addition, using an
+automated system such as a chatbot will allow teachers to spend more time on
+other topics that students struggle with.
 
@@
 \cite{gachago2015crossing}. However, this last paper also reflects the need for
-learners to ``take ownership of the tool'' and the advantages of social learning
+learners to "take ownership of the tool" and the advantages of social learning
 in general. At the same time, it also mentions different challenges, among which
@@
 
-This study employed a quantitative approach to address its research objectives.
-A significant amount of data was collected on the usage of messaging applications and chatbots by educators in universities and colleges.\footnote{In Spain, higher education institutions that would generally known as colleges in other places, are simply called high schools, and provide
-tertiary or associate degrees that do not have the same consideration as university degrees.}
-To collect this data, two online surveys were designed and developed using Google Forms
-in Spanish. These surveys consisted of six questions on demographic data
-(such as sector, gender, degrees, discipline, age, or teaching experience)
-followed by several multiple-choice questions allowing participants to choose multiple answers.
-
-The {\bf first survey} consisted of multiple-choice questions 
-focused on the use of messaging apps in teaching practice, the type of chatbot use cases that educators would find
-useful for their teaching and the impact of COVID on teaching practice.
-These questions can be found in their entirity in the Appendix.\footnote{This {\bf first survey} was split into two separate Google forms, one for
-university teachers and another for teachers in tertiary education institutions outside the university system (vocational training, including 1- and 2-year degrees). The questions and
+This study has employed a quantitative approach in order to address its research objective.
+A good amount of data was collected on the usage of messaging applications and chatbots by educators in universities and colleges.\footnote{In Spain, higher education institutions generally known elsewhere as colleges, are called simply high schools, and deliver
+tertiary or associate degrees that do not have the consideration of university degrees.}
+To achieve this goal two online surveys were designed and developed using Google Forms
+in Spanish. They are comprised of six questions focusing on demographic data
+(i.e., sector, gender, degrees, discipline, age, teaching experience)
+followed by several multiple choice questions allowing the participants to choose multiple answers.
+
+In the {\bf first survey}, the multiple choice questions are
+focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers would consider
+useful for their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
+university and the other for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees). Questions and
 responses were the same, except for the type of tertiary degrees that
-were considered.} This survey was piloted by the authors of this paper and their colleagues before using it in the
-study, and all feedback from this trial was incorporated into the survey.
-The survey link was primarily distributed via mailing lists and Telegram groups in order to reach a larger number of educators. The form targeting university teachers was sent to university in Spain
-(mainly in Andaluc\'{\i}a and Galicia), and also universities in Costa Rica and
-Mexico. Tertiary (non-university/college) educators who received the form were mainly based in
-Andaluc\'{\i}a. The survey was disseminated and responses were collected in the first quarter of
-2021, during the Covid-19 pandemic, while at least in Spain, many universities were implementing
+were considered.}
+
+This survey was piloted by the authors of the paper and their colleagues before using it in the
+study.  All the comments collected from this trial were incorporated in the survey.
+We primarily used mailing lists and Telegram groups to disseminate the survey link so that it would reach a larger number of educators. The form addressed at university teachers was sent to Spanish
+(mainly Andaluc\'{\i}a and Galicia) universities, and also  universities in Costa Rica and
+Mexico. The tertiary (non-university/college) teachers who received the form were based mainly in
+Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of
+2021, during the Covid-19 pandemic and while, at least in Spain, many universities had
 mandatory virtual teaching.
 
-A total of 282 educators responded to the survey: 193 teaching at the University
+A total of 282 teachers responded to the survey: 193 teaching at the University
 (68.4\%) and 89 at other tertiary education institutions (31.6\%).
-Of those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%), and 5 teachers preferred not to indicate their gender (1.8\%).
-In terms of age, the majority of participants (n=111) in this survey were 45-55 years old (39.4\%), while 91 educators were 35-45 (32.3\%), 46 were 25-35 (16.3\%), and 34 were older than 55 (12.1\%).
-Lastly, 84 educators had a teaching experience of 16-25 years (29.8\%), 75 educators had 6-15 years of experience (26.6\%), 69 educators had 0-5 years of experience (24.5\%), and finally, 54 educators had more than 25 years of teaching experience (19.1\%).
-
-Responses were automatically stored in a Google Drive spreadsheet. Eventually,
-the results from the two forms used for the first survey were collated in a
-single spreadsheet. Survey questions can be found in Appendix I (Section \ref{app:questions}).
-
-The {\bf second survey} was designed after initial results for the first survey arrived,
-and pointed out necessities and experiences of educators not covered by the first survey, specifically
-their experience with messaging platforms and the ways they were used to interact with students.
-It was piloted with a group of university teaching staff attending a training course, and validated by them.
-The survey was then extended to the rest of responders, using the same media: Telegram groups, email, and announcements in mailing lists.
-The questions asked in this survey can also be found in Appendix I
+From those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%) and 5 teachers preferred not to indicate their gender (1.8\%).
+In terms of age, the majority of the participants (n=111) in this survey was 45-55 years old (39.4\%), while 91 teachers were 35-45 (32.3\%), 46 were 25-35 (16.3\%) and 34 teachers were older than 55 (12.1\%).
+Last, 84 teachers had a teaching experience of 16-25 years (29.8\%), 75 teachers 6-15 years of experience (26.6\%), 69 teachers had 0-5 years of experience (24.5\%) and finally, 54 teachers had more than 25 years of teaching experience (19.1\%).
+
+Responses were stored automatically in a Google Drive spreadsheet. Eventually,
+the results from the two forms we used for the first survey were collated in a
+single spreadsheet. Survey questions are shown in Appendix I (Section \ref{app:questions}).
+
+The {\bf second survey} was designed after initial results to the first survey arrived,
+and pointed to necessities and experiences of teachers not being addressed by the first one; namely
+their experience with messaging platforms and the way they were used to interact with students.
+It was piloted in a group of university teachers attending to a formation course, and validated with them.
+It was then extended to the rest of the responders, using the same media: Telegram groups, email and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
 (Section \ref{app:questions}).
 
-A total of 205 educators responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%).
-Of those, 124 were male (60.5\%), 65 female (31.7\%), and 16 participants preferred not to indicate their gender (7.8\%).
-In terms of age, the majority of the participants (n=70) were again, as in the first survey, 45-55 years old (34.1\%), while 67 participants were 35-45 years old (32.7\%), 42 were 25-35 (20.5\%), and 26 participants were older than 55 (12.7\%).
-In terms of teaching experience, 59 participants had a teaching experience of 16-25 years (28.8\%), 51 participants had 6-15 years (24.9\%), 51 had 0-5 years of experience (24.9\%), and 44 participants had more than 25 years of teaching experience (21.5\%).
+A total of 205 teachers responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%).
+From those, 124 were male (60.5\%), 65 female (31.7\%) and 16 teachers preferred not to indicate their gender (7.8\%).
+In terms of age, the majority of the participants (n=70) was again, as in the first survey, 45-55 years old (34.1\%), while 67 teachers were 35-45 years old (32.7\%), 42 were 25-35 (20.5\%) and 26 teachers were older than 55 (12.7\%).
+In terms of teaching experience, 59 teachers had a teaching experience of 16-25 years (28.8\%), 51 teachers had 6-15 years (24.9\%) and 0-5 years of experience (24.9\%), and 44 teachers more than 25 years of teaching experience (21.5\%).
 
@@
 
-To avoid any kind of bias and to ensure the quality of the questionnaire, a panel of experts was consulted.
-The panel board evaluated three aspects for each item of the questionnaire: Clarity, Importance, and Adequateness.
-Clarity was measured as an answer to the question: ``Is the item well presented and without ambiguity?'' \footnote{Original text in Spanish: ¿El ítem está bien redactado y sin ambigüedad?} with two choices: ``Yes'' or ``No''.
-Both Importance and Adequateness were measured on a Likert scale from 1 to 4 (1 being low and 4 being high).
-
-The panel board was composed of 7 volunteer experts that have wide experience as educators and researchers. The results obtained are summarized in Table \ref{tab:validation}.
-
-As validation shows, all experts agree without any doubt about the clarity of each question.
-Furthermore, there is a large consensus regarding the Importance and Adequateness of all eight questions in the questionnaire.
+To avoid any kind of bias and to ensure the quality of the questionnaire, a panel board was consulted.
+There were three questions for each of the items of the questionnaire which were: Clarity, Importance, Adequateness.
+Clarity was measured as an answer to the question: Is the item well presented and without ambiguity?
+\footnote{Original text: ¿El ítem está bien redactado y sin ambigüedad?} with two choices: Yes or No.
+Both Importance and Adequateness were measured in a Likert scale from 1 to 4 (1 low, 4 high).
+
+The panel board was composed by 7 volunteer experts that have wide experience as educators and researchers. The results obtained are summarized in Table \ref{tab:validation}.
+
+As validation shows, all expert agree without any doubt about the clarity of each question.
+Furthermore, there is a large consensus regarding the Importance and Adequateness of all the eight questions in the questionnaire.
 
@@
 open for approximately the same amount of time, around two months. The sample
-includes mostly university teachers, although about 32\% and 8\% are from
+includes mostly teachers from university, although about 32\% and 8\% are from
 non-universitary tertiary education in the first and second survey respectively. Regarding
-gender, 61\% of teachers were male and 32\% female, while approximately 5\%
+gender, 61\% of the teachers were male and 32\% female, while approximately 5\%
 chose not to disclose it. Finally, the responses are more or less equally
@@
 We will try to find the answers to the four research questions next, by
-analyzing the responses to the different survey questions.
+analyzing the response to the different survey questions.
 
@@
 
-Group messaging apps have become a powerful tool for communicating with
-students. Also, many of them have embedded chatbots to enhance the learning
-process. After an initial analysis of the answers to the first survey, we
+Group messaging apps have become a powerful tool for \textcolor{black}{communicating} with
+students. Also, many of them have built-in chatbots to enhance the learning
+process. After an initial analysis to the answers to the first survey, we
 realized that there were some prior issues mainly related to the adoption of a
-technology, i.e. chatbots, that generally piggybacks on another, i.e. messaging
+technology, \textcolor{black}{i.e. chatbots}, that generally piggybacks on another, i.e. messaging
 applications. Generally, in a technology adoption model, perceived ease of use and
-perceived usefulness are essential. But it will be very difficult for
-teachers to find {\em chatbots} easy to use if they do not already
-consider or simply use, the messaging tools to which they are attached.
-
-This is why, in order to answer RQ1, teachers were queried about whether they use
-messaging apps in their classes, specifically Telegram, WhatsApp, Slack (an
+perceived usefulness are essential. But it is going to be very difficult for
+teachers to find {\em chatbots} easy to use if they, previously, do not
+consider, or simply use, the messaging tools to which they are attached.
+
+This is why for answering RQ1, teachers were queried about whether they use
+messaging apps in their classes, specifically, Telegram, WhatsApp, Slack (an
 application used mainly in IT departments and software development), or any
-other messaging app. They were also asked if they use messaging apps provided by their
+other messaging app, and whether they use messaging apps provided by their
 academic institution (see Table \ref{tab:use_messapps}).
-Overall, the majority of teachers responded that they do use messaging apps
-in their classrooms. The most common respones were messaging apps (or, more probably, messaging solutions) provided by their academic institutions (n=159, 56\%) and WhatsApp (n=124, 44.0\%). Only
+Overall, the majority of the teachers responded that they do use messaging apps
+in their classrooms, from which apps (or, more probably, messaging solutions) provided by the academic institution
+(n=159, 56\%) and WhatsApp (n=124, 44.0\%) were the most common responses. Only
 19 teachers (6.7\%) replied that they do not use any messaging app in their
@@
 show significant differences in the use of instant messaging apps between
-teachers from universities and vocational education institutions. In general, most teachers
+teachers from University and vocational education. In general, most teachers
 prefer messaging apps provided by their own institutions (we also show the
@@
 Telegram). With respect to specific disciplines, Engineering and Technology
-teachers are more active in their use, but it is also remarkable the number of teachers from Humanities
-who answered they used these apps in their classes (around 60\% use the apps provided by their institutions).
+teachers are more active in their use, but the number of teachers from Humanities
+who answered they used these apps in their classes is also remarkable
+(around 60\% use the apps provided by their institutions).
 
@@
 academic institutions. % Olia requests support for this.
-However, younger teachers also use Telegram with more than 25\% responding that they do, a percentage
+However, younger teachers also use Telegram with more than 25\% responding they do, a percentage
 that falls to about 10\% for teachers that are 55 or older. %The third column
@@
 % This is about changes (due to) after covid
-Some of the questions in the survey were focused on the impact of the COVID-19
-pandemic between the 2020 and 2021 academic years on the teachers' attitudes towards the use of
-instant messaging apps in their classes. Our main intention in this case was to
-assess whether a crisis will bring about a change in the use of
-these tools. The 282 answers are summarized in
+Some of the questions in the survey were focused on the impact of the COVID19
+pandemic between the 2020 and 2021 academic years in the teachers' attitudes towards the use of
+instant messaging apps in their class. Our main intention in this case was to
+assess whether a crisis will bring about some kind of change in the use of
+tools. The 282 answers are summarized in
 Figs. \ref{figure:gender*chatbots_use_postcovid},
@@
 already used these tools before the pandemic and kept using them during the
-pandemic lockdowns that forced students and educators to use remote education. 
-Additionally, approximately 15\% of them switched their messaging app for
+pandemic lockdowns that forced students and educators to use remote education
+schemes. Moreover, approximately 15\% of them switched their messaging app for
 one that offered a safer interaction with their students. According to the
@@
 
-Furthermore, a chi-square test of independence was performed in order to examine the relationship between instructors' discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the COVID-19 pandemic.
-The relationship between the latter variable and the instructors' sector was significant, $X^{2}_{(4, N = 282)} = 9.598$, $p =0.048$.
-Table \ref{tab:sector*covid} shows the frequencies that are cross-tabulated versus changes undertaken after the COVID-19 pandemic.
-This finding suggests that how teachers used messaging apps during the pandemic, specifically whether they changed their habits for teaching purposes, was related to the sector (university vs.
-vocational) in which they were working.
+Furthermore, a chi-square test of independence was performed in order to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the COVID-19 pandemic.
+The relation between the latter variable and the instructors’ sector was significant, $X^{2}_{(4, N = 282)} = 9.598$, $p =0.048$.
+Table \ref{tab:sector*covid} shows the frequencies that are cross-tabulated vs.
+changes undertaken after the COVID pandemic.
+This finding suggests that how teachers used messaging apps during the pandemic, specifically whether they changed their habits for teaching purposes, was related to the sector (university vs vocational) in which they were working.
 %
@@
 \multirow{4}{*}{\begin{tabular}[c]{@{}l@{}}Post-covid\\ changes\end{tabular}} & \begin{tabular}[c]{@{}l@{}}Yes, I use a safer messaging \\ app now\end{tabular} & 27 & 13 & 40 \\
- & \begin{tabular}[c]{@{}l@{}}Yes, I didn't use any \\ messaging app before, but \\ do use it now\end{tabular} & 31 & 13 & 44 \\
+ & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use any \\ messaging app before, but \\ do use it now\end{tabular} & 31 & 13 & 44 \\
  & \begin{tabular}[c]{@{}l@{}}No, I did use it before and \\ use it now\end{tabular} & 105 & 60 & 165 \\
- & \begin{tabular}[c]{@{}l@{}}No, I didn't use it before and \\ don’t use it now\end{tabular} & 22 & 2 & 24 \\
+ & \begin{tabular}[c]{@{}l@{}}No, I didn’t use it before and \\ don’t use it now\end{tabular} & 22 & 2 & 24 \\
 Total &  & 193 & 89 & 282 \\ \hline
@@
 \vspace{0.8em}
-\caption{Sector * post-COVID-19 changes cross-tabulation}
+\caption{Sector * post-covid changes cross-tabulation}
 \label{tab:sector*covid}
@@
 
-The majority of the teachers (n=165) mentioned that no changes in their habits occurred due to the shift to remote teaching due to the lock-down measures taken in their countries, as the use of messaging apps was part of their teaching practices and remained the same.
-Out of those 165 responders, 105 teachers come from the university and 60 teachers from the non-universitary tertiary sector.
-The relationships between changes in the use of messaging apps, due to the COVID-19 pandemic, and the instructors' discipline, $X^{2}_{(24, N = 282)} = 44.856$, $p =0.006$, as well as the gender, $X^{2}_{(8, N = 282)} = 16.249$, p= 0.039 were also significant.
+The majority of the teachers (n=165) mentioned that no changes in their habits occurred due to the emergency remote teaching, as the use of messaging apps was part of their teaching practices and remains the same, from which 105 teachers come from the university, and 60 teachers from the non-universitary tertiary sector.
+The relationships between changes in the use of messaging apps, due to the covid-19 pandemic, and the instructors’ discipline, $X^{2}_{(24, N = 282)} = 44.856$, $p =0.006$, as well as the gender, $X^{2}_{(8, N = 282)} = 16.249$, p= 0.039 were also significant.
 This finding indicates that how teachers responded to the use of messaging apps during the pandemic was also related to their gender and discipline.
-In fact, from the majority of the teachers who did not change their habits in this respect (n=165), most of them are males (n=114) and come from the technology (n=60) and engineering (n=53) disciplines (see Tables \ref{tab:gender*covid}, \ref{tab:discipline*covid}).
+In fact, from the majority of the teachers who did not change their habits in this respect (n=165), most of them are males (n=114), and come from the technology (n=60) and engineering (n=53) disciplines (see Tables \ref{tab:gender*covid}, \ref{tab:discipline*covid}).
 %
@@
 \multirow{4}{*}{\begin{tabular}[c]{@{}l@{}}Post-covid\\ changes\end{tabular}} & \begin{tabular}[c]{@{}l@{}}Yes, I use a safer messaging \\ app now\end{tabular} & 20 & 20 & 0 & 40 \\
- & \begin{tabular}[c]{@{}l@{}}Yes, I didn't use any \\ messaging app before, but \\ do use it now\end{tabular} & 20 & 23 & 1 & 44 \\
+ & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use any \\ messaging app before, but \\ do use it now\end{tabular} & 20 & 23 & 1 & 44 \\
  & \begin{tabular}[c]{@{}l@{}}No, I did use it before and \\ use it now\end{tabular} & 114 & 47 & 4 & 165 \\
- & \begin{tabular}[c]{@{}l@{}}No, I didn't use it before and \\ don’t use it now\end{tabular} & 18 & 6 & 0 & 24 \\
+ & \begin{tabular}[c]{@{}l@{}}No, I didn’t use it before and \\ don’t use it now\end{tabular} & 18 & 6 & 0 & 24 \\
  & Other & 7 & 2 & 0 & 9 \\
@@
 \vspace{0.8em}
-\caption{Gender * post-COVID-19 changes crosstabulation}
+\caption{Gender * post-covid changes crosstabulation}
 \label{tab:gender*covid}
@@
 \vspace{0.8em}
-\caption{Discipline * post-COVID-19 changes crosstabulation}
+\caption{Discipline * post-covid changes crosstabulation}
 \label{tab:discipline*covid}
@@
 % Olia - TODO: check for repetitions in the following paragraph that you added. thank you.
-Finally, we took a closer look at the post-COVID-19 changes and the variables
+Finally, we took a closer look at the post-covid changes and the variables
 gender, sector, and discipline for which the chi-square test is statistically
@@
 that shows the contribution of each cell to the test. In the Pearson's residual
-graphs, the responses to the question about the use of messaging apps were shortened for the sake of clarity according to: 1)
+graphs, \textcolor{black}{the responses to the question about the use of messaging apps were shortened for the sake of clarity according to}: 1)
 \textit{Did/do} stands for \textit{Yes, I did use it before and do use it now};
-2) \textit{Didn't/do} for \textit{Yes, I didn't use any messaging app before,
+2) \textit{Didn't/do} for \textit{Yes, I didn’t use any messaging app before,
   but do use it now}; 3) \textit{safer} for \textit{Yes, I use a safer messaging
-  app now}; 4) \textit{Didn't/Don't} for \textit{No, I didn't use it before and
-  don't use it now}.
+  app now}; 4) \textit{Didn't/Don't} for \textit{No, I didn’t use it before and
+  don’t use it now}.
 %
@@
 \begin{tabular}[c]{@{}l@{}}Post-\\ covid\\ changes\end{tabular} & \begin{tabular}[c]{@{}l@{}}Yes, I use a \\ safer messaging \\ app now\end{tabular} & 1.832 & 13.49\% & -1.832 & 7.50\% \\
- & \begin{tabular}[c]{@{}l@{}}Yes, I didn't use \\ any messaging \\ app before, but\\ do use it now\end{tabular} & \textbf{2.806} & \textbf{31.21\%} & \textbf{-2.806} & \textbf{17.36\%} \\
+ & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use \\ any messaging \\ app before, but\\ do use it now\end{tabular} & \textbf{2.806} & \textbf{31.21\%} & \textbf{-2.806} & \textbf{17.36\%} \\
  & \begin{tabular}[c]{@{}l@{}}No, I did use it \\ before and\\ use it now\end{tabular} & \textbf{2.850} & 15.15\% & \textbf{-2.850} & 8.43\% \\
- & \begin{tabular}[c]{@{}l@{}}No, I didn't use \\ it before and\\ don't use it now\end{tabular} & -1.011 & 4.40\% & 1.011 & 2.45\% \\ \hline
+ & \begin{tabular}[c]{@{}l@{}}No, I didn’t use \\ it before and\\ don’t use it now\end{tabular} & -1.011 & 4.40\% & 1.011 & 2.45\% \\ \hline
 \end{tabular}
@@
 \end{center}
-    \caption{Analysis for gender and post-COVID-19 changes: left) Pearson's residuals for the Chi-square test; right) Gender*post-COVID-19 changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized residuals) and contribution percentage to the total Chi-square test of each cell.}
+    \caption{Analysis for gender and post-covid changes: left) Pearson's residuals for the Chi-square test; right) Gender*post-covid changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized residuals) and contribution percentage to the total Chi-square test of each cell.}
 \label{figure:gender*postcovid_chisq}
@@
 
-As mentioned, the graphs on the left-hand side represent the Pearson's
+As mentioned, the graphs on the left hand side represent the Pearson's
 residuals, showing the difference between the observed and the expected values
 for each cell. Thus, large residuals indicate that variables are not truly
-independent. In our case, blue shows positive contributions and red negative
-contributions to the test. Additionally, the saturation shows how large the
-contribution is in contrast to the expected value by chance. 
-Tables show on the right hand side adjusted standardized residuals that according to
+independent. In our case, the blue shows positive contributions and red negative
+contributions to the test. Moreover, the saturation shows how large the
+contribution is in contrast to the expected value by chance. Additionally,
+tables on the right side show adjusted standardized residuals that according to
 \cite{agresti2013categorical}, if greater than +/-2 for cases with few cells,
-indicate lack of fit of $H_0$ (in boldface in our table). Complementarily, the
+indicate lack of fit of $H_0$ (in boldface in our table). Complementary, the
 table also shows the percentage of contribution to the test of each cell
-(the highest percentage per column also in boldface).
+(highest percentage per column also in boldface).
 
@@
 test results are explained by this cell. In contrast, male educators that
-responded the same were less than expected (negative contribution that explains
+respond the same were less than expected (negative contribution that explains
 17\% of the test results). Also, it is important to highlight the female
-educators that continued to use these apps before and after the pandemic and
+educators that kept using these apps before and after the pandemic and
 correspondingly the negative contribution of male educators to the same case
@@
           \begin{tabular}[c]{@{}l@{}}Post-\\ covid\\ changes\end{tabular} & \begin{tabular}[c]{@{}l@{}}Yes, I use a \\ safer messaging \\ app now\end{tabular} & 0.115 & 0.04\% & -0.115 & 0.08\% \\
-           & \begin{tabular}[c]{@{}l@{}}Yes, I didn't use \\ any messaging \\ app before, but\\ do use it now\end{tabular} & 0.454 & 0.56\% & -0.454 & 1.21\% \\
+           & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use \\ any messaging \\ app before, but\\ do use it now\end{tabular} & 0.454 & 0.56\% & -0.454 & 1.21\% \\
            & \begin{tabular}[c]{@{}l@{}}No, I did use it \\ before and\\ use it now\end{tabular} & \textbf{-2.122} & 5.71\% & \textbf{2.122} & 12.38\% \\
-           & \begin{tabular}[c]{@{}l@{}}No, I didn't use \\ it before and\\ don't use it now\end{tabular} & \textbf{2.939} & \textbf{25.26\%} & \textbf{-2.939} & \textbf{54.78\%} \\ \hline
+           & \begin{tabular}[c]{@{}l@{}}No, I didn’t use \\ it before and\\ don’t use it now\end{tabular} & \textbf{2.939} & \textbf{25.26\%} & \textbf{-2.939} & \textbf{54.78\%} \\ \hline
           \end{tabular}%
@@
 \end{center}
-    \caption{Analysis for sector and post-COVID-19 changes: left) Pearson's residuals for the Chi-square test; right) Sector*post-COVID-19 changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized  residuals) and contribution percentage to the total Chi-square test of each cell.}
+    \caption{Analysis for sector and post-covid changes: left) Pearson's residuals for the Chi-square test; right) Sector*post-covid changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized  residuals) and contribution percentage to the total Chi-square test of each cell.}
 \label{figure:sector*postcovid_chisq}
@@
 %
-With respect to the sector, results in Fig.
+With respect to the sector, the results in Fig.
 \ref{figure:sector*postcovid_chisq} show a positive contribution from university educators being reluctant to use any messaging apps before or after the pandemic: the positive contribution of their responses explain 25\% of the test results with an adjusted residual of 2.94.
 On the contrary, vocational teachers were more open to it, showing a negative Pearson's residual.
-Also, we find larger values than expected in vocational teachers that continued to use these apps after the pandemic.
+Also, we find larger values than expected in vocational teachers that kept using these apps after the pandemic.
 
@@
 \end{center}
-    \caption{Analysis for discipline and post-COVID-19 changes: left) Pearson's residuals for the Chi-square test; right) Discipline*post-COVID-19 changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized residuals) and contribution percentage to the total Chi-square test of each cell.}
+    \caption{Analysis for discipline and post-covid changes: left) Pearson's residuals for the Chi-square test; right) Discipline*post-covid changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized residuals) and contribution percentage to the total Chi-square test of each cell.}
 \label{figure:discipline*postcovid_chisq}
@@
 %
-Finally, statistical significance was found for discipline vs. post-COVID-19
+Finally, statistical significance was found for the discipline and post-covid
 changes. Regarding disciplines (see
@@
 19\% of the chi-square test results. Also, the number of educators from
-Technology or Engineering that started using safer alternatives \footnote{This addresses the issue of insecure/unsafe applications which do not encrypt messages or can be easily compromised by exposing information} are less than
+Technology or Engineering that started using safer alternatives \footnote{This addresses the issue of insecure/unsafe applications which do not encrypt messages or can be easily compromised exposing information} are less than
 expected (compared to the educators from other disciplines). Bear in mind that
@@
 
-For answering RQ2, teachers were provided with a list of different potential chatbot functionalities (use cases) and were requested to indicate whether each given use case would be useful in their classes.
+For answering RQ2, teachers were provided with a list of different potential chatbot functionalities (use cases) and were requested to respond on whether each given use case would be useful in their classes.
 The findings are summarized in Table \ref{tab:chatbottypes}.
@@
 The most beneficial use case for chatbots in higher education and vocational training is their ability to facilitate agenda formation and communication (171 positive responses, 60.6\%), followed by the FAQs use case
-(148 positive responses, 52.5\%), and the sharing class material use case (136;
-48.2\%). A chi-square test of independence was performed to examine the relationship
-among participants' preferences for particular chatbot use cases. Out of the 171 teachers who considered useful the use of
-chatbots for agenda preparation in the class, 103 also consider useful chatbots'
-use for FAQs. The relationship between agenda and the FAQs use case was significant, $X^{2}_{(1, N = 282)} =
-10.467$, $p =0.001$. The frequencies cross-tabulated are given in Table
+(148 positive responses, 52.5\%) and the sharing class material use case (136;
+48.2\%). A chi-square test of independence was performed to examine the relation
+among participants’ preferences for particular chatbot use cases. Out of the 171 teachers who consider useful the use of
+chatbots for agenda preparation in the class, 103 also consider useful chatbots’
+use for FAQs. The relation between agenda and the FAQs use case was significant, $X^{2}_{(1, N = 282)} =
+10.467$, $p =0.001$. The frequencies cross tabulated are given in Table
 \ref{tab:agenda*faq}.
@@
 by gender, sector, years of experience in education, and discipline
-respectively. As it was a multiple-choice question, the counts are over the
-total number of educators who answered.
+respectively. As it was a multiple choice question, the counts are over the
+total number of people that answered.
 
@@
 Since chatbots are intended to mediate or help in this interaction, it is
-essential to understand the kind of interaction that teachers prefer. Chatbots should
+essential to understand the kind of interaction teachers prefer. Chatbots should
 address those modes, and not others. In order to find out these modes, and thus
-answering RQ3, teachers were provided with a list of different kinds of
-interactions that may take place among students and between students and their
-teacher, when using messaging apps. The findings are summarized in Table
+answering RQ3, teachers were provided with a list of different kind of
+interactions that may take place among students and between students and the
+teacher, with the use of messaging apps. The findings are summarized in Table
 \ref{tab:kindinteractions}.
@@
 
-As it can be seen by the answers to the first and last questions, in general
-teachers do not want to participate in a chat group with their students. They either
+As it can be seen by the answer to the first and last question, in general
+teachers do not want to participate in a chat group with students; either they
 want to simply leave the students alone in their own chat group, or otherwise
@@
 to take any part in these informal or non institutionally-supported chat
-groups. Overwhelmingly, they do not want to participate in this kind of chat
+groups. Overwhelmingly, they do not want to participate in these kind of chat
 groups with students, but even less so if it includes the rest of the faculty.
 
-Then, the answer to this research question is that in general, teachers do
+The answer, then, to this research question, is that, in general, teachers do
 {\em not} want to have interaction with students in a chat group. To a certain
@@
 to Fig. \ref{figure:chatbots_messagingorganization} the vast majority prefer
-small groups only with their students from the same course. These are more focused
-groups with specific goals and dedicated to the course organization and
-its tasks, and from the pedagogic point of view it also seems more adequate to improve
-the learning process. Interestingly, and as a cross-check of the answers above,
+small groups only with the students from the same course. These are more focused
+groups with specific goals and dedicated to the organization of the course and
+its tasks, and from the pedagogic point of view \textcolor{black}{it also seems more appropriate to improve
+the learning process}. Interestingly, and as a cross-check of the answers above,
 about 30\% of teachers consider they should not be part of the chat group. This
@@
 a great amount of teachers that would be against being in a chat group with
-students. However, students will still need to get the services
+students. \textcolor{black}{However, students will still need to get the services
 that the university, through chatbots, provide, thus opening the door for deployment of chatbots
-without the intervention of their professors, simply tapping university provided
-services \cite{bernier2002services}.
-Whether that is a slim majority or not, that is open to debate (and
-would probably need a more focused survey). However, it is clear 
+without the intervention of the professor, simply tapping university provided
+services \cite{bernier2002services}.}
+Whether that's a slim majority or not, that's open to debate (and
+would probably need a more pointed survey focused on this), but what is clear is
 that forcing teachers to create chat groups with students and participate in
@@
 and social interaction (e.g. \cite{dibitonto2018chatbot}) might be the reason
-for the low percentage of teachers that chose this response.
+for the low percentage of teachers that selected this response.
 
@@
 
-As show in Table \ref{tab:interaction}, the bulk of responders expressed their wish to use a sustainable and official application, i.e.
-both being approved or provided by their educational institution, and also maintained by the technical staff of the institution instead of giving this responsibility/task to the teacher.
-In addition, it is very important for teachers that used the tools that all the members of the class communicate, including themselves; as well as using tools that are already known or used in everyday tasks, e.g.
-Telegram or WhatsApp.
+\textcolor{black}{As it can be seen in the table, the bulk of responders express their wish to use a sustainable and official application, i.e.
+both being approved or provided by the University (or the educational center), and also maintained by the technical staff of the center instead of giving this responsibility/task to the teacher.
+In addition, it is very important for the teachers that the used tools that all the members of the class communicate, including themselves; as well as being already known or used in everyday tasks, e.g.
+Telegram or WhatsApp.}
 
@@
 Every cell value represents $X^{2}_{(1, N = 205)}$.
-Details about each feature can be found in Appendix I.}
+Details about each feature can be read in Appendix I.}
 \label{tab:interactionfeatures}
@@
 have larger predictor importance for the clustering (see
-Fig. \ref{figure:predictor}). Two clusters resulted from the analysis: cluster 1
+Fig. \ref{figure:predictor}). Two clusters occurred from the analysis: cluster 1
 (n=78, 60.9\%) is formed with instructors who did not value interaction media
-pluggability, connectivity, and official formation, but valued interaction media
-analytics, familiarity, and support by their institution; cluster 2 (n=50,
+pluggability, connectivity, official formation, but valued interaction media
+analytics, familiarity, support by the institution; cluster 2 (n=50,
 39.1\%) groups instructors that did not value media
-analytics, official formation, and familiarity, but valued pluggability,
-connectivity, and support by their institution. Interaction media pluggability
+analytics, official formation, familiarity, but valued pluggability,
+connectivity, and support by the institution. Interaction media pluggability
 appears to have the most important predictor importance in the clustering of
@@
 important factor (predictor importance = 0.04). The cluster quality is fair, but
-not a good one (as indicated by the silhouette measure of cohesion and separation).
+not a good one (silhouette measure of cohesion and separation).
 
@@
 only listed a few functionalities for the chatbots, and just a few subjects selected
-the option ``Others''. This may suggest that most teachers did not really understand
+the option "Others". This may suggest that most teachers did not really understand
 at this point the actual potential of chatbots, since the responses listed were by no means exhaustive.
@@
 bring major changes in attitude 
-%(as a minor ``crisis'' we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.}),
+%(as a minor "crisis" we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.}),
 %or simply the introduction of new degrees. 
@@
 moment to introduce new technologies is always when the IT and managing staff is
-ready to support it (since, as we have seen before, ``official'' support is one of
+ready to support it (since, as we have seen before, "official" support is one of
 the factors that is most valued by teachers).

### 2023-01-10 edubots_surveys.Rnw
:recycle: with better grammar

@@
 
-The success of this adoption largely depends on the willingness and ability of
-teachers to embrace it, as they are the primary agents in this new educational
-approach. As such, gathering and assessing feedback from these users will be
-crucial in realizing the potential benefits of the technology.
+However, the success of this adoption largely depends on the willingness and
+ability of teachers to embrace it, as they are the primary agents in this new
+educational approach. As such, gathering and assessing feedback from these users
+will be crucial in realizing the potential benefits of the technology.
 

### 2023-01-10 edubots_surveys.Rnw
:refactor: to fill paragraphs
Eliminates commented out code and rewrites last paragraph

--- 2023-01-10 edubots_surveys.Rnw
@@
 
-New technologies have been introduced and widely adopted into the classroom in
-recent years. However, in order to be successful, their application will require
-a certain amount of extra work and training for the teacher, as well as for the
-students. Training will help the two collectives involved acquire new skills
-and, potentially, pupils will acquire a greater level of engagement with the
-subject matter, which is usually the main objective. Even if several
-technologies are already in use inside the classroom, there is still room for
-adopting others.
-
-The success of this adoption largely depends on the willingness and ability of
-teachers to embrace it, as they are the primary agents in this new educational
-approach. As such, gathering and assessing feedback from these users will be
-crucial in realizing the potential benefits of the technology.
-
-Over the past decade, messaging apps like WhatsApp and Telegram have become
-increasingly popular in teaching at the secondary and higher education levels
-\cite{gachago2015crossing,mwakapina2016whatsapp,yin2016adoption,panah2020study}. By
-creating groups at various levels (e.g. class, assignment, course), teachers and
-students have been able to use these apps for bilateral or group-level
-communication. In addition to their primary function of communication, many
-messaging programs also allow the creation of applications that can act as users
-through open application programming interfaces (APIs), which are often
-available through a free or freemium model.
-
-This opens the door to the introduction of \textit{chatbots}, that is,
-autonomous agents able to communicate and interact with humans (or other
-chatbots) in a natural way \cite{Gong2008,differ.chat}, answering question and
-even posing their own ones to the user, in the classroom; in this limited
-environment, chatbots can appear as regular users, thus being close to passing a
-Turing Test \cite{moor2003turing}, which gives them certain characteristics
-that, again, can enhance student engagement. Chatbots implement different
-Artificial Intelligence techniques, such as natural language processing as well
-as, in some cases, learning; this is not a requirement, however, and in most
-cases they are simply applications that have a conversational interface, as
-opposed to a graphical user interface.
-
-These qualities have made education one of the most promising areas for chatbot
-applications today \cite{clarizia2018,Smutny2020}. In this domain, they
-facilitate the so-called \textit{personalized learning}, i.e. they adapt
-themselves to students’ pace of learning and provide online tutoring outside the
-classroom, which have been proved to be very effective increasing their
-engagement and participation in the subjects \cite{agarwal2020}. Moreover
-chatbots' tutoring possibilities aid to reduce the stress of students
-\cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their
-teacher, or asking questions in front of the class. This situation normally
-conducts to a silence of the student and a later contact with the teacher by
-e-mail, which, in turn, will mean a workload for the teacher, that could be very
-significant given the existing disproportion between number of students per each
-teacher.
-
-Hence, the chatbot technology has a potential to mitigate this problem by
-providing answers to students’ questions and facilitating a dynamic and
-autonomous learning experience \cite{Griol2014,kim2020}. In addition, using an
-automated system such as a chatbot will allow teachers to spend more time on
-other topics that students struggle with.
+New technologies have been introduced and widely adopted into the classroom in recent years. However, in order to be successful, their application
+will require a certain amount of extra work and training for the teacher, as well as for the students.
+Training will help the two collectives involved acquire new skills and, potentially, pupils will acquire a greater level of engagement with the subject matter, which is usually the main objective.
+Even if several technologies are already in use inside the classroom, there is still room for adopting others.
+
+Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Given this,
+asking and analyzing user's opinions with regard to this scenario will help reaping the expected benefits of the technology.
+
+Over the past decade, messaging apps like WhatsApp and Telegram have become increasingly popular in teaching at the secondary and higher education levels \cite{gachago2015crossing,mwakapina2016whatsapp,yin2016adoption,panah2020study}.
+By creating groups at various levels (e.g.
+class, assignment, course), teachers and students have been able to use these apps for bilateral or group-level communication.
+In addition to their primary function of communication, many messaging programs also allow the creation of applications that can act as users through open application programming interfaces (APIs), which are often available through a free or freemium model.
+
+This opens the door to the introduction of \textit{chatbots}, that is, autonomous agents able to communicate and interact with humans (or other chatbots) in a natural way \cite{Gong2008,differ.chat}, answering question and even posing their own ones to the user, in the classroom; in this limited environment, chatbots can appear as regular users, thus being close to passing a Turing Test \cite{moor2003turing}, which gives them certain characteristics that, again, can enhance student engagement.
+Chatbots implement different Artificial Intelligence techniques, such as natural language processing as well as, in some cases, learning; this is not a requirement, however, and in most cases they are simply applications that have a conversational interface, as opposed to a graphical user interface.
+
+These qualities have made education one of the most promising areas for chatbot applications today \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called
+\textit{personalized learning}, i.e. they adapt themselves to students’ pace of learning and provide online tutoring outside the classroom, which have been proved to be very effective increasing their
+engagement and participation in the subjects \cite{agarwal2020}.
+Moreover chatbots' tutoring possibilities aid to reduce the stress of students \cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their teacher,
+or asking questions in front of the class.
+This situation normally conducts to a silence of the student and a later contact with the teacher by e-mail, which, in turn, will mean a workload for the teacher, that could be very
+significant given the existing disproportion between number of students per each teacher.
+
+Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning
+experience \cite{Griol2014,kim2020}. In addition, using an automated system such as a chatbot will allow teachers to spend more time on  other topics that students struggle with.
 
@@
 focus of the % EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
-unnamed European project, the main sponsor of this study, is to explore best
-practices and innovative use of chatbots, and to create a learning community of
-educators in higher education institutions.  Researchers and teachers
-participating in this project have developed several studies. Most of these
-works have been focused on how messaging applications and/or chatbots are
-normally applied to deliver personalized learning in classrooms that occurs
-anytime anywhere, and promote collaborative learning experiences or group
-discussions \cite{panah2020study}, and boost students' sense of belonging to
-their institutions \cite{abbas2021onlinechat}.  The majority of these studies
-were conducted focusing on the teachers' perspectives, so this paper aims to
-provide more conclusions regarding their opinions and needs, as well as the
-existing challenges or opportunities that arise when adopting these technologies
-in classrooms. This will lead to clarify how they can positively contribute to
-enhancing the learning process in higher education institutions.
+unnamed European project, the main sponsor of this study, is to explore best practices and innovative use of chatbots,
+and to create a learning community of educators in higher education institutions.
+Researchers and teachers participating in this project have developed several studies. Most of these works have been focused on how 
+messaging applications and/or chatbots are normally applied to deliver personalized learning in classrooms that occurs anytime anywhere, and
+promote collaborative learning experiences or group discussions \cite{panah2020study}, and boost students' sense of belonging to their institutions
+\cite{abbas2021onlinechat}.
+The majority of these studies were conducted focusing on the teachers' perspectives, so this paper aims to provide more conclusions regarding
+their opinions and needs, as well as the existing challenges or opportunities that arise when adopting these technologies in classrooms. This will lead to clarify
+how they can positively contribute to enhancing the learning process in higher education institutions.
 
@@
 
-We will try to respond to these research questions through the analysis of the
-answers provided by professors to the two aforementioned surveys.  Eventually,
-the main research outcome of this survey should be a series of recommendations
-to make a successful deployment of chatbot technologies (and, in some cases,
-general instant messaging applications) in higher education; from the response
-to RQ1 and RQ4 we will try to recommend specific technologies or applications to
-be deployed in the classroom; the response to RQ2 and RQ3 will help us recommend
-chatbots features or specific platforms; and finally, from RQ3 we will also try
-to find best practices in the adoption of messaging platforms and their matching
-chatbots.
+We will try to respond to these research questions through the analysis of the answers provided by professors to the two aforementioned surveys.
+Eventually, the main research outcome of this survey should be a series of
+recommendations to make a successful deployment of chatbot technologies (and, in
+some cases, general instant messaging applications) in higher education; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be deployed in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from RQ3 we will also try to find best practices in the adoption of messaging platforms and their matching chatbots.
 
@@
 % The Use of Mobile Instant Messaging (MIM) Platforms in Higher Education
-The widespread and rapid adoption of free Mobile Instant Messaging
-(MIM) tools/platforms such as WhatsApp, Telegram, WeChat and Facebook
-Messenger stems from their simplicity, ease of use and multi-modality
-(i.e. video, audio, text) \cite{tang2017mobile}. Using these tools in
-higher education institutions facilitates the delivery of personalized learning
-that occurs anytime anywhere, and promotes collaborative learning
-experiences and group discussions \cite{panah2020study}.
-
-WhatsApp is, at least in most Western countries, the most popular MIM platform. The reason is that it is the tool preferably
-used by educators to provide assignments' feedback to students, support course
-discussions, and post learning resources in a semi-formal learning context
-\cite{panah2020study}.  Moreover, the use of WhatsApp in higher education could
-enhance social presence \cite{tang2017mobile} and foster trust relationships
-between educators and students embedded in the social learning process
+The widespread and rapid adoption of free Mobile Instant Messaging (MIM)
+tools/platforms such as WhatsApp, Telegram, WeChat and Facebook Messenger stems
+from their simplicity, ease of use and multi-modality (i.e. video, audio, text)
+\cite{tang2017mobile}. Using these tools in higher education institutions
+facilitates the delivery of personalized learning that occurs anytime anywhere,
+and promotes collaborative learning experiences and group discussions
+\cite{panah2020study}.
+
+WhatsApp is, at least in most Western countries, the most popular MIM
+platform. The reason is that it is the tool preferably used by educators to
+provide assignments' feedback to students, support course discussions, and post
+learning resources in a semi-formal learning context \cite{panah2020study}.
+Moreover, the use of WhatsApp in higher education could enhance social presence
+\cite{tang2017mobile} and foster trust relationships between educators and
+students embedded in the social learning process
 \cite{gachago2015crossing}. However, this last paper also reflects the need for
@@
 in general. At the same time, it also mentions different challenges, among which
-the most important is the blurring of social and academic life; indeed, there are challenges when using MIM tools that occur due to the
-blurring of boundaries between academic and private life. This can lead to
-technostress \cite{gachago2015crossing}, difficulty in managing
-responsibilities, especially among mature students, and lack of privacy
-\cite{tang2017mobile}.  Students' dropout of the MIM groups, as they can leave
-groups at any time, can hinder their learning and undermine educators' efforts
-\cite{mwakapina2016whatsapp}.  In addition, there is a need to set rules and
-norms for these MIM groups in order to maintain the safety of these online
-communities for students \cite{abbas2021onlinechat}. However, these rules should
-not affect students' ownership and control, since it is vital to advance in
-their learning \cite{gachago2015crossing} process.  This is why examining the
-role of MIM platforms in higher education, as well as applications based on them such as chatbots, is still a challenge, and why the opinions of
-the teaching community towards them have to be examined, as we do in this paper.
+the most important is the blurring of social and academic life; indeed, there
+are challenges when using MIM tools that occur due to the blurring of boundaries
+between academic and private life. This can lead to technostress
+\cite{gachago2015crossing}, difficulty in managing responsibilities, especially
+among mature students, and lack of privacy \cite{tang2017mobile}.  Students'
+dropout of the MIM groups, as they can leave groups at any time, can hinder
+their learning and undermine educators' efforts \cite{mwakapina2016whatsapp}.
+In addition, there is a need to set rules and norms for these MIM groups in
+order to maintain the safety of these online communities for students
+\cite{abbas2021onlinechat}. However, these rules should not affect students'
+ownership and control, since it is vital to advance in their learning
+\cite{gachago2015crossing} process.  This is why examining the role of MIM
+platforms in higher education, as well as applications based on them such as
+chatbots, is still a challenge, and why the opinions of the teaching community
+towards them have to be examined, as we do in this paper.
 
 % The Use of Chatbots in Higher Education
-The use of MIM platforms, although possibly valuable by itself, can be enhanced with the
-use of chatbots, which are conversational agents that normally dwell in
-synchronous conversations systems. The use of chatbots in higher education is still in its early stages
-\cite{yang2019opportunities}. Nevertheless, recent studies have shown their
-positive impact on students' academic performance \cite{perez2020rediscovering}
-and engagement \cite{differ.chat,abbas2021onlinechat}, leading to a growing
-interest in using this technology in the (possibly virtual) classroom. Indeed,
-using chatbots to collect course feedback from students in higher
-education improved the quality of responses given by students in their assignments, and boosted engagement levels
-\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
-mobile devices along with gamification strategies
-\cite{Yildirim2017} can improve student motivation. In this sense, the authors
-in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
-report the positive impact of using instant messaging tools in boosting
-students' knowledge and mitigating their feelings of isolation.
-
-Several studies to evaluate chatbots in higher education have been conducted. For
-instance, a comprehensive study was presented by Smutny and Schreiberova
-\cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
-Messenger, concluding that most of these chatbots were very basic and that programmers require of more support to develop and 
-offer tools for improving coaching methods and students learning. Pérez and collaborators
-\cite{perez2020rediscovering} attempted to categorize educational chatbots attending to their purpose 
-as service-oriented or teaching-oriented. Service-oriented chatbots
-include those that provide service support, such as Ask Holly
-\cite{meetholly} and Dina \cite{santoso2018dinus}, which respond to
-students' questions about enrollment and registration. Ask L. U.
-\cite{LancasterUniversity_2019} answers students' frequently asked questions
-about schedules, grades, tutors, and societies. LISA \cite{dibitonto2018chatbot}
-and Differ \cite{differ.chat} facilitate breaking the ice between new students
-by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
-proposed a generic chatbot for university students that is able to answer 
-frequently asked questions. The University of Granada deployed
-Elvira, a chatbot embedded in its main web page \cite{MOREO20129} to perform the same task. In addition to being able
-to answer pre-established frequent questions, it did so from the website of
-the University of Granada using an inset persona, voiced by a real person, who
-lip-synced the answers. However, in the case of Elvira, the emphasis was on the
-authenticity of the speech-mouth and face gestures synchronization rather than making updating
-answered questions simpler or more interactive for the administrative staff, or more open to the rest of the university staff using actual messaging platforms. In
-most cases, the embedded search engine was able to provide more up-to-date
-and accurate answers than those provided by Elvira, which had to be updated
-by hand (and not too often).
-It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide a useful service.
-Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, which is the focus of this paper.
-
-Contrarily to the mentioned chatbots that are focused on administrative tasks, teaching-oriented chatbots are more sophisticated, as they
-set personalized learning outcomes and monitor learning progress. For instance,
+The use of MIM platforms, although possibly valuable by itself, can be enhanced
+with the use of chatbots, which are conversational agents that normally dwell in
+synchronous conversations systems. The use of chatbots in higher education is
+still in its early stages \cite{yang2019opportunities}. Nevertheless, recent
+studies have shown their positive impact on students' academic performance
+\cite{perez2020rediscovering} and engagement
+\cite{differ.chat,abbas2021onlinechat}, leading to a growing interest in using
+this technology in the (possibly virtual) classroom. Indeed, using chatbots to
+collect course feedback from students in higher education improved the quality
+of responses given by students in their assignments, and boosted engagement
+levels \cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
+mobile devices along with gamification strategies \cite{Yildirim2017} can
+improve student motivation. In this sense, the authors in \cite{Pimmer2019}
+adopted a quasi-experimental, survey-based approach to report the positive
+impact of using instant messaging tools in boosting students' knowledge and
+mitigating their feelings of isolation.
+
+Several studies to evaluate chatbots in higher education have been
+conducted. For instance, a comprehensive study was presented by Smutny and
+Schreiberova \cite{Smutny2020} reviewing 47 educational chatbots implemented in
+Facebook Messenger, concluding that most of these chatbots were very basic and
+that programmers require of more support to develop and offer tools for
+improving coaching methods and students learning. Pérez and collaborators
+\cite{perez2020rediscovering} attempted to categorize educational chatbots
+attending to their purpose as service-oriented or
+teaching-oriented. Service-oriented chatbots include those that provide service
+support, such as Ask Holly \cite{meetholly} and Dina \cite{santoso2018dinus},
+which respond to students' questions about enrollment and registration. Ask
+L. U.  \cite{LancasterUniversity_2019} answers students' frequently asked
+questions about schedules, grades, tutors, and societies. LISA
+\cite{dibitonto2018chatbot} and Differ \cite{differ.chat} facilitate breaking
+the ice between new students by introducing them to each other. Ranoliya et
+al. \cite{ranoliya2017chatbot} proposed a generic chatbot for university
+students that is able to answer frequently asked questions. The University of
+Granada deployed Elvira, a chatbot embedded in its main web page
+\cite{MOREO20129} to perform the same task. In addition to being able to answer
+pre-established frequent questions, it did so from the website of the University
+of Granada using an inset persona, voiced by a real person, who lip-synced the
+answers. However, in the case of Elvira, the emphasis was on the authenticity of
+the speech-mouth and face gestures synchronization rather than making updating
+answered questions simpler or more interactive for the administrative staff, or
+more open to the rest of the university staff using actual messaging
+platforms. In most cases, the embedded search engine was able to provide more
+up-to-date and accurate answers than those provided by Elvira, which had to be
+updated by hand (and not too often). It was eventually discontinued, and its
+technology was not adapted to other platforms, since it did not really provide a
+useful service. Its service was not tied to teaching anyway; it was more related
+to directory queries and university-wide administrative questions, so even if it
+is strictly an example of a chatbot in a university setting, it is not really a
+chatbot that can be adopted by teachers to affect the learning outcomes, which
+is the focus of this paper.
+
+Contrarily to the mentioned chatbots that are focused on administrative tasks,
+teaching-oriented chatbots are more sophisticated, as they set personalized
+learning outcomes and monitor learning progress. For instance,
 \cite{fernoagua2018intelligent} reported on ``eduAssistant'', a virtual teaching
 assistant chatbot developed on the Telegram messaging platform. In this study,
-the Telegram platform was chosen because it is easy to use, students are familiar
-with its features, and it enables them to exchange messages in different formats
-(text, audio and video) \cite{fernoagua2018intelligent}. In addition, Telegram
-can operate on all devices and operating systems. The ``eduAssistant'' chatbot
-acts as an automatic agent in the teacher-content-student relationship, providing real-time
-feedback loops and a personalized learning experience relevant to the
-students' acquired skills and knowledge. Using this chatbot, educators can
-create interactive instances in their lectures where they pose questions to
-their students and the chatbot assists those who need further help by giving
-them more hints and reporting it to the educator's dashboard
-\cite{fernoagua2018intelligent}. This could help educators identify
-students who need more attention and provide them with more educational resources
-relevant to their academic achievement. %In addition, a recent study
-%has analysed how the use of chatbots positively affected the learning outcomes
-%of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
+the Telegram platform was chosen because it is easy to use, students are
+familiar with its features, and it enables them to exchange messages in
+different formats (text, audio and video) \cite{fernoagua2018intelligent}. In
+addition, Telegram can operate on all devices and operating systems. The
+``eduAssistant'' chatbot acts as an automatic agent in the
+teacher-content-student relationship, providing real-time feedback loops and a
+personalized learning experience relevant to the students' acquired skills and
+knowledge. Using this chatbot, educators can create interactive instances in
+their lectures where they pose questions to their students and the chatbot
+assists those who need further help by giving them more hints and reporting it
+to the educator's dashboard \cite{fernoagua2018intelligent}. This could help
+educators identify students who need more attention and provide them with more
+educational resources relevant to their academic
+achievement.
 
 Despite its (arguably) successful implementation in different higher education
-institutions, particularly on the fringes of educational activity rather than actual
-student-teacher interaction, its implementation or deployment is not trivial.
-Some authors, for instance \cite{sjostrom2018designing}, have proposed a
-conceptual architecture for the adoption of teaching-oriented chatbots in higher
-education.  This conceptual architecture is based on a systematic literature
-review of previous studies examining the design of chatbots in higher
+institutions, particularly on the fringes of educational activity rather than
+actual student-teacher interaction, its implementation or deployment is not
+trivial.  Some authors, for instance \cite{sjostrom2018designing}, have proposed
+a conceptual architecture for the adoption of teaching-oriented chatbots in
+higher education.  This conceptual architecture is based on a systematic
+literature review of previous studies examining the design of chatbots in higher
 education, as well as making a content analysis of student emails and discussion
-forum posts from four instances of a Java programming course.  The study outlined
-several design considerations; among them, the authors emphasized the importance
-of developing chatbots in platforms that students and educators are familiar
-with and can easily access (i.e. Facebook Messenger), which was confirmed by
-\cite{hobert2019you} and \cite{fernoagua2018intelligent}. In addition, \cite{sjostrom2018designing} argued that 
-conceptualizing learners' questions could help designers integrate the
-appropriate types of questions that chatbots should support for different
-courses. Other authors, such as \cite{coronado2018cognitive}, have proposed agents that
-record learning materials to be provided on demand to students, while \cite{crockett2017predicting} 
-reported on tutoring systems that can
-perform initial assessments of students' understanding and provide learning
-materials to advance their understanding to the next level.
+forum posts from four instances of a Java programming course.  The study
+outlined several design considerations; among them, the authors emphasized the
+importance of developing chatbots in platforms that students and educators are
+familiar with and can easily access (i.e. Facebook Messenger), which was
+confirmed by \cite{hobert2019you} and \cite{fernoagua2018intelligent}. In
+addition, \cite{sjostrom2018designing} argued that conceptualizing learners'
+questions could help designers integrate the appropriate types of questions that
+chatbots should support for different courses. Other authors, such as
+\cite{coronado2018cognitive}, have proposed agents that record learning
+materials to be provided on demand to students, while
+\cite{crockett2017predicting} reported on tutoring systems that can perform
+initial assessments of students' understanding and provide learning materials to
+advance their understanding to the next level.
 
@@
 \cite{Roblyer2010,Pimmer2019}. However, higher education is a special domain
-where, according to \cite{hobert2019you}, specific pedagogical factors
-such as learning success and increased motivation are more important.  Therefore,
-to develop effective chatbots for higher education, the needs of all stakeholders
-(i.e. educators, students, institutions, etc) should be carefully
-collected and taken into consideration
-\cite{sjostrom2018designing,tsivitanidouusers}.
-These needs include, but are not limited to, student learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance.
-Both authors focus on what teachers need in terms of the latter; this paper will focus on a wider perspective, trying to determine what they are looking for in terms of general messaging technology.
-The classical literature \cite{tam91} already proposes that any adoption of technology must be tuned to the user needs and experience.
-In this paper, we will try to find out what those are in order to propose a successful model of adoption of chatbot technology.
-
-In line with this research, our previous work \cite{MoraChatbots2021:anon}
-aimed at analyzing the expectations of students in this regard. Another paper
-have also analysed how the use of chatbots affected the learning outcomes of
-students in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper
-considered conversational chatbots in a one-to-one setting, finding that learning
-truly benefited from it. This is, once again, an evidence of the benefit of
-chatbots in certain settings; however, there are some prior experiences, as well as needs, that may
-prevent the successful acceptance of the technology, and these are what we are
-trying to find out in this paper, along with what kind of features would improve
-its acceptance.
+where, according to \cite{hobert2019you}, specific pedagogical factors such as
+learning success and increased motivation are more important.  Therefore, to
+develop effective chatbots for higher education, the needs of all stakeholders
+(i.e. educators, students, institutions, etc) should be carefully collected and
+taken into consideration \cite{sjostrom2018designing,tsivitanidouusers}. These
+needs include, but are not limited to, student learning success due to higher
+motivation, but these are a posteriori effects that cannot be assessed in
+advance. Both authors focus on what teachers need in terms of the latter; this
+paper will focus on a wider perspective, trying to determine what they are
+looking for in terms of general messaging technology. The classical literature
+\cite{tam91} already proposes that any adoption of technology must be tuned to
+the user needs and experience. In this paper, we will try to find out what those
+are in order to propose a successful model of adoption of chatbot technology.
+
+In line with this research, our previous work \cite{MoraChatbots2021:anon} aimed
+at analyzing the expectations of students in this regard. Another paper have
+also analysed how the use of chatbots affected the learning outcomes of students
+in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper considered
+conversational chatbots in a one-to-one setting, finding that learning truly
+benefited from it. This is, once again, an evidence of the benefit of chatbots
+in certain settings; however, there are some prior experiences, as well as
+needs, that may prevent the successful acceptance of the technology, and these
+are what we are trying to find out in this paper, along with what kind of
+features would improve its acceptance.
 
 Besides, this work is focused on the other key actor in this challenge:
-educators. How they accept chatbots has been studied very recently by Chocarro et
-al. \cite{doi:10.1080/03055698.2020.1850426}, who, by analyzing surveys, created
-a TAM that proposed a series of features that
-would make chatbots easier to accept, including formality of language as well
-as easiness and usefulness. The survey targeted primary and secondary education
-teachers and was also more interested in the general use of chatbots in
-education, not specifically in a classroom setting, seeking educational
-outcomes. However, their results are obviously
-interesting and relevant for this work.
-
-We will present next the methodology we followed to find out teachers' opinions.
+educators. How they accept chatbots has been studied very recently by Chocarro
+et al. \cite{doi:10.1080/03055698.2020.1850426}, who, by analyzing surveys,
+created a TAM that proposed a series of features that would make chatbots easier
+to accept, including formality of language as well as easiness and
+usefulness. The survey targeted primary and secondary education teachers and was
+also more interested in the general use of chatbots in education, not
+specifically in a classroom setting, seeking educational outcomes. However,
+their results are obviously interesting and relevant for this work.
+
+Next, we will describe the methodology we employed to gather teachers' perspectives.
 

### 2023-01-10 edubots_surveys.Rnw
Reformat and rewrite sentence

@@
 
-Several studies to evaluate chatbots in higher education have been
-conducted. For instance, a comprehensive study was presented by Smutny and
+Multiple studies have been conducted to assess the effectiveness of chatbots in
+higher education; among them, a comprehensive paper was presented by Smutny and
 Schreiberova \cite{Smutny2020} reviewing 47 educational chatbots implemented in
@@
 that programmers require of more support to develop and offer tools for
-improving coaching methods and students learning. Pérez and collaborators
-\cite{perez2020rediscovering} attempted to categorize educational chatbots
-attending to their purpose as service-oriented or
+improving coaching methods and student learning outcomes. Pérez and
+collaborators \cite{perez2020rediscovering} attempted to categorize educational
+chatbots attending to their purpose as service-oriented or
 teaching-oriented. Service-oriented chatbots include those that provide service

### 2023-01-10 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

--- 2023-01-10 edubots_surveys.Rnw
@@
 
-This study has employed a quantitative approach in order to address its research objective.
-A good amount of data was collected on the usage of messaging applications and chatbots by educators in universities and colleges.\footnote{In Spain, higher education institutions generally known elsewhere as colleges, are called simply high schools, and deliver
-tertiary or associate degrees that do not have the consideration of university degrees.}
-To achieve this goal two online surveys were designed and developed using Google Forms
-in Spanish. They are comprised of six questions focusing on demographic data
-(i.e., sector, gender, degrees, discipline, age, teaching experience)
-followed by several multiple choice questions allowing the participants to choose multiple answers.
-
-In the {\bf first survey}, the multiple choice questions are
-focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers would consider
-useful for their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
-university and the other for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees). Questions and
+This study employed a quantitative approach to address its research objectives.
+A significant amount of data was collected on the usage of messaging applications and chatbots by educators in universities and colleges.\footnote{In Spain, higher education institutions that would generally known as colleges in other places, are simply called high schools, and provide
+tertiary or associate degrees that do not have the same consideration as university degrees.}
+To collect this data, two online surveys were designed and developed using Google Forms
+in Spanish. These surveys consisted of six questions on demographic data
+(such as sector, gender, degrees, discipline, age, or teaching experience)
+followed by several multiple-choice questions allowing participants to choose multiple answers.
+
+The {\bf first survey} consisted of multiple-choice questions 
+focused on the use of messaging apps in teaching practice, the type of chatbot use cases that educators would find
+useful for their teaching and the impact of COVID on teaching practice.
+These questions can be found in their entirety in the Appendix.\footnote{This {\bf first survey} was split into two separate Google forms, one for
+university teachers and another for teachers in tertiary education institutions outside the university system (vocational training, including 1- and 2-year degrees). The questions and
 responses were the same, except for the type of tertiary degrees that
-were considered.}
-
-This survey was piloted by the authors of the paper and their colleagues before using it in the
-study.  All the comments collected from this trial were incorporated in the survey.
-We primarily used mailing lists and Telegram groups to disseminate the survey link so that it would reach a larger number of educators. The form addressed at university teachers was sent to Spanish
-(mainly Andaluc\'{\i}a and Galicia) universities, and also  universities in Costa Rica and
-Mexico. The tertiary (non-university/college) teachers who received the form were based mainly in
-Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of
-2021, during the Covid-19 pandemic and while, at least in Spain, many universities had
+were considered.} This survey was piloted by the authors of this paper and their colleagues before using it in the
+study, and all feedback from this trial was incorporated into the survey.
+The survey link was primarily distributed via mailing lists and Telegram groups in order to reach a larger number of educators. The form targeting university teachers was sent to university in Spain
+(mainly in Andaluc\'{\i}a and Galicia), and also universities in Costa Rica and
+Mexico. Tertiary (non-university/college) educators who received the form were mainly based in
+Andaluc\'{\i}a. The survey was disseminated and responses were collected in the first quarter of
+2021, during the Covid-19 pandemic, while at least in Spain, many universities were implementing
 mandatory virtual teaching.
 
-A total of 282 teachers responded to the survey: 193 teaching at the University
+A total of 282 educators responded to the survey: 193 teaching at the University
 (68.4\%) and 89 at other tertiary education institutions (31.6\%).
-From those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%) and 5 teachers preferred not to indicate their gender (1.8\%).
-In terms of age, the majority of the participants (n=111) in this survey was 45-55 years old (39.4\%), while 91 teachers were 35-45 (32.3\%), 46 were 25-35 (16.3\%) and 34 teachers were older than 55 (12.1\%).
-Last, 84 teachers had a teaching experience of 16-25 years (29.8\%), 75 teachers 6-15 years of experience (26.6\%), 69 teachers had 0-5 years of experience (24.5\%) and finally, 54 teachers had more than 25 years of teaching experience (19.1\%).
-
-Responses were stored automatically in a Google Drive spreadsheet. Eventually,
-the results from the two forms we used for the first survey were collated in a
-single spreadsheet. Survey questions are shown in Appendix I (Section \ref{app:questions}).
-
-The {\bf second survey} was designed after initial results to the first survey arrived,
-and pointed to necessities and experiences of teachers not being addressed by the first one; namely
-their experience with messaging platforms and the way they were used to interact with students.
-It was piloted in a group of university teachers attending to a formation course, and validated with them.
-It was then extended to the rest of the responders, using the same media: Telegram groups, email and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
+Of those, 179 indicated their gender as male (63.5\%), 98 as female (34.8\%), and 5 teachers preferred not to indicate their gender (1.8\%).
+In terms of age, the majority of participants (n=111) in this survey were 45-55 years old (39.4\%), while 91 educators were 35-45 (32.3\%), 46 were 25-35 (16.3\%), and 34 were older than 55 (12.1\%).
+Lastly, 84 educators had a teaching experience of 16-25 years (29.8\%), 75 educators had 6-15 years of experience (26.6\%), 69 educators had 0-5 years of experience (24.5\%), and finally, 54 educators had more than 25 years of teaching experience (19.1\%).
+
+Responses were automatically stored in a Google Drive spreadsheet. Eventually,
+the results from the two forms used for the first survey were collated in a
+single spreadsheet. Survey questions can be found in Appendix I (Section \ref{app:questions}).
+
+The {\bf second survey} was designed after initial results for the first survey arrived,
+and pointed out necessities and experiences of educators not covered by the first survey, specifically
+their experience with messaging platforms and the ways they were used to interact with students.
+It was piloted with a group of university teaching staff attending a training course, and validated by them.
+The survey was then extended to the rest of responders, using the same media: Telegram groups, email, and announcements in mailing lists.
+The questions asked in this survey can also be found in Appendix I
 (Section \ref{app:questions}).
 
-A total of 205 teachers responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%).
-From those, 124 were male (60.5\%), 65 female (31.7\%) and 16 teachers preferred not to indicate their gender (7.8\%).
-In terms of age, the majority of the participants (n=70) was again, as in the first survey, 45-55 years old (34.1\%), while 67 teachers were 35-45 years old (32.7\%), 42 were 25-35 (20.5\%) and 26 teachers were older than 55 (12.7\%).
-In terms of teaching experience, 59 teachers had a teaching experience of 16-25 years (28.8\%), 51 teachers had 6-15 years (24.9\%) and 0-5 years of experience (24.9\%), and 44 teachers more than 25 years of teaching experience (21.5\%).
+A total of 205 educators responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%).
+Of those, 124 were male (60.5\%), 65 female (31.7\%), and 16 participants preferred not to indicate their gender (7.8\%).
+In terms of age, the majority of the participants (n=70) were again, as in the first survey, 45-55 years old (34.1\%), while 67 participants were 35-45 years old (32.7\%), 42 were 25-35 (20.5\%), and 26 participants were older than 55 (12.7\%).
+In terms of teaching experience, 59 participants had a teaching experience of 16-25 years (28.8\%), 51 participants had 6-15 years (24.9\%), 51 had 0-5 years of experience (24.9\%), and 44 participants had more than 25 years of teaching experience (21.5\%).
 
@@
 
-To avoid any kind of bias and to ensure the quality of the questionnaire, a panel board was consulted.
-There were three questions for each of the items of the questionnaire which were: Clarity, Importance, Adequateness.
-Clarity was measured as an answer to the question: Is the item well presented and without ambiguity?
-\footnote{Original text: ¿El ítem está bien redactado y sin ambigüedad?} with two choices: Yes or No.
-Both Importance and Adequateness were measured in a Likert scale from 1 to 4 (1 low, 4 high).
-
-The panel board was composed by 7 volunteer experts that have wide experience as educators and researchers. The results obtained are summarized in Table \ref{tab:validation}.
-
-As validation shows, all expert agree without any doubt about the clarity of each question.
-Furthermore, there is a large consensus regarding the Importance and Adequateness of all the eight questions in the questionnaire.
+To avoid any kind of bias and to ensure the quality of the questionnaire, a panel of experts was consulted.
+The panel board evaluated three aspects for each item of the questionnaire: Clarity, Importance, and Adequateness.
+Clarity was measured as an answer to the question: ``Is the item well presented and without ambiguity?'' \footnote{Original text in Spanish: ¿El ítem está bien redactado y sin ambigüedad?} with two choices: ``Yes'' or ``No''.
+Both Importance and Adequateness were measured on a Likert scale from 1 to 4 (1 being low and 4 being high).
+
+The panel board was composed of 7 volunteer experts that have wide experience as educators and researchers. The results obtained are summarized in Table \ref{tab:validation}.
+
+As validation shows, all experts agree without any doubt about the clarity of each question.
+Furthermore, there is a large consensus regarding the Importance and Adequateness of all eight questions in the questionnaire.
 
@@
 
-Furthermore, a chi-square test of independence was performed in order to examine the relation between instructors’ discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the COVID-19 pandemic.
-The relation between the latter variable and the instructors’ sector was significant, $X^{2}_{(4, N = 282)} = 9.598$, $p =0.048$.
-Table \ref{tab:sector*covid} shows the frequencies that are cross-tabulated vs.
-changes undertaken after the COVID pandemic.
-This finding suggests that how teachers used messaging apps during the pandemic, specifically whether they changed their habits for teaching purposes, was related to the sector (university vs vocational) in which they were working.
+Furthermore, a chi-square test of independence was performed in order to examine the relationship between instructors' discipline, sector, and gender and any potential changes that occurred to the use of messaging apps due to the COVID-19 pandemic.
+The relationship between the latter variable and the instructors' sector was significant, $X^{2}_{(4, N = 282)} = 9.598$, $p =0.048$.
+Table \ref{tab:sector*covid} shows the frequencies that are cross-tabulated versus changes undertaken after the COVID-19 pandemic.
+This finding suggests that how teachers used messaging apps during the pandemic, specifically whether they changed their habits for teaching purposes, was related to the sector (university vs.
+vocational) in which they were working.
 %
@@
 
-The majority of the teachers (n=165) mentioned that no changes in their habits occurred due to the emergency remote teaching, as the use of messaging apps was part of their teaching practices and remains the same, from which 105 teachers come from the university, and 60 teachers from the non-universitary tertiary sector.
-The relationships between changes in the use of messaging apps, due to the covid-19 pandemic, and the instructors’ discipline, $X^{2}_{(24, N = 282)} = 44.856$, $p =0.006$, as well as the gender, $X^{2}_{(8, N = 282)} = 16.249$, p= 0.039 were also significant.
+The majority of the teachers (n=165) mentioned that no changes in their habits occurred due to the shift to remote teaching due to the lock-down measures taken in their countries, as the use of messaging apps was part of their teaching practices and remained the same.
+Out of those 165 responders, 105 teachers come from the university and 60 teachers from the non-universitary tertiary sector.
+The relationships between changes in the use of messaging apps, due to the COVID-19 pandemic, and the instructors' discipline, $X^{2}_{(24, N = 282)} = 44.856$, $p =0.006$, as well as the gender, $X^{2}_{(8, N = 282)} = 16.249$, p= 0.039 were also significant.
 This finding indicates that how teachers responded to the use of messaging apps during the pandemic was also related to their gender and discipline.
-In fact, from the majority of the teachers who did not change their habits in this respect (n=165), most of them are males (n=114), and come from the technology (n=60) and engineering (n=53) disciplines (see Tables \ref{tab:gender*covid}, \ref{tab:discipline*covid}).
+In fact, from the majority of the teachers who did not change their habits in this respect (n=165), most of them are males (n=114) and come from the technology (n=60) and engineering (n=53) disciplines (see Tables \ref{tab:gender*covid}, \ref{tab:discipline*covid}).
 %
@@
 
-As mentioned, the graphs on the left hand side represent the Pearson's
+As mentioned, the graphs on the left-hand side represent the Pearson's
 residuals, showing the difference between the observed and the expected values
 for each cell. Thus, large residuals indicate that variables are not truly
-independent. In our case, the blue shows positive contributions and red negative
-contributions to the test. Moreover, the saturation shows how large the
-contribution is in contrast to the expected value by chance. Additionally,
-tables on the right side show adjusted standardized residuals that according to
+independent. In our case, blue shows positive contributions and red negative
+contributions to the test. Additionally, the saturation shows how large the
+contribution is in contrast to the expected value by chance. 
+Tables show on the right hand side adjusted standardized residuals that according to
 \cite{agresti2013categorical}, if greater than +/-2 for cases with few cells,
-indicate lack of fit of $H_0$ (in boldface in our table). Complementary, the
+indicate lack of fit of $H_0$ (in boldface in our table). Complementarily, the
 table also shows the percentage of contribution to the test of each cell
-(highest percentage per column also in boldface).
+(the highest percentage per column also in boldface).
 
@@
 \end{center}
-    \caption{Analysis for discipline and post-covid changes: left) Pearson's residuals for the Chi-square test; right) Discipline*post-covid changes crosstabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized residuals) and contribution percentage to the total Chi-square test of each cell.}
+    \caption{Analysis for discipline and post-COVID-19 changes: left) Pearson's residuals for the Chi-square test; right) Discipline*post-COVID-19 changes cross-tabulation, including standardized residuals \cite{agresti2013categorical} (also adjusted standardized residuals) and contribution percentage to the total Chi-square test of each cell.}
 \label{figure:discipline*postcovid_chisq}
@@
 
-%\subsection{RQ4 - What kind of interaction media features do teachers value the most?}
+%\subsection{RQ4 - Which kind of interaction media features do teachers value the most?}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
-The majority of the teachers were aged 45-55 years old (70; 34.1\%), followed by individuals aged 35-45 (67, 32.7\%), and 25-35 (42; 20.5\%), while the minority was aged >55 years old (26; 12.7\%).
-In terms of teaching experience, 59 teachers (28.8\%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9\%), 0-5 years (51; 24.9\%) and more than 25 years of experience (44; 21.5\%).
-The teachers were asked about what kind of interaction media features they value the most; the frequencies and percentages of their responses are given in the table that follows.
 
@@
 
-\subsection{RQ4 - What kind of interaction media features do teachers value the most? }
+\subsection{RQ4 - Which kind of interaction media features do teachers value the most? }
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%A total of 205 teachers responded to the second survey, 124 males (60.5\%), 65 females (31.7\%) and 16 individuals who chose not to identify their gender (7.8\%).
-The majority of the teachers were aged 45-55 years old (70; 34.1\%), followed by individuals aged 35-45 (67, 32.7\%), and 25-35 (42; 20.5\%), while the minority was aged $>$~55 years old (26; 12.7\%).
-In terms of teaching experience, 59 teachers (28.8\%) had an experience of 16-25 years, followed by teachers who had a teaching experience of 06-15 years (51; 24.9\%), 0-5 years (51; 24.9\%) and more than 25 years of experience (44; 21.5\%).
-The teachers were asked about what kind of interaction media features they value the most \textcolor{black}{; i.e.
-what their preferred features are in the applications/tools that they use to interact with their students.} The frequencies and percentages of their responses are given in Table \ref{tab:interaction}.
 

### 2023-01-10 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

@@
 
+% Only some COVID-response relationship.
 In our survey, we could not find an answer about the right moment to introducing chatbot technologies. The response to questions regarding to change of

### 2023-01-10 edubots_surveys.Rnw
Eliminates :coffin: comments
closes #50

--- 2023-01-10 edubots_surveys.Rnw
@@
 
-% The Use of Mobile Instant Messaging (MIM) Platforms in Higher Education
-The widespread and rapid adoption of free Mobile Instant Messaging (MIM)
-tools/platforms such as WhatsApp, Telegram, WeChat and Facebook Messenger stems
-from their simplicity, ease of use and multi-modality (i.e. video, audio, text)
-\cite{tang2017mobile}. Using these tools in higher education institutions
-facilitates the delivery of personalized learning that occurs anytime anywhere,
-and promotes collaborative learning experiences and group discussions
-\cite{panah2020study}.
-
-WhatsApp is, at least in most Western countries, the most popular MIM
-platform. The reason is that it is the tool preferably used by educators to
-provide assignments' feedback to students, support course discussions, and post
-learning resources in a semi-formal learning context \cite{panah2020study}.
-Moreover, the use of WhatsApp in higher education could enhance social presence
-\cite{tang2017mobile} and foster trust relationships between educators and
-students embedded in the social learning process
+The widespread and rapid adoption of free Mobile Instant Messaging
+(MIM) tools/platforms such as WhatsApp, Telegram, WeChat and Facebook
+Messenger stems from their simplicity, ease of use and multi-modality
+(i.e. video, audio, text) \cite{tang2017mobile}. Using these tools in
+higher education institutions facilitates the delivery of personalized learning
+that occurs anytime anywhere, and promotes collaborative learning
+experiences and group discussions \cite{panah2020study}.
+
+WhatsApp is, at least in most Western countries, the most popular MIM platform. The reason is that it is the tool preferably
+used by educators to provide assignments' feedback to students, support course
+discussions, and post learning resources in a semi-formal learning context
+\cite{panah2020study}.  Moreover, the use of WhatsApp in higher education could
+enhance social presence \cite{tang2017mobile} and foster trust relationships
+between educators and students embedded in the social learning process
 \cite{gachago2015crossing}. However, this last paper also reflects the need for
@@
 in general. At the same time, it also mentions different challenges, among which
-the most important is the blurring of social and academic life; indeed, there
-are challenges when using MIM tools that occur due to the blurring of boundaries
-between academic and private life. This can lead to technostress
-\cite{gachago2015crossing}, difficulty in managing responsibilities, especially
-among mature students, and lack of privacy \cite{tang2017mobile}.  Students'
-dropout of the MIM groups, as they can leave groups at any time, can hinder
-their learning and undermine educators' efforts \cite{mwakapina2016whatsapp}.
-In addition, there is a need to set rules and norms for these MIM groups in
-order to maintain the safety of these online communities for students
-\cite{abbas2021onlinechat}. However, these rules should not affect students'
-ownership and control, since it is vital to advance in their learning
-\cite{gachago2015crossing} process.  This is why examining the role of MIM
-platforms in higher education, as well as applications based on them such as
-chatbots, is still a challenge, and why the opinions of the teaching community
-towards them have to be examined, as we do in this paper.
+the most important is the blurring of social and academic life; indeed, there are challenges when using MIM tools that occur due to the
+blurring of boundaries between academic and private life. This can lead to
+technostress \cite{gachago2015crossing}, difficulty in managing
+responsibilities, especially among mature students, and lack of privacy
+\cite{tang2017mobile}.  Students' dropout of the MIM groups, as they can leave
+groups at any time, can hinder their learning and undermine educators' efforts
+\cite{mwakapina2016whatsapp}.  In addition, there is a need to set rules and
+norms for these MIM groups in order to maintain the safety of these online
+communities for students \cite{abbas2021onlinechat}. However, these rules should
+not affect students' ownership and control, since it is vital to advance in
+their learning \cite{gachago2015crossing} process.  This is why examining the
+role of MIM platforms in higher education, as well as applications based on them such as chatbots, is still a challenge, and why the opinions of
+the teaching community towards them have to be examined, as we do in this paper.
 
 % The Use of Chatbots in Higher Education
-The use of MIM platforms, although possibly valuable by itself, can be enhanced
-with the use of chatbots, which are conversational agents that normally dwell in
-synchronous conversations systems. The use of chatbots in higher education is
-still in its early stages \cite{yang2019opportunities}. Nevertheless, recent
-studies have shown their positive impact on students' academic performance
-\cite{perez2020rediscovering} and engagement
-\cite{differ.chat,abbas2021onlinechat}, leading to a growing interest in using
-this technology in the (possibly virtual) classroom. Indeed, using chatbots to
-collect course feedback from students in higher education improved the quality
-of responses given by students in their assignments, and boosted engagement
-levels \cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
-mobile devices along with gamification strategies \cite{Yildirim2017} can
-improve student motivation. In this sense, the authors in \cite{Pimmer2019}
-adopted a quasi-experimental, survey-based approach to report the positive
-impact of using instant messaging tools in boosting students' knowledge and
-mitigating their feelings of isolation.
-
-Multiple studies have been conducted to assess the effectiveness of chatbots in
-higher education; among them, a comprehensive paper was presented by Smutny and
-Schreiberova \cite{Smutny2020} reviewing 47 educational chatbots implemented in
-Facebook Messenger, concluding that most of these chatbots were very basic and
-that programmers require of more support to develop and offer tools for
-improving coaching methods and student learning outcomes. Pérez and
-collaborators \cite{perez2020rediscovering} attempted to categorize educational
-chatbots attending to their purpose as service-oriented or
-teaching-oriented. Service-oriented chatbots include those that provide service
-support, such as Ask Holly \cite{meetholly} and Dina \cite{santoso2018dinus},
-which respond to students' questions about enrollment and registration. Ask
-L. U.  \cite{LancasterUniversity_2019} answers students' frequently asked
-questions about schedules, grades, tutors, and societies. LISA
-\cite{dibitonto2018chatbot} and Differ \cite{differ.chat} facilitate breaking
-the ice between new students by introducing them to each other. Ranoliya et
-al. \cite{ranoliya2017chatbot} proposed a generic chatbot for university
-students that is able to answer frequently asked questions. The University of
-Granada deployed Elvira, a chatbot embedded in its main web page
-\cite{MOREO20129} to perform the same task. In addition to being able to answer
-pre-established frequent questions, it did so from the website of the University
-of Granada using an inset persona, voiced by a real person, who lip-synced the
-answers. However, in the case of Elvira, the emphasis was on the authenticity of
-the speech-mouth and face gestures synchronization rather than making updating
-answered questions simpler or more interactive for the administrative staff, or
-more open to the rest of the university staff using actual messaging
-platforms. In most cases, the embedded search engine was able to provide more
-up-to-date and accurate answers than those provided by Elvira, which had to be
-updated by hand (and not too often). It was eventually discontinued, and its
-technology was not adapted to other platforms, since it did not really provide a
-useful service. Its service was not tied to teaching anyway; it was more related
-to directory queries and university-wide administrative questions, so even if it
-is strictly an example of a chatbot in a university setting, it is not really a
-chatbot that can be adopted by teachers to affect the learning outcomes, which
-is the focus of this paper.
-
-Contrarily to the mentioned chatbots that are focused on administrative tasks,
-teaching-oriented chatbots are more sophisticated, as they set personalized
-learning outcomes and monitor learning progress. For instance,
+The use of MIM platforms, although possibly valuable by itself, can be enhanced with the
+use of chatbots, which are conversational agents that normally dwell in
+synchronous conversations systems. The use of chatbots in higher education is still in its early stages
+\cite{yang2019opportunities}. Nevertheless, recent studies have shown their
+positive impact on students' academic performance \cite{perez2020rediscovering}
+and engagement \cite{differ.chat,abbas2021onlinechat}, leading to a growing
+interest in using this technology in the (possibly virtual) classroom. Indeed,
+using chatbots to collect course feedback from students in higher
+education improved the quality of responses given by students in their assignments, and boosted engagement levels
+\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
+mobile devices along with gamification strategies
+\cite{Yildirim2017} can improve student motivation. In this sense, the authors
+in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
+report the positive impact of using instant messaging tools in boosting
+students' knowledge and mitigating their feelings of isolation.
+
+Several studies to evaluate chatbots in higher education have been conducted. For
+instance, a comprehensive study was presented by Smutny and Schreiberova
+\cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
+Messenger, concluding that most of these chatbots were very basic and that programmers require of more support to develop and 
+offer tools for improving coaching methods and students learning. Pérez and collaborators
+\cite{perez2020rediscovering} attempted to categorize educational chatbots attending to their purpose 
+as service-oriented or teaching-oriented. Service-oriented chatbots
+include those that provide service support, such as Ask Holly
+\cite{meetholly} and Dina \cite{santoso2018dinus}, which respond to
+students' questions about enrollment and registration. Ask L. U.
+\cite{LancasterUniversity_2019} answers students' frequently asked questions
+about schedules, grades, tutors, and societies. LISA \cite{dibitonto2018chatbot}
+and Differ \cite{differ.chat} facilitate breaking the ice between new students
+by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
+proposed a generic chatbot for university students that is able to answer 
+frequently asked questions. The University of Granada deployed
+Elvira, a chatbot embedded in its main web page \cite{MOREO20129} to perform the same task. In addition to being able
+to answer pre-established frequent questions, it did so from the website of
+the University of Granada using an inset persona, voiced by a real person, who
+lip-synced the answers. However, in the case of Elvira, the emphasis was on the
+authenticity of the speech-mouth and face gestures synchronization rather than making updating
+answered questions simpler or more interactive for the administrative staff, or more open to the rest of the university staff using actual messaging platforms. In
+most cases, the embedded search engine was able to provide more up-to-date
+and accurate answers than those provided by Elvira, which had to be updated
+by hand (and not too often).
+It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide a useful service.
+Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, which is the focus of this paper.
+
+Contrarily to the mentioned chatbots that are focused on administrative tasks, teaching-oriented chatbots are more sophisticated, as they
+set personalized learning outcomes and monitor learning progress. For instance,
 \cite{fernoagua2018intelligent} reported on ``eduAssistant'', a virtual teaching
 assistant chatbot developed on the Telegram messaging platform. In this study,
-the Telegram platform was chosen because it is easy to use, students are
-familiar with its features, and it enables them to exchange messages in
-different formats (text, audio and video) \cite{fernoagua2018intelligent}. In
-addition, Telegram can operate on all devices and operating systems. The
-``eduAssistant'' chatbot acts as an automatic agent in the
-teacher-content-student relationship, providing real-time feedback loops and a
-personalized learning experience relevant to the students' acquired skills and
-knowledge. Using this chatbot, educators can create interactive instances in
-their lectures where they pose questions to their students and the chatbot
-assists those who need further help by giving them more hints and reporting it
-to the educator's dashboard \cite{fernoagua2018intelligent}. This could help
-educators identify students who need more attention and provide them with more
-educational resources relevant to their academic
-achievement.
+the Telegram platform was chosen because it is easy to use, students are familiar
+with its features, and it enables them to exchange messages in different formats
+(text, audio and video) \cite{fernoagua2018intelligent}. In addition, Telegram
+can operate on all devices and operating systems. The ``eduAssistant'' chatbot
+acts as an automatic agent in the teacher-content-student relationship, providing real-time
+feedback loops and a personalized learning experience relevant to the
+students' acquired skills and knowledge. Using this chatbot, educators can
+create interactive instances in their lectures where they pose questions to
+their students and the chatbot assists those who need further help by giving
+them more hints and reporting it to the educator's dashboard
+\cite{fernoagua2018intelligent}. This could help educators identify
+students who need more attention and provide them with more educational resources
+relevant to their academic achievement. %In addition, a recent study
+%has analysed how the use of chatbots positively affected the learning outcomes
+%of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
 
 Despite its (arguably) successful implementation in different higher education
-institutions, particularly on the fringes of educational activity rather than
-actual student-teacher interaction, its implementation or deployment is not
-trivial.  Some authors, for instance \cite{sjostrom2018designing}, have proposed
-a conceptual architecture for the adoption of teaching-oriented chatbots in
-higher education.  This conceptual architecture is based on a systematic
-literature review of previous studies examining the design of chatbots in higher
+institutions, particularly on the fringes of educational activity rather than actual
+student-teacher interaction, its implementation or deployment is not trivial.
+Some authors, for instance \cite{sjostrom2018designing}, have proposed a
+conceptual architecture for the adoption of teaching-oriented chatbots in higher
+education.  This conceptual architecture is based on a systematic literature
+review of previous studies examining the design of chatbots in higher
 education, as well as making a content analysis of student emails and discussion
-forum posts from four instances of a Java programming course.  The study
-outlined several design considerations; among them, the authors emphasized the
-importance of developing chatbots in platforms that students and educators are
-familiar with and can easily access (i.e. Facebook Messenger), which was
-confirmed by \cite{hobert2019you} and \cite{fernoagua2018intelligent}. In
-addition, \cite{sjostrom2018designing} argued that conceptualizing learners'
-questions could help designers integrate the appropriate types of questions that
-chatbots should support for different courses. Other authors, such as
-\cite{coronado2018cognitive}, have proposed agents that record learning
-materials to be provided on demand to students, while
-\cite{crockett2017predicting} reported on tutoring systems that can perform
-initial assessments of students' understanding and provide learning materials to
-advance their understanding to the next level.
+forum posts from four instances of a Java programming course.  The study outlined
+several design considerations; among them, the authors emphasized the importance
+of developing chatbots in platforms that students and educators are familiar
+with and can easily access (i.e. Facebook Messenger), which was confirmed by
+\cite{hobert2019you} and \cite{fernoagua2018intelligent}. In addition, \cite{sjostrom2018designing} argued that 
+conceptualizing learners' questions could help designers integrate the
+appropriate types of questions that chatbots should support for different
+courses. Other authors, such as \cite{coronado2018cognitive}, have proposed agents that
+record learning materials to be provided on demand to students, while \cite{crockett2017predicting} 
+reported on tutoring systems that can
+perform initial assessments of students' understanding and provide learning
+materials to advance their understanding to the next level.
 
@@
 \cite{Roblyer2010,Pimmer2019}. However, higher education is a special domain
-where, according to \cite{hobert2019you}, specific pedagogical factors such as
-learning success and increased motivation are more important.  Therefore, to
-develop effective chatbots for higher education, the needs of all stakeholders
-(i.e. educators, students, institutions, etc) should be carefully collected and
-taken into consideration \cite{sjostrom2018designing,tsivitanidouusers}. These
-needs include, but are not limited to, student learning success due to higher
-motivation, but these are a posteriori effects that cannot be assessed in
-advance. Both authors focus on what teachers need in terms of the latter; this
-paper will focus on a wider perspective, trying to determine what they are
-looking for in terms of general messaging technology. The classical literature
-\cite{tam91} already proposes that any adoption of technology must be tuned to
-the user needs and experience. In this paper, we will try to find out what those
-are in order to propose a successful model of adoption of chatbot technology.
-
-In line with this research, our previous work \cite{MoraChatbots2021:anon} aimed
-at analyzing the expectations of students in this regard. Another paper have
-also analysed how the use of chatbots affected the learning outcomes of students
-in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper considered
-conversational chatbots in a one-to-one setting, finding that learning truly
-benefited from it. This is, once again, an evidence of the benefit of chatbots
-in certain settings; however, there are some prior experiences, as well as
-needs, that may prevent the successful acceptance of the technology, and these
-are what we are trying to find out in this paper, along with what kind of
-features would improve its acceptance.
+where, according to \cite{hobert2019you}, specific pedagogical factors
+such as learning success and increased motivation are more important.  Therefore,
+to develop effective chatbots for higher education, the needs of all stakeholders
+(i.e. educators, students, institutions, etc) should be carefully
+collected and taken into consideration
+\cite{sjostrom2018designing,tsivitanidouusers}.
+These needs include, but are not limited to, student learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance.
+Both authors focus on what teachers need in terms of the latter; this paper will focus on a wider perspective, trying to determine what they are looking for in terms of general messaging technology.
+The classical literature \cite{tam91} already proposes that any adoption of technology must be tuned to the user needs and experience.
+In this paper, we will try to find out what those are in order to propose a successful model of adoption of chatbot technology.
+
+In line with this research, our previous work \cite{MoraChatbots2021:anon}
+aimed at analyzing the expectations of students in this regard. Another paper
+have also analysed how the use of chatbots affected the learning outcomes of
+students in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper
+considered conversational chatbots in a one-to-one setting, finding that learning
+truly benefited from it. This is, once again, an evidence of the benefit of
+chatbots in certain settings; however, there are some prior experiences, as well as needs, that may
+prevent the successful acceptance of the technology, and these are what we are
+trying to find out in this paper, along with what kind of features would improve
+its acceptance.
 
 Besides, this work is focused on the other key actor in this challenge: 
-educators. How they accept chatbots has been studied very recently by Chocarro
-et al. \cite{doi:10.1080/03055698.2020.1850426}, who, by analyzing surveys,
-created a TAM that proposed a series of features that would make chatbots easier
-to accept, including formality of language as well as easiness and
-usefulness. The survey targeted primary and secondary education teachers and was
-also more interested in the general use of chatbots in education, not
-specifically in a classroom setting, seeking educational outcomes. However,
-their results are obviously interesting and relevant for this work.
-
-Next, we will describe the methodology we employed to gather teachers' perspectives.
+educators. How they accept chatbots has been studied very recently by Chocarro et
+al. \cite{doi:10.1080/03055698.2020.1850426}, who, by analyzing surveys, created
+a TAM that proposed a series of features that
+would make chatbots easier to accept, including formality of language as well
+as easiness and usefulness. The survey targeted primary and secondary education
+teachers and was also more interested in the general use of chatbots in
+education, not specifically in a classroom setting, seeking educational
+outcomes. However, their results are obviously
+interesting and relevant for this work.
+
+We will present next the methodology we followed to find out teachers' opinions.
 

### 2023-01-10 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

--- 2023-01-10 edubots_surveys.Rnw
@@
 This study employed a quantitative approach to address its research objectives.
-A significant amount of data was collected on the usage of messaging applications and chatbots by educators in universities and colleges.\footnote{In Spain, higher education institutions that would generally known as colleges in other places, are simply called high schools, and provide
+In order to fulfill them, we would need to collect a significant amount of data on the usage of messaging applications and chatbots by educators in universities and colleges.\footnote{In Spain, higher education institutions that would generally known as colleges in other places, are simply called high schools, and provide
 tertiary or associate degrees that do not have the same consideration as university degrees.}

### 2023-01-10 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

--- 2023-01-10 edubots_surveys.Rnw
@@
 tertiary or associate degrees that do not have the same consideration as university degrees.}
-To collect this data, two online surveys were designed and developed using Google Forms
+In order to collect this data, two online surveys were designed and developed using Google Forms
 in Spanish. These surveys consisted of six questions on demographic data

### 2023-01-10 edubots_surveys.Rnw

@@
 
-The widespread and rapid adoption of free Mobile Instant Messaging
-(MIM) tools/platforms such as WhatsApp, Telegram, WeChat and Facebook
-Messenger stems from their simplicity, ease of use and multi-modality
-(i.e. video, audio, text) \cite{tang2017mobile}. Using these tools in
-higher education institutions facilitates the delivery of personalized learning
-that occurs anytime anywhere, and promotes collaborative learning
-experiences and group discussions \cite{panah2020study}.
-
-WhatsApp is, at least in most Western countries, the most popular MIM platform. The reason is that it is the tool preferably
-used by educators to provide assignments' feedback to students, support course
-discussions, and post learning resources in a semi-formal learning context
-\cite{panah2020study}.  Moreover, the use of WhatsApp in higher education could
-enhance social presence \cite{tang2017mobile} and foster trust relationships
-between educators and students embedded in the social learning process
+The widespread and rapid adoption of free Mobile Instant Messaging (MIM)
+tools/platforms such as WhatsApp, Telegram, WeChat and Facebook Messenger stems
+from their simplicity, ease of use and multi-modality (i.e. video, audio, text)
+\cite{tang2017mobile}. Using these tools in higher education institutions
+facilitates the delivery of personalized learning that occurs anytime anywhere,
+and promotes collaborative learning experiences and group discussions
+\cite{panah2020study}.
+
+WhatsApp is, at least in most Western countries, the most popular MIM
+platform. The reason is that it is the tool preferably used by educators to
+provide assignments' feedback to students, support course discussions, and post
+learning resources in a semi-formal learning context \cite{panah2020study}.
+Moreover, the use of WhatsApp in higher education could enhance social presence
+\cite{tang2017mobile} and foster trust relationships between educators and
+students embedded in the social learning process
 \cite{gachago2015crossing}. However, this last paper also reflects the need for
@@
 in general. At the same time, it also mentions different challenges, among which
-the most important is the blurring of social and academic life; indeed, there are challenges when using MIM tools that occur due to the
-blurring of boundaries between academic and private life. This can lead to
-technostress \cite{gachago2015crossing}, difficulty in managing
-responsibilities, especially among mature students, and lack of privacy
-\cite{tang2017mobile}.  Students' dropout of the MIM groups, as they can leave
-groups at any time, can hinder their learning and undermine educators' efforts
-\cite{mwakapina2016whatsapp}.  In addition, there is a need to set rules and
-norms for these MIM groups in order to maintain the safety of these online
-communities for students \cite{abbas2021onlinechat}. However, these rules should
-not affect students' ownership and control, since it is vital to advance in
-their learning \cite{gachago2015crossing} process.  This is why examining the
-role of MIM platforms in higher education, as well as applications based on them such as chatbots, is still a challenge, and why the opinions of
-the teaching community towards them have to be examined, as we do in this paper.
+the most important is the blurring of social and academic life; indeed, there
+are challenges when using MIM tools that occur due to the blurring of boundaries
+between academic and private life. This can lead to technostress
+\cite{gachago2015crossing}, difficulty in managing responsibilities, especially
+among mature students, and lack of privacy \cite{tang2017mobile}.  Students'
+dropout of the MIM groups, as they can leave groups at any time, can hinder
+their learning and undermine educators' efforts \cite{mwakapina2016whatsapp}.
+In addition, there is a need to set rules and norms for these MIM groups in
+order to maintain the safety of these online communities for students
+\cite{abbas2021onlinechat}. However, these rules should not affect students'
+ownership and control, since it is vital to advance in their learning
+\cite{gachago2015crossing} process.  This is why examining the role of MIM
+platforms in higher education, as well as applications based on them such as
+chatbots, is still a challenge, and why the opinions of the teaching community
+towards them have to be examined, as we do in this paper.
 
 % The Use of Chatbots in Higher Education
-The use of MIM platforms, although possibly valuable by itself, can be enhanced with the
-use of chatbots, which are conversational agents that normally dwell in
-synchronous conversations systems. The use of chatbots in higher education is still in its early stages
-\cite{yang2019opportunities}. Nevertheless, recent studies have shown their
-positive impact on students' academic performance \cite{perez2020rediscovering}
-and engagement \cite{differ.chat,abbas2021onlinechat}, leading to a growing
-interest in using this technology in the (possibly virtual) classroom. Indeed,
-using chatbots to collect course feedback from students in higher
-education improved the quality of responses given by students in their assignments, and boosted engagement levels
-\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
-mobile devices along with gamification strategies
-\cite{Yildirim2017} can improve student motivation. In this sense, the authors
-in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
-report the positive impact of using instant messaging tools in boosting
-students' knowledge and mitigating their feelings of isolation.
-
-Several studies to evaluate chatbots in higher education have been conducted. For
-instance, a comprehensive study was presented by Smutny and Schreiberova
-\cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
-Messenger, concluding that most of these chatbots were very basic and that programmers require of more support to develop and 
-offer tools for improving coaching methods and students learning. Pérez and collaborators
-\cite{perez2020rediscovering} attempted to categorize educational chatbots attending to their purpose 
-as service-oriented or teaching-oriented. Service-oriented chatbots
-include those that provide service support, such as Ask Holly
-\cite{meetholly} and Dina \cite{santoso2018dinus}, which respond to
-students' questions about enrollment and registration. Ask L. U.
-\cite{LancasterUniversity_2019} answers students' frequently asked questions
-about schedules, grades, tutors, and societies. LISA \cite{dibitonto2018chatbot}
-and Differ \cite{differ.chat} facilitate breaking the ice between new students
-by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
-proposed a generic chatbot for university students that is able to answer 
-frequently asked questions. The University of Granada deployed
-Elvira, a chatbot embedded in its main web page \cite{MOREO20129} to perform the same task. In addition to being able
-to answer pre-established frequent questions, it did so from the website of
-the University of Granada using an inset persona, voiced by a real person, who
-lip-synced the answers. However, in the case of Elvira, the emphasis was on the
-authenticity of the speech-mouth and face gestures synchronization rather than making updating
-answered questions simpler or more interactive for the administrative staff, or more open to the rest of the university staff using actual messaging platforms. In
-most cases, the embedded search engine was able to provide more up-to-date
-and accurate answers than those provided by Elvira, which had to be updated
-by hand (and not too often).
-It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide a useful service.
-Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, which is the focus of this paper.
-
-Contrarily to the mentioned chatbots that are focused on administrative tasks, teaching-oriented chatbots are more sophisticated, as they
-set personalized learning outcomes and monitor learning progress. For instance,
+The use of MIM platforms, although possibly valuable by itself, can be enhanced
+with the use of chatbots, which are conversational agents that normally dwell in
+synchronous conversations systems. The use of chatbots in higher education is
+still in its early stages \cite{yang2019opportunities}. Nevertheless, recent
+studies have shown their positive impact on students' academic performance
+\cite{perez2020rediscovering} and engagement
+\cite{differ.chat,abbas2021onlinechat}, leading to a growing interest in using
+this technology in the (possibly virtual) classroom. Indeed, using chatbots to
+collect course feedback from students in higher education improved the quality
+of responses given by students in their assignments, and boosted engagement
+levels \cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
+mobile devices along with gamification strategies \cite{Yildirim2017} can
+improve student motivation. In this sense, the authors in \cite{Pimmer2019}
+adopted a quasi-experimental, survey-based approach to report the positive
+impact of using instant messaging tools in boosting students' knowledge and
+mitigating their feelings of isolation.
+
+Multiple studies have been conducted to assess the effectiveness of chatbots in
+higher education; among them, a comprehensive paper was presented by Smutny and
+Schreiberova \cite{Smutny2020} reviewing 47 educational chatbots implemented in
+Facebook Messenger, concluding that most of these chatbots were very basic and
+that programmers require of more support to develop and offer tools for
+improving coaching methods and student learning outcomes. Pérez and
+collaborators \cite{perez2020rediscovering} attempted to categorize educational
+chatbots attending to their purpose as service-oriented or
+teaching-oriented. Service-oriented chatbots include those that provide service
+support, such as Ask Holly \cite{meetholly} and Dina \cite{santoso2018dinus},
+which respond to students' questions about enrollment and registration. Ask
+L. U.  \cite{LancasterUniversity_2019} answers students' frequently asked
+questions about schedules, grades, tutors, and societies. LISA
+\cite{dibitonto2018chatbot} and Differ \cite{differ.chat} facilitate breaking
+the ice between new students by introducing them to each other. Ranoliya et
+al. \cite{ranoliya2017chatbot} proposed a generic chatbot for university
+students that is able to answer frequently asked questions. The University of
+Granada deployed Elvira, a chatbot embedded in its main web page
+\cite{MOREO20129} to perform the same task. In addition to being able to answer
+pre-established frequent questions, it did so from the website of the University
+of Granada using an inset persona, voiced by a real person, who lip-synced the
+answers. However, in the case of Elvira, the emphasis was on the authenticity of
+the speech-mouth and face gestures synchronization rather than making updating
+answered questions simpler or more interactive for the administrative staff, or
+more open to the rest of the university staff using actual messaging
+platforms. In most cases, the embedded search engine was able to provide more
+up-to-date and accurate answers than those provided by Elvira, which had to be
+updated by hand (and not too often). It was eventually discontinued, and its
+technology was not adapted to other platforms, since it did not really provide a
+useful service. Its service was not tied to teaching anyway; it was more related
+to directory queries and university-wide administrative questions, so even if it
+is strictly an example of a chatbot in a university setting, it is not really a
+chatbot that can be adopted by teachers to affect the learning outcomes, which
+is the focus of this paper.
+
+Contrarily to the mentioned chatbots that are focused on administrative tasks,
+teaching-oriented chatbots are more sophisticated, as they set personalized
+learning outcomes and monitor learning progress. For instance,
 \cite{fernoagua2018intelligent} reported on ``eduAssistant'', a virtual teaching
 assistant chatbot developed on the Telegram messaging platform. In this study,
-the Telegram platform was chosen because it is easy to use, students are familiar
-with its features, and it enables them to exchange messages in different formats
-(text, audio and video) \cite{fernoagua2018intelligent}. In addition, Telegram
-can operate on all devices and operating systems. The ``eduAssistant'' chatbot
-acts as an automatic agent in the teacher-content-student relationship, providing real-time
-feedback loops and a personalized learning experience relevant to the
-students' acquired skills and knowledge. Using this chatbot, educators can
-create interactive instances in their lectures where they pose questions to
-their students and the chatbot assists those who need further help by giving
-them more hints and reporting it to the educator's dashboard
-\cite{fernoagua2018intelligent}. This could help educators identify
-students who need more attention and provide them with more educational resources
-relevant to their academic achievement. %In addition, a recent study
-%has analysed how the use of chatbots positively affected the learning outcomes
-%of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
+the Telegram platform was chosen because it is easy to use, students are
+familiar with its features, and it enables them to exchange messages in
+different formats (text, audio and video) \cite{fernoagua2018intelligent}. In
+addition, Telegram can operate on all devices and operating systems. The
+``eduAssistant'' chatbot acts as an automatic agent in the
+teacher-content-student relationship, providing real-time feedback loops and a
+personalized learning experience relevant to the students' acquired skills and
+knowledge. Using this chatbot, educators can create interactive instances in
+their lectures where they pose questions to their students and the chatbot
+assists those who need further help by giving them more hints and reporting it
+to the educator's dashboard \cite{fernoagua2018intelligent}. This could help
+educators identify students who need more attention and provide them with more
+educational resources relevant to their academic
+achievement.
 
 Despite its (arguably) successful implementation in different higher education
-institutions, particularly on the fringes of educational activity rather than actual
-student-teacher interaction, its implementation or deployment is not trivial.
-Some authors, for instance \cite{sjostrom2018designing}, have proposed a
-conceptual architecture for the adoption of teaching-oriented chatbots in higher
-education.  This conceptual architecture is based on a systematic literature
-review of previous studies examining the design of chatbots in higher
+institutions, particularly on the fringes of educational activity rather than
+actual student-teacher interaction, its implementation or deployment is not
+trivial.  Some authors, for instance \cite{sjostrom2018designing}, have proposed
+a conceptual architecture for the adoption of teaching-oriented chatbots in
+higher education.  This conceptual architecture is based on a systematic
+literature review of previous studies examining the design of chatbots in higher
 education, as well as making a content analysis of student emails and discussion
-forum posts from four instances of a Java programming course.  The study outlined
-several design considerations; among them, the authors emphasized the importance
-of developing chatbots in platforms that students and educators are familiar
-with and can easily access (i.e. Facebook Messenger), which was confirmed by
-\cite{hobert2019you} and \cite{fernoagua2018intelligent}. In addition, \cite{sjostrom2018designing} argued that 
-conceptualizing learners' questions could help designers integrate the
-appropriate types of questions that chatbots should support for different
-courses. Other authors, such as \cite{coronado2018cognitive}, have proposed agents that
-record learning materials to be provided on demand to students, while \cite{crockett2017predicting} 
-reported on tutoring systems that can
-perform initial assessments of students' understanding and provide learning
-materials to advance their understanding to the next level.
+forum posts from four instances of a Java programming course.  The study
+outlined several design considerations; among them, the authors emphasized the
+importance of developing chatbots in platforms that students and educators are
+familiar with and can easily access (i.e. Facebook Messenger), which was
+confirmed by \cite{hobert2019you} and \cite{fernoagua2018intelligent}. In
+addition, \cite{sjostrom2018designing} argued that conceptualizing learners'
+questions could help designers integrate the appropriate types of questions that
+chatbots should support for different courses. Other authors, such as
+\cite{coronado2018cognitive}, have proposed agents that record learning
+materials to be provided on demand to students, while
+\cite{crockett2017predicting} reported on tutoring systems that can perform
+initial assessments of students' understanding and provide learning materials to
+advance their understanding to the next level.
 

### 2023-01-10 edubots_surveys.Rnw
reflow
:recycle: with better grammar

--- 2023-01-10 edubots_surveys.Rnw
@@
 
-% Describe the survey and population
 We collected responses from 282 teachers from Spain and Spanish-speaking
 countries for \textit{survey1} and 205 for \textit{survey2}. The two forms were
-open for approximately the same amount of time, around two months. The sample
-includes mostly university teachers, although about 32\% and 8\% are from
-non-universitary tertiary education in the first and second survey respectively. Regarding
+open for approximately the same amount of time, around two months. Most responders were university teachers, although about 32\% of them in \textit{survey1} and 8\% (in \textit{survey2} are from
+non-universitary tertiary education teachers. With respect to
 gender, 61\% of teachers were male and 32\% female, while approximately 5\%
-chose not to disclose it. Finally, the responses are more or less equally
-distributed according to the teaching experience, showing 24\% of responses from
+chose not to disclose their gender. Finally, the responses are more or less equally
+distributed according to the teacher's years of experience, showing 24\% of responses from
 teachers with 5 or less years of experience, 26\% for 6-15 years of experience,

### 2023-01-10 edubots_surveys.Rnw
:recycle: with better grammar

@@
 test results are explained by this cell. In contrast, male educators that
-responded the same were less than expected (negative contribution that explains
+responded in the same way were less than expected (negative contribution that explains
 17\% of the test results). Also, it is important to highlight the female
@@
 % AMM has revised the paper and researched the state of the art, as well as contributed to the survey design.
-% FB has made the analysis and processed data and contributed to the survey design.
+% FB has been involved in the survey design process, conducted the data analysis, processed the data, and reviewed the written content of the paper. 
 % NA has supervised the writing  of the section devoted to the state of the art and written the bulk of it, as well as contributed to discussion and conclusions.
@@
 
-The surveys have the same common initial demographic questions:\begin{itemize}
-\item Degrees or titles where the teacher was working, either university or other tertiary education.
-\item Discipline: Engineering, Social Sciences, Health and Bio, General Sciences, Humanities, Other.
+The surveys have the same common initial demographic questions:
+\begin{itemize}
+\item Degrees or titles for which the educator was teaching, either from a university or other tertiary education institution.
+\item Discipline: Engineering, Social Sciences, Health and Bioscience, General Sciences, Humanities, Other.
 \item Gender: Man, Woman, Rather not say.
@@
 \item Experience on the job: up to 5 years, 5-15 years, 15-25 years, more than 25 years.
-\textcolor{black}{
 \item Type of degree: university, other tertiary education.
-This question was implicit in the first survey: there were two different versions of the survey.
-However, it was an explicit question in the second survey.}
+This question was implicit in the first survey, as there were two different versions of the survey.
+However, it was an explicit question in the second survey.
 \end{itemize}
@@
 % Including questions in surveys
-The {\bf first survey}, shown in its original form in Figure \ref{figure:survey1}, which \textcolor{black}{focused on} the use of messaging apps in class, includes the following questions:
+The {\bf first survey}, shown in its original form in Figure \ref{figure:survey1}, which focused on the use of messaging apps in class, and that was used for addressing RQ1, RQ2, and RQ3, includes the following questions:
 
@@
 \item A chat group with the students in the same course
-\item Students self-organize and with the teacher not being part of any chat group
-\textcolor{black}{
+\item Students self-organize and the teacher is not part of any chat group
 \item A chat group with all the students and teachers of the School/High-School/Faculty
-}
 \item A chat group with all the students and teachers of the same study year
@@
 
-\textit{3. Which kind of chatbots (software that automatically respond to questions or commands) could be useful to improve the learning results with your students or help you managing your course?}
+\textit{3. Which kind of chatbots (software that automatically responds to questions or commands) could be useful to improve your students' learning results or help you managing your course?}
 \begin{itemize}
-\item Agenda bots that e.g. remind students about project deadlines
-\item Bots that collect and provide answers to frequent questions
+\item Agenda bots that e.g. remind students project deadlines
+\item Bots that collect and provide answers to frequent asked questions
 \item Bots that inform students about their grades
@@
 
-\textit{4. The virtualization of teaching due to the COVID pandemic during this year and the previous one, did it mean any change in your viewpoint or use of messaging apps in class?}
+\textit{4. Regarding the virtualization of teaching due to the COVID-19 pandemic during this year and the previous one, did it mean any change in your viewpoint or use of messaging apps in class?}
 \begin{itemize}
@@
 \item Yes, I did not use any messaging platform before but I do use it now
-\item No, I did not use any messaging platform before or now
+\item No, I have not used any messaging platform before or currently
 \end{itemize}
@@
 interaction media features that teachers value the most.  It was filled by
-teachers that were also students in a Professional Development course (on the
+teachers that were also students in a Professional Training Course (on the
 use of new technologies in higher education, around 1/4 of them) as well as
@@
 with few years of experience 2) teachers from the computer science faculty and
-3) teachers from Granada. We think, however that there's no explicit bias in
+3) teachers from Granada. We think, however that there is no explicit bias in
 this selection, although of course specific percentages will vary.
@@
 Specifically, this survey asked the teachers, in addition to general information
-(such as gender, age, experience, etc), what are their \textcolor{black}{past
-  experiences and needs} with regard to the use of instant messaging
+(such as gender, age, experience, etc), what their past
+  experiences and needs are with regard to the use of instant messaging
 applications with students, and even using bots or chatbots in the classroom. In
-addition the survey asked about the most relevant \textit{interaction media
-  features} for the teachers with respect to the potential tool to use in class.
+addition, the survey asked teachers about the most relevant \textit{interaction media
+  features} of the potential tool to be used in class.
 
@@
 \begin{itemize}
-\item Familiarity with its use i.e. that I do not need to learn a new tool. [\texttt{Familiarity}]
-\item The official formation/training provided by your institution on its use. [\texttt{Official formation}]
+\item Familiarity with its use i.e. that you do not need to learn a new tool. [\texttt{Familiarity}]
+\item The official training provided by your institution on its use. [\texttt{Official formation}]
 \item That only one-directional communication is allowed (from teachers to students). [\texttt{Unidirectionality}]
@@
 \item Possibility for teachers to develop/add their own functionalities (e.g. automatic correction tools). [\texttt{Pluggability}]
-\item Possibility for users to hide personal data (such as my telephone number). [\texttt{Hidden Phone Number}]
-\item Not having to worry about maintenance and that it is easily sustainable from one year to the next. [\texttt{Sustainability}]
-\item That it offers the chance to extract data to assess the student performance. [\texttt{Analytics}]
+\item Possibility for users to hide personal data (such as your telephone number). [\texttt{Hidden Phone Number}]
+\item Not having to worry about maintenance and that it is easily sustainable from year to year. [\texttt{Sustainability}]
+\item That it offers the chance of extracting data to assess the student performance. [\texttt{Analytics}]
 \end{itemize}

### 2023-01-10 edubots_surveys.Rnw
Updating biblio
small edit previously approved but not commited

--- 2023-01-10 edubots_surveys.Rnw
@@
 
+% Describe the survey and population
 We collected responses from 282 teachers from Spain and Spanish-speaking
 countries for \textit{survey1} and 205 for \textit{survey2}. The two forms were
-open for approximately the same amount of time, around two months. Most responders were university teachers, although about 32\% of them in \textit{survey1} and 8\% (in \textit{survey2} are from
-non-universitary tertiary education teachers. With respect to
+open for approximately the same amount of time, around two months. The sample
+includes mostly university teachers, although about 32\% and 8\% are from
+non-universitary tertiary education in the first and second survey respectively. Regarding
 gender, 61\% of teachers were male and 32\% female, while approximately 5\%
-chose not to disclose their gender. Finally, the responses are more or less equally
-distributed according to the teacher's years of experience, showing 24\% of responses from
+chose not to disclose it. Finally, the responses are more or less equally
+distributed according to the teaching experience, showing 24\% of responses from
 teachers with 5 or less years of experience, 26\% for 6-15 years of experience,

### 2023-01-10 edubots_surveys.Rnw
Review appendix

--- 2023-01-10 edubots_surveys.Rnw
@@
 % AMM has revised the paper and researched the state of the art, as well as contributed to the survey design.
-% FB has been involved in the survey design process, conducted the data analysis, processed the data, and reviewed the written content of the paper. 
+% FB has contributed to the survey design, made the analysis, processed data, and reviewed the writing of the paper. 
 % NA has supervised the writing  of the section devoted to the state of the art and written the bulk of it, as well as contributed to discussion and conclusions.
@@
 
-\textit{4. Regarding the virtualization of teaching due to the COVID-19 pandemic during this year and the previous one, did it mean any change in your viewpoint or use of messaging apps in class?}
+\textit{4. Regardin the virtualization of teaching due to the COVID-19 pandemic during this year and the previous one, did it mean any change in your viewpoint or use of messaging apps in class?}
 \begin{itemize}

### 2023-01-10 edubots_surveys.Rnw
Convert to footnote to keep URL

--- 2023-01-10 edubots_surveys.Rnw
@@
 \cite{meetholly} and Dina \cite{santoso2018dinus}, which respond to
-students' questions about enrollment and registration. Ask L. U.
-\cite{LancasterUniversity_2019} answers students' frequently asked questions
+students' questions about enrollment and registration.
+Ask L.
+U.\footnote{"Lancaster University launch pioneering chatbot companion for students", {\tt https://www.lancaster.ac.uk/news/lancaster-university-launch-pioneering-chatbot-companion-for-students}.}
+answers students' frequently asked questions
 about schedules, grades, tutors, and societies. LISA \cite{dibitonto2018chatbot}
@@
 
-We will try to find the answers to the four research questions next, by
+We will try to assess whether we found the answers to the four research questions next, by
 analyzing the responses to the different survey questions.
@@
 test results are explained by this cell. In contrast, male educators that
-responded in the same way were less than expected (negative contribution that explains
+responded the same were less than expected (negative contribution that explains
 17\% of the test results). Also, it is important to highlight the female

### 2023-01-10 edubots_surveys.Rnw
Convert to footnote to keep URL

--- 2023-01-10 edubots_surveys.Rnw
@@
 % AMM has revised the paper and researched the state of the art, as well as contributed to the survey design.
-% FB has contributed to the survey design, made the analysis, processed data, and reviewed the writing of the paper. 
+% FB has been involved in the survey design process, conducted the data analysis, processed the data, and reviewed the written content of the paper. 
 % NA has supervised the writing  of the section devoted to the state of the art and written the bulk of it, as well as contributed to discussion and conclusions.
@@
 
-\textit{4. Regardin the virtualization of teaching due to the COVID-19 pandemic during this year and the previous one, did it mean any change in your viewpoint or use of messaging apps in class?}
+\textit{4. Regarding the virtualization of teaching due to the COVID-19 pandemic during this year and the previous one, did it mean any change in your viewpoint or use of messaging apps in class?}
 \begin{itemize}

### 2023-01-10 edubots_surveys.Rnw
:crossed_swords:

--- 2023-01-10 edubots_surveys.Rnw
@@
 in general. At the same time, it also mentions different challenges, among which
-the most important is the blurring of social and academic life; indeed, there are challenges when using MIM tools that occur due to the
-blurring of boundaries between academic and private life. This can lead to
-technostress \cite{gachago2015crossing}, difficulty in managing
-responsibilities, especially among mature students, and lack of privacy
-\cite{tang2017mobile}.  Students' dropout of the MIM groups, as they can leave
-groups at any time, can hinder their learning and undermine educators' efforts
-\cite{mwakapina2016whatsapp}.  In addition, there is a need to set rules and
-norms for these MIM groups in order to maintain the safety of these online
-communities for students \cite{abbas2021onlinechat}. However, these rules should
-not affect students' ownership and control, since it is vital to advance in
-their learning \cite{gachago2015crossing} process.  This is why examining the
-role of MIM platforms in higher education, as well as applications based on them such as chatbots, is still a challenge, and why the opinions of
-the teaching community towards them have to be examined, as we do in this paper.
-
-% The Use of Chatbots in Higher Education
-The use of MIM platforms, although possibly valuable by itself, can be enhanced with the
-use of chatbots, which are conversational agents that normally dwell in
-synchronous conversations systems. The use of chatbots in higher education is still in its early stages
-\cite{yang2019opportunities}. Nevertheless, recent studies have shown their
-positive impact on students' academic performance \cite{perez2020rediscovering}
-and engagement \cite{differ.chat,abbas2021onlinechat}, leading to a growing
-interest in using this technology in the (possibly virtual) classroom. Indeed,
-using chatbots to collect course feedback from students in higher
-education improved the quality of responses given by students in their assignments, and boosted engagement levels
-\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
-mobile devices along with gamification strategies
-\cite{Yildirim2017} can improve student motivation. In this sense, the authors
-in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
-report the positive impact of using instant messaging tools in boosting
-students' knowledge and mitigating their feelings of isolation.
-
-Several studies to evaluate chatbots in higher education have been conducted. For
-instance, a comprehensive study was presented by Smutny and Schreiberova
-\cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
-Messenger, concluding that most of these chatbots were very basic and that programmers require of more support to develop and 
-offer tools for improving coaching methods and students learning. Pérez and collaborators
-\cite{perez2020rediscovering} attempted to categorize educational chatbots attending to their purpose 
-as service-oriented or teaching-oriented. Service-oriented chatbots
-include those that provide service support, such as Ask Holly
-\cite{meetholly} and Dina \cite{santoso2018dinus}, which respond to
-students' questions about enrollment and registration.
-Ask L.
-U.\footnote{"Lancaster University launch pioneering chatbot companion for students", {\tt https://www.lancaster.ac.uk/news/lancaster-university-launch-pioneering-chatbot-companion-for-students}.}
-answers students' frequently asked questions
-about schedules, grades, tutors, and societies. LISA \cite{dibitonto2018chatbot}
-and Differ \cite{differ.chat} facilitate breaking the ice between new students
-by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
-proposed a generic chatbot for university students that is able to answer 
-frequently asked questions. The University of Granada deployed
-Elvira, a chatbot embedded in its main web page \cite{MOREO20129} to perform the same task. In addition to being able
-to answer pre-established frequent questions, it did so from the website of
-the University of Granada using an inset persona, voiced by a real person, who
-lip-synced the answers. However, in the case of Elvira, the emphasis was on the
-authenticity of the speech-mouth and face gestures synchronization rather than making updating
-answered questions simpler or more interactive for the administrative staff, or more open to the rest of the university staff using actual messaging platforms. In
-most cases, the embedded search engine was able to provide more up-to-date
-and accurate answers than those provided by Elvira, which had to be updated
-by hand (and not too often).
-It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide a useful service.
-Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, which is the focus of this paper.
-
-Contrarily to the mentioned chatbots that are focused on administrative tasks, teaching-oriented chatbots are more sophisticated, as they
-set personalized learning outcomes and monitor learning progress. For instance,
+the most important is the blurring of social and academic life; indeed, there
+are challenges when using MIM tools that occur due to the blurring of boundaries
+between academic and private life. This can lead to technostress
+\cite{gachago2015crossing}, difficulty in managing responsibilities, especially
+among mature students, and lack of privacy \cite{tang2017mobile}.  Students'
+dropout of the MIM groups, as they can leave groups at any time, can hinder
+their learning and undermine educators' efforts \cite{mwakapina2016whatsapp}.
+In addition, there is a need to set rules and norms for these MIM groups in
+order to maintain the safety of these online communities for students
+\cite{abbas2021onlinechat}. However, these rules should not affect students'
+ownership and control, since it is vital to advance in their learning
+\cite{gachago2015crossing} process.  This is why examining the role of MIM
+platforms in higher education, as well as applications based on them such as
+chatbots, is still a challenge, and why the opinions of the teaching community
+towards them have to be examined, as we do in this paper.
+
+The use of MIM platforms, although possibly valuable by itself, can be enhanced
+with the use of chatbots, which are conversational agents that normally dwell in
+synchronous conversations systems. The use of chatbots in higher education is
+still in its early stages \cite{yang2019opportunities}. Nevertheless, recent
+studies have shown their positive impact on students' academic performance
+\cite{perez2020rediscovering} and engagement
+\cite{differ.chat,abbas2021onlinechat}, leading to a growing interest in using
+this technology in the (possibly virtual) classroom. Indeed, using chatbots to
+collect course feedback from students in higher education improved the quality
+of responses given by students in their assignments, and boosted engagement
+levels \cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, the use of
+mobile devices along with gamification strategies \cite{Yildirim2017} can
+improve student motivation. In this sense, the authors in \cite{Pimmer2019}
+adopted a quasi-experimental, survey-based approach to report the positive
+impact of using instant messaging tools in boosting students' knowledge and
+mitigating their feelings of isolation.
+
+Multiple studies have been conducted to assess the effectiveness of chatbots in
+higher education; among them, a comprehensive paper was presented by Smutny and
+Schreiberova \cite{Smutny2020} reviewing 47 educational chatbots implemented in
+Facebook Messenger, concluding that most of these chatbots were very basic and
+that programmers require of more support to develop and offer tools for
+improving coaching methods and student learning outcomes. Pérez and
+collaborators \cite{perez2020rediscovering} attempted to categorize educational
+chatbots attending to their purpose as service-oriented or
+teaching-oriented. Service-oriented chatbots include those that provide service
+support, such as Ask Holly \cite{meetholly} and Dina \cite{santoso2018dinus},
+which respond to students' questions about enrollment and registration. Ask
+L. U.  \footnote{"Lancaster University launch pioneering chatbot companion for
+students", {\tt
+https://www.lancaster.ac.uk/news/lancaster-university-launch-pioneering-chatbot-companion-for-students}.}
+answers students' frequently asked questions about schedules, grades, tutors,
+and societies. LISA \cite{dibitonto2018chatbot} and Differ \cite{differ.chat}
+facilitate breaking the ice between new students by introducing them to each
+other. Ranoliya et al. \cite{ranoliya2017chatbot} proposed a generic chatbot for
+university students that is able to answer frequently asked questions. The
+University of Granada deployed Elvira, a chatbot embedded in its main web page
+\cite{MOREO20129} to perform the same task. In addition to being able to answer
+pre-established frequent questions, it did so from the website of the University
+of Granada using an inset persona, voiced by a real person, who lip-synced the
+answers. However, in the case of Elvira, the emphasis was on the authenticity of
+the speech-mouth and face gestures synchronization rather than making updating
+answered questions simpler or more interactive for the administrative staff, or
+more open to the rest of the university staff using actual messaging
+platforms. In most cases, the embedded search engine was able to provide more
+up-to-date and accurate answers than those provided by Elvira, which had to be
+updated by hand (and not too often). It was eventually discontinued, and its
+technology was not adapted to other platforms, since it did not really provide a
+useful service. Its service was not tied to teaching anyway; it was more related
+to directory queries and university-wide administrative questions, so even if it
+is strictly an example of a chatbot in a university setting, it is not really a
+chatbot that can be adopted by teachers to affect the learning outcomes, which
+is the focus of this paper.
+
+Contrarily to the mentioned chatbots that are focused on administrative tasks,
+teaching-oriented chatbots are more sophisticated, as they set personalized
+learning outcomes and monitor learning progress. For instance,
 \cite{fernoagua2018intelligent} reported on ``eduAssistant'', a virtual teaching
 assistant chatbot developed on the Telegram messaging platform. In this study,
-the Telegram platform was chosen because it is easy to use, students are familiar
-with its features, and it enables them to exchange messages in different formats
-(text, audio and video) \cite{fernoagua2018intelligent}. In addition, Telegram
-can operate on all devices and operating systems. The ``eduAssistant'' chatbot
-acts as an automatic agent in the teacher-content-student relationship, providing real-time
-feedback loops and a personalized learning experience relevant to the
-students' acquired skills and knowledge. Using this chatbot, educators can
-create interactive instances in their lectures where they pose questions to
-their students and the chatbot assists those who need further help by giving
-them more hints and reporting it to the educator's dashboard
-\cite{fernoagua2018intelligent}. This could help educators identify
-students who need more attention and provide them with more educational resources
-relevant to their academic achievement. %In addition, a recent study
-%has analysed how the use of chatbots positively affected the learning outcomes
-%of students in a Chinese class \cite{doi:10.1177/0735633120929622}.
+the Telegram platform was chosen because it is easy to use, students are
+familiar with its features, and it enables them to exchange messages in
+different formats (text, audio and video) \cite{fernoagua2018intelligent}. In
+addition, Telegram can operate on all devices and operating systems. The
+``eduAssistant'' chatbot acts as an automatic agent in the
+teacher-content-student relationship, providing real-time feedback loops and a
+personalized learning experience relevant to the students' acquired skills and
+knowledge. Using this chatbot, educators can create interactive instances in
+their lectures where they pose questions to their students and the chatbot
+assists those who need further help by giving them more hints and reporting it
+to the educator's dashboard \cite{fernoagua2018intelligent}. This could help
+educators identify students who need more attention and provide them with more
+educational resources relevant to their academic
+achievement.
 
 Despite its (arguably) successful implementation in different higher education
-institutions, particularly on the fringes of educational activity rather than actual
-student-teacher interaction, its implementation or deployment is not trivial.
-Some authors, for instance \cite{sjostrom2018designing}, have proposed a
-conceptual architecture for the adoption of teaching-oriented chatbots in higher
-education.  This conceptual architecture is based on a systematic literature
-review of previous studies examining the design of chatbots in higher
+institutions, particularly on the fringes of educational activity rather than
+actual student-teacher interaction, its implementation or deployment is not
+trivial.  Some authors, for instance \cite{sjostrom2018designing}, have proposed
+a conceptual architecture for the adoption of teaching-oriented chatbots in
+higher education.  This conceptual architecture is based on a systematic
+literature review of previous studies examining the design of chatbots in higher
 education, as well as making a content analysis of student emails and discussion
-forum posts from four instances of a Java programming course.  The study outlined
-several design considerations; among them, the authors emphasized the importance
-of developing chatbots in platforms that students and educators are familiar
-with and can easily access (i.e. Facebook Messenger), which was confirmed by
-\cite{hobert2019you} and \cite{fernoagua2018intelligent}. In addition, \cite{sjostrom2018designing} argued that 
-conceptualizing learners' questions could help designers integrate the
-appropriate types of questions that chatbots should support for different
-courses. Other authors, such as \cite{coronado2018cognitive}, have proposed agents that
-record learning materials to be provided on demand to students, while \cite{crockett2017predicting} 
-reported on tutoring systems that can
-perform initial assessments of students' understanding and provide learning
-materials to advance their understanding to the next level.
+forum posts from four instances of a Java programming course.  The study
+outlined several design considerations; among them, the authors emphasized the
+importance of developing chatbots in platforms that students and educators are
+familiar with and can easily access (i.e. Facebook Messenger), which was
+confirmed by \cite{hobert2019you} and \cite{fernoagua2018intelligent}. In
+addition, \cite{sjostrom2018designing} argued that conceptualizing learners'
+questions could help designers integrate the appropriate types of questions that
+chatbots should support for different courses. Other authors, such as
+\cite{coronado2018cognitive}, have proposed agents that record learning
+materials to be provided on demand to students, while
+\cite{crockett2017predicting} reported on tutoring systems that can perform
+initial assessments of students' understanding and provide learning materials to
+advance their understanding to the next level.
 

### 2023-01-10 edubots_surveys.Rnw
:rotating_light:

@@
   technology-enhanced tools and its potential impact on educational institutions
-  policies. In order to assess these, this paper layed out the following
+  policies. In order to assess these, this paper laid out the following
   research questions:
@@
 Overall, the majority of teachers responded that they do use messaging apps
-in their classrooms. The most common respones were messaging apps (or, more probably, messaging solutions) provided by their academic institutions (n=159, 56\%) and WhatsApp (n=124, 44.0\%). Only
+in their classrooms. The most common responses were messaging apps (or, more probably, messaging solutions) provided by their academic institutions (n=159, 56\%) and WhatsApp (n=124, 44.0\%). Only
 19 teachers (6.7\%) replied that they do not use any messaging app in their

### 2023-01-11 edubots_surveys.Rnw
:rotating_light:
:recycle: with the help of ChatGPT
reflow

--- 2023-01-10 edubots_surveys.Rnw
@@
 technology-enhanced tools and its potential impact on educational institutions
-  policies. In order to assess these, this paper laid out the following
-  research questions:
+policies. In order to evaluate these factors, this paper presents the following research questions:
 
@@
 utilization. Nevertheless, in higher education, institutions play a role in
-integrating these tools into their educational systems, which can improve the uptake of
-these applications and shape the social and educational experiences of 
-students. To achieve this successful integration, institutions should ensure that
-these messaging applications GDPR- (General Data Protection Regulation) compliant to protect students’ data and 
-provide IT support to all stakeholders who use the applications.
-
-Comparing these results with those obtained from student surveys
-in \cite{MoraChatbots2021:anon}, we have better understood the differences between teachers’
-and students' points of view and intentions when using the
-messaging applications in higher education.  Teachers tend to adopt technologies
-supported by their institutions, which could be motivated by a desire to ensure that their
+integrating these tools into their educational systems, which can improve the
+uptake of these applications and shape the social and educational experiences of
+students. To achieve this successful integration, institutions should ensure
+that these messaging applications GDPR- (General Data Protection Regulation)
+compliant to protect students’ data and provide IT support to all stakeholders
+who use the applications.
+
+Comparing these results with those obtained from student surveys in
+\cite{MoraChatbots2021:anon}, we have better understood the differences between
+teachers’ and students' points of view and intentions when using the messaging
+applications in higher education.  Teachers tend to adopt technologies supported
+by their institutions, which could be motivated by a desire to ensure that their
 universities can oversee their efforts in supporting their students during the
 learning process.  Another reason could be their familiarity with the technology
-provided by their institutions. Meanwhile, students use 
-non-institution messaging applications to create informal discussion groups with
-their peers.  It is worth noting that peer support and collaboration are
-inseparable from learning \cite{timmis2012constant} and correlates positively
-with higher retention in higher education \cite{o2014front}.  Therefore, both
-perspectives are complementary and play different roles in promoting the
-learning process.
-
-As with many other methodologies for assessing technology acceptance, the survey results suggest
-that the introduction of simple, and institution-supported instant messaging
-and chatbot technologies would increase the perceived usefulness (which is one
-of the key metrics in technology acceptance models). Given that most institutions
-already have some {\em virtual campus} or learning management system, adding
-some easy automation or connection to personal instant messaging tools could
-help introduce these new technologies to the learning community.
-
-Based on the discussion of this study, we propose a potential process for introducing
-technology that would need to be piloted in order to determine its value and its
-relationship to improved learning outcomes and higher teacher staff satisfaction.
-
-Initially, institutions should introduce messaging automation tools that help with bureaucratic or repetitive tasks, such as answering frequently asked questions or providing information on class or assignment deadlines.
-These chatbots will pave the way for more complex chatbots that will
-have a greater impact on learning outcomes, such as chatbots that help students
-integrate in class or identify and address learning problems
-in individual students or groups of them. These chatbots should also be accompanied by
-analytics on student interaction and possibly some natural language
-processing (in vernacular language) to help assess the general mood of
-the class and how different materials or external factors affect it.
+provided by their institutions. Meanwhile, students use non-institution
+messaging applications to create informal discussion groups with their peers.
+It is worth noting that peer support and collaboration are inseparable from
+learning \cite{timmis2012constant} and correlates positively with higher
+retention in higher education \cite{o2014front}.  Therefore, both perspectives
+are complementary and play different roles in promoting the learning process.
+
+As with many other methodologies for assessing technology acceptance, the survey
+results suggest that the introduction of simple, and institution-supported
+instant messaging and chatbot technologies would increase the perceived
+usefulness (which is one of the key metrics in technology acceptance
+models). Given that most institutions already have some {\em virtual campus} or
+learning management system, adding some easy automation or connection to
+personal instant messaging tools could help introduce these new technologies to
+the learning community.
+
+Based on the discussion of this study, we propose a potential process for
+introducing technology that would need to be piloted in order to determine its
+value and its relationship to improved learning outcomes and higher teacher
+staff satisfaction.
+
+Initially, institutions should introduce messaging automation tools that help
+with bureaucratic or repetitive tasks, such as answering frequently asked
+questions or providing information on class or assignment deadlines.  These
+chatbots will pave the way for more complex chatbots that will have a greater
+impact on learning outcomes, such as chatbots that help students integrate in
+class or identify and address learning problems in individual students or groups
+of them. These chatbots should also be accompanied by analytics on student
+interaction and possibly some natural language processing (in vernacular
+language) to help assess the general mood of the class and how different
+materials or external factors affect it.
 
@@
 
-One of the questions in the {\bf second survey}, which asked about 
-the messaging applications used by tertiary education teachers, opens a new line
-of inquiry about what educators {\em perceive} as such, and how it is used.
-Namely, the responses indicated that teachers perceived as messaging
-application not only traditional chats or instant messaging app such
-as WhatsApp or Microsoft Teams, but also the means provided by their university for
-communicating with students, such as a feature of grading applications that
-emails grades to students. This suggests that teachers have a need for communication with students, 
-which is mostly unidirectional, and that it
-does not matter as much how that need is met. However, this will need careful
-consideration, including how it ties with the automation of the learning
-experience provided by chatbots.
-
-Our analysis of the survey results can inform several potential avenues for future research. 
-For instance, the rollout of extensive videoconferencing and virtual
-teaching solutions that the COVID pandemic has brought has also taught us a
-series of lessons: it increases isolation and decreases the
-amount of synchronous contact that happens in the fringes of the classroom (e.g. 
-teaching staff offices, or before and after class). A future line of research could 
-focus on these issues and explore how chatbot technology could address them.
-
-Finally, the full extent of chatbot technology is not really examined in
-these surveys. They can be connected to natural language processing engines with
-sentiment analysis as well as other analytics. Examining the mood of the class such 
-as responses to new materials, assignments, exams or external events will help
-any student-centered teaching strategy, which will also help students (and
-teachers) achieve their learning objectives. This line of work, however, would require
-the introduction of some pilot study combined with initial opinion
+One of the questions in the {\bf second survey}, which asked about the messaging
+applications used by tertiary education teachers, opens a new line of inquiry
+about what educators {\em perceive} as such, and how it is used.  Namely, the
+responses indicated that teachers perceived as messaging application not only
+traditional chats or instant messaging app such as WhatsApp or Microsoft Teams,
+but also the means provided by their university for communicating with students,
+such as a feature of grading applications that emails grades to students. This
+suggests that teachers have a need for communication with students, which is
+mostly unidirectional, and that it does not matter as much how that need is
+met. However, this will need careful consideration, including how it ties with
+the automation of the learning experience provided by chatbots.
+
+Our analysis of the survey results can inform several potential avenues for
+future research.  For instance, the rollout of extensive videoconferencing and
+virtual teaching solutions that the COVID pandemic has brought has also taught
+us a series of lessons: it increases isolation and decreases the amount of
+synchronous contact that happens in the fringes of the classroom (e.g.  teaching
+staff offices, or before and after class). A future line of research could focus
+on these issues and explore how chatbot technology could address them.
+
+Finally, the full extent of chatbot technology is not really examined in these
+surveys. They can be connected to natural language processing engines with
+sentiment analysis as well as other analytics. Examining the mood of the class
+such as responses to new materials, assignments, exams or external events will
+help any student-centered teaching strategy, which will also help students (and
+teachers) achieve their learning objectives. This line of work, however, would
+require the introduction of some pilot study combined with initial opinion
 assessments from students.

### 2023-01-11 edubots_surveys.Rnw
Adding conclusions to the different paragraphs

@@
 The key findings of this study shed light on educators’ preferences for using
-messaging applications supported by their institutions. Technology adoption
-literature often focuses on users’ perceptions of the technology usefulness and
-ease of use as important factors for its successful adoption and
-utilization. Nevertheless, in higher education, institutions play a role in
-integrating these tools into their educational systems, which can improve the
-uptake of these applications and shape the social and educational experiences of
-students. To achieve this successful integration, institutions should ensure
-that these messaging applications GDPR- (General Data Protection Regulation)
-compliant to protect students’ data and provide IT support to all stakeholders
-who use the applications.
+messaging applications supported by their institutions. The literature on
+technology adoption often highlights the importance of users' perceptions of the
+technology's usefulness and ease of use for its successful implementation and
+utilization. However, in the context of higher education, institutions also play
+a crucial role in integrating these tools into their educational systems. This
+can not only improve the uptake of these applications, but also shape the social
+and educational experiences of students. To achieve this successful integration,
+institutions should ensure that these messaging applications are (in Europe)
+GDPR- (General Data Protection Regulation) compliant to protect students’ data
+and provide IT support to all stakeholders who use the applications. In summary,
+a technology adoption strategy for instant messaging, including chatbots,
+implies an institutional adoption strategy first and foremost.
 
 Comparing these results with those obtained from student surveys in
-\cite{MoraChatbots2021:anon}, we have better understood the differences between
-teachers’ and students' points of view and intentions when using the messaging
-applications in higher education.  Teachers tend to adopt technologies supported
-by their institutions, which could be motivated by a desire to ensure that their
-universities can oversee their efforts in supporting their students during the
-learning process.  Another reason could be their familiarity with the technology
-provided by their institutions. Meanwhile, students use non-institution
-messaging applications to create informal discussion groups with their peers.
-It is worth noting that peer support and collaboration are inseparable from
-learning \cite{timmis2012constant} and correlates positively with higher
+\cite{MoraChatbots2021:anon}, we now have a clear vision of the differences
+between teachers’ and students' points of view and intentions when using the
+messaging applications in higher education. Teachers are more likely to adopt
+technologies that are supported by their institutions. This may be driven by a
+desire to ensure that their universities can monitor and support their efforts
+to assist students during the learning process, although another reason could
+simply be their familiarity with the technological services provided by their
+institutions. Meanwhile, students use non-institution messaging applications to
+create informal discussion groups with their peers. It is worth noting that peer
+support and collaboration are inseparable from learning
+\cite{timmis2012constant} and its presence correlates positively with higher
 retention in higher education \cite{o2014front}. Therefore, both perspectives
-are complementary and play different roles in promoting the learning process.
+are complementary and play different roles in promoting the learning process;
+however, there is a certain degree of incompatibility that would hinder the
+process of adoption of a single messaging service that fits the need of both
+collectives, or would favor the adoption of semi-informal solutions that would
+rely on a popular platform (such as WhatsApp or Telegram) enhanced with
+institutional agreements with their providers, as well as locally created and
+supported chatbots.
 

### 2023-01-11 edubots_surveys.Rnw
Revising conclusion

@@
 
-Based on the discussion of this study, we propose a potential process for
+Based on the discussion of this study, we propose here a potential process for
 introducing technology that would need to be piloted in order to determine its
@@
 
-Initially, institutions should introduce messaging automation tools that help
-with bureaucratic or repetitive tasks, such as answering frequently asked
-questions or providing information on class or assignment deadlines.  These
-chatbots will pave the way for more complex chatbots that will have a greater
-impact on learning outcomes, such as chatbots that help students integrate in
-class or identify and address learning problems in individual students or groups
-of them. These chatbots should also be accompanied by analytics on student
-interaction and possibly some natural language processing (in vernacular
-language) to help assess the general mood of the class and how different
-materials or external factors affect it.
+Initially, institutions should introduce messaging automation tools attached to
+some, or several, messaging platforms that are already popular among the
+university community, that would help with bureaucratic or repetitive tasks,
+such as answering frequently asked questions or providing information on class
+or assignment deadlines.  These chatbots will pave the way for more complex ones
+that will have a greater impact on learning outcomes, such as chatbots that help
+students integrate with other students in class or identify and address learning
+problems in individual students or groups of them. These chatbots should also be
+accompanied by analytics on student interaction and possibly some natural
+language processing (in vernacular language) to help assess the general mood of
+the class and how different materials or external factors affect it. These tools
+would have to be attached to a learning analytics platform, which, in turn,
+would be part of an institutional learning management system.
 
 The introduction of chatbots and chatbot technology will be helped by the fact
-that no discernible differences are found between different groups. Even though
-chatbots do have some potential for personalization or customization based on
-the class material, student, and teaching staff, the general introduction of the
-technology can be done in a general way and for all disciplines, teaching
-experience, and gender.
+that no discernible differences are found in the survey between different
+demographic groups. Even though chatbots do have some potential for
+personalization or customization based on the class material, student, and
+teaching staff, the general introduction of the technology can be done in a
+general way and for all disciplines, types or degrees, teaching experience, and
+gender.
 
 Overall, the general feeling that transpires from the survey is that it is
-essential for any institution to take into account shareholders' opinions
-when introducing chatbots. This is true almost across the board, but in the case
-of chatbots (and instant messaging applications) their immediacy and the fact
-that they can enter into what we could call the private sphere makes this even
-more necessary.
+essential for any institution to take into account stakeholders' opinions when
+introducing chatbots. This is true almost across the board for any new
+technology, but in the case of chatbots (and instant messaging applications)
+their immediacy and the fact that they can enter into what we could call the
+private sphere makes this even more necessary.
 
@@
 about what educators {\em perceive} as such, and how it is used.  Namely, the
-responses indicated that teachers perceived as messaging application not only
+responses indicated that teachers considered messaging application not only
 traditional chats or instant messaging app such as WhatsApp or Microsoft Teams,
-but also the means provided by their university for communicating with students,
-such as a feature of grading applications that emails grades to students. This
-suggests that teachers have a need for communication with students, which is
-mostly unidirectional, and that it does not matter as much how that need is
-met. However, this will need careful consideration, including how it ties with
-the automation of the learning experience provided by chatbots.
+but also any means provided by their university for communicating with students,
+such as a feature of the cmapus-wide learning management system that emails
+grades to students. This suggests that teachers have a need for communication
+with students, which is mostly unidirectional, and that it does not matter as
+much how that need is met. However, this will need careful consideration,
+including how it ties with the automation of the learning experience provided by
+chatbots.
 
@@
 require the introduction of some pilot study combined with initial opinion
-assessments from students.
+assessments from students and is thus left for the future.
 

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

@@
 a crucial role in integrating these tools into their educational systems. This
-can not only improve the uptake of these applications, but also shape the social
+does not only improve the uptake of these applications, but also shapes the social
 and educational experiences of students. To achieve this successful integration,
@@
 \cite{MoraChatbots2021:anon}, we now have a clear vision of the differences
-between teachers’ and students' points of view and intentions when using the
+between teachers' and students' points of view and intentions when using the
 messaging applications in higher education. Teachers are more likely to adopt

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

@@
 technologies that are supported by their institutions. This may be driven by a
-desire to ensure that their universities can monitor and support their efforts
+desire to ensure that their universities monitor and support their efforts
 to assist students during the learning process, although another reason could

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

@@
 simply be their familiarity with the technological services provided by their
-institutions. Meanwhile, students use non-institution messaging applications to
+institutions. Meanwhile, students use non-institutional messaging applications to
 create informal discussion groups with their peers. It is worth noting that peer
@@
 \cite{timmis2012constant} and its presence correlates positively with higher
-retention in higher education \cite{o2014front}. Therefore, both perspectives
+retention rate in higher education \cite{o2014front}. Therefore, both perspectives
 are complementary and play different roles in promoting the learning process;

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

@@
 technology, but in the case of chatbots (and instant messaging applications)
-their immediacy and the fact that they can enter into what we could call the
+their immediacy and the fact that they can invade what we could call the
 private sphere makes this even more necessary.

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

@@
 about what educators {\em perceive} as such, and how it is used.  Namely, the
-responses indicated that teachers considered messaging application not only
-traditional chats or instant messaging app such as WhatsApp or Microsoft Teams,
+responses indicated that teachers considered messaging applications not only
+traditional chats or instant messaging apps such as WhatsApp or Microsoft Teams,
 but also any means provided by their university for communicating with students,

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

@@
 future research. For instance, the rollout of extensive videoconferencing and
-virtual teaching solutions that the COVID pandemic has brought has also taught
+virtual teaching solutions that the COVID-19 pandemic has brought has also taught
 us a series of lessons: it increases isolation and decreases the amount of

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

@@
 require the introduction of some pilot study combined with initial opinion
-assessments from students and is thus left for the future.
+assessments from students and is thus left as future work.
 

### 2023-01-11 edubots_surveys.Rnw
Went for institutional

@@
 personalization or customization based on the class material, student, and
-teaching staff, the general introduction of the technology can be done in a
+teaching staff, the institutional introduction of the technology can be done in a
 general way and for all disciplines, types or degrees, teaching experience, and

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

@@
 introducing technology that would need to be piloted in order to determine its
-value and its relationship to improved learning outcomes and higher teacher
+value and its relationship to improved learning outcomes and higher teaching
 staff satisfaction.

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

@@
 retention rate in higher education \cite{o2014front}. Therefore, both perspectives
-are complementary and play different roles in promoting the learning process;
-however, there is a certain degree of incompatibility that would hinder the
+are complementary and play different roles in promoting the learning process.
+However, there is a certain degree of incompatibility that would hinder the
 process of adoption of a single messaging service that fits the need of both

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>
Reflow and some corrections in first paragraph

@@
 first was to check whether teachers already used some kind of messaging
-application, and the one they preferred. Depending on the answer, different
-technologies could be (or not) available for the introduction of chatbots. In
-this case, the design of the survey introduced some ambiguity on what we really
-consider ``messaging technology'', that was eventually resolved by the answers.
-Apparently, anything that sends messages (even if they are not instant, even if
-they do not have a dedicated application) was the concept in the minds of the
-surveyed. In this case, we would like
-to add a clarification. While we had in mind, as indicated by the possible answers,
-instant messaging applications when we elaborated this question,
-we included these institution-provided applications mainly for completion. But
-it should be noted that, in most cases, they are not {\em instant} messaging
-apps in the way Telegram or Facebook Messenger are; in most cases, they are
-messaging facilities provided by learning management systems such as (usually)
-Moodle. So the answer to this question must be understood in two different ways:
-their preference for the {\em provider} of the technology (the university itself, any
-company) as well as the {\em type} of technology (instant, app-based messaging
-systems vs. web-based messaging systems integrated in another learning management system).
-
-This inclusion of university-provided messaging applications in
-the survey might explain why there are so few teachers, just 6.7\%, that answered they did not
-use any messaging application. In general, universities provide official channels
-to send students academic information such as the exam schedule
-or the grades. The statistical mode is to use that kind of messaging. Some other
-teaching staff might not use it, but use some extraofficial or opt-in channels such as the others included in the survey; in the end, between these official and extra-official channels, most people cover their needs to communicate with students.
-This matches
-our subjective experience, in general.
+application, and the one they preferred. The availability of certain
+technologies for implementing chatbots may vary based on the outcome. In this
+sense, the design of the survey introduced some ambiguity on what we really
+consider ``messaging technology'', that was any way validated in the piloting
+phase of the survey, and eventually resolved by the answers.  Apparently,
+anything that sends messages (even if they are not instant messages or have no
+dedicated application) was the concept in the minds of the surveyed. In this
+case, we would like to add a clarification. While we had in mind, as indicated
+by the possible answers, instant messaging applications when we elaborated this
+question, we included these institution-provided applications mainly for
+completion. But it should be noted that, in most cases, they are not {\em
+  instant} messaging apps in the way Telegram or Facebook Messenger are; they
+are messaging facilities provided by learning management systems such as Moodle
+or Blackboard. So the answer to this question must be understood in two
+different ways: their preference for the {\em provider} of the technology (the
+university itself, any company) as well as the {\em type} of technology
+(instant, app-based messaging systems vs. web- or email-based messaging systems
+integrated in another learning management system).
+
+This inclusion of university-provided messaging applications in the survey might
+explain why there are so few teachers, just 6.7\%, that answered they did not
+use any messaging application. In general, universities provide official
+channels to send students academic information such as the exam schedule or the
+grades. The statistical mode is to use that kind of messaging. Some other
+teaching staff might not use it, but use some extraofficial or opt-in channels
+such as the others included in the survey; in the end, between these official
+and extra-official channels, most people cover their needs to communicate with
+students. This matches our subjective experience, in general.
 
 Additionally, the question on COVID reflected the big challenge that represents
-changing habits, even in the case of a major crisis. Very few responders actually
-changed their habits, although comparing women vs. men as well as those teaching social
-sciences show some significant differences. We do not have any kind of explanation for
-this behavior, other than technologies are perceived, and adopted, in a
-different way depending on background and, apparently, gender.
-
-One of the most interesting questions arising from the analysis of the
-results, and that should require further study, is: Are teachers really aware
-of the possibilities of chatbots in the classroom? The survey
-only listed a few functionalities for the chatbots, and just a few subjects selected
-the option ``Others''. This may suggest that most teachers did not really understand
-at this point the actual potential of chatbots, since the responses listed were by no means exhaustive.
-If the responders were more acquainted with the possibilities of this technology, this response would possibly have shown up many more times.
-Another way to look at it is that, unless you provide the specific instructions on how to use a
-tool, the teaching staff is already too busy or burnt out to think about innovation.
-
-We can speculate that teaching staff's opinions of chatbots are influenced by negative
-experiences with chatbots used in customer support, which is what most people are likely to have
-experienced. Further study may be needed to confirm this, but it is important to 
-keep in mind when introducing chatbot technologies in the classroom.
-To potentially change this existing perception, it will be necessary to make chatbots as simple and satisfying to use as possible.
+changing habits, even in the case of a major crisis. Very few responders
+actually changed their habits, although comparing women vs. men as well as those
+teaching social sciences show some significant differences. We do not have any
+kind of explanation for this behavior, other than technologies are perceived,
+and adopted, in a different way depending on background and, apparently, gender.
+
+One of the most interesting questions arising from the analysis of the results,
+and that should require further study, is: Are teachers really aware of the
+possibilities of chatbots in the classroom? The survey only listed a few
+functionalities for the chatbots, and just a few subjects selected the option
+``Others''. This may suggest that most teachers did not really understand at
+this point the actual potential of chatbots, since the responses listed were by
+no means exhaustive. If the responders were more acquainted with the
+possibilities of this technology, this response would possibly have shown up
+many more times. Another way to look at it is that, unless you provide the
+specific instructions on how to use a tool, the teaching staff is already too
+busy or burnt out to think about innovation.
+
+We can speculate that teaching staff's opinions of chatbots are influenced by
+negative experiences with chatbots used in customer support, which is what most
+people are likely to have experienced. Further study may be needed to confirm
+this, but it is important to keep in mind when introducing chatbot technologies
+in the classroom.  To potentially change this existing perception, it will be
+necessary to make chatbots as simple and satisfying to use as possible.
 
 Regarding gender grouping, both genders agree in their uses, so it seems not
-relevant at all. However, when we look at the plot containing the sector differentiation,
-it is interesting to note that university teaching staff are more likely to use chatbots 
-for grades and FAQs compared to other tertiary education teaching staff.
-This seems reasonable as the frequency of seeing the students
-is lower at the University so, an automatic tool for grade notification for
-continuous evaluation would be more helpful.
-Furthermore, the high student-to-teacher
-ratios that university educators often face could be another reason why
-a higher number of them are willing to use chatbots for FAQs, as this could
-reduce misunderstandings and email overload from students.
-
-The results, when grouping by teaching experience, confirm that
-experienced teachers are just as open to change and willing to embrace new
-technological challenges as younger educators. 
-From this concrete plot it is interesting as well to observe the fact that very few
-young teachers are willing to use chatbots for other uses. This
-reinforces the hypothesis thrown at the beginning of this section that younger
-teachers have less experience to consider new ways of using chatbots in their daily work.
-
-According to the responses presented above, teachers’ responses are evenly
-split between positive and negative in relation to the media features:
-analytics, connectivity, and hidden phone number. This means that none of these features is a
-deciding factor in their choice of technology. However, for features such as familiarity,
-horizontality, sustainability, and officiality the majority provided a positive
-response, designating their preference to these features. On the other hand, the majority of teachers
-do not seem to see the media features of official certification, pluggability, unidirectionality, 
-and synchrony as valuable in messaging apps.
+relevant at all. However, when we look at the plot containing the sector
+differentiation, it is interesting to note that university teaching staff are
+more likely to use chatbots for grades and FAQs compared to other tertiary
+education teaching staff.  This seems reasonable as the frequency of seeing the
+students is lower at the University so, an automatic tool for grade notification
+for continuous evaluation would be more helpful.  Furthermore, the high
+student-to-teacher ratios that university educators often face could be another
+reason why a higher number of them are willing to use chatbots for FAQs, as this
+could reduce misunderstandings and email overload from students.
+
+The results, when grouping by teaching experience, confirm that experienced
+teachers are just as open to change and willing to embrace new technological
+challenges as younger educators.  From this concrete plot it is interesting as
+well to observe the fact that very few young teachers are willing to use
+chatbots for other uses. This reinforces the hypothesis thrown at the beginning
+of this section that younger teachers have less experience to consider new ways
+of using chatbots in their daily work.
+
+According to the responses presented above, teachers’ responses are evenly split
+between positive and negative in relation to the media features: analytics,
+connectivity, and hidden phone number. This means that none of these features is
+a deciding factor in their choice of technology. However, for features such as
+familiarity, horizontality, sustainability, and officiality the majority
+provided a positive response, designating their preference to these features. On
+the other hand, the majority of teachers do not seem to see the media features
+of official certification, pluggability, unidirectionality, and synchrony as
+valuable in messaging apps.
 
@@
 \begin{itemize}
- \item Teaching staff want to have support from their institutions. This
-   is probably due to the strict European data regulations on data protection,
-   but also to avoid the overhead required to sign up new students every year.
-   In general, additional support with specific formation and access to IT help desk for specific features
-   enhance the possibility of a successful adoption that improves the learning outcomes. This is supported by the result of the two
-   surveys: they prefer whatever ``messaging'' application provided by
-  as well as the fact that this application is the ``official'' for the university, as shown in
-   Table \ref{tab:interaction}.
- \item Teachers need sustainability. The main reason is that implementing
-   changes is expensive in terms of effort and prone to errors in the first
-   years. Therefore, it is logical that if
-   chatbots or messaging platforms are to be introduced, teaching staff want this change
-   to be as permanent as possible.
- \item Keep it Simple.
-Media interaction requirements are simple and only 2.4\% of educators are requesting more features.
-This could be a sign of technological burnt out produced by the previous pandemic courses, when the use of computers significantly increased.
+\item Teaching staff want to have support from their institutions. This is
+  probably due to the strict European data regulations on data protection, but
+  also to avoid the overhead required to sign up new students every year.  In
+  general, additional support with specific formation and access to IT help desk
+  for specific features enhance the possibility of a successful adoption that
+  improves the learning outcomes. This is supported by the result of the two
+  surveys: they prefer whatever ``messaging'' application provided by as well as
+  the fact that this application is the ``official'' for the university, as
+  shown in Table \ref{tab:interaction}.
+\item Teachers need sustainability. The main reason is that implementing changes
+  is expensive in terms of effort and prone to errors in the first
+  years. Therefore, it is logical that if chatbots or messaging platforms are to
+  be introduced, teaching staff want this change to be as permanent as possible.
+ \item Keep it Simple. Media interaction requirements are simple and only 2.4\%
+   of educators are requesting more features. This could be a sign of
+   technological burnt out produced by the previous pandemic courses, when the
+   use of computers significantly increased.
 \end{itemize}
 
-The analysis of the questions related to RQ4 seems to indicate that teaching staff
-prefer to share an interaction space with their students. As
-shown in Tables \ref{tab:kindinteractions} and \ref{tab:interaction}, the majority of responders
-indicated that they {\em do not} want unidirectional communication, and that they prefer
-{\em horizontal} interaction. This point is reinforced by results on the kind of
-chatbots they preferred: most of them indicated FAQ bots, which might indicate a
-need to offload part of the burden of answering every single question posed by
-their students. In a horizontal setting, other students would answer if the teacher
-does not do it immediately. This might also be the reason why the possibility of
-using tools from which analytics can be extracted is also valued by teachers:
-in that way, the student activity in the chat tool, answering questions, or their regularity can all be
-assessed as part of the process of achieving learning objectives.
-
-In our survey, we could not find an answer about the right moment to introducing chatbot technologies. The response to questions regarding to change of
-behavior during and after the first stay-at-home stage of the pandemic do not suggest that a major (or minor, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.} or the introduction of new degrees) crisis could be an opportunity to introduce new technologies.
-The reason being that it does not
-bring major changes in attitude 
-%(as a minor ``crisis'' we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.}),
-%or simply the introduction of new degrees. 
-Although changes driven by external forces do offer the chance of piloting new technologies, they do not
-seem to bring internal changes in educators' attitudes (which, after all, is
-bound to be the same). In absence of a clear answer in this direction, the right
-moment to introduce new technologies is always when the IT and managing staff is
-ready to support it (since, as we have seen before, ``official'' support is one of
-the factors that is most valued by teachers).
+The analysis of the questions related to RQ4 seems to indicate that teaching
+staff prefer to share an interaction space with their students. As shown in
+Tables \ref{tab:kindinteractions} and \ref{tab:interaction}, the majority of
+responders indicated that they {\em do not} want unidirectional communication,
+and that they prefer {\em horizontal} interaction. This point is reinforced by
+results on the kind of chatbots they preferred: most of them indicated FAQ bots,
+which might indicate a need to offload part of the burden of answering every
+single question posed by their students. In a horizontal setting, other students
+would answer if the teacher does not do it immediately. This might also be the
+reason why the possibility of using tools from which analytics can be extracted
+is also valued by teachers: in that way, the student activity in the chat tool,
+answering questions, or their regularity can all be assessed as part of the
+process of achieving learning objectives.
+
+In our survey, we could not find an answer about the right moment to introducing
+chatbot technologies. The response to questions regarding to change of behavior
+during and after the first stay-at-home stage of the pandemic do not suggest
+that a major (or minor, such as new higher education laws\footnote{We seem to
+  have one of these, at least in Spain, every 10 years or so.} or the
+introduction of new degrees) crisis could be an opportunity to introduce new
+technologies. The reason being that it does not bring major changes in attitude
+Although changes driven by external forces do offer the chance of piloting new
+technologies, they do not seem to bring internal changes in educators' attitudes
+(which, after all, is bound to be the same). In absence of a clear answer in
+this direction, the right moment to introduce new technologies is always when
+the IT and managing staff is ready to support it (since, as we have seen before,
+``official'' support is one of the factors that is most valued by teachers).
 
@@
 the class and how different materials or external factors affect it. These tools
-would have to be attached to a learning analytics platform, which, in turn,
+would have to be attached to a learning analytics platform, which in turn,
 would be part of an institutional learning management system.

### 2023-01-11 edubots_surveys.Rnw
Reflow and some corrections in first paragraph

@@
 The key findings of this study shed light on educators’ preferences for using
-messaging applications supported by their institutions. The literature on
-technology adoption often highlights the importance of users' perceptions of the
-technology's usefulness and ease of use for its successful implementation and
-utilization. However, in the context of higher education, institutions also play
-a crucial role in integrating these tools into their educational systems. This
-does not only improve the uptake of these applications, but also shapes the social
-and educational experiences of students. To achieve this successful integration,
-institutions should ensure that these messaging applications are (in Europe)
-GDPR- (General Data Protection Regulation) compliant to protect students’ data
-and provide IT support to all stakeholders who use the applications. In summary,
-a technology adoption strategy for instant messaging, including chatbots,
-implies an institutional adoption strategy first and foremost.
-
-Comparing these results with those obtained from student surveys in
-\cite{MoraChatbots2021:anon}, we now have a clear vision of the differences
-between teachers' and students' points of view and intentions when using the
-messaging applications in higher education. Teachers are more likely to adopt
-technologies that are supported by their institutions. This may be driven by a
-desire to ensure that their universities monitor and support their efforts
-to assist students during the learning process, although another reason could
-simply be their familiarity with the technological services provided by their
-institutions. Meanwhile, students use non-institutional messaging applications to
-create informal discussion groups with their peers. It is worth noting that peer
-support and collaboration are inseparable from learning
-\cite{timmis2012constant} and its presence correlates positively with higher
-retention rate in higher education \cite{o2014front}. Therefore, both perspectives
-are complementary and play different roles in promoting the learning process.
-However, there is a certain degree of incompatibility that would hinder the
-process of adoption of a single messaging service that fits the need of both
-collectives, or would favor the adoption of semi-informal solutions that would
-rely on a popular platform (such as WhatsApp or Telegram) enhanced with
-institutional agreements with their providers, as well as locally created and
-supported chatbots.
-
-As with many other methodologies for assessing technology acceptance, the survey
-results suggest that the introduction of simple, and institution-supported
-instant messaging and chatbot technologies would increase the perceived
-usefulness (which is one of the key metrics in technology acceptance
-models). Given that most institutions already have some {\em virtual campus} or
-learning management system, adding some easy automation or connection to
-personal instant messaging tools could help introduce these new technologies to
-the learning community.
-
-Based on the discussion of this study, we propose here a potential process for
-introducing technology that would need to be piloted in order to determine its
-value and its relationship to improved learning outcomes and higher teaching
-staff satisfaction.
-
-Initially, institutions should introduce messaging automation tools attached to
-some, or several, messaging platforms that are already popular among the
-university community, that would help with bureaucratic or repetitive tasks,
-such as answering frequently asked questions or providing information on class
-or assignment deadlines.  These chatbots will pave the way for more complex ones
-that will have a greater impact on learning outcomes, such as chatbots that help
-students integrate with other students in class or identify and address learning
-problems in individual students or groups of them. These chatbots should also be
-accompanied by analytics on student interaction and possibly some natural
-language processing (in vernacular language) to help assess the general mood of
-the class and how different materials or external factors affect it. These tools
-would have to be attached to a learning analytics platform, which in turn,
-would be part of an institutional learning management system.
+messaging applications supported by their institutions. Technology adoption
+literature often focuses on users’ perceptions of the technology usefulness and
+ease of use as important factors for its successful adoption and
+utilization. Nevertheless, in higher education, institutions play a role in
+integrating these tools into their educational systems, which can improve the uptake of
+these applications and shape the social and educational experiences of 
+students. To achieve this successful integration, institutions should ensure that
+these messaging applications GDPR- (General Data Protection Regulation) compliant to protect students’ data and 
+provide IT support to all stakeholders who use the applications.
+
+Comparing these results with those obtained from student surveys
+in \cite{MoraChatbots2021:anon}, we have better understood the differences between teachers’
+and students' points of view and intentions when using the
+messaging applications in higher education.  Teachers tend to adopt technologies
+supported by their institutions, which could be motivated by a desire to ensure that their
+universities can oversee their efforts in supporting their students during the
+learning process.  Another reason could be their familiarity with the technology
+provided by their institutions. Meanwhile, students use 
+non-institution messaging applications to create informal discussion groups with
+their peers.  It is worth noting that peer support and collaboration are
+inseparable from learning \cite{timmis2012constant} and correlates positively
+with higher retention in higher education \cite{o2014front}.  Therefore, both
+perspectives are complementary and play different roles in promoting the
+learning process.
+
+As with many other methodologies for assessing technology acceptance, the survey results suggest
+that the introduction of simple, and institution-supported instant messaging
+and chatbot technologies would increase the perceived usefulness (which is one
+of the key metrics in technology acceptance models). Given that most institutions
+already have some {\em virtual campus} or learning management system, adding
+some easy automation or connection to personal instant messaging tools could
+help introduce these new technologies to the learning community.
+
+Based on the discussion of this study, we propose a potential process for introducing
+technology that would need to be piloted in order to determine its value and its
+relationship to improved learning outcomes and higher teacher staff satisfaction.
+
+Initially, institutions should introduce messaging automation tools that help with bureaucratic or repetitive tasks, such as answering frequently asked questions or providing information on class or assignment deadlines.
+These chatbots will pave the way for more complex chatbots that will
+have a greater impact on learning outcomes, such as chatbots that help students
+integrate in class or identify and address learning problems
+in individual students or groups of them. These chatbots should also be accompanied by
+analytics on student interaction and possibly some natural language
+processing (in vernacular language) to help assess the general mood of
+the class and how different materials or external factors affect it.
 
 The introduction of chatbots and chatbot technology will be helped by the fact
-that no discernible differences are found in the survey between different
-demographic groups. Even though chatbots do have some potential for
-personalization or customization based on the class material, student, and
-teaching staff, the institutional introduction of the technology can be done in a
-general way and for all disciplines, types or degrees, teaching experience, and
-gender.
+that no discernible differences are found between different groups. Even though
+chatbots do have some potential for personalization or customization based on
+the class material, student, and teaching staff, the general introduction of the
+technology can be done in a general way and for all disciplines, teaching
+experience, and gender.
 
 Overall, the general feeling that transpires from the survey is that it is
-essential for any institution to take into account stakeholders' opinions when
-introducing chatbots. This is true almost across the board for any new
-technology, but in the case of chatbots (and instant messaging applications)
-their immediacy and the fact that they can invade what we could call the
-private sphere makes this even more necessary.
-
-One of the questions in the {\bf second survey}, which asked about the messaging
-applications used by tertiary education teachers, opens a new line of inquiry
-about what educators {\em perceive} as such, and how it is used.  Namely, the
-responses indicated that teachers considered messaging applications not only
-traditional chats or instant messaging apps such as WhatsApp or Microsoft Teams,
-but also any means provided by their university for communicating with students,
-such as a feature of the cmapus-wide learning management system that emails
-grades to students. This suggests that teachers have a need for communication
-with students, which is mostly unidirectional, and that it does not matter as
-much how that need is met. However, this will need careful consideration,
-including how it ties with the automation of the learning experience provided by
-chatbots.
-
-Our analysis of the survey results can inform several potential avenues for
-future research. For instance, the rollout of extensive videoconferencing and
-virtual teaching solutions that the COVID-19 pandemic has brought has also taught
-us a series of lessons: it increases isolation and decreases the amount of
-synchronous contact that happens in the fringes of the classroom (e.g.  teaching
-staff offices, or before and after class). A future line of research could focus
-on these issues and explore how chatbot technology could address them.
-
-Finally, the full extent of chatbot technology is not really examined in these
-surveys. They can be connected to natural language processing engines with
-sentiment analysis as well as other analytics. Examining the mood of the class
-such as responses to new materials, assignments, exams or external events will
-help any student-centered teaching strategy, which will also help students (and
-teachers) achieve their learning objectives. This line of work, however, would
-require the introduction of some pilot study combined with initial opinion
-assessments from students and is thus left as future work.
+essential for any institution to take into account shareholders' opinions
+when introducing chatbots. This is true almost across the board, but in the case
+of chatbots (and instant messaging applications) their immediacy and the fact
+that they can enter into what we could call the private sphere makes this even
+more necessary.
+
+One of the questions in the {\bf second survey}, which asked about 
+the messaging applications used by tertiary education teachers, opens a new line
+of inquiry about what educators {\em perceive} as such, and how it is used.
+Namely, the responses indicated that teachers perceived as messaging
+application not only traditional chats or instant messaging app such
+as WhatsApp or Microsoft Teams, but also the means provided by their university for
+communicating with students, such as a feature of grading applications that
+emails grades to students. This suggests that teachers have a need for communication with students, 
+which is mostly unidirectional, and that it
+does not matter as much how that need is met. However, this will need careful
+consideration, including how it ties with the automation of the learning
+experience provided by chatbots.
+
+Our analysis of the survey results can inform several potential avenues for future research. 
+For instance, the rollout of extensive videoconferencing and virtual
+teaching solutions that the COVID pandemic has brought has also taught us a
+series of lessons: it increases isolation and decreases the
+amount of synchronous contact that happens in the fringes of the classroom (e.g. 
+teaching staff offices, or before and after class). A future line of research could 
+focus on these issues and explore how chatbot technology could address them.
+
+Finally, the full extent of chatbot technology is not really examined in
+these surveys. They can be connected to natural language processing engines with
+sentiment analysis as well as other analytics. Examining the mood of the class such 
+as responses to new materials, assignments, exams or external events will help
+any student-centered teaching strategy, which will also help students (and
+teachers) achieve their learning objectives. This line of work, however, would require
+the introduction of some pilot study combined with initial opinion
+assessments from students.
 

### 2023-01-11 edubots_surveys.Rnw
Improving some more with the help of ChatGPT

@@
 use any messaging application. In general, universities provide official
-channels to send students academic information such as the exam schedule or the
-grades. The statistical mode is to use that kind of messaging. Some other
-teaching staff might not use it, but use some extraofficial or opt-in channels
-such as the others included in the survey; in the end, between these official
-and extra-official channels, most people cover their needs to communicate with
-students. This matches our subjective experience, in general.
-
-Additionally, the question on COVID reflected the big challenge that represents
-changing habits, even in the case of a major crisis. Very few responders
-actually changed their habits, although comparing women vs. men as well as those
-teaching social sciences show some significant differences. We do not have any
-kind of explanation for this behavior, other than technologies are perceived,
-and adopted, in a different way depending on background and, apparently, gender.
+channels to send (or simply make available to) students academic information
+such as the exam schedule or the grades. The statistical mode is to use that
+kind of messaging. Some other teaching staff might not use it, but use some
+extraofficial or opt-in channels such as the others included in the survey; in
+the end, between these official and extra-official channels, most people cover
+their needs to communicate with students. This matches the subjective experience
+of the authors of this paper, in general.
+
+Furthermore, the answers to the survey question regarding COVID highlights the
+significant challenge of altering behavior, even during a major crisis. Very few
+responders actually changed their habits, although comparing women vs. men as
+well as those teaching social sciences vs. the rest of the disciplines, there
+are some significant differences. We do not have any kind of explanation for
+this behavior, other than technologies are perceived, and adopted, in a
+different way depending on background and, apparently, gender.
 

### 2023-01-11 edubots_surveys.Rnw
More revisions with the help of ChatGPT

@@
 well as those teaching social sciences vs. the rest of the disciplines, there
-are some significant differences. We do not have any kind of explanation for
-this behavior, other than technologies are perceived, and adopted, in a
-different way depending on background and, apparently, gender.
+are some significant differences. We do not have a clear understanding of the
+reasons behind this behavior; however, it appears that the perception and
+adoption of technologies in a major crisis may vary based on an individual's
+background and gender.
 
@@
 this point the actual potential of chatbots, since the responses listed were by
-no means exhaustive. If the responders were more acquainted with the
-possibilities of this technology, this response would possibly have shown up
-many more times. Another way to look at it is that, unless you provide the
-specific instructions on how to use a tool, the teaching staff is already too
-busy or burnt out to think about innovation.
-
-We can speculate that teaching staff's opinions of chatbots are influenced by
-negative experiences with chatbots used in customer support, which is what most
-people are likely to have experienced. Further study may be needed to confirm
-this, but it is important to keep in mind when introducing chatbot technologies
-in the classroom.  To potentially change this existing perception, it will be
-necessary to make chatbots as simple and satisfying to use as possible.
-
-Regarding gender grouping, both genders agree in their uses, so it seems not
-relevant at all. However, when we look at the plot containing the sector
-differentiation, it is interesting to note that university teaching staff are
-more likely to use chatbots for grades and FAQs compared to other tertiary
-education teaching staff.  This seems reasonable as the frequency of seeing the
-students is lower at the University so, an automatic tool for grade notification
-for continuous evaluation would be more helpful.  Furthermore, the high
-student-to-teacher ratios that university educators often face could be another
-reason why a higher number of them are willing to use chatbots for FAQs, as this
-could reduce misunderstandings and email overload from students.
+no means exhaustive. Had the responders been more acquainted with the
+possibilities of this technology, this ``Other'' response would possibly have
+shown up many more times. Another way to look at it is that, unless you provide
+the specific instructions on how to use a tool, the teaching staff is already
+too busy or burnt out to think about innovation, so they think it is not their
+job to think about new possibilities of existing or new technologies.
+
+The reluctance to adopt chatbots in class might have an explanation: We can
+speculate that teaching staff's opinions of chatbots are influenced by negative
+experiences with chatbots used in customer support, which is what most people
+are likely to have experienced. Further study may be needed to confirm this, but
+it is important to keep it in mind when introducing chatbot technologies in the
+classroom.  To potentially change this existing perception, it will be necessary
+to make chatbots as simple and satisfying to use as possible.
+
+Regarding gender grouping, both genders agree in the possible uses of chatbots,
+so it seems not relevant at all. However, when we look at the plot containing
+the sector differentiation, it is interesting to note that university teaching
+staff are more likely to use chatbots for grades and FAQs compared to teaching
+staff involved in other tertiary education institutions. This appears logical,
+as the number of personal interactions with students in certain classes at the
+university is smaller\footnote{Most university classes take place one or twice
+  week, as opposed to daily classes with the same teacher in other tertiary
+  education, and hold usually twice as many persons as the typical tertiary
+  education class}, thus an automated grade notification tool for continuous
+evaluation would be more beneficial.  Furthermore, the high student-to-teacher
+ratios that university educators often face could be another reason why a higher
+number of them are willing to use chatbots for FAQs, as this could reduce
+misunderstandings and email (or face to face tutoring) overload from students.
 
@@
 
-According to the responses presented above, teachers’ responses are evenly split
+According to the responses presented above, teachers’ reactions are evenly split
 between positive and negative in relation to the media features: analytics,
@@
 \begin{itemize}
-\item Teaching staff want to have support from their institutions. This is
-  probably due to the strict European data regulations on data protection, but
-  also to avoid the overhead required to sign up new students every year.  In
-  general, additional support with specific formation and access to IT help desk
-  for specific features enhance the possibility of a successful adoption that
-  improves the learning outcomes. This is supported by the result of the two
-  surveys: they prefer whatever ``messaging'' application provided by as well as
-  the fact that this application is the ``official'' for the university, as
-  shown in Table \ref{tab:interaction}.
-\item Teachers need sustainability. The main reason is that implementing changes
-  is expensive in terms of effort and prone to errors in the first
-  years. Therefore, it is logical that if chatbots or messaging platforms are to
-  be introduced, teaching staff want this change to be as permanent as possible.
- \item Keep it Simple. Media interaction requirements are simple and only 2.4\%
+\item Teaching staff wants to have support from their institutions. One of the
+  main reasons why this is a factor might be the strict European data
+  regulations on data protection; it is very likely that they also want to avoid
+  the overhead required to sign up new students every year and other maintenance
+  tasks.  In general, additional support with specific formation and access to
+  IT help desk for specific features enhance the possibility of a successful
+  adoption that improves the learning outcomes. This is supported by the result
+  of the two surveys: they prefer whatever ``messaging'' application provided by
+  as well as the fact that this application is the ``official'' for the
+  university, as shown in Table \ref{tab:interaction}.
+\item Teachers require sustainability. The primary rationale is that the
+  implementation of changes is costly in terms of effort and prone to mistakes
+  during the initial years of deployment of any new technology. Therefore, it is
+  logical that if chatbots or messaging platforms are to be introduced, teaching
+  staff want this change to be as permanent, and long-term, as possible.
+ \item ``Keep it Simple''. Media interaction requirements are simple and only 2.4\%
    of educators are requesting more features. This could be a sign of
-   technological burnt out produced by the previous pandemic courses, when the
-   use of computers significantly increased.
+   technological burnout produced by the previous pandemic courses, when the
+   use of computers significantly increased; however, simplicity is always a
+   feature that people want to have in any technology they adopt.
 \end{itemize}
 
-The analysis of the questions related to RQ4 seems to indicate that teaching
-staff prefer to share an interaction space with their students. As shown in
-Tables \ref{tab:kindinteractions} and \ref{tab:interaction}, the majority of
-responders indicated that they {\em do not} want unidirectional communication,
-and that they prefer {\em horizontal} interaction. This point is reinforced by
-results on the kind of chatbots they preferred: most of them indicated FAQ bots,
-which might indicate a need to offload part of the burden of answering every
-single question posed by their students. In a horizontal setting, other students
-would answer if the teacher does not do it immediately. This might also be the
-reason why the possibility of using tools from which analytics can be extracted
-is also valued by teachers: in that way, the student activity in the chat tool,
-answering questions, or their regularity can all be assessed as part of the
-process of achieving learning objectives.
-
-In our survey, we could not find an answer about the right moment to introducing
-chatbot technologies. The response to questions regarding to change of behavior
-during and after the first stay-at-home stage of the pandemic do not suggest
-that a major (or minor, such as new higher education laws\footnote{We seem to
-  have one of these, at least in Spain, every 10 years or so.} or the
-introduction of new degrees) crisis could be an opportunity to introduce new
-technologies. The reason being that it does not bring major changes in attitude
-Although changes driven by external forces do offer the chance of piloting new
-technologies, they do not seem to bring internal changes in educators' attitudes
-(which, after all, is bound to be the same). In absence of a clear answer in
-this direction, the right moment to introduce new technologies is always when
-the IT and managing staff is ready to support it (since, as we have seen before,
-``official'' support is one of the factors that is most valued by teachers).
+The analysis of the answers to questions related to RQ4 seems to indicate that
+teaching staff prefer to share an interaction space with their students. As
+shown in Tables \ref{tab:kindinteractions} and \ref{tab:interaction}, the
+majority of responders indicated that they {\em do not} want unidirectional
+communication, and that they prefer {\em horizontal} interaction. This point is
+reinforced by results on the kind of chatbots they preferred: most of them
+indicated FAQ bots, which might indicate a need to offload part of the burden of
+answering every single question posed by their students. In a horizontal
+setting, other students would answer if the teacher does not do it
+immediately. This might also be the reason why the possibility of using tools
+from which analytics can be extracted is also valued by teachers: in that way,
+the student activity in the chat tool, answering questions, or their regularity
+can all be assessed as part of the process of achieving learning objectives.
+
+In our survey, we could not find an answer about the right moment for the
+introduction of chatbot technologies. The response to questions regarding to
+change of behavior during and after the first stay-at-home stage of the pandemic
+do not suggest that a major (or minor, such as new higher education
+laws\footnote{We seem to have one of these, at least in Spain, every 10 years or
+  so.} or the introduction of new degrees) crisis could be an opportunity to
+introduce new technologies. The reason being that it does not bring major
+changes in attitude. Although changes driven by external forces do offer the
+chance of piloting new technologies, they do not seem to bring internal changes
+in educators' attitudes (which, after all, is bound to be the same). In absence
+of a clear answer in this direction, the right moment to introduce new
+technologies is always when the IT and managing staff is ready to support it
+(since, as we have seen before, ``official'' support is one of the factors that
+is most valued by teachers).
 

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

@@
 sense, the design of the survey introduced some ambiguity on what we really
-consider ``messaging technology'', that was any way validated in the piloting
+consider ``messaging technology'', that was anyway validated in the piloting
 phase of the survey, and eventually resolved by the answers.  Apparently,

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

--- 2023-01-11 edubots_surveys.Rnw
@@
 such as the exam schedule or the grades. The statistical mode is to use that
-kind of messaging. Some other teaching staff might not use it, but use some
+kind of messaging application. Some other teaching staff might not use it, but use some
 extraofficial or opt-in channels such as the others included in the survey; in
 the end, between these official and extra-official channels, most people cover
-their needs to communicate with students. This matches the subjective experience
-of the authors of this paper, in general.
-
-Furthermore, the answers to the survey question regarding COVID highlights the
+their needs to communicate with students. In general, this matches the subjective experience
+of the authors of this paper.
+
+Furthermore, the answers to the survey question regarding COVID-19 highlights the
 significant challenge of altering behavior, even during a major crisis. Very few

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

@@
 well as those teaching social sciences vs. the rest of the disciplines, there
-are some significant differences. We do not have a clear understanding of the
+were some significant differences. We do not have a clear understanding of the
 reasons behind this behavior; however, it appears that the perception and
@@
 the specific instructions on how to use a tool, the teaching staff is already
-too busy or burnt out to think about innovation, so they think it is not their
+too busy or burnt out to think about innovation, so they likely consider that it is not their
 job to think about new possibilities of existing or new technologies.

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

--- 2023-01-11 edubots_surveys.Rnw
@@
 The reluctance to adopt chatbots in class might have an explanation: We can
-speculate that teaching staff's opinions of chatbots are influenced by negative
+speculate that teaching staff's opinions are influenced by negative
 experiences with chatbots used in customer support, which is what most people

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

--- 2023-01-11 edubots_surveys.Rnw
@@
   the overhead required to sign up new students every year and other maintenance
-  tasks.  In general, additional support with specific formation and access to
+  tasks.  In general, additional support with specific training and access to
   IT help desk for specific features enhance the possibility of a successful

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

@@
 In our survey, we could not find an answer about the right moment for the
-introduction of chatbot technologies. The response to questions regarding to
+introduction of chatbot technologies. The response to questions regarding the
 change of behavior during and after the first stay-at-home stage of the pandemic

### 2023-01-11 edubots_surveys.Rnw
Small grammar fix

--- 2023-01-11 edubots_surveys.Rnw
@@
 the specific instructions on how to use a tool, the teaching staff is already
-too busy or burnt out to think about innovation, so they likely consider that it is not their
+too busy or burnt out to think about innovation, so they likely considered that it was not their
 job to think about new possibilities of existing or new technologies.

### 2023-01-11 edubots_surveys.Rnw
small edit

--- 2023-01-11 edubots_surveys.Rnw
@@
 as the number of personal interactions with students in certain classes at the
-university is smaller\footnote{Most university classes take place one or twice
-  week, as opposed to daily classes with the same teacher in other tertiary
+university is smaller\footnote{Most university classes take place once or twice
+ a week, as opposed to daily classes with the same teacher in other tertiary
   education, and hold usually twice as many persons as the typical tertiary

### 2023-01-12 edubots_surveys.Rnw
:rotating_light:

@@
 too busy or burnt out to think about innovation, so they likely considered that it was not their
-job to think about new possibilities of existing or new technologies.
+job to think about new possibilities for existing or new technologies.
 

### 2023-01-12 edubots_surveys.Rnw
Rewriting via ChatGPT again

--- 2023-01-11 edubots_surveys.Rnw
@@
 possibilities of this technology, this ``Other'' response would possibly have
-shown up many more times. Another way to look at it is that, unless you provide
-the specific instructions on how to use a tool, the teaching staff is already
-too busy or burnt out to think about innovation, so they likely considered that it was not their
-job to think about new possibilities of existing or new technologies.
+shown up many more times.
+Another perspective is that, without clear guidelines on how to utilize a tool, educators may not have the capacity or energy to consider innovative uses; thus, they may have assumed that it is not their responsibility to explore new possibilities with existing or new technologies.
 

### 2023-01-12 response-reviewers-3.tex
Response to reviewers uploaded

--- 2022-10-03 response-reviewers-2.tex
@@
 
-We are very grateful to the reviewers for their kind comments. We have rewritten
-the paper quite extensively, incorporating requested changes, but also
-attempting to give another angle that makes this paper apart from what was
-already published in another (hidden for double blind review).
+We are very grateful to the editor and reviewers for their kind comments. We have rewritten
+the paper quite extensively, improving grammar and, in some cases,
+spelling. Additionally, we have revised references extensively, updating some
+that were shown as ``under submission'' or ``accepted'', as well as fixed
+capitalization in some others.
 
-This explains that, in some cases, conclusions have been extended or
-reinterpreted over the ones published in that paper. Some of these extensive
-changes have been noted in blue for their easy identification.
-Additionally, we validated
-the survey, as was also requested by the reviewers.
-
-Next we will address the concerns of the reviewers individually.
+Next we will address the concerns of the single reviewer individually.
 
@@
 
-{\bf Reviewer \#3}: Paper Summary:
-This study surveyed teachers' feedback about their opinions regarding introducing the messaging platforms and chatbots in their classes, understand their needs, and gathering information about the various educational use cases where these tools are valuable.
-There are some suggestions below to improve the research work.
-1.
-Does the article address a topic of current concern about the aims of the journal and to what you perceive to be the current state of ICT concerning education?
-The article addresses issues bothering the introduction of messaging platforms and chatbots to augment teaching and learning, which I consider important concerning the current state of ICT education.}
+  {\bf Reviewer \#1}:
+
+The paper has been significantly revised to meet the comments submitted by various reviewers.
+As far as I am concerned the authors have satisfactorily addressed the comments of the earlier reviewers.
+As is often the case, the authors have made a case to answer queries, for example, about the research questions and the significance of the study.
+While addressing the queries ought to lead to accepting the submission, the issue I have is that the added text - in blue font in my copy - has significant grammatical errors.
+For instance, just in the first additional paragraph there are a number of issues as shown below:
+
+New technologies are being introduced and widely adopted into the classroom in the
+last years. (in recent years).
+
+However, in order to be successful, their application will require (many)
+extra work and training for the teacher, as well as for the students. (delete many).
+
+Thus, both of them will acquire new skills and, potentially, pupils will get a higher engagement to the subject, which is usually the main objective. (pupils will be more engaged).
+
+Therefore the new text needs a careful proofread before the submission can be accepted.}
 
@@
 
-The authors thank the comment for noticing the relevance of the topic and how it suits the journal scope.
-
-{\it 2.
-Does the abstract give a clear account of the scope of the paper?
-The abstract gave an overview of the paper.
-However, the key findings of the paper were not reported in the abstract.
-I suggest the authors summarize the study's findings and report them briefly in the abstract.}
-
-% -> answer 2
-
-The abstract as well as other sections in the paper have been rewritten. The abstract now summarizes the study's findings and reports them briefly.
-
-% -> answer 3
-
-{\it 3.      Do the keywords adequately reflect the paper? The authors should consider replacing Tutorship with teachers.}
-
-After consideration, the authors agree with the comment and we have replaced teachers for Tutorship in the keywords.
-
-% -> answer 4
-
-{\it 4.
-If the article is concerned with research activity, has a sound methodology been utilized and described?
-A sound methodology was utilized and described.
-However, it was observed that prior studies have not previously validated the measurement instrument used in collecting data.
-Thus, the authors need to conduct reliability and validity tests for their proposed measurement instrument used in collecting data.}
-
-The authors thank the reviewer for pointing out that flaw which was addressed, improving the quality of the paper.
-
-A new subsection whithin the methodology (Section 3.1 Survery validation) deals with the procedure to validate the tests by using a board of experts for the questionaire.
-
-% -> answer 5,6,7,8
-
-{\it 5.      Does the article distinguish clearly between opinion and empirical evidence? Yes
-6.      Does the article contribute to a critical understanding of the issues? Yes
-7.      Does the article alert readers to significant new developments in the subject area? Yes
-8.      Does the article take into account relevant contemporary literature in the area? Yes.}
-
-The authors want to thank the reviewer for evaluating positively those aspect of the paper.
-
-% -> answer 9
-
-{\it 9.
-Does the article clearly reference citations and quotations using the APA 7th edition?
-Partly, some of the references do not follow APA 7th edition.
-For example, the following references don't follow APA 7th edition referencing style
-     a.   O'Boyle, 2014. O'Boyle, N. (2014). Front row friendships: Relational dialectics and identity negotiations by mature students at univerty. Communication Education, 63(3):169-191
-     b.
-Panah and Babar, 2020.
-Panah, E.
-and Babar, M.
-Y.
-(2020).
-A survey of WhatsApp as a tool for instructor-learner dialogue, learner-content dialogue, and learner-learner dialogue.
-International Journal of Educational and Pedagogical
- Sciences, 14(12):1198 - 1205.
-     c.
-Perez et al., 2020.
-Perez, J.
-Q., Daradoumis, T., and Puig, J.
-M.
-M.
-(2020).
-Rediscovering the use of chatbots in education: A systematic literature review.
-Computer Applications in Engineering Education, 28(6):1549- 1565.
-     d.
-Ranoliya et al., 2017.
-Ranoliya, B.
-R., Raghuwanshi, N., and Singh, S.
-(2017).
-Chatbot for university related faqs.
-In 2017 International Conference on Advances in Computing, Communications and Informatics (ICACCI), pages 1525-1530.
-IEEE.
-     e.
-Roblyer et al., 2010.
-Roblyer, M., McDaniel, M., Webb, M., Herman, J., and Witty, J.
-V.
-(2010).
-Findings on facebook in higher education: A comparison of college faculty and student uses and perceptions of social networking sites.
-The Internet and Higher Education, 13(3):134 - 140.}
-
- We have used, as instructed by the template, the {\tt apalike} style in our
-  LaTeX source, as well as used standard BiBTeX files downloaded from the
-  publication itself. No tweaking has been mede on these, so I don't see what we
-  can do about it, other than report a bug in the style to the authors.
-
-We have been checking out the issue, and apparently the problem is that the 7th
-edition is not well covered by the current LaTeX styles, which are stuck at the
-6th edition. A pretty extensive change in tooling is needed, unfortunately,
-including the style of bibliography citation and the tool used for doing
-that. So while there's a path for doing this, we do not think it is something we
-should devote our time in the current version of the paper, if the reviewer does
-not mind. We will certainly do so as required by publication when (or if) this
-paper is finally accepted
-
-% -> answer 10      
-{\it 10.
-Is the article written in a clear and intelligible style to a reasonably well-informed international professional readership?
-Yes.
-However, there are a few grammatical errors.
-I suggest the authors proofread the manuscript to correct them.}
-
-The authors apologise for the grammatical errors and have strived to fix them and to avoid them in the new paragraphs.
-
-% -> answer 11
-{\it 11.     Other few comments the authors should consider:
-   a.   Reorganize the conclusion section to highlight the main aim of the research work briefly, key findings and the significance of the work, and future research work.
-   b.
-Some of the paragraphs in the conclusion section can be moved to Discussion.
-The Discussion section can be captioned as Discussion and Implications to cater for some of the paragraphs that will be moved to this section.
-For example, paragraphs on Page 23, Line 16, "In our survey..." and Page 23, Line 37, "One of the questions we made in the second survey..." should be moved to the Discussion and Implication section.}
-
-To address these final comments:
-    a. as cited before, the abstract and other sections have been rewritten
-    highlighting the key findings and the significance of this work as compared
-    with the others.
-
-    b. We have changed the title and moved the indicated paragraph. Thanks for
-    the suggestion.
-
-%%%%%% Rev 4
-
-{\bf Reviewer \#4}: {\it First of all, this paper seems to be the main topic of 'Analysis from the teacher's perspective of chatbots and messaging platforms in class'.
-It seems that simple survey results were analyzed and grouped.
-It seems like a lot of effort was put into it, but I doubt whether it has any academic significance.
-Why did you choose 4 questions? Is it appropriate for a chatbot and messaging platform if I just ask and group this? I am not sure.
-Looking at the research results and conclusions, there are some contents that are difficult to see as valid because the evidence for the researcher's conclusions is so abrupt and abstract.}
-
-The authors thank the reviewer for provinding useful feedback that has allowed
-us to improve the quality of the paper.
-
-Regarding the first issue (the lack of academic significance), we would like to
-stress the importance of the topic of artificial intelligence tools bringing
-changes in our lifestyle in the comming years. This study shares experiences
-from the academic and educational point of view and analyses the results
-obtained. Nonetheless, the Introduction (as well as other sections) has been
-rewritten with the hope of addressing the academic significance in a clearer
-way.
-
-Regarding the validation of the methodology, there is a new subsection that
-presents the validation procedure by means of an expert board which agrees with,
-in general, agrees with the questions and answers we used in the survey.
-
-For the final comment, we have rewritten the conclusions and abstract to improve
-the way the content is explained.
+We have rewritten almost every paragraph of the paper, notably those that have
+been pointed out in your review. We are again grateful for these suggestions.
 

### 2023-03-03 edubots_surveys.Rnw
:rotating_light:

@@
 but also any means provided by their university for communicating with students,
-such as a feature of the cmapus-wide learning management system that emails
+such as a feature of the campus-wide learning management system that emails
 grades to students. This suggests that teachers have a need for communication
